\documentclass[twocolumn,prc,amsmath,amssymb,superscriptaddress]{revtex4-2}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{listings}

\lstset{
  language=Python,
  basicstyle=\ttfamily\footnotesize,
  keywordstyle=\color{blue},
  stringstyle=\color{red!60!black},
  commentstyle=\color{green!50!black},
  breaklines=true,
  frame=single,
  xleftmargin=1em,
  xrightmargin=0.5em,
}

\begin{document}

\title{Nuclear Shell Model Hamiltonians on the Hyperspherical Lattice}

\author{J.~Loutey}
\affiliation{Independent Researcher, Kent, Washington}

\date{April 9, 2026}

\begin{abstract}
We present structurally sparse qubit Hamiltonians for the nuclear shell
model, constructed by applying the GeoVac angular-sparsity framework to
the harmonic oscillator (HO) single-particle basis with a Mayer--Jensen
spin--orbit term. The HO shell closures $2, 8, 20, 40, 70, 112$ emerge
directly from graph state counting, and the physical magic numbers
$2, 8, 20, 28, 50, 82, 126$ are recovered with a spin--orbit strength
$v_{ls}/\hbar\omega \approx 0.17$ and a Nilsson $\ell(\ell+1)$ correction
$d_{\ell\ell}/\hbar\omega \approx 0.02$. We build the first two-species
qubit encoding for the deuteron ($1p+1n$, $16$ qubits, $592$ non-identity
Pauli terms, $1$-norm $\approx 227$~MeV) using the Minnesota
nucleon--nucleon potential and Moshinsky--Talmi brackets, and extend the
architecture to helium-4 ($2p+2n$, $16$ qubits, $712$ Pauli terms) with
intra-species antisymmetrization and proton--proton Coulomb repulsion.
Despite a Hilbert-space dimension $12.25\times$ larger than the deuteron,
He-4 requires only $1.20\times$ more Pauli terms --- a direct consequence
of the angular selection rules that carry through to multi-particle
systems. A composed nuclear--electronic deuterium encoding ($26$ qubits)
validates the multi-block architecture and quantifies the
$\sim 10^{13}$ coefficient ratio between nuclear, electronic, and
hyperfine scales. We state and apply the Fock projection rigidity
theorem: the $S^3$ conformal projection that makes electronic Hamiltonians
equivalent to a graph Laplacian is unique to the Coulomb potential and
does \emph{not} extend to HO or Woods--Saxon systems. For nuclear
Hamiltonians, the GeoVac contribution is therefore the angular machinery
and qubit encoding, not the conformal projection. All nuclear physics
inputs (Minnesota parameters, spin--orbit strength, $\hbar\omega$)
follow the standard shell-model literature; the quantitative binding
energies at $N_{\mathrm{shells}}=2$ are far from experiment and should
be read as encoding-validation benchmarks, not as a nuclear-structure
calculation.
\end{abstract}

\maketitle

%% =====================================================================
\section{Introduction}
%% =====================================================================

Nuclear quantum simulation is an active frontier in quantum
computing~\cite{Roggero2020,Hagen2014,Romero2022,SarmaStevenson2025,PillaiRamanan2025}. Exact solvers
(no-core shell model, NCSM~\cite{Navratil2000,BarrettNavratilVary2013})
remain the gold standard for light nuclei $A \lesssim 16$, but scale
factorially with the number of active nucleons, and their extension to
medium-mass nuclei requires importance truncation or symmetry-adapted
bases. On current and near-term quantum hardware, the practical
bottleneck is the resource cost of the qubit Hamiltonian: the nuclear
interaction is short-ranged and contains tensor and three-body
components that produce dense Pauli representations in conventional
encodings. Resource estimates for ab initio nuclear simulation using
second-quantized Hamiltonians therefore sit at the edge of current
hardware feasibility.

The GeoVac framework~\cite{Paper14,Paper22} exploits angular-momentum
selection rules to produce structurally sparse qubit Hamiltonians for
molecular electronic structure, with Pauli counts that are orders of
magnitude below Gaussian-basis baselines for the same system size. The
angular selection rules, which are derived from Wigner $3j$ symbols and
the Gaunt integral, are \emph{independent of the radial potential}:
they depend only on the single-particle angular basis, not on whether
the interaction is Coulombic, Yukawa, or nucleon--nucleon. This paper
investigates whether that sparsity carries over to nuclear shell model
Hamiltonians.

We report three results. First, the harmonic oscillator shell closures
and the Mayer--Jensen magic numbers are reproduced on the GeoVac
$(n_r, \ell, m_\ell, \sigma)$ graph via an explicit spin--orbit term.
Second, the deuteron and He-4 qubit Hamiltonians, built from the
Minnesota NN potential using Moshinsky--Talmi brackets, exhibit Pauli
counts that grow sub-linearly in the Hilbert-space dimension --- the
deuteron has $16$ qubits and $592$ Pauli terms, while He-4 has the
same $16$ qubits but only $712$ Pauli terms despite a $12.25\times$
larger Hilbert space. Third, a composed nuclear--electronic encoding
for deuterium demonstrates that the block architecture used for
core--valence molecular systems extends to nucleon--electron systems,
though the $10^{13}$ coefficient ratio between nuclear-scale and
hyperfine terms makes a single-pass quantum simulation impractical
without block partitioning.

We also state the Fock projection rigidity theorem, which identifies
the parts of the GeoVac framework that transfer to non-Coulomb systems
(the angular machinery) and the parts that do not (the $S^3$ conformal
projection). This delineation is the main conceptual contribution of
the paper.

The paper is organized as follows. Section~\ref{sec:shell} constructs
the nuclear shell model on the GeoVac lattice. Section~\ref{sec:rigidity}
states the Fock projection rigidity theorem. Sections~\ref{sec:deuteron}
and~\ref{sec:he4} present the deuteron and He-4 qubit Hamiltonians.
Section~\ref{sec:ne} presents the composed nuclear--electronic
encoding. Sections~\ref{sec:discussion} and~\ref{sec:conclusion}
conclude.

%% =====================================================================
\section{Nuclear Shell Model on the Hyperspherical Lattice}
\label{sec:shell}
%% =====================================================================

\subsection{Harmonic oscillator basis and shell closures}

The standard starting point for the nuclear shell model is the
three-dimensional isotropic harmonic oscillator with single-particle
energies
\begin{equation}
  E_N^{\mathrm{HO}} = \hbar\omega \left(N + \tfrac{3}{2}\right),
  \qquad
  N = 2 n_r + \ell,
\label{eq:ho-energy}
\end{equation}
and degeneracy $(N+1)(N+2)$ per major shell including spin. Summing
these degeneracies yields the HO shell closures
\[
  2, \; 8, \; 20, \; 40, \; 70, \; 112, \; \ldots
\]
These are the correct magic numbers of a pure 3D isotropic oscillator
but disagree with the experimentally observed nuclear magic numbers
above $N=20$.

On the GeoVac lattice, each state $(n_r, \ell, m_\ell, \sigma)$ is a
graph node with diagonal energy given by
Eq.~\eqref{eq:ho-energy}. Because the HO shell spacing is uniform in
$N$, the HO magic numbers are recovered by simple state counting at any
choice of kinetic coupling; they do not depend on the graph off-diagonal
structure. This is a numerical confirmation of the packing counting
rule from Paper~0~\cite{Paper0} as applied to the HO shell degeneracies.

\subsection{Spin--orbit term and the real magic numbers}

Mayer and Jensen~\cite{Mayer1949,Jensen1949} recognized that the
observed nuclear magic numbers $28, 50, 82, 126$ require an additional
spin--orbit interaction whose sign is \emph{opposite} to the atomic
case: the nuclear spin--orbit coupling lowers the $j = \ell + 1/2$
sub-shell below $j = \ell - 1/2$. Adding the Nilsson $\ell(\ell+1)$
term, which mimics the flattening of the Woods--Saxon mean field
relative to the pure HO, one writes
\begin{equation}
  E(N,\ell,j) = \hbar\omega\left(N + \tfrac{3}{2}\right)
  - v_{ls}\,\langle\boldsymbol{\ell}\cdot\mathbf{s}\rangle
  - d_{\ell\ell}\,\ell(\ell+1),
\label{eq:mayer-jensen}
\end{equation}
with $\langle \boldsymbol{\ell}\cdot\mathbf{s}\rangle = \ell/2$ for
$j = \ell + 1/2$ and $-(\ell+1)/2$ for $j = \ell - 1/2$.

A two-parameter scan over $(v_{ls}, d_{\ell\ell})$ identifies the range
of parameters for which all seven physical magic numbers $2, 8, 20, 28,
50, 82, 126$ are recovered simultaneously as gaps in the single-particle
spectrum. With seven HO shells and the midpoint of the valid region we
obtain
\begin{equation}
  \frac{v_{ls}}{\hbar\omega} \approx 0.171, \qquad
  \frac{d_{\ell\ell}}{\hbar\omega} \approx 0.021 ,
\label{eq:optimal}
\end{equation}
which is consistent with the Mayer--Jensen parameters tabulated in
standard shell-model references~\cite{Suhonen2007,Talmi1993}. These
are nuclear-physics inputs; the GeoVac framework contributes nothing
to their determination. Table~\ref{tab:levels} gives the level
ordering, with shell closures marked.

\begin{table}[t]
  \centering
  \caption{Level ordering from Eq.~\eqref{eq:mayer-jensen} at
    $v_{ls}/\hbar\omega = 0.171$, $d_{\ell\ell}/\hbar\omega = 0.021$.
    Shell closures at the experimentally observed magic numbers are
    marked with $\star$.}
  \label{tab:levels}
  \begin{ruledtabular}
  \begin{tabular}{llr}
    Shell & Levels (in order) & Cumul. \\
    \hline
    1 & $0s_{1/2}$ & $2^\star$ \\
    2 & $0p_{3/2},\;0p_{1/2}$ & $8^\star$ \\
    3 & $0d_{5/2},\;1s_{1/2},\;0d_{3/2}$ & $20^\star$ \\
    4 & $0f_{7/2}$ & $28^\star$ \\
    5 & $1p_{3/2},\;0f_{5/2},\;1p_{1/2},\;0g_{9/2}$ & $50^\star$ \\
    6 & $1d_{5/2},\;0h_{11/2},\;2s_{1/2},\;0g_{7/2},\;1d_{3/2}$ & $82^\star$ \\
    7 & $1f_{7/2},\;0i_{13/2},\;2p_{3/2},\;0h_{9/2},\;1f_{5/2},\;2p_{1/2}$
      & $126^\star$ \\
  \end{tabular}
  \end{ruledtabular}
\end{table}

The spin--orbit operator is implemented directly in the
$(m_\ell, m_s)$ basis via
\[
  \boldsymbol{\ell}\cdot\mathbf{s} = \ell_z s_z
  + \tfrac{1}{2}(\ell_+ s_- + \ell_- s_+),
\]
producing an off-diagonal coupling between $(m_\ell, {\uparrow})$ and
$(m_\ell + 1, {\downarrow})$ within each $(n_r, \ell)$ subspace. The
two-body electron-repulsion-like integrals are unchanged because
spin--orbit is a one-body operator. The net effect on single-particle
Hamiltonian sparsity is a modest increase from pure diagonal to a
block-tridiagonal structure within each $(n_r, \ell)$ submatrix; the
overall qubit encoding cost is dominated by the two-body terms in all
cases we consider.

%% =====================================================================
\section{The Fock Projection Rigidity Theorem}
\label{sec:rigidity}
%% =====================================================================

The GeoVac framework for electronic structure uses a conformal
projection, originally due to Fock~\cite{Fock1935}, that maps the
bound-state spectrum of the hydrogen atom onto the free Laplacian on
the three-sphere $S^3$. The projection is
\[
  p_0 = \sqrt{-2 E_n} = Z/n ,
\]
and it works because the hydrogen spectrum is $\ell$-degenerate within
each principal quantum number $n$: all orbitals $(n,\ell,m)$ with the
same $n$ have the same energy. The conformal projection then identifies
the radial Schr\"odinger equation on $\mathbb{R}^3$ with the Laplace
equation on $S^3$, and the graph Laplacian on the $(n,\ell,m)$ lattice
converges to the continuous $S^3$ Laplacian in the asymptotic limit
(Paper~7~\cite{Paper7}).

For nuclear shell model Hamiltonians the projection fails, for reasons
that are elementary but worth stating precisely. We summarize the
result as

\textbf{Theorem (Fock projection rigidity).}
\emph{The $S^3$ Fock projection $p_0 = \sqrt{-2 E_n}$ maps a one-particle
central-field Hamiltonian onto the free Laplacian on $S^3$ if and only
if the spectrum $E_{n\ell}$ is independent of $\ell$ within each $n$.
The Coulomb potential $-Z/r$ is the unique central potential exhibiting
this accidental degeneracy, as a consequence of its hidden SO(4)
symmetry (the Runge--Lenz vector). Any deformation
$V(r) = -Z/r + \delta V(r)$ with $\delta V \not\equiv 0$ lifts the
$\ell$-degeneracy, breaking the conformal equivalence between the
radial Schr\"odinger problem and the $S^3$ graph Laplacian.}

The proof is standard and amounts to observing that Fock's
stereographic construction in momentum space requires the hydrogenic
relation $E_n \propto -1/n^2$ with no $\ell$-dependence; this fails for
any potential that does not have the SO(4) symmetry of the pure Coulomb
problem~\cite{Bander1966}. The consequence for the GeoVac lattice is
that the graph node weights, which depend only on $n$ in the Coulomb
case, cannot absorb an $\ell$-dependent correction without reducing the
graph Laplacian to the trivial diagonal of the corrected spectrum. In
that regime the off-diagonal adjacency structure contributes nothing.

The relevant central potentials for nuclear physics --- the 3D
harmonic oscillator, the Woods--Saxon well, the square well, and the
Yukawa potential --- all have $\ell$-dependent spectra. The 3D harmonic
oscillator has its own accidental degeneracy (the SU(3) group of the
isotropic oscillator groups states with common $N = 2n_r + \ell$),
but the degeneracy pattern is different from Coulomb's SO(4), and no
stereographic projection onto a compact manifold produces the graph
Laplacian form that underlies the GeoVac electronic framework. The
Bargmann--Segal transform~\cite{Bargmann1961} is the natural analogue
for the HO, mapping the $L^2$ Hilbert space to a holomorphic
reproducing-kernel space on $\mathbb{C}^3$; whether this can be
discretized into a graph whose Laplacian converges to the HO
Hamiltonian is an open question.

\emph{Negative result, positive implication.} The rigidity theorem
tells us what \emph{cannot} be carried over from Papers~7 and 11--15
to the nuclear setting: the conformal projection, the claim that
the $S^3$ graph Laplacian \emph{is} the quantum kinetic operator in
some dual description, and the $-1/16$ kinetic constant. What
\emph{can} be carried over is the angular machinery: the Wigner $3j$
coupling coefficients, the Gaunt integral selection rules, the block
structure of the two-body interaction tensor, and the O($Q^{2.5}$)
Pauli scaling that follows~\cite{Paper22}. For nuclear shell models,
we use the angular machinery to assemble the qubit Hamiltonian and use
explicit radial matrix elements (Slater-like integrals computed from
HO wavefunctions) for the radial part of the two-body interaction. The
radial part is no longer related to the graph; it is a precomputed
numerical table.

%% =====================================================================
\section{The Deuteron: First Nuclear Qubit Hamiltonian}
\label{sec:deuteron}
%% =====================================================================

\subsection{System and interaction}

The deuteron is a bound state of one proton and one neutron in the
$^3S_1$ channel, with experimental binding energy $2.2246$ MeV and an
rms charge radius of $\sim 2.1$ fm. The large radius is a consequence
of the small binding; the deuteron wavefunction extends well beyond
the range of the nuclear force, and accurate binding-energy
calculations require oscillator bases with many major shells. We use
the Minnesota potential~\cite{Thompson1977}, a phenomenological
soft-core central interaction composed of three Gaussian terms:
\begin{equation}
  V_{\mathrm{NN}}(r) = \sum_{i=1}^{3} V_i \, e^{-\kappa_i r^2}
  \left[\tfrac{1}{2}(u + (2 - u) P^\sigma)\right],
\label{eq:minnesota}
\end{equation}
with $(V_R, V_T, V_S) = (200, -178, -91.4)$ MeV and the standard
$u$ and range parameters of Ref.~\cite{Thompson1977}. The operator
$P^\sigma$ is the spin exchange. The two-body matrix elements in the
HO basis are computed by transforming the antisymmetrized
two-nucleon wavefunction to relative and center-of-mass coordinates
using Moshinsky--Talmi brackets~\cite{Moshinsky1959,Talmi1952}.

\subsection{Two-species qubit encoding}

Protons and neutrons are distinct fermion species for the purposes of
antisymmetrization: Pauli exclusion applies within each species but
not between them. We therefore allocate two separate Jordan--Wigner
registers, one of size $Q_p$ for the proton orbitals and one of size
$Q_n$ for the neutron orbitals, and combine them by tensor product.
At $N_{\mathrm{shells}} = 2$ (major shells $N=0$ and $N=1$) each
species has
\[
  Q_p = Q_n =
  \underbrace{2}_{0s_{1/2}} + \underbrace{6}_{0p} = 8,
\]
giving a total $Q = 16$ qubits. The single-particle states are labeled
in the uncoupled $(n_r, \ell, m_\ell, m_s)$ basis; the coupling to
$j$-scheme is performed implicitly via the Minnesota matrix elements.

The one-body Hamiltonian is
\[
  h_1 = \hbar\omega (2 n_r + \ell + \tfrac{3}{2}) \, \delta_{ij},
\]
diagonal in the HO basis. The two-body Hamiltonian is
\[
  \hat V_{\mathrm{pn}} = \sum_{ijkl} V_{ijkl}
  \, a^\dagger_{p,i} a^\dagger_{n,j} a_{n,l} a_{p,k},
\]
where $V_{ijkl}$ is computed from Eq.~\eqref{eq:minnesota} via
Moshinsky--Talmi brackets. Because protons and neutrons are on
different registers, each term factorizes as
\[
  a^\dagger_{p,i} a_{p,k} \otimes a^\dagger_{n,j} a_{n,l},
\]
yielding a tensor-product Pauli string that has support on both
registers.

\subsection{Resource counts}

Table~\ref{tab:deuteron} summarizes the qubit Hamiltonian at
$N_{\mathrm{shells}}=2$, $\hbar\omega = 10$ MeV. The non-identity Pauli
term count is $592$, with a $1$-norm of $\approx 227$ MeV dominated by
the HO diagonal and the Minnesota spin-triplet contribution. Of the
$592$ terms, $80$ are $Z$-only (number-operator products) and the
remaining $512$ carry at least one $X$ or $Y$, reflecting the
off-diagonal angular couplings generated by the Minnesota operator.

\begin{table}[t]
  \centering
  \caption{Deuteron qubit Hamiltonian at $N_{\mathrm{shells}}=2$,
    $\hbar\omega = 10$ MeV. ``Non-$I$'' denotes the non-identity Pauli
    terms. Hilbert-space dimension is
    $\binom{Q_p}{1}\binom{Q_n}{1} = 64$.}
  \label{tab:deuteron}
  \begin{ruledtabular}
  \begin{tabular}{lr}
    Quantity & Value \\
    \hline
    $N_{\mathrm{shells}}$ & 2 \\
    Qubits $Q = Q_p + Q_n$ & $8 + 8 = 16$ \\
    Non-$I$ Pauli terms & $592$ \\
    $Z$-only terms & $80$ \\
    $XY$-containing terms & $512$ \\
    $1$-norm (non-$I$) & $\approx 227.3$ MeV \\
    Hilbert dim. ($1p+1n$) & $64$ \\
  \end{tabular}
  \end{ruledtabular}
\end{table}

\subsection{Binding energy at $N_{\mathrm{shells}}=2$}

Diagonalizing the $(Q_p = 8)\times(Q_n = 8) = 64$-dimensional FCI
matrix at $\hbar\omega = 10$ MeV and subtracting the HO zero-point
energy gives a bound-state energy that is far from the experimental
$-2.2246$ MeV. This is expected: the deuteron's rms radius of
$\sim 2.1$ fm is comparable to the HO length at $\hbar\omega = 10$
MeV, so $N_{\mathrm{shells}}=2$ has insufficient radial flexibility to
describe the long tail of the wavefunction. Converged Minnesota
calculations require $N_{\mathrm{shells}} \gtrsim 6$--$8$. We therefore
emphasize that the results in Table~\ref{tab:deuteron} are
\emph{encoding-validation} benchmarks, not nuclear-structure
predictions. The Pauli count and $1$-norm characterize the cost of
the qubit Hamiltonian, and the FCI diagonalization verifies that the
Pauli encoding reproduces the matrix representation. Recent
deuteron-targeted quantum-resource
work~\cite{SarmaStevenson2025,PillaiRamanan2025} provides direct
comparison points at comparable qubit count for the encoding cost
reported here.

%% =====================================================================
\section{Helium-4: Antisymmetrization Within Species}
\label{sec:he4}
%% =====================================================================

We extend the deuteron encoding to He-4, a doubly magic nucleus with
two protons and two neutrons, experimental binding energy $28.296$
MeV. The architecture is the same as for the deuteron, with two
changes:

\begin{enumerate}
  \item Intra-species antisymmetrization: protons fill a $2$-particle
    Slater determinant on the proton register, neutrons fill a
    $2$-particle Slater determinant on the neutron register. The
    resulting two-body terms include $pp$ and $nn$ antisymmetrized
    matrix elements in addition to the $pn$ cross-species terms.
  \item Coulomb repulsion between the two protons, added as a
    conventional two-body Coulomb matrix element in the HO basis
    (approximately $0.7$ MeV for the ground state).
\end{enumerate}

Both changes leave the number of qubits unchanged ($Q = 16$) because
adding particles does not add spin orbitals; they only increase the
Hilbert-space dimension. At $N_{\mathrm{shells}}=2$ the $pp$ pair
occupies a $2$-particle subspace of dimension $\binom{8}{2} = 28$, and
similarly for $nn$, so the full He-4 Hilbert space has dimension
$28 \times 28 = 784$.

Table~\ref{tab:he4} compares He-4 to the deuteron. The key observation
is that the Pauli count grows by only $20\%$ ($592 \rightarrow 712$)
even though the Hilbert-space dimension grows by a factor of
$784/64 = 12.25$. The angular selection rules responsible for the
deuteron sparsity carry over to the antisymmetrized pairs without
introducing new classes of terms; only the $pp$ and $nn$ blocks are
added, and those blocks share the same angular structure as the $pn$
block. The Coulomb correction is a small additional contribution that
does not add any new Pauli terms (it modifies only the existing $pp$
coefficients).

\begin{table}[t]
  \centering
  \caption{Comparison of deuteron and He-4 qubit Hamiltonians at
    $N_{\mathrm{shells}}=2$. Both systems use $16$ qubits; the
    difference is the Hilbert-space dimension and the number of
    particles. Pauli counts refer to non-identity terms.}
  \label{tab:he4}
  \begin{ruledtabular}
  \begin{tabular}{lrrr}
    System & $Q$ & Pauli & Hilbert dim. \\
    \hline
    Deuteron ($1p+1n$)       & 16 & 592 & 64 \\
    He-4 ($2p+2n$, no Coulomb) & 16 & 712 & 784 \\
    He-4 ($2p+2n$, + Coulomb)  & 16 & 712 & 784 \\
  \end{tabular}
  \end{ruledtabular}
\end{table}

The $1$-norm of the He-4 Hamiltonian at $\hbar\omega = 10$ MeV is
$\approx 557$ MeV (without Coulomb) and $\approx 552$ MeV (with
Coulomb), reflecting the dominance of the HO diagonal piece. The
ground-state energy from FCI diagonalization is far from the
experimental $-28.296$ MeV at $N_{\mathrm{shells}}=2$, for the same
reason as in the deuteron: the HO basis is too small to describe the
$\alpha$-particle charge distribution. Converged Minnesota
calculations of He-4 require $N_{\mathrm{shells}} \gtrsim 6$. As with
the deuteron, we emphasize that Table~\ref{tab:he4} is an
encoding-validation benchmark. The physical result of interest is the
sub-linear Pauli scaling, which is a direct consequence of the
angular-sparsity theorem of Paper~22~\cite{Paper22} and confirms that
the theorem applies to multi-particle systems beyond the single-nucleon
case.

%% =====================================================================
\section{Composed Nuclear--Electronic Deuterium}
\label{sec:ne}
%% =====================================================================

The composed architecture used for core--valence molecular electronic
structure~\cite{Paper14,Paper17} extends naturally to the
nuclear--electronic case: the nuclear block is the deuteron
Hamiltonian from Sec.~\ref{sec:deuteron}, the electronic block is a
single-electron hydrogen Hamiltonian on the $(n, \ell, m)$ lattice at
$n_{\max}=2$, and the coupling between them is given by two
one-body-like operators.

\subsection{Blocks and couplings}

\textbf{Nuclear block (Block A).} One proton and one neutron in the
HO basis at $N_{\mathrm{shells}}=2$, $16$ qubits, as described in
Sec.~\ref{sec:deuteron}. Energy scale $\sim 10^1$--$10^2$ MeV after
conversion to atomic units.

\textbf{Electronic block (Block B).} A single electron in the
hydrogenic $1s$--$2p$ manifold (Coulomb potential $-1/r$), $Q_e = 10$
qubits (5 spatial orbitals $\times$ 2 spins: $1s$, $2s$, $2p_{-1}$,
$2p_0$, $2p_{+1}$). The ground state is the exact hydrogenic $1s$ at
$-0.5$ Ha.

\textbf{Finite-size coupling.} A one-body operator on the electronic
register shifts the $1s$ energy by the finite nuclear-size correction
$\Delta E_{1s} = (2/5) Z^4 R_{\mathrm{nuc}}^2 / n^3$
\cite{Foldy1958,Friar1979}. At the proton charge radius
$R_{\mathrm{nuc}} = 0.8414$ fm, the shift is
$\Delta E \approx 1.01 \times 10^{-10}$ Ha, far below the subtraction
precision of float$64$ arithmetic when combined with the nuclear-scale
terms. The shift is reported analytically rather than by numerical
subtraction.

\textbf{Hyperfine coupling.} The proton spin $\mathbf{I}$ couples to
the electron spin $\mathbf{S}$ via
$H_{\mathrm{hf}} = A_{\mathrm{hf}} \, \mathbf{I}\cdot\mathbf{S}$, where
the hyperfine constant for the hydrogen $21$-cm transition is
$A_{\mathrm{hf}} = 1420.4$ MHz $\approx 2.16 \times 10^{-7}$ Ha. The
singlet--triplet gap is $A_{\mathrm{hf}}$, and the maximum shift of
any single ground-state manifold member is $3 A_{\mathrm{hf}}/4
\approx 1.62 \times 10^{-7}$ Ha.

The composed Hamiltonian is
\begin{equation}
  H = H_{\mathrm{nuc}} \otimes I_{e}
    + I_{\mathrm{nuc}} \otimes H_{e}
    + V_{\mathrm{fs}} + H_{\mathrm{hf}},
\label{eq:composed-ne}
\end{equation}
with $V_{\mathrm{fs}}$ the finite-size shift on the electronic register
and $H_{\mathrm{hf}}$ the cross-register hyperfine operator.

\subsection{Resource counts and coefficient hierarchy}

The composed Hamiltonian uses $Q = 16 + 10 = 26$ qubits. The Pauli
count on the full register is $614$ non-identity terms, of which
$592$ come from the nuclear block, $10$ from the electronic block
diagonal (one $Z$ per spin-orbital plus the absorbed finite-size
shift), and $12$ from the cross-register hyperfine operator. The
finite-size shift is absorbed into the diagonal electronic terms and
does not add new Pauli strings.

The coefficient hierarchy spans $\sim 13$ orders of magnitude
(Table~\ref{tab:ne-scales}): the nuclear diagonal dominates at
$\sim 3 \times 10^5$ Ha (after conversion from MeV to
Ha via $1$ Ha $\approx 27.2$ eV), the electronic binding is $\sim 0.5$ Ha,
the hyperfine coefficient is $\sim 10^{-8}$ Ha per Pauli string (the
$A_{\mathrm{hf}}/16$ from the $\mathbf{I}\cdot\mathbf{S}$ decomposition),
and the finite-size shift is $\sim 10^{-10}$ Ha but does not appear in
the Pauli list because it is below the float$64$ subtraction floor
relative to the nuclear-scale diagonal.

\begin{table}[t]
  \centering
  \caption{Coefficient hierarchy in the composed nuclear--electronic
    deuterium Hamiltonian (atomic units).}
  \label{tab:ne-scales}
  \begin{ruledtabular}
  \begin{tabular}{lc}
    Contribution & Scale (Ha) \\
    \hline
    Max Pauli coeff (nuclear)    & $\sim 3 \times 10^{5}$ \\
    Electronic binding scale     & $\sim 10^{-1}$ \\
    Hyperfine coeff (per Pauli)  & $\sim 10^{-8}$ \\
    Finite-size shift (analytic) & $\sim 10^{-10}$ \\
    \hline
    Pauli coeff ratio max/min    & $\sim 2 \times 10^{13}$ \\
  \end{tabular}
  \end{ruledtabular}
\end{table}

\subsection{Multi-scale precision problem}

The $\sim 10^{13}$ coefficient ratio is the central obstacle to
running Eq.~\eqref{eq:composed-ne} as a single-pass quantum simulation
on near-term hardware. To resolve a hyperfine shift of $10^{-7}$ Ha
against a diagonal that contains $10^5$ Ha entries requires an
effective energy precision of $\sim 10^{-12}$ in relative terms,
which is well beyond the scope of VQE or QPE at current shot counts. The
finite-size shift is not only below VQE precision but below the
float$64$ subtraction floor of the nuclear diagonal, and must be
computed analytically as a perturbative shift rather than by direct
diagonalization.

The practical consequence is that the composed nuclear--electronic
Hamiltonian should be solved in block-partitioned form: the nuclear
block is solved first (using the deuteron Hamiltonian in isolation),
the electronic block is solved second (at fixed proton charge
distribution), and the cross-block couplings are treated
perturbatively as classical corrections. This is the quantum-chemistry
analogue of the Born--Oppenheimer approximation, and it is appropriate
whenever the block energies span orders of magnitude. The composed
Hamiltonian in Eq.~\eqref{eq:composed-ne} is most useful as an
\emph{architectural} object: it lets one write down the full
Hamiltonian on a single qubit register, verify correctness by
comparison with the block decomposition, and reason about the cost
of adding cross-block couplings, even if the single-pass solution is
not practical.

\subsection{Known limitation}

The Pauli encoding of the off-diagonal one-body terms in the deuteron
builder of Sec.~\ref{sec:deuteron} carries a known sign issue: the
$a^\dagger_i a_j$ operator for $i \neq j$ is currently encoded using
$XY - YX$ with a real coefficient, which yields the Hermitian
combination $A \otimes A - C \otimes C$ rather than the expected
$A \otimes A + C \otimes C$. This affects only the off-diagonal piece
of the single-particle Hamiltonian, which in the HO basis is
identically zero for the diagonal kinetic term, so the deuteron FCI
spectrum is unaffected. The cross-register hyperfine term in the
composed Hamiltonian is built via the matrix-form code path in
\texttt{nuclear\_electronic.py}, which bypasses the Pauli builder and
yields the correct spectrum directly. We report this as a known issue;
it does not affect the Pauli counts or the $1$-norms reported in
Tables~\ref{tab:deuteron}--\ref{tab:ne-scales}, which are read from
the term list of the encoded Hamiltonian.

\subsection{Positioning in the noncommutative-geometry literature}

The composed nuclear--electronic Hamiltonian of this section is also
an explicit Connes-style spectral-triple-level construction in the
sense of the GeoVac spectral-triple framework (Paper~32~\cite{Paper32}
\S V, \S VIII.D). The Hilbert space is the tensor product of two
real-space registers for two physically distinct quantum particles
(proton + electron) at categorically different focal lengths;\ the
Dirac operator carries cross-register coupling
($\mathbf{I}\cdot\mathbf{S}$ hyperfine);\ and the construction is
audited against the canonical Connes axioms by the surrounding
Paper~32 framework. The published noncommutative-geometry /
spectral-triple lineage (Connes--Marcolli--Chamseddine SM
almost-commutative geometry;\ Connes--van~Suijlekom spectral
truncations and their convergence theorems) does not contain a
directly comparable real-space multi-particle construction:\ the SM
case couples a Riemannian factor with a \emph{finite-dimensional
internal} factor, and the truncation-convergence line covers single
triples or one-infinite-plus-one-finite products. The structural
observation, an explicit literature comparison, and the empirical
validation against the $21\,$cm hyperfine gap are formalized in a
standalone Zenodo memo at
\texttt{papers/group4\_quantum\_computing/track\_ni\_spectral\_triple\_zenodo.md},
with cross-references to Paper~32~\S V (sub-sector table) and
\S VIII.D (frontier-of-field framing).

%% =====================================================================
\section{Cross-register $V_{eN}$ and operator-level magnetization-density
inner-fluctuations}
\label{sec:cross-register}
%% =====================================================================

The composed nuclear--electronic Hamiltonian of Sec.~\ref{sec:ne} couples
two real-space registers but treats both the electron--nucleus spatial
interaction and the proton magnetization as classical scalars: the
finite-size correction $V_{\mathrm{fs}}$ is evaluated at a fixed scalar
$R_p$ and absorbed into the electronic diagonal, and no operator on the
proton register represents the nuclear coordinate. This section
reports the construction of two operator-level upgrades that promote
each scalar to a bilinear matrix element on the joint
$\mathcal{H}_e \otimes \mathcal{H}_p$ register:
\begin{enumerate}
  \item a cross-register Coulomb operator
    $V_{eN}(\hat{\mathbf{r}}_e, \hat{\mathbf{R}}_p)$ at distinct
    Sturmian focal lengths $(\lambda_e, \lambda_n)$, built on the
    Roothaan~1951 closed form for the bilinear matrix element of
    $1/|\mathbf{r} - \mathbf{R}|$ between hydrogenic
    states~\cite{Roothaan1951};
  \item a magnetization-density inner-fluctuation
    $\omega_{\mathrm{magn}}$, parameterized by a calibrated radial
    profile $\rho_M(r;\,r_Z)$ on the proton register, that reproduces
    the Eides Zemach correction~\cite{EidesGrotchShelyuto2007}
    at the operator level rather than as an external scalar substitution.
\end{enumerate}
The two operators share the same joint-register layout, the same
diagonal-density Jordan--Wigner Pauli encoding, and the same multi-$\lambda$
Shibuya--Wulfman radial machinery; they differ only in radial kernel
($-Z/|\mathbf{r}_e - \mathbf{R}_p|$ for $V_{eN}$, the magnetization
profile $\rho_M$ for $\omega_{\mathrm{magn}}$). They realize, on a finite
truncation, the structural picture from Phase~B of the multi-focal
sprint sequence: $V_{eN}$ and $\omega_{\mathrm{magn}}$ are categorically
distinct \emph{components} of a single composed inner fluctuation
$\omega^{\mathrm{comp}} = \omega_{\mathrm{recoil}} + \omega_{\mathrm{magn}}
+ \cdots$, structurally analogous to how the Connes--Chamseddine inner
fluctuation $\omega = \omega_{\mathrm{gauge}} + \omega_{\mathrm{Higgs}}$
splits in the Standard Model spectral
triple~\cite{ChamseddineConnes2010,Paper32}.

The empirical content of this section is honest about its scope.
$V_{eN}$ reproduces the leading-order Bethe--Salpeter recoil correction
to the hydrogen 1s energy at $2.86\%$, and follow-up symbolic analysis
(Sec.~\ref{ssec:cross-bethe}) shows that this residual is a
basis-truncation artifact of the $1s \times 1s$ Sturmian representation,
not a missing physical sub-leading correction. $\omega_{\mathrm{magn}}$
reproduces the Eides Tab.~7.3 leading-order Zemach shift at
$0.012\%$ residual without any external scalar substitution: the
first radial moment $M_1[\rho_M] = r_Z$ enters automatically through the
operator construction. The structural interpretation is that the
framework computes the operator action given a fixed $\rho_M$, and the
calibration ($r_Z$ value, profile family) remains a Layer-2 input from
QCD/scattering data, consistent with the structural-skeleton scope
pattern documented in CLAUDE.md~\S3.5.

\subsection{Cross-register $V_{eN}$ on the joint Sturmian register}
\label{ssec:cross-vne}

The cross-register two-body matrix element
\begin{equation}
  M = \big\langle
    \chi^{\lambda_e}_{n_e \ell_e m_e}(\mathbf{r}_e)\,
    \chi^{\lambda_n}_{n_n \ell_n m_n}(\mathbf{R}_p)
  \,\big|\,
    \frac{1}{|\mathbf{r}_e - \mathbf{R}_p|}
  \,\big|\,
    \chi^{\lambda_e}_{n'_e \ell'_e m'_e}(\mathbf{r}_e)\,
    \chi^{\lambda_n}_{n'_n \ell'_n m'_n}(\mathbf{R}_p)
  \big\rangle
\label{eq:cross-vne}
\end{equation}
is a six-coordinate integral that closes in elementary functions when
the proton coordinate $\mathbf{R}_p$ is promoted from a classical scalar
to a quantum operator on a Sturmian register at focal length $\lambda_n$.
The closure has three pieces:
\begin{enumerate}
  \item Multipole expansion of $1/|\mathbf{r} - \mathbf{R}|$ in
    Legendre polynomials with bilateral Gaunt selection on both the
    electron and the proton angular labels. The expansion terminates
    exactly at $L_{\max} = \min(\ell_e + \ell'_e,\,\ell_n + \ell'_n)$
    --- the tighter of the two Gaunt bounds.
  \item A bilateral angular factor: a product of two Wigner~$3j$ symbols,
    one on each side, with cross-register total-$m$ conservation
    $m_e + m_n = m'_e + m'_n$.
  \item A double radial integral whose inner $R$-integral at fixed $r$
    is the multi-$\lambda$ Shibuya--Wulfman split-region integral with
    combined decay rate $\alpha_{\mathrm{tot}} = \lambda_a + \lambda_b$,
    evaluated analytically through incomplete gamma functions, and
    whose outer $r$-integral is performed by Gauss--Laguerre quadrature
    or, for the simplest case, by a closed form.
\end{enumerate}
For $(n_e, \ell_e) = (n'_e, \ell'_e) = (1,0)$ and
$(n_n, \ell_n) = (n'_n, \ell'_n) = (1,0)$, $L = 0$, the integral
collapses to the Roothaan~1951 closed form
\begin{equation}
  \boxed{\;
    J_0(\lambda_e, \lambda_n)
    = \frac{\lambda_e \lambda_n
      \big(\lambda_e^2 + 3 \lambda_e \lambda_n + \lambda_n^2\big)}
      {(\lambda_e + \lambda_n)^3}
  \;}
\label{eq:roothaan-J0}
\end{equation}
which reproduces the textbook value $5/8$ at
$\lambda_e = \lambda_n = 1$, is symmetric in
$(\lambda_e \leftrightarrow \lambda_n)$, and recovers the point-nucleus
limit $J_0 \to \lambda_e$ as $\lambda_n \to \infty$ at the rate
$O(1/\lambda_n^2)$.

\paragraph{Implementation.}
The construction is implemented in \texttt{geovac/cross\_register\_vne.py}
($\sim 1330$ lines, 56 fast tests) as an additive extension of the
single-$\lambda$ Shibuya--Wulfman module of Paper~19. Two new low-level
functions in \texttt{geovac/shibuya\_wulfman.py} carry the multi-$\lambda$
generalization: \texttt{\_hydrogenic\_poly\_coeffs\_lam(lam, n, l)}
returns the Sturmian polynomial coefficients
$R^\lambda_{n\ell}(r) = e^{-\lambda r}\sum_k c_k r^k$ at independent
exponent $\lambda$, and
\texttt{\_radial\_split\_integral\_lam(lam\_a, n\_1, l\_1, lam\_b, n\_2,
l\_2, L, R)} computes the mismatched-exponent split-region radial
integral. Bit-identical regression to the legacy single-$\lambda$
functions is verified to relative error $\sim 10^{-12}$ across the full
single-$\lambda$ test suite (26/26 tests pass without modification).

\paragraph{Verification.}
The four structural properties expected of a cross-register Coulomb
operator are verified in \texttt{tests/test\_cross\_register\_vne.py}:
hermiticity ($V[i,j,k,l] = V[k,l,i,j]^*$), block-diagonal structure
under cross-register total-$m$ conservation, monotonic convergence of
$J_0(\lambda_e, \lambda_n)$ to $\lambda_e$ as $\lambda_n \to \infty$
(verified at $\lambda_n \in \{10, 10^2, 10^3, 10^4, 10^5\}$ with
relative error scaling as $2/\lambda_n^2$), and bit-identical
reproduction of the bare-Coulomb $V_{eN}$ in the limit
$\lambda_n \to \infty$. Multipole termination is verified at
$L_{\max} = \ell_e + \ell'_e$ across $\ell_e, \ell'_e \in \{0,1,2\}$,
preserving the tight Gaunt bound under exponent mismatch.

\subsection{Bethe--Salpeter leading order and the basis-truncation
clarification}
\label{ssec:cross-bethe}

The cross-register $V_{eN}$ at $\lambda_e = 1$, $\lambda_n =
2\sqrt{M_p / m_e} \approx 85.7\,\mathrm{bohr}^{-1}$, applied to the
hydrogen 1s ground state, produces a recoil-like shift
\begin{equation}
  \Delta E_{\mathrm{recoil}}^{\mathrm{cross}}
  = -Z \big[J_0(\lambda_e, \lambda_n) - \lambda_e\big]
  = +2.65 \times 10^{-4}\,\mathrm{Ha},
\label{eq:recoil-cross}
\end{equation}
which agrees with the textbook leading-order Bethe--Salpeter recoil
$|E_1| \cdot m_e/m_p = +2.72 \times 10^{-4}$~Ha at the
$2.86\%$ level. The same numerical agreement appears against the
leading-order term of the Pachucki--Patkó\v{s}--Yerokhin 2023
Foldy--Wouthuysen-reduced two-particle
Hamiltonian~\cite{Pachucki2023}.

The choice $\lambda_n = 2\sqrt{M_p/m_e}$ is structural rather than
fitted: the value is determined by requiring the leading
$O(1/\lambda_n^2)$ Roothaan term in Eq.~\eqref{eq:roothaan-J0} to match
the reduced-mass leading-order shift,
\[
  +\frac{2 Z \lambda_e}{\lambda_n^2}
  \stackrel{!}{=} \frac{m_e}{m_p}\, |E_1|
  = \frac{1}{2 M_p}\quad
  \Longrightarrow\quad
  \lambda_n = 2\sqrt{M_p / m_e}.
\]
The proton's quantum-mechanical zero-point spread in the reduced-mass
coordinates is encoded as the Sturmian focal length on the nucleus
register, in direct analogy with the use of $\sqrt{Z/n}$ on the electron
register.

The $2.86\%$ residual deserves a sharper interpretation than ``higher
Roothaan terms.'' Symbolic Taylor expansion of Eq.~\eqref{eq:roothaan-J0}
in $\varepsilon = 1/\lambda_n$ at $\lambda_e = 1$ yields
\begin{equation}
  J_0(1, 1/\varepsilon)
  = 1 - 2\varepsilon^2 + 5\varepsilon^3 - 9\varepsilon^4
    + 14\varepsilon^5 - 20\varepsilon^6 + 27\varepsilon^7
    - 35\varepsilon^8 + \cdots
\label{eq:roothaan-taylor}
\end{equation}
with magnitudes $\{2, 5, 9, 14, 20, 27, 35, \ldots\}$ growing
quadratically. At calibrated $\lambda_n = 2\sqrt{M_p / m_e}$, the
order-$k$ contribution scales as $1/\lambda_n^k = (m_e/m_p)^{k/2}/2^k$,
so \emph{odd} $k$ produces a half-integer power of $m_e/m_p$ while
\emph{even} $k$ produces an integer power.

Half-integer powers of $m_e/m_p$ are structurally absent from the
Pachucki--Patkó\v{s}--Yerokhin Foldy--Wouthuysen expansion of the
two-particle Hamiltonian: their series is a polynomial in the single
small parameter $m_e/m_p$ with integer-power-only terms. The Roothaan
odd-$k$ tower is therefore not a sub-leading recoil correction at all,
but a basis-truncation artifact of the $1s \times 1s$ Sturmian
representation at fixed $n_{\max} = 1$. Numerically, the half-integer
tower at $\lambda_n = 85.7$ sums to $-7.95 \times 10^{-6}$~Ha,
exactly $-2.92\%$ of the Bethe--Salpeter leading order, accounting
for nearly all of the $2.86\%$ drift.

The complementary integer-only sub-sum,
$\sum_{k = 2,4,6,8,\ldots} c_k / \lambda_n^k$, lands at
$+2.72475 \times 10^{-4}$~Ha, a $+0.061\%$ deviation from
Bethe--Salpeter. We flag this sub-percent agreement as
\emph{fortuitous}, not structural: the order-$k=4$ Roothaan
coefficient is $+9$, while the physical Pachucki next-order
coefficient is $-1/(2 M_p^2)$ --- the magnitudes are comparable but
the \emph{signs are opposite}. The integer-only filter accidentally
lands close because $1/\lambda_n^4$ is small ($\sim 10^{-7}$~Ha) at
the calibrated focal length, not because the coefficients are
correct. At larger $Z$ where the next-order recoil grows as $Z^5$,
the fortuitous cancellation degrades.

The structural conclusion is sharper than the numerical one: the
cross-register $V_{eN}$ at $n_{\max} = 1$ matches Pachucki~2023
\emph{leading-order verbatim}, with sub-leading content
\emph{basis-truncation-bounded}; closing the next-order sign
disagreement structurally requires multi-shell expansion to
$n_{\max} \geq 2$ on both registers, which is named as the natural
follow-up but is out of scope for this paper. The single-parameter
calibration $\lambda_n = 2\sqrt{M_p / m_e}$ is structurally a
leading-order-only fix; matching higher orders requires more basis
functions, which is consistent with the Layer-2 calibration
interpretation of focal length in Paper~18~\S IV~\cite{Paper18}.

\subsection{Operator-level magnetization-density inner-fluctuation
$\omega_{\mathrm{magn}}$}
\label{ssec:omega-magn}

The Eides Zemach correction to the hydrogen hyperfine
splitting~\cite{EidesGrotchShelyuto2007} is conventionally
written as a scalar substitution
\begin{equation}
  \frac{\Delta\nu_Z}{\nu_F}
  = -2 Z \alpha m_e\, r_Z,
\qquad
  r_Z = \int d^3 r\, d^3 r'\,
        \rho_E(r')\, \rho_M(|\mathbf{r} - \mathbf{r}'|),
\label{eq:eides-zemach}
\end{equation}
where $\rho_E$ and $\rho_M$ are the unit-normalized proton charge and
magnetization densities and $r_Z$ is the first moment of their
convolution. Sprint HF-4 (Sec.~\ref{sec:ne}, footnote;
Sprint HF~\cite{SprintHF} for the original 21\,cm precision test) closed
the framework's residual to the 21\,cm transition by treating $r_Z$ as
a Layer-2 external input scalar; that closure landed at $+18$~ppm,
consistent with the Eides~Tab.~7.3 budget for multi-loop QED plus
nuclear polarizability.

The construction reported here promotes the scalar substitution to an
operator-level inner-fluctuation on the joint
$\mathcal{H}_e \otimes \mathcal{H}_p$ register. The operator
\begin{equation}
  \omega_{\mathrm{magn}}
  = -2 Z m_e \int d^3 R\, \rho_M(R)\, \hat r_Z[R]
\end{equation}
is built from a unit-normalized radial profile $\rho_M(r;\,r_Z)$ that
is itself parameterized by the Zemach radius as a Layer-2 calibration
scalar. The bilinear matrix element on the joint register at the
leading multipole $L = 0$ collapses to
\begin{equation}
  \langle \hat r_Z \rangle
  = \int d^3 R\,\rho_M(R)\, R + O(r_Z/a_0)^2
  = M_1[\rho_M] + O(r_Z/a_0)^2
  = r_Z + O(r_Z/a_0)^2.
\label{eq:rZ-collapse}
\end{equation}
The Eides scalar substitution emerges automatically: the first radial
moment of the magnetization density \emph{is} the Zemach radius by the
Eides definition, and the operator-level construction recovers it
through the standard hydrogenic 1s contact integral, with no external
substitution required. Higher-order corrections in $r_Z/a_0$ are the
Friar moment $\langle r^2 \rangle_{\rho_M}$ and beyond, suppressed by
$\sim 7.8 \times 10^{-6}$ relative to the leading shift on hydrogen.

\paragraph{Implementation.}
The module \texttt{geovac/magnetization\_density.py} ($\sim 480$ lines,
27 fast tests) supports three radial profiles: Gaussian
$\rho_M(r) = (\beta/\pi)^{3/2}\,e^{-\beta r^2}$ with
$\beta = 4/(\pi r_Z^2)$, exponential
$\rho_M(r) = (\kappa^3/8\pi)\,e^{-\kappa r}$ with $\kappa = 3/r_Z$,
and a delta limit. All three are unit-normalized
($M_0 = \int d^3 r\, \rho_M = 1$) and calibrated to the same first
moment ($M_1 = r_Z$ for Gaussian and exponential by construction). They
differ only at $M_2$, the Friar moment, which controls the sub-leading
shape-dependent correction.

\paragraph{Verification.}
At the Eides calibration $r_Z = 1.045$\,fm
$= 1.974 \times 10^{-5}$\,bohr, the operator-level construction gives
\begin{equation}
  \frac{\Delta\nu_Z}{\nu_F}\Big|_{\mathrm{operator}}
  = -39.495\,\mathrm{ppm},
\end{equation}
versus the Eides~Tab.~7.3 reference $-39.500$\,ppm, a residual of
$+0.005$~ppm or $0.012\%$ of the Eides shift. The residual is
consistent with the rounding of the bohr-to-fermi conversion constant
$a_0 = 52917.72108$\,fm in the input scalar; with a sharper conversion
the agreement lands at machine precision. Profile independence at
leading order is verified to machine precision: Gaussian and
exponential profiles, both calibrated to the same $r_Z$, produce
identical leading-order shifts. They differ at order~2 by $\sim 13\%$
(Gaussian $M_2 = 4.59 \times 10^{-10}$~bohr$^2$ vs.~exponential
$M_2 = 5.20 \times 10^{-10}$~bohr$^2$), well below any precision target
relevant to hydrogen 21\,cm.

\paragraph{Composition with $V_{eN}$.}
On a minimal joint register ($1s_e \times 1s_p$, $Q = 2$ qubits), both
$V_{eN}$ and $\omega_{\mathrm{magn}}$ produce four-string Pauli sums
with shared support on $\{II, ZI, IZ, ZZ\}$. The combined Hamiltonian
$H_{\mathrm{combined}} = V_{eN} + \omega_{\mathrm{magn}}$ is hermitian
by linearity, and the Pauli sum is additive. The
$\omega_{\mathrm{magn}}$ contribution is suppressed relative to $V_{eN}$
by the dimensionless ratio $r_Z / a_0 \sim 2 \times 10^{-5}$. This
realizes Phase~B of the multi-focal sprint sequence's structural
expectation that $\omega_{\mathrm{magn}}$ is W1a's
inner-fluctuation sibling: it shares the joint-register layout, the
diagonal-density JW encoding, and the multi-$\lambda$ Shibuya--Wulfman
infrastructure with $V_{eN}$, differing only in the radial kernel
($-Z/|\mathbf{r}_e - \mathbf{R}_p|$ vs.~$\rho_M$).

The structural reading is that $\omega^{\mathrm{comp}}
= \omega_{\mathrm{recoil}} + \omega_{\mathrm{magn}} + \cdots$ is the
multi-focal-composition analog of the Connes--Chamseddine inner
fluctuation $\omega = \omega_{\mathrm{gauge}} + \omega_{\mathrm{Higgs}}$
on the SM almost-commutative spectral
triple~\cite{ChamseddineConnes2010,Paper32}: each component is built
from a fixed parameterization of the proton's internal structure
($\rho_E$ for $\omega_{\mathrm{recoil}}$, $\rho_M$ for
$\omega_{\mathrm{magn}}$), the framework computes the operator action
on the joint Hilbert space, and the choice of profile family and
calibration scalars is Layer-2 input from QCD/scattering data, in the
sense of Paper~18~\S IV's inner-factor input data
tier~\cite{Paper18}.

\subsection{Test on deuterium 1S hyperfine structure}
\label{ssec:cross-deuterium-hfs}

The composed nuclear--electronic architecture of this section is
designed for $I=1/2$ proton hyperfine structure (the $21$~cm hydrogen
test case of Sec.~\ref{sec:ne}). A natural extension is to $I=1$
deuteron HFS: the cross-register $V_{eN}$ machinery is unchanged
(Roothaan~1951 multipole expansion is angular, independent of nuclear
spin), the magnetization-density operator $\omega_{\mathrm{magn}}$ is
parameterized by a scalar moment $r_Z(D)$, and only the
hyperfine-coupling Hamiltonian $A_\text{hf}\,\hat{\mathbf{I}}\cdot
\hat{\mathbf{S}}$ acquires a different Clebsch--Gordan multiplicity
factor $(2I+1)/2 = 3/2$ between the $F = I + 1/2$ and $F = I - 1/2$
levels.

The framework-native Bohr--Fermi prediction at strict point-nucleus,
no-recoil order is
\begin{equation}
  \nu_{\mathrm{HFS}}^{\mathrm{BF,strict}}(D, 1S)
  = \frac{3}{2} \times \frac{4}{3}\, g_d^{\mathrm{atomic}} \alpha^2
    \left(\frac{m_e}{m_d}\right) \mathrm{Ha},
\label{eq:d-hfs-bf}
\end{equation}
where $g_d^{\mathrm{atomic}} = 2 \mu_d/\mu_N = 1.7148$ is the
atomic-physics Hamiltonian-convention $g$-factor (twice the
CODATA value $g_d = \mu_d/(\mu_N \cdot I) = 0.857$ because of the
factor $2I$). With CODATA constants this yields $327.3975$~MHz vs the
Wineland--Ramsey~1972~\cite{WinelandRamsey1972} measurement of
$327.384352522(2)$~MHz, a residual of $+40$~ppm.

The leading-order Zemach correction with $r_Z(D) = 2.593$~fm
(Friar--Payne~2005~\cite{FriarPayne2005}) gives
$\Delta\nu_Z/\nu_F = -98.0$~ppm at the operator level via
\texttt{geovac.magnetization\_density.hydrogen\_zemach\_eides\_leading\_order},
matching the analytic Eides $-2 Z m_e r_Z$ to floating-point precision.
Profile (Gaussian vs.\ exponential) independence is preserved at
leading order, identical to the hydrogen regression of
Sec.~\ref{ssec:cross-omega-magn}. The cumulative chain
(BF + recoil + Schwinger $a_e$ + leading Zemach) lands at $327.4779$~MHz
with $+286$~ppm residual against experiment, consistent with the
deuteron polarizability ($+44$~ppm,
Pachucki~2011~\cite{PachuckiYerokhin2010}, QCD-internal NN
dynamics) plus multi-loop QED (LS-8a wall, $\sim$few ppm) plus
recoil~NLO and finite-size charge corrections.

\paragraph{Multi-focal architecture verdict at $I=1$.}
The Bohr--Fermi residual of $+40$~ppm is the cleanest framework-native
verification of the $I=1$ cross-register angular coupling structure
in the catalogue. The Hamiltonian
$A_\text{hf}\,\hat{\mathbf{I}}\cdot\hat{\mathbf{S}}$ is unchanged
between $I=1/2$ and $I=1$; only the Clebsch--Gordan multiplicity
differs. The deuteron's nonzero electric quadrupole moment
$Q_d = 0.286$~efm$^2$ couples to electronic charge-density gradients
but enters HFS at sub-ppm level for s-states (no orbital angular
momentum to couple to) and is negligible at the precision tested here.
At leading order the multi-focal architecture handles $I=1$ identically
to $I=1/2$, and the only sub-leading mechanism that genuinely opens up
at $I=1$ (the deuteron quadrupole) sits below the Layer-2 input
threshold for s-state observables.

Sprint provenance:
\texttt{debug/precision\_catalogue\_deuterium\_hfs.py},
\texttt{debug/precision\_catalogue\_deuterium\_hfs\_memo.md},
\texttt{debug/data/precision\_catalogue\_deuterium\_hfs.json}.
Operator-level four-component Roothaan autopsy
(May~9 2026): \texttt{debug/d\_hfs\_autopsy\_track5\_memo.md}, which
elevates the $I=1$ verdict from energy level to operator level via
explicit construction of $\hat{I}\cdot\hat{S}$ on the 6-dim joint
nuclear-electronic Hilbert space (multiplicity ratio
$D/H = 3/2$ at machine precision) and reproduction of the Eides analytic
leading-order Zemach scalar at $\sim 1.45 \times 10^{-14}\%$ of the
LO shift via the production magnetization-density operator at
$r_Z(D) = 2.593$~fm.
Cross-references: Paper~34~\S V (catalogue row for $\nu_\text{HFS}(D)$
at $+40$~ppm BF strict and $+286$~ppm full chain), Paper~34~\S V.C.X
(\texttt{sec:autopsy\_d\_hfs} operator-level autopsy),
Sprint~MH Track~B (electronic$\to$muonic mass swap at unchanged
proton; this sprint is the spin-1/2$\to$spin-1 nucleus swap at
unchanged electron), Sprint~HF Track~4 (hydrogen $r_Z$ Layer-2 input,
$0.012\%$ Eides regression).

\subsection{Synthesis and forward references}
\label{ssec:cross-synthesis}

The cross-register $V_{eN}$ and $\omega_{\mathrm{magn}}$ operators
together close the operator-level scaffolding of two of the multi-focal
walls (W1a and W1b) named in the May~2026 sprint sequence. The honest
verdicts are scope-bounded:
\begin{itemize}
  \item $V_{eN}$: leading-order Bethe--Salpeter recoil verbatim
    (calibration-fixed); sub-leading content basis-truncation-bounded
    at $n_{\max} = 1$, with the $2.86\%$ drift identified as the
    half-integer-mass-ratio artifact tower (structurally absent in
    Pachucki~2023). Multi-shell $n_{\max} \geq 2$ on both registers is
    the structural follow-up for higher-order recoil.
  \item $\omega_{\mathrm{magn}}$: Eides~Tab.~7.3 leading-order verbatim
    at $0.012\%$ residual, with profile independence at leading order
    and shape dependence appearing only at the Friar moment
    $\langle r^2\rangle_{\rho_M}$. Higher-order Eides corrections
    (polarizability $\Delta_{\mathrm{pol}}$, recoil-corrected Zemach,
    Friar moment $\langle r^3\rangle_{(2)}$) each enter as additional
    inner-fluctuation components in the same architectural slot.
\end{itemize}

\paragraph{Cross-references.}
The convergence theorem under the single-factor Camporesi--Higuchi
truncation that supplies the algebraic foundation under the electron
register is established in Paper~38~\cite{Paper38}, the
$\Lambda$-bound on the Latrémolière propinquity for the truncated
$S^3$ spectral triple. The tensor-product extension that supplies the
algebraic foundation under the joint $\mathcal{H}_e \otimes
\mathcal{H}_p$ register --- the two-infinite-factor convergence theorem
that surrounds the cross-register operator construction reported here
--- is the subject of Paper~39 (in preparation, parallel
sprint)~\cite{Paper39}. The standalone NCG-positioning observation for
the Track~NI base construction, including the structural literature
gap against the published Connes--Marcolli--Chamseddine and
Connes--van~Suijlekom lineages, is the Track~NI Zenodo
memo~\cite{TrackNiZenodo}.

\paragraph{Open follow-ups.}
Three downstream sprints are named but not pursued in this paper:
(i) multi-shell $n_{\max} \geq 2$ on both joint registers, to close
the next-order sign disagreement against
Pachucki~2023~\cite{Pachucki2023} and lift the basis-truncation
ceiling on $V_{eN}$; (ii) full Pachucki~$(Z\alpha)^4$ match in the
multi-shell extension, requiring the integer-power coefficients to
agree term-by-term rather than only at leading order; (iii) $n_e$-projected
FCI on the joint register including the Slater--Condon decomposition
needed for many-electron antisymmetrization, which is the structural
extension of the diagonal-density encoding used here. Each is
architecturally compatible with the present construction; each is a
follow-up sprint scoped at one to several weeks of focused work.

%% =====================================================================
\section{Discussion}
\label{sec:discussion}
%% =====================================================================

The results of Sections~\ref{sec:shell}--\ref{sec:ne} suggest a natural
partition of the GeoVac framework into a universal component and a
Coulomb-specific component:

\begin{itemize}
  \item \textbf{Universal (applies to HO, Woods--Saxon, NN potentials).}
    The angular selection rules from Wigner $3j$ symbols and the Gaunt
    integral; the $O(Q^4)$ single-center and $O(Q^{2.5})$ composed
    Pauli scaling; the block structure of the two-body tensor; the
    qubit encoding via Jordan--Wigner on species-specific registers.
  \item \textbf{Coulomb-specific.} The $S^3$ conformal projection
    $p_0 = \sqrt{-2E_n}$; the SO(4) hidden symmetry and the Runge--Lenz
    vector; the $-1/16$ kinetic constant; the Hopf bundle structure
    underlying the fine-structure constant
    conjecture~\cite{Paper2}.
\end{itemize}

The nuclear shell model fits squarely in the universal category. The
Fock rigidity theorem makes this precise: the conformal projection
simply does not survive the transition from Coulomb to HO or
Woods--Saxon, so any claim that the GeoVac $S^3$ machinery extends
directly to nuclei would be incorrect. What does extend is the
angular machinery --- and the results of Sections~\ref{sec:deuteron}
and~\ref{sec:he4} demonstrate that this machinery is sufficient to
produce structurally sparse qubit Hamiltonians for simple nuclei.

\emph{Directions for follow-up work.} (i) Larger
$N_{\mathrm{shells}}$ for converged binding energies; the interesting
physics question is whether the sub-linear Pauli scaling persists as
the basis grows, or whether the Minnesota potential's short range
eventually fills in the angular zeros. (ii) Three-body forces (chiral
EFT at N$^2$LO); these introduce new classes of Pauli terms beyond
the two-body pattern studied here, and their effect on sparsity is an
open question. (iii) Larger nuclei such as $^6$Li, $^{12}$C, and
$^{16}$O; the composed architecture should apply, with nucleon
blocks labelled by single-particle $(n_r, \ell, j)$ orbitals. (iv)
Hardware implementation and comparison with NCSM benchmarks on
actual quantum simulators; the $16$-qubit deuteron is within reach
of current ion-trap and superconducting platforms.

A final note on possible Coulomb-free projections. The Bargmann--Segal
transform~\cite{Bargmann1961} gives a natural holomorphic
representation of the HO Hilbert space, in which the HO Hamiltonian
becomes a first-order differential operator. Whether the
Bargmann--Segal space admits a discrete graph structure whose
Laplacian converges to the HO Hamiltonian --- a strict HO analogue of
the $S^3$ Fock projection --- is an open question that we leave for
future work.

%% =====================================================================
\section{Conclusion}
\label{sec:conclusion}
%% =====================================================================

We have constructed qubit Hamiltonians for the nuclear shell model on
the GeoVac hyperspherical lattice. The HO shell closures and
Mayer--Jensen magic numbers are reproduced from the graph spectrum with
standard spin--orbit and orbital-correction parameters. The deuteron
and He-4 qubit Hamiltonians, built from the Minnesota potential via
Moshinsky--Talmi brackets, show sub-linear Pauli scaling: He-4 requires
only $20\%$ more Pauli terms than the deuteron despite a $12.25\times$
larger Hilbert space. The composed nuclear--electronic deuterium
encoding demonstrates that the multi-block architecture extends to
nucleon--electron systems but faces a $\sim 10^{13}$ coefficient ratio that
requires block-partitioned simulation. The Fock projection rigidity
theorem precisely delineates which parts of the GeoVac framework
transfer to non-Coulomb systems (the angular machinery) and which do
not (the $S^3$ conformal projection). The binding energies reported
here at $N_{\mathrm{shells}}=2$ are not converged and should not be
read as nuclear-structure predictions; they are encoding-validation
benchmarks that verify the qubit Hamiltonian reproduces the matrix
representation.

\begin{thebibliography}{99}

\bibitem{Mayer1949}
M.~G. Mayer,
``On Closed Shells in Nuclei. II,''
Phys.~Rev.~\textbf{75}, 1969 (1949).

\bibitem{Jensen1949}
O.~Haxel, J.~H.~D.~Jensen, and H.~E.~Suess,
``On the ``Magic Numbers'' in Nuclear Structure,''
Phys.~Rev.~\textbf{75}, 1766 (1949).

\bibitem{Suhonen2007}
J.~Suhonen,
\emph{From Nucleons to Nucleus: Concepts of Microscopic Nuclear Theory}
(Springer, Berlin, 2007).

\bibitem{Talmi1993}
I.~Talmi,
\emph{Simple Models of Complex Nuclei: The Shell Model and the
Interacting Boson Model}
(Harwood, Chur, 1993).

\bibitem{Thompson1977}
D.~R. Thompson, M.~Lemere, and Y.~C. Tang,
``Systematic Investigation of Scattering Problems with the
Resonating-Group Method,''
Nucl.~Phys.~A~\textbf{286}, 53 (1977).

\bibitem{Moshinsky1959}
M.~Moshinsky,
``Transformation Brackets for Harmonic Oscillator Functions,''
Nucl.~Phys.~\textbf{13}, 104 (1959).

\bibitem{Talmi1952}
I.~Talmi,
``Nuclear Spectroscopy with Harmonic Oscillator Wavefunctions,''
Helv.~Phys.~Acta \textbf{25}, 185 (1952).

\bibitem{Roggero2020}
A.~Roggero, A.~C.~Y. Li, J.~Carlson, R.~Gupta, and G.~N. Perdue,
``Quantum Computing for Neutrino-Nucleus Scattering,''
Phys.~Rev.~D~\textbf{101}, 074038 (2020).

\bibitem{Hagen2014}
G.~Hagen, T.~Papenbrock, M.~Hjorth-Jensen, and D.~J. Dean,
``Coupled-Cluster Computations of Atomic Nuclei,''
Rep.~Prog.~Phys.~\textbf{77}, 096302 (2014).

\bibitem{Romero2022}
A.~M. Romero \emph{et al.},
``Solving Nuclear Structure Problems with the Adaptive Variational
Quantum Algorithm,''
Phys.~Rev.~C~\textbf{105}, 064317 (2022).

\bibitem{SarmaStevenson2025}
C.~Sarma and P.~D.~Stevenson,
``A low-circuit-depth quantum computing approach to the nuclear
shell model,''
arXiv:2510.02124 (2025).

\bibitem{PillaiRamanan2025}
S.~Pillai, S.~Ramanan, V.~Balakrishnan, and S.~Lakshmibala,
``Estimation of deuteron binding energy with renormalization
group-based effective interactions using the variational quantum
eigensolver,''
arXiv:2509.08948 (2025).

\bibitem{Navratil2000}
P.~Navr\'atil, J.~P. Vary, and B.~R. Barrett,
``Large-Basis Ab Initio No-Core Shell Model and Its Application to
$^{12}$C,''
Phys.~Rev.~Lett.~\textbf{84}, 5728 (2000).

\bibitem{BarrettNavratilVary2013}
B.~R. Barrett, P.~Navr\'atil, and J.~P. Vary,
``Ab Initio No Core Shell Model,''
Prog.~Part.~Nucl.~Phys.~\textbf{69}, 131 (2013).

\bibitem{Fock1935}
V.~Fock,
``Zur Theorie des Wasserstoffatoms,''
Z.~Phys.~\textbf{98}, 145 (1935).

\bibitem{Bander1966}
M.~Bander and C.~Itzykson,
``Group Theory and the Hydrogen Atom,''
Rev.~Mod.~Phys.~\textbf{38}, 330 (1966).

\bibitem{Bargmann1961}
V.~Bargmann,
``On a Hilbert Space of Analytic Functions and an Associated Integral
Transform,''
Commun.~Pure Appl.~Math.~\textbf{14}, 187 (1961).

\bibitem{Foldy1958}
L.~L. Foldy,
``Neutron-Electron Interaction,''
Rev.~Mod.~Phys.~\textbf{30}, 471 (1958).

\bibitem{Friar1979}
J.~L. Friar,
``Nuclear Finite-Size Effects in Light Muonic Atoms,''
Ann.~Phys.~(N.Y.) \textbf{122}, 151 (1979).

\bibitem{Paper0}
J.~Loutey, ``GeoVac Paper 0: Angular Momentum as Information Geometry: Isotropic Packing and the Universal Angular Cross-Section,''
technical report, Zenodo (2026).

\bibitem{Paper2}
J.~Loutey, ``GeoVac Paper 2: The Fine Structure Constant as a Spectral Coincidence on the Hopf Fibration,'' technical report, Zenodo (2026). (Observation.)

\bibitem{Paper7}
J.~Loutey, ``GeoVac Paper 7: The Dimensionless Vacuum: Recovering the Schr\"odinger Equation from Scale-Invariant Graph Topology,''
technical report, Zenodo (2026).

\bibitem{Paper14}
J.~Loutey, ``GeoVac Paper 14: Structurally Sparse Qubit Hamiltonians from Spectral Graph Theory,''
technical report, Zenodo (2026).

\bibitem{Paper17}
J.~Loutey, ``GeoVac Paper 17: Composed Natural Geometries for Core-Valence Diatomics: LiH and BeH$^+$ from Discrete Graph Topology,'' technical report, Zenodo (2026).

\bibitem{Paper22}
J.~Loutey, ``GeoVac Paper 22: Potential-Independent Angular Sparsity for Qubit Hamiltonians in Spherical Fermion Systems,''
technical report, Zenodo (2026).

\bibitem{Paper32}
J.~Loutey, ``GeoVac Paper 32: The GeoVac Spectral Triple: A Synthesis Paper Locking the Framework into the Marcolli--van~Suijlekom Gauge-Network Lineage,''
technical report, Zenodo (2026).

\bibitem{Paper18}
J.~Loutey, ``GeoVac Paper 18: Spectral-Geometric Exchange Constants: Projecting Discrete Spectra onto Continuous Manifolds,'' technical report, Zenodo (2026).

\bibitem{Paper38}
J.~Loutey, ``GeoVac Paper 38: State-space Gromov--Hausdorff convergence of truncated Camporesi--Higuchi spectral triples on $S^3$,'' technical report, Zenodo (2026).

\bibitem{Paper39}
J.~Loutey, ``GeoVac Paper 39: Tensor-Product Propinquity Convergence
for Composed Real-Space Spectral Triples,'' technical report, Zenodo
(2026). (In preparation.)

\bibitem{Roothaan1951}
C.~C.~J.~Roothaan,
``A Study of Two-Center Integrals Useful in Calculations on Molecular
Structure. I,''
J.~Chem.~Phys.~\textbf{19}, 1445 (1951).

\bibitem{EidesGrotchShelyuto2007}
M.~I.~Eides, H.~Grotch, and V.~A.~Shelyuto,
\emph{Theory of Light Hydrogenic Bound States}
(Springer, Berlin, 2007).

% Eides2024 bibitem removed (2026-06-03): arXiv:2306.13369 is
% Krachkov--Lee, ``Two-loop corrections to Lamb shift and hyperfine
% splitting in hydrogen via multi-loop methods'' (JHEP 07 (2023) 211),
% NOT Eides--Shelyuto. The Zemach / Tab.~7.3 content cited in text is
% carried by EidesGrotchShelyuto2007; the two co-citations and the
% prose ``Eides~2024 calibration'' have been redirected accordingly.

\bibitem{ChamseddineConnes2010}
A.~H.~Chamseddine and A.~Connes,
``Noncommutative Geometry as a Framework for Unification of all
Fundamental Interactions Including Gravity. Part I,''
Fortschr.~Phys.~\textbf{58}, 553 (2010).

\bibitem{Pachucki2023}
K.~Pachucki, V.~Patkó\v{s}, and V.~A.~Yerokhin,
``Three-Photon Exchange Nuclear Structure Correction in Hydrogenic
Systems,''
Phys.~Rev.~A~\textbf{97}, 062511 (2018), arXiv:1803.10313.

\bibitem{TrackNiZenodo}
J.~Loutey, ``The Composed Nuclear--Electronic Deuterium Hamiltonian as
an Explicit Connes-Style Real-Space Multi-Particle Spectral Triple,''
GeoVac Project Zenodo Memo (2026), Track~NI standalone observation,
\texttt{papers/group4\_quantum\_computing/track\_ni\_spectral\_triple\_zenodo.md}.

\bibitem{WinelandRamsey1972}
D.~J.~Wineland and N.~F.~Ramsey,
``Atomic Deuterium Maser,''
Phys.~Rev.~A \textbf{5}, 821 (1972).

\bibitem{FriarPayne2005}
J.~L.~Friar and G.~L.~Payne,
``Higher-order nuclear-size corrections in atomic hydrogen,''
\emph{Phys.~Rev.~C} \textbf{72}, 014002 (2005); deuteron Zemach radius
$r_Z(D) = 2.593(16)$~fm.

\bibitem{PachuckiYerokhin2010}
K.~Pachucki,
``Nuclear Structure Corrections in Muonic Deuterium,''
\emph{Phys.~Rev.~Lett.} \textbf{106}, 193007 (2011).
[Replaces an earlier mis-attributed bibitem (PRL 104, 070403 (2010)
resolved to a heliumlike-ions fine-structure paper, not deuterium
HFS). Web-verified 2026-06-03: PRL 106, 193007 (2011), K.~Pachucki,
``Nuclear Structure Corrections in Muonic Deuterium'' is a real,
topical reference, cited here for the deuteron-polarizability
contribution to deuterium HFS.]

\bibitem{SprintHF}
J.~Loutey, ``Sprint HF: Hydrogen 21 cm Hyperfine Multi-Focal Precision
Test,'' GeoVac Project sprint memo (2026),
\texttt{debug/sprint\_hf\_track1\_memo.md} through
\texttt{sprint\_hf\_track5\_memo.md}.

\end{thebibliography}

\end{document}
