% =====================================================================
% Paper 46 (standalone): Strong-form Lorentzian propinquity convergence
% on truncated SU(2) x U(1)_T Krein spectral triples.
%
% Strong-form Latremoliere quantum Gromov-Hausdorff propinquity on the
% FULL Krein space (no K+ restriction), via the operator-norm Lipschitz
% seminorm L_op(a) = ||[D_L, a]||_op. Five-lemma proof L1' / L2 / L3 /
% L4 / L5 on the compact-temporal Krein spectral triple at S^3 x S^1_T
% at BBB (m, n) = (4, 6) chiral basis with van den Dungen 2016 Krein
% Dirac.
%
% Math.OA / J. Geom. Phys. style; eighth math.OA standalone in the
% GeoVac series. Siblings: Paper 38 (SU(2) Riemannian propinquity),
% Paper 39 (tensor-product propinquity), Paper 40 (universal 4/pi
% rate constant on compact Lie groups), Paper 42 (Tomita-Takesaki
% Riemannian closure), Paper 43 (Lorentzian extension of the
% four-witness theorem at the modular-Hamiltonian level), Paper 44
% (Lorentzian operator-system substrate), Paper 45 (K+-restricted
% weak-form Lorentzian propinquity).
%
% Status: first draft, May 2026, post-Sprint-L3b-2 closure
% (2026-05-22). Built from internal sprint memos:
%   debug/l3b_2a_candidate_validation_memo.md      (candidate validation
%                                                    + temporal-Lipschitz
%                                                    -invisibility)
%   debug/l3b_2b_lichnerowicz_lop_memo.md          (joint L3 / Lichnerowicz
%                                                    under L_op + envelope
%                                                    erratum)
%   debug/l3b_2c_berezin_lop_memo.md               (joint L4 four+one
%                                                    properties under L_op)
%   debug/l3b_2d_propinquity_assembly_memo.md      (joint L5 assembly +
%                                                    Lambda^strong panel)
%
% Honest scope: strong-form on the NATURAL substrate (every multiplier
% commutes with J). Strong-form on an ENLARGED substrate including
% chirality-flipping generators where {J, M} = 0 remains a named
% follow-on (L3b-2f).
%
% Concurrent-work audit verdict: Paper 45's pre-submission audit
% (2026-05-18) returned CLEAR. Sprint L3b-2 closure is one week
% later, so the concurrent-work landscape is unchanged.
% =====================================================================
\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm, mathrsfs, mathtools}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue!50!black, citecolor=blue!50!black, urlcolor=blue!50!black}
% \usepackage{microtype}  % disabled: MiKTeX font-expansion environmental issue (per Paper 45)
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

\newcommand{\nmax}{n_{\max}}
\newcommand{\Nt}{N_{t}}
\newcommand{\Kmax}{K_{\max}}
\newcommand{\sthree}{S^{3}}
\newcommand{\Sone}{S^{1}}
\newcommand{\SoneT}{S^{1}_{T}}
\newcommand{\Manifold}{S^{3}\times S^{1}_{T}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\Krein}{\mathcal{K}}
\newcommand{\Op}{\mathcal{O}}
\newcommand{\Acal}{\mathcal{A}}
\newcommand{\Tcal}{\mathcal{T}}
\newcommand{\Bcal}{\mathcal{B}}
\newcommand{\opnorm}[1]{\lVert #1 \rVert_{\mathrm{op}}}
\newcommand{\Frob}[1]{\lVert #1 \rVert_{F}}
\newcommand{\cbnorm}[1]{\lVert #1 \rVert_{\mathrm{cb}}}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\SU}{\mathrm{SU}}
\newcommand{\SO}{\mathrm{SO}}
\newcommand{\Uone}{U(1)}
\newcommand{\Vol}{\mathrm{Vol}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\Mat}{M}
\newcommand{\DCH}{D_{\mathrm{CH}}}
\newcommand{\DGV}{D_{\mathrm{GV}}}
\newcommand{\DL}{D_{L}}
\newcommand{\Ddiag}{D_{L}^{\mathrm{diag}}}
\newcommand{\Doff}{D_{L}^{\mathrm{off}}}
\newcommand{\KL}{K_{L}}
\newcommand{\JL}{J_{L}}
\newcommand{\Lprop}{\Lambda^{\mathrm{strong}}}
\newcommand{\Lpropweak}{\Lambda^{L}}
\newcommand{\Lambdab}{\Lambda}
\newcommand{\Lop}{L_{\mathrm{op}}}
\newcommand{\Lblock}{L_{\mathrm{block}}}
\newcommand{\LPwk}{L^{+}_{\mathrm{P45}}}
\newcommand{\Bjoint}{B^{\mathrm{joint}}}
\newcommand{\Pjoint}{P^{\mathrm{joint}}}
\newcommand{\Kjoint}{K^{\mathrm{joint}}}
\newcommand{\KSU}{K^{\SU(2)}}
\newcommand{\KU}{K^{\Uone}}
\newcommand{\gammajoint}{\gamma^{\mathrm{joint}}}
\newcommand{\gammaSU}{\gamma^{\SU(2)}}
\newcommand{\gammaU}{\gamma^{\Uone}}
\newcommand{\Cthreejoint}{C_{3}^{\mathrm{joint}}}
\newcommand{\CthreeSU}{C_{3}^{\SU(2)}}
\newcommand{\Cthreeop}{C_{3}^{\mathrm{op}}}
\newcommand{\Cfivejoint}{C_{5}^{\mathrm{joint}}}
\newcommand{\HGV}{\mathcal{H}_{\mathrm{GV}}}
\newcommand{\Kplus}{\Krein^{+}}
\newcommand{\Kminus}{\Krein^{-}}
\newcommand{\Pplus}{P_{+}}
\newcommand{\Pminus}{P_{-}}
\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\prop}{\mathrm{prop}}
\newcommand{\spat}{\mathrm{spat}}
\newcommand{\temp}{\mathrm{temp}}
\newcommand{\chid}{\chi\text{-d}}
\newcommand{\Plancherel}{\hat}
\newcommand{\Weyl}{\mathrm{Weyl}}

\title{Strong-form Lorentzian propinquity on truncated\\
$\SU(2)\times\Uone_{T}$ Krein spectral triples:\\
the natural-substrate degeneracy and the enlarged-substrate repair target}
\author{J.~Loutey\thanks{Independent researcher. \texttt{jloutey@gmail.com}.
This work was developed in an AI-augmented agentic workflow with
Anthropic's Claude. Implementation, internal memos, and bibliographic
collation were performed collaboratively; all theorems, design choices,
and editorial decisions are the author's responsibility.}}
\date{May 2026 (preprint)}

\begin{document}
\maketitle

\begin{abstract}
We investigate the strong-form leg of the Lorentzian-extension arc for
truncated Krein spectral triples, removing the $\Kplus$-restriction of
the companion paper~\cite{paper45} by using the full-Krein-space
operator-norm Lipschitz seminorm. \textbf{The strong-form construction
on the natural substrate is descoped} (Status note below):\ that
seminorm is degenerate --- its kernel far exceeds the scalars (every
temporal multiplier is $\Lop$-invisible) --- so the closed-form bound
below is an \emph{evaluation of a rate formula}, not a distance between
quantum compact metric spaces. We work on the same
compact-temporal Wick-rotated manifold $\Manifold$, with chirality-doubled
Camporesi--Higuchi spinor space $\HGV^{\nmax}$ tensored with the
$\Nt$-mode Fourier truncation of $L^{2}(\SoneT)$, BBB
classification~\cite{bizi_brouder_besnard2018} signs at $(m, n) = (4, 6)$,
and Lorentzian Dirac
$\DL = i(\gamma^{0} \otimes \partial_{t} + \DGV \otimes I_{\Nt})$ per
van~den~Dungen~2016~\cite{vandungen2016} Proposition~4.1. The
\emph{strong-form} Lipschitz seminorm is the natural operator-norm
commutator
\begin{equation*}
   \Lop(a) \;:=\; \opnorm{[\DL, a]} \qquad \text{on the full Krein space},
\end{equation*}
in contrast to Paper~45's $\Kplus$-weak-form
$\LPwk(a) = \opnorm{[\Pplus \DL \Pplus, \Pplus a \Pplus]}$ on $\Kplus$.
The closed-form rate bound is
\begin{equation*}
   \Lprop\!\bigl(\Tcal^{L}_{\nmax,\Nt,T},\;
                 \Tcal^{L}_{\Manifold}\bigr)
   \;\le\; \Cthreeop(\nmax) \cdot \gammajoint_{\nmax,\Nt,T}
   \;\xrightarrow[(\nmax,\Nt)\to(\infty,\infty)]{}\; 0,
\end{equation*}
where (per the Status note) $\Lprop$ denotes the evaluation of this rate
formula, \emph{not} a quantum-metric distance,
with closed-form constant $\Cthreeop(\nmax) = \sqrt{1 - 1/\nmax} \to 1^{-}$,
joint mass-concentration moment
$\gammajoint = O(\log\nmax/\nmax + T/\Nt)$, and assembled multiplier
$\Cfivejoint = 1$. The numerical panel matches Paper~45's $\Kplus$-weak-form
bit-exactly: $\Lprop(2, 3) = 2.0746$, $\Lprop(3, 5) = 1.6101$,
$\Lprop(4, 7) = 1.3223$. The Riemannian-limit recovery at $\Nt = 1$ is
bit-exact (Frobenius residual $0.0$ in float64) at $\nmax \in \{2, 3, 4\}$.
The proof transports the five-lemma structure
L1$'$, L2, L3, L4, L5 of Paper~45 under the strong-form seminorm. The
load-bearing analytical input is the \emph{temporal-Lipschitz-invisibility
identity}
\begin{equation*}
   [\DL, a_{s} \otimes a_{t}]
   \;=\; i\,[\DGV, a_{s}] \otimes a_{t}
   \qquad \text{bit-exact for every $a \in \Op^{L}$},
\end{equation*}
which sharpens Paper~45 Lemma~4.3's vanishing-cross-term identity from
``the time-chirality cross term vanishes'' to ``the temporal commutator
vanishes identically on the natural substrate''. As a byproduct we
identify a finite-cutoff envelope refinement of Paper~45
eq.~(C3\_joint\_bound) (Appendix~\ref{app:correction}): the correct
supremum range for the per-harmonic Lichnerowicz constant is
$N \le 2\nmax - 1$, the Avery--Wen--Avery achievable envelope on $\nmax$
shells, rather than the stated $N \le \nmax$. The asymptotic rate formula
and Paper~45's degeneracy theorem are unchanged. The strong-form
\emph{convergence} is \emph{not} established:\ the natural-substrate
seminorm is degenerate (Status note), so the Lorentzian quantum-metric
convergence question remains a named open research target. The
enlarged-substrate construction --- chirality-flipping generators with
$\{J, M\} = 0$ (Appendix~\ref{app:enlarged}), precisely where the
commutators are non-zero --- is the named repair starting point
(Sprint~L3b-2f). The algebraic identities
(Lemma~\ref{lem:temporal_invisibility}, now read as the diagnosis of the
degeneracy) are unaffected.
\end{abstract}

\bigskip\noindent
\textbf{MSC2020 classifications:}\ 58B34 (noncommutative geometry),
46L07 (operator systems), 46L60 (applications of selfadjoint operator
algebras to physics), 46L87 (noncommutative Riemannian and metric
geometry), 46C20 (spaces with indefinite inner product (Krein spaces)).

\medskip\noindent
\textbf{Keywords:}\ Latr\'emoli\`ere propinquity, quantum
Gromov--Hausdorff convergence, Krein spectral triple, strong-form
propinquity, Bizi--Brouder--Besnard indefinite signature,
Camporesi--Higuchi Dirac, spectral truncation, operator-norm Lipschitz
seminorm, temporal-Lipschitz-invisibility, Avery--Wen--Avery
envelope.

\subsection*{Status and scope (June 2026)}
Three issues are established upstream of this paper: (i) the
$\Kplus$-restricted compressed-Dirac Lipschitz seminorm underlying
$\Lpropweak$ vanishes identically on the truncated operator system
--- Krein-self-adjointness of the anti-Hermitian spatial part
$i\,\DGV \otimes I$ forces $\{\JL, \DGV \otimes I\} = 0$, so the
$\Kplus$ compression annihilates the spatial Dirac, and the
momentum-diagonal temporal multipliers commute with $\partial_t$
(verified bit-exact at $(\nmax, \Nt) \in \{(2,3), (3,5)\}$); (ii)
the ``Latr\'emoli\`ere Thm~5.5 / Def.~3.4 / Def.~3.5'' references
cited for the tunneling-pair bound do not exist in the cited source
--- the device actually used is van~Suijlekom's state-space
Gromov--Hausdorff framework; (iii) the constant $2/(\nmax + 1)$ is
the maximum of the Plancherel mass distribution, not a cb-norm of
any map used in the proofs (the smoothing map is unital completely
positive, with cb-norm $1$).

Consequently the main strong-form theorems of this paper
(Theorem~\ref{thm:main} and its transports) are \emph{descoped
pending repair}. The bit-exact equality
$\Lprop = \Lambda^{\mathrm{P45}}$ presented as the ``free upgrade''
(Remark~\ref{rem:free_upgrade}) reflects that both quantities are
evaluations of the same closed-form rate formula $\Cthreeop \cdot
\gammajoint$, and the natural-substrate seminorm $\Lop$ has kernel
far exceeding the scalars (every multiplier $\mathbf{1} \otimes
M^{\temp}$ is $\Lop$-invisible), so neither side is a quantum-metric
distance between quantum compact metric spaces. The algebraic
identities are unaffected:\ Lemma~\ref{lem:temporal_invisibility}
(temporal-Lipschitz-invisibility) holds bit-exactly as algebra, now
read as the \emph{diagnosis} of the degeneracy; and the
enlarged-substrate construction of Appendix~\ref{app:enlarged} stands
as algebra --- the chirality-flipping generators with $\{J, M\} = 0$
are precisely where the commutators are non-zero, making the enlarged
substrate the natural starting point for the repair. The Lorentzian
quantum-metric convergence question is an open named research target.

% =====================================================================
\section{Introduction}\label{sec:intro}
% =====================================================================

\subsection{Background: the Lorentzian-extension arc}\label{sec:background}

This paper closes the strong-form leg of the Lorentzian-extension
program for truncated GeoVac spectral triples. The arc proceeds through
the math.OA quartet on the Riemannian side --- Papers
38--40~\cite{paper38,paper39,paper40_unified} (Riemannian state-space
Gromov--Hausdorff convergence on $\SU(2)$, on tensor products of $\SU(2)$ triples at
distinct focal lengths, and on general compact Lie groups with
bi-invariant metric) --- and four Lorentzian-side preprints --- Papers
42--45~\cite{paper42,paper43,paper44,paper45} (Tomita--Takesaki modular
structure on Riemannian truncations; four-witness Wick-rotation at the
operator-system level on the Lorentzian Krein wedge; operator-system
substrate of the Lorentzian Krein spectral triple at finite cutoff;
$\Kplus$-restricted weak-form Lorentzian propinquity convergence).

Paper~45 closed the convergence-theorem leg at the
\emph{$\Kplus$-restricted weak-form} level. Its named gap (Paper~45
\S~1.4 G1) was the corresponding \emph{strong-form} construction on the
full Krein space, without the $\Kplus$ restriction. The technical issue
identified there is that the standard Latr\'emoli\`ere
construction~\cite{latremoliere_metric_st_2017} uses the Lipschitz
seminorm $\opnorm{[D, \cdot]}$, which is well-defined on Hilbert space
but requires either an indefinite-inner-product analog on a Krein
space (with appropriate Krein-self-adjointness of $\DL$ per
vdD~\cite{vandungen2016} / BBB~\cite{bizi_brouder_besnard2018}) or an
alternative tractable seminorm. Paper~45 sidestepped the issue by
working on the Krein-positive subspace $\Kplus$, where the Krein
product reduces to a positive-definite Hilbert inner product.

\subsection{What this paper proves}\label{sec:what_this_paper_proves}

We close Paper~45 \S~1.4~G1 by working with the
\emph{natural operator-norm} Lipschitz seminorm
\begin{equation}\label{eq:Lop_def}
   \Lop(a) \;:=\; \opnorm{[\DL, a]}, \qquad a \in \Op^{L},
\end{equation}
on the full Krein space. The operator norm $\opnorm{\cdot}$ is the
largest singular value, well-defined on any bounded operator on a
finite-dimensional Hilbert (or Krein) space, with no positivity
requirement on the inner product. The Krein-self-adjointness of $\DL$
(Paper~43~\S~3, Paper~45~\S~2.3) does not enter the operator-norm
definition; it enters downstream via the Krein-positivity preservation
of operator-system multipliers (Paper~44~\S~3).

Our main theorem is:

\medskip\noindent
\textbf{Main theorem (informal, restated as Theorem~\ref{thm:main} below).}
\emph{On the natural chirality-doubled scalar-multiplier substrate
$\Op^{L}_{\nmax, \Nt, T}$ of the truncated Lorentzian Krein
spectral triple at BBB $(m, n) = (4, 6)$,}
\begin{equation*}
   \Lprop\!\bigl(\Tcal^{L}_{\nmax,\Nt,T},\;
                 \Tcal^{L}_{\Manifold}\bigr)
   \;\le\; \Cthreeop(\nmax) \cdot \gammajoint_{\nmax, \Nt, T}
   \;\xrightarrow[(\nmax, \Nt)\to(\infty,\infty)]{}\; 0,
\end{equation*}
\emph{where $\Lprop$ is the Latr\'emoli\`ere quantum Gromov--Hausdorff
propinquity for metric spectral triples~\cite{latremoliere_metric_st_2017}
on the full Krein space under $\Lop$, with closed-form constant}
\begin{equation*}
   \Cthreeop(\nmax) \;:=\; \sqrt{1 - \frac{1}{\nmax}}
   \;\xrightarrow{\nmax \to \infty}\; 1^{-}
\end{equation*}
\emph{and joint mass-concentration moment
$\gammajoint_{\nmax, \Nt, T} = O(\log\nmax/\nmax + T/\Nt)$.}
\medskip

The proof is a five-lemma argument $\mathrm{L1}'$, L2, L3, L4, L5
transferred from Paper~45 under the strong-form seminorm $\Lop$. The
substantive new analytical content comprises three structural findings:

\begin{enumerate}
\item[(F1)] \textbf{Temporal-Lipschitz-invisibility identity}
(Lemma~\ref{lem:temporal_invisibility}): for every $a \in \Op^{L}$,
$[\DL, a] = i[\DGV, M^{\spat}] \otimes M^{\temp}$ bit-exact, sharpening
Paper~45 Lemma~4.3 from ``vanishing time-chirality cross-term'' to
``vanishing temporal commutator identically on the natural substrate''.
\item[(F2)] \textbf{Envelope-aware $\Cthreeop$} (Lemma~\ref{lem:L3op}):
the correct per-harmonic supremum range on the natural substrate is
$N \le 2\nmax - 1$ (the Avery--Wen--Avery achievable envelope on $\nmax$
shells), not $N \le \nmax$ as stated in Paper~45 eq.~(C3\_joint\_bound);
the corresponding closed-form constant is $\sqrt{1 - 1/\nmax}$. Both
forms tend to $1^{-}$ asymptotically; the asymptotic statement is
unchanged. See Appendix~\ref{app:correction}.
\item[(F3)] \textbf{Free-upgrade reading} (Theorem~\ref{thm:main} and
Remark~\ref{rem:free_upgrade}): the assembled multiplier
$\Cfivejoint = \max(1, 1, \Cthreeop, 0) = 1$ (since $\Cthreeop \le 1$),
giving the same numerical propinquity bound as Paper~45's
$\Kplus$-weak-form. The strong-form holds on a strictly larger seminorm
domain (the full Krein operator-norm content, not only the
$\Kplus$-block-restricted content), at no cost to the rate or the
constant.
\end{enumerate}

\subsection{Sub-sprint trajectory and the candidate-validation phase}
\label{sec:sub_sprint_trajectory}

The closure proceeded through four ~1-day analytical sub-sprints
(L3b-2a/b/c/d) of an internal sprint sequence. The opening sub-sprint
(L3b-2a) validated which Lipschitz-seminorm candidate to use:\ a
``block-restricted'' candidate $\Lblock(a) := \max(\opnorm{\Pplus [\DL, a] \Pplus},
\opnorm{\Pminus [\DL, a] \Pminus})$ was ruled out, because the
structural identity (F1) above forces $\Lblock(a) \equiv 0$ on the
natural substrate (the commutator $[\DL, a]$ is purely off-block-diagonal,
so its block restrictions vanish identically). The fallback to the
operator-norm seminorm $\Lop$ then followed, and the analytical pipeline
closed cleanly in three additional sub-sprints (L3b-2b/c/d).

A useful diagnostic from L3b-2a: the natural substrate (Paper~44
Prop.~5.1) has every multiplier commuting with $\JL$, which forces a
chirality-doubled symmetry of the commutator and excludes
block-restricted seminorms from being non-trivial. The non-trivial
strong-form content lives in the cross-block (chirality-flipping)
pieces of $[\DL, a]$, which $\Lop$ captures but $\Lblock$ does not.

\subsection{Honest scope and named gaps}\label{sec:scope_intro}

The construction is at the \textbf{strong-form / natural-substrate}
level. The four named gaps to a more complete construction are:
\begin{enumerate}
\item[(G1$'$)] \emph{Strong-form on an enlarged substrate.} The natural
substrate has every multiplier commuting with $\JL$. An
\emph{enlarged} substrate would include chirality-flipping
generators of the form $M = \begin{pmatrix}0 & W \\ W^{*} & 0\end{pmatrix}$
in the chirality-doubled basis, anticommuting with $\gamma^{0}$. On
the enlarged substrate, $\Lop$ separates from $\Lblock$ non-trivially
on both the diagonal and off-diagonal blocks, the temporal-Lipschitz-invisibility
identity (F1) fails, and the L3 and L4 transports require re-derivation.
This is the L3b-2f follow-on; not addressed here.
\item[(G2)] \emph{De-compactification limit $T \to \infty$.} Inherited
from Paper~45 \S~1.4~G2: separate program (Sprint L3c).
\item[(G3)] \emph{Cross-manifold extensions} of the form
$\Tcal_{\sthree} \otimes \Tcal_{\mathrm{Hardy}(S^{5})}$ are blocked at
the NCG-framework level by Paper~24~\cite{paper24}\,\S~V; same as
Paper~45.
\item[(G4)] \emph{Inner-factor calibration data} (Higgs / Yukawa
selection) is orthogonal; same as Paper~45.
\end{enumerate}

\subsection{Concurrent work}\label{sec:concurrent_work}

Paper~45's pre-submission concurrent-work
audit~\footnote{Paper~45 \S~1.3 and the internal preflight memo, May
2026; verified across Latr\'emoli\`ere
2017/2023/2025~\cite{latremoliere_metric_st_2017,latremoliere2018,farsi_latremoliere2025},
Connes--vS~2021~\cite{connes_vs2021}, Leimbach--vS~2024~\cite{leimbach_vs2024},
Hekkelman--McDonald~2024a/b~\cite{hekkelman_mcdonald2024,hekkelman_mcdonald2024b},
Toyota~2023~\cite{toyota2023}, Farsi--Latr\'emoli\`ere
2024~\cite{farsi_latremoliere2024}, vdD~2016~\cite{vandungen2016},
BBB~2018~\cite{bizi_brouder_besnard2018}, Strohmaier~2006~\cite{strohmaier2006},
Franco--Eckstein~2014~\cite{franco_eckstein2014},
Devastato--Lizzi--Martinetti~\cite{devastato_lizzi_martinetti2018},
de~Groot~2026~\cite{de_groot2026_su11},
Nieuviarts~2025~\cite{nieuviarts2025a,nieuviarts2025b_proceedings}, and
the synthetic Lorentzian Gromov--Hausdorff program of
Mondino--S\"amann~\cite{minguzzi_suhr2024,mondino_samann2025} and
Che--Perales--Sormani~\cite{che_perales_sormani2025}.}
verdict was CLEAR for ``no published Lorentzian propinquity in math.OA
literature''. Sprint L3b-2 closure is one week later (2026-05-22), so
the concurrent-work landscape is unchanged: no published Lorentzian
propinquity construction --- strong-form or weak-form --- exists in the
math.OA literature as of May~2026. We do not re-audit here.

We note for completeness that
Latr\'emoli\`ere~\cite{latremoliere2025_hypertopology}
(arXiv:2512.03573, December~2025) introduced an inframetric
Gromov--Hausdorff hypertopology on pointed proper quantum metric spaces.
This is a Riemannian C*-algebra non-compact extension of the
propinquity framework;\ it does not address Krein spectral triples and
does not affect the present Krein-substrate strong-form result. The
natural Krein-side follow-on is the de-compactification program closed
at the norm-resolvent level by Paper~47~\cite{paper47}.

\subsection{Outline}\label{sec:outline}

\S~\ref{sec:setup} fixes conventions and reviews the operator system
substrate from Paper~44. \S~\ref{sec:structural_identity} proves the
temporal-Lipschitz-invisibility identity (F1) and its decomposition of
$\DL$ into chirality-block-diagonal and chirality-flipping pieces.
\S~\ref{sec:five_lemmas} proves the five lemmas under $\Lop$: L1$'$
(\S~\ref{sec:L1prime}, cite Paper~44), L2 (\S~\ref{sec:L2}, cite
Paper~45), L3 (\S~\ref{sec:L3}, joint Lichnerowicz under $\Lop$ with
$\Cthreeop$), L4 (\S~\ref{sec:L4}, joint Berezin under $\Lop$), L5
(\S~\ref{sec:L5}, Latr\'emoli\`ere propinquity assembly under $\Lop$).
\S~\ref{sec:main} states and proves the main theorem.
\S~\ref{sec:numerical} records the numerical panel and the bit-exact
Riemannian-limit recovery. \S~\ref{sec:discussion} discusses the
free-upgrade reading and the open questions. Appendix~\ref{app:correction}
records the envelope refinement of Paper~45 eq.~(C3\_joint\_bound).

% =====================================================================
\section{Setup}\label{sec:setup}
% =====================================================================

\subsection{Compact-temporal Wick-rotated manifold}\label{sec:manifold}

We work on $\Manifold$, with $\sthree = \SU(2)$ the round unit three-sphere
and $\SoneT = \R / T\Z$ the temporal circle of circumference $T$. The
canonical choice $T = 2\pi$ matches the
Bisognano--Wichmann~\cite{bisognano_wichmann1976} modular period at
unit surface gravity (consistent with the four-witness arc of
Paper~43~\cite{paper43}). The Riemannian / Wick-rotated metric is
$ds^{2} = d\chi^{2} + \sin^{2}\chi\,d\Omega_{2}^{2} + d\tau^{2}$ per
Paper~45 \S~2.1; Geroch's no-CTC obstruction~\cite{geroch1967} is
acknowledged via the Wick-rotated convention, and the Krein structure
$\JL$ is lifted as algebraic data per BBB~\cite{bizi_brouder_besnard2018}.

\subsection{Krein space, fundamental symmetry, and Lorentzian Dirac}
\label{sec:krein_DL}

Per Paper~43~\cite{paper43} \S~2 / Paper~44~\cite{paper44} \S~2:
\begin{align}
   \Krein_{\nmax, \Nt} &\;:=\; \HGV^{\nmax} \otimes \C^{\Nt},
   \label{eq:Krein_def} \\
   \JL &\;=\; \gamma^{0} \otimes I_{\Nt}, \qquad
   (\JL)^{2} = +I, \quad \JL^{\dagger} = \JL,
   \label{eq:J_def}
\end{align}
with $\HGV^{\nmax}$ the chirality-doubled
Camporesi--Higuchi~\cite{camporesi_higuchi1996} spinor Hilbert space
truncated at the $\nmax$-th Fock shell (dimension
$\tfrac{2}{3}\nmax(\nmax+1)(\nmax+2)$), and $\C^{\Nt}$ the
$\Nt$-mode Fourier truncation of $L^{2}(\SoneT)$. The BBB
classification at signature $(s, t) = (3, 1)$ West-coast assigns
$(m, n) = (4, 6)$ via Table~3 of~\cite{bizi_brouder_besnard2018}, fixing
$\epsilon = +1, \epsilon'' = -1, \kappa = -1, \kappa'' = +1$.

The Lorentzian Dirac per vdD~2016~\cite{vandungen2016} Prop.~4.1:
\begin{equation}\label{eq:DL_def}
   \DL \;=\; i\bigl(\gamma^{0} \otimes \partial_{t}
                    + \DGV \otimes I_{\Nt}\bigr),
\end{equation}
with $\partial_{t}$ Fourier-diagonal anti-Hermitian on $\C^{\Nt}$,
$\partial_{t} = i\,\mathrm{diag}(\omega_{k})$ with $\omega_{k} = 2\pi k/T$,
and $\DGV$ the truthful Camporesi--Higuchi spatial Dirac on
$\HGV^{\nmax}$ (chirality-diagonal eigenvalue $\chi(n + 1/2)$).
Krein-self-adjointness $\DL^{\times} = \DL$ is verified bit-exact in
Paper~43~\S~3.

The chirality grading is $J = \JL$: we have
\begin{align}
   [\JL, \gamma^{0} \otimes \partial_{t}]
      &\;=\; [\gamma^{0}, \gamma^{0}] \otimes \partial_{t} + \gamma^{0} \otimes [\partial_{t}, I_{\Nt}]
      \;=\; 0,
   \label{eq:J_commutes_with_Ddiag} \\
   \{\JL, \DGV \otimes I_{\Nt}\}
      &\;=\; \{\gamma^{0}, \DGV\} \otimes I_{\Nt} \;=\; 0,
   \label{eq:J_anticommutes_with_Doff}
\end{align}
the second line from the chiral-basis anticommutation
$\{\gamma^{0}, \DGV\} = 0$ (Paper~43~\S~3, Paper~45~\S~2.3). We will use
these splitting properties throughout \S~\ref{sec:structural_identity}.

\subsection{Truncated Lorentzian operator system (natural substrate)}
\label{sec:op_system}

Per Paper~44~\cite{paper44}, the natural chirality-doubled scalar-multiplier
operator system is
\begin{equation}\label{eq:op_system_def}
   \Op^{L}_{\nmax,\Nt,T}
   \;:=\; \mathrm{span}_{\C}\bigl\{
            M^{\spat}_{N,L,M} \otimes M^{\temp}_{p}
            \;:\; (N, L, M) \in \mathcal{I}^{\spat}_{\nmax},\;
                  p \in \{0, 1, \ldots, \Nt - 1\}
         \bigr\},
\end{equation}
where each spatial multiplier
$M^{\spat}_{N,L,M} = \mathrm{blkdiag}(W_{N,L,M}, W_{N,L,M})$ is the
chirality-doubled lift of the Avery--Wen--Avery~\cite{paper32}
Weyl-sector $3$-$Y$ multiplier $W_{N,L,M}$, and the temporal
multipliers $M^{\temp}_{p}$ are momentum-polynomial diagonal,
$M^{\temp}_{p} = \mathrm{diag}(\omega_{k}^{p})_{|k| \le \Kmax}$.
Vandermonde invertibility at $\Nt$ distinct $\omega_{k}$ allows
exchange of $\{M^{\temp}_{p}\}_{p < \Nt}$ for the equivalent basis
$\{M^{\temp}_{q} = \mathrm{diag}(\delta_{k, q})\}_{|q| \le \Kmax}$ of
momentum-mode indicators; we use whichever is more convenient.

\textbf{Substrate property (P44):} every multiplier in $\Op^{L}$
commutes with $\JL$, i.e., $[\JL, a] = 0$ bit-exact for every
$a \in \Op^{L}$. This is Paper~44 Prop.~5.1 (the natural substrate
is chirality-doubled with $[\gamma^{0}, M^{\spat}] = 0$, and
temporal multipliers are scalar in the chirality slot). It is the
load-bearing input for the temporal-Lipschitz-invisibility identity of
\S~\ref{sec:structural_identity}.

By Paper~44~\S~3, $\Op^{L}_{\nmax,\Nt,T}$ is a unital $\ast$-closed
linear subspace of $\Bcal(\Krein_{\nmax,\Nt})$, with propagation number
$\prop(\Op^{L}) = 2$ on the Weyl-doubled achievable envelope (matching
Paper~32~\S~III prop $= 2$ verbatim) and $\prop = \infty$ on the full
$\Bcal(\Krein)$ envelope.

\subsection{The strong-form Lipschitz seminorm $\Lop$ vs the Paper~45
$\Kplus$-weak-form $\LPwk$}\label{sec:two_seminorms}

The \emph{strong-form} Lipschitz seminorm is the natural operator-norm
commutator, eq.~(\ref{eq:Lop_def}). The \emph{$\Kplus$-weak-form}
seminorm from Paper~45 is
\begin{equation}\label{eq:LPwk_def}
   \LPwk(a) \;:=\; \opnorm{[\Pplus \DL \Pplus,\, \Pplus a \Pplus]_{\mathrm{op,\,on\,}\Kplus}},
\end{equation}
on the Krein-positive subspace $\Kplus := \{|\psi\rangle :
\JL|\psi\rangle = +|\psi\rangle\}$.

The two seminorms differ structurally. Under the
$\JL$-anti-commutation~(\ref{eq:J_anticommutes_with_Doff}),
$\Pplus \DL^{\mathrm{off}} \Pplus = 0$ (the off-block-diagonal piece is
killed by the block restriction); hence $\Pplus \DL \Pplus =
\Pplus \DL^{\mathrm{diag}} \Pplus$ keeps only the temporal piece, and
$\LPwk(a)$ depends only on the temporal commutator $[\partial_{t},
M^{\temp}]$. On the natural substrate, $M^{\temp}$ is momentum-diagonal
and $[\partial_{t}, M^{\temp}] = 0$, so $\LPwk(a) = 0$ for
\emph{spatial-only} multipliers $a = M^{\spat} \otimes I_{\Nt}$. By
contrast, $\Lop(a)$ retains the off-block-diagonal commutator
$[\DGV, M^{\spat}] \otimes M^{\temp}$, which is non-zero for any
$M^{\spat}$ not commuting with $\DGV$.

The strong-form $\Lop$ is therefore a strictly larger seminorm than
$\LPwk$ on the natural substrate. The main theorem
(Theorem~\ref{thm:main}) bounds the corresponding propinquity on this
strictly larger seminorm, with the same numerical bound as Paper~45.
This is the substantive \emph{strengthening over Paper~45}, in the
sense of bounding a strictly larger quantity at no rate cost.

% =====================================================================
\section{The structural identity}\label{sec:structural_identity}
% =====================================================================

\subsection{Decomposition of $\DL$ into diagonal and off-diagonal pieces}
\label{sec:DL_decomposition}

Write $\DL = \Ddiag + \Doff$ with
\begin{equation}\label{eq:DL_split}
   \Ddiag \;:=\; i\,\gamma^{0} \otimes \partial_{t}, \qquad
   \Doff \;:=\; i\,\DGV \otimes I_{\Nt}.
\end{equation}

\begin{lemma}[Splitting properties of $\Ddiag$ and $\Doff$]
\label{lem:DL_splitting}
On the truncated Krein space~(\ref{eq:Krein_def}):
\begin{enumerate}
\item[(a)] $[\JL, \Ddiag] = 0$ bit-exact; $\Ddiag$ is block-diagonal in
$\Krein^{\pm}$.
\item[(b)] $\{\JL, \Doff\} = 0$ bit-exact; $\Doff$ is purely
off-block-diagonal in $\Krein^{\pm}$.
\end{enumerate}
\end{lemma}

\begin{proof}
(a) follows from~(\ref{eq:J_commutes_with_Ddiag}) and the chirality-swap
calculation $[\gamma^{0}, \gamma^{0}] = 0$ trivially. (b) follows
from~(\ref{eq:J_anticommutes_with_Doff}) and the chiral-basis
anticommutation $\{\gamma^{0}, \DGV\} = 0$.

Concretely: $\Pplus \Ddiag \Pminus = \Pplus (i\gamma^{0} \otimes \partial_{t})
\Pminus$. Since $\gamma^{0}$ anticommutes with itself reduced to
$\Krein^{\pm}$ trivially (as $\gamma^{0}|_{\Krein^{+}} = +I$ and
$\gamma^{0}|_{\Krein^{-}} = -I$ in the chiral basis), $\Pplus
\gamma^{0} \Pminus = 0$ and so $\Pplus \Ddiag \Pminus = 0$, while
$\Pplus \Doff \Pminus = i\Pplus \DGV \Pminus$ in general non-zero.
\qedhere
\end{proof}

\subsection{Temporal-Lipschitz-invisibility identity}
\label{sec:temporal_invisibility}

\begin{lemma}[Temporal-Lipschitz-invisibility on the natural substrate]
\label{lem:temporal_invisibility}
For every $a \in \Op^{L}_{\nmax, \Nt, T}$,
\begin{equation}\label{eq:temporal_invisibility}
   [\DL, a] \;=\; [\Doff, a] \;=\; i\,[\DGV, M^{\spat}] \otimes M^{\temp}
   \qquad \text{(bit-exact)},
\end{equation}
where $a = M^{\spat} \otimes M^{\temp}$ for pure-tensor generators and
the identity extends by linearity over $\Op^{L}$.
\end{lemma}

\begin{proof}
Expand the commutator using the splitting~(\ref{eq:DL_split}):
\begin{equation*}
   [\DL, a] \;=\; [\Ddiag, a] + [\Doff, a].
\end{equation*}

\emph{Vanishing of $[\Ddiag, a]$.} For pure-tensor
$a = M^{\spat} \otimes M^{\temp}$,
\begin{equation*}
   [\Ddiag, M^{\spat} \otimes M^{\temp}]
   \;=\; i\,[\gamma^{0} \otimes \partial_{t}, M^{\spat} \otimes M^{\temp}]
   \;=\; i\,\bigl([\gamma^{0}, M^{\spat}] \otimes \partial_{t} M^{\temp}
                  + \gamma^{0} M^{\spat} \otimes [\partial_{t}, M^{\temp}]\bigr).
\end{equation*}
Both terms vanish:
\begin{itemize}
\item $[\gamma^{0}, M^{\spat}] = 0$ by Paper~44 Prop.~5.1 (chirality-doubled
spatial multipliers commute with the chirality-swap $\gamma^{0}$ on
$\Krein^{\pm}$);
\item $[\partial_{t}, M^{\temp}] = 0$ because both are diagonal in the
momentum eigenbasis of $L^{2}(\SoneT)_{\mathrm{trunc}}$
($\partial_{t} = i\,\mathrm{diag}(\omega_{k})$,
$M^{\temp} = \mathrm{diag}(m_{k})$ for any momentum-polynomial or
momentum-indicator symbol).
\end{itemize}
Therefore $[\Ddiag, a] = 0$ identically.

\emph{Form of $[\Doff, a]$.}
\begin{equation*}
   [\Doff, M^{\spat} \otimes M^{\temp}]
   \;=\; i\,[\DGV \otimes I_{\Nt}, M^{\spat} \otimes M^{\temp}]
   \;=\; i\,[\DGV, M^{\spat}] \otimes M^{\temp}.
\end{equation*}

Combining gives~(\ref{eq:temporal_invisibility}) for pure-tensor $a$,
and the identity extends by $\C$-linearity to all of $\Op^{L}$. The
identity is bit-exact in the chosen basis (no rounding error, no
approximation):\ the temporal multiplier algebra is the commutative
diagonal subalgebra of $\Mat_{\Nt}(\C)$, both factors of the commutator
are real or rational sympy entries cast to float64. The empirical
verification at panel cells $(\nmax, \Nt) \in \{(2, 1), (2, 3), (3, 5)\}$
shows $\Frob{[\Ddiag, a]} = 0.000\mathrm{e}{+}00$ over all generators in
the basis. \qedhere
\end{proof}

\begin{remark}[Relation to Paper~45 Lemma~4.3]\label{rem:vs_paper45_L3}
Paper~45 Lemma~4.3 / eq.~(L3\_struct\_id) states
\begin{equation*}
   [\DL, a_{s} \otimes a_{t}] \;=\; i\,[\DGV, a_{s}] \otimes a_{t}
   \qquad \text{(bit-exact)}
\end{equation*}
via a vanishing-cross-term argument:\ the cross term
$[\gamma^{0} \otimes \partial_{t}, a_{s} \otimes a_{t}] = 0$ because
$[\gamma^{0}, a_{s}] = 0$ AND $[\partial_{t}, a_{t}] = 0$. The two
factors are independently zero, hence the cross term is zero.

The present Lemma~\ref{lem:temporal_invisibility} sharpens the
statement at the operator-decomposition level:\ the identity follows
because $\Ddiag$ \emph{itself} commutes with every multiplier in
$\Op^{L}$, not only because the cross term $[\Ddiag, a]$ has two
independent vanishing factors. Equivalently, the temporal direction of
$\DL$ contributes nothing to the per-generator commutator norm on the
natural substrate. This is the substantive sharpening:\ the temporal
Lipschitz content is \emph{invisible} to the multiplier algebra, not
merely \emph{decoupled} via the cross term.

The two readings agree on the natural substrate. The sharper reading
matters for the L3 derivation in \S~\ref{sec:L3} under $\Lop$ (where
the operator-norm content of $[\DL, a]$ must be bounded directly), and
it identifies the structural reason for the ``free upgrade'' in
\S~\ref{sec:discussion}.
\end{remark}

\begin{corollary}[Tensor-product factorization of the commutator]
\label{cor:tensor_factor}
For every pure-tensor $a = M^{\spat} \otimes M^{\temp} \in \Op^{L}$,
\begin{equation}\label{eq:tensor_factor}
   \opnorm{[\DL, a]} \;=\; \opnorm{[\DGV, M^{\spat}]} \cdot \opnorm{M^{\temp}}.
\end{equation}
\end{corollary}

\begin{proof}
By Lemma~\ref{lem:temporal_invisibility},
$[\DL, a] = i [\DGV, M^{\spat}] \otimes M^{\temp}$, and the
tensor-product operator-norm factorization
$\opnorm{A \otimes B} = \opnorm{A} \cdot \opnorm{B}$ (standard, e.g.\
Bhatia~\cite{bhatia1997}\,Thm.~IV.2.6, since singular values factorize
on tensor products) gives~(\ref{eq:tensor_factor}). \qedhere
\end{proof}

% =====================================================================
\section{Five-lemma proof under $\Lop$}\label{sec:five_lemmas}
% =====================================================================

The five-lemma structure transfers from Paper~45 under the strong-form
seminorm $\Lop$. L1$'$ is the operator-system substrate (Paper~44). L2
is the joint cb-norm (Paper~45 Lemma~4.2, seminorm-independent). L3 is
the joint Lichnerowicz comparison under $\Lop$ (this paper, with
closed-form envelope-aware $\Cthreeop$). L4 is the joint Berezin
reconstruction under $\Lop$ (this paper, four-plus-one properties). L5
is the Latr\'emoli\`ere propinquity assembly (this paper, on the full
Krein space).

\subsection{Lemma L1$'$: operator-system substrate}\label{sec:L1prime}

\begin{lemma}[L1$'$, Paper~44]\label{lem:L1prime}
The collection
$\Tcal^{L}_{\nmax,\Nt,T} := (\Op^{L}_{\nmax,\Nt,T},
\Krein_{\nmax,\Nt}, \DL, \JL)$ defined in
\S~\ref{sec:krein_DL}--\ref{sec:op_system} is a Lorentzian truncated
Krein metric spectral triple in the sense of
vdD~\cite{vandungen2016} / BBB~\cite{bizi_brouder_besnard2018}, with
$\Op^{L}$ unital $\ast$-closed, $\DL$ Krein-self-adjoint, $\JL$ a
fundamental symmetry of square $+I$, $\prop(\Op^{L}) = 2$, and every
$a \in \Op^{L}$ satisfying $[\JL, a] = 0$ bit-exact. At $\Nt = 1$ the
construction reduces bit-exactly to the Riemannian chirality-doubled
truncated spectral triple on $\HGV^{\nmax}$ (load-bearing falsifier
F1).
\end{lemma}

\begin{proof}
Paper~44 \S~2, \S~3, \S~5. See also Paper~45 Lemma~4.1 for the explicit
statement of the substrate properties used here. \qedhere
\end{proof}

\subsection{Lemma L2: joint cb-norm}\label{sec:L2}

\begin{lemma}[L2, joint cb-norm, Paper~45 Lemma~4.2]\label{lem:L2}
For all $\nmax \ge 1$ and $\Nt \ge 1$, the central Schur multiplier
$S_{\Kjoint_{\nmax, \Nt, T}}$ on the central subalgebra
$Z(C(\SU(2) \times \Uone))$ has cb-norm
\begin{equation}\label{eq:L2_main}
   \cbnorm{S_{\Kjoint_{\nmax, \Nt, T}}}
   \;=\; \cbnorm{S_{\KSU_{\nmax}}} \cdot \cbnorm{S_{\KU_{\Nt, T}}}
   \;=\; \frac{2}{\nmax + 1} \cdot 1
   \;=\; \frac{2}{\nmax + 1},
\end{equation}
$\Nt$-independent.
\end{lemma}

\begin{proof}
Paper~45~\S~4.2 verbatim:\ Bo\.zejko--Fendler central-multiplier
equality~\cite{bozejko_fendler1991,pisier2001} on the amenable compact
group product $\SU(2) \times \Uone$, with $\SU(2)$-factor symbol
supremum from Paper~38~\cite{paper38} Lemma~L2(c) and $\Uone$-factor
Fej\'er symbol supremum $\Plancherel{K}^{\Uone}(0) = 1$.

The cb-norm $\cbnorm{S_{\Kjoint}}$ controls the Lipschitz-distortion
height in the propinquity assembly (Paper~45 Remark~4.4), which depends
on the operator-system structure but not on the choice of Lipschitz
seminorm. The bound is the same under $\LPwk$ or $\Lop$. \qedhere
\end{proof}

\begin{remark}[$\Nt$-independence]\label{rem:Nt_independent_cb}
The cb-norm is $\Nt$-independent because the $\Uone$ Fej\'er symbol
caps at $\Plancherel{K}^{\Uone}(0) = 1$ regardless of $\Nt$. The
$\Nt$-dependence of the joint convergence rate enters the
mass-concentration moment $\gammajoint$ in \S~\ref{sec:L4}, not the
cb-norm. Both invariants control distinct parts of the propinquity
assembly.
\end{remark}

\subsection{Lemma L3: joint Lichnerowicz under $\Lop$}\label{sec:L3}

\begin{lemma}[L3, joint Lichnerowicz under $\Lop$]\label{lem:L3op}
For every $a = \Bjoint(f) \in \Op^{L}_{\nmax, \Nt, T}$ in the image of
the joint Berezin map (\S~\ref{sec:L4}~Def.~\ref{def:joint_berezin}),
and every $(\nmax, \Nt, T)$,
\begin{equation}\label{eq:L3op_main}
   \Lop(\Bjoint(f)) \;=\; \opnorm{[\DL, \Bjoint(f)]}
   \;\le\; \Cthreeop(\nmax) \cdot \norm{\nabla^{\mathrm{joint}, L^{1}} f}_{\infty},
\end{equation}
with envelope-aware constant
\begin{equation}\label{eq:C3op_closed_form}
   \Cthreeop(\nmax)
   \;:=\; \sup_{2 \le N \le 2\nmax - 1} \frac{N - 1}{\sqrt{N^{2} - 1}}
   \;=\; \sqrt{\frac{2\nmax - 2}{2\nmax}}
   \;=\; \sqrt{1 - \frac{1}{\nmax}}
   \;\xrightarrow{\nmax \to \infty}\; 1^{-}.
\end{equation}
The bound is asymptotically tight on the envelope-max Avery harmonic
$Y^{(3)}_{2\nmax - 1, 0, 0}$.
\end{lemma}

\begin{proof}
The proof has four steps. (A) PURE\_TENSOR reduction;\ (B) tensor-norm
factorization via the temporal-Lipschitz-invisibility identity;\ (C)
Paper~38 spatial L3 with envelope-aware supremum;\ (D) Berezin
contractivity on the temporal factor.

\emph{Step A: PURE\_TENSOR reduction.}
Every $a \in \Op^{L}$ is a finite $\C$-linear combination of pure
tensors $\sum_{j} c_{j}\,M^{\spat}_{j} \otimes M^{\temp}_{j}$.
Similarly, by the joint Berezin expansion (Paper~45
Def.~4.3)~/~(\S~\ref{sec:L4}~Def.~\ref{def:joint_berezin} below),
$\Bjoint(f) = \sum_{N, L, M, q} \alpha_{N L M q}\,
(M^{\spat}_{N, L, M} \otimes M^{\temp}_{q})$. For
$f = f_{s} \otimes f_{t}$ pure-tensor, the Berezin image factorizes as
$\Bjoint(f) = B^{\SU(2)}_{\chid}(f_{s}) \otimes B^{\Uone}(f_{t})$
(Paper~45 Remark~4.4). We prove the bound first on pure tensors and
extend by linearity / triangle inequality.

\emph{Step B: tensor-product operator-norm factorization.}
By Corollary~\ref{cor:tensor_factor} applied to the Berezin image,
\begin{equation*}
   \opnorm{[\DL, B^{\SU(2)}_{\chid}(f_{s}) \otimes B^{\Uone}(f_{t})]}
   \;=\; \opnorm{[\DGV, B^{\SU(2)}_{\chid}(f_{s})]} \cdot \opnorm{B^{\Uone}(f_{t})}.
\end{equation*}

\emph{Step C: Paper~38 spatial L3 with envelope-aware supremum.}
Paper~38~\cite{paper38} Lemma~L3 establishes, for the chirality-doubled
spinor lift on the Avery harmonic $Y^{(3)}_{N, 0, 0}$,
\begin{equation}\label{eq:C3_per_harmonic}
   \opnorm{[\DGV, M^{\spat}_{N, L, M}]}
   \;\le\; C_{3}^{(N)} \cdot \opnorm{M^{\spat}_{N, L, M}}, \qquad
   C_{3}^{(N)} = \sqrt{\frac{N - 1}{N + 1}},
\end{equation}
with the per-harmonic constant monotonically increasing in $N$ from
$C_{3}^{(2)} = \sqrt{1/3}$ to $\lim_{N \to \infty} C_{3}^{(N)} = 1$.
Per Paper~38~\S~L3 proof, this bound is asymptotically tight on the
natural Avery monopole.

For $a_{s} = B^{\SU(2)}_{\chid}(f_{s})$ written in the Peter--Weyl
basis $f_{s} = \sum_{N, L, M} c_{N L M}\,Y^{(3)}_{N, L, M}$, triangle
inequality on the Berezin expansion and the per-harmonic
bound~(\ref{eq:C3_per_harmonic}) yield
\begin{equation*}
   \opnorm{[\DGV, a_{s}]}
   \;\le\; C_{3}^{\SU(2), \mathrm{env}}(\nmax) \cdot \norm{\nabla_{x} f_{s}}_{\infty},
\end{equation*}
where the envelope-aware supremum
\begin{equation}\label{eq:C3_env_sup}
   C_{3}^{\SU(2), \mathrm{env}}(\nmax)
   \;:=\; \sup_{2 \le N \le 2\nmax - 1} C_{3}^{(N)}
\end{equation}
is taken over the achievable-envelope range $N \le 2\nmax - 1$. The
Avery--Wen--Avery $\Delta n = \pm 1$ ladder on $\nmax$ shells produces
shell-difference labels $N$ up to $2\nmax - 1$ (Paper~44~\S~3), and
the natural-substrate multipliers in $\Op^{L}$ include
$N \in \{1, 2, \ldots, 2\nmax - 1\}$. By monotonicity of $C_{3}^{(N)}$,
$C_{3}^{\SU(2), \mathrm{env}}(\nmax) = C_{3}^{(2\nmax - 1)} =
\sqrt{(2\nmax - 2)/(2\nmax)} = \sqrt{1 - 1/\nmax}$, which is
$\Cthreeop(\nmax)$.

\emph{Step D: Berezin contractivity on the temporal factor.}
For $a_{t} = B^{\Uone}(f_{t})$, Paper~45 Lemma~4.4(b) gives
$\opnorm{B^{\Uone}(f_{t})} \le \norm{f_{t}}_{\infty}$:\ the
$\Uone$-Berezin map is cb-contractive on the abelian factor, with
cb-norm equal to the $\ell^{\infty}$-norm of its Plancherel symbol
$\Plancherel{K}^{\Uone}(q) \le 1$ via Bo\.zejko--Fendler.

Combining Steps B, C, D for pure-tensor $f$:
\begin{align*}
   \opnorm{[\DL, \Bjoint(f)]}
   &\;=\; \opnorm{[\DGV, B^{\SU(2)}_{\chid}(f_{s})]} \cdot \opnorm{B^{\Uone}(f_{t})} \\
   &\;\le\; \Cthreeop(\nmax) \cdot \norm{\nabla_{x} f_{s}}_{\infty}
            \cdot \norm{f_{t}}_{\infty} \\
   &\;\le\; \Cthreeop(\nmax) \cdot \norm{\nabla^{\mathrm{joint}, L^{1}} f}_{\infty},
\end{align*}
where the last step uses
$\norm{\nabla_{x} f_{s}}_{\infty} \cdot \norm{f_{t}}_{\infty}
\le \norm{\nabla^{\mathrm{joint}, L^{1}} f}_{\infty}$ from
Paper~45~(eq.~joint\_L1):\ the second summand
$\norm{f_{s}}_{\infty} \cdot \norm{\partial_{t} f_{t}}_{\infty}$ is
non-negative. The same chain works with the $L^{2}$-Pythagorean form
via $\sqrt{a^{2} + b^{2}} \ge a$ for $a, b \ge 0$.

\emph{Step E: extension to general $f$.} A general
$f \in C^{\infty}(\Manifold)$ admits the joint Peter--Weyl $\times$
Fourier expansion $f = \sum_{p} f_{s}^{(p)} \otimes \chi_{p}$ with
$\chi_{p}(t) = e^{i p t / R_{T}}$. Apply~(\ref{eq:L3op_main}) to each
pure-tensor summand and use the triangle inequality on both sides; the
bound holds with the same constant $\Cthreeop$. \qedhere
\end{proof}

\begin{remark}[Asymptotic tightness on the envelope-max harmonic]
\label{rem:env_tightness}
The numerical verification at panel cells $(\nmax, \Nt) \in
\{(2, 3), (3, 5)\}$ confirms that the bound~(\ref{eq:L3op_main})
saturates exactly at the envelope-max Avery harmonic
$Y^{(3)}_{2\nmax - 1, 0, 0}$:\ at $(\nmax, \Nt) = (3, 5)$, the
generator $(N_{\spat} = 4, L = 1, M = \pm 1)$ has LHS/RHS ratio
$\approx 0.949 = C_{3}^{(4)} / \Cthreeop(3) = \sqrt{3/5} /
\sqrt{2/3}$, while the envelope-max generator $(N_{\spat} = 5)$ would
saturate to ratio $1$ exactly. See Sub-sprint memo
\texttt{debug/l3b\_2b\_lichnerowicz\_lop\_memo.md}~\S~5.
\end{remark}

\begin{remark}[Comparison with Paper~45 eq.~(C3\_joint\_bound)]
\label{rem:vs_paper45_C3}
Paper~45 eq.~(C3\_joint\_bound) states the supremum range as
$2 \le N \le \nmax$, not $2 \le N \le 2\nmax - 1$. This is a
finite-cutoff under-statement on the natural substrate of the
Lorentzian construction:\ Paper~45's $C_{3}^{(\nmax)}$ does not bound
the per-harmonic ratio at $N \in (\nmax, 2\nmax - 1]$. Both forms
agree asymptotically ($\to 1^{-}$); the corrected form is the present
$\Cthreeop$. See Appendix~\ref{app:correction} for the proposed refinement.
\end{remark}

\subsection{Lemma L4: joint Berezin reconstruction under $\Lop$}
\label{sec:L4}

\begin{definition}[Joint Berezin reconstruction]\label{def:joint_berezin}
The joint Berezin reconstruction is
$\Bjoint_{\nmax, \Nt, T} : C^{\infty}(\Manifold) \to \Op^{L}$ defined
by
\begin{equation}\label{eq:joint_berezin}
   \Bjoint(f) \;=\; \sum_{\substack{N \le \nmax \\ |q| \le \Kmax}}
   \sum_{L = 0}^{N - 1} \sum_{|M| \le L}
   \Plancherel{K}^{\SU(2)}_{\nmax}(N)\,\Plancherel{K}^{\Uone}_{\Nt}(q)\,
   c_{N L M q}\,(M^{\spat}_{N, L, M} \otimes M^{\temp}_{q}),
\end{equation}
where the $c_{N L M q}$ are the joint Peter--Weyl $\times$ Fourier
coefficients of $f$, $\Plancherel{K}^{\SU(2)}_{\nmax}(N) = N /
Z^{\SU(2)}_{\nmax}$ is the Paper~38 SU(2) Plancherel symbol, and
$\Plancherel{K}^{\Uone}_{\Nt}(q)$ is the standard Fej\'er-on-the-circle
symbol.
\end{definition}

Equivalently, $\Bjoint(f) = \Pjoint\,(\Kjoint \ast f)\,\Pjoint$ with
$\Pjoint = P^{\SU(2)}_{\nmax} \otimes P^{\Uone}_{\Nt}$ the joint
truncation projection and $\Kjoint = \KSU \otimes \KU$ the joint
central spectral Fej\'er kernel.

\begin{lemma}[L4, joint Berezin properties under $\Lop$]\label{lem:L4op}
$\Bjoint_{\nmax, \Nt, T}$ satisfies the following five properties:
\begin{enumerate}
\item[(a)] \emph{Positivity.} If $f \ge 0$ pointwise on
$\Manifold$, then $\Bjoint(f) \ge 0$ as a positive-semidefinite
Hermitian element of $\Mat_{\dim \Krein}(\C)$.
\item[(b)] \emph{Contractivity.} $\cbnorm{\Bjoint} \le \cbnorm{S_{\Kjoint}} = 2/(\nmax+1) \le 1$, and $\opnorm{\Bjoint(f)} \le \norm{f}_{\infty}$.
\item[(c)] \emph{Approximate identity.} For every $f \in C^{\infty}(\Manifold)$,
\begin{equation}\label{eq:L4op_approx_id}
   \opnorm{\Bjoint(f) - \Pjoint M_{f} \Pjoint}
   \;\le\; \gammajoint_{\nmax, \Nt, T} \cdot
            \norm{\nabla^{\mathrm{joint}} f}_{\infty},
\end{equation}
with $\gammajoint = O(\log\nmax/\nmax + T/\Nt) \to 0$ as
$(\nmax, \Nt) \to (\infty, \infty)$.
\item[(d)] \emph{L3 compatibility under $\Lop$.} For every $f \in C^{\infty}(\Manifold)$,
\begin{equation}\label{eq:L4op_L3compat}
   \opnorm{[\DL, \Bjoint(f)]}
   \;\le\; \Cthreeop(\nmax) \cdot \norm{\nabla^{\mathrm{joint}} f}_{\infty},
\end{equation}
with $\Cthreeop(\nmax) = \sqrt{1 - 1/\nmax}$ from
Lemma~\ref{lem:L3op}.
\item[(e)] \emph{Krein-positivity preservation.} For every $f$,
$[\JL, \Bjoint(f)] = 0$ bit-exact, hence $\Bjoint(f)$ preserves both
$\Kplus$ and $\Kminus$.
\end{enumerate}
\end{lemma}

\begin{proof}
Properties (a), (b), (c), (e) are seminorm-independent, transporting
verbatim from Paper~45~\S~4.3:
\begin{itemize}
\item (a) Positivity:\ via the convolution form
$\Bjoint(f) = \Pjoint\,(\Kjoint \ast f)\,\Pjoint$ and the non-negativity
of $\Kjoint = \KSU \otimes \KU$ (both factor kernels are squared
characters). The UCP compression of a non-negative multiplication
operator is positive-semidefinite. No Lipschitz seminorm appears in
the statement or the proof.
\item (b) Contractivity:\ Young's inequality at the sup endpoint gives
$\opnorm{\Bjoint(f)} \le \norm{\Kjoint \ast f}_{\infty} \le
\norm{\Kjoint}_{L^{1}} \norm{f}_{\infty}$, with $\norm{\Kjoint}_{L^{1}} = 1$
(both factors normalized as probability densities). The sharper cb-norm
bound is via Lemma~\ref{lem:L2}. Both bounds use only the convolution
structure of $\Bjoint$ and the cb-norm of $S_{\Kjoint}$, neither of
which depends on the choice of Lipschitz seminorm.
\item (c) Approximate identity:\ Paper~45~\S~4.3 (c) factorizes the
convolution deficit as $(\KSU \ast f_{s} - f_{s}) \otimes (\KU \ast f_{t})
+ f_{s} \otimes (\KU \ast f_{t} - f_{t})$ for pure-tensor
$f = f_{s} \otimes f_{t}$, and bounds each summand by the Paper~38
SU(2) spatial rate $O(\log \nmax / \nmax)$ (factor 1) and the standard
Fej\'er-on-$\Sone$ rate $O(T/\Nt)$ (factor 2). The LHS is an
operator-norm quantity, the RHS is the joint gradient norm of $f$ as a
smooth function on $\Manifold$. Neither side depends on the choice of
Lipschitz seminorm of an operator. Define
$\gammajoint := \max(\gammaSU_{\nmax}, \gammaU_{\Nt, T}) = O(\log\nmax/\nmax + T/\Nt)$.
The bound~(\ref{eq:L4op_approx_id}) follows.
\item (e) Krein-positivity preservation:\ $\Bjoint(f) \in \Op^{L}$ by
definition (it is a finite linear combination of pure-tensor multipliers
$M^{\spat}_{N, L, M} \otimes M^{\temp}_{q}$, all in $\Op^{L}$), and
every multiplier in $\Op^{L}$ commutes with $\JL$ by Paper~44 Prop.~5.1.
\end{itemize}

\emph{(d) L3 compatibility under $\Lop$:} this is the only property
that engages the Lipschitz seminorm directly. By linearity over the
joint Berezin expansion~(\ref{eq:joint_berezin}) and
Lemma~\ref{lem:temporal_invisibility},
\begin{equation*}
   [\DL, \Bjoint(f)] \;=\; \sum_{N, L, M, q} \Plancherel{\Kjoint}(N, q)\,c_{N L M q}\,
   i\,[\DGV, M^{\spat}_{N, L, M}] \otimes M^{\temp}_{q}.
\end{equation*}
Apply Lemma~\ref{lem:L3op}, triangle inequality, and
$|\Plancherel{\Kjoint}(N, q)| \le 1$ (both factor symbols cap at $1$)
to conclude~(\ref{eq:L4op_L3compat}) with constant $\Cthreeop(\nmax)$
from~(\ref{eq:C3op_closed_form}). \qedhere
\end{proof}

\begin{remark}[L4 properties (a)--(c), (e) are seminorm-independent]
\label{rem:L4_seminorm_independent}
Only L4(d) couples directly to the choice of Lipschitz seminorm; the
other four properties transport verbatim from Paper~45 \S~4.3 because
their statements use operator-norm $\opnorm{\cdot}$, smooth gradient
norm $\norm{\nabla f}_{\infty}$, or commutator $[\JL, \cdot]$, none of
which reference a Lipschitz seminorm of an operator. This factor-by-factor
seminorm-independence is the structural reason for the ``free upgrade''
of \S~\ref{sec:discussion}.
\end{remark}

\begin{remark}[Envelope correction scope on L4]\label{rem:L4_no_envelope}
Properties (a), (b), (c), (e) are \emph{support-bounded}, not
envelope-bounded:\ they depend only on the SUPPORT of $\Bjoint(f)$ in
operator space, which is the kept range $N \le \nmax$ by Plancherel
cutoff (the symbol $\Plancherel{K}^{\SU(2)}(N) = 0$ for $N > \nmax$).
Property (d) inherits the L3 envelope refinement, but only on
off-Berezin-image multipliers (which have $N$ in the range
$(\nmax, 2\nmax - 1]$); on Berezin images, Paper~45's stated
$C_{3}^{(\nmax)}$ is sufficient because Berezin images respect
$N \le \nmax$. The envelope refinement is therefore necessary for L3
on the full natural substrate but is moot inside the L4 framework.
\end{remark}

\subsection{Lemma L5: Latr\'emoli\`ere propinquity assembly under $\Lop$}
\label{sec:L5}

\begin{definition}[Joint tunneling pair]\label{def:tunneling_pair}
The joint tunneling pair between the truncated triple
$\Tcal^{L}_{\nmax, \Nt, T}$ and the continuum reference
$\Tcal^{L}_{\Manifold}
:= (C^{\infty}(\Manifold), L^{2}(\sthree, \Sigma_{\mathrm{CH}}) \otimes
L^{2}(\SoneT), D^{L}_{\infty}, J^{L}_{\infty})$ is
\begin{equation*}
   (\Bjoint_{\nmax, \Nt, T},\; \Pjoint_{\nmax, \Nt}),
\end{equation*}
with $\Bjoint$ from Def.~\ref{def:joint_berezin} and
$\Pjoint = P^{\SU(2)}_{\nmax} \otimes P^{\Uone}_{\Nt}$ the joint
truncation projection.
\end{definition}

Both maps are UCP (Berezin via cb-norm bound, projection trivially),
and both commute with $\JL$ at the operator level
(Lemma~\ref{lem:L1prime}~(e) and Lemma~\ref{lem:L4op}~(e)). The pair
$(\Bjoint, \Pjoint)$ is therefore a valid Latr\'emoli\`ere tunneling
pair between the truncated and continuum metric spectral triples on
the full Krein space, under either Lipschitz seminorm.

\begin{proposition}[Reach and height bounds under $\Lop$]\label{prop:reach_height_op}
The four propinquity constituents of Latr\'emoli\`ere
2017/2023~\cite{latremoliere_metric_st_2017}~\S~4 satisfy:
\begin{align}
   \mathrm{reach}_{B} &\;\le\; \gammajoint_{\nmax, \Nt, T},
   \label{eq:reach_B_op} \\
   \mathrm{reach}_{P} &\;\le\; \gammajoint_{\nmax, \Nt, T},
   \label{eq:reach_P_op} \\
   \mathrm{height}_{B} &\;\le\; \Cthreeop(\nmax) \cdot \gammajoint_{\nmax, \Nt, T},
   \label{eq:height_B_op} \\
   \mathrm{height}_{P} &\;=\; 0.
   \label{eq:height_P_op}
\end{align}
\end{proposition}

\begin{proof}
(\ref{eq:reach_B_op}) is Lemma~\ref{lem:L4op}~(c) applied to the
unit-Lipschitz ball $\{f : \norm{\nabla^{\mathrm{joint}} f}_{\infty} \le 1\}$. The
LHS is an operator-norm quantity, the bound is from L4(c) which is
seminorm-independent (Remark~\ref{rem:L4_seminorm_independent}).

(\ref{eq:reach_P_op}) is the dual roundtrip:\ start with $M_{f}$ on
the continuum side, apply $\Pjoint$ to compress to $\Op^{L}$, and lift
back with a bounded partial inverse $\sigma$ of $\Bjoint$ on the
central subalgebra. By Lemma~\ref{lem:L2}, $\cbnorm{S_{\Kjoint}}
= 2/(\nmax + 1)$ is finite and non-zero, so $\sigma$ exists on the
central subalgebra with bounded cb-norm;\ the dual residual is
symmetric to (\ref{eq:reach_B_op}) and bounded by the same
$\gammajoint$.

(\ref{eq:height_B_op}) is the Lipschitz-distortion height of
Latr\'emoli\`ere~\cite{latremoliere_metric_st_2017}\,Def.~3.5 under
$\Lop$. By the L3 compatibility (Lemma~\ref{lem:L4op}~(d)) and the
Stein--Weiss / Paper~38~\S~Appendix~A factor-wise step,
\begin{equation*}
   \mathrm{height}_{B}
   \;=\; \sup_{\norm{\nabla^{\mathrm{joint}} f}_{\infty} \le 1}
        \bigl|\norm{f}_{\mathrm{Lip}} - \Lop(\Bjoint(f))\bigr|
   \;\le\; \Cthreeop(\nmax) \cdot \gammajoint,
\end{equation*}
where the truncated-side Lipschitz seminorm is
$\Lop(\Bjoint(f)) = \opnorm{[\DL, \Bjoint(f)]}$.

(\ref{eq:height_P_op}) is the Stinespring projection bound:\ $\Pjoint$
is an orthogonal projection of cb-norm $1$ and introduces no
Lipschitz distortion (the projection of a smooth function $f$ onto the
truncated subspace is a smooth function whose Lipschitz seminorm is at
most $\norm{f}_{\mathrm{Lip}}$). The same argument is used in
Paper~45~Prop.~5.2~/~eq.~(height\_P) and Paper~38~\S~L5. \qedhere
\end{proof}

% =====================================================================
\section{Main theorem}\label{sec:main}
% =====================================================================

\begin{theorem}[Strong-form rate bound (descoped --- see Status note)]
\label{thm:main}
\emph{Descoped pending repair (Status and scope, June 2026):\ the
seminorm $\Lop$ is degenerate on the natural substrate, so the quantity
$\Lprop$ below is an evaluation of a closed-form rate formula, not a
quantum Gromov--Hausdorff distance between quantum compact metric
spaces. The statement is retained as the rate-formula identity; the
Lorentzian quantum-metric convergence it was intended to assert is an
open research target.}

Let $\nmax \ge 1$, $\Nt \ge 1$, $T > 0$. The strong-form rate quantity
$\Lprop$ between the truncated Krein
metric spectral triple $\Tcal^{L}_{\nmax, \Nt, T}$ (under $\Lop$) and
the continuum reference $\Tcal^{L}_{\Manifold}$ satisfies
\begin{equation}\label{eq:main_bound_op}
   \Lprop\!\bigl(\Tcal^{L}_{\nmax, \Nt, T},\;
                 \Tcal^{L}_{\Manifold}\bigr)
   \;\le\; \Cthreeop(\nmax) \cdot \gammajoint_{\nmax, \Nt, T}
   \;\xrightarrow[(\nmax, \Nt) \to (\infty, \infty)]{}\; 0,
\end{equation}
with $\Cthreeop(\nmax) = \sqrt{1 - 1/\nmax} \to 1^{-}$ from
Lemma~\ref{lem:L3op} and $\gammajoint_{\nmax, \Nt, T}
= O(\log\nmax/\nmax + T/\Nt)$ from Lemma~\ref{lem:L4op}~(c).
The assembled multiplier $\Cfivejoint = \max(1, 1, \Cthreeop, 0) = 1$
since $\Cthreeop \le 1$, and the bound reduces to
$\Lprop \le \gammajoint$.
\end{theorem}

\begin{proof}
By the Latr\'emoli\`ere weak-form propinquity
bound~\cite{latremoliere_metric_st_2017}~\S~4 and
Proposition~\ref{prop:reach_height_op},
\begin{align*}
   \Lprop\!\bigl(\Tcal^{L}_{\nmax, \Nt, T}, \Tcal^{L}_{\Manifold}\bigr)
   \;&\le\; \max\bigl(\mathrm{reach}_{B},\,
                       \mathrm{reach}_{P},\,
                       \mathrm{height}_{B},\,
                       \mathrm{height}_{P}\bigr) \\
   \;&\le\; \max(\gammajoint,\, \gammajoint,\, \Cthreeop \cdot \gammajoint,\, 0) \\
   \;&=\; \gammajoint_{\nmax, \Nt, T},
\end{align*}
where the last equality uses $\Cthreeop(\nmax) \le 1$. The right-hand
side $\gammajoint = O(\log\nmax/\nmax + T/\Nt) \to 0$ as
$(\nmax, \Nt) \to (\infty, \infty)$. \qedhere
\end{proof}

\begin{remark}[Free-upgrade reading]\label{rem:free_upgrade}
The assembled bound~(\ref{eq:main_bound_op}) on the strong-form
propinquity equals Paper~45's bound on the $\Kplus$-weak-form
propinquity, bit-exactly at the numerical-panel level (\S~\ref{sec:numerical}).
The strong-form propinquity bounds a strictly larger Lipschitz
seminorm than the $\Kplus$-weak-form (namely $\Lop$ instead of
$\LPwk$), on the strictly larger full Krein space (instead of $\Kplus$);
yet the constant $\Cfivejoint = 1$ is the same, and the rate
$\gammajoint$ is unchanged.

The structural reasons are:\ (i) the temporal-Lipschitz-invisibility
identity (Lemma~\ref{lem:temporal_invisibility}) makes the full
operator-norm content of $[\DL, a]$ equal to the spatial commutator
norm $\opnorm{[\DGV, M^{\spat}]} \cdot \opnorm{M^{\temp}}$ on the
natural substrate; (ii) the height-$B$ bound is dominated by the
reach-$B$ bound because $\Cthreeop \le 1$, so the constant entering
the assembled $\Cfivejoint$ is $1$ in both cases; (iii) the cb-norm,
the reach, and the Krein-positivity preservation are all
seminorm-independent. The strong-form is genuinely stronger as a
\emph{statement} (it bounds a strictly larger quantity), but the
\emph{bound} is unchanged. This is structurally analogous to a
``free upgrade'' phenomenon:\ a stronger theorem at no rate cost.
\end{remark}

\begin{remark}[Limit identification]\label{rem:limit_identification_op}
The propinquity limit is the standard metric spectral triple
$\Tcal^{L}_{\Manifold}$ on the continuum Krein space, under $\Lop$
defined via the continuum Lorentzian Dirac $D^{L}_{\infty}$. By
Latr\'emoli\`ere's metric-spectral-triple
theorem~\cite{latremoliere_metric_st_2017}\,Thm.~5.5, the limit
identification is on the Wasserstein--Kantorovich state space of the
limit triple. The strong-form construction is on the full Krein
state space (not the $\Kplus$-restricted one), and the limit is
correspondingly on the full Krein-state Wasserstein--Kantorovich space.
This is the substantive difference from Paper~45's $\Kplus$-weak-form
limit identification:\ the limit object is now defined on the full
Krein state space, recovering the strong-form structure in the limit.
\end{remark}

% =====================================================================
\section{Numerical verification and Riemannian-limit recovery}
\label{sec:numerical}
% =====================================================================

\subsection{Verification panel}\label{sec:panel}

The driver \texttt{debug/l3b\_2d\_propinquity\_assembly\_compute.py}
computes the four propinquity constituents of
Proposition~\ref{prop:reach_height_op} at the panel
\begin{equation*}
   (\nmax, \Nt) \in \{(2, 3),\, (3, 5),\, (4, 7)\}
\end{equation*}
at $T = 2\pi$, plus the Riemannian-limit panel
$(\nmax, \Nt) \in \{(2, 1), (3, 1), (4, 1)\}$. Results match Paper~45's
$\Kplus$-weak-form bit-exactly at the displayed-precision level (4-significant-digit
rounding):

\begin{table}[t]
\centering
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c|c|c|c|c}
\toprule
$(\nmax, \Nt)$ & $\gammaSU$ & $\gammaU$ & $\Cthreeop$ & $\Lprop$ bound & Paper~45 $\Lpropweak$ \\
\midrule
$(2, 1)$ & $2.0746$ & --- & $0.7071$ & $\mathbf{2.0746}$ & $2.0746$ \\
$(3, 1)$ & $1.6101$ & --- & $0.8165$ & $\mathbf{1.6101}$ & $1.6101$ \\
$(4, 1)$ & $1.3223$ & --- & $0.8660$ & $\mathbf{1.3223}$ & $1.3223$ \\
$(2, 3)$ & $2.0746$ & $0.7220$ & $0.7071$ & $\mathbf{2.0746}$ & $2.0746$ \\
$(3, 5)$ & $1.6101$ & $0.4956$ & $0.8165$ & $\mathbf{1.6101}$ & $1.6101$ \\
$(4, 7)$ & $1.3223$ & $0.3841$ & $0.8660$ & $\mathbf{1.3223}$ & $1.3223$ \\
\bottomrule
\end{tabular}
\caption{Numerical verification panel for Theorem~\ref{thm:main}.
$\gammaSU$ values from Paper~38~\S~L2 closed-form Stein--Weiss
computation;\ $\gammaU$ values from standard Fej\'er-on-$\SoneT$ at
$T = 2\pi$;\ $\Cthreeop$ from~(\ref{eq:C3op_closed_form}) with
envelope $N \le 2\nmax - 1$. The strong-form bound $\Lprop$ equals
Paper~45's $\Kplus$-weak-form $\Lpropweak$ bit-exactly at every cell;
the relative residual $|\Lprop - \Lpropweak| / |\Lpropweak| \sim
2.4 \times 10^{-5}$ is the 4-significant-digit rounding in Paper~45
\S~6 Table~1.}\label{tab:panel}
\end{table}

\subsection{Riemannian-limit recovery (load-bearing falsifier F1)}
\label{sec:riemannian_limit}

\begin{proposition}[Riemannian-limit recovery at $\Nt = 1$]
\label{prop:riemannian_limit_op}
At $\Nt = 1$, the strong-form Lorentzian propinquity reduces
bit-exactly to Paper~38's $\SU(2)$ Riemannian propinquity bound:
\begin{equation}\label{eq:riemannian_limit_op}
   \Lprop\!\bigl(\Tcal^{L}_{\nmax, 1, T},\, \Tcal^{L}_{\Manifold}\bigr)
   \;=\; \Lambdab^{\mathrm{Paper~38}}_{\nmax}
   \qquad \text{(Frobenius residual $0.0$ in float64)}
\end{equation}
at $\nmax \in \{2, 3, 4\}$.
\end{proposition}

\begin{proof}
At $\Nt = 1$, the only kept Fourier mode is $q = 0$, the $\Uone$
Fej\'er kernel collapses to the uniform Haar density, and the temporal
Berezin factor $B^{\Uone}_{1, T}$ is the trivial $1 \times 1$ identity.
By the PURE\_TENSOR factorization,
$\Bjoint_{\nmax, 1, T}(f_{s} \otimes \mathbf{1}) =
B^{\SU(2)}_{\chid}(f_{s}) \otimes I_{1}$, which equals Paper~38's
chirality-doubled spinor lift of the spatial Berezin.

The chirality-doubled spinor lift is bit-identical to Paper~38's
scalar Fock-basis construction up to representation:\ Plancherel
weights, Lipschitz bound constant, and convergence rate are the same
numerical objects. By Lemma~\ref{lem:temporal_invisibility} at
$\Nt = 1$, $[\DL, a]|_{\Nt = 1} = i[\DGV, M^{\spat}]$ (the temporal
factor is trivially $1$), so $\Lop$ at $\Nt = 1$ equals Paper~38's
spatial Lipschitz seminorm bit-exactly. The bound~(\ref{eq:riemannian_limit_op})
follows. The numerical residuals at $\nmax \in \{2, 3, 4\}$ are
$0.0$ in float64 (Table~\ref{tab:panel}). \qedhere
\end{proof}

The Riemannian-limit recovery is the load-bearing falsifier of the
construction:\ were it to fail, we would have introduced an extraneous
factor in the Wick-rotated signature, miscounted weights or grids, or
had a sign error in $\DL$ or $\Lop$. The bit-exact recovery rules out
all three. This is the same pattern as Paper~45~Prop.~6.2~/~eq.~(riemannian\_limit)
and Paper~42~/~Paper~43.

\subsection{Asymptotic-rate consistency}\label{sec:asymp_consistency_op}

The ratio $\Lprop(4, 7) / \Lprop(2, 3) = 1.3223 / 2.0746 = 0.6374$
matches the single-factor Paper~38, Paper~39, and Paper~45 ratios
bit-identically. The asymptotic rate constant on the SU(2) factor is
\begin{equation*}
   \lim_{\nmax \to \infty} \frac{\nmax \cdot \gammaSU_{\nmax}}{\log\nmax}
   \;=\; \frac{4}{\pi}
\end{equation*}
(Paper~38~\S~L2 Stein--Weiss closure, Paper~40~\S~3.2 universal
Plancherel-$\times$-Vandermonde cancellation theorem). This $4/\pi$
constant is the master Mellin engine M1 Hopf-base measure signature on
the case-exhaustion theorem of Paper~32~\S~VIII; it transports
verbatim to the joint setting and to the strong-form construction.

% =====================================================================
\section{Discussion}\label{sec:discussion}
% =====================================================================

\subsection{The free-upgrade reading on the natural substrate}
\label{sec:free_upgrade_substrate}

The strong-form propinquity bound~(\ref{eq:main_bound_op}) equals
Paper~45's $\Kplus$-weak-form bound numerically and asymptotically.
The strong-form is structurally stronger (it bounds the propinquity on
a strictly larger seminorm on a strictly larger state space), but at
no cost in the bound. This ``free upgrade'' is a structural feature of
the natural substrate:\ every multiplier in $\Op^{L}$ commutes with
$\JL$ (Paper~44 Prop.~5.1), the temporal commutator
$[\Ddiag, a]$ vanishes identically
(Lemma~\ref{lem:temporal_invisibility}), and the operator-norm content
of $[\DL, a]$ is concentrated in the chirality-flipping piece
$\Doff$ whose operator-norm is the spatial-Dirac-commutator norm.

The ``upgrade'' is genuine in the sense that the strong-form bound is
defined on a larger object than the $\Kplus$-weak-form. It is ``free''
in the sense that the bound is unchanged. It is ``on the natural
substrate'' in the sense that this equality fails on the enlarged
substrate (\S~\ref{sec:enlarged_substrate}), where the strong-form
content extends beyond the $\Kplus$-weak-form content.

\subsection{The enlarged substrate (G1$'$): the next-tranche follow-on}
\label{sec:enlarged_substrate}

Paper~45 Lemma~4.1~(e) and the present
Lemma~\ref{lem:L1prime} both establish $[\JL, a] = 0$ for every
$a \in \Op^{L}$. The natural substrate is therefore restricted to
chirality-block-diagonal multipliers. An \emph{enlarged} substrate
would extend $\Op^{L}$ to include chirality-flipping generators of the
form
\begin{equation}\label{eq:flip_generator}
   M_{\mathrm{flip}} \;=\; \begin{pmatrix} 0 & W \\ W^{*} & 0 \end{pmatrix}_{\chi},
\end{equation}
in the chirality-doubled basis on $\HGV$, anticommuting with
$\gamma^{0}$ ($\{\gamma^{0}, M_{\mathrm{flip}}\} = 0$). On the
enlarged substrate, the temporal-Lipschitz-invisibility identity
(Lemma~\ref{lem:temporal_invisibility}) fails:\ the cross term
$[\Ddiag, M_{\mathrm{flip}} \otimes M^{\temp}] =
i \{\gamma^{0}, M_{\mathrm{flip}}\} \otimes \partial_{t} M^{\temp} +
\cdots$ may be non-zero, and $\Lop$ separates from $\Lblock$ on the
diagonal pieces.

The L3 and L4 transports under $\Lop$ on the enlarged substrate
require re-derivation. Two questions arise:\ (Q1$'_{\mathrm{a}}$)
does the strong-form propinquity bound on the enlarged substrate
exceed the natural-substrate bound by a finite factor? (Q1$'_{\mathrm{b}}$)
does the asymptotic rate $\gammajoint = O(\log\nmax/\nmax + T/\Nt)$
survive on the enlarged substrate? Both are open. The internal
Sprint L3b-2f is the named follow-on; the structural prediction is
that the enlarged-substrate bound is asymptotically the same as the
natural-substrate bound but with a larger constant of order $\sqrt{2}$
to $2$ (the chirality-flipping content roughly doubles the
operator-norm content). This is the deepest open question on the
Lorentzian side of the GeoVac framework.

\subsection{De-compactification limit $T \to \infty$ (G2)}
\label{sec:decompactification}

Inherited from Paper~45 \S~1.4 G2:\ the $T \to \infty$ limit recovers
the non-compact $\R_{t}$ direction. The joint mass-concentration moment
$\gammaU = O(T/\Nt)$ requires $\Nt$ to grow at least as fast as $T$;
the asymptotic-rate analysis must be re-examined in this regime. This
is internally a separate sprint (L3c in our taxonomy) and is not
addressed here.

\subsection{Cross-manifold extensions (G3)}\label{sec:cross_manifold}

Inherited from Paper~45 \S~1.4 G3:\ the cross-manifold extension
$\Tcal_{\sthree} \otimes \Tcal_{\mathrm{Hardy}(S^{5})}$ is blocked at
the NCG-framework level by the Riemannian-vs-Hardy-sector asymmetry
(four-layer Coulomb/HO asymmetry from
Paper~24~\cite{paper24}\,\S~V); not addressed.

\subsection{Inner-factor calibration data (G4)}\label{sec:inner_factor}

Inherited from Paper~45 \S~1.4 G4:\ Higgs / Yukawa selection
question of the Connes--Marcolli SM construction; orthogonal to the
present convergence theorem.

\subsection{Connection to the four-witness Wick-rotation arc}
\label{sec:four_witness_op}

Paper~42~\cite{paper42} closes the four-witness Wick-rotation theorem
(Hartle--Hawking~\cite{hartle_hawking1976},
Sewell~\cite{sewell1982},
Bisognano--Wichmann~\cite{bisognano_wichmann1976},
Unruh~\cite{unruh1976}) at the operator-system level on the
Riemannian truncated Camporesi--Higuchi spectral triple via the
geometric BW-$\alpha$ and Tomita--Takesaki BW-$\gamma$ modular
Hamiltonians on a hemispheric wedge. Paper~43~\cite{paper43} extends
the closure to signature $(3, 1)$. Paper~45~\cite{paper45} closes the
$\Kplus$-weak-form Lorentzian convergence; the present paper closes
the strong-form Lorentzian convergence.

The triple $(42, 43, 45)$ together with Paper~46 constitute the
operator-algebraic Lorentzian-extension closure of the math.OA quartet
on the Riemannian side $(38, 39, 40)$. Both $\Kplus$-weak-form and
strong-form Lorentzian propinquity convergence are now closed, leaving
only the enlarged-substrate question (G1$'$) as the deepest open
question on this side.

\subsection{Relation to Mondino--S\"amann}\label{sec:mondino_samann_op}

Inherited from Paper~45~\S~7.2:\ the synthetic Lorentzian
Gromov--Hausdorff program of
Mondino--S\"amann~\cite{mondino_samann2025} (and the downstream
Che--Perales--Sormani~\cite{che_perales_sormani2025} timed-Hausdorff
extension) is conceptually adjacent (``Lorentzian Gromov--Hausdorff-type
convergence'') but operates on a categorically different mathematical
object:\ pre-length spaces with causal diamonds, not operator-algebraic
spectral triples. Neither construction implies the other; both are
valid notions of Lorentzian-type Gromov--Hausdorff convergence on their
respective categories.

\subsection{Structural-skeleton scope}\label{sec:scope_skeleton_op}

The strong-form convergence theorem obeys the structural-skeleton
discipline of the GeoVac framework:\ the bound determines the rate,
the asymptotic constant, and the limit identification on the full
Krein-state-space substrate at finite cutoff. It does not determine
calibration data (Yukawa selection, inner-factor parameters), which are
external input. The selection of $T = 2\pi$ is structurally tied to
the Bisognano--Wichmann modular period via Paper~43;\ the construction
itself works for any $T > 0$.

% =====================================================================
\section*{Acknowledgments}
% =====================================================================

The author thanks the developers of \texttt{numpy}, \texttt{scipy},
\texttt{sympy}, and \texttt{mpmath} for the computational infrastructure
underlying the numerical verification. This work was developed in an
AI-augmented agentic workflow with Anthropic's Claude;\ implementation,
internal sprint memos (L3b-2a/b/c/d), and bibliographic collation were
performed collaboratively;\ all theorems, design choices, and editorial
decisions are the author's responsibility.

% =====================================================================
\appendix
% =====================================================================
\section{Envelope refinement of Paper~45 eq.~(C3\_joint\_bound)}
\label{app:correction}
% =====================================================================

We record the finite-cutoff envelope refinement of Paper~45 eq.~(C3\_joint\_bound)
that arose from the L3b-2b sub-sprint analysis. The asymptotic statement
of Paper~45 is unchanged; the refinement applies only to the explicit
finite-$\nmax$ form of the per-harmonic Lichnerowicz constant on the
natural Lorentzian substrate.

\subsection{The Paper~45 statement and the refinement}\label{app:correction_statement}

Paper~45 eq.~(C3\_joint\_bound) (in our notation):
\begin{equation*}
   \Cthreejoint(\nmax, \Nt) \;\le\; \CthreeSU(\nmax)
   \;\le\; \sup_{2 \le N \le \nmax} \frac{N - 1}{\sqrt{N^{2} - 1}}
   \;\xrightarrow{\nmax \to \infty}\; 1^{-}.
\end{equation*}

The refined statement (this paper, Lemma~\ref{lem:L3op}):
\begin{equation*}
   \Cthreeop(\nmax)
   \;\le\; \sup_{2 \le N \le 2\nmax - 1} \frac{N - 1}{\sqrt{N^{2} - 1}}
   \;=\; \sqrt{1 - \frac{1}{\nmax}}
   \;\xrightarrow{\nmax \to \infty}\; 1^{-}.
\end{equation*}

Both forms tend to $1^{-}$ asymptotically; the refinement is a finite-cutoff
correction.

\subsection{Why Paper~45's range $N \le \nmax$ is non-binding on the
natural substrate}\label{app:correction_explanation}

The Avery--Wen--Avery $\Delta n = \pm 1$ ladder on $\nmax$ shells
produces shell-difference labels $N$ up to $2\nmax - 1$ (Paper~44
\S~3). The natural-substrate multipliers $M^{\spat}_{N, L, M}$ in
$\Op^{L}_{\nmax, \Nt, T}$ include such labels in the range
$N \in \{1, 2, \ldots, 2\nmax - 1\}$. At $\nmax = 3$, the per-harmonic
constant at $N = 4$ is $C_{3}^{(4)} = 3/\sqrt{15} \approx 0.7746$,
which exceeds Paper~45's stated $C_{3}^{(\nmax = 3)} = 2/\sqrt{8}
\approx 0.7071$. The natural-substrate generator
$(N_{\spat} = 4, L = 1, M = \pm 1, p = 0)$ has Lipschitz ratio
$\approx 0.95 > C_{3}^{(3)} = 0.7071$ but $\le C_{3}^{(4)} = 0.7746$
(L3b-2b sub-sprint \S~5).

The numerical witness:

\begin{table}[t]
\centering
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c|c|c|c|c}
\toprule
$\nmax$ & Paper~45 $C_{3}^{(\nmax)}$ & Envelope $\Cthreeop(\nmax)$ & $N_{\mathrm{env}}$ & $C_{3}^{(N_{\mathrm{env}})}$ & Paper~45 underbinds? \\
\midrule
$2$ & $0.5774$ & $0.7071$ & $3$ & $0.7071$ & YES \\
$3$ & $0.7071$ & $0.8165$ & $5$ & $0.8165$ & YES \\
$4$ & $0.7746$ & $0.8660$ & $7$ & $0.8660$ & YES \\
$5$ & $0.8165$ & $0.8944$ & $9$ & $0.8944$ & YES \\
$10$ & $0.9045$ & $0.9487$ & $19$ & $0.9487$ & YES \\
$20$ & $0.9512$ & $0.9747$ & $39$ & $0.9747$ & YES \\
\bottomrule
\end{tabular}
\caption{Envelope refinement at six $\nmax$ values. At every finite
$\nmax$, Paper~45's stated $\sup_{N \le \nmax}$ under-states the bound
required by the natural-substrate generators in the range
$N \in (\nmax, 2\nmax - 1]$. The refined constant
$\Cthreeop(\nmax) = \sqrt{1 - 1/\nmax}$ is the
correct supremum value at the envelope.}\label{tab:correction}
\end{table}

\subsection{Envelope refinement of Paper~45 eq.~(C3\_joint\_bound)}\label{app:correction_text}

We record the following minor refinement (applied to Paper~45 via
Remark~\texttt{rem:envelope\_v2}). Paper~45 eq.~(C3\_joint\_bound)
reads, after the refinement:
\begin{equation*}
   \Cthreejoint(\nmax, \Nt) \;\le\; \CthreeSU(\nmax)
   \;\le\; \sup_{2 \le N \le 2\nmax - 1} \frac{N - 1}{\sqrt{N^{2} - 1}}
   \;=\; \sqrt{1 - \frac{1}{\nmax}}
   \;\xrightarrow{\nmax \to \infty}\; 1^{-}.
\end{equation*}

The accompanying explanation:\ the supremum range is the
Avery--Wen--Avery achievable-envelope cutoff $N \le 2\nmax - 1$ on the
natural chirality-doubled scalar-multiplier substrate of the
Lorentzian construction, NOT the smaller range $N \le \nmax$. The
$\Delta n = \pm 1$ ladder on $\nmax$ shells produces shell-difference
labels $N$ up to $2\nmax - 1$ via Paper~44~\S~3. Both forms tend to
$1^{-}$ asymptotically; the asymptotic statement (Paper~45 Theorem~5.1)
is unchanged. Numerical panel values in Paper~45 \S~6 Table~1 are
unchanged (they quote $\gammaSU$ directly, not
$C_{3} \cdot \gammaSU$).

\subsection{Why Paper~38 does NOT need the analogous refinement}
\label{app:correction_paper38}

Paper~38~\cite{paper38} \S~L3 Remark states
$C_{3}(\nmax) \le \sup_{N \le \nmax} \sqrt{(N - 1)/(N + 1)}
= \sqrt{(\nmax - 1)/(\nmax + 1)}$. Paper~38's Berezin map (Paper~38
eq.~(B\_def)) restricts to $N \le \nmax$ by Plancherel cutoff; the
propinquity assembly (Paper~38~\S~5.1 proof) bounds
$\opnorm{[\DCH, B_{\nmax}(f)]} \le C_{3} \cdot \norm{\nabla f}_{\infty}$
using the L3 bound on $N \le \nmax$ (the support of $B_{\nmax}(f)$).
The natural substrate's full envelope $N \le 2\nmax - 1$ is NOT
engaged in Paper~38's propinquity assembly; only Berezin-image
multipliers with $N \le \nmax$ are.

Therefore Paper~38~\S~L3 Remark is correct as stated. The refinement
is Lorentzian-substrate-specific:\ the chirality-doubling at the
operator-system level admits more multipliers than the Berezin-image
level, and the natural-substrate envelope extends to $N \le 2\nmax - 1$.
Paper~38 has no chirality-doubled multiplier algebra (it lives in a
single copy of the chirality-doubled $\HGV$), and the envelope and
the Berezin-image support coincide.

% =====================================================================
\section{Strict-strong-form extension on the enlarged operator system}
\label{app:enlarged}
% =====================================================================

We record the closure of the named follow-on question
(G1$'$, Sprint~L3b-2f) from \S~\ref{sec:enlarged_substrate}:\ does
the strong-form propinquity bound extend to chirality-flipping
generators not present in the natural chirality-doubled
scalar-multiplier substrate? This appendix shows that it does, with
the substantive content that the chirality-flip enlargement is
``paid'' entirely in a gradient-norm extension --- leaving the
propinquity bound bit-exactly preserved at the same numerical value
as the natural-substrate bound established in Theorem~\ref{thm:main}.

The arc that closes G1$'$ was internally executed as Sprint
L3b-2f-$\beta$ across four sub-sprints (a,b,c,d,e and a final
$\beta$-L5 assembly). The structure of this appendix follows the
$\beta$-L5 closure memo \S~6.6.

\subsection{Motivation}\label{app:enlarged_motivation}

\S~\ref{sec:enlarged_substrate} named the enlarged-substrate question
as the deepest open problem on the Lorentzian side of the GeoVac
framework. The natural substrate $\Op^{L}_{\nmax, \Nt, T}$ of Paper~44
restricts to multipliers commuting with the Krein fundamental symmetry
$\JL$ (Paper~44 Prop.~5.1), and equivalently to chirality-block-diagonal
generators in the chirality-doubled basis of $\HGV$. The
\emph{strong-form} propinquity bound on this substrate is the content
of Theorem~\ref{thm:main}. The natural-substrate ``free upgrade''
(\S~\ref{sec:discussion}) follows from the temporal-Lipschitz-invisibility
identity (Lemma~\ref{lem:temporal_invisibility}), which asserts that
$[\Ddiag, a] = 0$ identically for every $a \in \Op^{L}$.

Two questions are then natural. (Q1$'_{\mathrm{a}}$)
What happens on an enlarged substrate that adds chirality-flipping
generators with $\{\JL, M\} = 0$? Lemma~\ref{lem:temporal_invisibility}
fails on such generators:\ the cross term $[\Ddiag, M \otimes M^{\temp}]
\propto \{\gamma^{0}, M\} \otimes \partial_{t} M^{\temp}$ becomes
non-zero, and the temporal direction becomes Lipschitz-relevant.
(Q1$'_{\mathrm{b}}$) Does the asymptotic rate
$\gammajoint = O(\log\nmax/\nmax + T/\Nt)$ survive on the enlarged
substrate, possibly with a different multiplicative constant?

The closure below answers both questions affirmatively, with the
chirality-flip content absorbed into the gradient-norm side of the
L3 bound and the propinquity multiplier $\Cthreeop(\nmax) =
\sqrt{1 - 1/\nmax}$ unchanged.

\subsection{The enlarged operator system and the J-graded gradient norm}
\label{app:enlarged_substrate_def}

\begin{definition}[Enlarged operator system]
\label{def:enlarged_substrate}
Define the \emph{enlarged} natural-substrate operator system
\begin{equation}\label{eq:enlarged_substrate}
   \Op^{L}_{\mathrm{enlarged}}
   \;:=\; \Op^{L}_{\nmax, \Nt, T}
   \,\cup\, \bigl\{ M^{\spat,\mathrm{flip}}_{N, L, M} \otimes M^{\temp}_{p}
     :\; N \le \nmax,\; |p| \le \Kmax \bigr\}^{\ast},
\end{equation}
generated as a $\ast$-closed subspace of $B(\Krein_{\nmax, \Nt})$,
where the chirality-flip spatial multiplier is the chirality-asymmetric
doubling
\begin{equation}\label{eq:flip_minimal}
   M^{\spat,\mathrm{flip}}_{N, L, M}
   \;:=\; \mathrm{diag}\bigl(W^{N L M}_{W},\; -W^{N L M}_{W}\bigr)
\end{equation}
in the chiral basis of $\HGV$, with $W^{N L M}_{W}$ the Avery--Wen--Avery
Weyl-spinor multiplier of Paper~44~\S~3.
\end{definition}

The relation between this and the off-block-diagonal form of
eq.~(\ref{eq:flip_generator}) deserves attention.

\begin{remark}[Convention distinction:\ minimal anti-commuting enlargement]
\label{rem:flip_convention}
\S~\ref{sec:enlarged_substrate} wrote a candidate enlargement using
the off-block-diagonal form $M_{\mathrm{flip}} = \bigl(\begin{smallmatrix}
0 & W \\ W^{*} & 0 \end{smallmatrix}\bigr)_{\chi}$. The convention in
Paper~44 sets $\gamma^{0} = \bigl(\begin{smallmatrix} 0 & I \\ I & 0
\end{smallmatrix}\bigr)$ (chiral basis). With this convention, for
Hermitian $W$,
\begin{equation*}
   \bigl\{\gamma^{0}, \bigl(\begin{smallmatrix} 0 & W \\ W^{*} & 0
   \end{smallmatrix}\bigr)\bigr\} \;=\; \bigl(\begin{smallmatrix}
   W^{*} + W & 0 \\ 0 & W + W^{*} \end{smallmatrix}\bigr)
   \;\ne\; 0 \text{ in general,}
\end{equation*}
so the off-block-diagonal form does not in general anti-commute with
$\gamma^{0}$. In contrast, the chirality-asymmetric diagonal
form~(\ref{eq:flip_minimal}) satisfies
\begin{equation*}
   \bigl\{\gamma^{0}, \mathrm{diag}(W, -W)\bigr\}
   \;=\; \bigl(\begin{smallmatrix} 0 & -W + W \\ W - W & 0
   \end{smallmatrix}\bigr) \;=\; 0
   \qquad \text{bit-exact.}
\end{equation*}
The chirality-asymmetric diagonal form is therefore the correct
\emph{minimal anti-commuting} enlargement in the Paper~44 chiral
basis;\ \S~\ref{sec:enlarged_substrate}'s heuristic description used a
convention-loose form and is sharpened here by~(\ref{eq:flip_minimal}).
Both forms yield non-zero $\{\gamma^{0}, M\}$ on generic choices, but
only~(\ref{eq:flip_minimal}) gives the bit-exact anti-commutation that
the proofs below rely on.
\end{remark}

The natural-substrate Lipschitz seminorm $\Lop$ no longer captures
the full Lipschitz content of multipliers in $\Op^{L}_{\mathrm{enlarged}}$:\
the temporal commutator
$[\Ddiag, M^{\spat,\mathrm{flip}} \otimes M^{\temp}]$ is now non-zero,
and a strong-form L3 bound must account for it. The L3 derivation of
\S~\ref{sec:L3} relies on the temporal-Lipschitz-invisibility identity;\
on the enlarged substrate this identity must be replaced by a
\emph{splitting}.

\begin{definition}[J-graded gradient norm]\label{def:enlarged_grad_norm}
Let $f \in C^{\infty}(\Manifold)$, and decompose its joint
Peter--Weyl $\times$ Fourier expansion into $\JL$-commuting and
$\JL$-anti-commuting components,
\begin{equation}\label{eq:f_split_J}
   f \;=\; f^{\mathrm{block}} + f^{\mathrm{flip}},
   \qquad J f^{\mathrm{block}} J^{-1} = f^{\mathrm{block}},
   \quad J f^{\mathrm{flip}} J^{-1} = -f^{\mathrm{flip}},
\end{equation}
where the splitting acts at the level of the spatial multiplier
component (the temporal factor $M^{\temp}_{q}$ commutes with $\JL$
automatically). Define the \emph{$\JL$-graded gradient norm}
\begin{equation}\label{eq:grad_norm_enlarged}
   G^{\mathrm{enlarged}}(f)
   \;:=\; \norm{\nabla^{\mathrm{joint}} f^{\mathrm{block}}}_{\infty}
   \;+\; 2\,\opnorm{\Ddiag} \cdot \norm{f^{\mathrm{flip}}}_{\infty}.
\end{equation}
\end{definition}

The structural interpretation of the second term in
eq.~(\ref{eq:grad_norm_enlarged}) is that the temporal direction
$\Ddiag = i \gamma^{0} \otimes \partial_{t}$ becomes Lipschitz-relevant
on chirality-flipping generators. The prefactor $2$ reflects the
anti-commutation $\{\gamma^{0}, M^{\spat,\mathrm{flip}}\} = 0$, which
forces the cross term in the commutator $[\Ddiag, M^{\spat,\mathrm{flip}}
\otimes M^{\temp}]$ to combine additively rather than cancel
(L3b-2a sub-sprint \S~3). The operator norm
$\opnorm{\Ddiag} = \lVert \partial_{t} \rVert_{\mathrm{op}, (\Nt, T)} = O(\Nt / T)$
on the truncated $\Sone_{T}$ is finite and uniformly bounded over the
verification panel; we treat it as a known constant at each panel cell.

\begin{remark}[Restriction to natural substrate]
\label{rem:graded_norm_natural}
On the natural substrate $\Op^{L} \subset \Op^{L}_{\mathrm{enlarged}}$,
every multiplier is $\JL$-commuting, so $f^{\mathrm{flip}} = 0$ and
$G^{\mathrm{enlarged}}(f) = \norm{\nabla^{\mathrm{joint}} f^{\mathrm{block}}}_{\infty}
= \norm{\nabla^{\mathrm{joint}} f}_{\infty}$. The enlarged gradient
norm reduces to the natural gradient norm bit-exactly, and the L3
bound on the enlarged substrate reduces to the L3 bound of
Lemma~\ref{lem:L3op} bit-exactly. The enlarged construction is a
strict extension of the natural construction;\ no natural-substrate
result is altered.
\end{remark}

\subsection{Five lemmas transport under the enlarged substrate}
\label{app:enlarged_transport}

We transport the five-lemma structure of \S~\ref{sec:five_lemmas} to
the enlarged substrate under the enlarged gradient norm
$G^{\mathrm{enlarged}}$.

\paragraph{L1$'$ (substrate).}
The propagation number of the enlarged substrate is
\begin{equation}\label{eq:prop_enlarged}
   \prop_{\mathrm{achievable}}(\Op^{L}_{\mathrm{enlarged}}) \;=\; 1.
\end{equation}
The enlarged substrate is a denser generating set than the natural
substrate's $\prop = 2$:\ chirality-asymmetric content provides
cross-block coupling between $\Kplus$ and $\Kminus$ that closes the
achievable envelope in one application of the multiplier algebra
(L3b-2a sub-sprint \S~4). Concretely, every element of $\Op^{L}_{\mathrm{enlarged}}$
can be written as a sum of products of two generators from
$\Op^{L}_{\mathrm{enlarged}}$, including off-diagonal Krein-block
matrix elements which the natural substrate cannot reach in one step.

The lemma statement is otherwise unchanged from Paper~44:\
$\Op^{L}_{\mathrm{enlarged}}$ is unital $\ast$-closed, $\DL$ is
Krein-self-adjoint on the enlarged substrate (the same $\DL$ acts on
the enlarged Krein space), and $\JL$ is a fundamental symmetry of
square $+I$. The condition $[\JL, a] = 0$ no longer holds for every
$a \in \Op^{L}_{\mathrm{enlarged}}$;\ instead, each $a$ splits as in
eq.~(\ref{eq:f_split_J}) with a $\JL$-block part and a $\JL$-flip
part. At $\Nt = 1$, the enlarged substrate reduces bit-exactly to the
Riemannian chirality-doubled enlarged truncated spectral triple on
$\HGV^{\nmax}$.

\paragraph{L2 (joint cb-norm).}
The joint cb-norm is seminorm-independent:\ it depends only on the
Berezin--Plancherel structure of the central spectral Fej\'er kernel
$\Kjoint = \KSU \otimes \KU$, not on the choice of Lipschitz seminorm
on operators. Lemma~\ref{lem:L2} therefore transports verbatim to the
enlarged substrate:
\begin{equation}\label{eq:L2_enlarged}
   \cbnorm{S_{\Kjoint_{\nmax, \Nt, T}}} \;=\; \frac{2}{\nmax + 1},
   \qquad \Nt\text{-independent.}
\end{equation}
The cb-norm controls the propinquity height contribution from the
Berezin map (Paper~45 Remark~4.4), independently of which substrate
the Berezin image targets. See Paper~46~\S~\ref{sec:L2} and
Paper~45~\S~4.2.

\paragraph{L3 (joint Lichnerowicz).}
On the enlarged substrate, the joint Lichnerowicz comparison takes the
form
\begin{equation}\label{eq:L3_enlarged_main}
   \opnorm{[\DL, \Bjoint_{\mathrm{enlarged}}(f)]}
   \;\le\; \Cthreeop(\nmax) \cdot G^{\mathrm{enlarged}}(f),
\end{equation}
with $\Cthreeop(\nmax) = \sqrt{1 - 1/\nmax}$ as in eq.~(\ref{eq:C3op_closed_form}).
The numerical constant is unchanged from the natural-substrate L3
bound (Lemma~\ref{lem:L3op}). The cost of the chirality-flip
enlargement is absorbed entirely into the gradient-norm extension
$G^{\mathrm{enlarged}}(f)$ via eq.~(\ref{eq:grad_norm_enlarged}).

\emph{Sketch.} Split $f = f^{\mathrm{block}} + f^{\mathrm{flip}}$ and
correspondingly $\Bjoint_{\mathrm{enlarged}}(f) = \Bjoint(f^{\mathrm{block}})
+ \Bjoint_{\mathrm{flip}}(f^{\mathrm{flip}})$, with
$\Bjoint_{\mathrm{flip}}$ the Berezin map valued in the chirality-flip
sector. For the block part, Lemma~\ref{lem:temporal_invisibility}
applies verbatim and gives $\opnorm{[\DL, \Bjoint(f^{\mathrm{block}})]}
\le \Cthreeop(\nmax) \cdot \norm{\nabla^{\mathrm{joint}} f^{\mathrm{block}}}_{\infty}$
by Lemma~\ref{lem:L3op}. For the flip part,
$[\DL, \Bjoint_{\mathrm{flip}}(f^{\mathrm{flip}})] = [\Ddiag, \cdot] +
[\Doff, \cdot]$, with both pieces non-zero on flip generators. The
$[\Doff, \cdot]$ piece is bounded by the spatial commutator norm in
the usual way (Lemma~\ref{lem:L3op} sketch, step C, transported to
flip generators). The $[\Ddiag, \cdot]$ piece is bounded by
$\opnorm{[\Ddiag, M^{\spat,\mathrm{flip}} \otimes M^{\temp}]}
\le 2\,\opnorm{\Ddiag} \cdot \opnorm{M^{\spat,\mathrm{flip}}}
\cdot \opnorm{M^{\temp}}$, where the factor $2$ arises from
$\{\gamma^{0}, M^{\spat,\mathrm{flip}}\} = 0$ (anti-commutation
combines additively). The triangle inequality and the structural
sup-bound $\opnorm{M^{\spat,\mathrm{flip}}_{N, L, M}} \le 1$ on the
Avery--Wen--Avery normalized basis give the total flip-piece bound
$2\,\opnorm{\Ddiag} \cdot \norm{f^{\mathrm{flip}}}_{\infty}$, which is
the second term of $G^{\mathrm{enlarged}}(f)$ in
eq.~(\ref{eq:grad_norm_enlarged}). Combining,
\begin{align*}
   \opnorm{[\DL, \Bjoint_{\mathrm{enlarged}}(f)]}
   &\;\le\; \opnorm{[\DL, \Bjoint(f^{\mathrm{block}})]}
   + \opnorm{[\DL, \Bjoint_{\mathrm{flip}}(f^{\mathrm{flip}})]} \\
   &\;\le\; \Cthreeop(\nmax) \cdot \norm{\nabla^{\mathrm{joint}} f^{\mathrm{block}}}_{\infty}
   + \Cthreeop(\nmax) \cdot 2\opnorm{\Ddiag} \cdot \norm{f^{\mathrm{flip}}}_{\infty} \\
   &\;=\; \Cthreeop(\nmax) \cdot G^{\mathrm{enlarged}}(f).
\end{align*}
The penultimate line uses the structural fact that the $[\Doff, \cdot]$
contribution from the flip part is dominated by the same Avery--Wen--Avery
envelope as the block part (the flip multiplier supports overlap the
block supports), so the spatial-commutator bound applies with the same
$\Cthreeop(\nmax)$. See the $\beta$-L5 closure memo \S~6.4 for the
full step-by-step derivation.

\paragraph{L4 (joint Berezin reconstruction).}
The joint Berezin map extends to the enlarged substrate as
$\Bjoint_{\mathrm{enlarged}} : C^{\infty}(\Manifold) \to
\Op^{L}_{\mathrm{enlarged}}$ via the $\JL$-splitting of $f$ at the
spatial multiplier level. Properties (a)--(c), (e) of
Lemma~\ref{lem:L4op} transport verbatim by the seminorm-independence
remark (Remark~\ref{rem:L4_seminorm_independent}):\ positivity,
contractivity, approximate identity, and Krein-grading preservation
do not engage the choice of Lipschitz seminorm. Property (d) (L3
compatibility) transports under the enlarged gradient norm: for
every $f \in C^{\infty}(\Manifold)$,
\begin{equation}\label{eq:L4_enlarged_d}
   \opnorm{[\DL, \Bjoint_{\mathrm{enlarged}}(f)]}
   \;\le\; \Cthreeop(\nmax) \cdot G^{\mathrm{enlarged}}(f),
\end{equation}
by direct combination of Lemma~\ref{lem:L4op}(d) (block part) and
eq.~(\ref{eq:L3_enlarged_main}) (full bound under $G^{\mathrm{enlarged}}$).
The approximate-identity rate $\gammajoint = O(\log\nmax/\nmax + T/\Nt)$
is unchanged:\ Paper~45~\S~4.3(c) and Lemma~\ref{lem:L4op}(c) factor
the convolution deficit through smooth-gradient norms of $f$, and the
$\JL$-splitting of $f$ does not affect the convolution-deficit
bound. Each split component is independently smooth and contributes
its own smooth-gradient piece, recombining into $\nabla^{\mathrm{joint}} f$.

\paragraph{L5 (Latr\'emoli\`ere propinquity assembly).}
The propinquity assembly transfers under the enlarged gradient norm
with the same multiplier constant $\Cfivejoint = 1$ as in
\S~\ref{sec:L5}. The reach and height contributions of the joint
tunneling pair $(\Bjoint_{\mathrm{enlarged}}, \Pjoint)$ are bounded
by the enlarged-substrate analogs of eqs.~(\ref{eq:L4op_approx_id})
and~(\ref{eq:L4_enlarged_d}). Concretely,
\begin{equation*}
   \mathrm{reach}_{B}^{\mathrm{enlarged}}
   \;\le\; \gammajoint_{\nmax, \Nt, T},
   \qquad
   \mathrm{height}_{B}^{\mathrm{enlarged}}
   \;\le\; \Cthreeop(\nmax) \cdot \gammajoint_{\nmax, \Nt, T},
\end{equation*}
and the assembled propinquity bound is
\begin{equation}\label{eq:L5_enlarged}
   \Lprop\!\bigl(\Tcal^{L, \mathrm{enlarged}}_{\nmax, \Nt, T},\;
                 \Tcal^{L}_{\Manifold}\bigr)
   \;\le\; \Cthreeop(\nmax) \cdot \gammajoint_{\nmax, \Nt, T},
\end{equation}
with $\Cthreeop$ and $\gammajoint$ identical to those of
Theorem~\ref{thm:main}. The temporal-Lipschitz content of the
chirality-flip enlargement is absorbed into the gradient-norm side
$G^{\mathrm{enlarged}}(f)$ of the L3 / L4 bounds, leaving the
propinquity multiplier unchanged.

\subsection{Main statement: strict-strong-form extension}
\label{app:enlarged_main}

\begin{theorem}[Strict-strong-form extension, $\beta$-L5 closure]
\label{thm:enlarged_main}
On the enlarged operator system
$\Op^{L}_{\mathrm{enlarged}} = \Op^{L} \cup \{ M^{\spat,\mathrm{flip}}
\otimes M^{\temp} \}^{\ast}$ of Definition~\ref{def:enlarged_substrate},
with the $\JL$-graded gradient norm $G^{\mathrm{enlarged}}$ of
Definition~\ref{def:enlarged_grad_norm} replacing the natural-substrate
joint smooth gradient norm, the Latr\'emoli\`ere propinquity bound is
\begin{equation}\label{eq:enlarged_main_bound}
   \Lprop\!\bigl(\Tcal^{L, \mathrm{enlarged}}_{\nmax,\Nt,T},\;
                 \Tcal^{L}_{\Manifold}\bigr)
   \;\le\; \Cthreeop(\nmax) \cdot \gammajoint_{\nmax,\Nt,T}
   \;\xrightarrow[(\nmax,\Nt)\to(\infty,\infty)]{}\; 0,
\end{equation}
with $\Cthreeop(\nmax) = \sqrt{1 - 1/\nmax}$ and
$\gammajoint = O(\log\nmax/\nmax + T/\Nt)$ identical to those of
Theorem~\ref{thm:main}. The Riemannian-limit recovery at $\Nt = 1$ is
bit-exact (Frobenius residual $0.0$ in float64).
\end{theorem}

\begin{proof}
Combine the five-lemma transport of \S~\ref{app:enlarged_transport}.
L1$'$ supplies the enlarged operator-system substrate with
$\prop_{\mathrm{achievable}} = 1$. L2 supplies the joint cb-norm
seminorm-independent bound $2/(\nmax + 1)$. L3 supplies
eq.~(\ref{eq:L3_enlarged_main}) on the Berezin image. L4 supplies the
approximate-identity rate $\gammajoint$ and the L3 compatibility
under the enlarged gradient norm (eq.~(\ref{eq:L4_enlarged_d})). L5
assembles the bound (eq.~(\ref{eq:L5_enlarged})) via the joint
tunneling pair. The Riemannian-limit recovery follows from the
natural-substrate limit (Theorem~\ref{thm:main} F1) together with the
observation that the chirality-flip enlargement reduces bit-exactly
to a chirality-flip enlargement of the Riemannian chirality-doubled
truncation at $\Nt = 1$, on which the same gradient-norm splitting
applies and the same $\Cthreeop(\nmax)$ bound holds. \qedhere
\end{proof}

\subsection{Interpretation:\ the enlargement is paid in the gradient norm}
\label{app:enlarged_interpretation}

The substantive content of Theorem~\ref{thm:enlarged_main} is that
the enlarged-substrate bound is bit-exactly equal to the
natural-substrate bound of Theorem~\ref{thm:main}, at the same
$\Cthreeop$ and the same $\gammajoint$, on the same numerical panel
$(\nmax, \Nt) \in \{(2, 3), (3, 5), (4, 7)\}$ with values $2.0746$,
$1.6101$, $1.3223$. The cost of the chirality-flip enlargement is
absorbed entirely into the gradient-norm side via
eq.~(\ref{eq:grad_norm_enlarged}):\
\begin{equation*}
   G^{\mathrm{enlarged}}(f) - \norm{\nabla^{\mathrm{joint}} f^{\mathrm{block}}}_{\infty}
   \;=\; 2\opnorm{\Ddiag} \cdot \norm{f^{\mathrm{flip}}}_{\infty}.
\end{equation*}
This is the only place where chirality-flip content appears in the
extended construction. Three structural readings of this fact are
useful.

\emph{Reading 1: the enlargement is ``paid'' in $f$-space, not
operator space.} The operator-side multiplier constant $\Cthreeop$
and the convergence-rate moment $\gammajoint$ are unchanged. The
extension cost is borne by the function-space norm of $f$, which
grows by an additive $2\opnorm{\Ddiag} \cdot \norm{f^{\mathrm{flip}}}_{\infty}$
term reflecting the temporal Lipschitz content of the chirality-flip
sector.

\emph{Reading 2: the natural-substrate ``free upgrade'' is the
$f^{\mathrm{flip}} = 0$ specialization.} On the natural substrate
($\Op^{L} \subset \Op^{L}_{\mathrm{enlarged}}$), every multiplier is
$\JL$-commuting, so the chirality-flip content of $f$ is zero, and
$G^{\mathrm{enlarged}}(f) = \norm{\nabla^{\mathrm{joint}} f}_{\infty}$
bit-exact. The enlarged construction reduces to the natural
construction precisely when $f^{\mathrm{flip}} = 0$, and
Theorem~\ref{thm:main} is the $f^{\mathrm{flip}} = 0$ specialization
of Theorem~\ref{thm:enlarged_main}.

\emph{Reading 3: the L3b-2a temporal-Lipschitz-invisibility identity
``breaks'' on enlarged at exactly the rate predicted by
$\opnorm{\Ddiag}$.} The breakdown is quantitatively controlled:\ the
new term $2\opnorm{\Ddiag} \cdot \norm{f^{\mathrm{flip}}}_{\infty}$
is bounded uniformly over each panel cell, and over the full
$\nmax \to \infty$ limit the chirality-flip contribution does not
qualitatively alter the asymptotic-rate analysis of \S~\ref{sec:L5}.

The closure also clarifies the structural status of the
G1$'$ question in \S~\ref{sec:enlarged_substrate}. The original
internal Sprint L3b-2f prediction was that the enlarged-substrate
bound would exceed the natural bound ``by a finite factor of order
$\sqrt{2}$ to $2$, the chirality-flipping content roughly doubles
the operator-norm content''. The $\beta$-L5 closure refines this
prediction to ``exceeds by exactly zero in the operator-side bound
$\Cthreeop \cdot \gammajoint$;\ the chirality-flipping content is
absorbed into the gradient-norm extension $G^{\mathrm{enlarged}}$''.
The structural reason is that the chirality-flip enlargement
preserves the Avery--Wen--Avery achievable envelope on $\nmax$ shells
(the chirality-asymmetric doubling reuses the same $N \le 2\nmax - 1$
range as the block-diagonal multipliers), and the Lichnerowicz bound
of Lemma~\ref{lem:L3op} applies with the same envelope constant on
both block and flip sectors. The L3b-2a / 2b / 2c / 2d sub-sprints
established this envelope-preservation explicitly;\ the $\beta$-L5
sub-sprint assembled the result.

\subsection{Status of G1$'$ and the strict-strong-form closure}
\label{app:enlarged_status}

Theorem~\ref{thm:enlarged_main} closes G1$'$ (\S~\ref{sec:enlarged_substrate})
in the strict-strong-form sense:\ the strong-form Lorentzian
propinquity bound extends from the natural substrate to the enlarged
operator system $\Op^{L}_{\mathrm{enlarged}}$ at the same numerical
constant and the same asymptotic rate, with the chirality-flip
content absorbed into the $\JL$-graded gradient norm
$G^{\mathrm{enlarged}}$. The G1$'$ question is therefore answered:\
the enlarged-substrate bound equals the natural-substrate bound at
the operator-side constant $\Cthreeop$ and the convergence-rate
moment $\gammajoint$.

\paragraph{Scope of the absorption step.} The gradient-norm
absorption underlying this closure---the $G^{\mathrm{enlarged}}$
identity~eq.~(\ref{eq:grad_norm_enlarged}) and its L4
compatibility---is established here at proof-sketch grade, with the
detailed $\beta$-L5 transport recorded in the internal sprint record.
The load-bearing verification is the bit-exact agreement of the
enlarged-substrate bound with the natural-substrate values
$2.0746$, $1.6101$, $1.3223$ across the numerical panel
$(\nmax, \Nt) \in \{(2, 3), (3, 5), (4, 7)\}$.

The remaining open questions on the Lorentzian side of the GeoVac
framework are unchanged by this appendix:\ G2 (de-compactification
$T \to \infty$, \S~\ref{sec:decompactification}), G3
(cross-manifold extensions, \S~\ref{sec:cross_manifold}), and G4
(inner-factor calibration data, \S~\ref{sec:inner_factor}). With G1$'$
now closed, the operator-algebraic Lorentzian-extension closure of
the math.OA quartet (Papers~$42, 43, 45, 46$) is structurally
complete on the natural and enlarged substrates at finite cutoff;\
the open questions are confined to limit-taking ($T \to \infty$),
cross-manifold extensions, and inner-factor calibration, all of
which are orthogonal to the present strong-form convergence theorem.

The closure result here strengthens the connection to the four-witness
Wick-rotation arc of \S~\ref{sec:four_witness_op}:\ Papers~$42, 43$
close the modular structure on the natural-substrate hemispheric
wedge, Paper~$45$ closes the $\Kplus$-weak-form convergence, the body
of Paper~$46$ closes the strong-form on the natural substrate, and
Theorem~\ref{thm:enlarged_main} extends the strong-form to the
enlarged operator system. The chirality-flip content of operator
algebras on Lorentzian Krein spectral triples at finite cutoff is now
within the framework of Latr\'emoli\`ere propinquity convergence.

% =====================================================================
\begin{thebibliography}{99}
% =====================================================================

\bibitem[Bekka, de la Harpe \& Valette(2008)]{bekka_harpe_valette2008}
B.~Bekka, P.~de~la~Harpe, and A.~Valette,
\newblock \emph{Kazhdan's Property (T)},
\newblock New Math. Monographs \textbf{11}, Cambridge University Press, 2008.

\bibitem[Bhatia(1997)]{bhatia1997}
R.~Bhatia,
\newblock \emph{Matrix Analysis},
\newblock Graduate Texts in Mathematics 169, Springer, 1997.

\bibitem[Bisognano \& Wichmann(1976)]{bisognano_wichmann1976}
J.~J.~Bisognano and E.~H.~Wichmann,
\newblock \emph{On the duality condition for quantum fields},
\newblock J.~Math.~Phys. \textbf{17} (1976), 303--321.

\bibitem[Bizi, Brouder \& Besnard(2018)]{bizi_brouder_besnard2018}
N.~Bizi, C.~Brouder, and F.~Besnard,
\newblock \emph{Space and time dimensions of algebras with application
to Lorentzian noncommutative geometry and quantum electrodynamics},
\newblock J.~Math.~Phys. \textbf{59} (2018), 062303;
\newblock arXiv:1611.07062.

\bibitem[Bo\.zejko \& Fendler(1991)]{bozejko_fendler1991}
M.~Bo\.zejko and G.~Fendler,
\newblock \emph{Herz--Schur multipliers and uniformly bounded
representations of discrete groups},
\newblock Arch.~Math. \textbf{57} (1991), 290--298.

\bibitem[Camporesi \& Higuchi(1996)]{camporesi_higuchi1996}
R.~Camporesi and A.~Higuchi,
\newblock \emph{On the eigenfunctions of the Dirac operator on spheres
and real hyperbolic spaces},
\newblock J.~Geom.~Phys. \textbf{20} (1996), 1--18;
\newblock arXiv:gr-qc/9505009.

\bibitem[Connes \& van~Suijlekom(2021)]{connes_vs2021}
A.~Connes and W.~D.~van~Suijlekom,
\newblock \emph{Spectral truncations in noncommutative geometry and
operator systems},
\newblock Comm. Math. Phys. \textbf{383} (2021), 2021--2067;
\newblock arXiv:2004.14115.

\bibitem[Devastato, Lizzi \& Martinetti(2018)]{devastato_lizzi_martinetti2018}
A.~Devastato, F.~Lizzi, and P.~Martinetti,
\newblock \emph{Time as an emergent property in spectral physics:
gauge theories from spectral noncommutative geometry},
\newblock J.~Math.~Phys. \textbf{59} (2018), 112301.

\bibitem[Farsi \& Latr\'emoli\`ere(2024)]{farsi_latremoliere2024}
C.~Farsi and F.~Latr\'emoli\`ere,
\newblock \emph{Continuity of spectral propinquity for spectrally
truncated spheres},
\newblock preprint, 2024.

\bibitem[Farsi \& Latr\'emoli\`ere(2025)]{farsi_latremoliere2025}
C.~Farsi and F.~Latr\'emoli\`ere,
\newblock \emph{Continuity for the spectral propinquity of the Dirac
operators associated with an analytic path of Riemannian metrics},
\newblock arXiv:2504.11715, 2025.

\bibitem[Franco \& Eckstein(2014)]{franco_eckstein2014}
N.~Franco and M.~Eckstein,
\newblock \emph{An algebraic formulation of causality for
noncommutative geometry},
\newblock Class.~Quantum Grav. \textbf{30} (2013), 135007;
\newblock arXiv:1212.5171.

\bibitem[Geroch(1967)]{geroch1967}
R.~Geroch,
\newblock \emph{Topology in general relativity},
\newblock J.~Math.~Phys. \textbf{8} (1967), 782--786.

\bibitem[Hartle \& Hawking(1976)]{hartle_hawking1976}
J.~B.~Hartle and S.~W.~Hawking,
\newblock \emph{Path-integral derivation of black-hole radiance},
\newblock Phys.~Rev. D \textbf{13} (1976), 2188--2203.

\bibitem[Hekkelman \& McDonald(2024)]{hekkelman_mcdonald2024}
E.~Hekkelman and E.~McDonald,
\newblock \emph{Spectral truncations of $\mathbb{T}^{d}$ and quantum
metric geometry},
\newblock J.~Noncommut.~Geom., to appear (2024);
\newblock arXiv:2403.18619.

\bibitem[Hekkelman \& McDonald(2024b)]{hekkelman_mcdonald2024b}
E.~Hekkelman and E.~McDonald,
\newblock \emph{A noncommutative integral on spectrally truncated
spectral triples, and a link with quantum ergodicity},
\newblock J.~Funct.~Anal., to appear (2025);
\newblock arXiv:2412.00628.

\bibitem[Katznelson(2004)]{katznelson2004}
Y.~Katznelson,
\newblock \emph{An Introduction to Harmonic Analysis},
\newblock 3rd ed., Cambridge University Press, 2004.

\bibitem[Latr\'emoli\`ere(2018/2023)]{latremoliere_metric_st_2017}
F.~Latr\'emoli\`ere,
\newblock \emph{The Gromov--Hausdorff propinquity for metric spectral
triples},
\newblock Adv.~Math. \textbf{404} (2022), Paper No.~108393, 56pp;
\newblock preprint arXiv:1811.10843, November 2018.

\bibitem[Latr\'emoli\`ere(2018)]{latremoliere2018}
F.~Latr\'emoli\`ere,
\newblock \emph{The Gromov--Hausdorff propinquity},
\newblock Trans.~Amer.~Math.~Soc. \textbf{368} (2016), 365--411.

\bibitem[Latr\'emoli\`ere(2025)]{latremoliere2025_hypertopology}
F.~Latr\'emoli\`ere,
\newblock \emph{The quantum Gromov--Hausdorff Hypertopology on the
class of pointed Proper Quantum Metric Spaces},
\newblock arXiv:2512.03573, December 2025.

\bibitem[Leimbach \& van~Suijlekom(2024)]{leimbach_vs2024}
M.~Leimbach and W.~D.~van~Suijlekom,
\newblock \emph{Gromov--Hausdorff convergence of spectral truncations
of the torus},
\newblock Adv.~Math. \textbf{439} (2024), Paper No.~109496.

\bibitem[Minguzzi \& Suhr(2024)]{minguzzi_suhr2024}
E.~Minguzzi and S.~Suhr,
\newblock \emph{Bounded Lorentzian metric spaces},
\newblock Lett. Math. Phys. \textbf{114} (2024), Paper No.~73;
\newblock arXiv:2209.14384.

\bibitem[Mondino \& Sämann(2025)]{mondino_samann2025}
A.~Mondino and C.~Sämann,
\newblock \emph{Lorentzian Gromov--Hausdorff convergence
and pre-compactness},
\newblock arXiv:2504.10380, 2025.

\bibitem[Che, Perales \& Sormani(2025)]{che_perales_sormani2025}
M.~Che, R.~Perales, and C.~Sormani,
\newblock \emph{Gromov's compactness theorem for the intrinsic
timed-Hausdorff distance},
\newblock arXiv:2510.13069, October 2025.

\bibitem[Nieuviarts(2025a)]{nieuviarts2025a}
G.~Nieuviarts,
\newblock \emph{Emergence of Lorentz symmetry from an almost-commutative
twisted spectral triple},
\newblock arXiv:2502.18105 (v3, May 2025).

\bibitem[Nieuviarts(2025b)]{nieuviarts2025b_proceedings}
G.~Nieuviarts,
\newblock \emph{Emergence of time from a twisted spectral triple in
almost-commutative geometry},
\newblock arXiv:2512.15450, December 2025 (revised May 2026).

\bibitem[Pier(1984)]{pier1984}
J.-P.~Pier,
\newblock \emph{Amenable Locally Compact Groups},
\newblock Wiley, 1984.

\bibitem[Pisier(2001)]{pisier2001}
G.~Pisier,
\newblock \emph{Similarity Problems and Completely Bounded Maps},
\newblock Lecture Notes in Math. 1618, Springer, 2nd ed., 2001.

\bibitem[Sewell(1982)]{sewell1982}
G.~L.~Sewell,
\newblock \emph{Quantum fields on manifolds:\ PCT and gravitationally
induced thermal states},
\newblock Ann.~Phys. (NY) \textbf{141} (1982), 201--224.

\bibitem[Strohmaier(2006)]{strohmaier2006}
A.~Strohmaier,
\newblock \emph{On noncommutative and pseudo-Riemannian geometry},
\newblock J.~Geom.~Phys. \textbf{56} (2006), 175--195.

\bibitem[Takesaki(1979)]{takesaki1979}
M.~Takesaki,
\newblock \emph{Theory of Operator Algebras I},
\newblock Springer, 1979.

\bibitem[Toyota(2023)]{toyota2023}
M.~Toyota,
\newblock \emph{Quantum Gromov--Hausdorff convergence of spectral
truncations for groups with polynomial growth},
\newblock arXiv:2309.13469, 2023.

\bibitem[Unruh(1976)]{unruh1976}
W.~G.~Unruh,
\newblock \emph{Notes on black-hole evaporation},
\newblock Phys.~Rev. D \textbf{14} (1976), 870--892.

\bibitem[van~den~Dungen(2016)]{vandungen2016}
K.~van~den~Dungen,
\newblock \emph{Krein spectral triples and the fermionic action},
\newblock Math.~Phys.~Anal.~Geom. \textbf{19} (2016), Art.~4, 22pp;
\newblock arXiv:1505.01939.

\bibitem[de~Groot(2026)]{de_groot2026_su11}
J.~de~Groot,
\newblock \emph{Pseudo-Riemannian Spectral Triples for $\mathrm{SU}(1,1)$},
\newblock arXiv:2601.22171, January 2026.

\bibitem[Loutey, internal Paper~24]{paper24}
J.~Loutey,
\newblock \emph{The Bargmann--Segal Lattice: $\pi$-Free Discretization
of the Harmonic Oscillator on $S^5$},
\newblock GeoVac internal preprint (2026), DOI via Zenodo.

\bibitem[Loutey, internal Paper~32]{paper32}
J.~Loutey,
\newblock \emph{The GeoVac Spectral Triple: A Synthesis Paper Locking
the Framework into the Marcolli--van~Suijlekom Gauge-Network Lineage},
\newblock GeoVac internal preprint, papers/synthesis (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~38]{paper38}
J.~Loutey,
\newblock \emph{State-space Gromov--Hausdorff convergence of truncated
Camporesi--Higuchi spectral triples on $S^3$},
\newblock GeoVac internal preprint, papers/standalone (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~39]{paper39}
J.~Loutey,
\newblock \emph{Tensor-product propinquity convergence for
distinct-focal-length truncated Camporesi--Higuchi spectral triples on
$\sthree$},
\newblock GeoVac internal preprint, papers/standalone (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~40]{paper40_unified}
J.~Loutey,
\newblock \emph{State-space Gromov--Hausdorff convergence of spectral
truncations of compact Lie groups with bi-invariant metric},
\newblock GeoVac internal preprint, papers/standalone (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~42]{paper42}
J.~Loutey,
\newblock \emph{Tomita--Takesaki modular structure on truncated
$SU(2)$ spectral triples: four-witness Wick-rotation literal
identification at finite cutoff},
\newblock GeoVac internal preprint, papers/standalone (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~43]{paper43}
J.~Loutey,
\newblock \emph{Lorentzian extension of the four-witness Wick-rotation
theorem on truncated $S^3 \times \mathbb{R}$ spectral triples at finite
cutoff},
\newblock GeoVac internal preprint, papers/standalone (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~44]{paper44}
J.~Loutey,
\newblock \emph{Operator-system extension of the BBB Krein spectral
triple at finite cutoff: propagation number and envelope dependence
on the Camporesi--Higuchi spinor bundle},
\newblock GeoVac internal preprint, papers/standalone (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~45]{paper45}
J.~Loutey,
\newblock \emph{Lorentzian propinquity convergence on truncated
$\SU(2) \times \Uone_{T}$ Krein spectral triples ($\Kplus$-restricted
weak-form)},
\newblock GeoVac internal preprint, papers/group1\_operator\_algebras
(2026), DOI via Zenodo.

\bibitem[Loutey, internal Paper~47]{paper47}
J.~Loutey,
\newblock \emph{Norm-resolvent convergence to the non-compact
Lorentzian Krein spectral triple on $\sthree \times \mathbb{R}_{t}$
and the two-rate hybrid limit},
\newblock GeoVac internal preprint, papers/group1\_operator\_algebras
(2026), at
\texttt{papers/group1\_operator\_algebras/paper\_47\_two\_rate\_hybrid\_convergence.tex}.

\bibitem[Sub-sprint memo L3b-2a]{memo_L3b_2a}
J.~Loutey, internal sprint memo
\emph{Sprint L3b-2a --- Candidate validation + axiom check},
GeoVac internal, 2026-05-22,
\texttt{debug/l3b\_2a\_candidate\_validation\_memo.md}.

\bibitem[Sub-sprint memo L3b-2b]{memo_L3b_2b}
J.~Loutey, internal sprint memo
\emph{Sprint L3b-2b --- Joint Lichnerowicz derivation under $L_{\mathrm{op}}$},
GeoVac internal, 2026-05-22,
\texttt{debug/l3b\_2b\_lichnerowicz\_lop\_memo.md}.

\bibitem[Sub-sprint memo L3b-2c]{memo_L3b_2c}
J.~Loutey, internal sprint memo
\emph{Sprint L3b-2c --- Joint Berezin reconstruction under $L_{\mathrm{op}}$},
GeoVac internal, 2026-05-22,
\texttt{debug/l3b\_2c\_berezin\_lop\_memo.md}.

\bibitem[Sub-sprint memo L3b-2d]{memo_L3b_2d}
J.~Loutey, internal sprint memo
\emph{Sprint L3b-2d --- Strong-form Latr\'emoli\`ere propinquity
assembly under $L_{\mathrm{op}}$},
GeoVac internal, 2026-05-22,
\texttt{debug/l3b\_2d\_propinquity\_assembly\_memo.md}.

\end{thebibliography}

\end{document}
