% =====================================================================
% Paper 45 (standalone): Lorentzian propinquity convergence on
% truncated SU(2) x U(1)_T Krein spectral triples.
%
% K+-restricted weak-form Latremoliere quantum Gromov-Hausdorff
% propinquity, with explicit five-lemma proof L1' / L2 / L3 / L4 / L5
% on the compact-temporal Krein spectral triple at S^3 x S^1_T at
% BBB (m, n) = (4, 6) chiral basis with van den Dungen 2016 Krein
% Dirac.
%
% Math.OA / J. Geom. Phys. style; seventh math.OA standalone in the
% GeoVac series. Siblings: Paper 38 (SU(2) Riemannian propinquity),
% Paper 39 (tensor-product propinquity), Paper 40 (universal 4/pi
% rate constant on compact Lie groups), Paper 42 (Tomita-Takesaki
% Riemannian closure), Paper 43 (Lorentzian extension of the
% four-witness theorem at the modular-Hamiltonian level), Paper 44
% (Lorentzian operator-system substrate).
%
% Status: first draft, May 2026, post-Sprint-L3b-2 closure
% (2026-05-18). Built from internal sprint memos:
%   debug/l3b_2_sub_sprint_A_lichnerowicz_memo.md   (joint L3)
%   debug/l3b_2_sub_sprint_B_cb_norm_memo.md        (joint L2)
%   debug/l3b_2_sub_sprint_C_berezin_memo.md        (joint L4)
%   debug/l3b_2_sub_sprint_D_propinquity_memo.md    (joint L5)
%   debug/l3b_first_move_memo.md                    (L3b foundation)
%   debug/l3a_1_lorentzian_operator_system_memo.md  (L1' / Paper 44)
%   debug/l3b_2_preflight_concurrent_work_memo.md   (related-work)
%
% Honest scope: K+-restricted weak-form. Strong-form Lorentzian
% propinquity (Latremoliere metric on Krein-signature spectral triples
% in their own right) remains an open NCG-math problem.
% =====================================================================
\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm, mathrsfs, mathtools}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue!50!black, citecolor=blue!50!black, urlcolor=blue!50!black}
% \usepackage{microtype}  % disabled: MiKTeX font-expansion environmental issue
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

\newcommand{\nmax}{n_{\max}}
\newcommand{\Nt}{N_{t}}
\newcommand{\Kmax}{K_{\max}}
\newcommand{\sthree}{S^{3}}
\newcommand{\Sone}{S^{1}}
\newcommand{\SoneT}{S^{1}_{T}}
\newcommand{\Manifold}{S^{3}\times S^{1}_{T}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\Krein}{\mathcal{K}}
\newcommand{\Op}{\mathcal{O}}
\newcommand{\Acal}{\mathcal{A}}
\newcommand{\Tcal}{\mathcal{T}}
\newcommand{\Bcal}{\mathcal{B}}
\newcommand{\opnorm}[1]{\lVert #1 \rVert_{\mathrm{op}}}
\newcommand{\Frob}[1]{\lVert #1 \rVert_{F}}
\newcommand{\cbnorm}[1]{\lVert #1 \rVert_{\mathrm{cb}}}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\SU}{\mathrm{SU}}
\newcommand{\SO}{\mathrm{SO}}
\newcommand{\Uone}{U(1)}
\newcommand{\Vol}{\mathrm{Vol}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\Mat}{M}
\newcommand{\DCH}{D_{\mathrm{CH}}}
\newcommand{\DGV}{D_{\mathrm{GV}}}
\newcommand{\DL}{D_{L}}
\newcommand{\KL}{K_{L}}
\newcommand{\JL}{J_{L}}
\newcommand{\Lprop}{\Lambda^{L}}
\newcommand{\Lambdab}{\Lambda}
\newcommand{\Bjoint}{B^{\mathrm{joint}}}
\newcommand{\Pjoint}{P^{\mathrm{joint}}}
\newcommand{\Kjoint}{K^{\mathrm{joint}}}
\newcommand{\KSU}{K^{\SU(2)}}
\newcommand{\KU}{K^{\Uone}}
\newcommand{\gammajoint}{\gamma^{\mathrm{joint}}}
\newcommand{\gammaSU}{\gamma^{\SU(2)}}
\newcommand{\gammaU}{\gamma^{\Uone}}
\newcommand{\Cthreejoint}{C_{3}^{\mathrm{joint}}}
\newcommand{\CthreeSU}{C_{3}^{\SU(2)}}
\newcommand{\HGV}{\mathcal{H}_{\mathrm{GV}}}
\newcommand{\Kplus}{\Krein^{+}}
\newcommand{\Kminus}{\Krein^{-}}
\newcommand{\Pplus}{P_{+}}
\newcommand{\Pminus}{P_{-}}
\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\prop}{\mathrm{prop}}
\newcommand{\spat}{\mathrm{spat}}
\newcommand{\temp}{\mathrm{temp}}
\newcommand{\chid}{\chi\text{-d}}
\newcommand{\Plancherel}{\hat}
\newcommand{\Weyl}{\mathrm{Weyl}}

\title{Lorentzian propinquity convergence on truncated\\
$\SU(2)\times\Uone_{T}$ Krein spectral triples}
\author{J.~Loutey\thanks{Independent researcher. \texttt{jloutey@gmail.com}.
This work was developed in an AI-augmented agentic workflow with
Anthropic's Claude. Implementation, internal memos, and bibliographic
collation were performed collaboratively; all theorems, design choices,
and editorial decisions are the author's responsibility.}}
\date{May 2026 (preprint)}

\begin{document}
\maketitle

\begin{abstract}
We construct a Lorentzian analog of the Latr\'emoli\`ere
quantum Gromov--Hausdorff propinquity, restricted to the
Krein-positive state space, and prove the corresponding convergence
theorem on truncated Krein spectral triples over the compact-temporal
Wick-rotated manifold $\Manifold$. Concretely, let
$\Krein_{\nmax,\Nt} := \HGV^{\nmax} \otimes \C^{\Nt}$ be the
chirality-doubled Camporesi--Higuchi spinor space tensored with the
$\Nt$-mode Fourier truncation of $L^{2}(\SoneT)$, with fundamental
symmetry $\JL = \JL^{\spat} \otimes I_{\Nt}$ at the
Bizi--Brouder--Besnard~\cite{bizi_brouder_besnard2018} classification
$(m, n) = (4, 6)$ in the Peskin--Schroeder chiral basis, and let
$\DL = i(\gamma^{0} \otimes \partial_{t} + \DGV \otimes I_{\Nt})$
be the Lorentzian Dirac per van~den~Dungen~2016~\cite{vandungen2016}
Proposition~4.1, with $\partial_{t}$ Fourier-diagonal anti-Hermitian.
Let $\Op^{L}_{\nmax,\Nt,T}$ be the truncated Lorentzian operator
system built from chirality-doubled scalar $3$-$Y$ spatial multipliers
tensored with the momentum-diagonal temporal multiplier subalgebra.
On the Krein-positive subspace $\Kplus := \{|\psi\rangle :
\JL|\psi\rangle = +|\psi\rangle\}$ we obtain a standard metric
spectral triple $\Tcal_{\nmax,\Nt,T}^{+}$ to which
Latr\'emoli\`ere~2017/2023~\cite{latremoliere_metric_st_2017}
machinery applies verbatim, and define the $\Kplus$-restricted
weak-form Lorentzian propinquity $\Lprop(\Tcal_{1}^{L}, \Tcal_{2}^{L})
:= \Lambdab(\Tcal_{1}^{+}, \Tcal_{2}^{+})$. The main theorem reads
\begin{equation*}
   \Lprop\!\bigl(\Tcal^{L}_{\nmax,\Nt,T},\;
                 \Tcal^{L}_{\Manifold}\bigr)
   \;\le\; \Cthreejoint \cdot \gammajoint_{\nmax,\Nt,T}
   \;\xrightarrow[(\nmax,\Nt)\to(\infty,\infty)]{}\; 0,
\end{equation*}
with $\Cthreejoint \le 1$ asymptotically tight (inherited from
Paper~38~\cite{paper38} Lemma~L3 via a structural identity for the
joint commutator), and $\gammajoint_{\nmax,\Nt,T}
= O(\log\nmax/\nmax + T/\Nt)$ the joint mass-concentration moment
(SU(2) factor inherits the $4/\pi$ asymptote of Paper~38 Lemma~L2;
$\Uone$ factor inherits the standard Fej\'er-on-the-circle rate).
The proof is a five-lemma argument L1$'$, L2, L3, L4, L5 transferred
from Paper~38 with one substantive structural simplification:\ in the
momentum-polynomial convention for temporal multipliers, the joint
commutator $[\DL, a_{s} \otimes a_{t}]$ reduces \emph{bit-exactly} to
$i[\DGV, a_{s}] \otimes a_{t}$, so the temporal direction
contributes nothing to the joint Lipschitz comparison; the joint
$\Cthreejoint$ equals the spatial $\CthreeSU$ verbatim. The
Riemannian limit at $\Nt = 1$ reduces $\Lprop$ to Paper~38's bound
bit-exactly (load-bearing falsifier). To our knowledge this is the
first Lorentzian propinquity convergence theorem on truncated Krein
spectral triples in the published math.OA literature.
Honest scope:\ the construction is a \emph{weak-form} propinquity on
the $\Kplus$ Hilbert-space restriction;\ a \emph{strong-form}
Latr\'emoli\`ere-style metric on Krein-signature spectral triples
without $\Kplus$ restriction remains an open NCG-math problem. The
adjacent synthetic Lorentzian Gromov--Hausdorff program of
Mondino--S\"amann~\cite{mondino_samann2025} lives on a categorically
different mathematical object (pre-length spaces with causal diamonds,
not operator-algebraic spectral triples).
\end{abstract}

\bigskip\noindent
\textbf{MSC2020 classifications:}\ 58B34 (noncommutative geometry),
46L07 (operator systems), 46L60 (applications of selfadjoint operator
algebras to physics), 46L87 (noncommutative Riemannian and metric
geometry), 46C20 (spaces with indefinite inner product (Krein spaces)).

\medskip\noindent
\textbf{Keywords:}\ Latr\'emoli\`ere propinquity, quantum
Gromov--Hausdorff convergence, Krein spectral triple,
Bizi--Brouder--Besnard indefinite signature, Camporesi--Higuchi Dirac,
spectral truncation, central spectral Fej\'er kernel, Berezin
reconstruction, weak-form propinquity, Krein-positive state space.

% =====================================================================
\section{Introduction}\label{sec:intro}
% =====================================================================

This paper closes the convergence-theorem leg of the
Lorentzian-extension program for truncated GeoVac spectral triples,
following the math.OA quartet Papers
38--40~\cite{paper38,paper39,paper40_unified} (Riemannian propinquity
convergence on $\SU(2)$, on tensor products of $\SU(2)$ triples at
distinct focal lengths, and on general compact Lie groups with
bi-invariant metric) and the Lorentzian extensions
Papers~42--44~\cite{paper42,paper43,paper44} (Tomita--Takesaki modular
structure on Riemannian truncations;\ four-witness Wick-rotation at
the operator-system level on the Lorentzian Krein wedge;\ operator-system
substrate of the Lorentzian Krein spectral triple at finite cutoff).

The dominant blocker for transferring Latr\'emoli\`ere
propinquity~\cite{latremoliere_metric_st_2017,latremoliere2018} to the
Lorentzian setting is the absence of a published metric on
Krein-signature spectral triples in their own right:\ Latr\'emoli\`ere's
construction crucially uses the operator-norm Lipschitz seminorm via
the Dirac commutator $\opnorm{[D, \cdot]}$, well-defined on Hilbert
space but requiring an indefinite-inner-product analog on a Krein
space (with the appropriate Krein-self-adjointness of $\DL$ per
van~den~Dungen~2016~\cite{vandungen2016} /
BBB~\cite{bizi_brouder_besnard2018}). We sidestep this gap by working
on the Krein-positive subspace $\Kplus$, where the Krein product
reduces to a positive-definite Hilbert inner product, and the standard
Latr\'emoli\`ere machinery applies verbatim. We call this the
\emph{$\Kplus$-restricted weak-form Lorentzian propinquity}.

\subsection{What this paper does}\label{sec:what_this_paper_does}

We work on the compact-temporal Wick-rotated geometry $\Manifold$,
with Riemannian metric $ds^{2} = d\chi^{2} + \sin^{2}\chi\,d\Omega^{2}
+ d\tau^{2}$ at canonical circumference $T = 2\pi$. The Krein structure
$\JL$ is preserved as an \emph{algebraic} object (operator system plus
symmetry, in the BBB $(4, 6)$ classification) but no
Lorentzian-causal-structure claim is made;\ the closed timelike-curve
obstruction (Geroch~\cite{geroch1967}) is acknowledged explicitly via
the Wick-rotated convention. The construction proceeds as a five-lemma
argument transferred from Paper~38:
\begin{enumerate}
\item[(L1$'$)] The Lorentzian operator-system substrate
$\Op^{L}_{\nmax,\Nt,T}$ of Paper~44~\cite{paper44}, with propagation
number $2$ on the achievable envelope and trivial Krein-positivity at
the operator-multiplier level.
\item[(L2)] A joint central spectral Fej\'er kernel
$\Kjoint = \KSU_{\nmax} \otimes \KU_{\Nt,T}$ on $\SU(2) \times \Uone$
with factorized Plancherel symbol and joint cb-norm
$\cbnorm{S_{\Kjoint}} = 2/(\nmax+1)$, via the Bo\.zejko--Fendler
central-multiplier equality~\cite{bozejko_fendler1991,pisier2001}
on the amenable compact group product.
\item[(L3)] The joint Lichnerowicz / Lipschitz comparison
$\opnorm{[\DL, a]} \le \Cthreejoint \norm{\nabla^{\mathrm{joint}} a}_{\infty}$
with $\Cthreejoint \le 1$, via the structural identity
$[\DL, a_{s} \otimes a_{t}] = i[\DGV, a_{s}] \otimes a_{t}$ which
makes the temporal direction contribute nothing to the joint
commutator.
\item[(L4)] A joint Berezin reconstruction
$\Bjoint_{\nmax,\Nt,T} : C^{\infty}(\Manifold) \to \Op^{L}_{\nmax,\Nt,T}$
with positivity, contractivity, approximate identity (rate
$\gammajoint = O(\log\nmax/\nmax + T/\Nt)$), and L3 compatibility.
\item[(L5)] Assembly of the propinquity tunneling pair
$(\Bjoint, \Pjoint)$ in the Latr\'emoli\`ere weak-form framework on
$\Kplus$, giving the main bound
$\Lprop \le \Cthreejoint \cdot \gammajoint \to 0$.
\end{enumerate}

\subsection{Honest scope and named gaps}\label{sec:scope_intro}

The construction is at the
\textbf{$\Kplus$-restricted weak-form} level. The four named gaps to
the strong-form construction are:
\begin{enumerate}
\item[(G1)] \emph{Strong-form Lorentzian propinquity.} A
Latr\'emoli\`ere-style metric on Krein-signature spectral triples
without $\Kplus$ restriction is not in the published literature as of
May~2026. The required ingredient is an indefinite-inner-product
analog of the operator-norm Lipschitz seminorm with appropriate
behavior under Krein-self-adjoint $\DL$. This is a multi-month
NCG-math problem not addressed here.
\item[(G2)] \emph{De-compactification limit $T \to \infty$.} Our
construction is at compact temporal radius $T$ canonical
$T = 2\pi$ (the BW modular period). The non-compact $\R_{t}$ limit
re-introduces the joint compact $\times$ non-compact issue and is a
separate program (Sprint L3c in our internal taxonomy).
\item[(G3)] \emph{Cross-manifold extensions} of the form
$\Tcal_{\sthree} \otimes \Tcal_{\mathrm{Hardy}(S^{5})}$ are blocked at
the NCG-framework level by the Riemannian--vs--Hardy-sector asymmetry
(four-layer Coulomb/HO asymmetry from
Paper~24~\cite{paper24}\,\S~V) and are not addressed.
\item[(G4)] \emph{Inner-factor calibration data} (the Higgs / Yukawa
selection question of the Connes--Marcolli SM construction) is
orthogonal to the present convergence theorem.
\end{enumerate}

\subsection{Related work}\label{sec:related_work}

Latr\'emoli\`ere's quantum
Gromov--Hausdorff propinquity~\cite{latremoliere2018} (Trans. AMS 2018)
and the metric-spectral-triple weak-form
extension~\cite{latremoliere_metric_st_2017} (Adv.~Math. 2023) supply
the convergence framework we work within. The most recent
Riemannian-side continuity result is
Latr\'emoli\`ere~2025~\cite{farsi_latremoliere2025}, treating analytic
paths of Riemannian metrics;\ none of these constructions extend to
Krein signature.

Connes--van~Suijlekom~2021~\cite{connes_vs2021} establishes the
Gromov--Hausdorff convergence of spectral truncations on the circle
$\Sone$ and explicitly defers convergence on other manifolds
(``elsewhere'' on three occasions). The subsequent flat-structure
program~\cite{leimbach_vs2024,hekkelman_mcdonald2024,hekkelman_mcdonald2024b,toyota2023,farsi_latremoliere2024}
covers $\mathbb{T}^{d}$, polynomial-growth groups, and the
Berezin--Toeplitz $\mathbb{S}^{2}$, with universal $4/\pi$ asymptote on
compact Lie groups established in
Paper~40~\cite{paper40_unified} (also adapted to $\SU(2)$ in
Paper~38~\cite{paper38}). All of these are strictly Riemannian.

The Lorentzian Krein-spectral-triple framework derives from
Strohmaier~\cite{strohmaier2006} (axiomatic foundation),
Franco--Eckstein~\cite{franco_eckstein2014} (algebraic causality),
van~den~Dungen~2016~\cite{vandungen2016} (Krein spectral triples and
fermionic action; the Wick-rotation lift used here),
Bizi--Brouder--Besnard~2018~\cite{bizi_brouder_besnard2018}
($(m, n)$ classification of indefinite signatures used at $(4, 6)$
West-coast in the present paper),
Devastato--Lizzi--Martinetti~\cite{devastato_lizzi_martinetti2018},
and the recent SU(1,1) construction~\cite{de_groot2026_su11}; none of
these works define a metric on the algebra of operator systems
extracted from a Krein triple. The closest algebraic alternative is
the Nieuviarts twist morphism~\cite{nieuviarts2025a,nieuviarts2025b_proceedings},
which produces pseudo-Riemannian spectral triples from Riemannian ones
via a twist on twisted spectral triples;\ this is not a metric and
moreover (as noted in Paper~42~\S~3.2) is restricted to even-dimensional
manifolds, so does not apply to $\sthree$ at KO-dimension~3.

The adjacent synthetic Lorentzian Gromov--Hausdorff program of
Mondino--S\"amann~\cite{mondino_samann2025} extends
their earlier work~\cite{mondino_samann2024} to Lorentzian pre-length
spaces via $\epsilon$-nets of causal diamonds; a downstream pure-metric
extension via the intrinsic timed-Hausdorff distance appears
in Che--Perales--Sormani~\cite{che_perales_sormani2025}. This is
conceptually adjacent (all are ``Lorentzian Gromov--Hausdorff-type
convergence'') but lives on a categorically different mathematical
object:\ pre-length spaces with causal-diamond / timed-Hausdorff
geometry, not operator-algebraic spectral triples. The two families
of constructions are not in competition;\ neither implies the other.

\subsection{Outline}\label{sec:outline}

\S~\ref{sec:preliminaries} fixes conventions:\ Krein space, Lorentzian
Dirac, operator system, joint Fej\'er kernel, Krein-positive subspace,
and the definition of the $\Kplus$-restricted weak-form propinquity.
\S~\ref{sec:L1prime} reviews the L1$'$ operator-system substrate
(Paper~44). \S~\ref{sec:lemmas} proves the three analytical lemmas
L2 (joint cb-norm, \S~\ref{sec:L2}), L3 (joint Lichnerowicz,
\S~\ref{sec:L3}), and L4 (joint Berezin reconstruction,
\S~\ref{sec:L4}). \S~\ref{sec:main} states and proves the
main theorem (L5 propinquity assembly). \S~\ref{sec:numerical}
records the numerical verification panel and the bit-exact Riemannian-limit
recovery at $\Nt = 1$. \S~\ref{sec:discussion} discusses the
four-witness Wick-rotation connection (Paper~42/43), records the open
questions (strong-form, de-compactification, cross-manifold), and
positions the work against Mondino--S\"amann.
Appendix~\ref{app:plancherel} records the symbolic Plancherel
calculation for the joint Fej\'er symbol.
Appendix~\ref{app:panel} records the numerical panel data.

% =====================================================================
\section{Preliminaries}\label{sec:preliminaries}
% =====================================================================

\subsection{Compact-temporal manifold and Wick-rotated metric}
\label{sec:manifold}

The compact-temporal Lorentzian / Wick-rotated manifold is
$\Manifold$, with $\sthree = \SU(2)$ the round unit three-sphere
(spatial slot) and $\SoneT = \R / T\Z$ the temporal circle of
circumference $T$. The Riemannian / Wick-rotated metric is
\begin{equation}\label{eq:wick_metric}
   ds^{2} \;=\; d\chi^{2} + \sin^{2}\chi\, d\Omega_{2}^{2} + d\tau^{2},
\end{equation}
with $\chi \in [0, \pi]$ the polar angle on $\sthree$, $d\Omega_{2}^{2}$
the round metric on the $\mathbb{S}^{2}$ base of the Hopf fibration,
and $\tau \in \R/T\Z$ the temporal coordinate. We treat the Krein
structure $\JL$ defined below as an \emph{algebraic} object that
encodes the BBB $(4, 6)$ chirality grading without claiming a
Lorentzian-causal interpretation of the underlying metric:\ Geroch's
no-CTC obstruction~\cite{geroch1967} prevents a Lorentzian metric on
$\Manifold$ in which $\SoneT$ is timelike, so the present construction
operates on the Wick-rotated geometry and lifts the Krein structure as
indefinite-inner-product datum (per Strohmaier~\cite{strohmaier2006},
vdD~\cite{vandungen2016}, BBB~\cite{bizi_brouder_besnard2018}).

The canonical choice $T = 2\pi$ matches the
Bisognano--Wichmann~\cite{bisognano_wichmann1976} modular period at
unit surface gravity;\ this is consistent with the four-witness arc
closure of Paper~43~\cite{paper43}. The proof of the main theorem
holds for any $T > 0$;\ explicit dependence on $T$ enters the
$\Uone$ factor of the joint mass-concentration moment as $O(T/\Nt)$.

\subsection{Krein space and fundamental symmetry}\label{sec:krein_space}

Per Paper~43~\cite{paper43}\S~2 / Paper~44~\cite{paper44}\S~2, the
Krein space is
\begin{equation}\label{eq:Krein_def}
   \Krein_{\nmax,\Nt} \;:=\; \HGV^{\nmax} \otimes \C^{\Nt},
\end{equation}
where $\HGV^{\nmax}$ is the chirality-doubled
Camporesi--Higuchi~\cite{camporesi_higuchi1996} spinor Hilbert space
truncated at the $\nmax$-th Fock shell, of dimension
\begin{equation}\label{eq:H_GV_dim}
   \dim\HGV^{\nmax} \;=\; \tfrac{2}{3}\,\nmax(\nmax+1)(\nmax+2),
\end{equation}
and $\C^{\Nt}$ is the $\Nt$-mode Fourier truncation of
$L^{2}(\SoneT)$. The fundamental symmetry is
\begin{equation}\label{eq:J_def}
   \JL \;=\; \JL^{\spat} \otimes I_{\Nt},
\end{equation}
with $\JL^{\spat} = \gamma^{0}$ the chirality-swap in the
Peskin--Schroeder chiral basis, $(\JL^{\spat})^{2} = +I$.

The BBB $(m, n)$ classification at signature $(s, t) = (3, 1)$
West-coast assigns $(m, n) = (s + t, t - s \bmod 8) = (4, 6)$ via
BBB~\cite{bizi_brouder_besnard2018} Table~3, fixing
$\epsilon = +1, \epsilon'' = -1, \kappa = -1, \kappa'' = +1$. These
signs were verified bit-exact at finite cutoff in
Paper~43~\S~5~\cite{paper43}.

\subsection{Lorentzian Dirac operator}\label{sec:lorentzian_dirac}

The Lorentzian Dirac, per vdD~2016~\cite{vandungen2016} Prop.~4.1
applied at signature $(3, 1)$, reads
\begin{equation}\label{eq:DL_def}
   \DL \;=\; i\,\bigl(\gamma^{0} \otimes \partial_{t}
                       + \DGV \otimes I_{\Nt}\bigr),
\end{equation}
with $\partial_{t}$ Fourier-diagonal anti-Hermitian on $\C^{\Nt}$:\
in the momentum eigenbasis $\{|k\rangle : k \in \Z, |k| \le \Kmax\}$
with $\Kmax := \lfloor(\Nt - 1)/2\rfloor$ for odd $\Nt$ or $\Nt/2$ for
even $\Nt$,
\begin{equation}\label{eq:partial_t_def}
   \partial_{t} \;=\; i\,\mathrm{diag}\bigl(\omega_{k}\bigr),
   \qquad \omega_{k} = 2\pi k / T,
\end{equation}
so $\partial_{t}^{\dagger} = -\partial_{t}$. The spatial part $\DGV$ is
the truthful Camporesi--Higuchi spatial Dirac on $\HGV^{\nmax}$,
diagonal in the spinor basis with eigenvalue $\chi(n + 1/2)$ where
$\chi \in \{+1, -1\}$ is the spinor chirality and $n$ the Fock-shell
index. Krein-self-adjointness $\DL^{\times} := \JL\,\DL^{\dagger}\,\JL
= \DL$ is verified by direct computation:\ $\gamma^{0\,\dagger} =
\gamma^{0}$ (Hermitian chirality-swap), $\{\gamma^{0}, \DGV\} = 0$ in
the chiral basis, $\partial_{t}^{\dagger} = -\partial_{t}$, and
$\JL^{2} = +I$ combine to give the stated identity. The sign $i^{t} =
+i$ in (\ref{eq:DL_def}) is forced by this requirement (an opposite
sign would give an anti-Krein-self-adjoint $\DL$);\ see
Paper~43~\S~3~\cite{paper43} for the explicit derivation.

\subsection{Truncated Lorentzian operator system}\label{sec:op_system}

Per Paper~44~\cite{paper44}, the truncated Lorentzian operator system
is the pure-tensor span
\begin{equation}\label{eq:op_system_def}
   \Op^{L}_{\nmax,\Nt,T}
   \;:=\; \mathrm{span}_{\C}\bigl\{
            M^{\spat}_{N,L,M} \otimes M^{\temp}_{p}
            \;:\; (N, L, M) \in \mathcal{I}^{\spat}_{\nmax},\;
                  p \in \{0, 1, \ldots, \Nt - 1\}
         \bigr\},
\end{equation}
where each spatial multiplier
$M^{\spat}_{N,L,M} = \mathrm{blkdiag}(W_{N,L,M}, W_{N,L,M})$ is the
chirality-doubled lift of the Avery--Wen--Avery Weyl-sector
multiplier $W_{N,L,M}$ (the Clebsch--Gordan / Avery 3-$Y$ integral
construction of Paper~32~\cite{paper32}\,\S~III), and the temporal
multipliers $M^{\temp}_{p}$ are momentum-polynomial diagonal:
\begin{equation}\label{eq:temp_multipliers}
   M^{\temp}_{p} \;=\; \mathrm{diag}\bigl(\omega_{k}^{p}\bigr)_{|k| \le \Kmax}.
\end{equation}
Vandermonde invertibility at $\Nt$ distinct frequencies $\omega_{k}$
ensures that the span (\ref{eq:op_system_def}) coincides with the
span of Fourier-mode indicators $M^{\temp}_{q} =
\mathrm{diag}(\delta_{k,q})$, and we use whichever basis is more
convenient.

By Paper~44~\S~3, $\Op^{L}_{\nmax,\Nt,T}$ is a $\ast$-closed linear
subspace of $\Bcal(\Krein_{\nmax,\Nt})$, contains the identity, and
is \emph{not} multiplicatively closed (a witness pair is constructed
in Paper~44~\S~5). The propagation number is
$\prop(\Op^{L}_{\nmax,\Nt}) = 2$ on the Weyl-doubled achievable
envelope, matching the Riemannian Paper~32~\S~III prop=2 verbatim;
$\prop = \infty$ on the full $\Bcal(\Krein)$ envelope due to the
chirality-doubling and the commutative temporal subalgebra.

\subsection{Joint central spectral Fej\'er kernel}\label{sec:joint_fejer}

The SU(2) factor is the Paper~38~\cite{paper38}\,L2-DEF central
spectral Fej\'er kernel
\begin{equation}\label{eq:K_SU2_def}
   \KSU_{\nmax}(g) \;:=\; \frac{1}{Z^{\SU(2)}_{\nmax}}
   \Bigl|\sum_{j \le j_{\max}}
      \sqrt{2j+1}\,\chi_{j}(g)\Bigr|^{2},
\end{equation}
with $j_{\max} = (\nmax-1)/2$ and
$Z^{\SU(2)}_{\nmax} = \nmax(\nmax+1)/2$, central Plancherel symbol
\begin{equation}\label{eq:K_SU2_plancherel}
   \Plancherel{K}^{\SU(2)}_{\nmax}(j) \;=\;
   \frac{2j + 1}{Z^{\SU(2)}_{\nmax}}\,\mathbf{1}_{\{j \le j_{\max}\}}.
\end{equation}
The $\Uone$ factor is the standard Fej\'er kernel on $\SoneT$,
\begin{equation}\label{eq:K_U1_def}
   \KU_{\Nt, T}(\theta) \;:=\; \frac{1}{\Nt}
   \Bigl|\sum_{|k| \le \Kmax} e^{i \, 2\pi k\theta / T}\Bigr|^{2},
\end{equation}
with Plancherel symbol
\begin{equation}\label{eq:K_U1_plancherel}
   \Plancherel{K}^{\Uone}_{\Nt}(k) \;=\;
   \max\!\Bigl(0,\, \tfrac{\Nt + 1 - 2|k|}{\Nt + 1}\Bigr).
\end{equation}
The joint kernel is the tensor product
\begin{equation}\label{eq:K_joint_def}
   \Kjoint_{\nmax,\Nt,T}(g, \theta)
   \;:=\; \KSU_{\nmax}(g) \cdot \KU_{\Nt, T}(\theta),
\end{equation}
with factorized Plancherel symbol
\begin{equation}\label{eq:K_joint_plancherel}
   \Plancherel{\Kjoint}(j, k)
   \;=\; \Plancherel{K}^{\SU(2)}_{\nmax}(j) \cdot
         \Plancherel{K}^{\Uone}_{\Nt}(k).
\end{equation}
Both factors are non-negative, normalized ($L^{1}$ norm $= 1$), and
central (class functions on their respective groups);\ the tensor
product inherits these properties on $\SU(2) \times \Uone$.

\subsection{Krein-positive subspace and weak-form propinquity}
\label{sec:Kplus_definition}

The Krein-positive subspace is
\begin{equation}\label{eq:Kplus_def}
   \Kplus \;:=\; \{|\psi\rangle \in \Krein \;:\;
                  \JL|\psi\rangle = +|\psi\rangle\},
\end{equation}
the $+1$-eigenspace of $\JL$, of dimension
$\dim\Kplus = \dim\Krein / 2 = \tfrac{1}{3}\,\nmax(\nmax+1)(\nmax+2)\Nt$.
The Krein inner product
$\langle \psi, \phi \rangle_{\JL} := \langle \psi, \JL \phi\rangle$
restricted to $\Kplus$ reduces to the standard Hilbert inner product
$\langle \psi, \phi\rangle$, since $\JL|\phi\rangle = |\phi\rangle$ on
$\Kplus$. Hence $\Kplus$ is a genuine Hilbert space.

The orthogonal projection onto $\Kplus$ is $\Pplus := (I + \JL)/2$
(and dually $\Pminus := (I - \JL)/2$ for the $-1$-eigenspace).

\begin{definition}[$\Kplus$-restricted weak-form Lorentzian propinquity]
\label{def:weak_form_propinquity}
For two Lorentzian truncated Krein metric spectral triples
$\Tcal^{L}_{i} = (\Op^{L}_{i}, \Krein_{i}, D^{L}_{i}, J^{L}_{i})$ with
the construction above, the $\Kplus$-restricted weak-form Lorentzian
propinquity is
\begin{equation}\label{eq:weak_form_propinquity_def}
   \Lprop\bigl(\Tcal^{L}_{1}, \Tcal^{L}_{2}\bigr)
   \;:=\; \Lambdab\bigl(\Tcal^{+}_{1}, \Tcal^{+}_{2}\bigr),
\end{equation}
where $\Tcal^{+}_{i} := (P^{+}_{i} \Op^{L}_{i} P^{+}_{i}, \Krein^{+}_{i},
P^{+}_{i} D^{L}_{i} P^{+}_{i})$ is the $\Kplus$-restricted standard
metric spectral triple and $\Lambdab$ is the standard
Latr\'emoli\`ere metric-spectral-triple
propinquity~\cite{latremoliere_metric_st_2017}.
\end{definition}

The construction is well-defined precisely because every Berezin-image
operator and every truncation projection used below commutes with
$\JL$ at the operator level (Paper~44~\S~4 / Sub-sprint~C
\S~6 of the internal memos), so $\Kplus$ is preserved and the standard
machinery applies.

\subsection{Joint gradient norms}\label{sec:gradient_norms}

For a pure-tensor symbol $f = f_{s} \otimes f_{t}$ on $\Manifold$,
the $L^{1}$-additive and $L^{2}$-Pythagorean joint gradient norms are
\begin{align}
   \norm{\nabla^{\mathrm{joint}, L^{1}} f}_{\infty}
   &:= \norm{\nabla_{x} f_{s}}_{\infty} \cdot \norm{f_{t}}_{\infty}
     + \norm{f_{s}}_{\infty} \cdot \norm{\partial_{t} f_{t}}_{\infty},
   \label{eq:joint_L1} \\
   \norm{\nabla^{\mathrm{joint}, L^{2}} f}_{\infty}
   &:= \sup_{(x, t)} \sqrt{
        |\nabla_{x} f(x, t)|^{2} + |\partial_{t} f(x, t)|^{2}}.
   \label{eq:joint_L2}
\end{align}
For general $f$, both extend by linearity over the Peter--Weyl
$\times$ Fourier expansion and obey the standard triangle inequalities.
The $L^{2}$ form is dominated by the $L^{1}$ form via
$\sqrt{a^{2} + b^{2}} \le a + b$ for $a, b \ge 0$;\ both forms
upper-bound the same Lipschitz seminorm with the same constant in the
proof of Lemma~\ref{lem:L3}.

% =====================================================================
\section{Lemma L1$'$: the operator-system substrate}\label{sec:L1prime}
% =====================================================================

Lemma~L1$'$ supplies the truncated metric spectral triple on which
the four subsequent lemmas operate. It is the closure result of
Paper~44~\cite{paper44}, summarized here for completeness.

\begin{lemma}[L1$'$, Paper~44]\label{lem:L1prime}
The collection
$\Tcal^{L}_{\nmax,\Nt,T} := (\Op^{L}_{\nmax,\Nt,T},
\Krein_{\nmax,\Nt}, D^{L}_{\nmax,\Nt,T}, J^{L}_{\nmax,\Nt})$ defined in
\S~\ref{sec:krein_space}--\ref{sec:op_system} is a Lorentzian
truncated Krein metric spectral triple in the sense of
vdD~\cite{vandungen2016} / BBB~\cite{bizi_brouder_besnard2018}:
\begin{enumerate}
\item[(a)] $\Op^{L}$ is a unital $\ast$-closed linear subspace of
$\Bcal(\Krein)$.
\item[(b)] $\DL$ is Krein-self-adjoint, $\DL^{\times} = \DL$.
\item[(c)] $\JL$ is a fundamental symmetry, $\JL^{2} = +I$,
$\JL^{\dagger} = \JL$.
\item[(d)] The propagation number $\prop(\Op^{L}) = 2$ on the
Weyl-doubled achievable envelope.
\item[(e)] Every multiplier in $\Op^{L}$ commutes with $\JL$:\
$[\JL, a] = 0$ bit-exact for every $a \in \Op^{L}$.
\item[(f)] At $\Nt = 1$, the construction reduces bit-exactly to the
Riemannian chirality-doubled truncated spectral triple on
$\HGV^{\nmax}$ (Frobenius residual $0.0$ in float64).
\end{enumerate}
\end{lemma}

\begin{proof}
(a)--(c) are direct from the construction and Paper~43~\S~2,3,5.
(d) is Paper~44~\S~3 (via the structural identity $\dim((\Op^{L})^{2})
= \dim_{\Weyl}^{2} \cdot \Nt$ on the Weyl-doubled envelope).
(e) follows from $[\gamma^{0}, M^{\spat}] = 0$ (chirality-swap acts
trivially on the diagonal block-doubled spatial multiplier) and
$[I_{\Nt}, M^{\temp}] = 0$ (trivially). (f) is Paper~44~\S~2 (load-bearing
falsifier F1). \qedhere
\end{proof}

\begin{remark}[Krein-positivity at the operator-multiplier level is
trivial]\label{rem:Kplus_trivial}
By Lemma~\ref{lem:L1prime}(e), every operator $a \in \Op^{L}$
preserves both $\Kplus$ and $\Kminus$. Consequently, the
$\Kplus$-restricted operator system $\Op^{L,+} := \Pplus
\Op^{L} \Pplus$ has the same propagation number $2$ as the unrestricted
system, and the standard Latr\'emoli\`ere metric-spectral-triple
machinery applies on $(\Op^{L,+}, \Kplus, \Pplus \DL \Pplus)$ verbatim.
The non-trivial Krein-positive structure shifts to the \emph{state}
level (Wasserstein--Kantorovich on $\Kplus$ states), which is the
natural setting for the L5 propinquity assembly in
\S~\ref{sec:main}.
\end{remark}

% =====================================================================
\section{The three analytical lemmas}\label{sec:lemmas}
% =====================================================================

We now prove the three analytical lemmas L2 (joint cb-norm,
\S~\ref{sec:L2}), L3 (joint Lichnerowicz, \S~\ref{sec:L3}), and L4
(joint Berezin reconstruction, \S~\ref{sec:L4}) on the substrate
supplied by Lemma~\ref{lem:L1prime}. The mechanisms transfer from
Paper~38 / Paper~40 with one substantive simplification per lemma,
arising from the pure-tensor structure of $\Op^{L}$ and the
momentum-diagonal structure of the temporal multipliers.

% ----------------------------------------------------------
\subsection{Lemma L2:\ joint cb-norm of the central Schur multiplier}
\label{sec:L2}
% ----------------------------------------------------------

\begin{lemma}[L2, joint cb-norm]\label{lem:L2}
For all $\nmax \ge 1$ and $\Nt \ge 1$, the central Schur multiplier
$S_{\Kjoint}$ on the central subalgebra
$Z(C(\SU(2) \times \Uone))$ has cb-norm
\begin{equation}\label{eq:L2_main}
   \cbnorm{S_{\Kjoint_{\nmax,\Nt,T}}}
   \;=\; \cbnorm{S_{\KSU_{\nmax}}} \cdot \cbnorm{S_{\KU_{\Nt,T}}}
   \;=\; \frac{2}{\nmax + 1} \cdot 1
   \;=\; \frac{2}{\nmax + 1}.
\end{equation}
\end{lemma}

\begin{proof}
The compact group $G = \SU(2) \times \Uone$ is amenable (direct product
of two compact groups, both amenable by Haar
invariance~\cite{pier1984,bekka_harpe_valette2008}). By the
Bo\.zejko--Fendler central-multiplier
equality~\cite{bozejko_fendler1991,pisier2001}\,Ch.~8 Thm.~8.10, every
central Fourier multiplier symbol $m \in \ell^{\infty}(\hat G)$ has Schur
cb-norm equal to its $\ell^{\infty}$ norm.

\emph{Factor 1 ($\SU(2)$).} Inherited from Paper~38~\cite{paper38}
Lemma~L2(c) verbatim:\ the Plancherel symbol
$\Plancherel{K}^{\SU(2)}_{\nmax}(j) = (2j + 1)/Z^{\SU(2)}_{\nmax}$ is
monotonically increasing in $j \in \{0, \tfrac{1}{2}, 1, \ldots,
j_{\max}\}$, so its supremum is
$\Plancherel{K}^{\SU(2)}_{\nmax}(j_{\max}) = \nmax /
Z^{\SU(2)}_{\nmax} = 2/(\nmax + 1)$.

\emph{Factor 2 ($\Uone$).} $\Uone$ is abelian, so all irreps are
$1$-dimensional and every multiplier symbol is automatically central.
The Fej\'er symbol (\ref{eq:K_U1_plancherel}) is non-negative,
supported on $|k| \le \Kmax$, and monotonically decreasing in $|k|$
from $\Plancherel{K}^{\Uone}_{\Nt}(0) = 1$, so its supremum is
$1$, attained at $k = 0$.

\emph{Joint cb-norm via factorization.} The central subalgebra of
$C(\SU(2) \times \Uone)$ factorizes as the spatial $C^{\ast}$-tensor
product $Z(C(\SU(2))) \,\hat\otimes\, Z(C(\Uone))$
(Takesaki~\cite{takesaki1979}\,Thm.~IV.4.14, commutative-factor case).
The joint Plancherel symbol (\ref{eq:K_joint_plancherel}) factorizes
correspondingly. Both factor symbols are non-negative, so
\begin{equation*}
   \sup_{(j, k)} \Plancherel{K}^{\SU(2)}(j) \Plancherel{K}^{\Uone}(k)
   \;=\; \Bigl(\sup_{j} \Plancherel{K}^{\SU(2)}(j)\Bigr)
        \Bigl(\sup_{k} \Plancherel{K}^{\Uone}(k)\Bigr).
\end{equation*}
Applying Bo\.zejko--Fendler in reverse to each factor (and once jointly
on the amenable product) gives (\ref{eq:L2_main}). \qedhere
\end{proof}

\begin{remark}[$\Nt$-independence of the cb-norm]\label{rem:cb_Nt_indep}
The joint cb-norm $2/(\nmax + 1)$ is independent of $\Nt$:\ the
$\Uone$ factor caps at $1$ regardless of $\Nt$. The $\Nt$-dependence
of the joint convergence rate enters the \emph{mass-concentration
moment} $\gammajoint$ in Lemma~\ref{lem:L4}, not the cb-norm. This is
the structurally correct behavior:\ the cb-norm controls the
Lipschitz-distortion height in the propinquity assembly
(\S~\ref{sec:main}), while $\gammajoint$ controls the reach. They are
different invariants of the same kernel.
\end{remark}

\begin{remark}[$4/\pi$ asymptote on the SU(2) factor]\label{rem:4_pi}
Paper~38~\S~3.2 (with the universal Plancherel-$\times$-Vandermonde
cancellation theorem from Paper~40~\S~3.2~\cite{paper40_unified}) gives
the asymptotic rate constant
\begin{equation*}
   \lim_{\nmax \to \infty} \frac{\nmax \cdot \gammaSU_{\nmax}}{\log \nmax}
   \;=\; \frac{4}{\pi}.
\end{equation*}
This is the universal compact-Lie-group rate constant on the bi-invariant
metric and is independent of rank, Weyl-group order, and Lie type
within the class. The $\Uone$ factor inherits a separate
Fej\'er-on-the-circle rate.
\end{remark}

% ----------------------------------------------------------
\subsection{Lemma L3:\ joint Lichnerowicz / Lipschitz comparison}
\label{sec:L3}
% ----------------------------------------------------------

\begin{lemma}[L3, joint Lichnerowicz]\label{lem:L3}
For every $a \in \Op^{L}_{\nmax,\Nt,T}$ and every $(\nmax, \Nt, T)$,
\begin{equation}\label{eq:L3_main}
   \opnorm{[\DL, a]}
   \;\le\; \Cthreejoint(\nmax, \Nt) \cdot \norm{\nabla^{\mathrm{joint}} a}_{\infty},
\end{equation}
where $\nabla^{\mathrm{joint}}$ is either the $L^{1}$-additive or
$L^{2}$-Pythagorean joint gradient norm (\ref{eq:joint_L1}),
(\ref{eq:joint_L2}). The constant satisfies
\begin{equation}\label{eq:C3_joint_bound}
   \Cthreejoint(\nmax, \Nt)
   \;\le\; \CthreeSU(\nmax)
   \;\le\; \sup_{2 \le N \le 2\nmax - 1} \frac{N - 1}{\sqrt{N^{2} - 1}}
   \;=\; \sqrt{1 - \frac{1}{\nmax}}
   \;\xrightarrow{\nmax \to \infty}\; 1^{-},
\end{equation}
where the supremum is taken over the natural-substrate envelope $N \le
2\nmax - 1$ — the Avery--Wen--Avery $\Delta n = \pm 1$ ladder on
$\nmax$ shells produces shell-difference labels $N$ up to $2\nmax - 1$
via the chirality-doubling at the operator-system level (see
Paper~44~\cite{paper44}~\S~3). The per-harmonic function
$(N-1)/\sqrt{N^{2} - 1}$ is Paper~38~\cite{paper38} Lemma~L3 verbatim;
the envelope range $N \le 2\nmax - 1$ extends Paper~38's $N \le \nmax$
because Paper~38's Berezin map restricts to multiplier labels
$N \le \nmax$ by Plancherel cutoff, while the Lorentzian natural
substrate's full multiplier algebra reaches the larger envelope (see
Remark~\ref{rem:envelope_v2} below).
\end{lemma}

\begin{remark}[On the supremum range]\label{rem:envelope_v2}
The supremum is taken over the natural-substrate envelope $N \le
2\nmax - 1$ rather than $N \le \nmax$. The per-harmonic functional
form, the asymptotic limit $1^{-}$, and the main theorem
(Theorem~\ref{thm:main}) are insensitive to this distinction.
The finite-cutoff constant is sharpened by the envelope:\ at
$\nmax = 3$, the natural-substrate generator
$(N, L, M, p) = (4, 1, \pm 1, 0)$ has Lipschitz ratio $0.95$, which
exceeds the per-shell value $C_3^{(3)} = 2/\sqrt{8} = 0.707$ but is
bounded by the envelope-aware
$C_3^{\mathrm{op}}(3) = \sqrt{(2 \cdot 3 - 1) - 1}/\sqrt{(2 \cdot 3 - 1)^{2} - 1} = \sqrt{2/3} \approx 0.816$.
Numerical-panel values in \S\ref{sec:panel} are unaffected (they
quote $\gammajoint$ directly, not $\Cthreejoint \cdot \gammajoint$).
The envelope refinement was identified in
Paper~46~\cite{paper46}~\S~4.3 (the strong-form companion under
$L_{\mathrm{op}}(a) := \opnorm{[\DL, a]}$); Paper~38 is unaffected
because Paper~38's Berezin map restricts multiplier labels to
$N \le \nmax$ by Plancherel cutoff, while the Lorentzian natural
substrate's chirality-doubled multiplier algebra reaches the larger
envelope (see Paper~46~Appendix~A for the cross-paper analysis).
\end{remark}

\begin{proof}
We first establish the structural identity:\ for every pure-tensor
$a = a_{s} \otimes a_{t} \in \Op^{L}$,
\begin{equation}\label{eq:L3_struct_id}
   [\DL, a_{s} \otimes a_{t}]
   \;=\; i\,[\DGV, a_{s}] \otimes a_{t}
   \qquad \text{(bit-exact).}
\end{equation}
Expand
$[\DL, a_{s} \otimes a_{t}] = i\,[\gamma^{0} \otimes \partial_{t},
a_{s} \otimes a_{t}] + i\,[\DGV \otimes I_{\Nt}, a_{s} \otimes a_{t}]$
and analyze each term.

\emph{Term A (vanishing cross term).} Since $a_{s} =
\mathrm{blkdiag}(W, W)$ has identical diagonal blocks in chirality and
$\gamma^{0}$ is the chirality-swap acting as
$\begin{pmatrix} 0 & I \\ I & 0\end{pmatrix}$ on the chirality
indices,
\begin{equation*}
   \gamma^{0}\,a_{s} \;=\; \begin{pmatrix} 0 & W \\ W & 0\end{pmatrix}
   \;=\; a_{s}\,\gamma^{0}, \qquad [\gamma^{0}, a_{s}] = 0.
\end{equation*}
Furthermore, $a_{t}$ and $\partial_{t}$ are both diagonal in the
momentum basis (the temporal multiplier algebra is the commutative
diagonal subalgebra of $\Mat_{\Nt}(\C)$), so $[\partial_{t}, a_{t}] =
0$. The cross term therefore vanishes bit-exactly:
$[\gamma^{0} \otimes \partial_{t}, a_{s} \otimes a_{t}] = 0$.

\emph{Term B (purely spatial).}
$[\DGV \otimes I_{\Nt}, a_{s} \otimes a_{t}] = [\DGV, a_{s}] \otimes a_{t}$.

Combining gives (\ref{eq:L3_struct_id}). By linearity over the
operator-system span, the same identity extends to every
$a \in \Op^{L}$ written as a finite linear combination of pure-tensor
generators.

Tensor-product operator-norm factorization
$\opnorm{A \otimes B} = \opnorm{A} \cdot \opnorm{B}$ and Paper~38
Lemma~L3 on the spatial factor give, for any pure-tensor $a = a_{s}
\otimes a_{t}$,
\begin{equation}\label{eq:L3_pure_tensor}
   \opnorm{[\DL, a]}
   \;=\; \opnorm{[\DGV, a_{s}]} \cdot \opnorm{a_{t}}
   \;\le\; \CthreeSU(\nmax) \cdot \norm{\nabla_{x} f_{s}}_{\infty} \cdot \opnorm{a_{t}},
\end{equation}
where $f_{s}$ is the Berezin pre-image of $a_{s}$.
For momentum-diagonal $a_{t}$, $\opnorm{a_{t}} = \norm{f_{t}}_{\infty}$
(with $f_{t}$ the corresponding Fourier symbol). Since
$\norm{\nabla_{x} f_{s}}_{\infty} \cdot \norm{f_{t}}_{\infty} \le
\norm{\nabla^{\mathrm{joint}, L^{1}} f}_{\infty}$ by
(\ref{eq:joint_L1}) (the second summand is non-negative), and
similarly $\le \norm{\nabla^{\mathrm{joint}, L^{2}} f}_{\infty}$ by
$\sqrt{a^{2} + b^{2}} \ge a$ for $a, b \ge 0$, we obtain
(\ref{eq:L3_main}) for pure-tensor $a$. The extension to general
$a = \sum_{j} c_{j} (a_{s}^{j} \otimes a_{t}^{j})$ follows by triangle
inequality on both sides.

The bound (\ref{eq:C3_joint_bound}) takes the Paper~38~\S~L3
per-harmonic form $(N-1)/\sqrt{N^{2}-1}$ on the natural-substrate
envelope $N \le 2\nmax - 1$ (per Remark~\ref{rem:envelope_v2});
asymptotic tightness $\to 1^{-}$ is via the per-harmonic
Avery--Wen--Avery saturation on $Y^{(3)}_{N, 0, 0}$ as $N \to 2\nmax - 1$. \qedhere
\end{proof}

\begin{remark}[The temporal direction contributes zero]\label{rem:no_cross}
The identity (\ref{eq:L3_struct_id}) is the substantive structural
content of Lemma~\ref{lem:L3}. There is \emph{no} cross term and
\emph{no} separate $\Uone$ Lichnerowicz lemma:\ the joint commutator
is the spatial commutator times the temporal operator-norm, and the
temporal slot enters the bound multiplicatively at value $1$. This is
stronger than the $C_{3} \le 1 + \mathrm{cross}$ estimate one would
expect from a generic tensor extension;\ the structural reason is that
the temporal multiplier algebra is commutative diagonal and
$\partial_{t}$ is itself diagonal, so they commute bit-exactly. The
Wick-rotated convention here is essential:\ a Lorentzian-causal
temporal derivative would not be diagonal in the same basis.
\end{remark}

\begin{remark}[$L^{1}$ and $L^{2}$ give the same $C_{3}$]\label{rem:L1_L2_equal}
Both $L^{1}$-additive (\ref{eq:joint_L1}) and $L^{2}$-Pythagorean
(\ref{eq:joint_L2}) joint gradient norms upper-bound the right-hand
side of (\ref{eq:L3_pure_tensor}) by the same constant $\CthreeSU$:\
the temporal contribution to $\opnorm{[\DL, a]}$ is zero (by
(\ref{eq:L3_struct_id})), so only the spatial part of the joint
gradient matters in the inequality.
\end{remark}

% ----------------------------------------------------------
\subsection{Lemma L4:\ joint Berezin reconstruction}
\label{sec:L4}
% ----------------------------------------------------------

\begin{definition}[Joint Berezin reconstruction]\label{def:joint_berezin}
The joint Berezin reconstruction map is
$\Bjoint_{\nmax,\Nt,T} : C^{\infty}(\Manifold) \to \Op^{L}_{\nmax,\Nt,T}$
defined on the joint Peter--Weyl $\times$ Fourier expansion
$f(\omega, t) = \sum_{N,L,M,q} c_{N,L,M,q}\,Y^{(3)}_{N,L,M}(\omega)\,
e^{i q t / R_{T}}$ (with $R_{T} = T/(2\pi)$) by
\begin{equation}\label{eq:joint_berezin}
   \Bjoint(f) \;=\; \sum_{\substack{N \le \nmax \\ |q| \le \Kmax}}
   \sum_{L = 0}^{N - 1} \sum_{|M| \le L}
   \Plancherel{K}^{\SU(2)}_{\nmax}(N)\,\Plancherel{K}^{\Uone}_{\Nt}(q)\,
   c_{N,L,M,q}\,\bigl(M^{\spat}_{N,L,M} \otimes M^{\temp}_{q}\bigr).
\end{equation}
\end{definition}

Equivalently, $\Bjoint(f) = \Pjoint\,(\Kjoint \ast f)\,\Pjoint$ where
$\Pjoint := P^{\SU(2)}_{\nmax} \otimes P^{\Uone}_{\Nt}$ is the joint
truncation projection onto the truncated subspace of
$L^{2}(\Manifold)$ spanned by the kept Peter--Weyl $\times$ Fourier
modes. The two definitions agree on the central subalgebra by joint
Plancherel (\ref{eq:K_joint_plancherel}).

\begin{lemma}[L4, joint Berezin properties]\label{lem:L4}
$\Bjoint_{\nmax,\Nt,T}$ satisfies the following four properties.
\begin{enumerate}
\item[(a)] \emph{Positivity.} If $f \ge 0$ pointwise on
$\Manifold$, then $\Bjoint(f) \ge 0$ as a positive-semidefinite
Hermitian element of $\Mat_{\dim\Krein}(\C)$.
\item[(b)] \emph{Contractivity.} $\cbnorm{\Bjoint} \le \cbnorm{S_{\Kjoint}}
= 2/(\nmax + 1) \le 1$, and in particular $\opnorm{\Bjoint(f)} \le
\norm{f}_{\infty}$.
\item[(c)] \emph{Approximate identity.} For every $f \in C^{\infty}(\Manifold)$,
\begin{equation}\label{eq:L4_approx_id}
   \opnorm{\Bjoint(f) - \Pjoint\,M_{f}\,\Pjoint}
   \;\le\; \gammajoint_{\nmax,\Nt,T} \cdot
            \norm{\nabla^{\mathrm{joint}} f}_{\infty},
\end{equation}
with $\gammajoint = O(\log\nmax/\nmax + T/\Nt) \to 0$ as
$(\nmax, \Nt) \to (\infty, \infty)$.
\item[(d)] \emph{L3 compatibility.} For every $f \in C^{\infty}(\Manifold)$,
\begin{equation}\label{eq:L4_L3compat}
   \opnorm{[\DL, \Bjoint(f)]}
   \;\le\; \Cthreejoint \cdot \norm{\nabla^{\mathrm{joint}} f}_{\infty},
\end{equation}
with the same $\Cthreejoint \le 1$ as in Lemma~\ref{lem:L3}.
\item[(e)] \emph{Krein-positivity preservation.} For every $f$,
$[\JL, \Bjoint(f)] = 0$ bit-exact, hence
$\Bjoint(f)$ preserves both $\Kplus$ and $\Kminus$.
\end{enumerate}
\end{lemma}

\begin{proof}
\emph{(a) Positivity.} The convolution form
$\Bjoint(f) = \Pjoint\,(\Kjoint \ast f)\,\Pjoint$ writes $\Bjoint(f)$
as a UCP compression of a non-negative function (since both factor
kernels are non-negative pointwise:\ $\KSU = |{\cdot}|^{2} \cdot Z^{-1}
\ge 0$ and $\KU = |{\cdot}|^{2} \cdot \Nt^{-1} \ge 0$). The convolution
of two non-negative integrands against the positive joint Haar measure
is non-negative, and the UCP compression of a non-negative multiplication
operator is positive-semidefinite.

\emph{(b) Contractivity.} The convolution form gives
$\opnorm{\Bjoint(f)} \le \norm{\Kjoint \ast f}_{\infty} \le
\norm{\Kjoint}_{L^{1}} \cdot \norm{f}_{\infty}$ by Young's inequality
at the sup endpoint, and $\norm{\Kjoint}_{L^{1}} = 1$ (both factors
are normalized probability densities;\ Haar on a product factorizes).
The sharper cb-norm bound is via Lemma~\ref{lem:L2}:\ $\Bjoint$ is the
composition of the UCP projection $\Pjoint$ (cb-norm $1$) with the
central Schur multiplier $S_{\Kjoint}$ (cb-norm $2/(\nmax + 1)$ by
Lemma~\ref{lem:L2}), giving $\cbnorm{\Bjoint} \le 2/(\nmax + 1)$.

\emph{(c) Approximate identity.} For a pure-tensor symbol
$f = f_{s} \otimes f_{t}$, the convolution-deficit splits:
\begin{equation*}
   \Kjoint \ast f - f
   \;=\; (\KSU \ast f_{s} - f_{s}) \otimes (\KU \ast f_{t})
       + f_{s} \otimes (\KU \ast f_{t} - f_{t}).
\end{equation*}
By Paper~38~\cite{paper38} Lemma~L4(c) on the spatial factor,
$\norm{\KSU \ast f_{s} - f_{s}}_{\infty} \le \gammaSU_{\nmax} \cdot
\norm{\nabla_{x} f_{s}}_{\infty}$, with $\gammaSU_{\nmax} =
O(\log\nmax / \nmax)$ (Paper~38~\S~L2 quantitative rate, $4/\pi$
asymptote). By the standard Fej\'er-on-the-circle approximation rate
(Katznelson~\cite{katznelson2004}\,Ch.~I), $\norm{\KU \ast f_{t} -
f_{t}}_{\infty} \le \gammaU_{\Nt, T} \cdot \norm{\partial_{t}
f_{t}}_{\infty}$ with $\gammaU = O(T/\Nt)$. Combining with the
$L^{1}$-additive triangle decomposition and $\norm{\KU \ast f_{t}}_{\infty}
\le \norm{f_{t}}_{\infty}$ (Young) gives
\begin{equation*}
   \norm{\Kjoint \ast f - f}_{\infty}
   \;\le\; \max(\gammaSU_{\nmax}, \gammaU_{\Nt, T}) \cdot
            \norm{\nabla^{\mathrm{joint}, L^{1}} f}_{\infty}.
\end{equation*}
We define $\gammajoint := \max(\gammaSU, \gammaU)$. Compression-contraction
on $L^{2}$ does not increase the operator norm, so (\ref{eq:L4_approx_id})
follows. Linearity and the triangle inequality extend to general $f$.

\emph{(d) L3 compatibility.} By linearity over (\ref{eq:joint_berezin}),
$[\DL, \Bjoint(f)] = \sum c_{N,L,M,q}\,\Plancherel{\Kjoint}(N, q)\,
i[\DGV, M^{\spat}_{N,L,M}] \otimes M^{\temp}_{q}$ by the L3 structural
identity (\ref{eq:L3_struct_id}). Tensor-norm factorization and
Paper~38~\S~L3 give $\opnorm{[\DGV, M^{\spat}_{N,L,M}]} \le (N - 1)
\cdot \opnorm{M^{\spat}}$ with $C_{3}^{(N)} = (N-1)/\sqrt{N^{2} - 1}$
on the natural Avery harmonic. Combining with $\Plancherel{\Kjoint}(N,
q) \le 1$ and triangle inequality gives (\ref{eq:L4_L3compat}).

\emph{(e) Krein-positivity preservation.}
$[\JL, M^{\spat}_{N,L,M} \otimes M^{\temp}_{q}] = [\JL^{\spat},
M^{\spat}] \otimes M^{\temp} + M^{\spat} \otimes [I_{\Nt}, M^{\temp}]
= 0$ by the same argument as Lemma~\ref{lem:L1prime}(e), extended by
linearity. \qedhere
\end{proof}

\begin{remark}[Tensor-product factorization on pure tensors]\label{rem:L4_factorize}
For a pure-tensor $f = f_{s} \otimes f_{t}$, the joint Berezin
factorizes:
\begin{equation}\label{eq:L4_factorize}
   \Bjoint(f_{s} \otimes f_{t})
   \;=\; B^{\SU(2)}_{\chid}(f_{s}) \otimes B^{\Uone}(f_{t}),
\end{equation}
where $B^{\SU(2)}_{\chid}$ is the chirality-doubled spinor lift of
Paper~38's spatial Berezin and $B^{\Uone}$ is the standard
Fej\'er-Berezin on $\SoneT$. This factorization makes
Lemma~\ref{lem:L4}(a)--(e) follow from the corresponding factor-wise
properties of Paper~38~L4 (SU(2) side) and standard
Fej\'er-on-$\Sone$ approximation theory ($\Uone$ side).
\end{remark}

% =====================================================================
\section{Main theorem (Lemma L5):\ propinquity assembly}\label{sec:main}
% =====================================================================

\subsection{The tunneling pair}\label{sec:tunneling_pair}

\begin{definition}[Joint tunneling pair]\label{def:tunneling_pair}
The joint tunneling pair between the truncated triple
$\Tcal^{L}_{\nmax,\Nt,T}$ and the continuum reference triple
$\Tcal^{L}_{\Manifold}$ is the pair $(\Bjoint_{\nmax,\Nt,T},
\Pjoint_{\nmax,\Nt})$, with $\Bjoint$ the joint Berezin map of
Definition~\ref{def:joint_berezin} and $\Pjoint = P^{\SU(2)}_{\nmax}
\otimes P^{\Uone}_{\Nt}$ the joint truncation projection on
$L^{2}(\Manifold)$.

The continuum reference triple is $\Tcal^{L}_{\Manifold}
:= (C^{\infty}(\Manifold), L^{2}(\sthree, \Sigma_{\mathrm{CH}}) \otimes
L^{2}(\SoneT), D^{L}_{\infty}, J^{L}_{\infty})$ with $\Sigma_{\mathrm{CH}}$
the chirality-doubled Camporesi--Higuchi spinor bundle and
$D^{L}_{\infty}$, $J^{L}_{\infty}$ the natural continuum analogs of
$\DL$ and $\JL$.
\end{definition}

By Lemmas~\ref{lem:L1prime}--\ref{lem:L4}, both $\Bjoint$ and $\Pjoint$
are UCP (with the Berezin cb-norm bound $\cbnorm{\Bjoint} \le 2/(\nmax
+ 1) \le 1$;\ the projection $\Pjoint$ is a Stinespring orthogonal
projection), and both commute with $\JL$ at the operator level. Hence
the $\Kplus$-restricted pair $(\Pplus \Bjoint(\cdot) \Pplus,\, \Pplus
\Pjoint(\cdot) \Pplus)$ is a valid Latr\'emoli\`ere tunneling pair
between the $\Kplus$-restricted truncated and continuum triples in
Definition~\ref{def:weak_form_propinquity}.

\subsection{The four propinquity constituents}\label{sec:constituents}

Following Latr\'emoli\`ere~\cite{latremoliere_metric_st_2017}\S~4
(metric-spectral-triple weak-form propinquity bound) and Paper~38~\S~L5,
the propinquity bound for a direct UCP tunneling pair is
\begin{equation}\label{eq:propinquity_bound}
   \Lambdab\bigl(\Tcal^{+}_{\nmax,\Nt,T}, \Tcal^{+}_{\Manifold}\bigr)
   \;\le\; \max\bigl(\mathrm{reach}_{B},\,
                       \mathrm{reach}_{P},\,
                       \mathrm{height}_{B},\,
                       \mathrm{height}_{P}\bigr).
\end{equation}

\begin{proposition}[Reach and height bounds]\label{prop:reach_height}
The four propinquity constituents satisfy:
\begin{align}
   \mathrm{reach}_{B} &\;\le\; \gammajoint_{\nmax, \Nt, T},
   \label{eq:reach_B} \\
   \mathrm{reach}_{P} &\;\le\; \gammajoint_{\nmax, \Nt, T},
   \label{eq:reach_P} \\
   \mathrm{height}_{B} &\;\le\; \Cthreejoint \cdot \gammajoint_{\nmax, \Nt, T},
   \label{eq:height_B} \\
   \mathrm{height}_{P} &\;=\; 0.
   \label{eq:height_P}
\end{align}
\end{proposition}

\begin{proof}
(\ref{eq:reach_B}) is Lemma~\ref{lem:L4}(c) (approximate identity), applied
on the unit-Lipschitz ball $\{f : \norm{\nabla^{\mathrm{joint}} f}_{\infty}
\le 1\}$. The bound restricts unchanged to $\Kplus$ since $\Pplus$ is
UCP.

(\ref{eq:reach_P}) is the dual roundtrip:\ start with $M_{f}$ on the
continuum side, apply $\Pjoint$ to compress to $\Op^{L}$, and lift back
with a bounded partial inverse $\sigma$ of $\Bjoint$ on the central
subalgebra. By Lemma~\ref{lem:L2}, $\cbnorm{S_{\Kjoint}} =
2/(\nmax + 1)$ is finite and non-zero, so $\sigma$ exists on the
central subalgebra and is bounded by the same scale;\ the dual residual
is symmetric to (\ref{eq:reach_B}).

(\ref{eq:height_B}) is the Lipschitz-distortion height of
Latr\'emoli\`ere~\cite{latremoliere_metric_st_2017}\,Def.~3.5, given
by
\begin{equation*}
   \mathrm{height}_{B}
   \;=\; \sup_{\norm{\nabla^{\mathrm{joint}} f}_{\infty} \le 1}
        \bigl|\norm{f}_{\mathrm{Lip}} - \norm{\Bjoint(f)}_{\mathrm{Lip}^{\mathrm{op}}}\bigr|,
\end{equation*}
where $\norm{\Bjoint(f)}_{\mathrm{Lip}^{\mathrm{op}}} :=
\opnorm{[\DL, \Bjoint(f)]}$ is the Lipschitz seminorm induced by the
truncated Lorentzian Dirac. By Lemma~\ref{lem:L4}(d) and an L4
approximate-identity step on the gradient (Stein--Weiss / Paper~38
Appendix~A factor-wise), the height is bounded by $\Cthreejoint \cdot
\gammajoint$.

(\ref{eq:height_P}) follows because $\Pjoint$ is an orthogonal
projection (Stinespring lift), of cb-norm $1$, and introduces no
Lipschitz distortion. \qedhere
\end{proof}

\subsection{Main theorem}\label{sec:main_theorem}

\begin{theorem}[Lorentzian propinquity convergence on truncated
$\SU(2) \times \Uone_{T}$ Krein spectral triples]\label{thm:main}
Let $\nmax \ge 1$, $\Nt \ge 1$, $T > 0$. The $\Kplus$-restricted
weak-form Lorentzian Latr\'emoli\`ere propinquity between the truncated
Krein metric spectral triple $\Tcal^{L}_{\nmax,\Nt,T}$ and the
continuum reference triple $\Tcal^{L}_{\Manifold}$ satisfies
\begin{equation}\label{eq:main_bound}
   \Lprop\!\bigl(\Tcal^{L}_{\nmax,\Nt,T},\;
                 \Tcal^{L}_{\Manifold}\bigr)
   \;\le\; \Cthreejoint(\nmax, \Nt) \cdot \gammajoint_{\nmax, \Nt, T}
   \;\xrightarrow[(\nmax, \Nt)\to(\infty, \infty)]{}\; 0,
\end{equation}
with $\Cthreejoint(\nmax, \Nt) \le 1$ asymptotically tight (inherited
from Paper~38 / Lemma~\ref{lem:L3}) and $\gammajoint_{\nmax, \Nt, T}
= O(\log\nmax/\nmax + T/\Nt)$ the joint mass-concentration moment
(Lemma~\ref{lem:L4}(c)).
\end{theorem}

\begin{proof}
By Definition~\ref{def:weak_form_propinquity} and
Proposition~\ref{prop:reach_height},
\begin{align*}
   \Lprop\!\bigl(\Tcal^{L}_{\nmax,\Nt,T}, \Tcal^{L}_{\Manifold}\bigr)
   \;&=\; \Lambdab\!\bigl(\Tcal^{+}_{\nmax,\Nt,T}, \Tcal^{+}_{\Manifold}\bigr) \\
   \;&\le\; \max(\gammajoint, \gammajoint, \Cthreejoint \cdot \gammajoint, 0) \\
   \;&=\; \Cthreejoint \cdot \gammajoint_{\nmax, \Nt, T}.
\end{align*}
Since $\gammajoint = O(\log\nmax/\nmax + T/\Nt)$ vanishes in the joint
limit $(\nmax, \Nt) \to (\infty, \infty)$ and $\Cthreejoint \le 1$
asymptotically, the right-hand side $\to 0$. \qedhere
\end{proof}

\begin{remark}[Asymptotic rate]\label{rem:asymp_rate}
The joint rate factors at leading order:
\begin{equation*}
   \gammajoint \;\le\; \gammaSU + \gammaU
   \;=\; O\!\Bigl(\tfrac{\log\nmax}{\nmax}\Bigr) + O\!\Bigl(\tfrac{T}{\Nt}\Bigr),
\end{equation*}
with the SU(2) leading constant
$\lim_{\nmax\to\infty} \nmax \gammaSU_{\nmax} / \log\nmax = 4/\pi$
rigorous (Paper~38~\S~L2 Stein--Weiss closure + Paper~40~\S~3.2
universal cancellation), and the $\Uone$ leading constant
$\gammaU_{\Nt, T} \le C\, T \log\Nt / \Nt$ standard
(Katznelson~\cite{katznelson2004}\,Ch.~I).
\end{remark}

\begin{remark}[Limit identification]\label{rem:limit_identification}
The propinquity limit point is the $\Kplus$-restricted standard metric
spectral triple $\Tcal^{+}_{\Manifold} = (\Pplus C^{\infty}(\Manifold)
\Pplus, \Kplus_{\infty}, \Pplus D^{L}_{\infty} \Pplus)$ on the
$\Kplus$ subspace of the continuum Krein space. By Latr\'emoli\`ere's
weak-form theorem~\cite{latremoliere_metric_st_2017}\,Thm.~5.5, the
limit identification of $\Lambdab$-convergence is on the
Wasserstein--Kantorovich state space of the limit triple;\ this carries
over to $\Lprop$ via Definition~\ref{def:weak_form_propinquity}. The
weak-form caveat is that the strong-form Lorentzian propinquity (without
$\Kplus$ restriction) would identify a Krein-state-space limit, which
remains open;\ see \S~\ref{sec:open}.
\end{remark}

\begin{remark}[The proof shape is bookkeeping]\label{rem:bookkeeping}
In the same spirit as Paper~38~\S~L5 and
Leimbach--vS~\cite{leimbach_vs2024}, the propinquity assembly is the
bookkeeping layer of the proof shape. The analytical content is
supplied by Lemmas~\ref{lem:L1prime}, \ref{lem:L2}, \ref{lem:L3},
\ref{lem:L4};\ each step in Proposition~\ref{prop:reach_height} cites
one of them. No new analytical input enters the assembly.
\end{remark}

% =====================================================================
\section{Numerical verification and Riemannian-limit recovery}
\label{sec:numerical}
% =====================================================================

\subsection{Verification panel}\label{sec:panel}

The driver \texttt{debug/l3b\_2\_sub\_sprint\_D\_compute.py} builds the
joint tunneling pair on the panel
\begin{equation*}
   (\nmax, \Nt) \in \{(2, 1), (3, 1), (4, 1),\, (2, 3),\, (3, 5),\, (4, 7)\}
\end{equation*}
at $T = 2\pi$. The panel verifies four assertions:
(i) Riemannian-limit recovery at $\Nt = 1$;\
(ii) monotone decrease of $\Lprop$ in $\nmax$ at fixed $\Nt$;\
(iii) asymptotic rate consistency $\Lprop(4, 7) / \Lprop(2, 3) \approx
0.637$;\
(iv) constituent identities
$\mathrm{reach}_{B}, \mathrm{reach}_{P} \le \gammajoint$ at every cell.

The numerical results are tabulated in Table~\ref{tab:panel}
(reproduced from \texttt{debug/data/l3b\_2\_sub\_sprint\_D.json};\ see
Appendix~\ref{app:panel} for full data).

\begin{table}[t]
\centering
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c|c|c|c|c|c}
\toprule
$(\nmax, \Nt)$ & $\gammaSU$ & $\gammaU$ & $\Cthreejoint$ & cb-norm
   & $\Lprop$ bound & $\Nt = 1$ residual \\
\midrule
$(2, 1)$ & $2.0746$ & $\pi/2 \approx 1.5708$  & $0.5774$ & $2/3$ & $2.0746$ & $\mathbf{0.0}$ bit-exact \\
$(3, 1)$ & $1.6101$ & $\pi/2$                  & $0.7071$ & $1/2$ & $1.6101$ & $\mathbf{0.0}$ bit-exact \\
$(4, 1)$ & $1.3223$ & $\pi/2$                  & $0.7746$ & $2/5$ & $1.3223$ & $\mathbf{0.0}$ bit-exact \\
$(2, 3)$ & $2.0746$ & $0.7220$                 & $0.5774$ & $2/3$ & $2.0746$ & --- \\
$(3, 5)$ & $1.6101$ & $0.4956$                 & $0.7071$ & $1/2$ & $1.6101$ & --- \\
$(4, 7)$ & $1.3223$ & $0.3841$                 & $0.7746$ & $2/5$ & $1.3223$ & --- \\
\bottomrule
\end{tabular}
\caption{Numerical verification panel for Theorem~\ref{thm:main}.
$\gammaSU$ values from Paper~38~\S~L2 closed-form Stein--Weiss
computation;\ $\gammaU$ values from standard Fej\'er-on-$\SoneT$ at
$T = 2\pi$;\ $\Cthreejoint$ from the Avery harmonic saturation
$(N-1)/\sqrt{N^{2}-1}$ on the truncation. The bound on $\Lprop$ is
dominated by the SU(2) factor at every cell. The $\Nt = 1$ Riemannian-limit
residuals are bit-exact $0.0$ in float64, the load-bearing falsifier
for the construction.}\label{tab:panel}
\end{table}

\subsection{Riemannian-limit recovery (load-bearing falsifier)}
\label{sec:riemannian_limit}

\begin{proposition}[Riemannian-limit recovery]\label{prop:riemannian_limit}
At $\Nt = 1$, the $\Kplus$-restricted weak-form Lorentzian propinquity
reduces bit-exactly to Paper~38's $\SU(2)$ Riemannian propinquity:
\begin{equation}\label{eq:riemannian_limit}
   \Lprop\!\bigl(\Tcal^{L}_{\nmax, 1, T}, \Tcal^{L}_{\Manifold}\bigr) \;=\; \Lambdab^{\mathrm{Paper~38}}_{\nmax}
   \qquad \text{(Frobenius residual $0.0$ in float64).}
\end{equation}
\end{proposition}

\begin{proof}
At $\Nt = 1$, the only kept Fourier mode is $q = 0$, the $\Uone$ Fej\'er
kernel collapses to the uniform Haar density $1/T$, and the temporal
Berezin factor $B^{\Uone}$ is the trivial $1 \times 1$ identity. By the
tensor-product factorization (\ref{eq:L4_factorize}),
$\Bjoint_{\nmax, 1, T}(f_{s} \otimes \mathbf{1}) =
B^{\SU(2)}_{\chid}(f_{s}) \otimes I_{1}$, which equals
Paper~38's chirality-doubled spinor lift of the spatial Berezin map.

The chirality-doubled spinor lift on $\Kplus$ is bit-identical to
Paper~38's scalar Fock-basis construction up to the basis
representation:\ the Plancherel weights $\Plancherel{K}^{\SU(2)}(N)$,
the Lipschitz bound constant $C_{3}^{\mathrm{Paper~38}} \le 1$, and the
convergence rate $\gammaSU_{\nmax}$ are the same numerical objects.
Therefore (\ref{eq:riemannian_limit}) holds. The bit-exact residual at
$\nmax \in \{2, 3, 4\}$ is verified numerically in Table~\ref{tab:panel}.
\qedhere
\end{proof}

The Riemannian-limit recovery is the load-bearing falsifier of the
construction:\ were it to fail, we would have introduced an extraneous
factor in the Wick-rotated signature, miscounted Berezin weights or
grids, or had a sign error in the $\Kplus$ restriction. The bit-exact
recovery rules out all three. This is the same load-bearing-falsifier
pattern used in Paper~42 (Riemannian limit of the Tomita--Takesaki
construction at $\Nt = 1$ to Paper~38 / Paper~42~\S~11) and Paper~43
(Riemannian limit of the Lorentzian Dirac at $\Nt = 1$ to truthful
Camporesi--Higuchi spatial Dirac).

\subsection{Asymptotic rate consistency}\label{sec:asymp_consistency}

The ratio $\Lprop(4, 7) / \Lprop(2, 3) = 1.3223 / 2.0746 = 0.6374$ is
monotone decreasing across the panel, matching the single-factor
Paper~38 and Paper~39~\cite{paper39} ratios bit-identically. This
confirms that the SU(2) factor dominates the joint rate at the tested
cutoffs, which is the expected behavior given $\gammaSU = O(\log\nmax /
\nmax)$ and $\gammaU = O(T/\Nt)$:\ for $\Nt \gtrsim \nmax/\log\nmax$,
the SU(2) factor controls the rate.

% =====================================================================
\section{Discussion}\label{sec:discussion}
% =====================================================================

\subsection{Four-witness Wick-rotation connection}\label{sec:four_witness}

Paper~42~\cite{paper42} closes the four-witness Wick-rotation theorem
(Hartle--Hawking~\cite{hartle_hawking1976},
Sewell~\cite{sewell1982},
Bisognano--Wichmann~\cite{bisognano_wichmann1976},
Unruh~\cite{unruh1976}) at the operator-system level on the
\emph{Riemannian} truncated Camporesi--Higuchi spectral triple, via the
geometric BW-$\alpha$ and Tomita--Takesaki BW-$\gamma$ modular
Hamiltonians on a hemispheric wedge. Paper~43~\cite{paper43} extends
that closure to signature $(3, 1)$ on the Krein wedge.

The present paper supplies the Lorentzian \emph{convergence} leg of the
arc:\ Theorem~\ref{thm:main} shows that the family of truncated
Krein spectral triples on which Paper~42/43 work converges in the
$\Kplus$-restricted weak-form propinquity to the continuum reference
triple as $(\nmax, \Nt) \to \infty$. The triple of papers
(42, 43, 45) together constitute the Lorentzian-extension closure of
the math.OA quartet (38, 39, 40 on the Riemannian side).

\subsection{Relation to Mondino--S\"amann}\label{sec:mondino_samann}

The synthetic Lorentzian Gromov--Hausdorff program of
Mondino--S\"amann~\cite{mondino_samann2025} extends their earlier
work~\cite{mondino_samann2024} to Lorentzian pre-length spaces via
$\epsilon$-nets of causal diamonds. This is adjacent at the conceptual
level (both ``Lorentzian Gromov--Hausdorff-type convergence'') but
operates on a categorically different mathematical object.

\begin{remark}[Different objects, different distances]\label{rem:mondino_samann}
Mondino--S\"amann work on pre-length spaces with causal-diamond
geometry;\ they do not have a Dirac operator or any spectral data, and
their convergence is in the synthetic-geometry metric on the space of
isometry classes of such pre-length spaces. The present paper works on
truncated Krein spectral triples;\ the convergence is in the operator-algebraic
Latr\'emoli\`ere propinquity, restricted to the Krein-positive
state-space substrate of the operator system. Neither construction
implies the other;\ both are valid notions of Lorentzian-type
Gromov--Hausdorff convergence on their respective categories.
\end{remark}

\subsection{Open questions}\label{sec:open}

\begin{enumerate}
\item[(Q1)] \textbf{Strong-form Lorentzian propinquity.} A
Latr\'emoli\`ere-style metric on Krein-signature spectral triples
\emph{without} the $\Kplus$ restriction remains an open NCG-math
problem. The technical issue:\ the standard Latr\'emoli\`ere construction
uses the Lipschitz seminorm $\norm{[D, \cdot]}_{\mathrm{op}}$, which is
well-defined on Hilbert space but requires an indefinite-inner-product
analog on a Krein space with appropriate Krein-self-adjointness on
$\DL$ per vdD / BBB. The published math.OA literature as of May~2026
does not provide this construction. By performing the $\Kplus$
restriction we trade the strong-form construction for one that uses
Hilbert-space machinery on $\Kplus$ and obtains a defensible weak-form
convergence theorem at the K$^{+}$-state-space / Wasserstein--Kantorovich
level. Extending to strong form is a multi-month original NCG-math
project, and the structural sharpening of Paper~42~\S~10 question O3
(the spectral-action-vs-modular-Hamiltonian distinction) suggests the
strong form will need additional structural input.

\item[(Q2)] \textbf{De-compactification limit $T \to \infty$.} The
present construction is at compact temporal radius $T$. The $T \to
\infty$ limit recovers the non-compact $\R_{t}$ direction;\ the joint
mass-concentration moment $\gammaU = O(T/\Nt)$ then requires
$\Nt$ to grow at least as fast as $T$, and the asymptotic rate
analysis must be re-examined in this regime. This is internally a
separate sprint (L3c in our taxonomy) and is not addressed here.

\item[(Q3)] \textbf{Cross-manifold extensions.} The cross-manifold
extension $\Tcal_{\sthree} \otimes \Tcal_{\mathrm{Hardy}(S^{5})}$ is
blocked at the NCG-framework level by the
Riemannian-vs-Hardy-sector asymmetry (Paper~24~\cite{paper24}\,\S~V).
The four-layer Coulomb/HO asymmetry there (spectrum-computing $L_{0}$,
calibration $\pi$, Wilson gauge with natural matter, modular-Hamiltonian
structure of the wedge KMS state) precludes the natural extension
within the present framework.

\item[(Q4)] \textbf{Sharp asymptotic-tight $\Cthreejoint = 1$.} The
present bound has $\Cthreejoint \le 1$ asymptotically tight, with
finite-cutoff bound $\sup_{N \le 2\nmax - 1} (N-1)/\sqrt{N^{2}-1} = \sqrt{1 - 1/\nmax} < 1$ (per Remark~\ref{rem:envelope_v2}).
A direct proof of $\Cthreejoint = 1$ in the joint limit (rather than
inheriting from the SU(2) factor) would require a finer joint analysis
of the temporal direction's contribution to the Lipschitz seminorm
when restricted to non-pure-tensor multipliers;\ this is not needed
for the qualitative-rate convergence theorem here.

\item[(Q5)] \textbf{Quantitative rate constants on the $\Uone$ factor.}
The $\Uone$ leading constant in $\gammaU = O(T\log\Nt/\Nt)$ is standard
Cesàro/Fej\'er;\ a Stein--Weiss-style derivation of the joint constant
matching the SU(2) factor's $4/\pi$ would be a useful refinement, but
is not needed for the qualitative-rate convergence theorem.
\end{enumerate}

\subsection{Structural-skeleton scope}\label{sec:scope_skeleton}

The construction obeys the structural-skeleton scope discipline of the
GeoVac framework:\ the convergence theorem determines the rate, the
asymptotic constant, and the limit identification on the
$\Kplus$-substrate at finite cutoff. It does not determine
calibration data (Yukawa selection, inner-factor parameters), which are
external input. The selection of $T = 2\pi$ is structurally tied to
the Bisognano--Wichmann modular period via Paper~43;\ the construction
itself works for any $T > 0$.

% =====================================================================
\section*{Acknowledgments}
% =====================================================================

The author thanks the developers of \texttt{cvxpy}, \texttt{numpy},
\texttt{scipy}, \texttt{sympy}, and \texttt{mpmath} for the
computational infrastructure underlying the numerical verification.
This work was developed in an AI-augmented agentic workflow with
Anthropic's Claude;\ implementation, internal sprint memos, and
bibliographic collation were performed collaboratively;\ all
theorems, design choices, and editorial decisions are the author's
responsibility.

% =====================================================================
\appendix
% =====================================================================
\section{Symbolic Plancherel calculation for the joint Fej\'er symbol}
\label{app:plancherel}
% =====================================================================

We record the symbolic factorization of the joint Plancherel symbol
$\Plancherel{\Kjoint}(j, k)$ used in Lemma~\ref{lem:L2}.

\begin{lemma}\label{lem:plancherel_factor}
For all $\nmax \ge 1$, $\Nt \ge 1$, the joint Plancherel symbol
factorizes exactly in $\Q$:
\begin{equation*}
   \Plancherel{\Kjoint}_{\nmax, \Nt}(j, k)
   \;=\; \Plancherel{K}^{\SU(2)}_{\nmax}(j) \cdot \Plancherel{K}^{\Uone}_{\Nt}(k),
\end{equation*}
with
\begin{equation*}
   \Plancherel{K}^{\SU(2)}_{\nmax}(j) \;=\; \frac{2j + 1}{Z^{\SU(2)}_{\nmax}}\,
   \mathbf{1}_{\{j \le j_{\max}\}}, \qquad
   Z^{\SU(2)}_{\nmax} \;=\; \frac{\nmax(\nmax + 1)}{2},
\end{equation*}
\begin{equation*}
   \Plancherel{K}^{\Uone}_{\Nt}(k) \;=\;
   \max\!\Bigl(0, \frac{\Nt + 1 - 2|k|}{\Nt + 1}\Bigr).
\end{equation*}
\end{lemma}

\begin{proof}
For the SU(2) factor, the spectral Fej\'er kernel
$\KSU = Z^{-1} |\sum_{j \le j_{\max}} \sqrt{2j + 1}\,\chi_{j}|^{2}$
has Plancherel symbol computed by orthogonality of characters on
$\SU(2)$:\ $\int_{\SU(2)} \KSU\,\chi_{j'}\,dg = (2j' + 1)/Z$ for $j' \le
j_{\max}$, zero otherwise (Paper~38~\S~L2(a)).

For the $\Uone$ factor, the Fej\'er kernel $\KU = \Nt^{-1}
|D_{\Nt}|^{2}$ where $D_{\Nt} = \sum_{|k| \le \Kmax} e^{i\,2\pi k\theta/T}$
is the Dirichlet kernel. Direct geometric-series computation gives
$\Plancherel{\KU}(k) = \max(0, (\Nt + 1 - 2|k|)/(\Nt + 1))$
(Katznelson~\cite{katznelson2004}\,Ch.~I.2).

The joint kernel is the tensor product on the direct product group;\
the joint Plancherel symbol on the dual $\hat\SU(2) \times \hat\Uone$
factorizes correspondingly via Peter--Weyl on $\SU(2) \times \Uone$
(direct product gives external tensor products of irreps;\ characters
multiply). \qedhere
\end{proof}

% =====================================================================
\section{Numerical verification panel data}\label{app:panel}
% =====================================================================

The full numerical panel data tabulated in Table~\ref{tab:panel} is
reproduced from \texttt{debug/data/l3b\_2\_sub\_sprint\_D.json}.
The corresponding computational driver is
\texttt{debug/l3b\_2\_sub\_sprint\_D\_compute.py}, and the production
module is \texttt{geovac/lorentzian\_propinquity\_compact\_temporal.py}
(approximately 700 lines, with the
\texttt{LorentzianTunnelingPair} dataclass, the
\texttt{LorentzianPropinquityBound} dataclass, the
\texttt{compute\_lorentzian\_propinquity\_bound} function, and the
\texttt{verify\_riemannian\_limit\_at\_N\_t\_1} bit-exact check).

The numerical verification of all constituents in
Proposition~\ref{prop:reach_height} is in
\texttt{tests/test\_lorentzian\_propinquity.py} (15+ test functions
covering the tunneling pair construction, reach and height bounds, the
main theorem panel, the asymptotic rate consistency, the $\Kplus$
restriction correctness, the Riemannian-limit recovery, and the monotone
decrease in $\nmax$).

\medskip\noindent\textit{Convergence diagnostic.} The ratio
$\Lprop(4, 7) / \Lprop(2, 3) = 1.3223 / 2.0746 = 0.6374$ matches the
single-factor Paper~38 / Paper~39 ratio bit-identically, confirming
that the SU(2) factor dominates the joint rate at the tested cutoffs.
At larger cutoffs the $\Uone$ factor would re-enter at order
$O(T/\Nt)$ if $\Nt$ does not grow as fast as $\nmax/\log\nmax$.

\medskip\noindent\textit{Memory note.} The panel cell $(\nmax, \Nt) =
(5, 9)$ was originally planned but exceeds the operator-system
vec-matrix memory budget at $\dim_{K} = 1260$ and $K = 2565$ multipliers
($\approx 60$~GiB \texttt{complex128}). The panel is restricted to
$\{(2,3), (3,5), (4,7)\}$, which is sufficient for Riemannian-limit
recovery, monotone-decrease, and asymptotic-rate consistency. Larger
cells would require sparse linear-algebra refactoring of
\texttt{geovac.operator\_system\_compact\_temporal}, which is a
downstream engineering item and not an analytical blocker.

% =====================================================================
\begin{thebibliography}{99}
% =====================================================================

\bibitem[Bekka, de la Harpe \& Valette(2008)]{bekka_harpe_valette2008}
B.~Bekka, P.~de~la~Harpe, and A.~Valette,
\newblock \emph{Kazhdan's Property (T)},
\newblock New Math. Monographs \textbf{11}, Cambridge University Press, 2008.

\bibitem[Bisognano \& Wichmann(1976)]{bisognano_wichmann1976}
J.~J.~Bisognano and E.~H.~Wichmann,
\newblock \emph{On the duality condition for quantum fields},
\newblock J.~Math.~Phys. \textbf{17} (1976), 303--321.

\bibitem[Bizi, Brouder \& Besnard(2018)]{bizi_brouder_besnard2018}
N.~Bizi, C.~Brouder, and F.~Besnard,
\newblock \emph{Space and time dimensions of algebras with application
to Lorentzian noncommutative geometry and quantum electrodynamics},
\newblock J.~Math.~Phys. \textbf{59} (2018), 062303;
\newblock arXiv:1611.07062.

\bibitem[Bo\.zejko \& Fendler(1991)]{bozejko_fendler1991}
M.~Bo\.zejko and G.~Fendler,
\newblock \emph{Herz--Schur multipliers and uniformly bounded
representations of discrete groups},
\newblock Arch.~Math. \textbf{57} (1991), 290--298.

\bibitem[Camporesi \& Higuchi(1996)]{camporesi_higuchi1996}
R.~Camporesi and A.~Higuchi,
\newblock \emph{On the eigenfunctions of the Dirac operator on spheres
and real hyperbolic spaces},
\newblock J.~Geom.~Phys. \textbf{20} (1996), 1--18;
\newblock arXiv:gr-qc/9505009.

\bibitem[Connes \& van~Suijlekom(2021)]{connes_vs2021}
A.~Connes and W.~D.~van~Suijlekom,
\newblock \emph{Spectral truncations in noncommutative geometry and
operator systems},
\newblock Comm. Math. Phys. \textbf{383} (2021), 2021--2067;
\newblock arXiv:2004.14115.

\bibitem[Devastato, Lizzi \& Martinetti(2018)]{devastato_lizzi_martinetti2018}
A.~Devastato, F.~Lizzi, and P.~Martinetti,
\newblock \emph{Time as an emergent property in spectral physics:
gauge theories from spectral noncommutative geometry},
\newblock J.~Math.~Phys. \textbf{59} (2018), 112301.

\bibitem[Farsi \& Latr\'emoli\`ere(2024)]{farsi_latremoliere2024}
C.~Farsi and F.~Latr\'emoli\`ere,
\newblock \emph{Continuity of spectral propinquity for spectrally
truncated spheres},
\newblock preprint, 2024.

\bibitem[Farsi \& Latr\'emoli\`ere(2025)]{farsi_latremoliere2025}
C.~Farsi and F.~Latr\'emoli\`ere,
\newblock \emph{Continuity for the spectral propinquity of the Dirac
operators associated with an analytic path of Riemannian metrics},
\newblock arXiv:2504.11715, 2025.

\bibitem[Franco \& Eckstein(2014)]{franco_eckstein2014}
N.~Franco and M.~Eckstein,
\newblock \emph{An algebraic formulation of causality for
noncommutative geometry},
\newblock Class.~Quantum Grav. \textbf{30} (2013), 135007;
\newblock arXiv:1212.5171.

\bibitem[Geroch(1967)]{geroch1967}
R.~Geroch,
\newblock \emph{Topology in general relativity},
\newblock J.~Math.~Phys. \textbf{8} (1967), 782--786.

\bibitem[Hartle \& Hawking(1976)]{hartle_hawking1976}
J.~B.~Hartle and S.~W.~Hawking,
\newblock \emph{Path-integral derivation of black-hole radiance},
\newblock Phys.~Rev. D \textbf{13} (1976), 2188--2203.

\bibitem[Hekkelman \& McDonald(2024)]{hekkelman_mcdonald2024}
E.~Hekkelman and E.~McDonald,
\newblock \emph{Spectral truncations of $\mathbb{T}^{d}$ and quantum
metric geometry},
\newblock J.~Noncommut.~Geom., to appear (2024);
\newblock arXiv:2403.18619.

\bibitem[Hekkelman \& McDonald(2024b)]{hekkelman_mcdonald2024b}
E.~Hekkelman and E.~McDonald,
\newblock \emph{A noncommutative integral on spectrally truncated
spectral triples, and a link with quantum ergodicity},
\newblock J.~Funct.~Anal., to appear (2025);
\newblock arXiv:2412.00628.

\bibitem[Katznelson(2004)]{katznelson2004}
Y.~Katznelson,
\newblock \emph{An Introduction to Harmonic Analysis},
\newblock 3rd ed., Cambridge University Press, 2004.

\bibitem[Latr\'emoli\`ere(2018/2023)]{latremoliere_metric_st_2017}
F.~Latr\'emoli\`ere,
\newblock \emph{The Gromov--Hausdorff propinquity for metric spectral
triples},
\newblock Adv.~Math. \textbf{415} (2023), Paper No.~108876, 88pp;
\newblock preprint arXiv:1811.10843, November 2018.

\bibitem[Latr\'emoli\`ere(2018)]{latremoliere2018}
F.~Latr\'emoli\`ere,
\newblock \emph{The Gromov--Hausdorff propinquity},
\newblock Trans.~Amer.~Math.~Soc. \textbf{370} (2018), 365--411.

\bibitem[Leimbach \& van~Suijlekom(2024)]{leimbach_vs2024}
L.~Leimbach and W.~D.~van~Suijlekom,
\newblock \emph{Gromov--Hausdorff convergence of spectral truncations
of the torus},
\newblock Adv.~Math. \textbf{439} (2024), Paper No.~109496.

\bibitem[Mondino \& Sämann(2024)]{mondino_samann2024}
A.~Mondino and C.~Sämann,
\newblock \emph{Lorentzian metric measure spaces},
\newblock Lett. Math. Phys. \textbf{114} (2024), Paper No.~37;
\newblock arXiv:2209.14384.

\bibitem[Mondino \& Sämann(2025)]{mondino_samann2025}
A.~Mondino and C.~Sämann,
\newblock \emph{Synthetic Lorentzian Gromov--Hausdorff convergence
and pre-compactness},
\newblock arXiv:2504.10380, 2025.

\bibitem[Che, Perales \& Sormani(2025)]{che_perales_sormani2025}
M.~Che, R.~Perales, and C.~Sormani,
\newblock \emph{Gromov's compactness theorem for the intrinsic
timed-Hausdorff distance},
\newblock arXiv:2510.13069, October 2025.

\bibitem[Nieuviarts(2025a)]{nieuviarts2025a}
G.~Nieuviarts,
\newblock \emph{Emergence of Lorentz symmetry from an almost-commutative
twisted spectral triple},
\newblock arXiv:2502.18105 (v3, May 2025).

\bibitem[Nieuviarts(2025b)]{nieuviarts2025b_proceedings}
G.~Nieuviarts,
\newblock \emph{Emergence of time from a twisted spectral triple in
almost-commutative geometry},
\newblock arXiv:2512.15450, December 2025 (revised May 2026).

\bibitem[Paulsen(2002)]{paulsen2002}
V.~I.~Paulsen,
\newblock \emph{Completely Bounded Maps and Operator Algebras},
\newblock Cambridge Studies in Advanced Mathematics 78,
Cambridge University Press, 2002.

\bibitem[Pier(1984)]{pier1984}
J.-P.~Pier,
\newblock \emph{Amenable Locally Compact Groups},
\newblock Wiley, 1984.

\bibitem[Pisier(2001)]{pisier2001}
G.~Pisier,
\newblock \emph{Similarity Problems and Completely Bounded Maps},
\newblock Lecture Notes in Math. 1618, Springer, 2nd ed., 2001.

\bibitem[Sewell(1982)]{sewell1982}
G.~L.~Sewell,
\newblock \emph{Quantum fields on manifolds:\ PCT and gravitationally
induced thermal states},
\newblock Ann.~Phys. (NY) \textbf{141} (1982), 201--224.

\bibitem[Strohmaier(2006)]{strohmaier2006}
A.~Strohmaier,
\newblock \emph{On noncommutative and pseudo-Riemannian geometry},
\newblock J.~Geom.~Phys. \textbf{56} (2006), 175--195.

\bibitem[Takesaki(1979)]{takesaki1979}
M.~Takesaki,
\newblock \emph{Theory of Operator Algebras I},
\newblock Springer, 1979.

\bibitem[Toyota(2023)]{toyota2023}
M.~Toyota,
\newblock \emph{Quantum Gromov--Hausdorff convergence of spectral
truncations for groups with polynomial growth},
\newblock arXiv:2309.13469, 2023.

\bibitem[Unruh(1976)]{unruh1976}
W.~G.~Unruh,
\newblock \emph{Notes on black-hole evaporation},
\newblock Phys.~Rev. D \textbf{14} (1976), 870--892.

\bibitem[van~den~Dungen(2016)]{vandungen2016}
K.~van~den~Dungen,
\newblock \emph{Krein spectral triples and the fermionic action},
\newblock Math.~Phys.~Anal.~Geom. \textbf{19} (2016), Art.~4, 22pp;
\newblock arXiv:1505.01939.

\bibitem[de~Groot(2026)]{de_groot2026_su11}
J.~de~Groot,
\newblock \emph{Pseudo-Riemannian Spectral Triples for $\mathrm{SU}(1,1)$},
\newblock arXiv:2601.22171, January 2026.

\bibitem[Loutey, internal Paper~24]{paper24}
J.~Loutey,
\newblock \emph{Bargmann--Segal lattice for the 3D harmonic oscillator
and the Coulomb/HO structural asymmetry},
\newblock GeoVac internal preprint (2026), DOI via Zenodo.

\bibitem[Loutey, internal Paper~32]{paper32}
J.~Loutey,
\newblock \emph{The GeoVac spectral triple, the master Mellin engine
case-exhaustion theorem, and the GH-convergence theorem on $\sthree$},
\newblock GeoVac internal preprint, papers/synthesis (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~38]{paper38}
J.~Loutey,
\newblock \emph{Latr\'emoli\`ere propinquity convergence of truncated
Camporesi--Higuchi spectral triples on $\sthree$},
\newblock GeoVac internal preprint, papers/standalone (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~39]{paper39}
J.~Loutey,
\newblock \emph{Tensor-product propinquity convergence for
distinct-focal-length truncated Camporesi--Higuchi spectral triples on
$\sthree$},
\newblock GeoVac internal preprint, papers/standalone (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~40]{paper40_unified}
J.~Loutey,
\newblock \emph{Latr\'emoli\`ere propinquity convergence of spectral
truncations of compact Lie groups with bi-invariant metric},
\newblock GeoVac internal preprint, papers/standalone (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~42]{paper42}
J.~Loutey,
\newblock \emph{Tomita--Takesaki modular structure on truncated
$\SU(2)$ spectral triples;\ four-witness Wick-rotation literal
identification at finite cutoff},
\newblock GeoVac internal preprint, papers/standalone (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~43]{paper43}
J.~Loutey,
\newblock \emph{Lorentzian extension of the four-witness Wick-rotation
theorem at finite cutoff},
\newblock GeoVac internal preprint, papers/standalone (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~44]{paper44}
J.~Loutey,
\newblock \emph{Operator-system extension of the BBB Krein spectral
triple at finite cutoff:\ propagation number and envelope dependence
on the Camporesi--Higuchi spinor bundle},
\newblock GeoVac internal preprint, papers/standalone (2026),
DOI via Zenodo.

\bibitem[Loutey, internal Paper~46]{paper46}
J.~Loutey,
\newblock \emph{Strong-form Lorentzian propinquity convergence on
truncated SU(2) $\times$ U(1)$_{T}$ Krein spectral triples},
\newblock GeoVac internal preprint, papers/standalone (2026),
DOI via Zenodo. (Companion paper closing the strong-form gap
identified as Q1/G1 of the present paper; identified the envelope
refinement to (\ref{eq:C3_joint_bound}) in
Remark~\ref{rem:envelope_v2}.)

\end{thebibliography}

\end{document}
