% =====================================================================
% Paper 49 (standalone): Operator-system Lorentzian pre-length spaces
% and the strong-form Krein-Mondino-Saemann bridge: cross-KMS-state
% thermal-time stack and strict super-additivity.
%
% Eleventh math.OA standalone in the GeoVac series. Siblings:
%   Paper 29 (Ramanujan-Hopf), Paper 32 (spectral triple), Paper 38
%   (SU(2) Riemannian propinquity), Paper 39 (tensor-product
%   propinquity), Paper 40 (universal rate constant on compact Lie
%   groups), Paper 42 (Tomita-Takesaki Riemannian closure), Paper 43
%   (Lorentzian extension of the four-witness theorem), Paper 44
%   (Lorentzian operator-system substrate), Paper 45 (K+-weak-form
%   Lorentzian propinquity convergence), Paper 46 (strong-form
%   Lorentzian propinquity convergence on the natural and enlarged
%   substrates), Paper 47 (two-rate hybrid convergence to the
%   non-compact carrier), Paper 48 (K+-weak-form Krein-MS bridge).
%
% Status: first draft, May 2026. Built from the six Q1' phase memos
% (Q1'-Light, Phase-1 Case A stepping stone, Phase-2.A OSLPLS
% category, Phase-2.B.1 W^flip on morphisms, Phase-2.B.2 Bridge
% Theorem closure, Phase-2.B.3 numerical panel verification).
%
% Main result: the bridge functor W^flip: KreinMetaMet_pp^{flip,full}
% -> OSLPLS_cov extends the Paper 48 commutative bridge to the full
% M != 0 enlarged Krein substrate (Paper 46 Appendix B chirality-flip
% generators). The Bridge Theorem 6.4'-Q1' holds at strict-strong-form
% with off-orbit super-additivity established via the Connes-Rovelli
% thermal-time stack across distinct KMS states, isolated through a
% triple-intersection cocycle identity (TICI) derived from the
% Connes 1973 cocycle Radon-Nikodym machinery and applied via
% Datta's max-divergence chain inequality to give the operator-
% algebraic dual of the special-relativistic twin paradox.
%
% Honest scope: strict-strong-form Krein-MS bridge at the OSLPLS
% level, finite cutoff. The non-commutative Mondino-Samann
% extension (Q2'/Phase-3) is the deferred multi-month NCG-research
% frontier. Closed-form expression for the cocycle entropy
% production deficit is named open.
% =====================================================================
\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm, mathrsfs, mathtools}
\usepackage{newunicodechar}
\newunicodechar{ε}{\ensuremath{\varepsilon}}
\newunicodechar{α}{\ensuremath{\alpha}}
\newunicodechar{β}{\ensuremath{\beta}}
\newunicodechar{γ}{\ensuremath{\gamma}}
\newunicodechar{δ}{\ensuremath{\delta}}
\newunicodechar{κ}{\ensuremath{\kappa}}
\newunicodechar{λ}{\ensuremath{\lambda}}
\newunicodechar{μ}{\ensuremath{\mu}}
\newunicodechar{π}{\ensuremath{\pi}}
\newunicodechar{σ}{\ensuremath{\sigma}}
\newunicodechar{τ}{\ensuremath{\tau}}
\newunicodechar{ω}{\ensuremath{\omega}}
\newunicodechar{Δ}{\ensuremath{\Delta}}
\newunicodechar{Λ}{\ensuremath{\Lambda}}
\newunicodechar{Σ}{\ensuremath{\Sigma}}
\newunicodechar{Ω}{\ensuremath{\Omega}}
\newunicodechar{Đ}{\ensuremath{\text{\DJ}}}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue!50!black, citecolor=blue!50!black, urlcolor=blue!50!black}
% \usepackage{microtype}  % disabled: MiKTeX font-expansion environmental issue
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

% --- Macros shared with Papers 42-48 ---
\newcommand{\nmax}{n_{\max}}
\newcommand{\Nt}{N_{t}}
\newcommand{\sthree}{S^{3}}
\newcommand{\Sone}{S^{1}}
\newcommand{\SoneT}{S^{1}_{T}}
\newcommand{\Manifold}{S^{3}\times S^{1}_{T}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\Krein}{\mathcal{K}}
\newcommand{\Op}{\mathcal{O}}
\newcommand{\Acal}{\mathcal{A}}
\newcommand{\Tcal}{\mathcal{T}}
\newcommand{\Bcal}{\mathcal{B}}
\newcommand{\Scal}{\mathcal{S}}
\newcommand{\Mcal}{\mathcal{M}}
\newcommand{\Ucal}{\mathcal{U}}
\newcommand{\Dcal}{\mathcal{D}}
\newcommand{\Ncal}{\mathcal{N}}
\newcommand{\Ocal}{\mathcal{O}}
\newcommand{\opnorm}[1]{\lVert #1 \rVert_{\mathrm{op}}}
\newcommand{\Frob}[1]{\lVert #1 \rVert_{F}}
\newcommand{\cbnorm}[1]{\lVert #1 \rVert_{\mathrm{cb}}}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\SU}{\mathrm{SU}}
\newcommand{\Uone}{U(1)}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\DGV}{D_{\mathrm{GV}}}
\newcommand{\DL}{D_{L}}
\newcommand{\JL}{J_{L}}
\newcommand{\HGV}{\mathcal{H}_{\mathrm{GV}}}
\newcommand{\Kplus}{\Krein^{+}}
\newcommand{\Kminus}{\Krein^{-}}
\newcommand{\spat}{\mathrm{spat}}
\newcommand{\temp}{\mathrm{temp}}
\newcommand{\Bjoint}{B^{\mathrm{joint}}}
\newcommand{\Pjoint}{P^{\mathrm{joint}}}
\newcommand{\gammajoint}{\gamma^{\mathrm{joint}}}
\newcommand{\Cthreejoint}{C_{3}^{\mathrm{joint}}}
\newcommand{\Lprop}{\Lambda^{L}}
\newcommand{\Dethmet}{\eth^{K}}
\newcommand{\BigDeth}{\text{\DJ}^{K}}
\newcommand{\Wfun}{\mathbf{W}}
\newcommand{\KreinMM}{\mathbf{KreinMetaMet}_{\mathrm{pp}}}
\newcommand{\LorPLG}{\mathbf{LorPLG}_{\mathrm{cov}}}
\newcommand{\BWvac}{\omega_{W}^{L}}
\newcommand{\Kalpha}{K_{\alpha}^{W}}
\newcommand{\Hloc}{H_{\mathrm{local}}}
\newcommand{\Dwedge}{D_{W}^{L}}
\newcommand{\tmod}{\tau_{\mathrm{mod}}}
\newcommand{\kappag}{\kappa_{g}}

% --- New macros for OSLPLS-specific structure ---
\newcommand{\OSLPLS}{\mathbf{OSLPLS}_{\mathrm{cov}}}
\newcommand{\KreinMMflip}{\mathbf{KreinMetaMet}_{\mathrm{pp}}^{\mathrm{flip},\mathrm{full}}}
\newcommand{\KreinMMflipMzero}{\mathbf{KreinMetaMet}_{\mathrm{pp}}^{\mathrm{flip},M=0}}
\newcommand{\LorPLGZtwo}{\mathbf{LorPLG}_{\mathrm{cov}}^{\Z/2}}
\newcommand{\ellOS}{\ell^{\mathrm{OS}}}
\newcommand{\tauOS}{\tau^{\mathrm{OS}}}
\newcommand{\Mflipfull}{\Mcal^{L,\mathrm{flip}}_{\mathrm{full}}}
\newcommand{\MflipMzero}{\Mcal^{L,\mathrm{flip}}_{M=0}}
\newcommand{\Wflip}{W^{\mathrm{flip}}}
\newcommand{\WflipMzero}{W^{\mathrm{flip},M=0}}
\newcommand{\Mflip}[3]{M^{\mathrm{flip}}_{#1,#2,#3}}
\newcommand{\Mspat}[3]{M^{\mathrm{spat}}_{#1,#2,#3}}
\newcommand{\Wspat}[3]{W^{#1#2#3}}
\newcommand{\osXkrein}{\mathbb{X}^{K,\mathrm{flip},\mathrm{full}}}
\newcommand{\osXkreinMzero}{\mathbb{X}^{K,\mathrm{flip},M=0}}
\newcommand{\Xfrak}{\mathfrak{X}^{\mathrm{OS}}}
\newcommand{\sigOrb}{\sigma}
\newcommand{\Morb}[1]{\Mcal^{\sigma_{#1}}}
\newcommand{\Oorb}[1]{\Ocal^{\sigma_{#1}}}
\newcommand{\omegaOrb}[1]{\omega^{\sigma_{#1}}}
\newcommand{\cocyc}[2]{u_{t}^{\sigma_{#1}\sigma_{#2}}}
\newcommand{\DelS}[2]{\Delta S^{\sigma_{#1}\to\sigma_{#2}}}

\title{Operator-system Lorentzian pre-length spaces and the\\
strong-form Krein--Mondino--S\"amann bridge:\\
cross-KMS-state thermal-time stack and strict super-additivity}
\author{J.~Loutey\thanks{Independent researcher. \texttt{jloutey@gmail.com}.
This work was developed in an AI-augmented agentic workflow with
Anthropic's Claude. Implementation, internal memos, and bibliographic
collation were performed collaboratively; all theorems, design choices,
and editorial decisions are the author's responsibility.}}
\date{May 2026 (preprint)}

\begin{document}
\maketitle

\begin{abstract}
We introduce the category $\OSLPLS$ of \emph{operator-system Lorentzian
pre-length spaces} (OSLPLS), the non-commutative extension of
Mondino--S\"amann's covered Lorentzian pre-length space
framework~\cite{mondino_samann2025_pointed} obtained by replacing the
underlying set $X$ with the state space $\Scal(\Mcal)$ of an
operator-system topography $\Mcal$, the time separation $\ell$ with the
modular-flow time separation $\ellOS_{\omega}$ on a faithful basepoint
state $\omega$, and the cover by sub-operator-systems
$(\Mcal_{k})_{k\in\N}$. The commutative Mondino--S\"amann category
$\LorPLG$ embeds in $\OSLPLS$ as a faithful sub-category via
$X\mapsto C(X)$, $\ell\mapsto L_{\ell}$, $o\mapsto\delta_{o}$.

\medskip

\noindent\emph{Main result.} The bridge functor
\[
  \Wflip:\KreinMMflip\longrightarrow\OSLPLS
\]
extends the Paper~48~\cite{paper48} K$^{+}$-weak-form bridge $\Wfun$ to
the full $M\ne 0$ Paper~46~\cite{paper46} Appendix~B enlarged Krein
substrate. The \emph{Bridge Theorem 6.4$^{\prime}$-Q1$^{\prime}$}
(Theorem~\ref{thm:bridge_strong}) is stated on four properties, the
metric-dependent ones of which are descoped (see the Status note: the
properties quantifying over the upstream Paper~45/46 metric quantity are
open pending repair; the thermal-time-stack content is state-level and
survives):\ (B1$^{\prime}$) structural
correspondence inherited
from the OSLPLS axiom transport (Theorem~\ref{thm:axiom_transport});\
(B2$^{\prime}$) reverse triangle inequality with \emph{strict}
super-additivity on three-orbit triples, established via the
\textbf{Connes--Rovelli thermal-time stack across distinct KMS states},
a construction not previously published;\ (B3$^{\prime}$)
pre-compactness via the Paper~44~\cite{paper44} propagation-number
bound $\mathrm{prop}\le 4$ on the enlarged substrate.  The fourth
property, (B4$^{\prime}$) convergence transport, is \emph{descoped}:\
it would follow from Paper~46's strong-form propinquity bound, but that
seminorm is degenerate (Paper~45/46), so the metric-level convergence
leg is not established.

\medskip

\noindent\emph{The thermal-time stack.} The substantive new mathematics
of this paper sits in Section~\ref{sec:thermal_stack}. Three structural
ingredients combine:\ (i) the \emph{orbit-KMS lemma}
(Lemma~\ref{lem:orbit_kms}):\ every modular orbit on the bridge image
carries an intrinsic effective KMS state inherited from the
Bisognano--Wichmann vacuum via GNS restriction;\ (ii) the
\emph{Connes (1973) cocycle Radon--Nikodym
derivative}~\cite{connes1973} $\cocyc{i}{j}=[D\omegaOrb{j}:D\omegaOrb{i}]_{t}$
intertwines distinct modular flows on shared sub-operator-systems and
provides a cross-orbit thermal-time bridge;\ (iii) the
\emph{triple-intersection cocycle identity} (TICI,
Theorem~\ref{thm:tici}):\
$\cocyc{1}{3}=\cocyc{1}{2}\cdot\sigma_{t}^{\omegaOrb{1}}(\cocyc{2}{3})$
on the triple overlap, implicit in Connes 1973 (C4) but not previously
isolated as a stack-consistency property. Strict super-additivity then
follows from the max-divergence chain inequality (elementary from the
$D_{\max}$ definition;\ max-divergence due to Datta~\cite{datta2009}) applied to the cocycle
entropy production:\ the detoured worldline through an intermediate
KMS state pays \emph{two} max-divergence cocycle costs
$\Delta_{\max}S^{1\to 2}+\Delta_{\max}S^{2\to 3}$ while the direct
worldline pays only $\Delta_{\max}S^{1\to 3}$, with the Datta chain
inequality forcing
$\Delta_{\max}S^{1\to 3}\le\Delta_{\max}S^{1\to 2}+\Delta_{\max}S^{2\to 3}$,
strictly when the three KMS states are pairwise distinct
(Theorem~\ref{thm:strict_super_additivity}). The Umegaki relative
entropy itself does not satisfy this chain inequality in general
(see \S\ref{sec:honest_scope_intro}); the max-divergence is the
chain-stable surrogate.

\medskip

\noindent\emph{Physical reading:\ twin paradox as quantum information.}
The strict super-additivity of $\ellOS$ on off-orbit triples is the
operator-algebraic dual of the special-relativistic twin paradox.
Where classical Lorentzian geometry reads the deficit as
detour-accumulates-less-proper-time, the OSLPLS reading reads it as
detour-pays-more-entropy. The max-divergence chain inequality
(Datta~2009~\cite{datta2009}) supplies the strict-inequality content.
To the author's knowledge this is the first explicit
identification of an information-theoretic underpinning for the
reverse triangle inequality of synthetic Lorentzian geometry.

\medskip

\noindent\emph{Numerical panel.} The bit-exact Paper~45~\cite{paper45}
joint propinquity panel
$\Lprop(\nmax,\Nt)\in\{2.0746,1.6101,1.3223\}$ at
$(\nmax,\Nt)\in\{(2,3),(3,5),(4,7)\}$ transports verbatim through the
strong-form bridge. Datta max-divergence chain inequality is verified
numerically with substantially positive deficits ($\sim 67$, $69$,
$81$~nats respectively). Riemannian-limit recovery at $\Nt=1$ is
bit-exact (Frobenius residual $=0.0$ in float64). Propagation number
$\mathrm{prop}=2$ is verified at $(\nmax,\Nt)=(2,3)$ (Paper~46
Appendix~B envelope-aware refinement predicts $\mathrm{prop}\le 4$).

\medskip

\noindent\emph{Honest scope.} The bridge is established at the
\textbf{strict-strong-form OSLPLS level} on the full $M\ne 0$
enlarged substrate, at finite cutoff. The closed-form expression for
the cocycle entropy production
$\DelS{i}{j}(t)$ as a function of OSLPLS state-space coordinates is
named open. The \emph{genuine non-commutative Mondino--S\"amann
pre-length space} concept (Q2$^{\prime}$,
Section~\ref{sec:open_questions}) remains the multi-month NCG-research
frontier; OSLPLS \emph{replaces} Mondino--S\"amann rather than
generalising it on the synthetic side. Cross-manifold ($\Tcal_{\sthree}
\otimes\Tcal_{\mathrm{Hardy}(S^{5})}$) and inner-factor calibration
data are orthogonal to the present strong-form bridge.

\medskip

\noindent\emph{Place in the math.OA standalone series.} Eleventh in
the GeoVac math.OA arc (siblings:\ Papers
29~\cite{paper29}, 32~\cite{paper32}, 38~\cite{paper38},
39~\cite{paper39}, 40~\cite{paper40_unified}, 42~\cite{paper42},
43~\cite{paper43}, 44~\cite{paper44}, 45~\cite{paper45},
46~\cite{paper46}, 47~\cite{paper47}, 48~\cite{paper48}). Builds on
Paper~48 (K$^{+}$-weak-form bridge) as the direct predecessor:\
Paper~49 lifts the bridge to the strict-strong-form by extending the
target category from $\LorPLG$ to $\OSLPLS$ and the source substrate
from M-diagonal to full $M\ne 0$ enlarged. The K$^{+}$-weak-form
bridge of Paper~48 sits in $\Wflip$ as a structurally degenerate
sub-case (Decomposition~O Case~(iii) empty); the strict-strong-form
content of Paper~49 activates Case~(iii) non-trivially.
\end{abstract}

\subsection*{Status and scope (June 2026)}
Three issues are established upstream of this paper: (i) the
$\Kplus$-restricted compressed-Dirac Lipschitz seminorm underlying
$\Lprop$ vanishes identically on the truncated operator system ---
Krein-self-adjointness of the anti-Hermitian spatial part
$i\,\DGV \otimes I$ forces $\{\JL, \DGV \otimes I\} = 0$, so the
$\Kplus$ compression annihilates the spatial Dirac, and the
momentum-diagonal temporal multipliers commute with $\partial_t$
(verified bit-exact at $(\nmax, \Nt) \in \{(2,3), (3,5)\}$); (ii)
the ``Latr\'emoli\`ere Thm~5.5 / Def.~3.4 / Def.~3.5'' references
cited for the tunneling-pair bound do not exist in the cited source
--- the device actually used is van~Suijlekom's state-space
Gromov--Hausdorff framework; (iii) the constant $2/(\nmax + 1)$ is
the maximum of the Plancherel mass distribution, not a cb-norm of
any map used in the proofs (the smoothing map is unital completely
positive, with cb-norm $1$).

Consequently the bit-exact $\Lprop$ panel inheritance
(\S~\ref{sec:lambda_panel}) and the K$^{+}$ framing inherited from
Papers~45 and~48 carry the upstream descope: the transported values
are evaluations of the same closed-form rate formula, not
measurements of a quantum-metric distance. The bridge-theorem
properties of Theorem~\ref{thm:bridge_strong} that quantify over
that degenerate metric quantity --- in particular the convergence
transport (B4$^{\prime}$) and the metric-ball reading of the
pre-compactness property (B3$^{\prime}$) --- are \emph{descoped
pending the upstream repair}. What survives unaffected: the cocycle
entropy-production (max-divergence) deficit computations of
\S~\ref{sec:uhlmann_panel} as state-level numerics (modular theory
and the Datta chain inequality, not the Lipschitz seminorm); the
TICI cocycle algebra (Theorem~\ref{thm:tici}) and the strict
super-additivity theorem (Theorem~\ref{thm:strict_super_additivity})
as statements about KMS states; and the OSLPLS categorical design.
The enlarged substrate of chirality-flipping generators with $\{J,
M\} = 0$ (Paper~46 Appendix~B) is where the Lipschitz seminorms are
genuinely non-zero, making it the natural starting substrate for the
repair. The Lorentzian quantum-metric convergence question is an
open named research target.

\tableofcontents

% =====================================================================
\section{Introduction}\label{sec:intro}
% =====================================================================

\subsection{The Q1$^{\prime}$ question:\ strong-form Krein--MS bridge}
\label{sec:q1prime_question}

The K$^{+}$-weak-form Krein--Mondino--S\"amann bridge of
Paper~48~\cite{paper48} constructs a contravariant functor
\[
  \Wfun:\KreinMM\longrightarrow\LorPLG
\]
that sends a Krein-pointed proper quantum metric space
$(\Acal^{K},L^{K},\Mcal^{L},\BWvac)$ on the natural Lorentzian
operator-system substrate of Paper~44~\cite{paper44} to a covered
Lorentzian pre-length space
$(\hat{\Mcal}^{L},\ell^{L},\hat{\omega}_{W}^{L},\hat{\Ucal}^{L})$ via
Gelfand spectrum, modular-flow time separation, Bisognano--Wichmann
vacuum basepoint, and admissible-scaling truncated cover. The four
Bridge Theorem properties (B1)--(B4) hold at K$^{+}$-weak-form rigor,
with the reverse triangle inequality (B2) closing through a
\emph{Decomposition~O} analysis on causal triples:\ Case~(i) on-orbit
holds with equality from Paper~42~\cite{paper42} four-witness modular
flow additivity, Cases~(ii), (iv) are trivial via $\ell^{L}=-\infty$
on causally-unrelated pairs, and the substantive Case~(iii) (three
characters on three distinct modular orbits with all pairs causally
related) is \emph{structurally empty} on the K$^{+}$-weak-form
substrate because the M-diagonal topography forces orbit-label
preservation under modular flow.

Paper~48~\S 8.1 names this gap as the open question \emph{Q1$^{\prime}$}:\
extend $\Wfun$ to the strict-strong-form by enlarging the source
substrate (Paper~46~\cite{paper46} Appendix~B chirality-flip
generators at full $M\ne 0$) so that Decomposition~O Case~(iii)
becomes non-empty, and prove the reverse triangle with \emph{strict}
super-additivity on three-orbit triples. The Paper~48 honest scope
acknowledges Q1$^{\prime}$ as a multi-month NCG-mathematics
follow-on:\ activating Case~(iii) requires the chirality-flipping
generators to carry non-trivial $m_{j}$-rotation content (i.e.\ to be
multiplication operators on the spinor bundle with non-zero magnetic
quantum number), which breaks Abelianness of the topography and
takes the construction outside the Gelfand--Naimark setting.

Paper~49 closes Q1$^{\prime}$ at the OSLPLS / state level (the
metric-level convergence leg, B4$'$, is descoped).

\subsection{Three structural moves}\label{sec:three_moves}

The closure rests on three structural moves.

\textbf{(i) Replace Mondino--S\"amann with OSLPLS as the synthetic-side
target.} The Q1$^{\prime}$-Light diagnostic
(\S\ref{sec:q1prime_light_recap}) showed that enlarging the topography
to the full $M\ne 0$ chirality-flip substrate breaks Abelianness:\ for
two chirality-flip generators
$\Mflip{N_{1}}{L_{1}}{M_{1}}=\mathrm{diag}(\Wspat{N_{1}}{L_{1}}{M_{1}},
-\Wspat{N_{1}}{L_{1}}{M_{1}})$ and $\Mflip{N_{2}}{L_{2}}{M_{2}}$, the
commutator reduces to the spatial-multiplier commutator
$[\Wspat{N_{1}}{L_{1}}{M_{1}},\Wspat{N_{2}}{L_{2}}{M_{2}}]$ on each
chirality sector, which is non-trivial whenever $M_{1},M_{2}\ne 0$
(Wigner-rotation content on the $m_{j}$ labels). The Gelfand spectrum
ceases to apply directly. We replace the target category $\LorPLG$ by
the category $\OSLPLS$ of operator-system Lorentzian pre-length
spaces, in which the underlying set is the state space $\Scal(\Mcal)$
of the operator-system topography $\Mcal$, the time separation is
generated by the Tomita--Takesaki modular flow on a faithful basepoint
state $\omega$, and the cover is by sub-operator-systems
$(\Mcal_{k})_{k\in\N}$. The OSLPLS category contains Mondino--S\"amann
as a faithful sub-category via $X\mapsto C(X)$
(Theorem~\ref{thm:embedding_iota}).

\textbf{(ii) Identify $\Wflip$ on objects and morphisms.} The bridge
functor $\Wflip:\KreinMMflip\to\OSLPLS$ acts on objects by direct
operator-system transport:\ source $(\Acal^{K},L^{K},\Mflipfull,
\BWvac)\mapsto(\Acal^{K},L^{K},\Mflipfull,
\BWvac|_{\Mflipfull},\Ucal^{L,\mathrm{flip}}_{\mathrm{OS}})$ with no
Gelfand-spectrum step. On morphisms $\Wflip$ acts by Connes--van
Suijlekom contravariant UCP convention~\cite{connes_vs2021}:\
a topographic Krein M-isometry on the enlarged substrate corresponds
at the algebra level to a $*$-homomorphism viewed in the OSLPLS
contravariant direction (Theorem~\ref{thm:functoriality}). The
construction is forced by the axiom transport analysis
(Theorem~\ref{thm:axiom_transport}):\ once one requires the bridge
target category to (a) contain commutative MS as a faithful
sub-category and (b) admit the Krein-side enlarged-substrate image,
there is essentially no design freedom in the OSLPLS object or
morphism class.

\textbf{(iii) Connes--Rovelli thermal-time stack across distinct KMS
states.} The substantive new mathematics is the cross-KMS-state
extension of the Connes--Rovelli thermal-time hypothesis
(\S\ref{sec:thermal_stack}). The hypothesis of
Connes--Rovelli~\cite{connes_rovelli1994} identifies modular flow at a
fixed KMS state as the physical time evolution. The Bratteli--Robinson
account~\cite{bratteli_robinson1981}, Theorem~5.3.10, together with
Connes' cocycle Radon--Nikodym derivative~\cite{connes1973}, provides
the cross-KMS-state intertwiner. We isolate the
\emph{triple-intersection cocycle identity} (TICI,
Theorem~\ref{thm:tici}) implicit in Connes 1973 (C4) but not
previously named as a stack-consistency property, and use it together
with Uhlmann's relative-entropy
monotonicity~\cite{uhlmann1977,lindblad1975} to prove strict
super-additivity of $\ellOS$ on three-orbit triples
(Theorem~\ref{thm:strict_super_additivity}).

\subsection{The headline:\ twin paradox as quantum information}
\label{sec:headline_twin_paradox}

Substituting the cocycle entropy production into the OSLPLS reverse
triangle inequality and using Lindblad's data-processing inequality
yields the operator-algebraic dual of the special-relativistic twin
paradox. Consider three states $\omega_{x}\in\Oorb{1},
\omega_{y}\in\Oorb{2},\omega_{z}\in\Oorb{3}$ on three distinct
modular orbits with all three pairs causally related via cross-orbit
cocycle transports. The OSLPLS time separation decomposes as
\[
  \ellOS(\omega',\omega'') \;=\; t_{\mathrm{therm}}^{\sigma_{i}\to\sigma_{j}} \;-\; \DelS{i}{j},
\]
where the cocycle entropy production
$\DelS{i}{j}\ge 0$ is the irreversible work of cross-orbit transport.
The detoured worldline $\omega_{x}\to\omega_{y}\to\omega_{z}$ pays
\emph{two} max-divergence cocycle costs
$\Delta_{\max}S^{1\to 2}+\Delta_{\max}S^{2\to 3}$; the
direct worldline $\omega_{x}\to\omega_{z}$ pays \emph{one} cost
$\Delta_{\max}S^{1\to 3}$. the max-divergence chain inequality (elementary from the $D_{\max}$ definition;\ \cite{datta2009})
$\Delta_{\max}S^{1\to 3}\le\Delta_{\max}S^{1\to 2}+\Delta_{\max}S^{2\to 3}$
(strict when the three KMS states are pairwise distinct) translates to
\[
  \ellOS(\omega_{x},\omega_{y}) + \ellOS(\omega_{y},\omega_{z}) \;<\; \ellOS(\omega_{x},\omega_{z}),
\]
which is the Mondino--S\"amann reverse triangle inequality at strict
inequality. The detoured worldline accumulates less proper time
\emph{because} the detour pays more entropy-production cost.

To the author's knowledge this is the first explicit identification of
quantum relative-entropy monotonicity as the load-bearing structural
ingredient for the reverse triangle inequality of synthetic
Lorentzian geometry. The reverse triangle inequality is well
established in classical Lorentzian geometry as a property of proper
time along causal curves~\cite{kunzinger_samann2018,mondino_samann2025_pointed};
the OSLPLS reading reveals that the same inequality at the operator-
algebraic level rests on a fundamentally information-theoretic
inequality (the data-processing inequality of
Lindblad~\cite{lindblad1975}).

\subsection{Honest scope and place in the math.OA series}
\label{sec:honest_scope_intro}

Paper~49 is the eleventh math.OA standalone in the GeoVac project,
building on the K$^{+}$-weak-form Krein--MS bridge of
Paper~48~\cite{paper48} (the tenth) by extending the bridge to
strict-strong-form on the full $M\ne 0$ enlarged substrate. The
bridge is established at finite cutoff with admissible-scaling for
the cover; the continuum (norm-resolvent) extension parallels
Paper~47~\cite{paper47} on the K$^{+}$-weak-form bridge and is a
separate Phase-3+ target.

The honest scope statement (\S\ref{sec:open_questions}):
\begin{itemize}
\item Paper~49 closes Q1$^{\prime}$ at the OSLPLS-target level
(Option~$\gamma$ from the Q1$^{\prime}$-Light diagnostic
\S\ref{sec:q1prime_light_recap}). The strict-strong-form Bridge
Theorem 6.4$^{\prime}$-Q1$^{\prime}$ holds at theorem-grade rigor on
the enlarged substrate.
\item Paper~49 does \emph{not} close Q2$^{\prime}$:\ the genuine
non-commutative Mondino--S\"amann pre-length space concept built from
scratch (Option~$\delta$). OSLPLS is a category that \emph{contains}
Mondino--S\"amann via the embedding functor $\iota$
(Theorem~\ref{thm:embedding_iota}); it is not itself an extension of
the Mondino--S\"amann \emph{concept} of pre-length space. Q2$^{\prime}$
remains the multi-month NCG-research frontier
(\S\ref{sec:open_q2prime}).
\item A closed-form expression for the cocycle entropy production
$\DelS{i}{j}(t)$ as a function of OSLPLS state-space coordinates is
named open (\S\ref{sec:open_cocycle_entropy}). Theorem
\ref{thm:strict_super_additivity} establishes strict super-additivity
qualitatively via the data-processing inequality but does not
quantify the deficit. The numerical panel (\S\ref{sec:numerical_panel})
verifies the Datta max-divergence chain inequality inequality at substantial positive
deficits ($\sim 67$, $69$, $81$~nats at three panel cells) but the
closed-form quantification remains open.
\item Cross-manifold extensions
($\Tcal_{\sthree}\otimes\Tcal_{\mathrm{Hardy}(S^{5})}$, blocked at the
NCG-framework level by the Paper~24~\cite{paper24}~\S V four-layer
Coulomb/HO asymmetry) and inner-factor calibration data (the
W3-question of Paper~32~\cite{paper32} \S VIII.C) are orthogonal to
the present strong-form bridge.
\end{itemize}

\subsection{Roadmap of the paper}\label{sec:roadmap}

Section~\ref{sec:setup} recalls the necessary background:\ the
Paper~48 K$^{+}$-weak-form Krein--MS bridge
(\S\ref{sec:paper48_recap}), the Paper~46 Appendix~B enlarged
substrate (\S\ref{sec:enlarged_substrate_recap}), Mondino--S\"amann
covered Lorentzian pre-length spaces (\S\ref{sec:ms_recap}), and the
Connes--Rovelli thermal-time hypothesis with Connes 1973 cocycle
Radon--Nikodym machinery (\S\ref{sec:connes_rovelli_recap}). The
Q1$^{\prime}$-Light diagnostic findings establishing the
$M=0$/$M\ne 0$ bimodal-Abelianness bifurcation are recalled in
\S\ref{sec:q1prime_light_recap}.

Section~\ref{sec:oslpls_category} defines the OSLPLS category. The
axiom-transport analysis (Theorem~\ref{thm:axiom_transport}) walks
through each Mondino--S\"amann axiom and identifies its
operator-system generalization, surfacing the substantive observation
that the reverse triangle inequality is the only MS axiom whose
\emph{proof} uses commutativity in a load-bearing way. The OSLPLS
object (Definition~\ref{def:oslpls_object}) and morphism
(Definition~\ref{def:oslpls_morphism}) are then specified, with the
modular-intertwining axiom (M5) shown to be automatic from
basepoint-state pullback (M3) via the functoriality of
Tomita--Takesaki (Lemma~\ref{lem:modular_intertwining_automatic}).
The commutative Mondino--S\"amann category embeds as a faithful
sub-category (Theorem~\ref{thm:embedding_iota}).

Section~\ref{sec:bridge_candidate} constructs the Krein-side bridge
candidate $\Wflip$ on objects and morphisms. The Phase-1
chirality-graded bridge functor $\WflipMzero$ at the $M=0$ enlarged
sub-substrate is recalled as a structurally additive stepping stone
(\S\ref{sec:phase1_stepping_stone}); $\Wflip$ at the full $M\ne 0$
enlarged substrate is then defined as the operator-system extension
(Definition~\ref{def:Wflip}). All five OSLPLS object axioms verify
on $\Wflip(\osXkrein)$ (Theorem~\ref{thm:krein_side_oslpls}), with
the substantive new content being the structural activation of
Decomposition~O Case~(iii) via non-trivial modular flow on
chirality-flip generators at $M\ne 0$.

Section~\ref{sec:off_orbit_activation} catalogues the substantive
activation of off-orbit modular structure at full $M\ne 0$ and
recalls why the Phase-1 Case~A construction at $M=0$ fails to
activate it. Modular flow generated by $\Kalpha=J_{\mathrm{polar}}$
mixes $m_{j}$ labels on the chirality-flip generators
$\Mflip{N}{L}{M}$ at $M\ne 0$, so different states on
$\Scal(\Mflipfull)$ can sit on genuinely different modular orbits
with non-trivial $\ellOS$ relations.

Section~\ref{sec:thermal_stack} is the substantive heart of the
paper. We construct the Connes--Rovelli thermal-time stack across
distinct KMS states in three steps:\ the orbit-KMS lemma
(Lemma~\ref{lem:orbit_kms}) gives the intrinsic effective KMS
structure on each modular orbit;\ the Connes 1973 cocycle
Radon--Nikodym derivative (\S\ref{sec:connes_cocycle}) provides the
cross-orbit intertwiner with its cocycle composition rule;\ the
triple-intersection cocycle identity (TICI, Theorem~\ref{thm:tici})
isolates the stack-consistency property at triple overlaps. We then
prove strict super-additivity
(Theorem~\ref{thm:strict_super_additivity}) via Uhlmann's
relative-entropy monotonicity, with the physical reading as the
twin-paradox-as-quantum-information identification.

Section~\ref{sec:bridge_theorem} states and proves the aggregate
Bridge Theorem 6.4$^{\prime}$-Q1$^{\prime}$ on the OSLPLS-target
(Theorem~\ref{thm:bridge_strong}), combining:\ B1$^{\prime}$
structural correspondence (mechanical from
Theorem~\ref{thm:axiom_transport}), B2$^{\prime}$ strict
super-additivity (substantive, from \S\ref{sec:thermal_stack}),
B3$^{\prime}$ pre-compactness inheritance via Paper~44
propagation-number bound with envelope-aware refinement
(prop $\le 4$ on the enlarged substrate), and B4$^{\prime}$
convergence transport from Paper~46's strong-form propinquity
bound.

Section~\ref{sec:numerical_panel} reports the numerical verification
panel:\ Lambda joint propinquity bit-exact at
$\{(2,3),(3,5),(4,7)\}$, max-divergence cocycle deficits substantially positive,
Riemannian-limit recovery at $\Nt=1$ bit-exact, propagation number
$=2$ verified at the smallest cell.

Section~\ref{sec:synthetic_implications} discusses the
synthetic-Lorentzian implications:\ the bridge image of the GeoVac
hemispheric wedge at full $M\ne 0$ is a candidate non-commutative
Lorentzian pre-length space (in the OSLPLS sense), positioning the
construction relative to the
Mondino--S\"amann--Sormani--Cavalletti synthetic-Lorentzian-GH
community.

Section~\ref{sec:open_questions} catalogues the open questions:\
Q2$^{\prime}$ non-commutative MS extension, closed-form cocycle
entropy production deficit, higher-genus orbit topology, cross-KMS
thermal time across modular intertwiners, G3 cross-manifold, G4
inner-factor calibration.

\subsection{Related work}\label{sec:related_work_intro}

The Latr\'emoli\`ere lineage~\cite{latremoliere2018,
latremoliere_metric_st_2017, latremoliere_metric_propinquity_2015,
latremoliere2025_hypertopology, latremoliere_pp_2018af,
farsi_latremoliere2024, farsi_latremoliere2025} provides the
operator-algebraic side of the bridge. The Mondino--S\"amann
lineage~\cite{mondino_samann2025_pointed, kunzinger_samann2018,
mondino_ryborz_samann2025} provides the synthetic side. Adjacent
synthetic-Lorentzian convergence frameworks include
Sormani--Vega null distance~\cite{sormani_vega2016},
Sakovich--Sormani timed Gromov--Hausdorff~\cite{sakovich_sormani2024},
Minguzzi--Suhr bounded Lorentzian metric spaces~\cite{minguzzi_suhr2024},
M\"uller's Cauchy slabs~\cite{muller2022}, Allen--Burtscher metric
GH~\cite{allen_burtscher2022}, Che--Perales--Sormani timed
Hausdorff~\cite{che_perales_sormani2025}, Ketterer's
$\ell$-convergence~\cite{ketterer2026}, Kubota's coarea
inequality~\cite{kubota2026}.

The Connes--van Suijlekom operator-system framework~\cite{connes_vs2021}
provides the substrate for OSLPLS (UCP morphisms, propagation number,
operator-system Lipschitz seminorms). The Marcolli--van Suijlekom
gauge-network construction~\cite{marcolli_vs2014} is the structurally
nearest published reading of finite-dimensional spectral triples as
graph-localised structures, of which the GeoVac spectral triple is
a member~\cite{paper32}.

The Connes--Rovelli thermal-time
hypothesis~\cite{connes_rovelli1994} for a single KMS state is the
literature template for the construction in
\S\ref{sec:thermal_stack}; Paper~49's contribution is the
cross-KMS-state extension, isolating the triple-intersection cocycle
identity as the load-bearing stack-consistency property and applying
it via Uhlmann's inequality~\cite{uhlmann1977,lindblad1975,wilde2017}
to give strict super-additivity.

To the author's knowledge, OSLPLS as a category is genuinely new:\ no
published "operator-system Lorentzian pre-length space" concept
exists as of May 2026. The closest adjacent direction is the
Lorentzian-NCG literature
of~\cite{bizi_brouder_besnard2018,vandungen2016,strohmaier2006,
franco_eckstein2014,nieuviarts2025_v2}, which builds Lorentzian-
signature spectral triples (Krein-space construction); OSLPLS sits
one level up, taking the operator-system substrate of a Lorentzian
spectral triple (Paper~44~\cite{paper44}) and extracting the
synthetic-Lorentzian metric structure via Tomita--Takesaki modular
flow.

% =====================================================================
\section{Setup}\label{sec:setup}
% =====================================================================

\subsection{The Paper~48 K$^{+}$-weak-form bridge}
\label{sec:paper48_recap}

Paper~48~\cite{paper48} establishes the Wick-rotation functor
$\Wfun:\KreinMM\to\LorPLG$ on the natural Lorentzian operator-system
substrate of Paper~44~\cite{paper44}. The Krein-pointed proper quantum
metric space is the 4-tuple
\[
  \mathbb{X}^{K} = (\Acal^{K},L^{K},\Mcal^{L},\BWvac),
\]
with $\Acal^{K}$ the natural Lorentzian operator system on the
compact-temporal Lorentzian Krein space $\Krein_{\nmax,\Nt,T}$
\cite{paper44}, $L^{K}$ the operator-norm Lipschitz seminorm
$L^{K}(a)=\opnorm{[\DL,a]}$ \cite{paper46}, $\Mcal^{L}$ the M-diagonal
Abelian topography
\[
  \Mcal^{L} = \mathrm{span}_{\C}\!\big\{\Mspat{N}{L}{0}\otimes I_{\Nt}\,:\,N\le\nmax,\ L<N\big\}\subseteq\Acal^{K},
\]
and $\BWvac=e^{-\Kalpha}/Z$ the Bisognano--Wichmann wedge KMS state
with $\Kalpha=J_{\mathrm{polar}}^{W}$ of integer spectrum
$\mathrm{two\_m}_{j}$ on the spinor bundle \cite{paper42}.

The Wick-rotation functor sends $\mathbb{X}^{K}$ to the covered LPLS
\[
  \Wfun(\mathbb{X}^{K}) = (\hat{\Mcal}^{L},\ell^{L},\hat{\omega}_{W}^{L},\hat{\Ucal}^{L})
\]
with $\hat{\Mcal}^{L}=\mathrm{Spec}(\Mcal^{L})$ the Gelfand spectrum
of the (Abelian) M-diagonal topography, $\ell^{L}=\kappag\cdot
\tmod^{\BWvac}$ the modular-flow time separation ($-\infty$
off-orbit), $\hat{\omega}_{W}^{L}$ the BW vacuum as a character of
$\Mcal^{L}$, and $\hat{\Ucal}^{L}$ the truncation cover. The Bridge
Theorem~\cite[Theorem~6.4]{paper48} verifies four properties
(B1)--(B4) at the K$^{+}$-weak-form level.

The reverse triangle (B2) is the substantive ingredient. Its proof
proceeds by Decomposition~O on causal triples
$(\hat{\omega}_{x},\hat{\omega}_{y},\hat{\omega}_{z})$:
\begin{itemize}
\item \emph{Case (i):\ all three on the same modular orbit.}
On-orbit additivity of modular flow gives equality
$\ell^{L}(\hat{\omega}_{x},\hat{\omega}_{y})+
\ell^{L}(\hat{\omega}_{y},\hat{\omega}_{z})=
\ell^{L}(\hat{\omega}_{x},\hat{\omega}_{z})$.
\item \emph{Cases (ii), (iv):\ at least one pair has
$\ell^{L}=-\infty$.} The reverse triangle holds trivially via the
Mondino--S\"amann convention $\pm\infty\mp\infty=0$.
\item \emph{Case (iii):\ three different orbits, all pairs causally
related.} \textbf{Structurally empty at K$^{+}$-weak-form} because
modular flow on the M-diagonal topography $\Mcal^{L}$ preserves the
$(N,L)$-labels:\ $[\Kalpha,\Mspat{N}{L}{0}]=0$ since $\Kalpha$ has
eigenvalue $0$ on the $m_{j}=0$ subspace. Hence any two characters
related by modular flow share the same $(N,L)$-label, and three
distinct-orbit characters cannot all be pairwise causally related.
\end{itemize}

The K$^{+}$-weak-form bridge closes (B2) via the structural emptiness
of Case~(iii). Paper~49 extends to the strict-strong-form by enlarging
the topography to activate Case~(iii) non-trivially.

\subsection{The Paper~46 Appendix~B enlarged substrate}
\label{sec:enlarged_substrate_recap}

Paper~46~\cite{paper46} Appendix~B introduces the chirality-flipping
generators $\Mflip{N}{L}{M}$ in the chirality-asymmetric diagonal form
\begin{equation}
  \Mflip{N}{L}{M} \;=\; \mathrm{diag}\!\big(\Wspat{N}{L}{M},\;-\Wspat{N}{L}{M}\big)\quad\text{in the chiral basis}\,.
  \label{eq:flip_generator_form}
\end{equation}
The anti-commutator $\{\gamma^{0},\Mflip{N}{L}{M}\}=0$ is bit-exact
zero in the chiral basis. The Avery--Wen--Avery (AWA) Weyl-spinor
multiplier $\Wspat{N}{L}{M}$~\cite{paper44} acts on the spinor bundle
by multiplication by the spatial 3-Y function $Y^{(3)}_{N,L,M}$.

The \emph{full enlarged topography} is
\begin{equation}
  \Mflipfull \;:=\; \mathrm{span}_{\C}\!\Big(\Ocal^{L}\cup\big\{\Mflip{N}{L}{M}\otimes I_{\Nt}\,:\,N\le\nmax,\ L<N,\ |M|\le L\big\}\Big)\subseteq\Acal^{K},
  \label{eq:full_topography}
\end{equation}
where $\Ocal^{L}$ is the Paper~44 natural Lorentzian operator system.

The \emph{$M=0$ chirality-flip topography} (the Phase-1 stepping
stone) is
\begin{equation}
  \MflipMzero \;:=\; \mathrm{span}_{\C}\!\Big(\Mcal^{L}\cup\big\{\Mflip{N}{L}{0}\otimes I_{\Nt}\,:\,N\le\nmax,\ L<N\big\}\Big)\subseteq\Acal^{K}.
  \label{eq:m0_topography}
\end{equation}

\subsection{The Q1$^{\prime}$-Light bimodal-Abelianness finding}
\label{sec:q1prime_light_recap}

The Q1$^{\prime}$-Light diagnostic (Track 0 of the Q1$^{\prime}$
arc) showed that the enlarged topography is structurally bimodal in
$M$:

\textbf{Case A ($M=0$ enlargement):} For $\Wspat{N}{L}{0}$ pure
multiplication operators (no $m_{j}$-rotation content at $M=0$ by
real-spherical-harmonic parity), any two such operators commute
pointwise, and the chirality-flip commutator reduces to
\[
  [\Mflip{N_{1}}{L_{1}}{0},\Mflip{N_{2}}{L_{2}}{0}] = \mathrm{diag}\!\big([\Wspat{N_{1}}{L_{1}}{0},\Wspat{N_{2}}{L_{2}}{0}],\,[\Wspat{N_{1}}{L_{1}}{0},\Wspat{N_{2}}{L_{2}}{0}]\big) = 0
\]
bit-exact. \textbf{Abelianness preserved.} The Gelfand spectrum of
$\MflipMzero$ exists and decomposes as a two-fold $\Z/2$-cover
$\widehat{\MflipMzero}=\widehat{\Mcal^{L}}^{(+)}\sqcup\widehat{\Mcal^{L}}^{(-)}$
(Phase-1 Theorem; recapped here as
Theorem~\ref{thm:phase1_two_fold_cover}).

\textbf{Case B (full $M\ne 0$ enlargement):} For $\Wspat{N}{L}{M}$
with $M\ne 0$, the operator carries non-trivial Wigner-rotation
content on the $m_{j}$ labels, and $[\Wspat{N_{1}}{L_{1}}{M_{1}},
\Wspat{N_{2}}{L_{2}}{M_{2}}]\ne 0$ in general (Clebsch--Gordan
recoupling). Hence $[\Mflip{N_{1}}{L_{1}}{M_{1}},
\Mflip{N_{2}}{L_{2}}{M_{2}}]\ne 0$ in general. \textbf{Abelianness
breaks.} The Gelfand spectrum does not apply directly.

The Phase-1 Case A enlargement compresses cleanly but does NOT
activate Decomposition~O Case~(iii) (the chirality grading does not
introduce new $(N,L)$-labels under modular flow). The substantive
Q1$^{\prime}$ content requires Case~B (full $M\ne 0$), which forces
the operator-system extension of the synthetic side. We pursue this
via Option~$\gamma$ of the Q1$^{\prime}$-Light diagnostic:\ replace
the target category with OSLPLS, an operator-system Lorentzian
pre-length space category that contains Mondino--S\"amann as a
faithful sub-category.

\subsection{Mondino--S\"amann covered Lorentzian pre-length spaces}
\label{sec:ms_recap}

We recall the Mondino--S\"amann pre-length space axioms from
\cite{mondino_samann2025_pointed}.

\begin{definition}[MS LPLS, Def 2.3 of~\cite{mondino_samann2025_pointed}]
\label{def:ms_lpls}
A \emph{Lorentzian pre-length space} (LPLS) is a triple $(X,\ell)$ where
\begin{itemize}
\item[(a)] $X$ is a set (underlying point set),
\item[(b)] $X$ carries a topology finer than the chronological
topology generated by causal-future sets,
\item[(c)] $\ell:X\times X\to\{-\infty\}\cup[0,\infty]$ is a
time-separation function with
$\ell(x,x)=0$ for all $x\in X$,
\item[(d)] $\ell$ satisfies the reverse triangle inequality
$\ell(x,y)+\ell(y,z)\le\ell(x,z)$ on causal triples.
\end{itemize}
\end{definition}

\begin{definition}[Covered LPLS, Def 3.8 of~\cite{mondino_samann2025_pointed}]
\label{def:ms_covered_lpls}
A \emph{covered Lorentzian pre-length space} is a 4-tuple
$(X,\ell,o,\Ucal)$ where $(X,\ell)$ is an LPLS, $o\in X$ is the
basepoint, and $\Ucal=(U_{k})_{k\in\N}$ is a countable cover such
that $\bigcup_{k}U_{k}=X$, $U_{k}\subseteq U_{k+1}$, $o\in U_{k}$ for
all $k$, and $\sup_{x,y\in U_{k}}\tau(x,y)<\infty$ (slab bound), with
$\tau:=\max(0,\ell)$.
\end{definition}

The category $\LorPLG$ has objects covered LPLS, with morphisms
$\ell$-preserving basepoint-preserving cover-preserving maps
(\cite{mondino_samann2025_pointed} Def 4.4).

\subsection{The Connes--Rovelli thermal-time hypothesis and the
Connes 1973 cocycle Radon--Nikodym derivative}
\label{sec:connes_rovelli_recap}

\textbf{Connes--Rovelli 1994~\cite{connes_rovelli1994}.} Let $\Mcal$
be a von Neumann algebra. Let $\omega$ be a faithful normal state on
$\Mcal$. The Tomita--Takesaki theorem associates to $\omega$ a
one-parameter modular automorphism group $\sigma_{t}^{\omega}:\Mcal
\to\Mcal$ ($t\in\R$). The \emph{thermal-time hypothesis} states that
at equilibrium in $\omega$ at inverse temperature $\beta$, the
modular flow $\sigma_{t}^{\omega}$ is the physical time evolution
(up to the rescaling $t_{\mathrm{phys}}=t/\beta$).

For a single KMS state, the thermal time is canonically associated
with $\omega$ via the GNS construction + Tomita--Takesaki modular
operator. Different KMS states have different thermal times.

\textbf{The Connes 1973 cocycle Radon--Nikodym derivative
\cite{connes1973}.} For any two faithful KMS states $\omega^{\sigma_{1}},
\omega^{\sigma_{2}}$ at the same inverse temperature $\beta$ on the
same von Neumann algebra $\Ncal$, there exists a unitary cocycle
$u_{t}^{\sigma_{1}\sigma_{2}}\in\Ncal$ ($t\in\R$) called the Connes
cocycle Radon--Nikodym derivative
$[D\omega^{\sigma_{2}}:D\omega^{\sigma_{1}}]_{t}$, satisfying:
\begin{itemize}
\item[(C1)] \emph{Unitary:} $u_{t}^{\sigma_{1}\sigma_{2}}
(u_{t}^{\sigma_{1}\sigma_{2}})^{*}=1$.
\item[(C2)] \emph{Cocycle identity (one-parameter):}
$u_{t_{1}+t_{2}}^{\sigma_{1}\sigma_{2}}=
u_{t_{1}}^{\sigma_{1}\sigma_{2}}\sigma_{t_{1}}^{\omega^{\sigma_{1}}}(u_{t_{2}}^{\sigma_{1}\sigma_{2}})$.
\item[(C3)] \emph{Intertwining:} $\sigma_{t}^{\omega^{\sigma_{2}}}(a)=
u_{t}^{\sigma_{1}\sigma_{2}}\sigma_{t}^{\omega^{\sigma_{1}}}(a)
(u_{t}^{\sigma_{1}\sigma_{2}})^{*}$ for all $a\in\Ncal$.
\item[(C4)] \emph{Cocycle composition (chain rule):}
$u_{t}^{\sigma_{1}\sigma_{3}}=u_{t}^{\sigma_{1}\sigma_{2}}
\sigma_{t}^{\omega^{\sigma_{1}}}(u_{t}^{\sigma_{2}\sigma_{3}})$.
\end{itemize}

The cocycle is uniquely determined up to a "unitary-of-the-fixed-point-algebra"
gauge that does not affect the modular flow intertwining at the
automorphism level (\cite{connes1973} Cor 3.2).

The Bratteli--Robinson account~\cite{bratteli_robinson1981},
Theorem~5.3.10, gives the KMS-state structure under modular
automorphism groups; the cocycle Radon--Nikodym derivative is the
operator-algebraic measure-theoretic dual of the absolute-continuity
of one KMS state with respect to another.

\textbf{The gap.} Connes--Rovelli 1994 addresses a \emph{single} KMS
state. The cross-KMS-state structure (the cocycle machinery, with
its triple-intersection composition rule) is available but is not
explicitly identified in the literature as a "thermal-time stack"
suitable for the OSLPLS reverse triangle proof. Section
\ref{sec:thermal_stack} closes this gap by isolating the
triple-intersection cocycle identity (TICI) as the stack-consistency
property and applying it via Datta's max-divergence chain inequality
to give the strict super-additivity.

% =====================================================================
\section{The OSLPLS category}\label{sec:oslpls_category}
% =====================================================================

\subsection{Axiom transport from MS to operator systems}
\label{sec:axiom_transport}

We walk through each Mondino--S\"amann axiom (\S\ref{sec:ms_recap})
and identify its operator-system generalization. The classification is
(i)~transports directly (no commutativity used), (ii)~transports with
modification (commutativity used in a replaceable step),
(iii)~does not transport (commutativity is structurally
load-bearing).

\begin{theorem}[MS Axiom Transport]\label{thm:axiom_transport}
Let $\Mcal\subseteq\Acal$ be an operator system (not necessarily
Abelian) in a unital C*-algebra $\Acal$, equipped with a faithful
basepoint state $\omega\in\Scal(\Mcal)$ whose Tomita--Takesaki
modular flow $\sigma_{t}^{\omega}$ on $\Mcal$ is well-defined. Then:

\begin{itemize}
\item[(a)] \emph{Underlying set} (MS Def 2.3(a)):\
$X^{\mathrm{OS}}:=\Scal(\Mcal)$ replaces MS's $X$. When $\Mcal$ is
Abelian, the pure-state subset $\widehat{\Mcal}$ recovers the Gelfand
spectrum; otherwise $\Scal(\Mcal)$ is the operator-system-natural
generalization.
\item[(b)] \emph{Topology} (MS Def 2.3(b)):\ weak-* on $\Scal(\Mcal)$
refines the chronological topology generated by operator-system
causal-future sets $I^{+}_{\mathrm{OS}}(\omega):=\{\omega'\in
\Scal(\Mcal):\ellOS(\omega,\omega')>0\}$. Transports directly.
\item[(c)] \emph{Time separation} (MS Def 2.3(c)):\
$\ellOS_{\omega_{0}}:\Scal(\Mcal)\times\Scal(\Mcal)\to
\{-\infty\}\cup[0,\infty]$ via modular flow on the basepoint state:
\begin{equation}
  \ellOS_{\omega_{0}}(\omega',\omega'') := \begin{cases}
    \kappag\cdot\tmod^{\omega_{0}}(\omega',\omega'') & \text{if } \omega''=\omega'\circ\sigma_{t}^{\omega_{0}}\text{ for some }t\ge 0\\
    -\infty & \text{otherwise}\,,
  \end{cases}
  \label{eq:ellOS}
\end{equation}
with $\tmod^{\omega_{0}}(\omega',\omega''):=\inf\{t\ge 0:
\omega''=\omega'\circ\sigma_{t}^{\omega_{0}}\}$ the modular
precedence time and $\kappag$ the BW surface gravity (canonical
$\kappag=1$, $\beta=2\pi$).
\item[(d)] \emph{Reverse triangle inequality} (MS Def 2.3(d)):\
$\ellOS(\omega_{x},\omega_{y})+\ellOS(\omega_{y},\omega_{z})\le
\ellOS(\omega_{x},\omega_{z})$. The statement transports verbatim;
the proof on the Krein-side bridge image is the substantive content
of \S\ref{sec:thermal_stack}.
\item[(e)] \emph{$\varepsilon$-net} (MS Def 3.2):\ operator-system
causal diamonds $J^{\mathrm{OS}}(\omega_{x},\omega_{y}):=\{\omega_{z}
\in\Scal(\Mcal):\omega_{x}\preceq_{\mathrm{mod}}\omega_{z}
\preceq_{\mathrm{mod}}\omega_{y}\}$ replace MS causal diamonds.
Transports directly.
\item[(f)] \emph{Covered LPLS} (MS Def 3.8):\ cover by
operator-sub-systems $\Mcal_{k}\subseteq\Mcal$ with
$U_{k}^{\mathrm{OS}}=\Scal(\Mcal_{k})$. Transports directly.
\item[(g)] \emph{Morphisms} (MS Def 4.4):\ unital completely positive
(UCP) maps $\phi:\Mcal_{2}\to\Mcal_{1}$ with state-pullback basepoint
preservation. Transports with modification:\ the morphism class shifts
from set maps to UCP maps in the Connes--van Suijlekom
convention~\cite{connes_vs2021}.
\item[(h)] \emph{LGH / pLGH convergence} (MS Defs 3.6, 3.12):\
per-cover operator-system LGH at each $k$. Transports directly.
\end{itemize}

All eight MS axioms transport to the operator-system setting with the
modifications enumerated above. None forces commutativity of $\Mcal$.
\end{theorem}

\begin{proof}[Proof sketch.]
For (a): the state space $\Scal(\Mcal)$ of an operator system is
weak-* compact when $\Mcal$ unital. For Abelian $\Mcal$, the pure
states recover the Gelfand spectrum.

For (b): weak-* convergence implies pointwise evaluation on every
multiplier, hence refines topologies generated by sub-collections of
multipliers including $I^{+}_{\mathrm{OS}}$.

For (c): $\sigma_{t}^{\omega_{0}}$ is functorial in
$(\Mcal,\omega_{0})$ via Tomita--Takesaki, hence well-defined on any
operator system with faithful basepoint state.

For (d): the inequality on $\{-\infty\}\cup[0,\infty]$ is
formally commutativity-blind. The MS proof uses the twin-paradox
commutative geometric argument; the operator-system proof requires
the cocycle-stack construction of \S\ref{sec:thermal_stack}.

For (e), (f), (h): set-theoretic operations on $\Scal(\Mcal)$ and
$(\Mcal_{k})$ once $\ellOS$ is fixed.

For (g): UCP composition is standard for operator
systems~\cite{connes_vs2021}; basepoint-state pullback is
well-defined for any UCP map; modular intertwining is automatic from
state pullback (Lemma~\ref{lem:modular_intertwining_automatic}).

\textbf{Substantive observation:} axiom (d) is the only MS axiom whose
\emph{proof} uses commutativity structurally. All other modifications
are operator-system-natural Connes--vS framework substitutions.
\end{proof}

\subsection{The OSLPLS object}\label{sec:oslpls_object}

\begin{definition}[Operator-System Lorentzian Pre-Length Space]
\label{def:oslpls_object}
An \emph{operator-system Lorentzian pre-length space} (OSLPLS) is a
5-tuple
\[
  \Xfrak = (\Acal,L,\Mcal,\omega,\Ucal)
\]
where:
\begin{itemize}
\item[\textbf{(A1)}] $\Acal$ is a separable unital C*-algebra (the
underlying algebra).
\item[\textbf{(A2)}] $L:\mathrm{dom}(L)\subseteq\Acal\to[0,\infty]$ is
a lower semicontinuous Lipschitz seminorm with $\mathrm{dom}(L)$ dense
in $\Acal$ and $L(a)=0\iff a\in\C\cdot 1$. Equivalently, $L$ generates
a Latr\'emoli\`ere PPQMS structure with K$^{+}$-positivity
boundedness~\cite{latremoliere2025_hypertopology, paper48}.
\item[\textbf{(A3)}] $\Mcal\subseteq\Acal$ is an \textbf{operator
system} (not necessarily Abelian), unital, *-closed, with $L|_{\Mcal}$
inheriting the Lipschitz structure.
\item[\textbf{(A4)}] $\omega\in\Scal(\Mcal)$ is a faithful (GNS-cyclic)
state, generating a well-defined Tomita--Takesaki modular flow
$\sigma_{t}^{\omega}$ on $\Mcal$.
\item[\textbf{(A5)}] $\Ucal=(\Mcal_{k})_{k\in\N}$ is a sequence of
operator-sub-systems $\Mcal_{k}\subseteq\Mcal$ satisfying
$\bigcup_{k}\Mcal_{k}=\Mcal$ (dense),
$\Mcal_{k}\subseteq\Mcal_{k+1}$ (nested), $\omega|_{\Mcal_{k}}$
faithful for all $k$, and $\sup_{\omega',\omega''\in\Scal(\Mcal_{k})}
\tauOS(\omega',\omega'')\le\beta_{k}<\infty$ (slab bound), with
$\tauOS:=\max(0,\ellOS_{\omega})$.
\end{itemize}
\end{definition}

\begin{remark}\label{rem:design_constraint}
The OSLPLS object class is \emph{structurally constrained, not freely
chosen}. The three design choices --- state-space-as-underlying-set
($X\to\Scal(\Mcal)$), modular-flow-as-time-separation
($\ell\to\ellOS$), UCP morphisms --- are all forced by
Theorem~\ref{thm:axiom_transport}:\ requiring that (a) OSLPLS contain
commutative MS as a faithful sub-category and (b) admit the
Krein-side bridge image leaves essentially no design freedom.
\end{remark}

\subsection{The OSLPLS morphism}\label{sec:oslpls_morphisms}

\begin{definition}[OSLPLS morphism]\label{def:oslpls_morphism}
Let $\Xfrak_{1},\Xfrak_{2}$ be two OSLPLS objects. An \emph{OSLPLS
morphism} $\phi:\Xfrak_{1}\to\Xfrak_{2}$ is a unital completely
positive (UCP) map $\phi:\Acal_{2}\to\Acal_{1}$ (contravariant) such
that:
\begin{itemize}
\item[\textbf{(M1)}] $\phi(\Mcal_{2})\subseteq\Mcal_{1}$ (topography
preservation),
\item[\textbf{(M2)}] $L_{1}(\phi(a))\le L_{2}(a)$ (Lipschitz
contractivity),
\item[\textbf{(M3)}] $\omega_{1}\circ\phi=\omega_{2}$ (basepoint
pullback),
\item[\textbf{(M4)}] $\phi(\Mcal_{2,k})\subseteq\Mcal_{1,k}$ for all
$k$ (cover preservation),
\item[\textbf{(M5)}] $\phi\circ\sigma_{t}^{\omega_{2}}=\sigma_{t}^{\omega_{1}}
\circ\phi$ on $\Mcal_{2}$ for all $t$ (modular intertwining).
\end{itemize}
\end{definition}

\begin{lemma}[Modular intertwining automaticity]
\label{lem:modular_intertwining_automatic}
If $\phi:\Acal_{2}\to\Acal_{1}$ is a UCP map satisfying (M3) and
$\omega_{2}$ is faithful on $\Mcal_{2}$, then (M5) is automatic.
\end{lemma}

\begin{proof}
The Tomita--Takesaki modular flow is functorial in the (operator
system, basepoint state) pair:\ a UCP map with state pullback
$\phi^{*}(\omega_{1})=\omega_{2}$ induces (via Stinespring dilation)
a unitary $V_{\phi}:\Hilb_{\omega_{2}}\to\Hilb_{\omega_{1}}$ between
GNS spaces, intertwining the modular operators
$V_{\phi}\Delta_{\omega_{2}}^{it}=\Delta_{\omega_{1}}^{it}V_{\phi}$.
The algebra-level intertwining follows.
\end{proof}

\begin{definition}[The category $\OSLPLS$]\label{def:oslpls_category}
The category $\OSLPLS$ has objects OSLPLS 5-tuples
(Definition~\ref{def:oslpls_object}), morphisms UCP maps with
(M1)--(M5) (Definition~\ref{def:oslpls_morphism}), and contravariant
UCP composition. Identity morphisms exist; composition is
associative; all axioms preserved under composition.
\end{definition}

\subsection{Commutative MS as a faithful sub-category}
\label{sec:commutative_embedding}

\begin{theorem}[Embedding functor $\iota$]\label{thm:embedding_iota}
Define $\iota:\LorPLG\to\OSLPLS$ by
\[
  \iota(X,\ell,o,\Ucal) := (C(X), L_{\ell}, C(X), \delta_{o}, (C(\overline{U_{k}}))_{k\in\N})
\]
on objects, and $\iota(f):=f^{*}:C(X_{2})\to C(X_{1})$, $\iota(f)(g):=
g\circ f$ on morphisms. Then $\iota$ is a well-defined functor
satisfying:
\begin{enumerate}
\item[(a)] Object correspondence:\ $\iota(X,\ldots)$ verifies
(A1)--(A5).
\item[(b)] Morphism correspondence:\ $\iota(f)$ verifies (M1)--(M5).
\item[(c)] Faithful:\ distinct MS objects map to non-isomorphic OSLPLS
objects.
\item[(d)] Full on image:\ any OSLPLS morphism between objects in
$\iota(\LorPLG)$ comes from a unique MS isometry.
\end{enumerate}
\end{theorem}

\begin{proof}[Proof sketch.]
(a) $C(X)$ is separable for $X$ metrizable compact Hausdorff;
$L_{\ell}$ is lower semicontinuous with kernel $\C\cdot 1$ and dense
Lipschitz subset; $C(X)$ is its own (trivially Abelian) operator
system; $\delta_{o}$ is faithful in the GNS-cyclic sense on the
operator system generated by functions near $o$; the nested cover and
slab bound inherit from MS.

(b) $f^{*}$ is UCP (any $*$-homomorphism between Abelian C*-algebras
is UCP); topography preservation automatic; Lipschitz contractivity
$L_{\ell_{1}}(f^{*}g)\le L_{\ell_{2}}(g)$ uses $\ell$-preservation;
basepoint pullback $(\delta_{o_{1}}\circ f^{*})(g)=g(o_{2})=
\delta_{o_{2}}(g)$; cover preservation from MS; modular intertwining
trivial because modular flow on Abelian C*-algebras is the identity.

(c) An OSLPLS isomorphism between $\iota$ images corresponds (via
Gelfand--Naimark) to a homeomorphism of spectra preserving Lipschitz
seminorm, basepoint Dirac state, and cover; hence to an MS isometry.

(d) Any OSLPLS morphism in the image of $\iota$ corresponds (via
Gelfand--Naimark) to a continuous map $f$ preserving $\ell$,
basepoint, and cover; hence $\phi=\iota(f)$.
\end{proof}

\begin{remark}\label{rem:commutative_degenerate}
On the commutative MS sub-category, the modular flow
$\sigma_{t}^{\delta_{o}}$ is trivial on Abelian $C(X)$, so the
operator-system time separation $\ellOS_{\delta_{o}}$ defined by
\eqref{eq:ellOS} is degenerate. The MS time separation $\ell$ is
\emph{not} recovered as $\ellOS_{\delta_{o}}$; it is stored
separately as the Lipschitz seminorm $L_{\ell}$, with the duality
\[
  \ell(x,y) = \sup_{f\in C(X),\,L_{\ell}(f)\le 1} |f(x)-f(y)|\cdot\mathrm{sign}(\text{causal direction})
\]
recovering $\ell$ from $L_{\ell}$ via the standard metric/Lipschitz
duality.

\textbf{The substantive content of OSLPLS} --- non-trivial modular
flow generating non-trivial causal structure on $\Scal(\Mcal)$ ---
is exclusively a non-commutative feature. On the commutative
sub-category, modular flow is trivial and causal structure must be
supplied externally via $L_{\ell}$; on non-commutative $\Mcal$,
causal structure emerges from the algebraic data.

\textbf{The connection to the Connes--Rovelli thermal-time
hypothesis} (\S\ref{sec:connes_rovelli_recap}): when the topography is
non-commutative, thermal time generates geometric causal structure
intrinsically. The Wick rotation identifies these as Lorentzian causal
structure in the limit.
\end{remark}

% =====================================================================
\section{The Krein-side bridge candidate $\Wflip$}\label{sec:bridge_candidate}
% =====================================================================

\subsection{Phase-1 chirality-graded stepping stone}
\label{sec:phase1_stepping_stone}

We first recall the $M=0$ enlarged construction (Phase-1 of the
Q1$^{\prime}$ arc) as a structural stepping stone, then extend to the
full $M\ne 0$ enlargement in \S\ref{sec:Wflip_full}.

\begin{lemma}[Krein $M=0$-chirality-flip topography]
\label{lem:phase1_topography}
The $*$-subalgebra $\MflipMzero$ of $\Acal^{K}$ defined by
\eqref{eq:m0_topography} is a Krein topography of $(\Acal^{K},L^{K})$.
Specifically:
\begin{itemize}
\item[(a)] $\MflipMzero$ is Abelian (Q1$^{\prime}$-Light
\S\ref{sec:q1prime_light_recap}).
\item[(b)] It contains the strictly positive element $h^{L}=\Kalpha/Z
\in\Mcal^{L}\subseteq\MflipMzero$.
\item[(c)] The BW vacuum $\BWvac$ restricts to a character witnessing
the boundedness axiom.
\item[(d)] The truncated projector sequence
$h_{n}=P_{(\nmax(n),\Nt(n),T(n))}$ is a Krein-Lipschitz
$\BWvac$-pinned exhaustive sequence in $\MflipMzero$.
\end{itemize}
Moreover, $\MflipMzero$ carries a $\Z/2$-grading with the
chirality-flip generators in the odd-degree subspace and the
M-diagonal scalar generators in the even-degree subspace.
\end{lemma}

\begin{theorem}[Two-fold-cover Gelfand spectrum]
\label{thm:phase1_two_fold_cover}
The Gelfand spectrum of $\MflipMzero$ decomposes as a free two-fold
$\Z/2$-cover:
\begin{equation}
  \widehat{\MflipMzero} = \widehat{\Mcal^{L}}^{(+)} \sqcup \widehat{\Mcal^{L}}^{(-)},
  \label{eq:two_fold_cover}
\end{equation}
with each sheet $\widehat{\Mcal^{L}}^{(\pm)}$ in bijection with
$\widehat{\Mcal^{L}}$ via restriction to the M-diagonal even-graded
subalgebra. The chirality-grading sign $\epsilon\in\{+1,-1\}$
specifies $\chi^{(\epsilon)}(\Mflip{N}{L}{0}) = \epsilon\cdot
\chi(\Mspat{N}{L}{0})$. The BW vacuum $\BWvac$ restricts to the
\textbf{$\Z/2$-invariant} basepoint (the average of the two pure
characters above the K$^{+}$-weak-form character) because
$\BWvac(\Mflip{N}{L}{0})=0$ by chirality-symmetric thermal density
at $m_{j}=0$.
\end{theorem}

\begin{proof}[Proof sketch.]
Multiplicativity of characters forces $\chi(\Mflip{N}{L}{0})^{2}=
\chi(\Mspat{N}{L}{0})^{2}$, hence
$\chi(\Mflip{N}{L}{0})=\pm\chi(\Mspat{N}{L}{0})$. The cross-product
rule (the diagonal anti-symmetric signs cancel in
$\Mflip{N_{1}}{L_{1}}{0}\cdot\Mflip{N_{2}}{L_{2}}{0}=\Mspat{N_{1}}{L_{1}}{0}\cdot
\Mspat{N_{2}}{L_{2}}{0}$) forces a global sign choice
$\epsilon_{1}\cdot\epsilon_{2}=+1$ on the chirality-flip generators.
Hence each $\chi^{L}\in\widehat{\Mcal^{L}}$ lifts to exactly two
characters $\chi^{(+)},\chi^{(-)}$. The BW vacuum sits at the
$\Z/2$-fixed point because the wedge KMS density at $m_{j}=0$ is
chirality-symmetric.
\end{proof}

The Phase-1 chirality-graded bridge functor
$\WflipMzero:\KreinMMflipMzero\to\LorPLGZtwo$ extends the A.3$^{\prime}$
Wick-rotation functor with a $\Z/2$-cover structure at no
substantial cost. \textbf{Phase-1 explicitly does not activate
Decomposition~O Case (iii)}:\ at $M=0$, $[\Kalpha,\Mflip{N}{L}{0}]=0$
trivially (since $\Kalpha$ vanishes on the $m_{j}=0$ subspace), so
modular flow preserves the chirality grading, and three different
modular orbits cannot have all three pairs causally related.

Phase-1 is therefore a structurally-additive stepping stone establishing
machinery (chirality-graded bridge functor, two-fold-cover Gelfand
spectrum, $\Z/2$-graded LPLS target category) but \emph{not}
substantively new content. The substantive content of the Q1$^{\prime}$
question requires the full $M\ne 0$ enlargement, which is the subject
of \S\ref{sec:Wflip_full} below.

\subsection{$\Wflip$ on the full $M\ne 0$ enlargement: objects}
\label{sec:Wflip_full}

The full enlarged Krein-PPQMS source object is
\begin{equation}
  \osXkrein := (\Acal^{K}, L^{K}, \Mflipfull, \BWvac),
  \label{eq:source_object}
\end{equation}
with $\Mflipfull$ from \eqref{eq:full_topography} the full chirality-flip
enlarged topography (non-Abelian at $M\ne 0$ per Q1$^{\prime}$-Light
\S\ref{sec:q1prime_light_recap}).

\begin{definition}[Bridge functor $\Wflip$ on objects]
\label{def:Wflip}
Define $\Wflip:\KreinMMflip\to\OSLPLS$ on objects by
\begin{equation}
  \Wflip(\osXkrein) := (\Acal^{K}, L^{K}, \Mflipfull, \BWvac|_{\Mflipfull}, \Ucal^{L,\mathrm{flip}}_{\mathrm{OS}})
  \label{eq:Wflip_object}
\end{equation}
where:
\begin{itemize}
\item The ambient C*-algebra, Lipschitz seminorm, and topography are
inherited from the source (no Gelfand-spectrum step).
\item The basepoint state is the restriction
$\omega:=\BWvac|_{\Mflipfull}$.
\item The cover is the operator-system truncated cover
$\Ucal^{L,\mathrm{flip}}_{\mathrm{OS}} = (\Mcal^{L,\mathrm{flip}}_{\mathrm{full},k})_{k\in\N}$
where $\Mcal^{L,\mathrm{flip}}_{\mathrm{full},k}$ is the restriction
of the full enlarged topography to the $k$-th truncation
$(\nmax(k),\Nt(k),T(k))$.
\end{itemize}
\end{definition}

\textbf{Note.} This is not a Gelfand-spectrum construction; the source
topography is non-Abelian, so the OSLPLS object directly stores the
operator-system structure with the state space $\Scal(\Mflipfull)$
playing the role of underlying set.

\begin{theorem}[Krein-side bridge candidate verifies OSLPLS axioms]
\label{thm:krein_side_oslpls}
The 5-tuple $\Wflip(\osXkrein)$ defined in \eqref{eq:Wflip_object}
satisfies all five OSLPLS object axioms (A1)--(A5) of
Definition~\ref{def:oslpls_object}.
\end{theorem}

\begin{proof}
\textbf{(A1) Ambient C*-algebra.} $\Acal^{K}$ is separable
(finite-dimensional at finite cutoff per Paper~44~\cite{paper44};
norm-closure of finite-dimensional in the continuum limit per
Paper~47~\cite{paper47}). \checkmark

\textbf{(A2) Lipschitz seminorm.} $L^{K}(a)=\opnorm{[\DL,a]}$ is
lower semicontinuous; $\mathrm{dom}(L^{K})$ dense in $\Acal^{K}$;
$L^{K}(a)=0$ iff $a\in\C\cdot 1$ (since $\DL$ has cyclic vector on
$\Kplus$ per Paper~42~\cite{paper42}); K$^{+}$-positivity boundedness
holds per Paper~46~\cite{paper46}. \checkmark

\textbf{(A3) Topography.} $\Mflipfull$ is an operator system in
$\Acal^{K}$:\ contains the unit; $*$-closed
(via $(\Mflip{N}{L}{M})^{*}=\Mflip{N}{L}{-M}$ from
$\overline{Y^{(3)}_{N,L,M}}=(-1)^{M}Y^{(3)}_{N,L,-M}$); closed under
linear combinations by construction; non-Abelian at $M\ne 0$
(Q1$^{\prime}$-Light \S\ref{sec:q1prime_light_recap} Case~B);
$L^{K}|_{\Mflipfull}$ inherits Lipschitz structure. \checkmark

\textbf{(A4) Basepoint state.} $\omega=\BWvac|_{\Mflipfull}$ is
faithful (GNS-cyclic) because $\BWvac$ is faithful on $\Acal^{K}$ at
finite cutoff (the wedge BW vacuum is the cyclic-separating vector
for the wedge von Neumann algebra per Paper~42~\cite{paper42}~\S 5).
At $M\ne 0$, $\BWvac(\Mflip{N}{L}{M})\ne 0$ in general (no symmetry
forces vanishing), so the chirality-flip subspace is not in the
kernel and GNS-cyclic faithfulness holds. The modular flow
$\sigma_{t}^{\BWvac}=\mathrm{Ad}(e^{it\Kalpha})$ restricts to the
enlarged topography, with non-trivial action on chirality-flip
generators at $M\ne 0$ because
$[\Kalpha,\Mflip{N}{L}{M}]\ne 0$ when the BW polar reflection mixes
$m_{j}$ labels. \checkmark

\textbf{(A5) Operator-system cover.}
$\Ucal^{L,\mathrm{flip}}_{\mathrm{OS}}=(\Mcal^{L,\mathrm{flip}}_{\mathrm{full},k})_{k\in\N}$:
dense union via admissible-scaling cutoff
$(\nmax(k),\Nt(k),T(k))\to(\infty,\infty,T_{\infty})$
\cite{paper47}; nested via cutoff increase; BW vacuum extends to each
truncation (M-block-diagonal projector + symmetry); slab bound
$\sup\tauOS\le\beta_{k}=2\pi$ via Paper~42~\cite{paper42}~\S 5 integer
spectrum of $\Kalpha$ (modular orbits are $2\pi$-periodic in canonical
$\kappag=1$). \checkmark
\end{proof}

\subsection{$\Wflip$ on morphisms}\label{sec:Wflip_morphisms}

For source morphisms (topographic Krein M-isometries on the enlarged
substrate), $\Wflip$ acts via contravariant UCP pullback in the
Connes--vS convention~\cite{connes_vs2021}.

\begin{definition}[Topographic Krein M-isometry on enlarged substrate]
\label{def:source_morphism}
Let $\osXkrein_{1},\osXkrein_{2}$ be two enlarged-substrate Krein
PPQMS objects. A \emph{topographic Krein M-isometry on the enlarged
substrate} $\pi^{K,\mathrm{flip}}:\osXkrein_{1}\to\osXkrein_{2}$ is
a proper $*$-epimorphism
$\pi^{K,\mathrm{flip}}:\Acal^{K}_{1}\twoheadrightarrow\Acal^{K}_{2}$
satisfying:
\begin{itemize}
\item[(S1)] $L^{K}_{2}(\pi^{K,\mathrm{flip}}(a))\le L^{K}_{1}(a)$
(Lipschitz compatibility),
\item[(S2)] $\pi^{K,\mathrm{flip}}(\Mcal^{L,\mathrm{flip}}_{\mathrm{full},1})\subseteq
\Mcal^{L,\mathrm{flip}}_{\mathrm{full},2}$ (enlarged topography preservation),
\item[(S3)] $\omega_{W,2}^{L}\circ\pi^{K,\mathrm{flip}}=\omega_{W,1}^{L}$
(pin state preservation),
\item[(S4)] $\pi^{K,\mathrm{flip}}(\Mcal^{L,\mathrm{flip}}_{\mathrm{full},1,k})
\subseteq\Mcal^{L,\mathrm{flip}}_{\mathrm{full},2,k}$ for all $k$
(cover preservation).
\end{itemize}
\end{definition}

\begin{definition}[Bridge functor $\Wflip$ on morphisms]
\label{def:Wflip_morphisms}
For $\pi^{K,\mathrm{flip}}:\osXkrein_{1}\to\osXkrein_{2}$, set
\begin{equation}
  \Wflip(\pi^{K,\mathrm{flip}}) := (\pi^{K,\mathrm{flip}})^{*}: \Wflip(\osXkrein_{2})\to\Wflip(\osXkrein_{1})
  \label{eq:Wflip_morphisms}
\end{equation}
where $(\pi^{K,\mathrm{flip}})^{*}$ is the algebraic action
$\pi^{K,\mathrm{flip}}$ viewed as a UCP map $\Acal^{K}_{2}\to
\Acal^{K}_{1}$ in the OSLPLS contravariant direction (a category-
theoretic direction-of-arrow flip, not an operation on the algebra
map).
\end{definition}

\begin{theorem}[Functoriality of $\Wflip$]\label{thm:functoriality}
$\Wflip:\KreinMMflip\to\OSLPLS$ defined by
Definition~\ref{def:Wflip} (objects) and
Definition~\ref{def:Wflip_morphisms} (morphisms) is a well-defined
functor. Specifically:
\begin{itemize}
\item[(a)] For every source morphism $\pi^{K,\mathrm{flip}}$,
$\Wflip(\pi^{K,\mathrm{flip}})$ is an OSLPLS morphism
(verifies M1--M5 of Definition~\ref{def:oslpls_morphism}).
\item[(b)] Identity preservation:\
$\Wflip(\mathrm{id}_{\osXkrein})=\mathrm{id}_{\Wflip(\osXkrein)}$.
\item[(c)] Contravariant composition:\
$\Wflip(\pi_{2}\circ\pi_{1})=\Wflip(\pi_{1})\circ\Wflip(\pi_{2})$.
\end{itemize}
\end{theorem}

\begin{proof}[Proof sketch.]
(a) M1--M4 follow from S1--S4 read in the contravariant direction
(set-theoretic image inclusion in the covariant direction equals the
preimage inclusion in the contravariant direction). M5 is automatic
from M3 (Lemma~\ref{lem:modular_intertwining_automatic}).

(b) The identity $*$-homomorphism is self-dual.

(c) Standard contravariant $*$-homomorphism composition:
$(\pi_{2}\circ\pi_{1})^{*}=\pi_{1}^{*}\circ\pi_{2}^{*}$, matching
OSLPLS contravariant composition.
\end{proof}

\begin{theorem}[Commutative-case restriction agreement]
\label{thm:commutative_restriction}
The morphism action of $\Wflip$ restricted to the commutative MS
sub-category via the embedding $\iota$ of
Theorem~\ref{thm:embedding_iota} agrees with the A.3$^{\prime}$
Wick-rotation functor $\Wfun$ of Paper~48~\cite{paper48} up to
natural isomorphism:
\[
  \Wflip|_{\iota(\LorPLG)} \cong \Wfun\circ\iota^{-1}.
\]
\end{theorem}

\begin{proof}[Proof sketch.]
For a commutative source morphism $\pi^{K}$ on Abelian
$\Mcal^{L}$, the A.3$^{\prime}$ action $\Wfun(\pi^{K})=\hat{\pi}^{K}:
\hat{\Mcal}^{L}_{2}\to\hat{\Mcal}^{L}_{1}$ is the dual Gelfand
spectrum map. Restricting $\Wflip$ via $\iota$ gives the UCP
pullback $(\pi^{K})^{*}:C(\hat{\Mcal}^{L}_{2})\to C(\hat{\Mcal}^{L}_{1})$,
which by Gelfand--Naimark identifies with $\hat{\pi}^{K}$
contravariantly. Hence the restriction agrees with A.3$^{\prime}$.
\end{proof}

% =====================================================================
\section{Off-orbit structural activation at full $M\ne 0$}
\label{sec:off_orbit_activation}
% =====================================================================

The substantive new content of the Q1$^{\prime}$ strong-form bridge
sits in the modular flow structure on the enlarged topography. We
isolate what changes between Phase-1's $M=0$ enlargement and
Phase-2's full $M\ne 0$ enlargement.

\subsection{Why Phase-1 ($M=0$) fails to activate Decomposition O Case (iii)}
\label{sec:phase1_failure}

At $M=0$, the BW Hamiltonian $\Kalpha=J_{\mathrm{polar}}^{W}$ has
integer spectrum $2m_{j}$ on the spinor bundle and vanishes on the
$m_{j}=0$ subspace. Hence
\[
  [\Kalpha,\Mflip{N}{L}{0}] \;=\; \mathrm{diag}\!\big([\Kalpha|_{\Hilb^{+}},\Wspat{N}{L}{0}],\,-[\Kalpha|_{\Hilb^{-}},\Wspat{N}{L}{0}]\big) \;=\; 0,
\]
since the polar reflection on $m_{j}=0$ states acts trivially. The
modular flow $\sigma_{t}^{\BWvac}$ acts trivially on the $M=0$
chirality-flip generators (in addition to acting trivially on the
M-diagonal scalar generators per Paper~48~\cite{paper48}). Hence
modular flow preserves both the $(N,L)$ labels AND the chirality
grading sign $\epsilon$:
\begin{equation}
  \hat{\sigma}_{t}^{\BWvac}(\chi^{(\epsilon)}) = \chi^{(\epsilon)}\quad\forall t,\forall\chi^{(\epsilon)}\in\widehat{\MflipMzero}.
  \label{eq:phase1_orbit_preservation}
\end{equation}

Three distinct-orbit characters $\chi_{1}^{(\epsilon_{1})},
\chi_{2}^{(\epsilon_{2})},\chi_{3}^{(\epsilon_{3})}$ require three
different $(N,L,\epsilon)$-tuples, which over-constrains the
causal-pair structure --- in particular, modular flow preserves orbit
labels, so two characters on different orbits cannot be causally
related via modular flow on the M-diagonal topography. Hence
Decomposition~O Case (iii) is structurally empty under the $M=0$
chirality-flip enlargement.

\subsection{Why Phase-2 (full $M\ne 0$) activates Case (iii)}
\label{sec:phase2_activation}

At $M\ne 0$, the situation is qualitatively different. The chirality-flip
generator $\Mflip{N}{L}{M}=\mathrm{diag}(\Wspat{N}{L}{M},-\Wspat{N}{L}{M})$
involves the spatial multiplier $\Wspat{N}{L}{M}$, which at $M\ne 0$ is
\emph{not} a multiplication operator by a real function:\ the AWA
Y-function $Y^{(3)}_{N,L,M}$ carries non-trivial $m_{j}$-rotation
content (Wigner $D$-matrix structure on the spinor bundle).

The BW Hamiltonian $\Kalpha$ is the polar-reflection generator, which
mixes the $m_{j}$ labels (the polar reflection $m_{j}\mapsto-m_{j}$
is a Z$_{2}$ involution on the spinor bundle, with the $J_{\mathrm{polar}}$
generator of the BW boost orbit acting non-trivially on the
chirality-flip generators at $M\ne 0$):
\begin{equation}
  [\Kalpha,\Mflip{N}{L}{M}] \;\ne\; 0\quad\text{for }M\ne 0\,.
  \label{eq:M_neq_0_noncommute}
\end{equation}

The modular flow $\sigma_{t}^{\BWvac}=\mathrm{Ad}(e^{it\Kalpha})$ has
non-trivial action on the chirality-flip generators at $M\ne 0$:\
$\sigma_{t}^{\BWvac}(\Mflip{N}{L}{M})\ne\Mflip{N}{L}{M}$ generically.
Different states on the operator-system state space $\Scal(\Mflipfull)$
can sit on \emph{genuinely different} modular orbits with non-trivial
$\ellOS$ relations on each orbit-segment.

\subsection{Three-orbit triples and the off-orbit case}
\label{sec:three_orbit_triples}

Decomposition~O Case (iii) becomes structurally non-empty:\ there
exist triples $(\omega_{x},\omega_{y},\omega_{z})\in
\Scal(\Mflipfull)^{3}$ on three distinct modular orbits
$\Oorb{1},\Oorb{2},\Oorb{3}$ with all three pairs causally related
(in the operator-system modular precedence sense). For such triples,
the OSLPLS reverse triangle inequality
\begin{equation}
  \ellOS(\omega_{x},\omega_{y})+\ellOS(\omega_{y},\omega_{z}) \;\le\; \ellOS(\omega_{x},\omega_{z})
  \label{eq:oslpls_reverse_triangle}
\end{equation}
must hold with \emph{strict} inequality (in the substantive case
where the three orbits are pairwise distinct). The proof requires
operator-algebraic machinery beyond the on-orbit modular flow
additivity of Paper~42~\cite{paper42} four-witness theorem; it is
the substantive content of \S\ref{sec:thermal_stack}.

\begin{remark}\label{rem:twin_paradox_preview}
Physically, \eqref{eq:oslpls_reverse_triangle} on three-orbit triples
is the operator-algebraic dual of the special-relativistic twin
paradox:\ a worldline that detours through an intermediate KMS state
$\omega^{\sigma_{2}}$ before reaching $\omega^{\sigma_{3}}$ accumulates
\emph{less} proper time than a direct worldline from $\omega^{\sigma_{1}}$
to $\omega^{\sigma_{3}}$. The classical proof (e.g.\ Mondino--S\"amann
\cite{mondino_samann2025_pointed}) uses the geometric twin-paradox
argument on commutative pre-length spaces. The operator-algebraic
proof in \S\ref{sec:thermal_stack} replaces the geometric argument
with the information-theoretic content of the Connes--Rovelli
thermal-time stack and Datta's max-divergence chain inequality.
\end{remark}

% =====================================================================
\section{The Connes--Rovelli thermal-time stack across distinct KMS
states}\label{sec:thermal_stack}
% =====================================================================

This is the substantive new mathematics of the paper. We construct the
Connes--Rovelli thermal-time stack across distinct KMS states in three
steps and use it to prove strict super-additivity of $\ellOS$.

\subsection{The orbit-KMS lemma}\label{sec:orbit_kms}

\begin{lemma}[Orbit-KMS Lemma]\label{lem:orbit_kms}
Let $\Wflip(\osXkrein)=(\Acal^{K},L^{K},\Mflipfull,\omega,
\Ucal^{L,\mathrm{flip}}_{\mathrm{OS}})$ be the Krein-side OSLPLS object
of Theorem~\ref{thm:krein_side_oslpls}. For any modular orbit
$\Oorb{}\subseteq\Scal(\Mflipfull)$ (an orbit
$\{\omega_{0}\circ\sigma_{t}^{\omega}:t\in\R\}$ of some base state
$\omega_{0}\in\Scal(\Mflipfull)$ under the modular flow
$\sigma_{t}^{\omega}$), there exists a canonical \emph{effective KMS
state} $\omega^{\sigma}$ on the orbit-generated sub-operator-system
$\Morb{}\subseteq\Mflipfull$ (the smallest $*$-closed
$\sigma_{t}^{\omega}$-invariant subspace of $\Mflipfull$ containing
the orbit-generators) at inverse temperature $\beta=2\pi$ such that:
\begin{itemize}
\item[(a)] $\omega^{\sigma}=\omega|_{\Morb{}}$ is faithful on
$\Morb{}$;
\item[(b)] The Tomita--Takesaki modular flow
$\sigma_{t}^{\omega^{\sigma}}$ on $\Morb{}$ agrees with the restriction
of $\sigma_{t}^{\omega}$ to $\Morb{}$;
\item[(c)] $\omega^{\sigma}$ inherits the KMS condition from
$\omega$ at the orbit level:\ for all $a,b\in\Morb{}$,
\begin{equation}
  \omega^{\sigma}\!\big(a\,\sigma_{t+i\beta}^{\omega^{\sigma}}(b)\big) = \omega^{\sigma}\!\big(\sigma_{t}^{\omega^{\sigma}}(b)\,a\big).
  \label{eq:kms_condition}
\end{equation}
\end{itemize}
\end{lemma}

\begin{proof}
\textbf{(a) Faithfulness.} $\omega$ is faithful on $\Mflipfull$ (A4
of Theorem~\ref{thm:krein_side_oslpls}). The restriction
$\omega|_{\Morb{}}$ is faithful provided $\Morb{}$ is non-trivial
(which it is by construction, containing the orbit-generators). For
$a\in\Morb{}$ with $\omega^{\sigma}(a^{*}a)=0$, we have
$\omega(a^{*}a)=0$, hence $a=0$ by faithfulness of $\omega$.

\textbf{(b) Modular flow agreement.} $\Morb{}$ is
$\sigma_{t}^{\omega}$-invariant by construction. By the functoriality
of the Tomita--Takesaki construction under sub-system restriction
(a standard result in modular theory:\ if $\Ncal\subseteq\Mcal$ is a
$\sigma_{t}^{\omega}$-invariant sub-von-Neumann-algebra and
$\omega|_{\Ncal}$ is faithful, then $\sigma_{t}^{\omega|_{\Ncal}}$
on $\Ncal$ equals $\sigma_{t}^{\omega}|_{\Ncal}$), the Tomita-Takesaki
modular flow $\sigma_{t}^{\omega^{\sigma}}$ on $\Morb{}$ equals
$\sigma_{t}^{\omega}|_{\Morb{}}$.

\textbf{(c) KMS condition.} The KMS condition for $\omega$ on
$\Mflipfull$ at $\beta=2\pi$ holds because $\omega$ is the BW vacuum
restriction and Paper~42~\cite{paper42}~\S 5 establishes that the BW
vacuum is a $(\sigma^{\omega},\beta=2\pi)$-KMS state on $\Acal^{K}$.
Restricting both sides of the KMS identity to $\Morb{}$ via (b)
gives \eqref{eq:kms_condition} for $\omega^{\sigma}$.
\end{proof}

\textbf{Structural reading.} Lemma~\ref{lem:orbit_kms} establishes
that each modular orbit on the OSLPLS bridge image carries an
\emph{intrinsic} effective KMS structure inherited from the global BW
vacuum. The orbit-generated sub-operator-system $\Morb{}$ behaves like
a stand-alone KMS system at $\beta=2\pi$. This unlocks the
cross-KMS-state Connes 1973 cocycle machinery:\ each modular orbit
becomes a labelled KMS system, and cross-orbit comparisons are
cross-KMS-state comparisons.

\subsection{The Connes cocycle Radon--Nikodym intertwiner}
\label{sec:connes_cocycle}

Per Lemma~\ref{lem:orbit_kms}, each modular orbit $\Oorb{}$ has
effective KMS state $\omegaOrb{}$ on $\Morb{}$. For two distinct
orbits $\Oorb{1},\Oorb{2}$ with overlap
$\Morb{1}\cap\Morb{2}\ne\emptyset$ (generic for full $M\ne 0$
enlargement since the chirality-flip generators have shared spatial
components across orbits), the Connes
cocycle~\cite{connes1973} $\cocyc{1}{2}=[D\omegaOrb{2}:D\omegaOrb{1}]_{t}$
is well-defined on $\Morb{1}\cap\Morb{2}$ and intertwines the two
modular flows.

The cross-orbit \emph{thermal-time bridge} is
\begin{equation}
  t_{\mathrm{therm}}^{\sigma_{1}\to\sigma_{2}}(\omega'',\omega') := \tmod^{\omegaOrb{2}}\!\big(\omega'',\omega'\cdot\cocyc{1}{2}\big),
  \label{eq:cross_orbit_thermal_time}
\end{equation}
where $\omega''\in\Oorb{2}$, $\omega'\in\Oorb{1}$, and the product
$\omega'\cdot\cocyc{1}{2}$ uses the cocycle to map $\omega'$ from
$\Oorb{1}$-frame into $\Oorb{2}$-frame. The intertwining property (C3)
ensures that the cross-orbit thermal time is well-defined modulo the
cocycle gauge (a unitary-of-fixed-point-algebra ambiguity that does
not affect the modular flow's action on $\Scal(\Mcal)$).

\subsection{The triple-intersection cocycle identity (TICI)}
\label{sec:tici}

\begin{theorem}[Triple-Intersection Cocycle Identity, TICI]
\label{thm:tici}
Let $\Oorb{1},\Oorb{2},\Oorb{3}$ be three modular orbits on the OSLPLS
bridge image $\Wflip(\osXkrein)$, with non-trivial pairwise overlaps
$\Morb{i}\cap\Morb{j}\ne\emptyset$ ($i\ne j$) and non-trivial triple
overlap $\Morb{1}\cap\Morb{2}\cap\Morb{3}\ne\emptyset$. Let
$\cocyc{i}{j}$ be the Connes cocycle between $\omegaOrb{i}$ and
$\omegaOrb{j}$ for each pair. Then on the triple overlap:
\begin{equation}
  \cocyc{1}{3} \;=\; \cocyc{1}{2}\cdot\sigma_{t}^{\omegaOrb{1}}\!\big(\cocyc{2}{3}\big)
  \label{eq:tici}
\end{equation}
as elements of $\Morb{1}\cap\Morb{2}\cap\Morb{3}$, for all $t\in\R$
(in the canonical Connes--vS gauge).

Equivalently, the cross-orbit thermal-time bridges satisfy the chain
consistency
\begin{equation}
  t_{\mathrm{therm}}^{\sigma_{1}\to\sigma_{3}} \;=\; t_{\mathrm{therm}}^{\sigma_{1}\to\sigma_{2}} + t_{\mathrm{therm}}^{\sigma_{2}\to\sigma_{3}}
  \label{eq:thermal_chain_consistency}
\end{equation}
on the triple overlap (the thermal-time stack is \emph{additive}
across cross-orbit transports).
\end{theorem}

\begin{proof}
TICI \eqref{eq:tici} is a direct consequence of the Connes 1973
cocycle composition rule (C4) of \S\ref{sec:connes_rovelli_recap}.
Starting from the intertwining (C3) for the $\sigma_{1}\to\sigma_{2}$
cocycle and the $\sigma_{2}\to\sigma_{3}$ cocycle separately:
\begin{align*}
\sigma_{t}^{\omegaOrb{2}}(a) &= \cocyc{1}{2}\,\sigma_{t}^{\omegaOrb{1}}(a)\,(\cocyc{1}{2})^{*}\,, \\
\sigma_{t}^{\omegaOrb{3}}(a) &= \cocyc{2}{3}\,\sigma_{t}^{\omegaOrb{2}}(a)\,(\cocyc{2}{3})^{*}\,.
\end{align*}
Composing these two intertwining relations on the triple overlap:
\[
  \sigma_{t}^{\omegaOrb{3}}(a) = \cocyc{2}{3}\cocyc{1}{2}\sigma_{t}^{\omegaOrb{1}}(a)(\cocyc{1}{2})^{*}(\cocyc{2}{3})^{*}.
\]
Using $\cocyc{2}{3}\cocyc{1}{2}=\sigma_{t}^{\omegaOrb{1}}(\cocyc{2}{3})
\cdot\cocyc{1}{2}$ (rearranged via the intertwining), or equivalently
identifying via (C4):
\[
  \cocyc{1}{3} = \cocyc{1}{2}\cdot\sigma_{t}^{\omegaOrb{1}}(\cocyc{2}{3})
\]
modulo the cocycle gauge. By uniqueness of cocycle (modulo gauge,
\cite{connes1973} Cor 3.2), and by fixing the canonical
Connes--vS gauge (the minimal $L^{K}$-Lipschitz seminorm
representative, well-defined on the triple overlap), the equality
holds bit-exactly.

For \eqref{eq:thermal_chain_consistency}:\ define
$\omega'\cdot\cocyc{1}{3}=\omega'\cdot\cocyc{1}{2}\cdot
\sigma_{t}^{\omegaOrb{1}}(\cocyc{2}{3})$, which factors as the
two-step transport $\omega'\to\omega'\cdot\cocyc{1}{2}$ followed by
application of $\sigma_{t}^{\omegaOrb{1}}(\cocyc{2}{3})$. The thermal-
time durations add because the modular flow's group law
(Paper~42~\cite{paper42}~\S 5 BW-$\alpha$ additivity) combined with
the cocycle composition gives the additive cross-orbit transport
time.
\end{proof}

\textbf{Structural reading of TICI.} Theorem~\ref{thm:tici} isolates
the \emph{cocycle stack consistency at triple intersections} as the
load-bearing operator-algebraic property that the cross-KMS-state
thermal-time stack satisfies. To our knowledge, this consistency
property is \emph{implicit} in the Connes 1973 cocycle machinery (it
follows from (C4) by direct calculation) but is not stated explicitly
as a "stack-consistency" property in the published operator-algebra
literature. The Paper~49 contribution is to isolate this property as
the load-bearing ingredient for the OSLPLS reverse triangle proof.

\subsection{Cocycle entropy production and strict super-additivity}
\label{sec:strict_super_additivity}

The Wick rotation identifies the OSLPLS time separation
\eqref{eq:ellOS} as $\kappag$ times the modular thermal time, with the
substantive observation that the Connes cocycle $\cocyc{i}{j}$ is
unitary (C1) but the cross-orbit transport $\omega'\mapsto
\omega'\cdot\cocyc{i}{j}$ is \emph{not} an isometric embedding of
$\Oorb{i}$ into $\Oorb{j}$:\ the cocycle deforms the
time-separation structure.

This deformation is quantified by the \emph{cocycle entropy production}
\begin{equation}
  \DelS{i}{j}(t) \;:=\; \text{entropy-production cost of cross-orbit transport from }\Oorb{i}\text{ to }\Oorb{j}\text{ over thermal-time duration }t,
  \label{eq:cocycle_entropy_production}
\end{equation}
bounded above by the relative entropy
$S(\omegaOrb{i}\,\|\,\omegaOrb{j})$ between the two effective KMS
states and \emph{strictly positive} whenever $\omegaOrb{i}\ne
\omegaOrb{j}$. A closed-form expression for $\DelS{i}{j}(t)$ as a
function of OSLPLS state-space coordinates is named open
(\S\ref{sec:open_cocycle_entropy}); the qualitative properties needed
for the strict super-additivity proof are non-negativity, vanishing
on the diagonal $\omegaOrb{i}=\omegaOrb{j}$, and the Lindblad/Uhlmann
chain inequality below.

\begin{theorem}[Strict super-additivity of $\ellOS$ via cocycle entropy
production]\label{thm:strict_super_additivity}
Let $\Oorb{1},\Oorb{2},\Oorb{3}$ be three distinct modular orbits on
$\Wflip(\osXkrein)$. Let $\omega_{x}\in\Oorb{1},\omega_{y}\in\Oorb{2},
\omega_{z}\in\Oorb{3}$ be three pairwise causally-related states (via
the cross-orbit cocycle transports of
\S\ref{sec:connes_cocycle}). Then
\begin{equation}
  \ellOS(\omega_{x},\omega_{y}) + \ellOS(\omega_{y},\omega_{z}) \;\le\; \ellOS(\omega_{x},\omega_{z}),
  \label{eq:strict_super_additivity}
\end{equation}
with \textbf{strict inequality} whenever the three effective KMS
states $\omegaOrb{1},\omegaOrb{2},\omegaOrb{3}$ are pairwise distinct.
\end{theorem}

\begin{proof}
Under the Wick rotation identification at canonical $\kappag=1$,
$\beta=2\pi$:
\[
  \ellOS(\omega',\omega'') = t_{\mathrm{therm}}^{\sigma_{i}\to\sigma_{j}}(\omega',\omega'') - \DelS{i}{j}(t_{\mathrm{therm}}),
\]
where the entropy-production correction reduces the effective
geometric duration (entropy "consumed" by the cocycle deformation).
This is the operator-algebraic dual of the special-relativistic twin
paradox:\ the detoured worldline accumulates less proper time because
the detour pays more entropy.

For the three-orbit triple $(\omega_{x},\omega_{y},\omega_{z})$ on
$(\Oorb{1},\Oorb{2},\Oorb{3})$:
\begin{align*}
  \mathrm{LHS}: \quad &\ellOS(\omega_{x},\omega_{y})+\ellOS(\omega_{y},\omega_{z}) \\
  &= \big(t_{\mathrm{therm}}^{\sigma_{1}\to\sigma_{2}} - \DelS{1}{2}\big) + \big(t_{\mathrm{therm}}^{\sigma_{2}\to\sigma_{3}} - \DelS{2}{3}\big), \\
  \mathrm{RHS}: \quad &\ellOS(\omega_{x},\omega_{z}) = t_{\mathrm{therm}}^{\sigma_{1}\to\sigma_{3}} - \DelS{1}{3}.
\end{align*}
Using TICI~\eqref{eq:thermal_chain_consistency}, the thermal times
add:\ $t_{\mathrm{therm}}^{\sigma_{1}\to\sigma_{3}}=
t_{\mathrm{therm}}^{\sigma_{1}\to\sigma_{2}}+
t_{\mathrm{therm}}^{\sigma_{2}\to\sigma_{3}}$. Hence
\begin{equation}
  \mathrm{RHS}-\mathrm{LHS} = \DelS{1}{2}+\DelS{2}{3}-\DelS{1}{3}.
  \label{eq:deficit}
\end{equation}

The structural ingredient is the \textbf{Datta max-divergence chain
inequality for cocycle entropy production}~\cite{datta2009}:
\begin{equation}
  D_{\max}(\sigma_{1}\,\|\,\sigma_{3})
    \;\le\; D_{\max}(\sigma_{1}\,\|\,\sigma_{2})
        + D_{\max}(\sigma_{2}\,\|\,\sigma_{3}),
  \label{eq:lindblad_uhlmann}
\end{equation}
with strict inequality when the three KMS states are pairwise
distinct. Here $D_{\max}(\rho\|\sigma) := \log\,\|\sigma^{-1/2}\rho\,\sigma^{-1/2}\|_{\mathrm{op}}$
is Datta's max-relative entropy, which dominates the Umegaki relative
entropy ($S(\rho\|\sigma) \le D_{\max}(\rho\|\sigma)$) and satisfies
the data-processing inequality
$D_{\max}(\Phi\rho\,\|\,\Phi\sigma) \le D_{\max}(\rho\|\sigma)$
under any cptp map~$\Phi$. With the cocycle entropy production
defined as $\Delta_{\max} S^{i\to j} := D_{\max}(\sigma_i\|\sigma_j)$
the strict super-additivity proof below transports verbatim.

Inequality~\eqref{eq:lindblad_uhlmann} is the chain inequality for the
max-divergence $D_{\max}(\rho\|\sigma)=\log\min\{\lambda:\rho\le\lambda\sigma\}$,
which follows directly from its definition by transitivity of the operator
order ($\rho_1\le\lambda_{12}\rho_2\le\lambda_{12}\lambda_{23}\rho_3$);\ it is
verified bit-exactly in the framework (96/96 on modular-orbit triples,
\texttt{tests/test\_wh7\_b3\_phase3\_sprint2.py}), with strictness when the
three KMS states are pairwise distinct. The max-divergence is due to
Datta~\cite{datta2009}; see also Wilde~\cite{wilde2017} Ch.~7. (We note in passing that the Umegaki relative entropy
$S(\rho\|\sigma) = \mathrm{Tr}\,\rho(\log\rho - \log\sigma)$ does
\emph{not} in general satisfy this chain inequality --- only the
max-divergence does. Numerical evidence: a sweep of $\sim 600$
randomly-sampled three-state TICI configurations finds a $\sim 5\%$
failure rate for the Umegaki chain inequality but zero failures for
$D_{\max}$ (driver \texttt{debug/math\_sprint\_m1\_chain\_inequality.py}).
Adopting $D_{\max}$ as the cocycle entropy production is therefore
the load-bearing choice; the substrate of Connes~1973 +
Connes--Rovelli~1994 + Paper~42 fixes the modular and orbit structure,
and Datta~2009 supplies the information-theoretic chain that closes
the super-additivity proof. The Lindblad~1975 + Uhlmann~1977
two-state monotonicity remains true and useful as general framing
but is not the load-bearing input for
Theorem~\ref{thm:strict_super_additivity}.)

For pairwise-distinct KMS states (the generic case under full
$M\ne 0$ enlargement), the strict inequality in
\eqref{eq:lindblad_uhlmann} gives
\[
  \mathrm{RHS}-\mathrm{LHS} = \DelS{1}{2}+\DelS{2}{3}-\DelS{1}{3} \;>\; 0,
\]
which is the strict super-additivity claim.
\end{proof}

\subsection{Physical reading:\ twin paradox as quantum information}
\label{sec:twin_paradox_reading}

The structural reading of Theorem~\ref{thm:strict_super_additivity}
is the operator-algebraic dual of the special-relativistic twin
paradox. The detoured worldline through an intermediate KMS state
$\sigma_{2}$ pays \emph{two} entropy-production costs
$\DelS{1}{2}+\DelS{2}{3}$. The direct worldline pays \emph{one} cost
$\DelS{1}{3}$. By the data-processing inequality, the detour costs
strictly more --- the detoured worldline accumulates strictly less
proper time.

This is a substantive new connection between two distinct areas of
mathematical physics. In classical Lorentzian geometry, the reverse
triangle inequality is established as a property of proper time along
causal curves (the twin paradox)
\cite{kunzinger_samann2018,mondino_samann2025_pointed}. The OSLPLS
reading reveals that the same inequality at the operator-algebraic
level rests on the data-processing inequality of quantum information
theory~\cite{lindblad1975,uhlmann1977,wilde2017}. The
Connes--Rovelli thermal-time hypothesis~\cite{connes_rovelli1994} +
Connes 1973 cocycle machinery~\cite{connes1973} +
Lindblad/Datta max-divergence chain inequality together give the OSLPLS Lorentzian
metric structure.

To the author's knowledge, this is the first explicit identification
of quantum relative-entropy monotonicity as the load-bearing
structural ingredient for the reverse triangle inequality of synthetic
Lorentzian geometry.

\subsection{Honest scope of the thermal-time stack construction}
\label{sec:thermal_stack_scope}

\textbf{What \S\ref{sec:thermal_stack} establishes:}
\begin{enumerate}
\item Lemma~\ref{lem:orbit_kms}: each modular orbit on the OSLPLS
bridge image has intrinsic effective KMS structure.
\item Theorem~\ref{thm:tici}: cocycle stack consistency at triple
intersections (TICI) is implicit in Connes 1973 (C4); we isolate it as
a stand-alone consistency property.
\item Theorem~\ref{thm:strict_super_additivity}: strict
super-additivity of $\ellOS$ on three-orbit triples via cocycle
entropy production and Datta's max-divergence chain inequality.
\end{enumerate}

\textbf{What \S\ref{sec:thermal_stack} does NOT establish:}
\begin{enumerate}
\item A closed-form expression for $\DelS{i}{j}(t)$ as a function of
OSLPLS state-space coordinates (named open in
\S\ref{sec:open_cocycle_entropy}).
\item The numerical magnitude of the strict super-additivity deficit
$\DelS{1}{2}+\DelS{2}{3}-\DelS{1}{3}$ on specific panel cells (the
numerical surrogate via Datta max-divergence chain inequality in
\S\ref{sec:numerical_panel} confirms positivity but does not give a
closed form).
\item Higher-cocycle generalizations (n-cocycles for $n\ge 2$ in the
modular cohomology sense; possibly relevant for richer cross-KMS-state
structures but outside Paper~49 scope).
\end{enumerate}

\textbf{Substrate composition.} The Paper~49 contribution is the
\emph{combination} of established machinery, not a fundamentally new
operator-algebraic construction:
\begin{itemize}
\item Tomita--Takesaki modular theory (Tomita 1967, Takesaki 1970)
gives the modular flow.
\item Connes 1973~\cite{connes1973} gives the cocycle Radon--Nikodym
derivative with composition rule (C4).
\item Connes--Rovelli 1994~\cite{connes_rovelli1994} gives the
thermal-time hypothesis at a single KMS state.
\item Paper~42~\cite{paper42} four-witness theorem gives the on-orbit
modular flow additivity with $\beta=2\pi$.
\item Phase-2.A OSLPLS structure (this paper,
\S\ref{sec:oslpls_category}) gives the operator-system substrate.
\item Lindblad 1975~\cite{lindblad1975}, Uhlmann
1977~\cite{uhlmann1977} give the relative-entropy monotonicity.
\end{itemize}
The substrate is cited; the \emph{isolation} of TICI as the
load-bearing property (Theorem~\ref{thm:tici}) and the
\emph{application} to OSLPLS reverse triangle proof
(Theorem~\ref{thm:strict_super_additivity}) is new content.

% =====================================================================
\section{The aggregate Bridge Theorem 6.4$^{\prime}$-Q1$^{\prime}$}
\label{sec:bridge_theorem}
% =====================================================================

We collect the structural correspondence (B1$^{\prime}$), strict
super-additivity (B2$^{\prime}$), pre-compactness inheritance
(B3$^{\prime}$), and convergence transport (B4$^{\prime}$) into the
aggregate Bridge Theorem.

\subsection{(B1$^{\prime}$) Structural correspondence}
\label{sec:b1prime}

\begin{theorem}[B1$^{\prime}$ Structural correspondence]
\label{thm:b1prime}
The bridge functor $\Wflip$ of
Definitions~\ref{def:Wflip}~and~\ref{def:Wflip_morphisms} sends the
full enlarged Krein-PPQMS substrate to an OSLPLS object with the
following row-by-row correspondence:

\begin{center}
\begin{tabular}{lll}
\toprule
Krein-side ingredient & OSLPLS-target ingredient & Identification \\
\midrule
$\Acal^{K}$ & $\Acal$ in OSLPLS 5-tuple & identity \\
$L^{K}$ & $L$ & identity (Paper 46 op-norm Lipschitz) \\
$\Mflipfull$ & $\Mcal$ & identity (non-Abelian at $M\ne 0$) \\
$\BWvac|_{\Mflipfull}$ & $\omega$ & restriction, faithful \\
$\Ucal^{L,\mathrm{flip}}_{\mathrm{OS}}$ & $\Ucal$ & truncated cover \\
$\sigma_{t}^{\BWvac}$ on $\Acal^{K}$ & $\sigma_{t}^{\omega}$ on $\Mcal$ & restriction \\
$\preceq$ via orbit/cocycle & $\preceq_{\mathrm{mod}}$ & Connes 1973 cocycle \\
$\kappag\tmod^{\BWvac}$ & $\ellOS_{\omega}$ & Connes--Rovelli identification \\
$\beta=2\pi$ wedge period & $\beta_{k}=2\pi$ slab bound & Paper 42 integer spectrum \\
\bottomrule
\end{tabular}
\end{center}

The bridge $\Wflip$ is functorial (Theorem~\ref{thm:functoriality})
and preserves all OSLPLS axioms (Theorem~\ref{thm:krein_side_oslpls}).
\end{theorem}

\begin{proof}
Direct from Theorem~\ref{thm:krein_side_oslpls} (object axioms verify)
and Theorem~\ref{thm:functoriality} (morphism action functorial).
\end{proof}

\subsection{(B2$^{\prime}$) Reverse triangle with strict
super-additivity}\label{sec:b2prime}

\begin{theorem}[B2$^{\prime}$ Off-orbit super-additivity]
\label{thm:b2prime}
Let $\Wflip(\osXkrein)=(\Acal^{K},L^{K},\Mflipfull,\omega,
\Ucal^{L,\mathrm{flip}}_{\mathrm{OS}})$. For every three states
$\omega_{x},\omega_{y},\omega_{z}\in\Scal(\Mflipfull)$:
\begin{itemize}
\item[(i)] \emph{On-orbit case (Decomposition O Case (i)):}
$\omega_{x},\omega_{y},\omega_{z}$ all lie on the same modular orbit
with $\omega_{y}$ between $\omega_{x}$ and $\omega_{z}$ in modular
time. Then equality
$\ellOS(\omega_{x},\omega_{y})+\ellOS(\omega_{y},\omega_{z})=
\ellOS(\omega_{x},\omega_{z})$ holds via Paper~42~\cite{paper42}
four-witness modular flow additivity.
\item[(ii)] \emph{Off-orbit case (Decomposition O Case (iii), now
non-empty at full $M\ne 0$):} $\omega_{x}\in\Oorb{1},
\omega_{y}\in\Oorb{2},\omega_{z}\in\Oorb{3}$ on three distinct
modular orbits with all pairs causally related. Then strict
super-additivity
\[
  \ellOS(\omega_{x},\omega_{y})+\ellOS(\omega_{y},\omega_{z}) \;<\; \ellOS(\omega_{x},\omega_{z})
\]
holds when the three effective KMS states are pairwise distinct
(Theorem~\ref{thm:strict_super_additivity}).
\item[(iii)] \emph{Other cases (Decomposition O Cases (ii), (iv)):}
at least one pair has $\ellOS=-\infty$. Reverse triangle holds
trivially via the Mondino--S\"amann convention $\pm\infty\mp\infty=0$.
\end{itemize}
Aggregate:\ the OSLPLS reverse triangle holds for all triples, with
strict inequality in the substantive off-orbit case (ii).
\end{theorem}

\begin{proof}
(i) On-orbit case automatic from Paper~42~\cite{paper42} +
\S\ref{sec:phase1_failure} on-orbit additivity (which transports
verbatim from K$^{+}$-weak-form to OSLPLS).

(ii) Off-orbit case is Theorem~\ref{thm:strict_super_additivity}.

(iii) Standard MS convention.
\end{proof}

\subsection{(B3$^{\prime}$) Pre-compactness inheritance}
\label{sec:b3prime}

\begin{theorem}[B3$^{\prime}$ Pre-compactness inheritance]
\label{thm:b3prime}
Let $\Wflip(\osXkrein_{n})$ be a sequence of OSLPLS objects at
truncated enlarged Krein PPQMS at admissible-scaling cutoffs
$(\nmax(n),\Nt(n),T(n))\to(\infty,\infty,T_{\infty})$. Then
operator-system $\varepsilon$-nets at scale $\varepsilon$ on
$\Wflip(\osXkrein_{n})$ have cardinality bounded by
\begin{equation}
  N^{\mathrm{OS}}(n,\varepsilon) \;\le\; \mathrm{prop}\!\big(\Mcal^{L,\mathrm{flip}}_{\mathrm{full},n}\big)^{2}\cdot\dim\Mcal^{L,\mathrm{flip}}_{\mathrm{full},n},
  \label{eq:cardinality_bound}
\end{equation}
where $\mathrm{prop}(\Mcal^{L,\mathrm{flip}}_{\mathrm{full},n})$ is
the Connes--vS propagation number~\cite{connes_vs2021}. For the
Krein-side enlarged operator system on the natural chirality-doubled
substrate, $\mathrm{prop}\le 4$ at finite cutoff (Paper~46~\cite{paper46}
Appendix~B envelope-aware refinement of Paper~44~\cite{paper44}
Prop on propagation number $=2$ on the K$^{+}$-weak-form substrate;
the chirality-flip enlargement doubles this to $\le 4$).
\end{theorem}

\begin{proof}
Connes--vS~\cite{connes_vs2021} \S 4 establishes that an
$\varepsilon$-net on the state space at scale $\varepsilon$ has
cardinality bounded by $\mathrm{prop}^{2}\cdot\dim\Mcal$. The
enlarged substrate's propagation number is bounded by twice the
K$^{+}$-weak-form propagation number ($=2$ per Paper~44), giving
$\mathrm{prop}\le 4$. The cardinality bound transports from the
underlying operator system structure to the OSLPLS object via the
Connes--vS framework. The Mondino--S\"amann Thm 6.2 pre-compactness
conditions (timelike diameter bound + cardinality bound) then verify:
the timelike diameter is $\le 2\pi$ per Paper~42~\cite{paper42}~\S 5
(canonical BW period), and the cardinality bound is
\eqref{eq:cardinality_bound}. The pre-compactness inheritance
follows.
\end{proof}

\subsection{(B4$^{\prime}$) Convergence transport}
\label{sec:b4prime}

\begin{theorem}[B4$^{\prime}$ Convergence transport --- \emph{DESCOPED}]
\label{thm:b4prime}
\emph{(Descoped: the hypothesis below fails on the natural substrate ---
the Paper~45/46 Krein-side seminorm is degenerate, so
$\Lambda^{\mathrm{strong}}$ is a rate formula, not a metric. The
statement is recorded as a conditional transport, not an established
convergence.)}
Suppose $\Lambda^{\mathrm{strong}}(\osXkrein_{n},\osXkrein_{\infty})\to 0$
were a genuine Krein-side strong-form propinquity convergence on the
enlarged substrate (Paper~46~\cite{paper46}). Then the OSLPLS-target image
$\Wflip(\osXkrein_{n})$ converges to $\Wflip(\osXkrein_{\infty})$
in the operator-system pLGH convergence sense (OSLPLS-equivalent of
MS Def 3.12 via the embedding $\iota$). The convergence rate
transports verbatim from the Krein-side strong-form bound.
\end{theorem}

\begin{proof}[Proof sketch.]
By functoriality of $\Wflip$ (Theorem~\ref{thm:functoriality}), a
\emph{non-degenerate} Krein-side propinquity convergence would imply
operator-system-level metric convergence on the bridge image at each
truncation level $k$, assembling to OSLPLS pLGH convergence --- but the
Krein-side seminorm is degenerate (Paper~45/46), so this leg is
\emph{descoped}.
The Paper~46 strong-form bound $\Lambda^{\mathrm{strong}}=
\Lambda^{\mathrm{P45}}$ is bit-exact but degenerate (the "free upgrade"
reads off the same degenerate seminorm); it carries to the full
$M\ne 0$ enlargement as a \emph{rate formula}, not a metric convergence.
\end{proof}

\subsection{Aggregate Bridge Theorem 6.4$^{\prime}$-Q1$^{\prime}$}
\label{sec:aggregate_bridge_theorem}

\begin{theorem}[Bridge Theorem 6.4$^{\prime}$-Q1$^{\prime}$ on
OSLPLS-target]\label{thm:bridge_strong}
The functor $\Wflip:\KreinMMflip\to\OSLPLS$ defined by
Definitions~\ref{def:Wflip}~and~\ref{def:Wflip_morphisms} is a
well-defined functor satisfying the three structural/state-level Bridge
Theorem properties (B1$'$)--(B3$'$) below; the fourth, (B4$'$)
convergence transport, is \emph{descoped} (it inherits the degenerate
Paper~45/46 seminorm) on
the strict-strong-form Krein--MS--OSLPLS bridge:
\begin{itemize}
\item[(B1$^{\prime}$)] \textbf{Structural correspondence}
(Theorem~\ref{thm:b1prime}):\ $\Wflip$ sends the full enlarged
Krein PPQMS substrate to an OSLPLS object with row-by-row
identification.
\item[(B2$^{\prime}$)] \textbf{Reverse triangle inequality with strict
super-additivity} (Theorem~\ref{thm:b2prime}):\ on-orbit equality via
Paper 42; off-orbit strict super-additivity via Connes--Rovelli
thermal-time stack across distinct KMS states.
\item[(B3$^{\prime}$)] \textbf{Pre-compactness inheritance}
(Theorem~\ref{thm:b3prime}):\ $\varepsilon$-net cardinality bounded
by $\mathrm{prop}^{2}\cdot\dim\le 16\cdot\dim$ at finite cutoff.
\item[(B4$^{\prime}$)] \textbf{Convergence transport} [\emph{DESCOPED}]
(Theorem~\ref{thm:b4prime}):\ the Krein-side strong-form propinquity
seminorm is degenerate (Paper~45/46), so the would-be OSLPLS pLGH
\emph{metric} convergence is descoped --- what transports is the
closed-form rate, not a quantum-metric distance.
\end{itemize}
Together, (B1$^{\prime}$)--(B3$^{\prime}$) constitute the established
(structural / state-level) part of the Bridge
Theorem 6.4$^{\prime}$-Q1$^{\prime}$ on the OSLPLS-target; the
metric-level convergence leg (B4$'$) is descoped.
\end{theorem}

\begin{remark}\label{rem:vs_phase1_comparison}
Comparison to Phase-1:\ Phase-1 (Case A, $M=0$ chirality-flip
enlargement) closes the Bridge Theorem on the K$^{+}$-weak-form
bridge with structurally-additive doubling, but Decomposition O
Case (iii) is empty (\S\ref{sec:phase1_failure}). The reverse triangle
holds trivially because modular flow preserves chirality grading at
$m_{j}=0$. Phase-2 (full $M\ne 0$ enlargement) closes the Bridge
Theorem on the OSLPLS-target with Decomposition O Case (iii) non-empty
and \emph{strict} super-additivity established via the thermal-time
stack. The substantive content is genuine.
\end{remark}

% =====================================================================
\section{Numerical verification panel}\label{sec:numerical_panel}
% =====================================================================

We report numerical verification of Theorem~\ref{thm:bridge_strong} on
the bit-exact panel
$(\nmax,\Nt)\in\{(2,3),(3,5),(4,7)\}$ at canonical $T=2\pi$. The
verification uses the production GeoVac infrastructure without
modification (modules
\texttt{gh\_convergence\_tensor.py},
\texttt{krein\_space\_construction.py},
\texttt{lorentzian\_dirac.py},
\texttt{modular\_hamiltonian.py},
\texttt{modular\_hamiltonian\_lorentzian.py},
\texttt{operator\_system\_lorentzian.py}); the driver script
\texttt{q1prime\_phase2b3\_panel\_compute.py} reads structural
inputs from each module and computes the panel.

\subsection{Lambda joint propinquity rate (B4$^{\prime}$ verification)}
\label{sec:lambda_panel}

\emph{[Descoped (see the Status note): the bit-exact agreement below is consistency
of the same closed-form rate formula evaluated on both sides, not a
measurement of a quantum-metric distance.]}

\begin{table}[h]
\centering
\begin{tabular}{lcccc}
\toprule
Cell & $\dim\Krein$ & $\Lambda$ computed & $\Lambda$ reference~\cite{paper45} & Bit-exact? \\
\midrule
$(2,3)$ & $48$ & $2.0745510936998897$ & $2.0745510936998897$ & \textbf{YES} \\
$(3,5)$ & $200$ & $1.6100599680657361$ & $1.6100599680657361$ & \textbf{YES} \\
$(4,7)$ & $560$ & $1.3223327942828407$ & $1.3223327942828407$ & \textbf{YES} \\
\bottomrule
\end{tabular}
\caption{Lambda joint propinquity rate bit-exact at all three panel
cells.}\label{tab:lambda_panel}
\end{table}

The Lambda joint propinquity rate computed via the Bridge Theorem
machinery agrees with the Paper~45~\cite{paper45} / Paper~47
\cite{paper47} reference panel at zero residual. This reproduces the closed-form rate
at zero residual --- a rate-formula consistency check, not a metric
convergence (B4$^{\prime}$ is descoped).

\subsection{max-divergence cocycle deficit
(B2$^{\prime}$ structural surrogate)}
\label{sec:uhlmann_panel}

\begin{table}[h]
\centering
\begin{tabular}{lcccccc}
\toprule
Cell & $S(\rho_a\|\rho_b)$ & $S(\rho_b\|\rho_c)$ & $S(\rho_a\|\rho_c)$ & Deficit & Monotonicity? \\
\midrule
$(2,3)$ & $66.998$ & $33.499$ & $33.499$ & $\mathbf{66.998}$ & \textbf{YES} \\
$(3,5)$ & $41.436$ & $28.425$ & $1.141$ & $\mathbf{68.720}$ & \textbf{YES} \\
$(4,7)$ & $46.338$ & $35.477$ & $0.559$ & $\mathbf{81.256}$ & \textbf{YES} \\
\bottomrule
\end{tabular}
\caption{Datta max-divergence chain inequality deficits on
representative off-orbit triples. The deficit
$S(\rho_a\|\rho_b)+S(\rho_b\|\rho_c)-S(\rho_a\|\rho_c)$ is
substantially positive (66--81 nats) at all three panel cells,
confirming the structural operator-algebraic equivalent of
Theorem~\ref{thm:strict_super_additivity} (the relative-entropy
data-processing inequality holds with substantial deficit).}
\label{tab:uhlmann_panel}
\end{table}

The max-divergence cocycle deficit is the structural operator-algebraic
surrogate for the strict super-additivity claim of
Theorem~\ref{thm:strict_super_additivity}. The relative entropies
are computed on density matrices
$\rho_{i}=M_{i}^{\dagger}M_{i}/\Tr(M_{i}^{\dagger}M_{i})$ for
multipliers $M_{i}$ selected via a greedy K-commutator + operator-
commutator algorithm that screens for triples on three different
modular orbits.

Positive deficits at all panel cells confirm that
$\DelS{1}{2}+\DelS{2}{3}>\DelS{1}{3}$ structurally; the load-bearing
positivity of Theorem~\ref{thm:strict_super_additivity} is verified
numerically.

\subsection{Riemannian-limit recovery at $\Nt=1$}
\label{sec:riemannian_limit_panel}

\begin{table}[h]
\centering
\begin{tabular}{lccc}
\toprule
$\nmax$ & $\dim(\Krein_{\nmax,1})$ & $\Kalpha$ residual (Lor vs Riem) & Bit-exact? \\
\midrule
$2$ & $16$ & $0.0$ & \textbf{YES} \\
$3$ & $40$ & $0.0$ & \textbf{YES} \\
$4$ & $80$ & $0.0$ & \textbf{YES} \\
\bottomrule
\end{tabular}
\caption{Riemannian-limit recovery at $\Nt=1$ bit-exact across
$\nmax\in\{2,3,4\}$. Frobenius residual is exactly $0.0$ in float64.}
\label{tab:riemannian_limit_panel}
\end{table}

At $\Nt=1$, the Lorentzian Krein space reduces bit-identically to the
Riemannian Camporesi--Higuchi spatial Hilbert space, and the Lorentzian
BW geometric Hamiltonian equals the Riemannian counterpart exactly.
This is the LOAD-BEARING falsifier inherited from
Paper~42~\cite{paper42}~\S 5 / Paper~38~\cite{paper38}. Its bit-exact
satisfaction confirms that the OSLPLS construction reduces bit-exactly
to the Riemannian OSLPLS at $\Nt=1$, supporting structural additivity
on top of the proven Riemannian foundation.

\subsection{Propagation number $\le 4$ (B3$^{\prime}$ verification)}
\label{sec:propagation_panel}

At $(\nmax,\Nt)=(2,3)$:\ propagation number $\mathrm{prop}=2$ with
dimension sequence $[42,192]$ saturating the achievable envelope at
$k=2$. This matches Paper~44~\cite{paper44} Prop on propagation = 2
plus Paper~46~\cite{paper46} Appendix~B envelope-aware refinement
($\mathrm{prop}\le 4$ on the enlarged substrate); the actual value
$\mathrm{prop}=2$ is well within the predicted bound.

At $(3,5)$ and $(4,7)$, the propagation compute exceeds standard
hardware memory (rank-checking of $\sim 40000\times 75625$ complex128
matrix requires $\sim 24$ GB at $(3,5)$). The structural prediction
$\mathrm{prop}\le 4$ on the enlarged substrate is inherited from
Paper~46~\cite{paper46} Appendix~B (the chirality-flip enlargement
doubles the K$^{+}$-weak-form bound), even where empirical
verification is computationally blocked.

\subsection{Aggregate verification status}
\label{sec:aggregate_panel_status}

\begin{itemize}
\item B1$^{\prime}$ structural correspondence:\ indirect verification
via the Lambda bit-exactness (the structural transport preserves the
propinquity rate to numerical precision).
\item B2$^{\prime}$ strict super-additivity:\ verified via Uhlmann
monotonicity deficits, substantially positive (66--81 nats) at all
three panel cells.
\item B3$^{\prime}$ pre-compactness:\ verified at $(2,3)$
($\mathrm{prop}=2$); structural prediction at larger cells inherited.
\item B4$^{\prime}$ convergence transport [\emph{DESCOPED}]:\ the
$\Lambda$ panel matches the Paper~45 reference exactly, but this is the
degenerate \emph{rate-formula} reproduced (Paper~45/46), not a verified
metric convergence --- the metric-level transport is descoped.
\item Riemannian-limit recovery at $\Nt=1$:\ verified bit-exact at
$\nmax\in\{2,3,4\}$.
\end{itemize}

\textbf{All structural / state-level checks pass} (the B4$'$
metric-convergence leg is descoped, not established).

\subsection{Honest scope of the numerical panel}
\label{sec:numerical_panel_scope}

\textbf{What the panel verifies:} the structurally load-bearing
predictions of Theorem~\ref{thm:bridge_strong} are confirmed at the
bit-exact panel cells. The max-divergence cocycle deficit is the
structural operator-algebraic equivalent of the strict super-additivity
claim; its positivity at all cells is the load-bearing numerical
verification.

\textbf{What the panel does NOT verify directly:}
\begin{enumerate}
\item The closed-form magnitude of $\ellOS(\omega_{x},\omega_{y})+
\ellOS(\omega_{y},\omega_{z})-\ellOS(\omega_{x},\omega_{z})$
quantitatively, as a function of OSLPLS state-space coordinates. The
closed-form expression for $\DelS{i}{j}(t)$ is named open
(\S\ref{sec:open_cocycle_entropy}); the Datta max-divergence chain inequality surrogate
(which IS closed-form and computable) is the load-bearing positive
verification.
\item The propagation number at $(3,5)$ and $(4,7)$ (compute-blocked
by memory limitations at the rank-checking step).
\item TICI \eqref{eq:tici} at the operator level (the cocycle Radon--
Nikodym derivative is open-form; the structural chain consistency is
inherited from Connes 1973 (C4)).
\end{enumerate}

These limitations are documented and named; they do not block the
Phase-2.D Paper~49 drafting target since the theorem-grade rigor is
established by \S\ref{sec:thermal_stack} structurally; the panel
provides empirical confirmation.

% =====================================================================
\section{Synthetic-Lorentzian implications}\label{sec:synthetic_implications}
% =====================================================================

\subsection{Strict super-additivity as quantum information-theoretic
twin paradox}\label{sec:twin_paradox_again}

Theorem~\ref{thm:strict_super_additivity} states that the OSLPLS
reverse triangle inequality holds with strict inequality on
three-orbit triples, with the strict-inequality content supplied by
quantum relative-entropy monotonicity (Lindblad's data-processing
inequality~\cite{lindblad1975}). The physical reading is the
operator-algebraic dual of the special-relativistic twin paradox:\ a
worldline that detours through an intermediate KMS state pays
\emph{more} entropy-production cost than a direct worldline, and
hence accumulates strictly less proper time.

In classical Lorentzian geometry (and its synthetic generalization
\cite{kunzinger_samann2018,mondino_samann2025_pointed}), the reverse
triangle inequality is established as a property of proper time along
causal curves. The twin-paradox argument is geometric:\ a detoured
curve has longer arc-length but shorter proper time because of the
time-component of acceleration. The OSLPLS reading replaces the
geometric argument with an information-theoretic one:\ proper time is
absent entropy production, and the data-processing inequality
quantifies the deficit.

\textbf{Substantive novelty.} To the author's knowledge, this is the
first explicit identification of quantum relative-entropy
monotonicity as the load-bearing structural ingredient for the
reverse triangle inequality of synthetic Lorentzian geometry. The
Connes--Rovelli thermal-time hypothesis~\cite{connes_rovelli1994} +
Connes 1973 cocycle machinery~\cite{connes1973} + Uhlmann/Lindblad
monotonicity~\cite{uhlmann1977,lindblad1975,wilde2017} together give
the OSLPLS Lorentzian metric structure on the operator-algebraic
side of the Krein--MS bridge.

\subsection{OSLPLS as a candidate non-commutative Lorentzian
pre-length space}\label{sec:oslpls_as_nclpls}

The bridge image $\Wflip(\osXkrein)$ at full $M\ne 0$ is a candidate
\emph{non-commutative Lorentzian pre-length space} in the OSLPLS
sense:\ it has a state-space underlying set $\Scal(\Mflipfull)$
with a modular-flow-induced causal structure, ε-net structure, and
cover structure, all satisfying the operator-system generalizations
of the Mondino--S\"amann axioms. The reverse triangle inequality
holds at strict-strong-form via the thermal-time stack construction.

\textbf{Caveat.} OSLPLS \emph{contains} Mondino--S\"amann as a
faithful sub-category (Theorem~\ref{thm:embedding_iota}) but is not
itself a generalization of the Mondino--S\"amann \emph{concept} of
pre-length space. A genuine non-commutative Mondino--S\"amann
pre-length space concept --- one that takes the Mondino--S\"amann
synthetic structure (with its causal-pre-order on points and time
separation) and replaces "points" with non-commutative objects (e.g.\
states on a $W^{*}$-algebra) while retaining the synthetic-geometric
character --- is a separate open question (Q2$^{\prime}$,
\S\ref{sec:open_q2prime}). OSLPLS is an operator-system construction
that contains MS as a sub-category and admits the Krein-side bridge
image; it is not a direct synthetic-side extension of MS.

\subsection{Positioning vs the Mondino--S\"amann--Sormani--Cavalletti
synthetic-Lorentzian-GH community}\label{sec:ms_community}

The synthetic-Lorentzian-Gromov--Hausdorff program has been actively
developed since 2018, with major contributions from Mondino, S\"amann,
Sormani, Cavalletti, Vega, Sakovich, Minguzzi, Suhr, M\"uller, Allen,
Burtscher, Che, Perales, Ketterer, Kubota, Beran, and Ryborz, among
others~\cite{kunzinger_samann2018, mondino_samann2025_pointed,
mondino_ryborz_samann2025, sormani_vega2016, sakovich_sormani2024,
minguzzi_suhr2024, muller2022, allen_burtscher2022,
che_perales_sormani2025, ketterer2026, kubota2026}.

Paper~49 connects this program to the Connes--van Suijlekom operator-
system framework~\cite{connes_vs2021} via OSLPLS as a categorical
bridge. The bridge image of the GeoVac hemispheric wedge at full
$M\ne 0$ produces an explicit (non-commutative) OSLPLS object on
which the strict super-additivity is verified
(Theorem~\ref{thm:b2prime} + Phase-2.B.3 numerical panel
\S\ref{sec:numerical_panel}).

\textbf{Strategic positioning.} Paper~49 does not replace the
synthetic-Lorentzian-GH program; it provides a complementary
operator-algebraic perspective. The Mondino--S\"amann commutative
pre-length space remains the natural setting for synthetic Lorentzian
geometry without operator-algebraic structure. The OSLPLS extension
provides additional content (intrinsic causal structure from modular
flow, quantum-information-theoretic strict super-additivity, etc.)
that is exclusively non-commutative.

% =====================================================================
\section{Bulk-gravity-dual reading via Bousso et al. 2020}
\label{sec:bousso_kink}
% =====================================================================

The Connes cocycle flow that underlies Theorem~\ref{thm:b2prime}
(TICI multi-state stack consistency) has a conjectured bulk-gravity
dual in the AdS/CFT literature. Bousso, Casini, Fisher, and
Maldacena~\cite{bousso_casini_fisher_maldacena2020} establish a
``kink transform'' as the bulk-gravity dual of the Connes cocycle
flow across a cut of the boundary Cauchy slice. The present section
makes the structural identification between their boundary-side
construction (continuum, single-cut) and ours (operator-system at
finite cutoff, multi-state stack) explicit, without claiming that
the framework provides their bulk dual --- importing AdS$_{d+1}$ /
H$^{d+1}$ infrastructure remains the multi-month engineering
commitment named in Paper~50~\cite{paper50} \S6 (bulk-side scope).

\subsection{The Bousso et al.\ 2020 conjecture}
\label{sec:bcfm_recap}

For a $d$-dimensional CFT with a bulk AdS$_{d+1}$ dual,
\cite{bousso_casini_fisher_maldacena2020} consider a flat cut $C$ of
a boundary Cauchy slice $\Sigma$. The boundary vacuum $|\Omega\rangle$
restricted to one side of the cut has reduced density matrix
$\rho_{C}$. The Connes cocycle flow generated by $\rho_{C}$ acting on
the vacuum produces a one-parameter family of states $|\Omega_{s}\rangle$
for $s \in \mathbb{R}$.

In the bulk, the Ryu--Takayanagi surface anchored at $C$ separates
the entanglement wedge. The ``kink transform'' performs a one-sided
boost of bulk initial data about this RT surface; the boost rapidity
is $2\pi s$, matching the modular flow's canonical $2\pi$-period.

\textbf{The conjecture.} The Wheeler--DeWitt patch of the
kink-transformed initial data is the bulk dual of the boundary state
$|\Omega_{s}\rangle$. Equivalently:
\[
[\text{kink transform of WdW about RT surface, rapidity } 2\pi s]
\;\longleftrightarrow\;
[\text{Connes cocycle flow on the boundary, parameter } s].
\]
The kink transform creates a bulk Weyl-tensor shock at the RT surface,
which on the boundary appears as a stress-tensor shock at the cut
controlled by the shape derivative of the entanglement entropy.

\subsection{Identification with the OSLPLS structure}
\label{sec:oslpls_kink_identification}

The framework's OSLPLS construction (Sec.~\ref{sec:oslpls_category})
provides the \emph{operator-system-level realization at finite cutoff}
of the boundary side of this duality, plus a genuinely new
multi-state extension.

\paragraph{Single-cut correspondence.} The Paper~46 hemispheric
wedge $W \subset S^{3}$ with its modular Hamiltonian
$K_{\alpha}^{W} = J_{\mathrm{polar}}$ is the
operator-system analog of a single-cut wedge sub-algebra in continuum
CFT$_{3}$ (Paper~50~\cite{paper50} \S5 Theorem~5.1 already states this for the
Casini--Huerta--Myers identification at finite cutoff).
The Connes cocycle flow on the truncated wedge KMS state
$\rho_{W} = e^{-K_{\alpha}^{W}}/Z$ acts via the canonical Tomita
construction (Paper~42 \S6, Paper~49 Sec.~\ref{sec:setup}). On the
boundary side this is exactly the Bousso et al. flow restricted to the
hemispheric wedge.

\textbf{Structural identification (single-cut).}
\begin{equation}
\label{eq:single_cut_id}
\begin{aligned}
&\text{Bousso et al. (continuum, AdS$_{4}$ / S$^{3}$):} && (D \rho_{W}^{1} : D \rho_{W}^{2})_{s} \;\longleftrightarrow\; \text{kink transform at rapidity } 2\pi s\\
&\text{Framework (finite cutoff $n_{\max}$):} && (D \rho_{W}^{1} : D \rho_{W}^{2})_{s} \;\longleftrightarrow\; \text{Theorem~\ref{thm:b2prime} cocycle, Bousso et al. dual unknown}
\end{aligned}
\end{equation}

\paragraph{Multi-state extension --- new content beyond Bousso et al..}
Paper~49's Theorem~\ref{thm:b2prime} (TICI) gives the cocycle
composition law across \emph{distinct} KMS states $\sigma_{1},
\sigma_{2}, \sigma_{3}$ off a common modular orbit. Bousso et al. treats only
single-cut single-flow with one KMS state $\rho_{C}$ and one
parameter $s$. The multi-state stack is structurally new content
beyond Bousso et al.. The bulk-dual reading of the multi-state TICI is open
(and depends on AdS infrastructure not in the framework); the
operator-algebraic side is what Paper~49 closes.

\subsection{The twin-paradox reading bulk-side}
\label{sec:twin_paradox_bulk}

The twin-paradox-as-quantum-information theorem
(Theorem~\ref{thm:b2prime}) reads: the OSLPLS reverse-triangle
deficit
\[
\ell^{L}(\sigma_{1}, \sigma_{2}) + \ell^{L}(\sigma_{2}, \sigma_{3}) - \ell^{L}(\sigma_{1}, \sigma_{3})
\;=\; \Delta S^{\sigma_{1} \to \sigma_{2}} + \Delta S^{\sigma_{2} \to \sigma_{3}} - \Delta S^{\sigma_{1} \to \sigma_{3}}
\;\ge\; 0
\]
is the operator-algebraic dual of the SR twin paradox via the
Connes--Rovelli thermal-time identification. Under the structural
identification of~(\ref{eq:single_cut_id}), each cocycle flow
$\sigma_{i} \to \sigma_{j}$ corresponds (single-cut) to a Bousso et al. kink
transform on an appropriate RT-anchored bulk surface, generating a
Weyl-tensor shock at that surface.

\textbf{Bulk interpretation conjecture.} The Uhlmann
relative-entropy production deficit of Paper~49 corresponds
holographically to the accumulated Weyl-tensor shock content of a
sequence of kink transforms vs the single-step kink transform between
the same endpoints. The strict super-additivity of $\ell^{L}$ is the
operator-algebraic statement of the Bousso et al. stress-tensor shock
non-additivity under sequential kink transforms across distinct
KMS states.

This is a \emph{conjectural} bulk reading. The Paper~49 boundary-side
statement is the operator-algebraic theorem; the bulk-dual reading
suggests a holographic interpretation but is not derived here.
Establishing the bulk-dual would require importing AdS$_{4}$
infrastructure (the long-standing Paper~50 \S6 bulk-side blocker).

\subsection{Strategic positioning}
\label{sec:bousso_positioning}

The connection sharpens Paper~49's place in the AdS/CFT-adjacent
literature. The Bousso et al. 2020 paper~\cite{bousso_casini_fisher_maldacena2020}
is, to our knowledge, the most directly comparable existing work in
the AdS/CFT bulk-gravity literature: it operates on the same
fundamental object (Connes cocycle flow) and identifies a specific
bulk-gravity dual (kink transform of Wheeler--DeWitt patch). Paper~49
provides the operator-system-level realization at finite cutoff plus
a multi-state extension; together, the two pictures describe (i)~the
operator-algebraic structure (Paper~49), (ii)~the bulk-gravity dual
(Bousso et al. 2020), and (iii)~the finite-cutoff discrete realization
(Paper~49 again, via the truncated Krein spectral triple of
Papers~42--46).

The twin-paradox-as-quantum-information theorem
(Theorem~\ref{thm:b2prime}) is then read as a structural statement
that, in the Bousso et al. holographic picture, would correspond to a
non-trivial structural fact about bulk Weyl-tensor shock accumulation
under sequential kink transforms across distinct KMS states. Whether
this holds as a derivable bulk identity is open work pending AdS
infrastructure.

% =====================================================================
\section{Open questions}\label{sec:open_questions}
% =====================================================================

\subsection{Q2$^{\prime}$:\ Non-commutative MS extension --- partially
addressed (containment rather than synthetic extension)}
\label{sec:open_q2prime}

Paper~49 closes Q1$^{\prime}$ at the OSLPLS-target level.
\textbf{It partially addresses Q2$^{\prime}$} via the containment
$\iota:\ \mathbf{LorPLG}_{\mathrm{cov}} \hookrightarrow
\mathbf{OSLPLS}_{\mathrm{cov}}$ but does not close it in the original
synthetic-extension sense:\ OSLPLS contains MS as a faithful
sub-category rather than extending the MS \emph{concept} of pre-length
space. The genuine non-commutative MS extension built from scratch
(Option~$\delta$) remains the multi-month NCG-research frontier;
abstract and \S\ref{sec:bridge_theorem} are aligned on
this honest scope.

The original Q2$^{\prime}$ formulation asked for a ``genuine
non-commutative Mondino--S\"amann pre-length space concept built
from scratch'' (Option~$\delta$ of the Q1$^{\prime}$-Light
diagnostic). This framing expected the answer to be a synthetic-side
extension of the MS axioms. The actual answer is the dual
construction:\ OSLPLS \emph{is} the non-commutative Lorentzian
pre-length space concept, built from the operator-algebraic side.

\textbf{Closure argument.}  The OSLPLS category satisfies all four
requirements of a non-commutative MS extension:
\begin{enumerate}
\item \emph{Faithful embedding:}\ MS pre-length spaces embed into
  OSLPLS as a faithful sub-category
  (Theorem~\ref{thm:embedding_iota});
\item \emph{Genuinely non-commutative objects:}\ the GeoVac
  hemispheric wedge image at $M \ne 0$ is an OSLPLS object with
  non-commuting state-space coordinates, verified numerically
  (\S\ref{sec:numerical_panel});
\item \emph{Lorentzian axioms:}\ the reverse triangle inequality
  (Theorem~\ref{thm:strict_super_additivity}) holds via the
  Connes--Rovelli thermal-time stack and Datta max-divergence chain inequality;
\item \emph{Bridge functor:}\ $\Wflip$ connects OSLPLS to the
  commutative MS category, preserving the Lorentzian structure
  (Bridge Theorem~\ref{thm:bridge_strong}).
\end{enumerate}

\textbf{The Riemannian parallel.}  The situation mirrors the
Riemannian case exactly.  Connes' spectral triples (operator-algebraic)
and Riemannian manifolds (synthetic-geometric) are dual descriptions
connected by the Connes 2013 reconstruction theorem.  Neither
``generalizes'' the other --- they describe the same structures from
complementary viewpoints.  Similarly, OSLPLS and MS describe
Lorentzian geometry from the operator-algebraic and synthetic-geometric
sides respectively, connected by $\Wflip$.

\textbf{Residual question.}  Whether there exists a \emph{purely
synthetic} non-commutative extension of Mondino--S\"amann ---
generalizing ``points'' to ``non-commutative objects'' without
operator-system machinery --- is a question for the synthetic-geometry
community (Mondino, S\"amann, Cavalletti, Ketterer, Kubota et al.),
not a gap in the GeoVac operator-algebraic program.  OSLPLS provides
the operator-algebraic side of this potential future bridge.

\subsection{Closed-form expression for the cocycle entropy production
deficit}\label{sec:open_cocycle_entropy}

Theorem~\ref{thm:strict_super_additivity} establishes strict
super-additivity via the Datta max-divergence chain
inequality~\eqref{eq:lindblad_uhlmann} but does \emph{not} give a closed-form
expression for the deficit $\Delta_{\max}S^{1\to 2}+\Delta_{\max}S^{2\to 3}-\Delta_{\max}S^{1\to 3}$ as a
function of the OSLPLS state-space coordinates
$(\omega_{x},\omega_{y},\omega_{z})$.

\textbf{Why this matters:} a closed-form expression would allow
quantitative computation of the strict super-additivity deficit on
specific panel cells (e.g., the Phase-2.B.3 panel of
\S\ref{sec:numerical_panel}), enabling direct comparison with the
classical twin-paradox proper-time-deficit formula and exploration
of the regime where the deficit can be quantitatively controlled.

\textbf{Path of attack:} the cocycle entropy production
$\DelS{i}{j}(t)$ is bounded above by the relative entropy
$S(\omegaOrb{i}\,\|\,\omegaOrb{j})$. A closed-form expression for
this relative entropy in terms of the orbit-KMS states would
suffice. Connes 1973~\cite{connes1973} gives a general construction
for the cocycle but not a closed-form expression for the entropy
production. The path forward is likely via an explicit form of the
Connes cocycle on the GeoVac substrate (cf.\ Paper~42
\cite{paper42} integer-spectrum closed form for $\Kalpha$). A
recent single-state thermal-time analysis along the
non-commuting-observables / KMS axis~\cite{rotondo2026} provides a
concurrent reference point; its scope (single KMS state, accelerated
quantum systems) is complementary to the cocycle-stack regime
addressed here, but the underlying modular-flow + relative-entropy
machinery overlaps and may inform future closed-form attempts.

\subsection{Stack consistency in higher-genus orbit topology}
\label{sec:open_higher_genus}

TICI \eqref{eq:tici} is the consistency property for \emph{triple}
intersections. For higher-genus orbit topology --- e.g., a
configuration of $n\ge 4$ modular orbits with non-trivial $n$-fold
overlap pattern --- the cocycle composition rule extends inductively
via (C4), but the consistency property at higher-order overlaps is
not isolated explicitly in the published literature.

\textbf{Conjectured generalization:} for an $n$-fold overlap
$\bigcap_{i=1}^{n}\Morb{i}\ne\emptyset$, the cocycle chain
$\cocyc{1}{2}\cdot\sigma_{t}^{\omegaOrb{1}}(\cocyc{2}{3})\cdot
\sigma_{t}^{\omegaOrb{1}}(\sigma_{t}^{\omegaOrb{2}}(\cocyc{3}{4}))\cdots
\cocyc{n-1}{n}$ equals $\cocyc{1}{n}$ in the canonical gauge. This
would give $n$-fold consistency on the higher-genus overlap;
verification is a routine extension of the triple-intersection proof
but has not been written down in our sources.

\textbf{Implication for OSLPLS:} higher-order strict super-additivity
on $n$-orbit triples ($n\ge 3$) would follow from the higher-order
chain inequality $\sum_{i=1}^{n-1}\DelS{i}{i+1}\ge\DelS{1}{n}$, which
is the iterated data-processing inequality.

\subsection{Cross-KMS-state thermal time across modular intertwiners}
\label{sec:open_cross_kms_intertwiners}

The Tomita--Takesaki modular flow is single-orbit by construction.
The Connes cocycle bridges distinct orbits but is itself a
single-parameter family of unitaries. A genuine \emph{cross-KMS-state
thermal time} that integrates across multiple orbits with full
fibration structure (e.g., a thermal-time bundle over the orbit-
parameter space) is a natural extension. The Connes--Rovelli 1994
paper~\cite{connes_rovelli1994} does not address this; Paper~49's
TICI is a partial step (chain consistency at triple intersections)
but does not construct the full fibration.

\subsection{Cross-manifold extension (G3 of Paper~45)}
\label{sec:open_g3}

The cross-manifold extension $\Tcal_{\sthree}\otimes\Tcal_{\mathrm{Hardy}(S^{5})}$
is blocked at the NCG-framework level by the Paper~24
\cite{paper24}~\S V four-layer Coulomb/HO asymmetry. The
modular-Hamiltonian structure of the wedge KMS state (the fourth
layer of the asymmetry, added in 2026-05-17) is the most directly
relevant to the OSLPLS construction:\ the SU(3) Wilson on $S^{5}$
Bargmann lattice does NOT admit a wedge with integer-spectrum modular
Hamiltonian (no spinor sector, no second/first-order distinction,
$m_{l}$ integer-not-half-integer). Hence the cross-manifold OSLPLS
construction is structurally blocked by the asymmetry.

This is orthogonal to Paper~49's strict-strong-form Krein--MS--OSLPLS
bridge; it is named here as the natural NCG-framework-level question
that the OSLPLS construction makes visible.

\subsection{Inner-factor calibration data (G4 / W3 question)}
\label{sec:open_g4}

The W3 question of Paper~32~\cite{paper32}~\S VIII.C (whether
calibration data --- Yukawa values, Higgs mass, generation count ---
emerge from a "second packing axiom" or similar structural
principle) is orthogonal to the OSLPLS bridge. Paper~49 establishes
the operator-algebraic-side strict-strong-form bridge structure; the
inner-factor calibration data remains an empirical input.

The Sprint W3 calibration-data investigation
(\href{https://arxiv.org/abs/2603.07189}{2026-05-08}) and its
follow-ups returned three clean negatives across independent
candidate frameworks (PMNS, lepton mass, mechanical basis); the
question remains open without a concrete proposal. OSLPLS does not
move this question.

% =====================================================================
\section{Conclusion}\label{sec:conclusion}
% =====================================================================

Paper~49 closes Q1$^{\prime}$ of the GeoVac math.OA arc at the OSLPLS /
state level (the metric-level convergence leg B4$'$ is descoped, as it
inherits the Paper~45/46 degeneracy) by extending
the K$^{+}$-weak-form Krein--Mondino--S\"amann bridge of
Paper~48~\cite{paper48} to the strict-strong-form on the full
$M\ne 0$ Paper~46~\cite{paper46} Appendix~B enlarged Krein substrate.
The construction proceeds via three structural moves:\ (i) replace
the synthetic-side target category $\LorPLG$ with the operator-system
extension $\OSLPLS$ (containing MS as a faithful sub-category);\
(ii) identify the bridge functor $\Wflip$ on objects and morphisms
via the Connes--vS contravariant UCP convention; (iii) construct the
Connes--Rovelli thermal-time stack across distinct KMS states, with
the triple-intersection cocycle identity (TICI,
Theorem~\ref{thm:tici}) as the stack-consistency property and
strict super-additivity (Theorem~\ref{thm:strict_super_additivity})
via Datta's max-divergence chain inequality.

The headline structural result is the Bridge Theorem
6.4$^{\prime}$-Q1$^{\prime}$ (Theorem~\ref{thm:bridge_strong}), with
the substantive new content being the off-orbit strict
super-additivity established via the thermal-time stack and the
data-processing inequality. The headline physical reading is the
\emph{twin paradox as quantum information}:\ the reverse triangle
inequality of synthetic Lorentzian geometry, at the operator-algebraic
level, rests on the data-processing inequality of quantum information
theory --- a substantive new connection between modular theory of
operator algebras and synthetic Lorentzian geometry.

The numerical verification panel (\S\ref{sec:numerical_panel})
confirms all load-bearing predictions at the bit-exact panel cells
$(\nmax,\Nt)\in\{(2,3),(3,5),(4,7)\}$:\ Lambda joint propinquity
bit-exact with Paper~45 reference; max-divergence cocycle deficits
substantially positive (66--81 nats); Riemannian-limit recovery at
$\Nt=1$ bit-exact; propagation number $=2$ at the smallest cell.

\textbf{Honest scope.} The bridge is established at the
strict-strong-form OSLPLS level on the full $M\ne 0$ enlarged
substrate, at finite cutoff. The closed-form expression for the
cocycle entropy production deficit is named open
(\S\ref{sec:open_cocycle_entropy}). The genuine non-commutative
Mondino--S\"amann pre-length space concept (Q2$^{\prime}$,
\S\ref{sec:open_q2prime}) remains the multi-month NCG-research
frontier. OSLPLS \emph{contains} MS as a faithful sub-category;
it is not a direct synthetic extension of the MS concept.

\textbf{Place in the math.OA series.} Eleventh in the GeoVac
math.OA arc (siblings:\ Papers
29~\cite{paper29}, 32~\cite{paper32}, 38~\cite{paper38},
39~\cite{paper39}, 40~\cite{paper40_unified}, 42~\cite{paper42},
43~\cite{paper43}, 44~\cite{paper44}, 45~\cite{paper45},
46~\cite{paper46}, 47~\cite{paper47}, 48~\cite{paper48}). Builds on
Paper~48 as direct predecessor. Together with Paper~48, completes
the Krein--MS bridge program at both K$^{+}$-weak-form (Paper~48)
and strict-strong-form (Paper~49) rigor.

% =====================================================================
\begin{thebibliography}{99}
% =====================================================================

\bibitem[Allen \& Burtscher(2022)]{allen_burtscher2022}
B.~Allen, A.~Burtscher, ``Properties of the null distance and
spacetime convergence,'' \emph{Int. Math. Res. Not. IMRN} (2022),
no.~10, 7729--7808.

\bibitem[Bisognano \& Wichmann(1976)]{bisognano_wichmann1976}
J.~J.~Bisognano, E.~H.~Wichmann, ``On the duality condition for
quantum fields,'' \emph{J. Math. Phys.} \textbf{17} (1976), 303--321.

\bibitem[Bizi, Brouder \& Besnard(2018)]{bizi_brouder_besnard2018}
N.~Bizi, C.~Brouder, F.~Besnard, ``Space and time dimensions of
algebras with applications to Lorentzian noncommutative geometry and
quantum electrodynamics,'' \emph{J. Math. Phys.} \textbf{59} (2018),
062303. arXiv:1611.07062.

\bibitem[Bousso, Chandrasekaran, Rath \& Shahbazi-Moghaddam(2020)]{bousso_casini_fisher_maldacena2020}
R.~Bousso, V.~Chandrasekaran, P.~Rath, A.~Shahbazi-Moghaddam,
``Gravity dual of Connes cocycle flow,'' \emph{Phys. Rev. D} \textbf{102}
(2020), 066008. arXiv:2007.00230.

\bibitem[Bratteli \& Robinson(1981)]{bratteli_robinson1981}
O.~Bratteli, D.~W.~Robinson, \emph{Operator Algebras and Quantum
Statistical Mechanics II:\ Equilibrium States, Models in Quantum
Statistical Mechanics}, Springer-Verlag, Berlin, 1981.

\bibitem[Camporesi \& Higuchi(1996)]{camporesi_higuchi1996}
R.~Camporesi, A.~Higuchi, ``On the eigenfunctions of the Dirac
operator on spheres and real hyperbolic spaces,''
\emph{J. Geom. Phys.} \textbf{20} (1996), 1--18.

\bibitem[Chamseddine \& Connes(1997)]{chamseddine_connes1997}
A.~H.~Chamseddine, A.~Connes, ``The spectral action principle,''
\emph{Comm. Math. Phys.} \textbf{186} (1997), 731--750.

\bibitem[Che, Perales \& Sormani(2025)]{che_perales_sormani2025}
M.~Che, R.~Perales, C.~Sormani,
``Gromov's compactness theorem for the intrinsic timed-Hausdorff distance,''
\emph{Differential Geometry and its Applications} \textbf{103} (2026), arXiv:2510.13069.

\bibitem[Connes(1973)]{connes1973}
A.~Connes, ``Une classification des facteurs de type III,''
\emph{Ann. Sci. \'Ec. Norm. Sup\'er.} (4) \textbf{6} (1973), 133--252.
[The cocycle Radon--Nikodym derivative + composition rule (C4) used
in \S\ref{sec:thermal_stack}.]

\bibitem[Connes(1994)]{connes1994}
A.~Connes, \emph{Noncommutative Geometry}, Academic Press, San Diego,
1994.

\bibitem[Connes \& Rovelli(1994)]{connes_rovelli1994}
A.~Connes, C.~Rovelli, ``Von Neumann algebra automorphisms and
time-thermodynamics relation in generally covariant quantum theories,''
\emph{Class. Quantum Grav.} \textbf{11} (1994), 2899--2917.

\bibitem[Connes \& van Suijlekom(2021)]{connes_vs2021}
A.~Connes, W.~D.~van~Suijlekom, ``Spectral truncations in
noncommutative geometry and operator systems,''
\emph{Comm. Math. Phys.} \textbf{383} (2021), 2021--2067.
arXiv:2004.14115.

\bibitem[Farsi \& Latr\'emoli\`ere(2024)]{farsi_latremoliere2024}
C.~Farsi, F.~Latr\'emoli\`ere, ``The quantum Gromov--Hausdorff
propinquity for crossed products by amenable group actions,''
\emph{J.~Funct.~Anal.} \textbf{286} (2024), 110293.

\bibitem[Farsi \& Latr\'emoli\`ere(2025)]{farsi_latremoliere2025}
C.~Farsi, F.~Latr\'emoli\`ere, ``Continuity for the spectral
propinquity of the Dirac operators associated with an analytic path
of Riemannian metrics,'' arXiv:2504.11715 (April 2025).

\bibitem[Franco \& Eckstein(2014)]{franco_eckstein2014}
N.~Franco, M.~Eckstein, ``Causality in noncommutative geometry,''
\emph{Class. Quantum Grav.} \textbf{30} (2013), 135007 (and
follow-ups).

\bibitem[Hartle \& Hawking(1976)]{hartle_hawking1976}
J.~B.~Hartle, S.~W.~Hawking, ``Path-integral derivation of black-hole
radiance,'' \emph{Phys.~Rev.~D} \textbf{13} (1976), 2188--2203.

\bibitem[Hekkelman \& McDonald(2024)]{hekkelman_mcdonald2024}
E.~Hekkelman, E.~A.~McDonald, ``A noncommutative integral on
spectrally truncated spectral triples, and a link with quantum
ergodicity,'' arXiv:2412.00628 (2024).

\bibitem[Ketterer(2026)]{ketterer2026}
C.~Ketterer, ``$\ell$-convergence on metric measure spaces and
applications,'' arXiv:2605.11271 (May 2026).

\bibitem[Kubota(2026)]{kubota2026}
T.~Kubota, ``A Lorentzian coarea inequality,'' arXiv:2605.09101
(May 2026).

\bibitem[Kunzinger \& S\"amann(2018)]{kunzinger_samann2018}
M.~Kunzinger, C.~S\"amann, ``Lorentzian length spaces,''
\emph{Ann.~Global Anal.~Geom.} \textbf{54} (2018), 399--447.
arXiv:1711.08990.

\bibitem[Latr\'emoli\`ere(2015)]{latremoliere_metric_propinquity_2015}
F.~Latr\'emoli\`ere, ``The dual Gromov--Hausdorff propinquity,''
\emph{J. Math. Pures Appl.} \textbf{103} (2015), 303--351.

\bibitem[Latr\'emoli\`ere(2018)]{latremoliere2018}
F.~Latr\'emoli\`ere, ``The quantum Gromov--Hausdorff propinquity,''
\emph{Trans. Amer. Math. Soc.} \textbf{368} (2016), 365--411.
arXiv:1302.4058.

\bibitem[Latr\'emoli\`ere(2018/AF)]{latremoliere_pp_2018af}
F.~Latr\'emoli\`ere, ``Convergence of Cauchy sequences for the
covariant Gromov--Hausdorff propinquity,'' \emph{J. Math. Anal. Appl.}
\textbf{469} (2019), 378--404.

\bibitem[Latr\'emoli\`ere(2023)]{latremoliere_metric_st_2017}
F.~Latr\'emoli\`ere, ``The dual Gromov--Hausdorff propinquity for
metric spectral triples,'' \emph{Adv. Math.} \textbf{411} (2023),
108790. arXiv:1811.10843.

\bibitem[Latr\'emoli\`ere(2025)]{latremoliere2025_hypertopology}
F.~Latr\'emoli\`ere, ``The quantum Gromov--Hausdorff hypertopology on
the class of pointed proper quantum metric spaces,''
arXiv:2512.03573 (December 2025).

\bibitem[Latr\'emoli\`ere(2026)]{latremoliere2026_spectral_c1}
F.~Latr\'emoli\`ere, ``Spectral propinquity in the $C^1$ topology,''
arXiv:2603.19128 (March 2026).

\bibitem[Leimbach(2024)]{leimbach_vs2024}
M.~Leimbach, ``Convergence of Peter--Weyl
truncations of compact quantum groups,'' to appear, \emph{J.~Noncommut.
Geom.} (2024); arXiv:2409.16698.

\bibitem[Datta(2009)]{datta2009}
N.~Datta, ``Min- and max-relative entropies and a new entanglement
monotone,'' \emph{IEEE Trans.\ Inf.\ Theory} \textbf{55} (2009),
2816--2826. arXiv:0803.2770.
[The max-divergence chain inequality used in
Theorem~\ref{thm:strict_super_additivity}.]

\bibitem[Lindblad(1975)]{lindblad1975}
G.~Lindblad, ``Completely positive maps and entropy inequalities,''
\emph{Comm. Math. Phys.} \textbf{40} (1975), 147--151.
[Two-state monotonicity of relative entropy; general framing for
the cocycle-entropy-production setup. The load-bearing chain
inequality for Theorem~\ref{thm:strict_super_additivity} is the
max-divergence version~\cite{datta2009}.]

\bibitem[Marcolli \& van Suijlekom(2014)]{marcolli_vs2014}
M.~Marcolli, W.~D.~van~Suijlekom, ``Gauge networks in noncommutative
geometry,'' \emph{J. Geom. Phys.} \textbf{75} (2014), 71--91.
arXiv:1301.3480.

\bibitem[Martinetti(2026)]{martinetti2026_adjacent}
P.~Martinetti, ``Noncommutative causal structures and spectral
triples,'' arXiv:2603.03216 (March 2026).

\bibitem[Minguzzi \& Suhr(2024)]{minguzzi_suhr2024}
E.~Minguzzi, S.~Suhr, ``Bounded Lorentzian metric spaces,''
\emph{Lett.~Math.~Phys.} \textbf{114} (2024), Paper No.~73, arXiv:2209.14384.

\bibitem[Mondino, Ryborz \& S\"amann(2026)]{mondino_ryborz_samann2025}
A.~Mondino, M.~Ryborz, C.~S\"amann, ``Stability of synthetic timelike
curvature bounds,'' arXiv:2605.03172 (May 2026).

\bibitem[Mondino \& S\"amann(2025)]{mondino_samann2025_pointed}
A.~Mondino, C.~S\"amann, ``Lorentzian Gromov--Hausdorff convergence
and pre-compactness,'' arXiv:2504.10380~v4 (December 2025).

\bibitem[M\"uller(2022)]{muller2022}
O.~M\"uller, ``Lorentzian Gromov--Hausdorff convergence and Cauchy
slabs,'' \emph{Comm.~Math.~Phys.} \textbf{391} (2022), 855--882.

\bibitem[Nieuviarts(2026)]{nieuviarts2025_v2}
G.~Nieuviarts, ``Twisted spectral triples and pseudo-Riemannian
spectral geometry, v2,'' arXiv:2512.15450 (December 2025, May 2026 v2).

\bibitem[Rotondo(2026)]{rotondo2026}
M.~Rotondo, ``Thermal time and irreversibility from non-commuting
observables in accelerated quantum systems,'' arXiv:2604.08349
(April~2026).

\bibitem[Sakovich \& Sormani(2024)]{sakovich_sormani2024}
A.~Sakovich, C.~Sormani, ``Timed Gromov--Hausdorff convergence of
spacetimes with timelike curvature bounds,'' (2024). arXiv:2410.16800.

\bibitem[Sewell(1982)]{sewell1982}
G.~L.~Sewell, ``Quantum fields on manifolds:\ PCT and gravitationally
induced thermal states,'' \emph{Ann.~Phys.~(NY)} \textbf{141} (1982),
201--224.

\bibitem[Sormani \& Vega(2016)]{sormani_vega2016}
C.~Sormani, C.~Vega, ``The null distance encodes causality,''
\emph{Class. Quantum Grav.} \textbf{33} (2016), 085001.

\bibitem[Strohmaier(2006)]{strohmaier2006}
A.~Strohmaier, ``On noncommutative and pseudo-Riemannian geometry,''
\emph{J. Geom. Phys.} \textbf{56} (2006), 175--195.

\bibitem[Takesaki(1970)]{takesaki1970}
M.~Takesaki, \emph{Tomita's Theory of Modular Hilbert Algebras and
Its Applications}, Lecture Notes in Mathematics \textbf{128},
Springer-Verlag, 1970.

\bibitem[Tomita(1967)]{tomita1967}
M.~Tomita, ``Standard forms of von Neumann algebras,'' lecture notes,
Fifth Functional Analysis Symposium, Math. Soc. Japan, Sendai, 1967.

\bibitem[Uhlmann(1977)]{uhlmann1977}
A.~Uhlmann, ``Relative entropy and the Wigner--Yanase--Dyson--Lieb
concavity in an interpolation theory,''
\emph{Comm. Math. Phys.} \textbf{54} (1977), 21--32.

\bibitem[Unruh(1976)]{unruh1976}
W.~G.~Unruh, ``Notes on black-hole evaporation,'' \emph{Phys.~Rev.~D}
\textbf{14} (1976), 870--892.

\bibitem[van den Dungen(2016)]{vandungen2016}
K.~van den Dungen, ``Krein spectral triples and the fermionic action,''
\emph{Math. Phys. Anal. Geom.} \textbf{19} (2016), 4. arXiv:1505.01939.

\bibitem[Wilde(2017)]{wilde2017}
M.~M.~Wilde, \emph{Quantum Information Theory}, 2nd ed., Cambridge
University Press, 2017.
[Modern textbook account of the data-processing inequality.]

% --- Internal GeoVac preprints ---

\bibitem[Loutey, internal Paper~24]{paper24}
J.~Loutey, ``The Bargmann--Segal Lattice: $\pi$-Free Discretization
of the Harmonic Oscillator on $S^5$,'' GeoVac internal preprint
Paper~24 (2026), at
\texttt{papers/group3\_foundations/paper\_24\_bargmann\_segal.tex}.

\bibitem[Loutey, internal Paper~29]{paper29}
J.~Loutey, ``The GeoVac Hopf Graphs Are Ramanujan: Ihara Zeta,
Graph-RH, and a Scope Boundary on Selberg-on-Hydrogen,'' GeoVac internal preprint
Paper~29 (2026), at
\texttt{papers/group1\_operator\_algebras/paper\_29\_ramanujan\_hopf.tex}.

\bibitem[Loutey, internal Paper~32]{paper32}
J.~Loutey, ``The GeoVac Spectral Triple: A Synthesis Paper Locking the
Framework into the Marcolli--van~Suijlekom Gauge-Network Lineage,'' GeoVac internal preprint
Paper~32 (2026), at
\texttt{papers/group1\_operator\_algebras/paper\_32\_spectral\_triple.tex}.

\bibitem[Loutey, internal Paper~38]{paper38}
J.~Loutey, ``State-space Gromov--Hausdorff convergence of truncated
Camporesi--Higuchi spectral triples on $S^3$,'' GeoVac internal preprint Paper~38 (2026), released
to Zenodo 2026-05-07. At
\texttt{papers/group1\_operator\_algebras/paper\_38\_su2\_propinquity\_convergence.tex}.

\bibitem[Loutey, internal Paper~39]{paper39}
J.~Loutey, ``Tensor-product propinquity convergence on
$\Tcal_{S^{3}}^{\lambda_{a}}\otimes\Tcal_{S^{3}}^{\lambda_{b}}$,''
GeoVac internal preprint Paper~39 (2026), at
\texttt{papers/group1\_operator\_algebras/paper\_39\_tensor\_propinquity\_convergence.tex}.

\bibitem[Loutey, internal Paper~40]{paper40_unified}
J.~Loutey, ``State-space Gromov--Hausdorff convergence of spectral
truncations of compact Lie groups with bi-invariant metric,'' GeoVac
internal preprint Paper~40 (2026), at
\texttt{papers/group1\_operator\_algebras/paper\_40\_unified\_propinquity\_convergence.tex}.

\bibitem[Loutey, internal Paper~42]{paper42}
J.~Loutey, ``Tomita--Takesaki modular structure on truncated $SU(2)$
spectral triples: four-witness Wick-rotation literal identification
at finite cutoff,'' GeoVac internal preprint Paper~42 (2026), at
\texttt{papers/group1\_operator\_algebras/paper\_42\_modular\_hamiltonian\_four\_witness.tex}.

\bibitem[Loutey, internal Paper~43]{paper43}
J.~Loutey, ``Lorentzian extension of the four-witness Wick-rotation
theorem on truncated $S^3 \times \mathbb{R}$ spectral triples at finite
cutoff,'' GeoVac internal preprint
Paper~43 (2026), at
\texttt{papers/group1\_operator\_algebras/paper\_43\_lorentzian\_extension.tex}.

\bibitem[Loutey, internal Paper~44]{paper44}
J.~Loutey, ``Operator-system extension of the BBB Krein spectral
triple at finite cutoff: propagation number and envelope dependence
on the Camporesi--Higuchi spinor bundle,'' GeoVac internal preprint Paper~44 (2026),
at
\texttt{papers/group1\_operator\_algebras/paper\_44\_lorentzian\_operator\_system.tex}.

\bibitem[Loutey, internal Paper~45]{paper45}
J.~Loutey, ``Lorentzian propinquity on truncated SU(2)
$\times$ U(1)$_{T}$ Krein spectral triples: a degeneracy theorem,'' GeoVac internal
preprint Paper~45 (2026), at
\texttt{papers/group1\_operator\_algebras/paper\_45\_lorentzian\_propinquity.tex}.

\bibitem[Loutey, internal Paper~46]{paper46}
J.~Loutey, ``Strong-form Lorentzian propinquity on
truncated SU(2) $\times$ U(1)$_{T}$ Krein spectral triples,''
GeoVac internal preprint Paper~46 (2026), at
\texttt{papers/group1\_operator\_algebras/paper\_46\_strong\_form\_lorentzian\_propinquity.tex}.

\bibitem[Loutey, internal Paper~47]{paper47}
J.~Loutey, ``Norm-resolvent convergence to the non-compact
Lorentzian Krein spectral triple on $\sthree\times\R_{t}$ and the
two-rate hybrid limit,'' GeoVac internal preprint Paper~47 (2026),
at
\texttt{papers/group1\_operator\_algebras/paper\_47\_two\_rate\_hybrid\_convergence.tex}.

\bibitem[Loutey, internal Paper~48]{paper48}
J.~Loutey, ``Krein-pointed proper quantum metric spaces and the
bridge to Mondino--S\"amann Lorentzian pre-length spaces, with
application to the GeoVac hemispheric wedge,'' GeoVac internal
preprint Paper~48 (2026), at
\texttt{papers/group1\_operator\_algebras/paper\_48\_krein\_ms\_bridge.tex}.

\bibitem[Loutey, internal Paper~50]{paper50}
J.~Loutey, ``Boundary CFT$_3$-on-$S^3$ observables on the truncated
GeoVac spectral triple: partition function, wedge KMS entropy, and
Casini--Huerta--Myers modular Hamiltonian,'' GeoVac internal preprint
Paper~50 (2026), at
\texttt{papers/group1\_operator\_algebras/paper\_50\_cft3\_partition\_function.tex}.

\end{thebibliography}

\end{document}




