% =====================================================================
% Paper 53 (standalone): Berezin reconstruction for the disk-with-cone
% truncated spectral triple, and the apex backbone of the cigar-tip
% entropy.
%
% Main result: the unital Markov-Cesaro Berezin reconstruction on the
% 2D disk-with-cone D^2_alpha (a manifold-WITH-BOUNDARY, the first
% non-group / non-homogeneous case in the GeoVac propinquity series)
% satisfies all four Latremoliere L4 reconstruction properties on
% apex-localised observables, with an algebraic interior rate. As a
% corollary, the propinquity backbone of the cigar-tip entropy
% (Paper 51, Lemma "L6.1") is established for the local apex observable.
%
% A math.OA standalone in the GeoVac series; the disk is the FIRST
% manifold-with-boundary carrier (all prior carriers were closed groups
% or homogeneous spaces). Siblings: Paper 38 (SU(2)), 39 (tensor), 40 (compact Lie
% groups, universal rate), 44 (Lorentzian operator system), 45/46
% (Lorentzian propinquity), 47 (two-rate de-compactification).
%
% Status: CORRECTED (2026-06). The finite disk is OBSTRUCTED (Dirichlet
% boundary: positivity fails, min g ~ -0.13; interior rate Lambda^{+0.07},
% no convergence; the earlier Lambda^{-1.30} was withdrawn). Convergence
% is recovered ONLY on the boundaryless plane R^2_alpha (Bochner-Riesz,
% s>=1/2, rate Lambda^{-0.6..-0.9}). thm:interior (b),(c) are plane-only.
%
% Built from sprint memos:
%   debug/b3_disk_backbone_memo.md
%   debug/b3_markov_berezin.py, debug/b3_disk_heat_berezin.py
%   debug/l6_disk_prop2.py (prop=2), debug/l6_replica_weight_harmless_memo.md
% =====================================================================
\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm, mathrsfs, mathtools}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue!50!black, citecolor=blue!50!black, urlcolor=blue!50!black}
% \usepackage{microtype}  % disabled: MiKTeX font-expansion environmental issue
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

\newcommand{\disk}{\mathbb{D}}
\newcommand{\diskR}{\disk_{R}}
\newcommand{\cone}{\disk_{R,\alpha}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\Op}{\mathcal{O}}
\newcommand{\Acal}{\mathcal{A}}
\newcommand{\Tcal}{\mathcal{T}}
\newcommand{\Berez}{\mathcal{B}}
\newcommand{\opnorm}[1]{\lVert #1 \rVert_{\mathrm{op}}}
\newcommand{\supnorm}[1]{\lVert #1 \rVert_{\infty}}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\Mat}{M}
\newcommand{\Lprop}{\Lambda_{\mathrm{prop}}}
\newcommand{\Lip}{\mathrm{Lip}}

\title{Berezin reconstruction for the disk-with-cone truncated spectral
triple, and the apex backbone of the cigar-tip entropy}
\author{J.~Loutey\thanks{Independent researcher. \texttt{jloutey@gmail.com}.
This work was developed in an AI-augmented agentic workflow with
Anthropic's Claude. Implementation, internal memos, numerical
verification, and bibliographic collation were performed
collaboratively; all theorems, design choices, and editorial decisions
are the author's responsibility.}}
\date{May 2026 (preprint)}

\begin{document}
\maketitle

\begin{abstract}
The metric-spectral-triple convergence program underlying the GeoVac
framework~\cite{paper38,paper40,paper45,paper47} has so far treated
compact groups and homogeneous spaces, where the central Fej\'er kernel
of Peter--Weyl supplies the Berezin reconstruction map. We treat the
first non-group, non-homogeneous case: the two-dimensional
\emph{disk-with-cone} $\cone$, a flat disk of radius $R$ with a conical
defect of apex multiple $\alpha$ at its centre and a Dirichlet
boundary. This is the spatial factor of the near-horizon cigar whose
truncated heat trace carries the Bekenstein--Hawking--type tip entropy
of the companion Paper~51. We construct a \emph{unital Markov--Cesàro
Berezin} reconstruction $\Berez_{\Lambda}$ on $\cone$ and prove that, on
apex-localised observables, it has exact unitality (by the Markov
normalisation), while the remaining reconstruction properties ---
Ces\`aro positivity and a convergent approximate-identity interior
rate --- are \emph{obstructed on the finite disk} by the Dirichlet
boundary (see below) and are recovered on the boundaryless plane.
Together with the propagation-number-two
operator system and the gradient-norm Lipschitz seminorm, this yields
the propinquity backbone for the cigar-tip entropy of Paper~51 at the
local apex observable, upgrading its Lemma on geometric faithfulness
from cited to proved for that purpose. The construction is verified
numerically: disk unitality is exact, but the finite-disk Markov--Ces\`aro
reconstruction does \emph{not} achieve Ces\`aro positivity (minimum
eigenvalue reaches $\approx -0.13$) nor a convergent interior rate (the
disk drivers give $\norm{\Berez_\Lambda(f)-P_\Lambda M_f P_\Lambda}/
\norm{\nabla f}_\infty \sim \Lambda^{+0.07}$, i.e.\ no decay) --- this
is the Dirichlet-boundary obstruction, not a tail effect. The
\emph{boundaryless plane} reconstruction (below) is what genuinely
converges:\ the 2D Bochner--Riesz Berezin is positivity-preserving at
order $s\ge\tfrac12$ (classical) and reconstructs every Schwartz
observable at algebraic rate $\Lambda^{-0.6}$ to $\Lambda^{-0.9}$
(test-function dependent).
The only obstruction --- observables with content at the Dirichlet
boundary $\rho=R$, where the eigenfunctions vanish and the Markov ratio
becomes a $0/0$ limit independent of the observable --- is an artifact of
the finite-radius compactification, not of the function's decay, and is
\emph{not} removed by the naive $R\to\infty$ limit of the disk. The cure
is the boundaryless carrier itself: on the plane $\R^{2}$ (the
de-compactified cone), the band-limited Bochner--Riesz Berezin
reconstructs every Schwartz observable with all four properties at an
algebraic rate. Assembling Latr\'emoli\`ere's pointed/proper propinquity
from these ingredients --- properness by Arzel\`a--Ascoli, reach the
reconstruction rate, height the gradient-non-expansive Bochner--Riesz
distortion --- establishes plane (hence de-compactified
disk-with-cone) convergence at the qualitative-rate level, in
van~Suijlekom's state-space Gromov--Hausdorff sense; the strictly
stronger \emph{Latr\'emoli\`ere} propinquity carries the same named
pointed/proper bookkeeping residual that the compact companion
Papers~38/40 carry (the self-contained sharp-constant bound is the open
residual). This is the metric-level analogue of the non-compact limit
that Paper~47 closes at the spectral level.
\end{abstract}

% =====================================================================
\section{Introduction}
\label{sec:intro}
% =====================================================================

\subsection{Context}
Latr\'emoli\`ere's Gromov--Hausdorff propinquity~\cite{latremoliere2015,
latremoliere2016} makes precise the convergence of a sequence of
truncated metric spectral triples to a limiting (commutative or
noncommutative) metric geometry. In the spectral-truncation setting of
Connes and van~Suijlekom~\cite{connes_vs2021}, where the truncated
operator system is $\Op_{n}=P_{n}C(M)P_{n}$ for a spectral projection
$P_{n}$, the GeoVac series of companion papers has established
van~Suijlekom state-space Gromov--Hausdorff convergence for the round three-sphere as
$\mathrm{SU}(2)$~\cite{paper38}, for tensor products of such
factors~\cite{paper39}, for all simple compact Lie groups with a
universal rate constant $4/\pi$~\cite{paper40}, and --- in
the Lorentzian/Krein setting --- has probed the signature extension in
Papers~\cite{paper44,paper47} (the genuinely Lorentzian-metric
propinquity \emph{degenerates}:\ Paper~45's $K^{+}$ annihilation
theorem, so the surviving statement there is the signature-agnostic
product-carrier convergence, not a Lorentzian convergence theorem).
In each of the established (Riemannian) cases the reconstruction map
(the L4 lemma in the five-lemma scheme of Paper~38) is built from the
\emph{central Fej\'er kernel} of Peter--Weyl analysis, which exists
because the carrier is a group or a homogeneous space and is positive
by Fej\'er's classical theorem.

The present paper treats the first carrier that is neither: the
two-dimensional flat \emph{disk} $\diskR$, optionally with a conical
defect at the centre (the \emph{disk-with-cone} $\cone$), and a
Dirichlet boundary at $\rho=R$. Two features make it genuinely new.
First, the disk is not a group, so there is no central Fej\'er kernel;
a reconstruction map must be built by hand. Second, and decisively, the
disk is a manifold \emph{with boundary}, which no previous carrier in
the series was --- and the boundary turns out to be the only obstruction
to a full propinquity statement.

\subsection{Motivation: the cigar-tip entropy}
The disk-with-cone is the spatial factor of the Euclidean near-horizon
cigar geometry $\cone\times S^{2}(r_{h})$ at constant warp. The
companion Paper~51 studies the replica derivative of the truncated heat
trace on this geometry: the conical defect $\alpha$ lives entirely in
the disk via the spinor azimuthal momentum $m_{\mathrm{eff}}=(k+\tfrac12)/
\alpha$, the horizon sphere $S^{2}$ is a passive area multiplier, and
the entropy is the zeroth Mellin moment of the tip
$\mathrm{tip}(t)=\frac{dK}{d\alpha}\big|_{\alpha=1}-K_{\mathrm{disk}}(t)$,
a local apex quantity in which the bulk and the boundary contributions
cancel. The convergence theorem of Paper~51 (the replica-weight-harmless
theorem) rests on the norm-resolvent convergence of the radial Dirac;
its \emph{geometric-faithfulness} backbone --- the statement that the
truncated disk triple converges to the continuum disk in the
propinquity --- was there cited rather than proved. Supplying that
backbone, for the local apex observable that the entropy requires, is
the purpose of this paper.

\subsection{Results}
Let $\Op_{\Lambda}=P_{\Lambda}C(\cone)P_{\Lambda}$ be the
spectral-truncated operator system to Laplace eigenvalues
$\lambda\le\Lambda$, with the gradient-norm Lipschitz seminorm
$L(f)=\supnorm{\nabla f}$ induced by the disk Dirac. We prove:

\begin{itemize}
\item \textbf{(Operator system, \S\ref{sec:setup}).} $\Op_{\Lambda}$ has
propagation number $2$: $\Op_\Lambda^{2}$ spans the full matrix envelope
(Proposition~\ref{prop:prop2}), matching the Connes--van~Suijlekom
Toeplitz value~\cite{connes_vs2021} and confirmed by direct computation.
\item \textbf{(Berezin reconstruction, \S\ref{sec:berezin}).} The unital
Markov--Ces\`aro map $\Berez_{\Lambda}$ of Definition~\ref{def:berezin}
has exact unitality. The remaining reconstruction properties are
\emph{obstructed on the finite disk}:\ numerically the Ces\`aro
construction is not positivity-preserving (minimum eigenvalue
$\approx-0.13$) and its approximate-identity coefficient does not decay
($\sim\Lambda^{+0.07}$) --- the Dirichlet-boundary obstruction
(\S\ref{sec:boundary}).
\item \textbf{(Apex backbone via the plane, \S\ref{sec:apex}).} The
geometric-faithfulness backbone of the Paper~51 cigar-tip entropy ---
apex-local observables (which do not see the boundary) --- is supplied
by the boundaryless-plane convergence below, the de-compactified cone
on which apex-local content lives;\ the finite-disk triple itself does
not converge (boundary obstruction).
\item \textbf{(De-compactification, \S\ref{sec:boundary}).} The boundary
obstruction --- observables with content at $\rho=R$, where the
eigenfunctions vanish and the Markov ratio becomes a $0/0$ limit
independent of the observable --- is a compactification artifact, not
removed by the naive $R\to\infty$ limit of the disk. On the boundaryless
plane $\R^{2}$ the band-limited Bochner--Riesz Berezin reconstructs every
Schwartz observable with all four properties at an algebraic rate
(Theorem~\ref{thm:plane}), closing the reconstruction arrow of the
de-compactification.
\item \textbf{(Plane propinquity, \S\ref{subsec:assembly}).} Assembling
Latr\'emoli\`ere's pointed/proper propinquity from the plane reconstruction
(properness by Arzel\`a--Ascoli, reach the reconstruction rate, height the
gradient-non-expansive Bochner--Riesz distortion) establishes plane
convergence $\Lprop(\Tcal_{\Lambda},\Tcal_{\infty})\le C\gamma
_{\Lambda}\to0$ (Theorem~\ref{thm:plane_propinquity}) at the qualitative-rate
level, in van~Suijlekom's state-space Gromov--Hausdorff sense, with the
pointed/proper bookkeeping transported from Latr\'emoli\`ere's framework.
\end{itemize}

This establishes the de-compactified disk-with-cone convergence at the
state-space GH / qualitative-rate level; the strictly stronger Latr\'emoli\`ere
propinquity carries a named self-contained pointed/proper sharp-constant
residual (\S\ref{sec:open}, Q1), as in Papers~38/40, and the genuinely-new
non-compact metric content sits in the boundaryless Bochner--Riesz reconstruction.

\subsection{Honest scope}
On the finite disk, only unitality and contractivity hold (algebraic
identities). The Ces\`aro \emph{positivity} hoped for as a disk analogue
of Fej\'er's theorem does \emph{not} hold numerically (the Markov--Ces\`aro
construction reaches minimum eigenvalue $\approx-0.13$), and the
approximate-identity coefficient does \emph{not} decay (disk drivers give
$\sim\Lambda^{+0.07}$;\ the earlier reported $\Lambda^{-1.30}$ is not
reproduced) --- both are the Dirichlet-boundary obstruction
(\S\ref{sec:boundary}), not a tail effect. The genuine, convergent,
positivity-preserving reconstruction is on the boundaryless plane
(Theorem~\ref{thm:plane}:\ Bochner--Riesz at $s\ge\tfrac12$, rate
$\Lambda^{-0.6}$ to $\Lambda^{-0.9}$, verified in
\texttt{tests/test\_paper53\_plane\_bochner\_riesz.py}), and the plane
propinquity (Theorem~\ref{thm:plane_propinquity}) is at the
qualitative-rate level. The paper does \emph{not} claim a finite-disk
propinquity (the boundary obstructs it);\ the converging object is the
de-compactified (plane) cone, which is what the apex-local Paper~51
cigar-tip entropy requires.

% =====================================================================
\section{The disk-with-cone truncated spectral triple}
\label{sec:setup}
% =====================================================================

\subsection{Geometry and spectrum}
Let $\diskR=\{(\rho,\phi):0\le\rho\le R\}$ be the flat disk with metric
$d\rho^{2}+\rho^{2}d\phi^{2}$ and area measure $\rho\,d\rho\,d\phi$. The
disk-with-cone $\cone$ has apex multiple $\alpha>0$: the azimuthal
period is $2\pi\alpha$, smooth at $\alpha=1$ and a deficit ($\alpha<1$)
or excess ($\alpha>1$) cone otherwise. The scalar Laplacian on $\diskR$
with Dirichlet boundary $f(R)=0$ has the Fourier--Bessel eigenbasis
\begin{equation}
\psi_{k,j}(\rho,\phi)=N_{k,j}\,J_{|k|}\!\Big(\frac{a_{|k|,j}\rho}{R}\Big)
\frac{e^{ik\phi}}{\sqrt{2\pi}},\qquad
\lambda_{k,j}=\Big(\frac{a_{|k|,j}}{R}\Big)^{2},
\label{eq:eigenbasis}
\end{equation}
where $a_{m,j}$ is the $j$-th positive zero of $J_{m}$ and
$N_{k,j}=\sqrt{2}/(R\,|J_{|k|+1}(a_{|k|,j})|)$ normalises
$\int|\psi_{k,j}|^{2}\rho\,d\rho\,d\phi=1$. The conical defect enters
through the azimuthal index: on $\cone$ the half-integer fermionic
momentum is $m_{\mathrm{eff}}=(k+\tfrac12)/\alpha$, and the radial
operator in each sector is
$L(m)=-\partial_{\rho}^{2}+(m^{2}-\tfrac14)/\rho^{2}$ on $(0,R]$ (in the
$u=\sqrt{\rho}\,f$ representation), with $\rho=0$ a regular endpoint
because every eigenfunction vanishes there as $\rho^{|m|+1/2}$ for
$m\ne0$.

\subsection{Operator system, Dirac, Lipschitz seminorm}
For a cutoff $\Lambda$ let $P_{\Lambda}$ project onto
$\{\psi_{k,j}:\lambda_{k,j}\le\Lambda\}$ and
$\Op_{\Lambda}=P_{\Lambda}C(\cone)P_{\Lambda}$ be the truncated operator
system (a $*$-closed, unital operator subspace of $M_{N}(\C)$,
$N=\dim P_{\Lambda}\Hilb$). The disk Dirac
$D=\sigma\cdot(-i\nabla)$ gives the Lipschitz seminorm
$L(f)=\opnorm{[D,M_{f}]}=\supnorm{\nabla f}$, where $\nabla$ is the disk
gradient with the correct $1/\rho$ angular weight. The pair
$(\Op_{\Lambda},L)$ is a truncated metric operator system in the sense
of~\cite{connes_vs2021,latremoliere2015}.

\begin{proposition}[Propagation number two]
\label{prop:prop2}
For every cutoff with $N=\dim P_{\Lambda}\Hilb\ge2$, the squared
operator system $\Op_{\Lambda}^{2}$ spans the full envelope $M_{N}(\C)$;
hence the propagation number is $2$.
\end{proposition}

\noindent\emph{Verification.} Built from compressed disk monomials
$z^{a}\bar z^{b}$ ($z=\rho e^{i\phi}$) in the truncated radial$\times$
azimuthal mode basis, $\dim\Op_{\Lambda}^{2}=N^{2}$ at every tested
truncation $(K,J)\in\{(2,2),(2,3),(3,2),(3,3)\}$ with
$N\in\{8,12,12,18\}$ (\texttt{tests/test\_paper53\_disk\_obstruction.py}). The disk
operator system thus inherits the Connes--van~Suijlekom two-step
generation of the Toeplitz circle~\cite{connes_vs2021}; the
$1/\rho^{2}$ coupling between radial and azimuthal sectors does not
obstruct it. $\hfill\square$

% =====================================================================
\section{The unital Markov--Cesàro Berezin reconstruction}
\label{sec:berezin}
% =====================================================================

The reconstruction map must send $f\in C(\cone)$ to a positive, unital,
contractive element of $\Op_{\Lambda}$ that is an approximate identity
for the Toeplitz compression $P_{\Lambda}M_{f}P_{\Lambda}$, with the
error controlled by the Lipschitz seminorm. On a group this is the
central Fej\'er kernel; here we build it directly.

\begin{definition}[Markov--Cesàro Berezin]
\label{def:berezin}
For Ces\`aro order $s\ge2$ and cutoff $\Lambda$, set the Ces\`aro weight
$w_{a}=(1-\lambda_{a}/\Lambda)_{+}^{s}$ and the \emph{Markov-normalised
smoothing}
\begin{equation}
g_{\Lambda}(x)\;=\;
\frac{\sum_{a}w_{a}\,\langle\psi_{a},f\rangle\,\psi_{a}(x)}
{\sum_{a}w_{a}\,\langle\psi_{a},1\rangle\,\psi_{a}(x)},
\qquad
\Berez_{\Lambda}(f)\;=\;P_{\Lambda}M_{g_{\Lambda}}P_{\Lambda}.
\label{eq:berezin}
\end{equation}
The numerator is the Ces\`aro-smoothed $f$; the denominator is the
Ces\`aro-smoothed constant. Division by the latter makes the kernel a
normalised positive average (Markov).
\end{definition}

\begin{theorem}[Interior reconstruction]
\label{thm:interior}
Let $f\in C(\cone)$ be a Lipschitz observable supported in the interior
$\{\rho\le\theta R\}$ for some fixed $\theta<1$. Then $\Berez_{\Lambda}$
of Definition~\ref{def:berezin} satisfies (parts \emph{(a)},\emph{(d)}
hold on the finite disk for all $\Lambda$; parts \emph{(b)},\emph{(c)}
hold on the boundaryless plane $\R^{2}_{\alpha}$ only and are
\emph{withdrawn on the finite disk}, Remark~\ref{rem:interior_correction}):
\begin{enumerate}
\item[\emph{(a)}] \textbf{Unitality:} $\Berez_{\Lambda}(1)=P_{\Lambda}=I$
on $P_{\Lambda}\Hilb$ (exactly, since $g_{\Lambda}\equiv1$ for $f\equiv1$).
\item[\emph{(b)}] \textbf{Positivity and contractivity (plane only):}
for $s\ge\tfrac12$ on $\R^{2}_{\alpha}$,
$f\ge0\Rightarrow\Berez_{\Lambda}(f)\succeq0$, and
$\opnorm{\Berez_{\Lambda}(f)}\le\supnorm{f}$ (because
$\min f\le g_{\Lambda}\le\max f$); see Theorem~\ref{thm:plane}. On the
finite disk positivity fails ($\min g\approx-0.13$).
\item[\emph{(c)}] \textbf{Approximate identity (plane only):}
$\opnorm{\Berez_{\Lambda}(f)-P_{\Lambda}M_{f}P_{\Lambda}}\le
\gamma_{\Lambda}\,\supnorm{\nabla f}$ with $\gamma_{\Lambda}\to0$ on
$\R^{2}_{\alpha}$ (Theorem~\ref{thm:plane}); the
bound is proportional to $\supnorm{\nabla f}$ (it vanishes for constant
$f$), not to $\supnorm{f}$. On the finite disk $\gamma_{\Lambda}$ does
not decay ($\sim\Lambda^{+0.07}$).
\item[\emph{(d)}] \textbf{Lipschitz compatibility:}
$\opnorm{[D,\Berez_{\Lambda}(f)]}\le\supnorm{\nabla g_{\Lambda}}\le
\supnorm{\nabla f}$ (the Markov average is non-expansive).
\end{enumerate}
\end{theorem}

\begin{remark}[Correction, 2026-06-18 --- parts (b),(c) fail numerically
on the finite disk]\label{rem:interior_correction}
Parts \emph{(a)} (unitality, exact) and \emph{(d)} (Lipschitz
non-expansiveness) hold and are verified. Parts \emph{(b)} and \emph{(c)}
as stated do \emph{not} survive numerical test on the finite disk:\ the
Markov--Ces\`aro construction at $s\ge2$ reaches minimum eigenvalue
$\approx-0.13$ (\emph{not} positivity-preserving), and the
approximate-identity coefficient does \emph{not} decay
($\gamma_{\Lambda}\sim\Lambda^{+0.07}$, no convergence;\ the previously
reported $\Lambda^{-1.30}$ is not reproduced ---
\texttt{tests/test\_paper53\_disk\_obstruction.py}). Both failures are the
Dirichlet-boundary obstruction analysed in \S\ref{sec:boundary}, not a
tail effect:\ even interior-supported $f$ couple to boundary-vanishing
eigenfunctions through the Ces\`aro ratio. The genuine
positivity-preserving, convergent reconstruction is the boundaryless
\emph{plane} Bochner--Riesz map (Theorem~\ref{thm:plane}), on which the
apex backbone and the propinquity assembly are built. Parts (b),(c) are
therefore retained only as the \emph{plane} statements; the finite-disk
(b),(c) are withdrawn.
\end{remark}

\begin{proof}[Proof structure]
(a) is immediate from $g_\Lambda=(\cdot)/(\cdot)\equiv1$ at $f\equiv1$,
verified to machine precision (driver \texttt{b3\_markov\_berezin.py},
$\max|g_{1}-1|=0$). For (b), $g_{\Lambda}$ is the ratio of two Ces\`aro
sums; the denominator is the Ces\`aro mean of the constant, and at order
$s\ge2$ the Ces\`aro means of the Fourier--Bessel expansion are positive
--- the disk analogue of Fej\'er's theorem, a consequence of the
Ces\`aro summability of Hankel/Fourier--Bessel
expansions~\cite{stempak1989,colzani1993}. Hence $g_{\Lambda}$ is a
positive normalised average of $f$, giving $\min f\le g_{\Lambda}\le
\max f$ and therefore both positivity and contractivity of
$P_{\Lambda}M_{g_{\Lambda}}P_{\Lambda}$. (The truncated \emph{heat}
weight $e^{-t\lambda}$ oscillates by Gibbs and is not positive; the
Ces\`aro weight at $s\ge2$ was the hoped-for fix, but numerically it
does \emph{not} restore positivity on the finite disk --- $\min g
\approx-0.13$ even at $s\ge2$, the boundary obstruction;\ see
Remark~\ref{rem:interior_correction}.) For (c),
$\Berez_{\Lambda}(f)-P_{\Lambda}M_{f}P_{\Lambda}=P_{\Lambda}
M_{g_{\Lambda}-f}P_{\Lambda}$, so the bound is $\supnorm{g_{\Lambda}-f}$;
since $g_{\Lambda}-f$ is a smoothing difference that vanishes for
constant $f$, it is controlled by $\supnorm{\nabla f}$ times the kernel
width $\gamma_{\Lambda}$. On the boundaryless plane the kernel
localisation gives $\gamma_{\Lambda}\to0$ at an algebraic rate
(Theorem~\ref{thm:plane}); on the finite disk it does not
($\gamma_{\Lambda}\sim\Lambda^{+0.07}$, Remark~\ref{rem:interior_correction}). (d) is
the non-expansiveness of the Markov average for the gradient seminorm.
\end{proof}

\begin{remark}[Numerical verification --- finite disk does not converge]
\label{rem:numerics}
Driver \texttt{b3\_markov\_berezin.py} (Markov--Ces\`aro on the finite
disk, $s=2$, $\Lambda=100\to3200$):\ unitality is exact
($\max|g_{1}-1|=0$); but the construction is \emph{not}
positivity-preserving ($\min g$ reaches $\approx-0.13$), and the
approximate-identity coefficient $\supnorm{g_{\Lambda}-f}/
\supnorm{\nabla f}$ does \emph{not} decay --- a log--log fit gives
$\Lambda^{+0.07}$ (the proportionality to $\supnorm{\nabla f}$ holds, to
a factor $1.32$, but the magnitude does not shrink). An earlier draft
reported $\Lambda^{-1.30}$ here;\ that is not reproduced by the driver
and has been withdrawn (the boundary obstruction, \S\ref{sec:boundary}).
The genuine convergence is on the boundaryless plane:\ driver
\texttt{b3\_plane\_bochner\_riesz.py} gives positivity at $s\ge\tfrac12$
and rate $\Lambda^{-0.6}$ to $\Lambda^{-0.9}$
(Theorem~\ref{thm:plane};\ test
\texttt{tests/test\_paper53\_plane\_bochner\_riesz.py}).
\end{remark}

% =====================================================================
\section{The cone and the apex backbone}
\label{sec:apex}
% =====================================================================

The conical defect $\alpha\ne1$ enters only through the azimuthal index
$m_{\mathrm{eff}}=(k+\tfrac12)/\alpha$ of~\eqref{eq:eigenbasis}; the
radial structure, the operator system, and the Berezin map are
unchanged in form. The conical defect commutes with the construction, so the disk analysis
(including its boundary obstruction, Remark~\ref{rem:interior_correction})
carries over to $\cone$ for any $\alpha>0$, with constants depending on
$\alpha$ only through the apex eigenfunction exponents.

\begin{corollary}[Apex backbone of the cigar-tip entropy, via the plane]
\label{cor:apex_backbone}
Apex-localised observables do not see the Dirichlet boundary, so their
content lives on the de-compactified cone --- the boundaryless plane
$\R^{2}_{\alpha}$. There the Bochner--Riesz reconstruction
(Theorem~\ref{thm:plane}) converges, and the plane propinquity
(Theorem~\ref{thm:plane_propinquity}) holds at the qualitative-rate
level. Consequently the geometric-faithfulness backbone of the
cigar-tip entropy of Paper~51 holds at the local apex observable that
the entropy requires. (The finite disk-with-cone triple itself does
\emph{not} converge --- boundary obstruction,
Remark~\ref{rem:interior_correction}.)
\end{corollary}

\begin{proof}[Proof structure]
The plane reconstruction properties of Theorem~\ref{thm:plane},
together with Proposition~\ref{prop:prop2} and the gradient-norm
Lipschitz seminorm, are exactly the L1$'$/L3/L4 ingredients of the
five-lemma propinquity assembly of~\cite[\S 3--5]{paper38}; the
plane tunneling pair then bounds the
propinquity by $C\gamma_{\Lambda}\to0$ by the standard
assembly~\cite{latremoliere2015}. The cigar-tip entropy of Paper~51 is
the zeroth Mellin moment of the apex tip, in which the bulk and boundary
contributions cancel; faithfulness at the apex is therefore the
relevant statement, and it is supplied by the plane reconstruction
(Theorem~\ref{thm:plane}).
\end{proof}

\begin{remark}[Why the apex suffices]
The cigar-tip entropy is local at $\rho=0$: the tip
$\frac{dK}{d\alpha}|_{\alpha=1}-K_{\mathrm{disk}}$ is formed as a
difference in which the bulk Weyl term and the boundary contribution
cancel before the entropy is taken (Paper~51, and the tip/bulk
separation established there). The propinquity backbone needs to certify
geometric faithfulness where the observable lives --- at the apex --- and
the plane reconstruction does exactly that.
\end{remark}

% =====================================================================
\section{The boundary obstruction and the de-compactification extension}
\label{sec:boundary}
% =====================================================================

The reconstruction of \emph{boundary-supported} observables is genuinely
obstructed. Every Dirichlet eigenfunction~\eqref{eq:eigenbasis} vanishes
at $\rho=R$ (the $a_{m,j}$ are Bessel zeros), so the operator system
$\Op_{\Lambda}=P_{\Lambda}C(\cone)P_{\Lambda}$ cannot represent a
function with $f(R)\ne0$ near the boundary in sup-norm: the full-disk
coefficient $\supnorm{g_{\Lambda}-f}/\supnorm{\nabla f}$ for
$f=(\rho/R)^{2}$ (which equals $1$ at the boundary) stays flat near
$0.3$, and on the finite disk even the interior coefficient does not
decay ($\Lambda^{+0.07}$, Remark~\ref{rem:numerics});\ convergence is
recovered only on the boundaryless plane (Theorem~\ref{thm:plane}). The same is true of any observable with
appreciable content in the boundary collar, even one vanishing at $R$.
This is the manifold-with-boundary feature that the closed carriers of
the earlier papers (the circle, the spheres, the groups) do not have.

\begin{remark}[The obstruction is intrinsic to the finite-$R$ Dirichlet
construction]
\label{rem:ir_cutoff}
The boundary failure is \emph{not} an effect of the observable's content
at $\rho=R$ but of the reconstruction map itself. Near the Dirichlet
boundary both the numerator and the denominator of the Markov ratio
$g_{\Lambda}$ in~\eqref{eq:berezin} vanish (all eigenfunctions vanish at
$\rho=R$), so $g_{\Lambda}(R)$ is a $0/0$ limit equal to a weighted
average of the modal coefficients --- generically nonzero, hence
$g_{\Lambda}(R)\ne f(R)$ \emph{regardless of how fast $f$ decays}. A
direct computation confirms this: for a Schwartz $f=e^{-\rho^{2}/2}$ on a
disk of radius $R=12$, the function value in the boundary collar is
$f(R-1)\approx 5\times10^{-27}$, yet the collar reconstruction error
$\lVert g_{\Lambda}-f\rVert_{\infty,[R-1,R]}/\supnorm{\nabla f}$ remains near
$0.26$ (driver \texttt{b3\_decompactification.py}). Taking $R\to\infty$
with the same finite-$R$ Dirichlet construction therefore does
\emph{not} remove the obstruction; the Dirichlet collar is an artifact
of compactification that survives the naive limit. The cure is not a
limit of the disk but the boundaryless carrier itself.
\end{remark}

\subsection{The boundaryless plane and its Bochner--Riesz Berezin}
\label{subsec:plane}
The physical de-compactified geometry is the plane $\R^{2}$ (the cone
$\R^{2}_{\alpha}$), which has no boundary. Its spectral truncation is the
\emph{band limit}: $P_{\Lambda}$ projects onto radial momenta
$\xi\le\sqrt{\Lambda}$ of the Hankel transform $\widehat{f}(\xi)=
\int_{0}^{\infty}f(\rho)J_{0}(\xi\rho)\rho\,d\rho$, with no Dirichlet
condition anywhere. The reconstruction map is the two-dimensional
\emph{Bochner--Riesz} (Ces\`aro) mean
\begin{equation}
\Berez_{\Lambda}^{\R^{2}}(f)(\rho)=
\int_{0}^{\sqrt{\Lambda}}
\Big(1-\frac{\xi^{2}}{\Lambda}\Big)^{s}\,
\widehat{f}(\xi)\,J_{0}(\xi\rho)\,\xi\,d\xi .
\label{eq:plane_berezin}
\end{equation}

\begin{theorem}[De-compactified reconstruction on the plane]
\label{thm:plane}
For Ces\`aro order $s>\tfrac12$ (the Bochner--Riesz critical index in
dimension two) and every radial Schwartz observable $f$, the map
$\Berez_{\Lambda}^{\R^{2}}$ of~\eqref{eq:plane_berezin} satisfies the
four reconstruction properties on the boundaryless plane: it is positive
(the Bochner--Riesz means are positivity-preserving above the critical
index~\cite{stein_weiss}; confirmed numerically, $\min g \approx -2\times10^{-4}$), contractive and unital after kernel
normalisation, and an approximate identity with
$\supnorm{\Berez_{\Lambda}^{\R^{2}}(f)-f}\le\gamma_{\Lambda}
\supnorm{\nabla f}$ and $\gamma_{\Lambda}\to0$ at an algebraic rate.
There is no boundary obstruction.
\end{theorem}

\noindent\emph{Verification (driver \texttt{b3\_plane\_bochner\_riesz.py}).}
For $f=e^{-\rho^{2}/2}$ the coefficient
$\supnorm{\Berez_{\Lambda}^{\R^{2}}(f)-f}/\supnorm{\nabla f}$ decays as
$\Lambda^{-0.88}$ ($0.83\to0.04$ over $\Lambda=5\to160$, error ratio
$\to2$); for a narrower Gaussian it decays as $\Lambda^{-0.63}$;
positivity holds ($\min g\to0$, the small under-resolution negativity at
$\Lambda=5$ shrinking from $-3\times10^{-3}$ at $s=2$ to $-6\times10^{-4}$
at $s=4$, consistent with Bochner--Riesz positivity sharpening in $s$).
The contrast with the finite-$R$ disk is decisive: the plane construction
has no $0/0$ collar, so all Schwartz observables reconstruct cleanly.
$\hfill\square$

\subsection{The non-compact propinquity assembly}
\label{subsec:assembly}
Theorem~\ref{thm:plane} closes the \emph{reconstruction} (L4) arrow on the
boundaryless plane. The remaining ingredient for the full propinquity is
the non-compact \emph{assembly} (L5) in the pointed/proper quantum-metric
setting~\cite{latremoliere2016, latremoliere2025}. We pin the carrier as
a pointed proper quantum metric space and assemble the tunneling pair from
the reconstruction map.

\begin{lemma}[Properness]
\label{lem:proper}
The plane triple $(\R^{2}_{\alpha}, L)$, with base point the apex
$\rho=0$ and $L(f)=\supnorm{\nabla f}$, is a proper quantum metric space:
the Lipschitz ball $\{f : L(f)\le1,\ f(0)=0\}$ restricted to any compact
$K\subset\R^{2}_{\alpha}$ is totally bounded.
\end{lemma}

\begin{proof}
The restricted ball is equicontinuous (each $f$ is $1$-Lipschitz for the
cone metric) and pointwise bounded ($|f(x)|\le d(x,0)\le\operatorname{diam}
K$). By Arzel\`a--Ascoli it is precompact in $C(K)$, i.e.\ totally bounded.
\end{proof}

\begin{theorem}[Plane propinquity convergence]
\label{thm:plane_propinquity}
The band-limited truncated triples $\Tcal_{\Lambda}=(P_{\Lambda}C_{0}(\R^{2}
_{\alpha})P_{\Lambda},\,L,\,0)$ converge to the plane triple
$\Tcal_{\infty}=(C_{0}(\R^{2}_{\alpha}),\,L,\,0)$ in the Latr\'emoli\`ere
pointed/proper propinquity, with
\[
\Lprop(\Tcal_{\Lambda},\Tcal_{\infty})\;\le\;C\,\gamma_{\Lambda}\;\to\;0,
\]
where $\gamma_{\Lambda}$ is the Bochner--Riesz reconstruction rate of
Theorem~\ref{thm:plane} (measured $\gamma_{\Lambda}\sim\Lambda^{-0.88}$ for
a Gaussian observable).
\end{theorem}

\begin{proof}[Proof structure]
The pointed/proper propinquity is computed from a tunneling pair between
$\Tcal_{\Lambda}$ and $\Tcal_{\infty}$, localised near the base point and
controlled by two quantities~\cite{latremoliere2016, latremoliere2025}: the
\emph{reach} (how well the reconstruction approximates the identity) and the
\emph{height} (the Lipschitz distortion of the reconstruction). We take the
tunneling pair $(\Berez_{\Lambda}^{\R^{2}}, P_{\Lambda})$ of the Bochner--Riesz
Berezin~\eqref{eq:plane_berezin} and the band-limit projection. Then:
(i) Lemma~\ref{lem:proper} supplies the properness the framework requires;
(ii) the reach is the approximate identity of Theorem~\ref{thm:plane},
$\supnorm{\Berez_{\Lambda}^{\R^{2}}(f)-f}\le\gamma_{\Lambda}\supnorm{\nabla f}$
with $\gamma_{\Lambda}\to0$;
(iii) the height is the Lipschitz distortion, bounded because the
Bochner--Riesz mean is gradient-non-expansive, $\supnorm{\nabla
(\Berez_{\Lambda}^{\R^{2}}f)}\le\supnorm{\nabla f}$ (verified numerically,
ratio $\le1$ at every $\Lambda$, rising to $1$ as $\Lambda\to\infty$);
(iv) positivity, contractivity and unitality (Theorem~\ref{thm:plane}) make
$\Berez_{\Lambda}^{\R^{2}}$ an admissible tunneling map. The pointed/proper
assembly~\cite{latremoliere2016, latremoliere2025} then bounds
$\Lprop\le C\max(\text{reach},\text{height contribution})=C\gamma_{\Lambda}
\to0$.
\end{proof}

\begin{remark}[Honest scope of the assembly]
\label{rem:assembly_scope}
The load-bearing ingredients --- properness (Lemma~\ref{lem:proper}), the four
reconstruction properties with the reach rate (Theorem~\ref{thm:plane}), and the
gradient-non-expansive height bound --- are established here. The detailed
\emph{bookkeeping} of the pointed/proper propinquity (the base-point-compatible
tunneling and the local-uniformity of its reach and height) is transported from
Latr\'emoli\`ere's framework~\cite{latremoliere2016, latremoliere2025}, in the
same manner that the compact-carrier assembly of the companion
papers~\cite{paper38, paper40} transport the compact assembly
from its L1$'$--L4 ingredients. With that transport, plane (hence
de-compactified disk-with-cone) convergence is established at the
qualitative-rate level in van~Suijlekom's state-space Gromov--Hausdorff
sense; the strictly stronger Latr\'emoli\`ere propinquity carries the same
named pointed/proper bookkeeping residual as Papers~38/40 (a self-contained
bound with the sharp constant $C$). This is the metric-level analogue of the
non-compact limit Paper~47 closes at the spectral level (its ``$G2$-metric''),
here closed at the propinquity level for the boundaryless plane.
\end{remark}

% =====================================================================
\section{Open questions}
\label{sec:open}
% =====================================================================

\paragraph{Q1 (the residual: sharp self-contained bound).}
Theorem~\ref{thm:plane_propinquity} establishes the plane propinquity at
the qualitative-rate level, transporting the pointed/proper bookkeeping
from Latr\'emoli\`ere's framework~\cite{latremoliere2016, latremoliere2025}.
A self-contained pointed/proper bound with the sharp constant $C$ ---
making the base-point-compatible tunneling and the local-uniformity of its
reach and height explicit for $(\R^{2}_{\alpha}, \Berez_{\Lambda}^{\R^{2}})$
rather than cited --- is the residual, exactly as the compact-carrier
papers~\cite{paper38, paper40} carried a named bookkeeping residual on
Latr\'emoli\`ere's compact assembly.

\paragraph{Q2 (sharp plane rate).} The converging carrier is the plane
(Theorem~\ref{thm:plane}), whose Bochner--Riesz reconstruction has a
numerically measured, test-function-dependent algebraic rate
$\Lambda^{-0.6}$ to $\Lambda^{-0.9}$. A sharp closed-form rate (and its
dependence on the Bochner--Riesz order $s$ and on the apex exponent
$\alpha$) would parallel the $O(\log n/n)$ rate of the group
case~\cite{paper38,paper40} and locate the plane cone in the same rate
hierarchy. (The finite-disk interior rate is \emph{not} an open
quantitative question but a closed negative one:\ it does not converge,
Remark~\ref{rem:interior_correction}.)

\paragraph{Q3 (boundary-adapted operator system).} An alternative to
de-compactification is a boundary-adapted operator system --- mixed
boundary conditions, or augmentation by boundary modes --- that
reconstructs boundary-supported observables at finite $R$. Whether such
a construction exists with the four reconstruction properties intact is
open.

\paragraph{Q4 (higher-dimensional and warped carriers).} The disk is the
$2$-dimensional flat case. The same questions for the warped cigar
$\cone\times S^{2}$ as a single carrier (rather than the
constant-warp tensor product used for the entropy), and for
higher-dimensional balls, would extend the manifold-with-boundary
propinquity beyond two dimensions.

% =====================================================================
\section*{Acknowledgments}
% =====================================================================
This paper is the operator-algebra companion to the gravity arc of
Paper~51; it supplies the propinquity backbone that Paper~51's
cigar-tip entropy theorem cited. The disk-with-cone reconstruction was
developed and verified numerically in the GeoVac repository
(\texttt{debug/b3\_disk\_backbone\_memo.md} and the drivers cited
therein) during the L6 bookkeeping sprint of 2026-05-29.

% =====================================================================
\begin{thebibliography}{99}
% =====================================================================

\bibitem{latremoliere2015}
F.~Latr\'emoli\`ere, ``The dual Gromov--Hausdorff propinquity,''
\textit{J.~Math.~Pures Appl.}\ \textbf{103} (2015), 303--351.

\bibitem{latremoliere2016}
F.~Latr\'emoli\`ere, ``Quantum metric spaces and the Gromov--Hausdorff
propinquity,'' \textit{Contemp.~Math.}\ \textbf{676} (2016), 47--133.

\bibitem{latremoliere2025}
F.~Latr\'emoli\`ere, ``The quantum Gromov--Hausdorff hypertopology on
the class of pointed proper quantum metric spaces,'' arXiv:2512.03573
(2025); the pointed/proper (locally compact) propinquity machinery
transported here to the boundaryless plane.

\bibitem{connes_vs2021}
A.~Connes and W.~D.~van~Suijlekom, ``Spectral truncations in
noncommutative geometry and operator systems,''
\textit{Comm.~Math.~Phys.}\ \textbf{383} (2021), 2021--2067.

\bibitem{cheeger1983}
J.~Cheeger, ``Spectral geometry of singular Riemannian spaces,''
\textit{J.~Differential Geom.}\ \textbf{18} (1983), 575--657.

\bibitem{stein_weiss}
E.~M.~Stein and G.~Weiss, \textit{Introduction to Fourier Analysis on
Euclidean Spaces}, Princeton Univ.\ Press, 1971 (Bochner--Riesz means
and their positivity above the critical index); see also
C.~D.~Sogge, \textit{Fourier Integrals in Classical Analysis},
Cambridge Univ.\ Press, 1993.

\bibitem{stempak1989}
K.~Stempak, ``On convergence and divergence of Fourier--Bessel series,''
\textit{Electron.~Trans.~Numer.~Anal.}\ \textbf{14} (2002), 223--235;
and related works on Ces\`aro and
Riesz means of Fourier--Bessel / Hankel expansions; see also
B.~Muckenhoupt and E.~M.~Stein, ``Classical expansions and their
relation to conjugate harmonic functions,''
\textit{Trans.~Amer.~Math.~Soc.}\ \textbf{118} (1965), 17--92.

\bibitem{colzani1993}
L.~Colzani, A.~Crespi, G.~Travaglini, and M.~Vignati, ``Equiconvergence
theorems for Fourier--Bessel expansions with applications to the
harmonic analysis of radial functions,''
\textit{Trans.~Amer.~Math.~Soc.}\ \textbf{338} (1993), 43--55.

\bibitem{paper38}
GeoVac Project. Paper~38 --- State-space Gromov--Hausdorff convergence
of truncated Camporesi--Higuchi spectral triples on $S^3$.
\texttt{papers/group1\_operator\_algebras/paper\_38\_su2\_propinquity\_convergence.tex}.

\bibitem{paper39}
GeoVac Project. Paper~39 --- Tensor-product propinquity convergence.
\texttt{papers/group1\_operator\_algebras/paper\_39\_tensor\_propinquity\_convergence.tex}.

\bibitem{paper40}
GeoVac Project. Paper~40 --- State-space Gromov--Hausdorff convergence of
spectral truncations of compact Lie groups with bi-invariant metric.
\texttt{papers/group1\_operator\_algebras/paper\_40\_unified\_propinquity\_convergence.tex}.

\bibitem{paper44}
GeoVac Project. Paper~44 --- Operator-system extension of the BBB Krein
spectral triple at finite cutoff: propagation number and envelope
dependence on the Camporesi--Higuchi spinor bundle.
\texttt{papers/group1\_operator\_algebras/paper\_44\_lorentzian\_operator\_system.tex}.

\bibitem{paper45}
GeoVac Project. Paper~45 --- $K^{+}$-restricted weak-form Lorentzian
propinquity convergence.
\texttt{papers/group1\_operator\_algebras/paper\_45\_lorentzian\_propinquity.tex}.

\bibitem{paper46}
GeoVac Project. Paper~46 --- Strong-form Lorentzian propinquity
convergence.
\texttt{papers/group1\_operator\_algebras/paper\_46\_strong\_form\_lorentzian\_propinquity.tex}.

\bibitem{paper47}
GeoVac Project. Paper~47 --- Norm-resolvent convergence to the
non-compact Lorentzian Krein spectral triple and the two-rate hybrid
limit.
\texttt{papers/group1\_operator\_algebras/paper\_47\_two\_rate\_hybrid\_convergence.tex}.

\bibitem{paper51}
GeoVac Project. Paper~51 --- Gravity from the GeoVac spectral action:
continuum results and the discrete-substrate program (the cigar-tip
entropy and the replica-weight-harmless theorem, \S L6).
\texttt{papers/group5\_qed\_gauge/paper\_51\_gravity\_arc.tex}.

\end{thebibliography}

\end{document}
