% =====================================================================
% Paper 39 (standalone): Latremoliere propinquity convergence on the
% tensor product of two truncated Camporesi-Higuchi spectral triples
% on S^3 at distinct focal lengths.
%
% Math.OA-style companion to Paper 38 (single-factor S^3 = SU(2)).
% Closes the W2b-easy keystone of the GeoVac multi-focal-composition
% program: tensor product of two infinite non-abelian metric spectral
% triples on the same Riemannian manifold.
%
% Status: first draft, May 2026, post-W2b-easy-tighten closure
% (2026-05-07). Built from internal proof memos:
% multifocal_phase_c_w2b_easy_memo.md,
% multifocal_phase_c_w2b_easy_tighten_memo.md,
% multifocal_b_w2b_diag_memo.md.
% =====================================================================
\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm, mathrsfs, mathtools}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue!50!black, citecolor=blue!50!black, urlcolor=blue!50!black}
% \usepackage{microtype}  % disabled: MiKTeX font-expansion environmental issue (same fix as Papers 38/40/42/45/46/47)
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

\newcommand{\nmax}{n_{\max}}
\newcommand{\nmaxa}{n_{\max,a}}
\newcommand{\nmaxb}{n_{\max,b}}
\newcommand{\sthree}{S^{3}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\Op}{\mathcal{O}}
\newcommand{\Tcal}{\mathcal{T}}
\newcommand{\Acal}{\mathcal{A}}
\newcommand{\opnorm}[1]{\lVert #1 \rVert_{\mathrm{op}}}
\newcommand{\cbnorm}[1]{\lVert #1 \rVert_{\mathrm{cb}}}
\newcommand{\Lipnorm}[1]{\lVert #1 \rVert_{\mathrm{Lip}}}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\SU}{\mathrm{SU}}
\newcommand{\SO}{\mathrm{SO}}
\newcommand{\Vol}{\mathrm{Vol}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\Mat}{M}
\newcommand{\DCH}{D_{\mathrm{CH}}}
\newcommand{\KS}{K}
\newcommand{\Khat}{\widehat{K}}

\title{State-space Gromov--Hausdorff convergence of \\
truncated tensor-product Camporesi--Higuchi \\
spectral triples on $\sthree \times \sthree$}
\author{J.~Loutey\thanks{Independent researcher. \texttt{jloutey@gmail.com}.
This work was developed in an AI-augmented agentic workflow with
Anthropic's Claude. Implementation, internal memos, and bibliographic
collation were performed collaboratively; all theorems, design choices,
and editorial decisions are the author's responsibility.}}
\date{May 2026 (preprint)}

\begin{document}
\maketitle

\begin{abstract}
We prove that the Connes--van~Suijlekom truncations of the
tensor-product Camporesi--Higuchi spectral triple
$\Tcal_{\sthree}^{\lambda_a} \otimes \Tcal_{\sthree}^{\lambda_b}$ on
$\sthree \times \sthree$ at two (possibly distinct) focal lengths
$\lambda_a, \lambda_b > 0$ converge to the continuum tensor-product
triple in van~Suijlekom's state-space Gromov--Hausdorff distance,
with explicit qualitative-rate bound
\(
   \Lambda(\Tcal_{\nmaxa} \otimes \Tcal_{\nmaxb},
            \Tcal_{\sthree}^{\lambda_a} \otimes \Tcal_{\sthree}^{\lambda_b})
   \le C_3^{(2)} \cdot (1 + 2\sqrt{2}) \cdot
        \max(\gamma_{\nmaxa}/\lambda_a,\, \gamma_{\nmaxb}/\lambda_b),
\)
where $C_3^{(2)} \le \sqrt{2}$ is a closed-form Lipschitz comparison
constant from the (tight) triangle bound on the Connes--Marcolli joint
Leibniz rule, and $\gamma_n = (4/\pi)\log n / n + O(1/n)$ inherits
from the single-factor result of~\cite{loutey_paper38}. The proof
proceeds factor-by-factor through tensor extensions of the five
single-factor lemmas (operator system, central spectral Fej\'er kernel,
Lipschitz comparison, Berezin reconstruction, propinquity assembly).
The two technical risks specific to the tensor product --- a
closed-form Lipschitz comparison constant on the full operator system,
and a rigorous bound on the cross-Stein--Weiss height term --- both
close via the triangle bound on the joint Leibniz rule. (An earlier
Pythagorean refinement claiming $C_3^{(2)} < 1$ has been
\emph{withdrawn}:\ the graded anticommutation does \emph{not} make the
two Leibniz terms operator-norm orthogonal --- on the actual
Camporesi--Higuchi harmonics they add constructively, so the triangle
bound is tight and $C_3^{(2)} \nearrow \sqrt{2}$, exceeding $1$ for
cutoffs beyond $(3,3)$. The convergence theorem is unaffected, since
$\sqrt{2}$ is a finite constant.) The strictly stronger
Latr\'emoli\`ere propinquity is \emph{not} claimed:\ the dual-reach
($\mathrm{reach}_P$) step of the joint assembly inherits the
single-factor $\mathrm{reach}_P$ named gap of Papers~38/40 (the invalid
cb-norm dual-reach), so the object established is van~Suijlekom
state-space Gromov--Hausdorff convergence. The result extends
\cite{connes_vs2021,leimbach_vs2024,loutey_paper38} to the simplest
non-abelian tensor case, and closes a tensor-product state-space-GH
case that the published literature on
products of metric spectral triples~\cite{latremoliere2026,
farsi_latremoliere2024,farsi_latremoliere2025,aguilar2019} does not
cover; existing tensor-product propinquity results require the second
factor to be finite-dimensional, AF, abelian, or to reduce to a
single-character / Hopf-$S^1$ structure.
\end{abstract}

\bigskip\noindent
\textbf{MSC2020 classifications:}\ 58B34 (noncommutative geometry),
46L87 (noncommutative Riemannian and metric geometry),
46L52 (noncommutative function spaces),
22E45 (representations of compact Lie groups),
46L06 (tensor products of operator systems).

\medskip\noindent
\textbf{Keywords:}\ spectral triple, tensor product, Connes--Marcolli
graded Dirac, quantum Gromov--Hausdorff propinquity, Camporesi--Higuchi
Dirac, operator system, Berezin reconstruction, graded Leibniz
rule, $\SU(2) \times \SU(2)$.

% =====================================================================
\section{Introduction}\label{sec:intro}
% =====================================================================

The Connes--van~Suijlekom~\cite{connes_vs2021} framework of truncated
operator systems and the subsequent propinquity-convergence results of
Hekkelman~\cite{hekkelman2022}, Hekkelman--McDonald~\cite{hekkelman_mcdonald2024b},
Leimbach--van~Suijlekom~\cite{leimbach_vs2024}, and the present
author~\cite{loutey_paper38} establish quantitative
Gromov--Hausdorff convergence for spectral truncations of a
\emph{single} compact Riemannian spectral triple, with the abelian and
$\SU(2)$ cases now closed at qualitative rate. A natural and
operationally important next question is whether the convergence
behaviour transfers to \emph{tensor products} of two such truncated
triples.

The published propinquity tensor-product literature does not cover
this case in its central form. Latr\'emoli\`ere~\cite{latremoliere2026}
closes the \emph{almost-commutative} case in which one factor is an
infinite-dimensional Riemannian spectral triple and the other is
finite-dimensional. Farsi--Latr\'emoli\`ere~\cite{farsi_latremoliere2024}
prove spectral continuity for collapse of products of spectral triples
in which at least one factor is abelian.
Farsi--Latr\'emoli\`ere~\cite{farsi_latremoliere2025} treat
continuity of a \emph{single} metric spectral triple along an analytic
path of Riemannian metrics --- a setting distinct from the
discrete-truncation product considered here.
Aguilar~\cite{aguilar2019} addresses tensor products $C(X) \otimes A$
where one factor is commutative and the other AF.
Hekkelman--McDonald~\cite{hekkelman_mcdonald2024b} treats a
noncommutative integral on a single spectrally truncated triple, not a
product. The published thread covers Riemannian-by-finite,
Riemannian-by-AF, Riemannian-by-abelian, $C(X)$-by-AF,
single-triple-along-paths, and single-truncation. None of these covers
two infinite non-abelian Riemannian metric spectral triples.

The present paper closes that gap in the simplest physically natural
non-K\"ahler case: two copies of the round $\sthree = \SU(2)$
Camporesi--Higuchi triple~\cite{camporesi_higuchi1996}, each in its own
focal-length scaling, tensored together via the Connes--Marcolli
graded convention.

Let $\Tcal_{\sthree}^{\lambda} = (C^\infty(\sthree),
L^2(\sthree, \Sigma), \lambda^{-1} \DCH)$ denote the round
Camporesi--Higuchi spectral triple at \emph{focal length} $\lambda > 0$,
i.e.\ the unit-round triple with the Dirac operator rescaled so that
the spectral gap is $\lambda^{-1}$ rather than $1$. (In the GeoVac
hydrogenic context this corresponds to placing two electrons in
distinct hydrogenic shells with focal lengths $\lambda_a = n_a / Z$ and
$\lambda_b = n_b / Z$.) Form the tensor product
\begin{equation}\label{eq:tensor_triple}
   \Tcal_{\sthree}^{\lambda_a} \otimes \Tcal_{\sthree}^{\lambda_b}
   \;:=\; \bigl(C^\infty(\sthree) \otimes C^\infty(\sthree),\;
          L^2(\sthree, \Sigma) \otimes L^2(\sthree, \Sigma),\;
          D_{a,b} \bigr),
\end{equation}
with Connes--Marcolli graded composed Dirac
\begin{equation}\label{eq:CM_dirac}
   D_{a,b} \;=\; \lambda_a^{-1} \DCH^{(a)} \otimes I_b
                \;+\; \gamma_a \otimes \lambda_b^{-1} \DCH^{(b)},
\end{equation}
where $\gamma_a$ is the chirality grading on $L^2(\sthree, \Sigma)$.
The combined object has KO-dimension $3 + 3 = 6 \pmod 8$. Truncate
each factor independently at cutoffs $\nmaxa, \nmaxb$ and form the
tensor-product truncated triple $\Tcal_{\nmaxa} \otimes \Tcal_{\nmaxb}$.

\begin{theorem}[Main theorem; cf.~\S\ref{sec:main_theorem}]
\label{thm:main_intro}
The truncated tensor-product triples $\Tcal_{\nmaxa} \otimes
\Tcal_{\nmaxb}$ converge to $\Tcal_{\sthree}^{\lambda_a} \otimes
\Tcal_{\sthree}^{\lambda_b}$ in van~Suijlekom's state-space
Gromov--Hausdorff distance, with bound
\begin{equation}\label{eq:main_rate_intro}
   \Lambda\bigl(\Tcal_{\nmaxa} \otimes \Tcal_{\nmaxb},
                \Tcal_{\sthree}^{\lambda_a} \otimes
                \Tcal_{\sthree}^{\lambda_b}\bigr)
   \;\le\; C_3^{(2)}(\nmaxa, \nmaxb) \cdot (1 + 2\sqrt{2}) \cdot
   \max\!\Bigl(\frac{\gamma_{\nmaxa}}{\lambda_a},\,
                \frac{\gamma_{\nmaxb}}{\lambda_b}\Bigr),
\end{equation}
where $\gamma_n$ is the central spectral Fej\'er moment of
\cite{loutey_paper38} satisfying $\gamma_n = (4/\pi) \log n / n +
O(1/n)$, and the joint Lipschitz comparison constant is
\begin{equation}\label{eq:C3_2_intro}
   C_3^{(2)}(\nmaxa, \nmaxb)
   \;\le\; \sup_{\substack{2 \le N_a \le \nmaxa+1 \\ 2 \le N_b \le \nmaxb+1}}
            \sqrt{\frac{\bigl((N_a - 1) + (N_b - 1)\bigr)^2}
                       {N_a^2 + N_b^2 - 2}},
\end{equation}
bounded by $\sqrt 2$ at every finite $(\nmaxa, \nmaxb)$ and approaching
$\sqrt 2$ from below as both cutoffs grow (this is the \emph{tight}
triangle bound; the convergence is driven by $\gamma_n \to 0$, not by
the constant).
\end{theorem}

The proof is a factor-by-factor lift of the five single-factor lemmas
of~\cite{loutey_paper38} to the tensor product, supplemented by two
new ingredients specific to the product:
\begin{itemize}\setlength{\itemsep}{2pt}
\item a closed-form Lipschitz comparison estimate from the (tight)
operator-norm triangle bound $\norm{A + B}_{\mathrm{op}} \le \norm{A}
+ \norm{B}$ on the two Connes--Marcolli Leibniz terms
(Lemma~\ref{lem:L3-T}); and
\item an explicit Stein--Weiss-type bound on the joint
Lipschitz-distortion height of the tunnel map, again via the triangle
bound applied to the joint commutator (Lemma~\ref{lem:L5-T}).
\end{itemize}
(An earlier draft used a \emph{Pythagorean} refinement of these two
bounds, claiming $C_3^{(2)} < 1$; that refinement is withdrawn --- the
graded anticommutation does not produce operator-norm orthogonality
--- and replaced throughout by the rigorous triangle bound, giving
$C_3^{(2)} \le \sqrt 2$; see Remark~\ref{rem:no_pythagorean}.)

The mechanism is unified: the same KO-dim-6 graded structure
that defines the Connes--Marcolli composed Dirac splits both
the joint Lipschitz constant (R1) and the joint height-distortion
bound (R2) into Leibniz terms controlled by the triangle bound. Each
of the five single-factor lemmas of \cite{loutey_paper38} extends
factor-by-factor with no novel analytical machinery.

\paragraph{Why this is the \emph{easy} case.}
The same-manifold tensor product treated here is the most accessible
of three plausible tensor-product extensions of~\cite{loutey_paper38}.
The cross-manifold case
$\Tcal_{\sthree} \otimes \Tcal_{S^5}^{\mathrm{Bargmann}}$, in which the
second factor is a holomorphic Hardy-sector spectral triple of the
type used in the Bargmann--Segal lattice
construction~\cite{paper24}, is structurally obstructed at the
framework level: the $\sthree$ factor is a second-order Riemannian
spinor Dirac, while the $S^5$ Bargmann factor is a first-order
complex-analytic Euler operator on a Hardy sector and does not fit
standard NCG Dirac axioms. There is no published prescription for
tensoring a Riemannian spinor Dirac with a Hardy-sector first-order
complex operator in the propinquity framework, and the obstruction is
the four-layer Coulomb/HO asymmetry of~\cite{paper24}~\S V resurfacing
at the spectral-triple level. A separate variant ---
$\Tcal_{\sthree} \otimes \Tcal_{S^5}^{\mathrm{Riem}}$ with both factors
Riemannian --- is mathematically clean (KO-arithmetic $3+5=8\equiv
0\pmod 8$) but requires propinquity convergence for the rank-2
$\Tcal_{S^5}^{\mathrm{Riem}}$ as a separate prerequisite, which is not
available in the literature. We address only the same-manifold case in
the present paper, and discuss the obstructions to the cross-manifold
extensions in \S\ref{sec:related_work}.

\paragraph{Outline.}
Section~\ref{sec:setup} sets up the rescaled Camporesi--Higuchi
spectral triple at focal length $\lambda$, the truncations, and the
tensor-product Connes--Marcolli graded structure.
Section~\ref{sec:main_theorem} states the main theorem.
Section~\ref{sec:lemmas} proves the five tensor lemmas.
Section~\ref{sec:numerical} reports the numerical verification panel.
Section~\ref{sec:related_work} places the result in the
Connes--van~Suijlekom / Latr\'emoli\`ere / Farsi--Latr\'emoli\`ere /
Hekkelman--McDonald lineage and discusses obstructions to the
cross-manifold extensions.
Section~\ref{sec:open} lists open questions.
Section~\ref{sec:conclusion} concludes.

% =====================================================================
\section{The setting}\label{sec:setup}
% =====================================================================

\paragraph{Convergence convention and descope note.}
The object established here is van~Suijlekom's \emph{state-space
Gromov--Hausdorff distance} (the convention of Paper~38
\cite{loutey_paper38}), \emph{not} the strictly stronger
Latr\'emoli\`ere propinquity \cite{latremoliere_metric_st_2017}
(Adv.~Math.\ \textbf{404} (2022), Paper No.~108393, preprint
\texttt{arXiv:1811.10843}). The bound symbol $\Lambda(\cdot, \cdot)$
below denotes the state-space GH distance. The joint assembly
(Lemma~\ref{lem:L5-T}) bounds the dual reach
$\mathrm{reach}_{P_{\nmaxa} \otimes P_{\nmaxb}}$ by inheriting the
single-factor $\mathrm{reach}_P$ estimate;\ that single-factor step is
the invalid cb-norm dual-reach that descoped Papers~38/40 from
Latr\'emoli\`ere propinquity to state-space GH, so the joint result
inherits the same named gap and is stated at the state-space-GH level.
The rate and the joint Lipschitz constant $C_3^{(2)} \le \sqrt 2$
(Lemma~\ref{lem:L3-T}, triangle bound) are unaffected by this
distinction.

\subsection{Single-factor recall: the rescaled $\sthree$ Camporesi--Higuchi triple}
\label{sec:single_factor_recall}

For $\lambda > 0$, the \emph{$\lambda$-scaled Camporesi--Higuchi
spectral triple} on the unit-round $\sthree = \SU(2)$ is
\begin{equation}\label{eq:single_factor_triple}
   \Tcal_{\sthree}^{\lambda}
   \;=\; \bigl(\, C^\infty(\sthree),\; L^2(\sthree, \Sigma),\;
   \lambda^{-1}\DCH \,\bigr),
\end{equation}
with $\DCH$ as in~\cite{loutey_paper38}~\S 2.1, eigenvalues
$\sigma(\lambda^{-1}\DCH) = \{\pm \lambda^{-1}(n + 1/2) : n \in \N\}$ on
each chirality sector. The truncated triple at cutoff $\nmax$ is
$\Tcal_{\nmax}^{\lambda} = (\Op_{\nmax}, \Hilb_{\nmax},
\lambda^{-1} D_{\nmax})$, with the truncated operator system
$\Op_{\nmax} = P_{\nmax} C^\infty(\sthree) P_{\nmax}$ and the truncated
Dirac $D_{\nmax} = P_{\nmax} \DCH P_{\nmax}$. We will write
$\Tcal^\lambda$ when the dependence on $\lambda$ matters; the rescaling
multiplies single-factor Connes distances and propinquity bounds by
$\lambda$, but is otherwise transparent for our purposes.

\subsection{The tensor-product spectral triple}
\label{sec:tensor_triple}

Let $\lambda_a, \lambda_b > 0$. Define
\begin{equation}\label{eq:tensor_triple_def}
\Tcal_{\sthree}^{\lambda_a} \otimes \Tcal_{\sthree}^{\lambda_b}
\;:=\; \bigl(\Acal_{a,b},\; \Hilb_{a,b},\; D_{a,b},\; \gamma_{a,b},\;
J_{a,b}\bigr),
\end{equation}
with
\begin{align}
\Acal_{a,b} &= C^\infty(\sthree) \otimes C^\infty(\sthree) =
C^\infty(\sthree \times \sthree), \\
\Hilb_{a,b} &= L^2(\sthree, \Sigma) \otimes L^2(\sthree, \Sigma), \\
D_{a,b} &= \lambda_a^{-1} \DCH^{(a)} \otimes I_b
        + \gamma_a \otimes \lambda_b^{-1} \DCH^{(b)}, \label{eq:CM_dirac_recall} \\
\gamma_{a,b} &= \gamma_a \otimes \gamma_b, \\
J_{a,b} &= J_a \otimes J_b
\end{align}
in the standard Connes--Marcolli graded tensor product convention
\cite{connes1995, marcolli_vs2014}. The crucial structural identity is
\begin{equation}\label{eq:anticomm}
   \bigl\{ \DCH^{(a)} \otimes I_b,\; \gamma_a \otimes \DCH^{(b)} \bigr\}
   \;=\; \bigl(\DCH^{(a)} \gamma_a + \gamma_a \DCH^{(a)}\bigr) \otimes
         \DCH^{(b)} \;=\; 0,
\end{equation}
since $\{\DCH^{(a)}, \gamma_a\} = 0$ on the unit-round $\sthree$ Dirac.
This anticommutation of the two \emph{Dirac} summands is what gives the
clean two-term graded Leibniz rule \eqref{eq:joint_leibniz} (it does
\emph{not}, however, make the two resulting \emph{commutator} terms
operator-norm orthogonal --- see Remark~\ref{rem:no_pythagorean}); the
joint commutator is then controlled by the triangle bound, which
suffices to make the tensor-product propinquity convergent.

The truncated tensor-product triple at cutoffs $(\nmaxa, \nmaxb)$ is
\begin{equation}\label{eq:tensor_truncated}
\Tcal_{\nmaxa}^{\lambda_a} \otimes \Tcal_{\nmaxb}^{\lambda_b}
\;:=\; \bigl(\Op_{\nmaxa} \otimes \Op_{\nmaxb},\;
\Hilb_{\nmaxa} \otimes \Hilb_{\nmaxb},\;
P_{\nmaxa} \otimes P_{\nmaxb} \cdot D_{a,b} \cdot P_{\nmaxa} \otimes
P_{\nmaxb}\bigr),
\end{equation}
with the algebraic tensor-product operator system $\Op_{\nmaxa} \otimes
\Op_{\nmaxb} \subset M_{\dim \Hilb_{\nmaxa}} (\C) \otimes
M_{\dim \Hilb_{\nmaxb}}(\C)$ defined as the linear span of Kronecker
products $\Mat_a \otimes \Mat_b$ with $\Mat_\bullet \in \Op_{\nmax,
\bullet}$.

% =====================================================================
\section{Main theorem}\label{sec:main_theorem}
% =====================================================================

\begin{theorem}[Main theorem]\label{thm:main}
The truncated tensor-product Camporesi--Higuchi spectral triples
converge to their continuum tensor-product limit in van~Suijlekom's
state-space Gromov--Hausdorff distance (the strictly stronger
Latr\'emoli\`ere propinquity is not claimed; see the convergence
convention below):
\begin{equation}\label{eq:main_thm}
   \Lambda\bigl(\Tcal_{\nmaxa}^{\lambda_a} \otimes
                \Tcal_{\nmaxb}^{\lambda_b},\;
                \Tcal_{\sthree}^{\lambda_a} \otimes
                \Tcal_{\sthree}^{\lambda_b}\bigr)
   \;\le\; C_3^{(2)}(\nmaxa, \nmaxb) \cdot (1 + 2\sqrt{2}) \cdot
            \max\!\Bigl(\frac{\gamma_{\nmaxa}}{\lambda_a},\,
                        \frac{\gamma_{\nmaxb}}{\lambda_b}\Bigr),
\end{equation}
with
\begin{equation}\label{eq:C3_2_full}
   C_3^{(2)}(\nmaxa, \nmaxb)
   \;:=\; \sup_{\substack{2 \le N_a \le \nmaxa+1 \\ 2 \le N_b \le \nmaxb+1}}
            \sqrt{\frac{\bigl((N_a - 1) + (N_b - 1)\bigr)^2}
                       {N_a^2 + N_b^2 - 2}}
   \;\le\; \sqrt{2}
\end{equation}
at every finite $(\nmaxa, \nmaxb)$, and $C_3^{(2)} \nearrow \sqrt{2}$
as both cutoffs grow. (This is the \emph{tight} triangle bound on the
joint Leibniz rule; it is achieved with equality on a pair of
top-shell raising harmonics, where the two Leibniz terms add
constructively. The earlier closed form
$\sqrt{((N_a-1)^2+(N_b-1)^2)/(N_a^2+N_b^2-2)}<1$ rested on a Pythagorean
operator-norm identity that does \emph{not} hold for these operators;
see Lemma~\ref{lem:L3-T}.) The right-hand side of \eqref{eq:main_thm} tends to
zero as $\nmaxa, \nmaxb \to \infty$, with rate
$\max(\gamma_{\nmaxa}, \gamma_{\nmaxb}) = O(\log \nmax / \nmax)$
inherited from the single-factor central Fej\'er moment
\cite{loutey_paper38}. The asymptotic constant $4/\pi$ on each factor
is preserved in the joint rate.
\end{theorem}

\begin{proof}
The proof assembles five tensor lemmas L1$'$-T through L5-T proved in
\S\ref{sec:lemmas}, each of which lifts the corresponding single-factor
lemma of~\cite{loutey_paper38}~\S 3. Lemma~\ref{lem:L1prime-T} provides
the operator-system substrate; Lemma~\ref{lem:L2-T} the joint central
spectral Fej\'er kernel with closed-form Plancherel symbol; Lemma
\ref{lem:L3-T} the joint Lipschitz comparison constant via the
(tight) triangle bound on the Connes--Marcolli graded Leibniz rule;
Lemma~\ref{lem:L4-T} the
joint Berezin reconstruction with the four properties needed for a
Latr\'emoli\`ere tunneling pair; and Lemma~\ref{lem:L5-T} the
state-space-GH assembly with explicit cross-Stein--Weiss height bound
(modulo the inherited $\mathrm{reach}_P$ named gap; see the convergence
convention).
The factor $1 + 2\sqrt{2}$ in \eqref{eq:main_thm} is the sum of the
joint reach contribution (bounded by $\max(\gamma)$, contributing $1$)
and the joint height contribution (bounded by $2\sqrt{2}\max(\gamma)$
on the unit-norm panel, contributing $2\sqrt{2}$). The
$\lambda^{-1}$-rescalings of the single-factor Diracs propagate
linearly through the bound and produce the
$\max(\gamma/\lambda)$-form of \eqref{eq:main_thm}.
\end{proof}

% =====================================================================
\section{The five tensor lemmas}\label{sec:lemmas}
% =====================================================================

We work at unit focal length $\lambda_a = \lambda_b = 1$ throughout
this section; the $\lambda$-rescaling is reinstated at the end of
\S\ref{sec:L5-T}.

% ---------------------------------------------------------------------
\subsection{Lemma L1$'$-T: tensor-product operator system}
\label{sec:L1prime-T}
% ---------------------------------------------------------------------

\begin{lemma}[L1$'$-T:\ tensor-product operator system substrate]
\label{lem:L1prime-T}
Let $\Op_{\nmaxa}$ and $\Op_{\nmaxb}$ be the truncated operator systems
of \cite[\S 3.1]{loutey_paper38}~\&~\cite[Lemma~3.1]{loutey_paper38}.
The algebraic tensor product
\begin{equation*}
  \Op_{\nmaxa} \otimes \Op_{\nmaxb}
  \;\subset\; M_{\dim \Hilb_{\nmaxa}}(\C) \otimes M_{\dim \Hilb_{\nmaxb}}(\C),
\end{equation*}
defined as the linear span of Kronecker products $\Mat_a \otimes \Mat_b$
with $\Mat_a \in \Op_{\nmaxa}$, $\Mat_b \in \Op_{\nmaxb}$, satisfies:
\begin{enumerate}\setlength{\itemsep}{2pt}
\item[(a)] (Dimension factorization.)
$\dim(\Op_{\nmaxa} \otimes \Op_{\nmaxb})
= \dim(\Op_{\nmaxa}) \cdot \dim(\Op_{\nmaxb})$.
\item[(b)] (Propagation bound.) $\mathrm{prop}(\Op_{\nmaxa} \otimes
\Op_{\nmaxb}) \le 2$, matching the single-factor Connes--van~Suijlekom
$\mathrm{prop} = 2$ value~\cite[\S 4.2]{connes_vs2021}.
\item[(c)] (Cross-shell finite Connes distance.) Under the
chirality-mixing offdiagonal extension $D_{a,b}^{\mathrm{offdiag}}$
defined factor-by-factor in the sense
of~\cite[Lemma~3.1]{loutey_paper38}, every cross-shell pair of pure
node-evaluation states has finite truncated joint Connes distance.
\end{enumerate}
\end{lemma}

\begin{proof}
\textbf{(a)} The single-factor multiplier matrices $\{\Mat_{NLM}\}$
are linearly independent in $M_{\dim \Hilb_{\nmax,\bullet}}(\C)$ by
construction (\cite[\S 3.1]{loutey_paper38}). The Kronecker product
preserves linear independence: $\mathrm{vec}(\Mat_a \otimes \Mat_b)
= \mathrm{vec}(\Mat_a) \otimes \mathrm{vec}(\Mat_b)$, and tensors of
linearly independent vectors are linearly independent. Hence
$\dim(\Op_{\nmaxa} \otimes \Op_{\nmaxb}) = \dim(\Op_{\nmaxa}) \cdot
\dim(\Op_{\nmaxb})$.

\textbf{(b)} For any operator system $\Op$ with $\mathrm{prop}(\Op) =
p$, $\Op^p = M_{\dim \Hilb}(\C)$. For $p_a = p_b = 2$, we have
$(\Op_{\nmaxa} \otimes \Op_{\nmaxb})^2 \supset \Op_{\nmaxa}^2 \otimes
\Op_{\nmaxb}^2 = M_{\dim \Hilb_{\nmaxa}}(\C) \otimes M_{\dim
\Hilb_{\nmaxb}}(\C) = M_{\dim \Hilb_{a,b}}(\C)$, so
$\mathrm{prop}(\Op_{\nmaxa} \otimes \Op_{\nmaxb}) \le 2$.

\textbf{(c)} The chirality-mixing offdiagonal extension
$D_{a,b}^{\mathrm{offdiag}}$ inherits the cross-shell-finite property
factor-by-factor from \cite[Lemma~3.1]{loutey_paper38}. For a state
pair $(\varphi_a \otimes \varphi_b, \psi_a \otimes \psi_b)$ in
distinct shells, at least one factor differs in shell, and the
single-factor finite-distance property on that factor produces a
non-trivial structural multiplier bounding the supremum
in the SDP definition of the joint truncated Connes distance.
\end{proof}

\begin{remark}\label{rem:offdiag-T}
As in~\cite[Remark~3.2]{loutey_paper38}, the offdiagonal extension is a
metric-only device for finite-distance verification; the truthful
$D_{a,b} = \DCH^{(a)} \otimes I + \gamma_a \otimes \DCH^{(b)}$ is what
satisfies the KO-dim-6 chirality and real-structure axioms and is what
underlies Lemmas~\ref{lem:L3-T}--\ref{lem:L4-T}.
\end{remark}

% ---------------------------------------------------------------------
\subsection{Lemma L2-T: joint central spectral Fej\'er kernel}
\label{sec:L2-T}
% ---------------------------------------------------------------------

Let $\KS^{(a)}_{\nmaxa}$ and $\KS^{(b)}_{\nmaxb}$ denote the
single-factor central spectral Fej\'er kernels on $\SU(2)$ defined in
\cite[Definition~3.3]{loutey_paper38}. Define the joint product kernel
\begin{equation}\label{eq:joint_kernel}
   \KS^{(a,b)}_{\nmaxa, \nmaxb}(g_1, g_2)
   \;:=\; \KS^{(a)}_{\nmaxa}(g_1)\, \KS^{(b)}_{\nmaxb}(g_2)
   \qquad\text{on}\quad \SU(2) \times \SU(2).
\end{equation}

\begin{lemma}[L2-T: joint kernel construction and rate]\label{lem:L2-T}
The joint central kernel $\KS^{(a,b)}$ has the following properties:
\begin{enumerate}\setlength{\itemsep}{2pt}
\item[(a)] (Positivity and unit mass.)
$\KS^{(a,b)}(g_1, g_2) \ge 0$ on $\SU(2) \times \SU(2)$, and
$\int (\KS^{(a,b)})\,dg_1\,dg_2 = 1$ in the product Haar measure.
\item[(b)] (Plancherel factorization.) The joint Plancherel symbol
factorizes:
$\widehat{\KS}^{(a,b)}(j_1, j_2) = \widehat{\KS}^{(a)}(j_1) \cdot
\widehat{\KS}^{(b)}(j_2)$, with each factor the closed-form
$\widehat{\KS}^{(\bullet)}(j) = (2j+1)/Z_{\nmax,\bullet}$ for
$j \le j_{\max,\bullet}$ and zero otherwise.
\item[(c)] (Cb-norm factorization.)
$\cbnorm{T_{\KS^{(a,b)}}}^{\mathrm{cent}} =
\cbnorm{T_{\KS^{(a)}}}^{\mathrm{cent}} \cdot
\cbnorm{T_{\KS^{(b)}}}^{\mathrm{cent}}
= 4 / [(\nmaxa + 1)(\nmaxb + 1)]$.
\item[(d)] (Subadditive joint mass concentration.) Define
$\gamma^{(a,b)}_{\nmaxa, \nmaxb} := \int \KS^{(a,b)}(g_1, g_2)\,
d_{\sthree \times \sthree}\bigl((e,e), (g_1, g_2)\bigr)\,dg_1\,dg_2$.
Then
\begin{equation}\label{eq:gamma_joint_subadditive}
   \gamma^{(a,b)}_{\nmaxa, \nmaxb}
   \;\le\; \gamma_{\nmaxa} + \gamma_{\nmaxb}
   \;\le\; 2\,\max(\gamma_{\nmaxa}, \gamma_{\nmaxb}).
\end{equation}
\end{enumerate}
\end{lemma}

\begin{proof}
\textbf{(a)} The product of two non-negative unit-mass kernels is a
non-negative unit-mass kernel under the product Haar measure.
\textbf{(b)} The Plancherel decomposition of $L^2(G_1 \times G_2)$ is
the product of the two single-factor Plancherel decompositions, and
convolution by a central function on a product of compact groups acts
diagonally on each isotypic component as the product of single-factor
Fourier coefficients.
\textbf{(c)} The Bo{\.z}ejko--Fendler equality
$\cbnorm{T_K} = \norm{\widehat{K}}_{\ell^\infty}$ for
central convolutions on amenable compact groups
\cite{bozejko_fendler1991, pisier2003} extends to product kernels via
the standard tensor-product cb-norm identity
$\cbnorm{A \otimes B} = \cbnorm{A}
\cbnorm{B}$ on the minimal tensor product
\cite[Ch.~8]{pisier2003}. Substituting the single-factor result
\cite[Lemma~3.4(c)]{loutey_paper38} gives the displayed value.
\textbf{(d)} The product Riemannian metric on $\sthree \times \sthree$
satisfies the triangle inequality $d_{\sthree \times \sthree}((e,e),
(g_1, g_2)) \le d_{\sthree}(e, g_1) + d_{\sthree}(e, g_2)$ at every
point. Integrating against $\KS^{(a,b)}(g_1, g_2) \,dg_1 \,dg_2$ and
applying Fubini gives \eqref{eq:gamma_joint_subadditive}.
\end{proof}

\begin{remark}\label{rem:cb_norm_rate}
Property (c) shows that the joint cb-norm is one order faster than the
single-factor rate: $\cbnorm{T_{\KS^{(a,b)}}} =
O(1/(\nmaxa \nmaxb))$ vs.\ single-factor $O(1/\nmax)$. This is the
structural reason joint convergence is well-behaved.
\end{remark}

% ---------------------------------------------------------------------
\subsection{Lemma L3-T: joint Lipschitz comparison via the triangle
bound on the graded Leibniz rule}\label{sec:L3-T}
% ---------------------------------------------------------------------

This is the central new technical content of the paper. The
Connes--Marcolli graded Dirac \eqref{eq:CM_dirac_recall} on the
KO-dim-6 graded module splits the joint commutator into two Leibniz
terms \eqref{eq:joint_leibniz}; the operator-norm triangle bound on
that sum is what controls the joint Lipschitz comparison constant.

\begin{remark}[Withdrawn Pythagorean refinement]\label{rem:no_pythagorean}
An earlier version of this lemma claimed the \emph{Pythagorean}
identity $\norm{A + B}_{\mathrm{op}}^2 = \norm{A}^2 + \norm{B}^2$ for
the two Leibniz terms (citing the graded anticommutation
$\{A,B\}=0$), which would have given $C_3^{(2)} < 1$. That refinement
is \textbf{false}:\ $\{A,B\}=0$ does \emph{not} imply operator-norm
orthogonality (the elementary counterexample
$A=\mathrm{diag}(1,0)$, $B=\mathrm{diag}(0,1)$ has $\{A,B\}=0$ but
$\norm{A+B}^2 = 1 \ne 2 = \norm{A}^2+\norm{B}^2$), and the
specific factorisation that was invoked is invalid because the two
Leibniz terms carry \emph{different} second tensor factors
($\Mat_g[\DCH^{(b)},\Mat_g]$ vs.\ $[\DCH^{(b)},\Mat_g]\Mat_g$, which do
not commute). A direct numerical test on the actual Camporesi--Higuchi
harmonics (the supporting test below) finds the Pythagorean bound
\emph{maximally violated} ($\norm{A+B}^2 / (\norm{A}^2+\norm{B}^2) = 2$
exactly at a pair of top-shell raising harmonics, where the two terms
add constructively) and the \emph{triangle} bound tight
($\norm{A+B} = \norm{A}+\norm{B}$ there). The constant is therefore
$C_3^{(2)} \nearrow \sqrt 2$, not $<1$. This does not affect
convergence:\ $\sqrt 2$ is a finite constant, so the right-hand side of
\eqref{eq:main_thm} still $\to 0$ as the cutoffs grow.
\end{remark}

\begin{lemma}[L3-T: joint Lipschitz comparison constant]\label{lem:L3-T}
For every simple-tensor multiplier $\Mat_{f \otimes g} = \Mat_f
\otimes \Mat_g$ with $f, g \in C^\infty(\sthree)$, the joint
Connes--Marcolli commutator satisfies the Leibniz identity
\begin{equation}\label{eq:joint_leibniz}
   \bigl[D_{a,b},\, \Mat_f \otimes \Mat_g\bigr]
   \;=\; [\DCH^{(a)}, \Mat_f] \otimes \Mat_g
        + (\gamma_a \Mat_f) \otimes [\DCH^{(b)}, \Mat_g],
\end{equation}
and, by the operator-norm triangle inequality applied to the two
Leibniz terms (which is \emph{tight} --- see
Remark~\ref{rem:no_pythagorean}),
\begin{equation}\label{eq:pythagorean_op_norm}
   \bigl\|[D_{a,b}, \Mat_f \otimes \Mat_g]\bigr\|_{\mathrm{op}}
   \;\le\; \opnorm{[\DCH^{(a)}, \Mat_f]} \cdot \opnorm{\Mat_g}
        \;+\; \opnorm{\Mat_f} \cdot \opnorm{[\DCH^{(b)}, \Mat_g]}.
\end{equation}
Combining \eqref{eq:pythagorean_op_norm} with the single-factor L3
estimate \cite[Lemma~3.5]{loutey_paper38} for each factor at level
$(N_a, N_b)$ in the Avery 3-Y harmonic basis gives the per-irrep ratio
\begin{equation}\label{eq:per_irrep_ratio_T}
   \frac{\opnorm{[D_{a,b},\, \Mat_{N_a L_a M_a} \otimes
                                \Mat_{N_b L_b M_b}]}^2}
        {\norm{Y^{(3)}_{N_a L_a M_a} \otimes Y^{(3)}_{N_b L_b M_b}}_{\mathrm{Lip}}^2}
   \;\le\; \frac{\bigl((N_a - 1) + (N_b - 1)\bigr)^2}{N_a^2 + N_b^2 - 2}.
\end{equation}
Taking square roots and supping over the irrep grid gives the joint
Lipschitz comparison constant $C_3^{(2)}(\nmaxa, \nmaxb)$ of
\eqref{eq:C3_2_full}, which is bounded by $\sqrt 2$ at every finite
$(\nmaxa, \nmaxb)$ and increases to $\sqrt 2$ as the cutoffs grow.
\end{lemma}

\begin{proof}
The Leibniz identity \eqref{eq:joint_leibniz} is a direct computation
on Kronecker products:
\begin{equation*}
[D_{a,b}, \Mat_f \otimes \Mat_g]
= [\DCH^{(a)} \otimes I_b, \Mat_f \otimes \Mat_g]
 + [\gamma_a \otimes \DCH^{(b)}, \Mat_f \otimes \Mat_g],
\end{equation*}
with $[\DCH^{(a)} \otimes I_b, \Mat_f \otimes \Mat_g] = [\DCH^{(a)},
\Mat_f] \otimes \Mat_g$ (since $I_b$ commutes with $\Mat_g$), and
$[\gamma_a \otimes \DCH^{(b)}, \Mat_f \otimes \Mat_g] = \gamma_a
\Mat_f \otimes [\DCH^{(b)}, \Mat_g]$ (since $\gamma_a \Mat_f \ne
\Mat_f \gamma_a$ in general but the chirality grading commutes with
the scalar multiplier as a chirality-blind operator;\ in components,
the chirality flip is absorbed into the $\gamma_a$ factor on the left).

The bound \eqref{eq:pythagorean_op_norm} is the operator-norm triangle
inequality $\norm{A + B}_{\mathrm{op}} \le \norm{A} + \norm{B}$ applied
to the two Leibniz terms $A = [\DCH^{(a)}, \Mat_f] \otimes \Mat_g$ and
$B = (\gamma_a \Mat_f) \otimes [\DCH^{(b)}, \Mat_g]$, together with the
multiplicativity of the operator norm on simple tensors
($\norm{X \otimes Y} = \norm{X}\,\norm{Y}$, and $\norm{\gamma_a \Mat_f}
= \norm{\Mat_f}$ since $\gamma_a$ is unitary). This bound is
\emph{tight}:\ on a pair of top-shell raising harmonics the two terms
align so that $\norm{A + B} = \norm{A} + \norm{B}$ exactly. There
$\norm{A} = \norm{B}$, so $\norm{A+B}^2 = (2\norm{A})^2 = 4\norm{A}^2$
while the Pythagorean value is $\norm{A}^2 + \norm{B}^2 = 2\norm{A}^2$
--- a factor $2$ violation of the would-be identity (see
Remark~\ref{rem:no_pythagorean} for why the
graded anticommutation does \emph{not} give operator-norm
orthogonality). The numerical verification on the actual
Camporesi--Higuchi harmonics --- the joint commutator built from the
real $\DCH$ matrices and the graded multipliers at
$(\nmaxa, \nmaxb) = (2,2), (2,3)$, with the operator norm computed by
singular-value decomposition --- finds, over every harmonic pair, the
triangle ratio $\norm{A+B}/(\norm{A}+\norm{B})$ attaining its maximum
$1$ and the Pythagorean ratio $\norm{A+B}^2/(\norm{A}^2+\norm{B}^2)$
attaining its maximum $2$, confirming both the tightness of
\eqref{eq:pythagorean_op_norm} and the failure of the Pythagorean form
(backing test \texttt{tests/test\_paper39\_triangle\_tight.py}).

For the per-irrep ratio \eqref{eq:per_irrep_ratio_T}, the
single-factor L3 estimate \cite[Eq.~(3.18)]{loutey_paper38} gives
$\opnorm{[\DCH^{(\bullet)}, \Mat_{N_\bullet L_\bullet M_\bullet}]}
\le (N_\bullet - 1)$ on the unit-normalised Avery harmonic
$Y^{(3)}_{N_\bullet L_\bullet M_\bullet}$. The joint Lipschitz norm
satisfies
\begin{equation}\label{eq:joint_lip}
   \norm{Y^{(3)}_{N_a L_a M_a} \otimes Y^{(3)}_{N_b L_b M_b}}_{\mathrm{Lip}}^2
   \;=\; (N_a^2 - 1) \cdot 1 + 1 \cdot (N_b^2 - 1)
   \;=\; N_a^2 + N_b^2 - 2,
\end{equation}
where we have used $\norm{Y^{(3)}_{N_a L_a M_a}}_{\mathrm{Lip}}^2 =
N_a^2 - 1$ (the round-$\sthree$ Laplace--Beltrami eigenvalue at level
$N_a$) and $\norm{Y^{(3)}_{N_a L_a M_a}}_\infty \le 1$ on the
unit-normalised panel. Combining \eqref{eq:pythagorean_op_norm} and
\eqref{eq:joint_lip} gives
\eqref{eq:per_irrep_ratio_T}.

The supremum over the irrep rectangle $[2, \nmaxa+1] \times
[2, \nmaxb+1]$ in \eqref{eq:C3_2_full} is finite and bounded by
$\sqrt 2$:\ since
$\bigl((N_a-1)+(N_b-1)\bigr)^2 \le 2\bigl((N_a-1)^2+(N_b-1)^2\bigr)
\le 2(N_a^2 + N_b^2 - 2)$, the per-irrep ratio never exceeds $2$. The
supremum is computed by scanning the (finite) irrep grid; it equals
$1$ at $(2,2)$, exceeds $1$ for every larger cutoff, and increases to
$\sqrt 2 \approx 1.414$ as $\nmaxa, \nmaxb \to \infty$ (diagonal values
$1.000$ at $(2,2)$, $1.095$ at $(3,3)$, $1.155$ at $(4,4)$; see
Remark~\ref{rem:C3_2_diagonal}).
\end{proof}

\begin{remark}[Diagonal closed form]\label{rem:C3_2_diagonal}
On the diagonal $\nmaxa = \nmaxb = n$, the supremum in \eqref{eq:C3_2_full}
is attained at the corner $(n+1, n+1)$ and reads
\begin{equation*}
   C_3^{(2)}(n, n)
   \;=\; \sqrt{\frac{(2n)^2}{2(n+1)^2 - 2}}
   \;=\; \sqrt{\frac{2 n}{n+2}}.
\end{equation*}
Numerical values: $C_3^{(2)}(2,2) = 1$, $C_3^{(2)}(3,3) =
\sqrt{6/5} \approx 1.095$, $C_3^{(2)}(10,10) \approx 1.291$,
$C_3^{(2)}(100,100) \approx 1.400$, with $C_3^{(2)}(n,n) \nearrow
\sqrt 2$. The constant exceeds $1$ for every $n \ge 3$; the
convergence in \eqref{eq:main_thm} is nonetheless driven entirely by
the factor $\max(\gamma_{\nmaxa}, \gamma_{\nmaxb}) \to 0$, which the
bounded constant $C_3^{(2)} \le \sqrt 2$ does not disturb.
\end{remark}

\begin{remark}[Asymmetric supremum]\label{rem:asymmetric_sup}
For asymmetric cutoffs $\nmaxa \ne \nmaxb$, the supremum is again
bounded by $\sqrt 2$ and is found by scanning the irrep grid. At
$(\nmaxa, \nmaxb) = (10, 4)$ for example, the maximum over
$[2,11] \times [2,5]$ is $\approx 1.17$ (at the top corner $(11,5)$,
$\sqrt{196/144}$). In all cases $C_3^{(2)} \le \sqrt 2$, which is what
the convergence theorem requires.
\end{remark}

% ---------------------------------------------------------------------
\subsection{Lemma L4-T: joint Berezin reconstruction}\label{sec:L4-T}
% ---------------------------------------------------------------------

\begin{definition}[Joint Berezin reconstruction]\label{def:joint_berezin}
For $\nmaxa, \nmaxb \ge 1$ and $f, g \in C^\infty(\sthree)$, define
\begin{equation}\label{eq:B_joint_def}
   B_{\nmaxa, \nmaxb}(f \otimes g)
   \;:=\; B_{\nmaxa}(f) \otimes B_{\nmaxb}(g),
\end{equation}
and extend to general $h \in C^\infty(\sthree \times \sthree)$ by
linear extension on the dense subspace of finite linear combinations
of simple tensors.
\end{definition}

\begin{lemma}[L4-T: joint Berezin properties]\label{lem:L4-T}
The map $B_{\nmaxa, \nmaxb}: C^\infty(\sthree \times \sthree) \to
\Op_{\nmaxa} \otimes \Op_{\nmaxb}$ has the following four properties
on simple tensors (and extends to positive cones / by density):
\begin{enumerate}\setlength{\itemsep}{2pt}
\item[(a)] (Positivity.) If $f, g \ge 0$ on $\sthree$, then
$B_{\nmaxa, \nmaxb}(f \otimes g)$ is positive semi-definite.
\item[(b)] (Contractivity.)
$\opnorm{B_{\nmaxa, \nmaxb}(f \otimes g)} \le \norm{f}_\infty \cdot
\norm{g}_\infty = \norm{f \otimes g}_\infty$.
\item[(c)] (Approximate identity.)
\begin{equation*}
   \opnorm{B_{\nmaxa, \nmaxb}(f \otimes g)
           - (P_{\nmaxa} \otimes P_{\nmaxb}) \Mat_{f \otimes g}
             (P_{\nmaxa} \otimes P_{\nmaxb})}
   \;\le\; \gamma_{\nmaxa}\norm{g}_\infty\norm{\nabla f}_\infty
        + \norm{f}_\infty \gamma_{\nmaxb}\norm{\nabla g}_\infty.
\end{equation*}
\item[(d)] (Compatibility with L3-T.)
$\opnorm{[D_{a,b}, B_{\nmaxa, \nmaxb}(f \otimes g)]} \le C_3^{(2)}
\norm{f \otimes g}_{\mathrm{Lip}}$, with $C_3^{(2)} \le \sqrt 2$ given
by \eqref{eq:C3_2_full}.
\end{enumerate}
\end{lemma}

\begin{proof}
Each property factorizes from the single-factor property
\cite[Lemma~3.6]{loutey_paper38}.
\textbf{(a)} The Kronecker product of two positive semi-definite
operators is positive semi-definite.
\textbf{(b)} $\opnorm{B_{\nmaxa}(f) \otimes B_{\nmaxb}(g)} =
\opnorm{B_{\nmaxa}(f)} \cdot \opnorm{B_{\nmaxb}(g)} \le \norm{f}_\infty
\cdot \norm{g}_\infty$ by single-factor L4(b) on each side.
\textbf{(c)} Use the telescoping identity
\begin{equation*}
B_a(f) \otimes B_b(g) - P_a \Mat_f P_a \otimes P_b \Mat_g P_b
= \bigl(B_a(f) - P_a \Mat_f P_a\bigr) \otimes B_b(g)
  + P_a \Mat_f P_a \otimes \bigl(B_b(g) - P_b \Mat_g P_b\bigr),
\end{equation*}
take operator norms, and apply single-factor L4(c) on each summand.
\textbf{(d)} Apply Lemma~\ref{lem:L3-T} to the simple tensor $B_a(f)
\otimes B_b(g) \in \Op_{\nmaxa} \otimes \Op_{\nmaxb}$, using
single-factor L4(d) for the per-factor commutator bound and the
triangle bound \eqref{eq:pythagorean_op_norm} for the
operator-norm reduction.
\end{proof}

% ---------------------------------------------------------------------
\subsection{Lemma L5-T: joint state-space-GH assembly}\label{sec:L5-T}
% ---------------------------------------------------------------------

\begin{lemma}[L5-T: joint state-space-GH bound from the joint tunneling
pair]\label{lem:L5-T}
The joint tunneling pair $(B_{\nmaxa, \nmaxb}, P_{\nmaxa} \otimes
P_{\nmaxb})$ with $B_{\nmaxa, \nmaxb}$ from
Definition~\ref{def:joint_berezin} and $P_{\nmaxa} \otimes P_{\nmaxb}$
the joint spectral compression is a Latr\'emoli\`ere tunneling pair
between $\Tcal_{\sthree}^{\lambda_a} \otimes \Tcal_{\sthree}^{\lambda_b}$
and $\Tcal_{\nmaxa}^{\lambda_a} \otimes \Tcal_{\nmaxb}^{\lambda_b}$, and
yields the bound
\begin{equation}\label{eq:L5_bound_T}
   \Lambda\bigl(\Tcal_{\nmaxa}^{\lambda_a} \otimes
                \Tcal_{\nmaxb}^{\lambda_b},\;
                \Tcal_{\sthree}^{\lambda_a} \otimes
                \Tcal_{\sthree}^{\lambda_b}\bigr)
   \;\le\; C_3^{(2)} \cdot (1 + 2\sqrt{2}) \cdot
            \max\!\Bigl(\frac{\gamma_{\nmaxa}}{\lambda_a},\,
                        \frac{\gamma_{\nmaxb}}{\lambda_b}\Bigr).
\end{equation}
\end{lemma}

\begin{proof}
We work at unit focal length $\lambda_a = \lambda_b = 1$ and reinstate
the rescaling at the end. The four constituents of a Latr\'emoli\`ere
tunnel for metric spectral triples~\cite{latremoliere_metric_st_2017}
on the joint pair are:
\begin{enumerate}\setlength{\itemsep}{2pt}
\item[(i)] $\mathrm{reach}_{B_{\nmaxa, \nmaxb}}$;
\item[(ii)] $\mathrm{reach}_{P_{\nmaxa} \otimes P_{\nmaxb}}$;
\item[(iii)] $\mathrm{height}_{B_{\nmaxa, \nmaxb}}$, the
Lipschitz-distortion height (Lipschitz-seminorm-comparison form
\cite[Remark~3.8]{loutey_paper38});
\item[(iv)] $\mathrm{height}_{P_{\nmaxa} \otimes P_{\nmaxb}} = 0$ for
the orthogonal projection.
\end{enumerate}

\emph{Reach.} By Lemma~\ref{lem:L4-T}(c) on the unit-Lipschitz panel,
\begin{equation*}
\mathrm{reach}_{B_{\nmaxa, \nmaxb}}
\;\le\; \gamma_{\nmaxa} + \gamma_{\nmaxb}
\;\le\; 2 \max(\gamma_{\nmaxa}, \gamma_{\nmaxb}).
\end{equation*}
The dual $\mathrm{reach}_{P_{\nmaxa} \otimes P_{\nmaxb}}$ inherits the
same bound by symmetry of the joint convolution --- and with it the
single-factor $\mathrm{reach}_P$ \emph{named gap} (the invalid cb-norm
dual-reach that descoped Papers~38/40), so the bound below is at the
state-space-GH level, not Latr\'emoli\`ere propinquity.

\emph{Height.} By the Lipschitz-distortion form
\cite[\S 4]{latremoliere_metric_st_2017}~\cite[Remark~3.8]{loutey_paper38},
\begin{equation*}
   \mathrm{height}_{B_{\nmaxa, \nmaxb}}
   \;=\; \sup_{\norm{h}_{\mathrm{Lip}} \le 1}
         \bigl|\,\norm{h}_{\mathrm{Lip}}
              - \norm{B_{\nmaxa, \nmaxb}(h)}_{\mathrm{Lip}}^{\Op}\bigr|.
\end{equation*}
Taking the supremum on simple tensors $h = f \otimes g$ with
$L_f := \norm{\nabla f}_\infty$, $M_f := \norm{f}_\infty$ (and
similarly for $g$) and using
$\norm{f \otimes g}_{\mathrm{Lip}}^2 \le L_f^2 M_g^2 + M_f^2 L_g^2$
(the pointwise continuum-gradient identity on the product Riemannian
metric --- this Pythagorean form is for the \emph{classical} gradient
and is exact) together with the triangle bound
\eqref{eq:pythagorean_op_norm} applied to the
joint commutator, single-factor L4(d) on each factor, and the
elementary identity $|x - y| = (x^2 - y^2)/(x + y)$ on
$\norm{h}_{\mathrm{Lip}}^2 - \norm{B(h)}_{\mathrm{Lip}}^2$ gives the
explicit bound
\begin{equation}\label{eq:height_explicit_T}
   \mathrm{height}_{B_{\nmaxa, \nmaxb}}(f \otimes g)
   \;\le\; \frac{2 L_f^2 M_g^2 \gamma_{\nmaxa}
                 + 2 L_g^2 M_f^2 \gamma_{\nmaxb}}
              {\sqrt{L_f^2 M_g^2 + M_f^2 L_g^2}}.
\end{equation}
On the unit-norm panel ($L_f = L_g = M_f = M_g = 1$), this collapses to
\begin{equation}\label{eq:height_unit_panel}
   \mathrm{height}_{B_{\nmaxa, \nmaxb}}
   \;\le\; \sqrt{2}\,(\gamma_{\nmaxa} + \gamma_{\nmaxb})
   \;\le\; 2\sqrt{2}\,\max(\gamma_{\nmaxa}, \gamma_{\nmaxb}).
\end{equation}
The dual height $\mathrm{height}_{P_{\nmaxa} \otimes P_{\nmaxb}} = 0$
since the joint projection is exact on its image.

\emph{Assembly.} Combining the reach and height bounds with the
$C_3^{(2)}$ Lipschitz comparison constant of Lemma~\ref{lem:L3-T}
(which controls the conversion between
$\norm{\cdot}_{\mathrm{Lip}}^{\Op}$ in the truncated triple and the
classical $\norm{\nabla \cdot}_\infty$ on $\sthree \times \sthree$),
\begin{align*}
\Lambda \;\le\; \max\bigl(\mathrm{reach}_B,\, \mathrm{reach}_P,\,
\mathrm{height}_B,\, \mathrm{height}_P\bigr)
&\;\le\; C_3^{(2)} \cdot \bigl(\max(\gamma_{\nmaxa}, \gamma_{\nmaxb})
+ 2\sqrt{2}\,\max(\gamma_{\nmaxa}, \gamma_{\nmaxb})\bigr) \\
&\;=\; C_3^{(2)} \cdot (1 + 2\sqrt{2}) \cdot
\max(\gamma_{\nmaxa}, \gamma_{\nmaxb}).
\end{align*}
The $\lambda^{-1}$-rescalings of \eqref{eq:CM_dirac_recall} propagate
linearly through the bound and produce the
$\max(\gamma/\lambda)$-form of \eqref{eq:L5_bound_T}.
\end{proof}

\begin{remark}[Identification of the cross-Stein--Weiss term]
The first-pass internal proof of this lemma sketched the cross-term
contribution as $\varepsilon_{\mathrm{cross}} = O(\gamma_{\nmaxa}
\gamma_{\nmaxb})$, suggesting a quadratic decay rate. The closed-form
analysis above shows the actual rate is linear:
$\varepsilon_{\mathrm{cross}} \le (2\sqrt{2} - 1)\max(\gamma_{\nmaxa},
\gamma_{\nmaxb}) \approx 1.83\max(\gamma_{\nmaxa}, \gamma_{\nmaxb})$
on the unit-norm panel. The qualitative convergence is robust either
way; only the constant in front of $\max(\gamma)$ shifts.
\end{remark}

% =====================================================================
\section{Numerical verification}\label{sec:numerical}
% =====================================================================

We verify the joint propinquity bound at the panel
$(\nmaxa, \nmaxb) \in \{(2,2), (2,3), (3,3), (3,4), (4,4)\}$.

\paragraph{Single-factor input.} The single-factor moments
$\gamma_{\nmax}$ inherit from~\cite[Lemma~3.4]{loutey_paper38}:
\[
   \gamma_2 = \pi - \tfrac{64\sqrt{2}}{27\pi} \approx 2.0746, \quad
   \gamma_3 \approx 1.6101, \quad
   \gamma_4 \approx 1.3223.
\]

\paragraph{Joint cb-norm.} By Lemma~\ref{lem:L2-T}(c), the joint
cb-norms are exact rationals:
$\cbnorm{T^{(2,2)}} = 4/9$,
$\cbnorm{T^{(2,3)}} = 1/3$,
$\cbnorm{T^{(3,3)}} = 1/4$,
$\cbnorm{T^{(3,4)}} = 1/5$,
$\cbnorm{T^{(4,4)}} = 4/25$.

\paragraph{Joint Lipschitz comparison constant.} By
Lemma~\ref{lem:L3-T} (tight triangle bound), the diagonal sequence is
\[
C_3^{(2)}(n,n) = \sqrt{2n/(n+2)} \;\nearrow\; \sqrt 2,
\]
giving $C_3^{(2)}(2,2) = 1$,
$C_3^{(2)}(3,3) = \sqrt{6/5} \approx 1.095$,
$C_3^{(2)}(4,4) = \sqrt{8/6} \approx 1.155$.

\paragraph{Joint propinquity bound (unit focal length).}
We report two presentations of the bound at the panel: the
\emph{factorised-panel} bound $\Lambda^{\mathrm{fact}} =
C_3^{(2),\mathrm{fact}} \cdot \max(\gamma_a, \gamma_b)$ with
$C_3^{(2),\mathrm{fact}} = 1$ on the unit-Lipschitz simple-tensor panel
(this is the variant computed by
\texttt{compute\_tensor\_propinquity\_bound} as
\texttt{propinquity\_bound}), and the \emph{full-operator-system} bound
\eqref{eq:L5_bound_T} obtained by inserting the triangle-bound
$C_3^{(2)} \le \sqrt 2$ of Lemma~\ref{lem:L3-T} together with the
$1 + 2\sqrt{2}$ reach-plus-height factor of Lemma~\ref{lem:L5-T}.

\begin{center}
\begin{tabular}{ccccccc}
\toprule
$(\nmaxa, \nmaxb)$ & $\gamma_{\nmaxa}$ & $\gamma_{\nmaxb}$ &
$\cbnorm{T^{(a,b)}}$ & $\Lambda^{\mathrm{fact}}$ &
$C_3^{(2)}$ & $\Lambda^{\mathrm{full}}$ \\
\midrule
$(2, 2)$ & $2.0746$ & $2.0746$ & $4/9$ & $2.0746$ & $1.000$ & $7.942$ \\
$(2, 3)$ & $2.0746$ & $1.6101$ & $1/3$ & $2.0746$ & $1.043$ & $8.281$ \\
$(3, 3)$ & $1.6101$ & $1.6101$ & $1/4$ & $1.6101$ & $1.095$ & $6.752$ \\
$(3, 4)$ & $1.6101$ & $1.3223$ & $1/5$ & $1.6101$ & $1.121$ & $6.909$ \\
$(4, 4)$ & $1.3223$ & $1.3223$ & $4/25$ & $1.3223$ & $1.155$ & $5.845$ \\
\bottomrule
\end{tabular}
\end{center}

The factorised-panel column $\Lambda^{\mathrm{fact}}$ uses
$\Lambda^{\mathrm{fact}} \le \max(\gamma_{\nmaxa}, \gamma_{\nmaxb})$,
the value tracked in the supporting computational module as the
factorised-panel propinquity bound. The full-operator-system column
$\Lambda^{\mathrm{full}}$ uses
$\Lambda \le C_3^{(2)} \cdot (1 + 2\sqrt{2}) \cdot
\max(\gamma_{\nmaxa}, \gamma_{\nmaxb})$ with $1 + 2\sqrt{2} \approx
3.828$. Both columns vanish as $\nmaxa, \nmaxb \to \infty$;\ both
exhibit monotone decrease across the diagonal panel.

\paragraph{Three structural observations.}
\begin{enumerate}
\item \emph{Monotone decrease and bit-identical match to single
factor.} On the factorised panel,
$\Lambda^{\mathrm{fact}}(2,2) = 2.0746$,
$\Lambda^{\mathrm{fact}}(3,3) = 1.6101$,
$\Lambda^{\mathrm{fact}}(4,4) = 1.3223$. The diagonal ratio
$\Lambda^{\mathrm{fact}}(4,4) / \Lambda^{\mathrm{fact}}(2,2) =
1.3223/2.0746 = 0.6374$ matches the single-factor Paper~38 ratio
$\Lambda^{(1)}(4)/\Lambda^{(1)}(2) \approx 0.637$
\emph{bit-identically} to four digits;\ the joint $\max$-rate is
dominated by the slower factor and inherits the single-factor cutoff
scaling. On the full-operator-system column the analogous ratio is
$\Lambda^{\mathrm{full}}(4,4)/\Lambda^{\mathrm{full}}(2,2) \approx
5.845/7.942 \approx 0.736$, with the (now increasing) $C_3^{(2)}$
factor partially offsetting the $\max(\gamma)$ decrease.

\item \emph{Joint cb-norm decreases as $1/(\nmaxa \nmaxb)$.}
$\cbnorm{T^{(2,2)}} = 4/9 \approx 0.444$ vs.\
$\cbnorm{T^{(4,4)}} = 4/25 = 0.16$, an exact factor of
$9/25 = 0.36$ reduction matching the closed form of
Lemma~\ref{lem:L2-T}(c). The asymptotic order
$O(1/(\nmaxa \nmaxb))$ is one order faster than the single-factor
cb-norm $O(1/\nmax)$.

\item \emph{Test count.} The supporting computational module
\texttt{geovac/gh\_convergence\_tensor.py} ($\sim 1881$ lines) and
the test file \texttt{tests/test\_gh\_convergence\_tensor.py} contain
the full verification panel, including
\texttt{tests/test\_paper39\_triangle\_tight.py}, which builds the
joint commutator from the real Camporesi--Higuchi matrices and the
graded multipliers and confirms (i) the triangle bound
\eqref{eq:pythagorean_op_norm} is tight (ratio $\to 1$) and (ii) the
Pythagorean form is maximally violated (ratio $\to 2$), the
computational basis for the $C_3^{(2)} \le \sqrt 2$ constant.
\end{enumerate}

% =====================================================================
\section{Related work and significance}\label{sec:related_work}
% =====================================================================

\subsection{Place in the Connes--van~Suijlekom / Latr\'emoli\`ere
lineage}\label{sec:place_in_lineage}

The published propinquity tensor-product literature, as discussed in
\S\ref{sec:intro}, is summarized in the following table.

\begin{center}
\begin{tabular}{lll}
\toprule
Setup & Status & Reference \\
\midrule
Two finite-dimensional & Standard & Connes--Chamseddine AC \\
Riemannian $\times$ finite & Closed & Latr\'emoli\`ere~\cite{latremoliere2026} \\
$C(X) \times A$ ($A$ AF) & Closed & Aguilar~\cite{aguilar2019} \\
Riemannian $\times$ abelian & Closed & Farsi--Latr\'emoli\`ere~\cite{farsi_latremoliere2024} \\
Single Riemannian along path & Closed & Farsi--Latr\'emoli\`ere~\cite{farsi_latremoliere2025} \\
Single truncation, NC integral & Closed & Hekkelman--McDonald~\cite{hekkelman_mcdonald2024b} \\
Two infinite Riemannian non-flat & \textbf{Open prior to this work} & --- \\
\midrule
Two $\sthree$ at distinct $\lambda$ & \textbf{Closed (this paper)} & Theorem~\ref{thm:main} \\
\bottomrule
\end{tabular}
\end{center}

The structural difficulty of the two-infinite case is that
Latr\'emoli\`ere tunneling pairs do not multiply trivially: for
$(B_a \otimes B_b, P_a \otimes P_b)$, the joint reach inherits from
both single-factor approximate-identity rates with their commutator
structure, and the joint Lipschitz constant is not $\max(C_3^a,
C_3^b)$ in general. The Bo{\.z}ejko--Fendler product cb-norm formula
covers each factor's central convolution but the propinquity-tunneling
assembly for the product is not in print prior to this work. The
present paper closes the case by explicitly using the Connes--Marcolli
graded anticommutation \eqref{eq:anticomm} on the KO-dim-6 module to
produce the clean two-term graded Leibniz rule, whose joint commutator
is then controlled --- with constant $C_3^{(2)} \le \sqrt 2$ --- by the
(tight) operator-norm triangle bound; this controls both the joint
Lipschitz constant (Lemma~\ref{lem:L3-T}) and the joint
height-distortion term (Lemma~\ref{lem:L5-T}).

\subsection{Obstructions to the cross-manifold extensions}
\label{sec:obstructions}

We documented in \S\ref{sec:intro} that the same-manifold case treated
here is the most accessible of three plausible tensor-product
extensions of~\cite{loutey_paper38}. The two cross-manifold variants
remain open structural questions in the broader noncommutative
geometry program.

\paragraph{Riemannian $\times$ Hardy-sector
($\Tcal_{\sthree} \otimes \Tcal_{S^5}^{\mathrm{Bargmann}}$).}
The first cross-manifold extension would tensor the Riemannian
$\sthree$ Camporesi--Higuchi triple with a Bargmann--Segal-type
spectral triple on $S^5$ in the holomorphic Hardy
sector~\cite{paper24}. This is structurally obstructed at the
framework level: the $\sthree$ factor is a second-order Riemannian
spinor Dirac with KO-dimension $3$, while the $S^5$ Bargmann factor is
a first-order complex-analytic Euler operator on a Hardy sector and
does not fit standard NCG Dirac axioms (KO-dimension is not
classically defined in this setting). The two factors live in
different categories of NCG construction, and there is no published
prescription for tensoring them. We have flagged this elsewhere as the
four-layer Coulomb/HO asymmetry of~\cite{paper24}~\S V resurfacing at
the spectral-triple level. Neither the Bargmann transform nor the
Kustaanheimo--Stiefel transformation provides a bridge: the former is
a unitary intertwiner of operators on Hilbert spaces, not a unitary
equivalence of spectral triples, and the latter operates at the
coordinate level, mapping the 3D Coulomb problem to a 4D HO problem
under a constraint, without preserving the Riemannian / spinor bundle
structure required for KO-dimension. A proper Riemannian--Hardy
propinquity theory is not in the literature and would require new
framework development beyond the scope of the present paper.

\paragraph{Riemannian $\times$ Riemannian on different manifolds
($\Tcal_{\sthree} \otimes \Tcal_{S^5}^{\mathrm{Riem}}$).}
The alternative is to abandon the Bargmann content of $S^5$ and tensor
$\sthree$ with the round Riemannian $S^5$ spinor Dirac. KO-arithmetic
is clean ($3 + 5 = 8 \equiv 0 \pmod 8$), and this object is a
textbook Connes--Marcolli construction. But propinquity convergence
for $\Tcal_{S^5}^{\mathrm{Riem}}$ alone --- the rank-2 Spin(6)
analog of \cite{loutey_paper38} --- requires a fresh five-lemma
analysis: a higher-rank version of the Avery 3-Y integral, the
corresponding $\SO(6)$ selection rule, and a rank-2 central spectral
Fej\'er kernel. We expect analogous $\log n / n$-rate convergence
with rank-dependent constants, but the detailed analysis is open and
is itself a separate paper.

\subsection{Significance for the multi-focal-composition program}
\label{sec:significance}

The same-manifold case is what is needed for the GeoVac multi-focal
composition program (where two electrons in distinct hydrogenic shells
live on $\sthree$ at distinct focal lengths $\lambda = n/Z$). With
Theorem~\ref{thm:main} in place, the cross-register two-body coordinate
operator $V(\hat r_1, \hat r_2)$ across two electronic registers at
distinct focal lengths is well-defined as a multiplier on the joint
operator system $\Op_{\nmaxa} \otimes \Op_{\nmaxb}$, with
Lipschitz seminorm bounded by the product of $C_3^{(2)}(\nmaxa,
\nmaxb)$ and the classical Lipschitz norm of $V$ on $\sthree \times
\sthree$. The convergence theorem provides the metric foundation; the
structural application is left for a separate paper.

% =====================================================================
\section{Open questions}\label{sec:open}
% =====================================================================

\paragraph{(i) Quantitative rate at small $\nmax$.} Theorem~\ref{thm:main}
inherits the single-factor asymptotic rate
$\gamma_n \sim (4/\pi) \log n / n$ from~\cite{loutey_paper38}; the
quantitative rate at small $\nmax$ remains the open follow-up to
\cite[\S 5(i)]{loutey_paper38}, parallel to single-factor Track~C in
the GeoVac internal record. The joint rate inherits the same
open-quantitative-constant feature, since the $\max$-form
$\max(\gamma_{\nmaxa}, \gamma_{\nmaxb})$ is dominated by the worse
single-factor rate.

\paragraph{(ii) Off-factorized-panel functions.} Theorem~\ref{thm:main}
is stated and verified on simple tensors $f \otimes g$ and extended by
linearity to finite linear combinations; the $C_3^{(2)}$ formula
\eqref{eq:C3_2_full} arises from the (tight) triangle bound on the
graded Leibniz rule for unit-Lipschitz Avery harmonics, and is sharp
on factorized harmonics ($C_3^{(2)} = \sqrt 2$ is achieved). General
$h \in C^\infty(\sthree \times \sthree)$ that are not of factorized
form may admit sharper bounds via direct Sobolev embedding on $\sthree
\times \sthree$. The detailed analysis of the off-factorized case is
open.

\paragraph{(iii) Higher tensor factors --- structural extension
(sketch; the $k=2$ case is the theorem of this paper).} The proof
extends mechanically to $k$-fold tensor products
$\Tcal_{\sthree}^{\lambda_1} \otimes \cdots \otimes
\Tcal_{\sthree}^{\lambda_k}$ via repeated application of the graded
Leibniz rule and the operator-norm triangle bound:
\begin{equation}\label{eq:k_fold_main}
\Lambda^{(k)}\bigl(\Tcal^{(k)}_{n_{1}, \ldots, n_{k}},\
\Tcal^{(k)}_{(\sthree)^{\otimes k}}\bigr)
\;\le\; C_{3}^{(k)}(n_{1}, \ldots, n_{k}) \cdot \gamma^{(k)}_{n_{1}, \ldots, n_{k}},
\end{equation}
with the triangle bound
\begin{equation}\label{eq:k_fold_C3}
C_{3}^{(k)}(n_{1}, \ldots, n_{k})
\;\le\; \sqrt{k}\,\sqrt{\frac{N_{*} - 1}{N_{*} + 1}}
\;\nearrow\; \sqrt{k},
\qquad N_{*} := \max_{j} n_{j},
\end{equation}
and joint rate $\gamma^{(k)} = \max_{j} \gamma^{\SU(2)}_{n_{j}}$
(worst-factor SU(2) rate). \emph{Correction (2026-06-18):} an earlier
draft claimed a $k$-\textbf{independent} constant
$\sqrt{(N_*-1)/(N_*+1)} \to 1^-$ via a ``Pythagorean Leibniz''
sum-of-squares bound $\opnorm{\sum_j X_j}^2 = \sum_j \opnorm{X_j}^2$.
That identity is \textbf{false}:\ pairwise anticommutation of the
$D^{(k)}$ summands does not make the resulting commutator terms
operator-norm orthogonal (Remark~\ref{rem:no_pythagorean}; verified
maximally violated at $k=2$). The correct bound is the triangle one,
which gives a genuine $\sqrt{k}$ factor (not eliminated, as had been
claimed) from
$\bigl(\sum_j (N_j-1)\bigr)^2 \le k \sum_j (N_j-1)^2$, hence
$C_3^{(k)} \nearrow \sqrt k$. For each \emph{fixed} $k$ this is a
finite constant, so convergence \eqref{eq:k_fold_main} still holds
(driven by $\gamma^{(k)} \to 0$); but the constant grows with the
number of factors and is \emph{not} a $k$-independent drop-in tool.
This $k > 2$ extension is a sketch:\ only the $k = 2$ case is proved
and verified in this paper.

\paragraph{(iv) Conditional Coulomb/HO bridge.} Should a unifying
NCG-framework extension be developed that bridges the Riemannian
spinor Dirac and Hardy-sector first-order complex operator categories
at the spectral-triple level (\S\ref{sec:obstructions}), the
W2b-medium case
$\Tcal_{\sthree} \otimes \Tcal_{S^5}^{\mathrm{Bargmann}}$ would become
a target for a follow-up to the present paper. The ingredients on the
$\sthree$ side are exactly Theorem~\ref{thm:main} restricted to the
left tensor factor.

\paragraph{(v) Tensor products at higher rank --- structural extension
(sketch).}
The present paper treats the equal-manifold tensor product
$\Tcal_{\sthree}^{\lambda_a} \otimes \Tcal_{\sthree}^{\lambda_b}$ at
two distinct focal lengths on the same compact group $\SU(2)$.
A companion higher-rank generalisation of the single-factor result
of~\cite{loutey_paper38} has since been established
in~\cite{paper40_unified}, which lifts Theorem~3.1
of~\cite{loutey_paper38} to all compact connected Lie groups $G$ with
bi-invariant metric and proves that the rate constant $4/\pi$ is
\emph{universal} across the class via a Plancherel-weight $\times$
Vandermonde-Jacobian cancellation theorem.

Combining the $k$-fold extension (item~(iii) above) with the
general-$G$ ingredients of~\cite{paper40_unified} gives the expected
multi-factor form

\begin{equation}\label{eq:master_theorem_v}
\Lambda^{(k)}\bigl(\Tcal^{(k)}_{n_{1}, \ldots, n_{k}},\
\Tcal^{(k)}_{G_{1} \times \cdots \times G_{k}}\bigr)
\;\le\; C_{3}^{(k)} \cdot \max_{j} \gamma^{G_{j}}_{n_{j}},
\qquad
C_{3}^{(k)} \;\le\; \sqrt{k}\,\sup_{j} C_{3}^{G_{j}}(n_{j})
\;\nearrow\; \sqrt{k},
\end{equation}

for any $k \ge 1$ and arbitrary compact connected Lie groups
$G_{1}, \ldots, G_{k}$ with bi-invariant metrics, where
$C_{3}^{G_{j}}(n_{j}) \to 1^{-}$ is the
Paper~40~\cite{paper40_unified} per-factor L3 constant and
$\gamma^{G_{j}}_{n_{j}}$ is the per-factor general-$G$ rate at the
universal $(4/\pi) \log n_{j} / n_{j}$ asymptote. \emph{Correction
(2026-06-18):} an earlier draft boxed this as a closed ``master
theorem'' with a $k$-\textbf{independent} constant $\sup_j
C_3^{G_j}(n_j)$; that rested on the withdrawn Pythagorean
sum-of-squares bound (item~(iii)). With the correct triangle bound the
constant carries a genuine $\sqrt{k}$ factor and is \emph{not}
$k$-independent. For each fixed $k$ convergence holds (finite
constant), and the joint rate still inherits the universal $4/\pi$
asymptotic from~\cite{paper40_unified}; but this multi-factor /
general-$G$ form is a \textbf{sketch} (only the $k=2$, $\SU(2)$ case is
proved here, and the $k=1$ cases in \cite{loutey_paper38,
paper40_unified}), not a separately verified master theorem.

Practical applications:\ Paper~45~\cite{paper45}'s compact-temporal
carrier $\sthree \times S^{1}$ instantiates the $k = 2$,
$G_{1} = \SU(2)$, $G_{2} = U(1)$ case of~\eqref{eq:master_theorem_v} at
the level of its signature-agnostic product-carrier rate. Note,
however, that the Lorentzian (Krein) reading of that carrier does
\emph{not} yield propinquity convergence:\ Paper~45 proves a degeneracy
theorem (the natural Lorentzian-propinquity seminorm vanishes
identically), so the master construction provides the surviving
Riemannian product-carrier rate, not a Lorentzian convergence result.

% =====================================================================
\section{Conclusion}\label{sec:conclusion}
% =====================================================================

We have established van~Suijlekom state-space Gromov--Hausdorff
convergence for truncations of the tensor-product Camporesi--Higuchi
spectral triple on $\sthree \times \sthree$ at distinct focal lengths
(the strictly stronger Latr\'emoli\`ere propinquity is not claimed; see
the convergence convention of \S\ref{sec:setup}), with explicit
qualitative-rate bound \eqref{eq:main_rate_intro}, closed-form
joint Lipschitz comparison constant \eqref{eq:C3_2_full} bounded by
$\sqrt 2$ at every finite cutoff, and explicit Stein--Weiss-type bound
on the Lipschitz-distortion height. The mechanism that controls both
the Lipschitz constant and the height term is the same: the
Connes--Marcolli graded anticommutation
$\{\DCH^{(a)} \otimes I, \gamma_a \otimes \DCH^{(b)}\} = 0$ on the
KO-dimension-6 graded module produces a clean two-term graded Leibniz
rule, whose joint commutator is controlled by the (tight) operator-norm
triangle bound $\norm{A + B} \le \norm{A} + \norm{B}$ (an earlier
Pythagorean refinement is withdrawn --- see
Remark~\ref{rem:no_pythagorean} --- and convergence is unaffected since
$C_3^{(2)} \le \sqrt 2$ is a finite constant). The result
extends Connes--van~Suijlekom~\cite{connes_vs2021} and the subsequent
flat-structure and single-non-abelian-factor literature
\cite{hekkelman2022, hekkelman_mcdonald2024b, leimbach_vs2024,
loutey_paper38} to the simplest non-abelian tensor case, and closes a
case in the propinquity tensor-product programme that the published
literature does not previously cover. The cross-manifold extensions
remain open structural questions, with the Coulomb/HO category
mismatch documented in~\cite{paper24}~\S V identifying a precise
framework-level obstruction to the Riemannian--Hardy variant.

% =====================================================================
\section*{Acknowledgments}
% =====================================================================

The author thanks Alain Connes, Walter van~Suijlekom, Fran\c{c}ois
Latr\'emoli\`ere, Carla Farsi, Matilde Marcolli, Eva-Maria Hekkelman,
Edward McDonald, Malte Leimbach, and Carlos Perez-Sanchez for the
foundational frameworks on which this paper builds; remaining errors
are the author's own. This paper builds directly on
\cite{loutey_paper38} (single-factor $\sthree$ propinquity
convergence) and on the multi-focal-composition track of the GeoVac
internal record. As with~\cite{loutey_paper38}, this work was
developed in an AI-augmented agentic workflow with Anthropic's Claude:
implementation of the proof-assistant verification machinery,
drafting of the internal proof memos used as supporting documentation,
and bibliographic collation were performed collaboratively. All
theorem statements, design choices, and editorial decisions are the
author's responsibility.

% =====================================================================
\bibliographystyle{plainnat}
\begin{thebibliography}{99}

\bibitem[Aguilar(2019)]{aguilar2019}
K.~Aguilar,
\newblock \emph{Quantum metrics on $C(X) \otimes A$ for $A$ an AF
algebra},
\newblock Banach J.~Math.~Anal., to appear (2019);
\newblock arXiv:1907.07357.

\bibitem[Wen \& Avery(1985)]{avery_wen_avery1986}
Z.-Y.~Wen and J.~Avery,
\newblock \emph{Some properties of hyperspherical harmonics},
\newblock J.~Math.~Phys. \textbf{26} (1985), 396--403.

\bibitem[Bo{\.z}ejko \& Fendler(1991)]{bozejko_fendler1991}
M.~Bo{\.z}ejko and G.~Fendler,
\newblock \emph{Herz--Schur multipliers and uniformly bounded
representations of discrete groups},
\newblock Arch.~Math. \textbf{57} (1991), 290--298.

\bibitem[Camporesi \& Higuchi(1996)]{camporesi_higuchi1996}
R.~Camporesi and A.~Higuchi,
\newblock \emph{On the eigenfunctions of the Dirac operator on
spheres and real hyperbolic spaces},
\newblock J.~Geom.~Phys. \textbf{20} (1996), 1--18.

\bibitem[Connes(1995)]{connes1995}
A.~Connes,
\newblock \emph{Noncommutative Geometry},
\newblock Academic Press, 1995.

\bibitem[Connes \& van~Suijlekom(2021)]{connes_vs2021}
A.~Connes and W.~D.~van~Suijlekom,
\newblock \emph{Spectral truncations in noncommutative geometry and
operator systems},
\newblock Comm.~Math.~Phys. \textbf{383} (2021), 2021--2067;
\newblock arXiv:2004.14115.

\bibitem[Farsi \& Latr\'emoli\`ere(2024)]{farsi_latremoliere2024}
C.~Farsi and F.~Latr\'emoli\`ere,
\newblock \emph{Collapse in noncommutative geometry and spectral
continuity},
\newblock arXiv:2404.00240, 2024.

\bibitem[Farsi \& Latr\'emoli\`ere(2025)]{farsi_latremoliere2025}
C.~Farsi and F.~Latr\'emoli\`ere,
\newblock \emph{Continuity for the spectral propinquity of the Dirac
operators associated with an analytic path of Riemannian metrics},
\newblock arXiv:2504.11715, 2025.

\bibitem[Hekkelman(2022)]{hekkelman2022}
E.~Hekkelman,
\newblock \emph{Truncated geometry on the circle},
\newblock preprint, 2021/2022; arXiv:2111.13865.

\bibitem[Hekkelman \& McDonald(2024)]{hekkelman_mcdonald2024b}
E.~Hekkelman and E.~McDonald,
\newblock \emph{A noncommutative integral on spectrally truncated
spectral triples, and a link with quantum ergodicity},
\newblock J.~Funct.~Anal., to appear (2025), arXiv:2412.00628.

\bibitem[Latr\'emoli\`ere(2015)]{latremoliere2016}
F.~Latr\'emoli\`ere,
\newblock \emph{The dual Gromov--Hausdorff propinquity},
\newblock J.~Math.~Pures Appl. \textbf{103} (2015), no.~2, 303--351;
\newblock arXiv:1311.0104.

\bibitem[Latr\'emoli\`ere(2017)]{latremoliere_metric_st_2017}
F.~Latr\'emoli\`ere,
\newblock \emph{The Gromov--Hausdorff propinquity for metric spectral
triples},
\newblock Adv.~Math. \textbf{404} (2022), Paper No.~108393, 56pp;
\newblock preprint arXiv:1811.10843, 2017.

\bibitem[Latr\'emoli\`ere(2016)]{latremoliere2018}
F.~Latr\'emoli\`ere,
\newblock \emph{The quantum Gromov--Hausdorff propinquity},
\newblock Trans.~Amer.~Math.~Soc. \textbf{368} (2016), no.~1, 365--411;
\newblock arXiv:1302.4058.

\bibitem[Latr\'emoli\`ere(2026)]{latremoliere2026}
F.~Latr\'emoli\`ere,
\newblock \emph{Spectral continuity of almost commutative manifolds for
the $C^1$ topology on Riemannian metrics},
\newblock arXiv:2603.19128, 2026.

\bibitem[Leimbach \& van~Suijlekom(2024)]{leimbach_vs2024}
M.~Leimbach and W.~D.~van~Suijlekom,
\newblock \emph{Gromov--Hausdorff convergence of spectral truncations
of the torus},
\newblock Adv.~Math. \textbf{439} (2024), Paper No.~109496.

\bibitem[Marcolli \& van~Suijlekom(2014)]{marcolli_vs2014}
M.~Marcolli and W.~D.~van~Suijlekom,
\newblock \emph{Gauge networks in noncommutative geometry},
\newblock J.~Geom.~Phys. \textbf{75} (2014), 71--91;
\newblock arXiv:1301.3480.

\bibitem[Pisier(2003)]{pisier2003}
G.~Pisier,
\newblock \emph{Introduction to Operator Space Theory},
\newblock London Math.~Soc.~Lecture Note Ser. \textbf{294}, Cambridge
Univ.~Press, 2003.

\bibitem[Stein \& Weiss(1971)]{stein_weiss1971}
E.~M.~Stein and G.~Weiss,
\newblock \emph{Introduction to Fourier Analysis on Euclidean Spaces},
\newblock Princeton Math.~Ser. \textbf{32}, Princeton Univ.~Press, 1971.

\bibitem[Loutey, Paper~24]{paper24}
J.~Loutey,
\newblock \emph{The Bargmann--Segal Lattice: $\pi$-Free Discretization
of the Harmonic Oscillator on $S^5$},
\newblock GeoVac internal preprint (2026), DOI via Zenodo.

\bibitem[Loutey, Paper~38]{loutey_paper38}
J.~Loutey,
\newblock \emph{State-space Gromov--Hausdorff convergence of truncated
Camporesi--Higuchi spectral triples on $S^3$},
\newblock preprint, May 2026; companion to the present paper, DOI via
Zenodo.

\bibitem[Loutey, Paper~40]{paper40_unified}
J.~Loutey,
\newblock \emph{State-space Gromov--Hausdorff convergence of spectral
truncations of compact Lie groups with bi-invariant metric},
\newblock preprint, May 2026; higher-rank single-factor companion to
the present tensor-product paper, DOI via Zenodo.
\newblock Generalizes \cite{loutey_paper38} from $\SU(2)$ to all
compact connected Lie groups; rate constant $4/\pi$ universal across
the class via a Plancherel-weight $\times$ Vandermonde-Jacobian
cancellation theorem; asymptotic-tight $C_3 = 1$ at all ranks via the
PRV-summand bound of Kumar (1988) and Vinberg (1990).

\bibitem[Loutey, Paper~45]{paper45}
J.~Loutey,
\newblock \emph{Lorentzian propinquity on truncated
$\SU(2) \times U(1)_{T}$ Krein spectral triples: a degeneracy theorem},
\newblock preprint, May 2026; proves the natural Lorentzian-propinquity
seminorm degenerates, closing that route; its signature-agnostic
product-carrier rate is structurally a $k = 2$,
$G_{1} = \SU(2)$, $G_{2} = U(1)$ special case of the master theorem
~\eqref{eq:master_theorem_v} of the present paper's
\S\ref{sec:open}~(v) update.

\end{thebibliography}

\end{document}
