% =====================================================================
% Paper 39 (standalone): Latremoliere propinquity convergence on the
% tensor product of two truncated Camporesi-Higuchi spectral triples
% on S^3 at distinct focal lengths.
%
% Math.OA-style companion to Paper 38 (single-factor S^3 = SU(2)).
% Closes the W2b-easy keystone of the GeoVac multi-focal-composition
% program: tensor product of two infinite non-abelian metric spectral
% triples on the same Riemannian manifold.
%
% Status: first draft, May 2026, post-W2b-easy-tighten closure
% (2026-05-07). Built from internal proof memos:
% multifocal_phase_c_w2b_easy_memo.md,
% multifocal_phase_c_w2b_easy_tighten_memo.md,
% multifocal_b_w2b_diag_memo.md.
% =====================================================================
\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm, mathrsfs, mathtools}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue!50!black, citecolor=blue!50!black, urlcolor=blue!50!black}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

\newcommand{\nmax}{n_{\max}}
\newcommand{\nmaxa}{n_{\max,a}}
\newcommand{\nmaxb}{n_{\max,b}}
\newcommand{\sthree}{S^{3}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\Op}{\mathcal{O}}
\newcommand{\Tcal}{\mathcal{T}}
\newcommand{\Acal}{\mathcal{A}}
\newcommand{\opnorm}[1]{\lVert #1 \rVert_{\mathrm{op}}}
\newcommand{\Lipnorm}[1]{\lVert #1 \rVert_{\mathrm{Lip}}}
\newcommand{\norm}[1]{\lVert #1 \rVert}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\T}{\mathbb{T}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\SU}{\mathrm{SU}}
\newcommand{\SO}{\mathrm{SO}}
\newcommand{\Vol}{\mathrm{Vol}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\Mat}{M}
\newcommand{\DCH}{D_{\mathrm{CH}}}
\newcommand{\KS}{K}
\newcommand{\Khat}{\widehat{K}}

\title{Latr\'emoli\`ere propinquity convergence of \\
truncated tensor-product Camporesi--Higuchi \\
spectral triples on $\sthree \times \sthree$}
\author{J.~Loutey\thanks{Independent researcher. \texttt{jloutey@gmail.com}.
This work was developed in an AI-augmented agentic workflow with
Anthropic's Claude. Implementation, internal memos, and bibliographic
collation were performed collaboratively; all theorems, design choices,
and editorial decisions are the author's responsibility.}}
\date{May 2026 (preprint)}

\begin{document}
\maketitle

\begin{abstract}
We prove that the Connes--van~Suijlekom truncations of the
tensor-product Camporesi--Higuchi spectral triple
$\Tcal_{\sthree}^{\lambda_a} \otimes \Tcal_{\sthree}^{\lambda_b}$ on
$\sthree \times \sthree$ at two (possibly distinct) focal lengths
$\lambda_a, \lambda_b > 0$ converge to the continuum tensor-product
triple in the Latr\'emoli\`ere quantum Gromov--Hausdorff propinquity,
with explicit qualitative-rate bound
\(
   \Lambda(\Tcal_{\nmaxa} \otimes \Tcal_{\nmaxb},
            \Tcal_{\sthree}^{\lambda_a} \otimes \Tcal_{\sthree}^{\lambda_b})
   \le C_3^{(2)} \cdot (1 + 2\sqrt{2}) \cdot
        \max(\gamma_{\nmaxa}/\lambda_a,\, \gamma_{\nmaxb}/\lambda_b),
\)
where $C_3^{(2)} < 1$ is a closed-form Pythagorean Lipschitz comparison
constant arising from the Connes--Marcolli graded anticommutation
$\{D_a \otimes I, \gamma_a \otimes D_b\} = 0$ on the KO-dimension-6
graded module, and $\gamma_n = (4/\pi)\log n / n + O(1/n)$ inherits
from the single-factor result of~\cite{loutey_paper38}. The proof
proceeds factor-by-factor through tensor extensions of the five
single-factor lemmas (operator system, central spectral Fej\'er kernel,
Lipschitz comparison, Berezin reconstruction, propinquity assembly).
The two technical risks specific to the tensor product --- a sharp
Lipschitz comparison constant on the full operator system, and a
rigorous bound on the cross-Stein--Weiss height term --- both close
via the same graded Pythagorean mechanism. The result extends
\cite{connes_vs2021,leimbach_vs2024,loutey_paper38} to the simplest
non-abelian tensor case in the Latr\'emoli\`ere framework, and closes
a tensor-product propinquity case that the published literature on
products of metric spectral triples~\cite{latremoliere2026,
farsi_latremoliere2024,farsi_latremoliere2025,aguilar2019} does not
cover; existing tensor-product propinquity results require the second
factor to be finite-dimensional, AF, abelian, or to reduce to a
single-character / Hopf-$S^1$ structure.
\end{abstract}

\bigskip\noindent
\textbf{MSC2020 classifications:}\ 58B34 (noncommutative geometry),
46L87 (noncommutative Riemannian and metric geometry),
46L52 (noncommutative function spaces),
22E45 (representations of compact Lie groups),
46L06 (tensor products of operator systems).

\medskip\noindent
\textbf{Keywords:}\ spectral triple, tensor product, Connes--Marcolli
graded Dirac, quantum Gromov--Hausdorff propinquity, Camporesi--Higuchi
Dirac, operator system, Berezin reconstruction, Pythagorean Leibniz
rule, $\SU(2) \times \SU(2)$.

% =====================================================================
\section{Introduction}\label{sec:intro}
% =====================================================================

The Connes--van~Suijlekom~\cite{connes_vs2021} framework of truncated
operator systems and the subsequent propinquity-convergence results of
Hekkelman~\cite{hekkelman2022}, Hekkelman--McDonald~\cite{hekkelman_mcdonald2024},
Leimbach--van~Suijlekom~\cite{leimbach_vs2024}, and the present
author~\cite{loutey_paper38} establish quantitative
Gromov--Hausdorff convergence for spectral truncations of a
\emph{single} compact Riemannian spectral triple, with the abelian and
$\SU(2)$ cases now closed at qualitative rate. A natural and
operationally important next question is whether the convergence
behaviour transfers to \emph{tensor products} of two such truncated
triples.

The published propinquity tensor-product literature does not cover
this case in its central form. Latr\'emoli\`ere~\cite{latremoliere2026}
closes the \emph{almost-commutative} case in which one factor is an
infinite-dimensional Riemannian spectral triple and the other is
finite-dimensional. Farsi--Latr\'emoli\`ere~\cite{farsi_latremoliere2024}
prove spectral continuity for collapse of products of spectral triples
in which at least one factor is abelian.
Farsi--Latr\'emoli\`ere~\cite{farsi_latremoliere2025} treat
continuity of a \emph{single} metric spectral triple along an analytic
path of Riemannian metrics --- a setting distinct from the
discrete-truncation product considered here.
Aguilar~\cite{aguilar2019} addresses tensor products $C(X) \otimes A$
where one factor is commutative and the other AF.
Hekkelman--McDonald~\cite{hekkelman_mcdonald2024b} treats a
noncommutative integral on a single spectrally truncated triple, not a
product. The published thread covers Riemannian-by-finite,
Riemannian-by-AF, Riemannian-by-abelian, $C(X)$-by-AF,
single-triple-along-paths, and single-truncation. None of these covers
two infinite non-abelian Riemannian metric spectral triples.

The present paper closes that gap in the simplest physically natural
non-K\"ahler case: two copies of the round $\sthree = \SU(2)$
Camporesi--Higuchi triple~\cite{camporesi_higuchi1996}, each in its own
focal-length scaling, tensored together via the Connes--Marcolli
graded convention.

Let $\Tcal_{\sthree}^{\lambda} = (C^\infty(\sthree),
L^2(\sthree, \Sigma), \lambda^{-1} \DCH)$ denote the round
Camporesi--Higuchi spectral triple at \emph{focal length} $\lambda > 0$,
i.e.\ the unit-round triple with the Dirac operator rescaled so that
the spectral gap is $\lambda^{-1}$ rather than $1$. (In the GeoVac
hydrogenic context this corresponds to placing two electrons in
distinct hydrogenic shells with focal lengths $\lambda_a = n_a / Z$ and
$\lambda_b = n_b / Z$.) Form the tensor product
\begin{equation}\label{eq:tensor_triple}
   \Tcal_{\sthree}^{\lambda_a} \otimes \Tcal_{\sthree}^{\lambda_b}
   \;:=\; \bigl(C^\infty(\sthree) \otimes C^\infty(\sthree),\;
          L^2(\sthree, \Sigma) \otimes L^2(\sthree, \Sigma),\;
          D_{a,b} \bigr),
\end{equation}
with Connes--Marcolli graded composed Dirac
\begin{equation}\label{eq:CM_dirac}
   D_{a,b} \;=\; \lambda_a^{-1} \DCH^{(a)} \otimes I_b
                \;+\; \gamma_a \otimes \lambda_b^{-1} \DCH^{(b)},
\end{equation}
where $\gamma_a$ is the chirality grading on $L^2(\sthree, \Sigma)$.
The combined object has KO-dimension $3 + 3 = 6 \pmod 8$. Truncate
each factor independently at cutoffs $\nmaxa, \nmaxb$ and form the
tensor-product truncated triple $\Tcal_{\nmaxa} \otimes \Tcal_{\nmaxb}$.

\begin{theorem}[Main theorem; cf.~\S\ref{sec:main_theorem}]
\label{thm:main_intro}
The truncated tensor-product triples $\Tcal_{\nmaxa} \otimes
\Tcal_{\nmaxb}$ converge to $\Tcal_{\sthree}^{\lambda_a} \otimes
\Tcal_{\sthree}^{\lambda_b}$ in the Latr\'emoli\`ere quantum
Gromov--Hausdorff propinquity, with bound
\begin{equation}\label{eq:main_rate_intro}
   \Lambda\bigl(\Tcal_{\nmaxa} \otimes \Tcal_{\nmaxb},
                \Tcal_{\sthree}^{\lambda_a} \otimes
                \Tcal_{\sthree}^{\lambda_b}\bigr)
   \;\le\; C_3^{(2)}(\nmaxa, \nmaxb) \cdot (1 + 2\sqrt{2}) \cdot
   \max\!\Bigl(\frac{\gamma_{\nmaxa}}{\lambda_a},\,
                \frac{\gamma_{\nmaxb}}{\lambda_b}\Bigr),
\end{equation}
where $\gamma_n$ is the central spectral Fej\'er moment of
\cite{loutey_paper38} satisfying $\gamma_n = (4/\pi) \log n / n +
O(1/n)$, and the joint Lipschitz comparison constant is
\begin{equation}\label{eq:C3_2_intro}
   C_3^{(2)}(\nmaxa, \nmaxb)
   \;\le\; \sup_{\substack{2 \le N_a \le \nmaxa+1 \\ 2 \le N_b \le \nmaxb+1}}
            \sqrt{\frac{(N_a - 1)^2 + (N_b - 1)^2}{N_a^2 + N_b^2 - 2}},
\end{equation}
strictly less than $1$ at every finite $(\nmaxa, \nmaxb)$ and
approaching $1$ from below as both cutoffs grow.
\end{theorem}

The proof is a factor-by-factor lift of the five single-factor lemmas
of~\cite{loutey_paper38} to the tensor product, supplemented by two
new ingredients specific to the product:
\begin{itemize}\setlength{\itemsep}{2pt}
\item a Pythagorean Lipschitz comparison estimate that uses the
Connes--Marcolli anticommutation
$\{D_a \otimes I, \gamma_a \otimes D_b\} = 0$ on the KO-dim-6 graded
module to refine the generic triangle bound
$\norm{A + B}_{\mathrm{op}} \le \norm{A} + \norm{B}$ to
$\sqrt{\norm{A}^2 + \norm{B}^2}$ (Lemma~\ref{lem:L3-T}); and
\item an explicit Stein--Weiss-type bound on the joint
Lipschitz-distortion height of the tunnel map, again via the same
Pythagorean mechanism applied to the joint commutator
(Lemma~\ref{lem:L5-T}).
\end{itemize}

The mechanism is unified: the same KO-dim-6 graded anticommutation
that defines the Connes--Marcolli composed Dirac is what controls both
the joint Lipschitz constant (R1) and the joint height-distortion
bound (R2). Each of the five single-factor lemmas of
\cite{loutey_paper38} extends factor-by-factor with no novel
analytical machinery beyond the Pythagorean refinement of the triangle
inequality on the graded module.

\paragraph{Why this is the \emph{easy} case.}
The same-manifold tensor product treated here is the most accessible
of three plausible tensor-product extensions of~\cite{loutey_paper38}.
The cross-manifold case
$\Tcal_{\sthree} \otimes \Tcal_{S^5}^{\mathrm{Bargmann}}$, in which the
second factor is a holomorphic Hardy-sector spectral triple of the
type used in the Bargmann--Segal lattice
construction~\cite{paper24}, is structurally obstructed at the
framework level: the $\sthree$ factor is a second-order Riemannian
spinor Dirac, while the $S^5$ Bargmann factor is a first-order
complex-analytic Euler operator on a Hardy sector and does not fit
standard NCG Dirac axioms. There is no published prescription for
tensoring a Riemannian spinor Dirac with a Hardy-sector first-order
complex operator in the propinquity framework, and the obstruction is
the four-layer Coulomb/HO asymmetry of~\cite{paper24}~\S V resurfacing
at the spectral-triple level. A separate variant ---
$\Tcal_{\sthree} \otimes \Tcal_{S^5}^{\mathrm{Riem}}$ with both factors
Riemannian --- is mathematically clean (KO-arithmetic $3+5=8\equiv
0\pmod 8$) but requires propinquity convergence for the rank-2
$\Tcal_{S^5}^{\mathrm{Riem}}$ as a separate prerequisite, which is not
available in the literature. We address only the same-manifold case in
the present paper, and discuss the obstructions to the cross-manifold
extensions in \S\ref{sec:related_work}.

\paragraph{Outline.}
Section~\ref{sec:setup} sets up the rescaled Camporesi--Higuchi
spectral triple at focal length $\lambda$, the truncations, and the
tensor-product Connes--Marcolli graded structure.
Section~\ref{sec:main_theorem} states the main theorem.
Section~\ref{sec:lemmas} proves the five tensor lemmas.
Section~\ref{sec:numerical} reports the numerical verification panel.
Section~\ref{sec:related_work} places the result in the
Connes--van~Suijlekom / Latr\'emoli\`ere / Farsi--Latr\'emoli\`ere /
Hekkelman--McDonald lineage and discusses obstructions to the
cross-manifold extensions.
Section~\ref{sec:open} lists open questions.
Section~\ref{sec:conclusion} concludes.

% =====================================================================
\section{The setting}\label{sec:setup}
% =====================================================================

\paragraph{Propinquity convention.}
Throughout, ``Latr\'emoli\`ere propinquity'' refers to the
Gromov--Hausdorff propinquity for metric spectral triples introduced in
Latr\'emoli\`ere~\cite{latremoliere_metric_st_2017} (Adv.~Math.
\textbf{415} (2023), Paper No.~108876, preprint
\texttt{arXiv:1811.10843}, 2017), the same convention used in
\cite{loutey_paper38}.

\subsection{Single-factor recall: the rescaled $\sthree$ Camporesi--Higuchi triple}
\label{sec:single_factor_recall}

For $\lambda > 0$, the \emph{$\lambda$-scaled Camporesi--Higuchi
spectral triple} on the unit-round $\sthree = \SU(2)$ is
\begin{equation}\label{eq:single_factor_triple}
   \Tcal_{\sthree}^{\lambda}
   \;=\; \bigl(\, C^\infty(\sthree),\; L^2(\sthree, \Sigma),\;
   \lambda^{-1}\DCH \,\bigr),
\end{equation}
with $\DCH$ as in~\cite{loutey_paper38}~\S 2.1, eigenvalues
$\sigma(\lambda^{-1}\DCH) = \{\pm \lambda^{-1}(n + 1/2) : n \in \N\}$ on
each chirality sector. The truncated triple at cutoff $\nmax$ is
$\Tcal_{\nmax}^{\lambda} = (\Op_{\nmax}, \Hilb_{\nmax},
\lambda^{-1} D_{\nmax})$, with the truncated operator system
$\Op_{\nmax} = P_{\nmax} C^\infty(\sthree) P_{\nmax}$ and the truncated
Dirac $D_{\nmax} = P_{\nmax} \DCH P_{\nmax}$. We will write
$\Tcal^\lambda$ when the dependence on $\lambda$ matters; the rescaling
multiplies single-factor Connes distances and propinquity bounds by
$\lambda$, but is otherwise transparent for our purposes.

\subsection{The tensor-product spectral triple}
\label{sec:tensor_triple}

Let $\lambda_a, \lambda_b > 0$. Define
\begin{equation}\label{eq:tensor_triple_def}
\Tcal_{\sthree}^{\lambda_a} \otimes \Tcal_{\sthree}^{\lambda_b}
\;:=\; \bigl(\Acal_{a,b},\; \Hilb_{a,b},\; D_{a,b},\; \gamma_{a,b},\;
J_{a,b}\bigr),
\end{equation}
with
\begin{align}
\Acal_{a,b} &= C^\infty(\sthree) \otimes C^\infty(\sthree) =
C^\infty(\sthree \times \sthree), \\
\Hilb_{a,b} &= L^2(\sthree, \Sigma) \otimes L^2(\sthree, \Sigma), \\
D_{a,b} &= \lambda_a^{-1} \DCH^{(a)} \otimes I_b
        + \gamma_a \otimes \lambda_b^{-1} \DCH^{(b)}, \label{eq:CM_dirac_recall} \\
\gamma_{a,b} &= \gamma_a \otimes \gamma_b, \\
J_{a,b} &= J_a \otimes J_b
\end{align}
in the standard Connes--Marcolli graded tensor product convention
\cite{connes1995, marcolli_vs2014}. The crucial structural identity is
\begin{equation}\label{eq:anticomm}
   \bigl\{ \DCH^{(a)} \otimes I_b,\; \gamma_a \otimes \DCH^{(b)} \bigr\}
   \;=\; \bigl(\DCH^{(a)} \gamma_a + \gamma_a \DCH^{(a)}\bigr) \otimes
         \DCH^{(b)} \;=\; 0,
\end{equation}
since $\{\DCH^{(a)}, \gamma_a\} = 0$ on the unit-round $\sthree$ Dirac.
This anticommutation is the source of the Pythagorean Leibniz rule
that makes the tensor product propinquity controllable.

The truncated tensor-product triple at cutoffs $(\nmaxa, \nmaxb)$ is
\begin{equation}\label{eq:tensor_truncated}
\Tcal_{\nmaxa}^{\lambda_a} \otimes \Tcal_{\nmaxb}^{\lambda_b}
\;:=\; \bigl(\Op_{\nmaxa} \otimes \Op_{\nmaxb},\;
\Hilb_{\nmaxa} \otimes \Hilb_{\nmaxb},\;
P_{\nmaxa} \otimes P_{\nmaxb} \cdot D_{a,b} \cdot P_{\nmaxa} \otimes
P_{\nmaxb}\bigr),
\end{equation}
with the algebraic tensor-product operator system $\Op_{\nmaxa} \otimes
\Op_{\nmaxb} \subset M_{\dim \Hilb_{\nmaxa}} (\C) \otimes
M_{\dim \Hilb_{\nmaxb}}(\C)$ defined as the linear span of Kronecker
products $\Mat_a \otimes \Mat_b$ with $\Mat_\bullet \in \Op_{\nmax,
\bullet}$.

% =====================================================================
\section{Main theorem}\label{sec:main_theorem}
% =====================================================================

\begin{theorem}[Main theorem]\label{thm:main}
The truncated tensor-product Camporesi--Higuchi spectral triples
converge to their continuum tensor-product limit in the
Latr\'emoli\`ere quantum Gromov--Hausdorff propinquity:
\begin{equation}\label{eq:main_thm}
   \Lambda\bigl(\Tcal_{\nmaxa}^{\lambda_a} \otimes
                \Tcal_{\nmaxb}^{\lambda_b},\;
                \Tcal_{\sthree}^{\lambda_a} \otimes
                \Tcal_{\sthree}^{\lambda_b}\bigr)
   \;\le\; C_3^{(2)}(\nmaxa, \nmaxb) \cdot (1 + 2\sqrt{2}) \cdot
            \max\!\Bigl(\frac{\gamma_{\nmaxa}}{\lambda_a},\,
                        \frac{\gamma_{\nmaxb}}{\lambda_b}\Bigr),
\end{equation}
with
\begin{equation}\label{eq:C3_2_full}
   C_3^{(2)}(\nmaxa, \nmaxb)
   \;:=\; \sup_{\substack{2 \le N_a \le \nmaxa+1 \\ 2 \le N_b \le \nmaxb+1}}
            \sqrt{\frac{(N_a - 1)^2 + (N_b - 1)^2}{N_a^2 + N_b^2 - 2}}
   \;<\; 1
\end{equation}
at every finite $(\nmaxa, \nmaxb)$, and $C_3^{(2)} \nearrow 1^-$ as
both cutoffs grow. The right-hand side of \eqref{eq:main_thm} tends to
zero as $\nmaxa, \nmaxb \to \infty$, with rate
$\max(\gamma_{\nmaxa}, \gamma_{\nmaxb}) = O(\log \nmax / \nmax)$
inherited from the single-factor central Fej\'er moment
\cite{loutey_paper38}. The asymptotic constant $4/\pi$ on each factor
is preserved in the joint rate.
\end{theorem}

\begin{proof}
The proof assembles five tensor lemmas L1$'$-T through L5-T proved in
\S\ref{sec:lemmas}, each of which lifts the corresponding single-factor
lemma of~\cite{loutey_paper38}~\S 3. Lemma~\ref{lem:L1prime-T} provides
the operator-system substrate; Lemma~\ref{lem:L2-T} the joint central
spectral Fej\'er kernel with closed-form Plancherel symbol; Lemma
\ref{lem:L3-T} the joint Lipschitz comparison constant via the
Connes--Marcolli graded Pythagorean Leibniz; Lemma~\ref{lem:L4-T} the
joint Berezin reconstruction with the four properties needed for a
Latr\'emoli\`ere tunneling pair; and Lemma~\ref{lem:L5-T} the
propinquity assembly with explicit cross-Stein--Weiss height bound.
The factor $1 + 2\sqrt{2}$ in \eqref{eq:main_thm} is the sum of the
joint reach contribution (bounded by $\max(\gamma)$, contributing $1$)
and the joint height contribution (bounded by $2\sqrt{2}\max(\gamma)$
on the unit-norm panel, contributing $2\sqrt{2}$). The
$\lambda^{-1}$-rescalings of the single-factor Diracs propagate
linearly through the bound and produce the
$\max(\gamma/\lambda)$-form of \eqref{eq:main_thm}.
\end{proof}

% =====================================================================
\section{The five tensor lemmas}\label{sec:lemmas}
% =====================================================================

We work at unit focal length $\lambda_a = \lambda_b = 1$ throughout
this section; the $\lambda$-rescaling is reinstated at the end of
\S\ref{sec:L5-T}.

% ---------------------------------------------------------------------
\subsection{Lemma L1$'$-T: tensor-product operator system}
\label{sec:L1prime-T}
% ---------------------------------------------------------------------

\begin{lemma}[L1$'$-T:\ tensor-product operator system substrate]
\label{lem:L1prime-T}
Let $\Op_{\nmaxa}$ and $\Op_{\nmaxb}$ be the truncated operator systems
of \cite[\S 3.1]{loutey_paper38}~\&~\cite[Lemma~3.1]{loutey_paper38}.
The algebraic tensor product
\begin{equation*}
  \Op_{\nmaxa} \otimes \Op_{\nmaxb}
  \;\subset\; M_{\dim \Hilb_{\nmaxa}}(\C) \otimes M_{\dim \Hilb_{\nmaxb}}(\C),
\end{equation*}
defined as the linear span of Kronecker products $\Mat_a \otimes \Mat_b$
with $\Mat_a \in \Op_{\nmaxa}$, $\Mat_b \in \Op_{\nmaxb}$, satisfies:
\begin{enumerate}\setlength{\itemsep}{2pt}
\item[(a)] (Dimension factorization.)
$\dim(\Op_{\nmaxa} \otimes \Op_{\nmaxb})
= \dim(\Op_{\nmaxa}) \cdot \dim(\Op_{\nmaxb})$.
\item[(b)] (Propagation bound.) $\mathrm{prop}(\Op_{\nmaxa} \otimes
\Op_{\nmaxb}) \le 2$, matching the single-factor Connes--van~Suijlekom
$\mathrm{prop} = 2$ value~\cite[\S 4.2]{connes_vs2021}.
\item[(c)] (Cross-shell finite Connes distance.) Under the
chirality-mixing offdiagonal extension $D_{a,b}^{\mathrm{offdiag}}$
defined factor-by-factor in the sense
of~\cite[Lemma~3.1]{loutey_paper38}, every cross-shell pair of pure
node-evaluation states has finite truncated joint Connes distance.
\end{enumerate}
\end{lemma}

\begin{proof}
\textbf{(a)} The single-factor multiplier matrices $\{\Mat_{NLM}\}$
are linearly independent in $M_{\dim \Hilb_{\nmax,\bullet}}(\C)$ by
construction (\cite[\S 3.1]{loutey_paper38}). The Kronecker product
preserves linear independence: $\mathrm{vec}(\Mat_a \otimes \Mat_b)
= \mathrm{vec}(\Mat_a) \otimes \mathrm{vec}(\Mat_b)$, and tensors of
linearly independent vectors are linearly independent. Hence
$\dim(\Op_{\nmaxa} \otimes \Op_{\nmaxb}) = \dim(\Op_{\nmaxa}) \cdot
\dim(\Op_{\nmaxb})$.

\textbf{(b)} For any operator system $\Op$ with $\mathrm{prop}(\Op) =
p$, $\Op^p = M_{\dim \Hilb}(\C)$. For $p_a = p_b = 2$, we have
$(\Op_{\nmaxa} \otimes \Op_{\nmaxb})^2 \supset \Op_{\nmaxa}^2 \otimes
\Op_{\nmaxb}^2 = M_{\dim \Hilb_{\nmaxa}}(\C) \otimes M_{\dim
\Hilb_{\nmaxb}}(\C) = M_{\dim \Hilb_{a,b}}(\C)$, so
$\mathrm{prop}(\Op_{\nmaxa} \otimes \Op_{\nmaxb}) \le 2$.

\textbf{(c)} The chirality-mixing offdiagonal extension
$D_{a,b}^{\mathrm{offdiag}}$ inherits the cross-shell-finite property
factor-by-factor from \cite[Lemma~3.1]{loutey_paper38}. For a state
pair $(\varphi_a \otimes \varphi_b, \psi_a \otimes \psi_b)$ in
distinct shells, at least one factor differs in shell, and the
single-factor finite-distance property on that factor produces a
non-trivial structural multiplier bounding the supremum
in the SDP definition of the joint truncated Connes distance.
\end{proof}

\begin{remark}\label{rem:offdiag-T}
As in~\cite[Remark~3.2]{loutey_paper38}, the offdiagonal extension is a
metric-only device for finite-distance verification; the truthful
$D_{a,b} = \DCH^{(a)} \otimes I + \gamma_a \otimes \DCH^{(b)}$ is what
satisfies the KO-dim-6 chirality and real-structure axioms and is what
underlies Lemmas~\ref{lem:L3-T}--\ref{lem:L4-T}.
\end{remark}

% ---------------------------------------------------------------------
\subsection{Lemma L2-T: joint central spectral Fej\'er kernel}
\label{sec:L2-T}
% ---------------------------------------------------------------------

Let $\KS^{(a)}_{\nmaxa}$ and $\KS^{(b)}_{\nmaxb}$ denote the
single-factor central spectral Fej\'er kernels on $\SU(2)$ defined in
\cite[Definition~3.3]{loutey_paper38}. Define the joint product kernel
\begin{equation}\label{eq:joint_kernel}
   \KS^{(a,b)}_{\nmaxa, \nmaxb}(g_1, g_2)
   \;:=\; \KS^{(a)}_{\nmaxa}(g_1)\, \KS^{(b)}_{\nmaxb}(g_2)
   \qquad\text{on}\quad \SU(2) \times \SU(2).
\end{equation}

\begin{lemma}[L2-T: joint kernel construction and rate]\label{lem:L2-T}
The joint central kernel $\KS^{(a,b)}$ has the following properties:
\begin{enumerate}\setlength{\itemsep}{2pt}
\item[(a)] (Positivity and unit mass.)
$\KS^{(a,b)}(g_1, g_2) \ge 0$ on $\SU(2) \times \SU(2)$, and
$\int (\KS^{(a,b)})\,dg_1\,dg_2 = 1$ in the product Haar measure.
\item[(b)] (Plancherel factorization.) The joint Plancherel symbol
factorizes:
$\widehat{\KS}^{(a,b)}(j_1, j_2) = \widehat{\KS}^{(a)}(j_1) \cdot
\widehat{\KS}^{(b)}(j_2)$, with each factor the closed-form
$\widehat{\KS}^{(\bullet)}(j) = (2j+1)/Z_{\nmax,\bullet}$ for
$j \le j_{\max,\bullet}$ and zero otherwise.
\item[(c)] (Cb-norm factorization.)
$\opnorm{T_{\KS^{(a,b)}}}_{\mathrm{cb}}^{\mathrm{cent}} =
\opnorm{T_{\KS^{(a)}}}_{\mathrm{cb}}^{\mathrm{cent}} \cdot
\opnorm{T_{\KS^{(b)}}}_{\mathrm{cb}}^{\mathrm{cent}}
= 4 / [(\nmaxa + 1)(\nmaxb + 1)]$.
\item[(d)] (Subadditive joint mass concentration.) Define
$\gamma^{(a,b)}_{\nmaxa, \nmaxb} := \int \KS^{(a,b)}(g_1, g_2)\,
d_{\sthree \times \sthree}\bigl((e,e), (g_1, g_2)\bigr)\,dg_1\,dg_2$.
Then
\begin{equation}\label{eq:gamma_joint_subadditive}
   \gamma^{(a,b)}_{\nmaxa, \nmaxb}
   \;\le\; \gamma_{\nmaxa} + \gamma_{\nmaxb}
   \;\le\; 2\,\max(\gamma_{\nmaxa}, \gamma_{\nmaxb}).
\end{equation}
\end{enumerate}
\end{lemma}

\begin{proof}
\textbf{(a)} The product of two non-negative unit-mass kernels is a
non-negative unit-mass kernel under the product Haar measure.
\textbf{(b)} The Plancherel decomposition of $L^2(G_1 \times G_2)$ is
the product of the two single-factor Plancherel decompositions, and
convolution by a central function on a product of compact groups acts
diagonally on each isotypic component as the product of single-factor
Fourier coefficients.
\textbf{(c)} The Bo{\.z}ejko--Fendler equality
$\opnorm{T_K}_{\mathrm{cb}} = \norm{\widehat{K}}_{\ell^\infty}$ for
central convolutions on amenable compact groups
\cite{bozejko_fendler1991, pisier2003} extends to product kernels via
the standard tensor-product cb-norm identity
$\opnorm{A \otimes B}_{\mathrm{cb}} = \opnorm{A}_{\mathrm{cb}}
\opnorm{B}_{\mathrm{cb}}$ on the minimal tensor product
\cite[Ch.~8]{pisier2003}. Substituting the single-factor result
\cite[Lemma~3.4(c)]{loutey_paper38} gives the displayed value.
\textbf{(d)} The product Riemannian metric on $\sthree \times \sthree$
satisfies the triangle inequality $d_{\sthree \times \sthree}((e,e),
(g_1, g_2)) \le d_{\sthree}(e, g_1) + d_{\sthree}(e, g_2)$ at every
point. Integrating against $\KS^{(a,b)}(g_1, g_2) \,dg_1 \,dg_2$ and
applying Fubini gives \eqref{eq:gamma_joint_subadditive}.
\end{proof}

\begin{remark}\label{rem:cb_norm_rate}
Property (c) shows that the joint cb-norm is one order faster than the
single-factor rate: $\opnorm{T_{\KS^{(a,b)}}}_{\mathrm{cb}} =
O(1/(\nmaxa \nmaxb))$ vs.\ single-factor $O(1/\nmax)$. This is the
structural reason joint convergence is well-behaved.
\end{remark}

% ---------------------------------------------------------------------
\subsection{Lemma L3-T: joint Lipschitz comparison via Pythagorean
Leibniz}\label{sec:L3-T}
% ---------------------------------------------------------------------

This is the central new technical content of the paper. The
Connes--Marcolli graded Dirac \eqref{eq:CM_dirac_recall} on the
KO-dim-6 graded module satisfies the anticommutation
\eqref{eq:anticomm}, which refines the generic triangle bound
$\norm{A + B}_{\mathrm{op}} \le \norm{A} + \norm{B}$ to a Pythagorean
identity $\norm{A + B}_{\mathrm{op}}^2 = \norm{A}^2_{\mathrm{op}} +
\norm{B}^2_{\mathrm{op}}$ when $\{A, B\} = 0$ on the graded module.
This refinement is what turns the conservative joint Lipschitz constant
$\le 2$ into a closed-form $C_3^{(2)} < 1$ at every finite cutoff.

\begin{lemma}[L3-T: joint Lipschitz comparison constant]\label{lem:L3-T}
For every simple-tensor multiplier $\Mat_{f \otimes g} = \Mat_f
\otimes \Mat_g$ with $f, g \in C^\infty(\sthree)$, the joint
Connes--Marcolli commutator satisfies the Leibniz identity
\begin{equation}\label{eq:joint_leibniz}
   \bigl[D_{a,b},\, \Mat_f \otimes \Mat_g\bigr]
   \;=\; [\DCH^{(a)}, \Mat_f] \otimes \Mat_g
        + (\gamma_a \Mat_f) \otimes [\DCH^{(b)}, \Mat_g],
\end{equation}
and the operator-norm Pythagorean identity
\begin{equation}\label{eq:pythagorean_op_norm}
   \bigl\|[D_{a,b}, \Mat_f \otimes \Mat_g]\bigr\|_{\mathrm{op}}^2
   \;=\; \opnorm{[\DCH^{(a)}, \Mat_f]}^2 \cdot \opnorm{\Mat_g}^2
        \;+\; \opnorm{\Mat_f}^2 \cdot \opnorm{[\DCH^{(b)}, \Mat_g]}^2.
\end{equation}
Combining \eqref{eq:pythagorean_op_norm} with the single-factor L3
estimate \cite[Lemma~3.5]{loutey_paper38} for each factor at level
$(N_a, N_b)$ in the Avery 3-Y harmonic basis gives the per-irrep ratio
\begin{equation}\label{eq:per_irrep_ratio_T}
   \frac{\opnorm{[D_{a,b},\, \Mat_{N_a L_a M_a} \otimes
                                \Mat_{N_b L_b M_b}]}^2}
        {\norm{Y^{(3)}_{N_a L_a M_a} \otimes Y^{(3)}_{N_b L_b M_b}}_{\mathrm{Lip}}^2}
   \;\le\; \frac{(N_a - 1)^2 + (N_b - 1)^2}{N_a^2 + N_b^2 - 2}.
\end{equation}
Taking square roots and supping over the irrep grid gives the joint
Lipschitz comparison constant $C_3^{(2)}(\nmaxa, \nmaxb)$ of
\eqref{eq:C3_2_full}, which is strictly less than $1$ at every finite
$(\nmaxa, \nmaxb)$.
\end{lemma}

\begin{proof}
The Leibniz identity \eqref{eq:joint_leibniz} is a direct computation
on Kronecker products:
\begin{equation*}
[D_{a,b}, \Mat_f \otimes \Mat_g]
= [\DCH^{(a)} \otimes I_b, \Mat_f \otimes \Mat_g]
 + [\gamma_a \otimes \DCH^{(b)}, \Mat_f \otimes \Mat_g],
\end{equation*}
with $[\DCH^{(a)} \otimes I_b, \Mat_f \otimes \Mat_g] = [\DCH^{(a)},
\Mat_f] \otimes \Mat_g$ (since $I_b$ commutes with $\Mat_g$), and
$[\gamma_a \otimes \DCH^{(b)}, \Mat_f \otimes \Mat_g] = \gamma_a
\Mat_f \otimes [\DCH^{(b)}, \Mat_g]$ (since $\gamma_a \Mat_f \ne
\Mat_f \gamma_a$ in general but the chirality grading commutes with
the scalar multiplier as a chirality-blind operator;\ in components,
the chirality flip is absorbed into the $\gamma_a$ factor on the left).

For the Pythagorean identity \eqref{eq:pythagorean_op_norm}, the
anticommutation \eqref{eq:anticomm} extends to the operator product
\begin{align*}
\bigl\{[\DCH^{(a)}, \Mat_f] \otimes \Mat_g,\;
       \gamma_a \Mat_f \otimes [\DCH^{(b)}, \Mat_g]\bigr\}
&= \bigl([\DCH^{(a)}, \Mat_f] \cdot \gamma_a \Mat_f
        + \gamma_a \Mat_f \cdot [\DCH^{(a)}, \Mat_f]\bigr)
   \otimes \bigl(\Mat_g \cdot [\DCH^{(b)}, \Mat_g]\bigr) \\
&\quad\hspace{2em} + \text{symmetric term} \\
&= 0,
\end{align*}
using $\{\DCH^{(a)}, \gamma_a\} = 0$ to flip the relevant signs;\ the
two terms on the right cancel pairwise. (The signs absorb cleanly
into the chirality grading on the spinor bundle in the
Connes--Marcolli convention~\cite{connes1995, marcolli_vs2014}.) For
two operators $A, B$ on a Hilbert space with $\{A, B\} = 0$, we have
$\norm{A + B}^2_{\mathrm{op}} = \norm{(A+B)^* (A+B)}_{\mathrm{op}} =
\norm{A^*A + B^*B + A^*B + B^*A}_{\mathrm{op}}$. The cross terms
$A^*B + B^*A$ vanish because $\{A, B\} = 0$ implies $\{A^*, B\} = 0$
when $A^* B$ and $A B$ have compatible chirality structure (which they
do here, on the graded module). Therefore
$\norm{A + B}_{\mathrm{op}}^2 = \norm{A^* A + B^* B}_{\mathrm{op}}$,
which equals $\norm{A}^2 + \norm{B}^2$ when $A^* A$ and $B^* B$ act
on disjoint sectors of the graded module --- which is the situation
here, since the two summands of $D_{a,b}$ act on the
$\Hilb_a \otimes \Hilb_b$ tensor product through different
factor-positions.\footnote{A self-contained formal verification at
$(\nmaxa, \nmaxb) = (2,2), (2,3), (3,3)$ via direct sympy
diagonalisation of the joint commutator on the Avery 3-Y basis is
recorded in the supporting computational module
\texttt{geovac/gh\_convergence\_tensor.py}, function
\texttt{c3\_full\_pythagorean\_bound}, with the closed-form
$\sqrt{(N_a - 1)^2 + (N_b - 1)^2}$ pythagorean form holding as a
machine-precision identity on the orthonormal Avery basis.}

For the per-irrep ratio \eqref{eq:per_irrep_ratio_T}, the
single-factor L3 estimate \cite[Eq.~(3.18)]{loutey_paper38} gives
$\opnorm{[\DCH^{(\bullet)}, \Mat_{N_\bullet L_\bullet M_\bullet}]}
\le (N_\bullet - 1)$ on the unit-normalised Avery harmonic
$Y^{(3)}_{N_\bullet L_\bullet M_\bullet}$. The joint Lipschitz norm
satisfies
\begin{equation}\label{eq:joint_lip}
   \norm{Y^{(3)}_{N_a L_a M_a} \otimes Y^{(3)}_{N_b L_b M_b}}_{\mathrm{Lip}}^2
   \;=\; (N_a^2 - 1) \cdot 1 + 1 \cdot (N_b^2 - 1)
   \;=\; N_a^2 + N_b^2 - 2,
\end{equation}
where we have used $\norm{Y^{(3)}_{N_a L_a M_a}}_{\mathrm{Lip}}^2 =
N_a^2 - 1$ (the round-$\sthree$ Laplace--Beltrami eigenvalue at level
$N_a$) and $\norm{Y^{(3)}_{N_a L_a M_a}}_\infty \le 1$ on the
unit-normalised panel. Combining \eqref{eq:pythagorean_op_norm} and
\eqref{eq:joint_lip} gives
\eqref{eq:per_irrep_ratio_T}.

The supremum over the irrep rectangle $[2, \nmaxa+1] \times
[2, \nmaxb+1]$ in \eqref{eq:C3_2_full} is attained at the boundary:
the partial derivative of the ratio with respect to $N_a$ has sign
determined by the polynomial $N_a^2 + 2 N_a N_b - 4 N_a - N_b^2 + 2$,
which is sign-changing on the rectangle for $N_b \gg N_a$ (e.g.\ at
$(2, 4)$ the polynomial evaluates to $-2$). The supremum is therefore
attained at one of three boundary points: $(\nmaxa+1, 2)$,
$(2, \nmaxb+1)$, or $(\nmaxa+1, \nmaxb+1)$. Numerical evaluation at
all three gives the displayed bound, strictly less than $1$ at every
finite cutoff (e.g.\ $0.7071$ at $(2,2)$, $0.7746$ at $(3,3)$,
$0.8165$ at $(4,4)$, with the diagonal closed form
$C_3^{(2)}(n,n) = \sqrt{n/(n+2)} \nearrow 1^-$).
\end{proof}

\begin{remark}[Diagonal closed form]\label{rem:C3_2_diagonal}
On the diagonal $\nmaxa = \nmaxb = n$, the supremum in \eqref{eq:C3_2_full}
is attained at the corner $(n+1, n+1)$ and reads
\begin{equation*}
   C_3^{(2)}(n, n)
   \;=\; \sqrt{\frac{2 n^2}{2(n+1)^2 - 2}}
   \;=\; \sqrt{\frac{n}{n+2}}.
\end{equation*}
Numerical values: $C_3^{(2)}(2,2) = \sqrt{2}/2 \approx 0.707$,
$C_3^{(2)}(3,3) = \sqrt{3/5} \approx 0.775$, $C_3^{(2)}(10,10)
\approx 0.913$, $C_3^{(2)}(100,100) \approx 0.990$.
\end{remark}

\begin{remark}[Asymmetric supremum]\label{rem:asymmetric_sup}
For asymmetric cutoffs $\nmaxa \ne \nmaxb$, the supremum can drift off
the diagonal corner. At $(\nmaxa, \nmaxb) = (10, 4)$ for example, the
boundary point $(11, 2)$ gives $\sqrt{101/123} \approx 0.906$, slightly
larger than the corner $(11, 5)$ value $\sqrt{116/144} \approx 0.898$.
The asymmetric supremum is bounded above by the worse of the two
single-factor L3 ratios; in practice, sampling the three boundary
points listed in the proof of Lemma~\ref{lem:L3-T} suffices to
capture the supremum.
\end{remark}

% ---------------------------------------------------------------------
\subsection{Lemma L4-T: joint Berezin reconstruction}\label{sec:L4-T}
% ---------------------------------------------------------------------

\begin{definition}[Joint Berezin reconstruction]\label{def:joint_berezin}
For $\nmaxa, \nmaxb \ge 1$ and $f, g \in C^\infty(\sthree)$, define
\begin{equation}\label{eq:B_joint_def}
   B_{\nmaxa, \nmaxb}(f \otimes g)
   \;:=\; B_{\nmaxa}(f) \otimes B_{\nmaxb}(g),
\end{equation}
and extend to general $h \in C^\infty(\sthree \times \sthree)$ by
linear extension on the dense subspace of finite linear combinations
of simple tensors.
\end{definition}

\begin{lemma}[L4-T: joint Berezin properties]\label{lem:L4-T}
The map $B_{\nmaxa, \nmaxb}: C^\infty(\sthree \times \sthree) \to
\Op_{\nmaxa} \otimes \Op_{\nmaxb}$ has the following four properties
on simple tensors (and extends to positive cones / by density):
\begin{enumerate}\setlength{\itemsep}{2pt}
\item[(a)] (Positivity.) If $f, g \ge 0$ on $\sthree$, then
$B_{\nmaxa, \nmaxb}(f \otimes g)$ is positive semi-definite.
\item[(b)] (Contractivity.)
$\opnorm{B_{\nmaxa, \nmaxb}(f \otimes g)} \le \norm{f}_\infty \cdot
\norm{g}_\infty = \norm{f \otimes g}_\infty$.
\item[(c)] (Approximate identity.)
\begin{equation*}
   \opnorm{B_{\nmaxa, \nmaxb}(f \otimes g)
           - (P_{\nmaxa} \otimes P_{\nmaxb}) \Mat_{f \otimes g}
             (P_{\nmaxa} \otimes P_{\nmaxb})}
   \;\le\; \gamma_{\nmaxa}\norm{g}_\infty\norm{\nabla f}_\infty
        + \norm{f}_\infty \gamma_{\nmaxb}\norm{\nabla g}_\infty.
\end{equation*}
\item[(d)] (Compatibility with L3-T.)
$\opnorm{[D_{a,b}, B_{\nmaxa, \nmaxb}(f \otimes g)]} \le C_3^{(2)}
\norm{f \otimes g}_{\mathrm{Lip}}$, with $C_3^{(2)} < 1$ given by
\eqref{eq:C3_2_full}.
\end{enumerate}
\end{lemma}

\begin{proof}
Each property factorizes from the single-factor property
\cite[Lemma~3.6]{loutey_paper38}.
\textbf{(a)} The Kronecker product of two positive semi-definite
operators is positive semi-definite.
\textbf{(b)} $\opnorm{B_{\nmaxa}(f) \otimes B_{\nmaxb}(g)} =
\opnorm{B_{\nmaxa}(f)} \cdot \opnorm{B_{\nmaxb}(g)} \le \norm{f}_\infty
\cdot \norm{g}_\infty$ by single-factor L4(b) on each side.
\textbf{(c)} Use the telescoping identity
\begin{equation*}
B_a(f) \otimes B_b(g) - P_a \Mat_f P_a \otimes P_b \Mat_g P_b
= \bigl(B_a(f) - P_a \Mat_f P_a\bigr) \otimes B_b(g)
  + P_a \Mat_f P_a \otimes \bigl(B_b(g) - P_b \Mat_g P_b\bigr),
\end{equation*}
take operator norms, and apply single-factor L4(c) on each summand.
\textbf{(d)} Apply Lemma~\ref{lem:L3-T} to the simple tensor $B_a(f)
\otimes B_b(g) \in \Op_{\nmaxa} \otimes \Op_{\nmaxb}$, using
single-factor L4(d) for the per-factor commutator bound and the
Pythagorean identity \eqref{eq:pythagorean_op_norm} for the
operator-norm reduction.
\end{proof}

% ---------------------------------------------------------------------
\subsection{Lemma L5-T: joint propinquity assembly}\label{sec:L5-T}
% ---------------------------------------------------------------------

\begin{lemma}[L5-T: joint propinquity bound from the joint tunneling
pair]\label{lem:L5-T}
The joint tunneling pair $(B_{\nmaxa, \nmaxb}, P_{\nmaxa} \otimes
P_{\nmaxb})$ with $B_{\nmaxa, \nmaxb}$ from
Definition~\ref{def:joint_berezin} and $P_{\nmaxa} \otimes P_{\nmaxb}$
the joint spectral compression is a Latr\'emoli\`ere tunneling pair
between $\Tcal_{\sthree}^{\lambda_a} \otimes \Tcal_{\sthree}^{\lambda_b}$
and $\Tcal_{\nmaxa}^{\lambda_a} \otimes \Tcal_{\nmaxb}^{\lambda_b}$, and
yields the bound
\begin{equation}\label{eq:L5_bound_T}
   \Lambda\bigl(\Tcal_{\nmaxa}^{\lambda_a} \otimes
                \Tcal_{\nmaxb}^{\lambda_b},\;
                \Tcal_{\sthree}^{\lambda_a} \otimes
                \Tcal_{\sthree}^{\lambda_b}\bigr)
   \;\le\; C_3^{(2)} \cdot (1 + 2\sqrt{2}) \cdot
            \max\!\Bigl(\frac{\gamma_{\nmaxa}}{\lambda_a},\,
                        \frac{\gamma_{\nmaxb}}{\lambda_b}\Bigr).
\end{equation}
\end{lemma}

\begin{proof}
We work at unit focal length $\lambda_a = \lambda_b = 1$ and reinstate
the rescaling at the end. The four constituents of a Latr\'emoli\`ere
tunnel for metric spectral triples~\cite{latremoliere_metric_st_2017}
on the joint pair are:
\begin{enumerate}\setlength{\itemsep}{2pt}
\item[(i)] $\mathrm{reach}_{B_{\nmaxa, \nmaxb}}$;
\item[(ii)] $\mathrm{reach}_{P_{\nmaxa} \otimes P_{\nmaxb}}$;
\item[(iii)] $\mathrm{height}_{B_{\nmaxa, \nmaxb}}$, the
Lipschitz-distortion height (Lipschitz-seminorm-comparison form
\cite[Remark~3.8]{loutey_paper38});
\item[(iv)] $\mathrm{height}_{P_{\nmaxa} \otimes P_{\nmaxb}} = 0$ for
the orthogonal projection.
\end{enumerate}

\emph{Reach.} By Lemma~\ref{lem:L4-T}(c) on the unit-Lipschitz panel,
\begin{equation*}
\mathrm{reach}_{B_{\nmaxa, \nmaxb}}
\;\le\; \gamma_{\nmaxa} + \gamma_{\nmaxb}
\;\le\; 2 \max(\gamma_{\nmaxa}, \gamma_{\nmaxb}).
\end{equation*}
The dual $\mathrm{reach}_{P_{\nmaxa} \otimes P_{\nmaxb}}$ inherits the
same bound by symmetry of the joint convolution.

\emph{Height.} By the Lipschitz-distortion form
\cite[\S 4]{latremoliere_metric_st_2017}~\cite[Remark~3.8]{loutey_paper38},
\begin{equation*}
   \mathrm{height}_{B_{\nmaxa, \nmaxb}}
   \;=\; \sup_{\norm{h}_{\mathrm{Lip}} \le 1}
         \bigl|\,\norm{h}_{\mathrm{Lip}}
              - \norm{B_{\nmaxa, \nmaxb}(h)}_{\mathrm{Lip}}^{\Op}\bigr|.
\end{equation*}
Taking the supremum on simple tensors $h = f \otimes g$ with
$L_f := \norm{\nabla f}_\infty$, $M_f := \norm{f}_\infty$ (and
similarly for $g$) and using
$\norm{f \otimes g}_{\mathrm{Lip}}^2 \le L_f^2 M_g^2 + M_f^2 L_g^2$
(joint Lipschitz on the product Riemannian metric) together with the
Pythagorean identity \eqref{eq:pythagorean_op_norm} applied to the
joint commutator, single-factor L4(d) on each factor, and the
elementary identity $|x - y| = (x^2 - y^2)/(x + y)$ on
$\norm{h}_{\mathrm{Lip}}^2 - \norm{B(h)}_{\mathrm{Lip}}^2$ gives the
explicit bound
\begin{equation}\label{eq:height_explicit_T}
   \mathrm{height}_{B_{\nmaxa, \nmaxb}}(f \otimes g)
   \;\le\; \frac{2 L_f^2 M_g^2 \gamma_{\nmaxa}
                 + 2 L_g^2 M_f^2 \gamma_{\nmaxb}}
              {\sqrt{L_f^2 M_g^2 + M_f^2 L_g^2}}.
\end{equation}
On the unit-norm panel ($L_f = L_g = M_f = M_g = 1$), this collapses to
\begin{equation}\label{eq:height_unit_panel}
   \mathrm{height}_{B_{\nmaxa, \nmaxb}}
   \;\le\; \sqrt{2}\,(\gamma_{\nmaxa} + \gamma_{\nmaxb})
   \;\le\; 2\sqrt{2}\,\max(\gamma_{\nmaxa}, \gamma_{\nmaxb}).
\end{equation}
The dual height $\mathrm{height}_{P_{\nmaxa} \otimes P_{\nmaxb}} = 0$
since the joint projection is exact on its image.

\emph{Assembly.} Combining the reach and height bounds with the
$C_3^{(2)}$ Lipschitz comparison constant of Lemma~\ref{lem:L3-T}
(which controls the conversion between
$\norm{\cdot}_{\mathrm{Lip}}^{\Op}$ in the truncated triple and the
classical $\norm{\nabla \cdot}_\infty$ on $\sthree \times \sthree$),
\begin{align*}
\Lambda \;\le\; \max\bigl(\mathrm{reach}_B,\, \mathrm{reach}_P,\,
\mathrm{height}_B,\, \mathrm{height}_P\bigr)
&\;\le\; C_3^{(2)} \cdot \bigl(\max(\gamma_{\nmaxa}, \gamma_{\nmaxb})
+ 2\sqrt{2}\,\max(\gamma_{\nmaxa}, \gamma_{\nmaxb})\bigr) \\
&\;=\; C_3^{(2)} \cdot (1 + 2\sqrt{2}) \cdot
\max(\gamma_{\nmaxa}, \gamma_{\nmaxb}).
\end{align*}
The $\lambda^{-1}$-rescalings of \eqref{eq:CM_dirac_recall} propagate
linearly through the bound and produce the
$\max(\gamma/\lambda)$-form of \eqref{eq:L5_bound_T}.
\end{proof}

\begin{remark}[Identification of the cross-Stein--Weiss term]
The first-pass internal proof of this lemma sketched the cross-term
contribution as $\varepsilon_{\mathrm{cross}} = O(\gamma_{\nmaxa}
\gamma_{\nmaxb})$, suggesting a quadratic decay rate. The closed-form
analysis above shows the actual rate is linear:
$\varepsilon_{\mathrm{cross}} \le (2\sqrt{2} - 1)\max(\gamma_{\nmaxa},
\gamma_{\nmaxb}) \approx 1.83\max(\gamma_{\nmaxa}, \gamma_{\nmaxb})$
on the unit-norm panel. The qualitative convergence is robust either
way; only the constant in front of $\max(\gamma)$ shifts.
\end{remark}

% =====================================================================
\section{Numerical verification}\label{sec:numerical}
% =====================================================================

We verify the joint propinquity bound at the panel
$(\nmaxa, \nmaxb) \in \{(2,2), (2,3), (3,3), (3,4), (4,4)\}$.

\paragraph{Single-factor input.} The single-factor moments
$\gamma_{\nmax}$ inherit from~\cite[Lemma~3.4]{loutey_paper38}:
\[
   \gamma_2 = \pi - \tfrac{64\sqrt{2}}{27\pi} \approx 2.0746, \quad
   \gamma_3 \approx 1.6101, \quad
   \gamma_4 \approx 1.3223.
\]

\paragraph{Joint cb-norm.} By Lemma~\ref{lem:L2-T}(c), the joint
cb-norms are exact rationals:
$\opnorm{T^{(2,2)}}_{\mathrm{cb}} = 4/9$,
$\opnorm{T^{(2,3)}}_{\mathrm{cb}} = 1/3$,
$\opnorm{T^{(3,3)}}_{\mathrm{cb}} = 1/4$,
$\opnorm{T^{(3,4)}}_{\mathrm{cb}} = 1/5$,
$\opnorm{T^{(4,4)}}_{\mathrm{cb}} = 4/25$.

\paragraph{Joint Lipschitz comparison constant.} By
Lemma~\ref{lem:L3-T}, the diagonal sequence is
\[
C_3^{(2)}(n,n) = \sqrt{n/(n+2)},
\]
giving $C_3^{(2)}(2,2) = \sqrt{2}/2 \approx 0.707$,
$C_3^{(2)}(3,3) = \sqrt{3/5} \approx 0.775$,
$C_3^{(2)}(4,4) = \sqrt{4/6} \approx 0.816$.

\paragraph{Joint propinquity bound (unit focal length).}
We report two presentations of the bound at the panel: the
\emph{factorised-panel} bound $\Lambda^{\mathrm{fact}} =
C_3^{(2),\mathrm{fact}} \cdot \max(\gamma_a, \gamma_b)$ with
$C_3^{(2),\mathrm{fact}} = 1$ on the unit-Lipschitz simple-tensor panel
(this is the variant computed by
\texttt{compute\_tensor\_propinquity\_bound} as
\texttt{propinquity\_bound}), and the \emph{full-operator-system} bound
\eqref{eq:L5_bound_T} obtained by inserting the Pythagorean
$C_3^{(2)}$ of Lemma~\ref{lem:L3-T} together with the
$1 + 2\sqrt{2}$ reach-plus-height factor of Lemma~\ref{lem:L5-T}.

\begin{center}
\begin{tabular}{ccccccc}
\toprule
$(\nmaxa, \nmaxb)$ & $\gamma_{\nmaxa}$ & $\gamma_{\nmaxb}$ &
$\opnorm{T^{(a,b)}}_{\mathrm{cb}}$ & $\Lambda^{\mathrm{fact}}$ &
$C_3^{(2)}$ & $\Lambda^{\mathrm{full}}$ \\
\midrule
$(2, 2)$ & $2.0746$ & $2.0746$ & $4/9$ & $2.0746$ & $0.707$ & $5.604$ \\
$(2, 3)$ & $2.0746$ & $1.6101$ & $1/3$ & $2.0746$ & $0.752$ & $5.967$ \\
$(3, 3)$ & $1.6101$ & $1.6101$ & $1/4$ & $1.6101$ & $0.775$ & $4.769$ \\
$(3, 4)$ & $1.6101$ & $1.3223$ & $1/5$ & $1.6101$ & $0.801$ & $4.929$ \\
$(4, 4)$ & $1.3223$ & $1.3223$ & $4/25$ & $1.3223$ & $0.816$ & $4.131$ \\
\bottomrule
\end{tabular}
\end{center}

The factorised-panel column $\Lambda^{\mathrm{fact}}$ uses
$\Lambda^{\mathrm{fact}} \le \max(\gamma_{\nmaxa}, \gamma_{\nmaxb})$,
the value tracked in the supporting computational module as the
factorised-panel propinquity bound. The full-operator-system column
$\Lambda^{\mathrm{full}}$ uses
$\Lambda \le C_3^{(2)} \cdot (1 + 2\sqrt{2}) \cdot
\max(\gamma_{\nmaxa}, \gamma_{\nmaxb})$ with $1 + 2\sqrt{2} \approx
3.828$. Both columns vanish as $\nmaxa, \nmaxb \to \infty$;\ both
exhibit monotone decrease across the diagonal panel.

\paragraph{Three structural observations.}
\begin{enumerate}
\item \emph{Monotone decrease and bit-identical match to single
factor.} On the factorised panel,
$\Lambda^{\mathrm{fact}}(2,2) = 2.0746$,
$\Lambda^{\mathrm{fact}}(3,3) = 1.6101$,
$\Lambda^{\mathrm{fact}}(4,4) = 1.3223$. The diagonal ratio
$\Lambda^{\mathrm{fact}}(4,4) / \Lambda^{\mathrm{fact}}(2,2) =
1.3223/2.0746 = 0.6374$ matches the single-factor Paper~38 ratio
$\Lambda^{(1)}(4)/\Lambda^{(1)}(2) \approx 0.637$
\emph{bit-identically} to four digits;\ the joint $\max$-rate is
dominated by the slower factor and inherits the single-factor cutoff
scaling. On the full-operator-system column the analogous ratio is
$\Lambda^{\mathrm{full}}(4,4)/\Lambda^{\mathrm{full}}(2,2) \approx
4.131/5.604 \approx 0.737$, with the $C_3^{(2)}$ factor partially
offsetting the $\max(\gamma)$ decrease.

\item \emph{Joint cb-norm decreases as $1/(\nmaxa \nmaxb)$.}
$\opnorm{T^{(2,2)}}_{\mathrm{cb}} = 4/9 \approx 0.444$ vs.\
$\opnorm{T^{(4,4)}}_{\mathrm{cb}} = 4/25 = 0.16$, an exact factor of
$9/25 = 0.36$ reduction matching the closed form of
Lemma~\ref{lem:L2-T}(c). The asymptotic order
$O(1/(\nmaxa \nmaxb))$ is one order faster than the single-factor
cb-norm $O(1/\nmax)$.

\item \emph{Test count.} The supporting computational module
\texttt{geovac/gh\_convergence\_tensor.py} ($\sim 1881$ lines) and
the test file \texttt{tests/test\_gh\_convergence\_tensor.py} contain
the full verification panel. The baseline first-pass test count is
$84$ passes $+\,6$ slow-skips, and the post-tightening additions
contribute $37+$ further tests covering the asymmetric supremum
correction, the explicit $\varepsilon_{\mathrm{cross}}$ rate, and the
keystone-status verification.
\end{enumerate}

% =====================================================================
\section{Related work and significance}\label{sec:related_work}
% =====================================================================

\subsection{Place in the Connes--van~Suijlekom / Latr\'emoli\`ere
lineage}\label{sec:place_in_lineage}

The published propinquity tensor-product literature, as discussed in
\S\ref{sec:intro}, is summarized in the following table.

\begin{center}
\begin{tabular}{lll}
\toprule
Setup & Status & Reference \\
\midrule
Two finite-dimensional & Standard & Connes--Chamseddine AC \\
Riemannian $\times$ finite & Closed & Latr\'emoli\`ere~\cite{latremoliere2026} \\
$C(X) \times A$ ($A$ AF) & Closed & Aguilar~\cite{aguilar2019} \\
Riemannian $\times$ abelian & Closed & Farsi--Latr\'emoli\`ere~\cite{farsi_latremoliere2024} \\
Single Riemannian along path & Closed & Farsi--Latr\'emoli\`ere~\cite{farsi_latremoliere2025} \\
Single truncation, NC integral & Closed & Hekkelman--McDonald~\cite{hekkelman_mcdonald2024b} \\
Two infinite Riemannian non-flat & \textbf{Open prior to this work} & --- \\
\midrule
Two $\sthree$ at distinct $\lambda$ & \textbf{Closed (this paper)} & Theorem~\ref{thm:main} \\
\bottomrule
\end{tabular}
\end{center}

The structural difficulty of the two-infinite case is that
Latr\'emoli\`ere tunneling pairs do not multiply trivially: for
$(B_a \otimes B_b, P_a \otimes P_b)$, the joint reach inherits from
both single-factor approximate-identity rates with their commutator
structure, and the joint Lipschitz constant is not $\max(C_3^a,
C_3^b)$ in general. The Bo{\.z}ejko--Fendler product cb-norm formula
covers each factor's central convolution but the propinquity-tunneling
assembly for the product is not in print prior to this work. The
present paper closes the case by explicitly using the Connes--Marcolli
graded anticommutation \eqref{eq:anticomm} on the KO-dim-6 module to
turn the generic triangle bound into a Pythagorean identity, which is
what controls both the joint Lipschitz constant
(Lemma~\ref{lem:L3-T}) and the joint height-distortion term
(Lemma~\ref{lem:L5-T}).

\subsection{Obstructions to the cross-manifold extensions}
\label{sec:obstructions}

We documented in \S\ref{sec:intro} that the same-manifold case treated
here is the most accessible of three plausible tensor-product
extensions of~\cite{loutey_paper38}. The two cross-manifold variants
remain open structural questions in the broader noncommutative
geometry program.

\paragraph{Riemannian $\times$ Hardy-sector
($\Tcal_{\sthree} \otimes \Tcal_{S^5}^{\mathrm{Bargmann}}$).}
The first cross-manifold extension would tensor the Riemannian
$\sthree$ Camporesi--Higuchi triple with a Bargmann--Segal-type
spectral triple on $S^5$ in the holomorphic Hardy
sector~\cite{paper24}. This is structurally obstructed at the
framework level: the $\sthree$ factor is a second-order Riemannian
spinor Dirac with KO-dimension $3$, while the $S^5$ Bargmann factor is
a first-order complex-analytic Euler operator on a Hardy sector and
does not fit standard NCG Dirac axioms (KO-dimension is not
classically defined in this setting). The two factors live in
different categories of NCG construction, and there is no published
prescription for tensoring them. We have flagged this elsewhere as the
four-layer Coulomb/HO asymmetry of~\cite{paper24}~\S V resurfacing at
the spectral-triple level. Neither the Bargmann transform nor the
Kustaanheimo--Stiefel transformation provides a bridge: the former is
a unitary intertwiner of operators on Hilbert spaces, not a unitary
equivalence of spectral triples, and the latter operates at the
coordinate level, mapping the 3D Coulomb problem to a 4D HO problem
under a constraint, without preserving the Riemannian / spinor bundle
structure required for KO-dimension. A proper Riemannian--Hardy
propinquity theory is not in the literature and would require new
framework development beyond the scope of the present paper.

\paragraph{Riemannian $\times$ Riemannian on different manifolds
($\Tcal_{\sthree} \otimes \Tcal_{S^5}^{\mathrm{Riem}}$).}
The alternative is to abandon the Bargmann content of $S^5$ and tensor
$\sthree$ with the round Riemannian $S^5$ spinor Dirac. KO-arithmetic
is clean ($3 + 5 = 8 \equiv 0 \pmod 8$), and this object is a
textbook Connes--Marcolli construction. But propinquity convergence
for $\Tcal_{S^5}^{\mathrm{Riem}}$ alone --- the rank-2 Spin(6)
analog of \cite{loutey_paper38} --- requires a fresh five-lemma
analysis: a higher-rank version of the Avery 3-Y integral, the
corresponding $\SO(6)$ selection rule, and a rank-2 central spectral
Fej\'er kernel. We expect analogous $\log n / n$-rate convergence
with rank-dependent constants, but the detailed analysis is open and
is itself a separate paper.

\subsection{Significance for the multi-focal-composition program}
\label{sec:significance}

The same-manifold case is what is needed for the GeoVac multi-focal
composition program (where two electrons in distinct hydrogenic shells
live on $\sthree$ at distinct focal lengths $\lambda = n/Z$). With
Theorem~\ref{thm:main} in place, the cross-register two-body coordinate
operator $V(\hat r_1, \hat r_2)$ across two electronic registers at
distinct focal lengths is well-defined as a multiplier on the joint
operator system $\Op_{\nmaxa} \otimes \Op_{\nmaxb}$, with
Lipschitz seminorm bounded by the product of $C_3^{(2)}(\nmaxa,
\nmaxb)$ and the classical Lipschitz norm of $V$ on $\sthree \times
\sthree$. The convergence theorem provides the metric foundation; the
structural application is left for a separate paper.

% =====================================================================
\section{Open questions}\label{sec:open}
% =====================================================================

\paragraph{(i) Quantitative rate at small $\nmax$.} Theorem~\ref{thm:main}
inherits the single-factor asymptotic rate
$\gamma_n \sim (4/\pi) \log n / n$ from~\cite{loutey_paper38}; the
quantitative rate at small $\nmax$ remains the open follow-up to
\cite[\S 5(i)]{loutey_paper38}, parallel to single-factor Track~C in
the GeoVac internal record. The joint rate inherits the same
open-quantitative-constant feature, since the $\max$-form
$\max(\gamma_{\nmaxa}, \gamma_{\nmaxb})$ is dominated by the worse
single-factor rate.

\paragraph{(ii) Off-factorized-panel functions.} Theorem~\ref{thm:main}
is stated and verified on simple tensors $f \otimes g$ and extended by
linearity to finite linear combinations; the $C_3^{(2)}$ formula
\eqref{eq:C3_2_full} arises from the Pythagorean Leibniz on
unit-Lipschitz Avery harmonics. General $h \in C^\infty(\sthree
\times \sthree)$ that are not of factorized form may admit
sharper bounds via direct Sobolev embedding on $\sthree \times
\sthree$. The detailed analysis of the off-factorized case --- and in
particular whether $C_3^{(2)}$ is sharp on functions with cross-mixing
between the two factors --- is open.

\paragraph{(iii) Higher tensor factors.} The proof extends mechanically
to $k$-fold tensor products $\Tcal_{\sthree}^{\lambda_1} \otimes \cdots
\otimes \Tcal_{\sthree}^{\lambda_k}$ via repeated application of the
Pythagorean Leibniz rule, with $C_3^{(k)}$ growing as $O(\sqrt{k})$ in
the appropriate norm. The $k$-fold case is not motivated by a current
GeoVac physics application, but is mathematically natural and
structurally accessible.

\paragraph{(iv) Conditional Coulomb/HO bridge.} Should a unifying
NCG-framework extension be developed that bridges the Riemannian
spinor Dirac and Hardy-sector first-order complex operator categories
at the spectral-triple level (\S\ref{sec:obstructions}), the
W2b-medium case
$\Tcal_{\sthree} \otimes \Tcal_{S^5}^{\mathrm{Bargmann}}$ would become
a target for a follow-up to the present paper. The ingredients on the
$\sthree$ side are exactly Theorem~\ref{thm:main} restricted to the
left tensor factor.

% =====================================================================
\section{Conclusion}\label{sec:conclusion}
% =====================================================================

We have established Latr\'emoli\`ere propinquity convergence for
truncations of the tensor-product Camporesi--Higuchi spectral triple
on $\sthree \times \sthree$ at distinct focal lengths, with explicit
qualitative-rate bound \eqref{eq:main_rate_intro}, closed-form
joint Lipschitz comparison constant \eqref{eq:C3_2_full} less than $1$
at every finite cutoff, and explicit Stein--Weiss-type bound on the
Lipschitz-distortion height. The mechanism that controls both the
Lipschitz constant and the height term is the same: the
Connes--Marcolli graded anticommutation
$\{\DCH^{(a)} \otimes I, \gamma_a \otimes \DCH^{(b)}\} = 0$ on the
KO-dimension-6 graded module turns the generic triangle inequality
$\norm{A + B} \le \norm{A} + \norm{B}$ into a Pythagorean identity
$\norm{A + B}^2 = \norm{A}^2 + \norm{B}^2$ when the two summands of
$D_{a,b}$ act on disjoint sectors of the graded module. The result
extends Connes--van~Suijlekom~\cite{connes_vs2021} and the subsequent
flat-structure and single-non-abelian-factor literature
\cite{hekkelman2022, hekkelman_mcdonald2024, leimbach_vs2024,
loutey_paper38} to the simplest non-abelian tensor case, and closes a
case in the propinquity tensor-product programme that the published
literature does not previously cover. The cross-manifold extensions
remain open structural questions, with the Coulomb/HO category
mismatch documented in~\cite{paper24}~\S V identifying a precise
framework-level obstruction to the Riemannian--Hardy variant.

% =====================================================================
\section*{Acknowledgments}
% =====================================================================

The author thanks Alain Connes, Walter van~Suijlekom, Fran\c{c}ois
Latr\'emoli\`ere, Carla Farsi, Matilde Marcolli, Edward Hekkelman,
Edward McDonald, Lukas Leimbach, and Carlos Perez-Sanchez for the
foundational frameworks on which this paper builds; remaining errors
are the author's own. This paper builds directly on
\cite{loutey_paper38} (single-factor $\sthree$ propinquity
convergence) and on the multi-focal-composition track of the GeoVac
internal record. As with~\cite{loutey_paper38}, this work was
developed in an AI-augmented agentic workflow with Anthropic's Claude:
implementation of the proof-assistant verification machinery,
drafting of the internal proof memos used as supporting documentation,
and bibliographic collation were performed collaboratively. All
theorem statements, design choices, and editorial decisions are the
author's responsibility.

% =====================================================================
\bibliographystyle{plainnat}
\begin{thebibliography}{99}

\bibitem[Aguilar(2019)]{aguilar2019}
K.~Aguilar,
\newblock \emph{Quantum metrics on $C(X) \otimes A$ for $A$ an AF
algebra},
\newblock Banach J.~Math.~Anal., to appear (2019);
\newblock arXiv:1907.07357.

\bibitem[Avery, Wen \& Avery(1986)]{avery_wen_avery1986}
J.~Avery, Z.-Y.~Wen, and J.~S.~Avery,
\newblock \emph{Hyperspherical harmonics: Some properties and applications},
\newblock J.~Math.~Phys. \textbf{27} (1986), 396--402.

\bibitem[Bo{\.z}ejko \& Fendler(1991)]{bozejko_fendler1991}
M.~Bo{\.z}ejko and G.~Fendler,
\newblock \emph{Herz--Schur multipliers and uniformly bounded
representations of discrete groups},
\newblock Arch.~Math. \textbf{57} (1991), 290--298.

\bibitem[Camporesi \& Higuchi(1996)]{camporesi_higuchi1996}
R.~Camporesi and A.~Higuchi,
\newblock \emph{On the eigenfunctions of the Dirac operator on
spheres and real hyperbolic spaces},
\newblock J.~Geom.~Phys. \textbf{20} (1996), 1--18.

\bibitem[Connes(1995)]{connes1995}
A.~Connes,
\newblock \emph{Noncommutative Geometry},
\newblock Academic Press, 1995.

\bibitem[Connes \& van~Suijlekom(2021)]{connes_vs2021}
A.~Connes and W.~D.~van~Suijlekom,
\newblock \emph{Spectral truncations in noncommutative geometry and
operator systems},
\newblock Comm.~Math.~Phys. \textbf{383} (2021), 2021--2067;
\newblock arXiv:2004.14115.

\bibitem[Farsi \& Latr\'emoli\`ere(2024)]{farsi_latremoliere2024}
C.~Farsi and F.~Latr\'emoli\`ere,
\newblock \emph{Collapse in noncommutative geometry and spectral
continuity},
\newblock arXiv:2404.00240, 2024.

\bibitem[Farsi \& Latr\'emoli\`ere(2025)]{farsi_latremoliere2025}
C.~Farsi and F.~Latr\'emoli\`ere,
\newblock \emph{Continuity for the spectral propinquity of the Dirac
operators associated with an analytic path of Riemannian metrics},
\newblock arXiv:2504.11715, 2025.

\bibitem[Hekkelman(2022)]{hekkelman2022}
E.~Hekkelman,
\newblock \emph{Truncations of the circle and Connes' geometric
formula},
\newblock M.Sc.\ thesis, Radboud University, 2022;
\newblock arXiv:2206.13744.

\bibitem[Hekkelman \& McDonald(2024)]{hekkelman_mcdonald2024}
E.~Hekkelman and E.~McDonald,
\newblock \emph{Spectral truncations of $T^d$ and quantum metric
geometry},
\newblock J.~Noncommut.~Geom., to appear (2024);
\newblock arXiv:2403.18619.

\bibitem[Hekkelman \& McDonald(2024b)]{hekkelman_mcdonald2024b}
E.~Hekkelman and E.~McDonald,
\newblock \emph{A noncommutative integral on spectrally truncated
spectral triples, and a link with quantum ergodicity},
\newblock J.~Funct.~Anal., to appear (2025), arXiv:2412.00628.

\bibitem[Latr\'emoli\`ere(2016)]{latremoliere2016}
F.~Latr\'emoli\`ere,
\newblock \emph{The dual Gromov--Hausdorff propinquity},
\newblock Banach J.~Math.~Anal. \textbf{10} (2016), 175--229.

\bibitem[Latr\'emoli\`ere(2017)]{latremoliere_metric_st_2017}
F.~Latr\'emoli\`ere,
\newblock \emph{The Gromov--Hausdorff propinquity for metric spectral
triples},
\newblock Adv.~Math. \textbf{415} (2023), Paper No.~108876, 88pp;
\newblock preprint arXiv:1811.10843, 2017.

\bibitem[Latr\'emoli\`ere(2018)]{latremoliere2018}
F.~Latr\'emoli\`ere,
\newblock \emph{The Gromov--Hausdorff propinquity},
\newblock Trans.~Amer.~Math.~Soc. \textbf{370} (2018), 365--411.

\bibitem[Latr\'emoli\`ere(2026)]{latremoliere2026}
F.~Latr\'emoli\`ere,
\newblock \emph{Spectral continuity of almost commutative manifolds for
the $C^1$ topology on Riemannian metrics},
\newblock arXiv:2603.19128, 2026.

\bibitem[Leimbach \& van~Suijlekom(2024)]{leimbach_vs2024}
L.~Leimbach and W.~D.~van~Suijlekom,
\newblock \emph{Gromov--Hausdorff convergence of spectral truncations
of the torus},
\newblock Adv.~Math. \textbf{439} (2024), Paper No.~109496.

\bibitem[Marcolli \& van~Suijlekom(2014)]{marcolli_vs2014}
M.~Marcolli and W.~D.~van~Suijlekom,
\newblock \emph{Gauge networks in noncommutative geometry},
\newblock J.~Geom.~Phys. \textbf{75} (2014), 71--91;
\newblock arXiv:1301.3480.

\bibitem[Pisier(2003)]{pisier2003}
G.~Pisier,
\newblock \emph{Introduction to Operator Space Theory},
\newblock London Math.~Soc.~Lecture Note Ser. \textbf{294}, Cambridge
Univ.~Press, 2003.

\bibitem[Stein \& Weiss(1971)]{stein_weiss1971}
E.~M.~Stein and G.~Weiss,
\newblock \emph{Introduction to Fourier Analysis on Euclidean Spaces},
\newblock Princeton Math.~Ser. \textbf{32}, Princeton Univ.~Press, 1971.

\bibitem[Loutey, Paper~24]{paper24}
J.~Loutey,
\newblock \emph{Bargmann--Segal lattice for the 3D harmonic oscillator
and the Coulomb/HO structural asymmetry},
\newblock GeoVac internal preprint (2026), DOI via Zenodo.

\bibitem[Loutey, Paper~38]{loutey_paper38}
J.~Loutey,
\newblock \emph{Latr\'emoli\`ere propinquity convergence of truncated
Camporesi--Higuchi spectral triples on $\sthree$},
\newblock preprint, May 2026; companion to the present paper, DOI via
Zenodo.

\end{thebibliography}

\end{document}
