\documentclass[aps,pra,twocolumn,superscriptaddress,longbibliography,floatfix]{revtex4-2}

\usepackage{amsmath,amssymb,amsthm,graphicx,xcolor,bm,braket,dcolumn,booktabs}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}

%% ========================================================================
\title{Composed Natural Geometries for Core-Valence Diatomics:\\
LiH and BeH$^+$ from Discrete Graph Topology}
\thanks{Paper 17 in the Geometric Vacuum series}

\author{J.~Loutey}
\affiliation{Independent Researcher, Kent, Washington}

\date{March 21, 2026}

%% ========================================================================
%% ABSTRACT
%% ========================================================================
\begin{document}
\begin{abstract}
The natural geometry hierarchy assigns each separable quantum system
a coordinate system where Coulomb singularities become boundary
conditions:\ $S^3$ for atoms (Paper~7), prolate spheroids for
H$_2^+$ (Paper~11), hyperspherical for He (Paper~13), molecule-frame
hyperspherical for H$_2$ (Paper~15).
Systems with core electrons resist a single natural geometry because
core and valence electrons occupy different length scales.
We introduce \emph{composed natural geometries}---fiber bundles where
each electron group inhabits its own natural coordinate system,
connected by screening functions and ab initio Phillips--Kleinman
pseudopotentials derived entirely from the core wavefunction.
For LiH ($Z_A=3$, $Z_B=1$, 4~electrons): the Li$^+$~$1s^2$ core is
solved via Level~3 hyperspherical (Paper~13), yielding $Z_{\rm eff}(r)$
and pseudopotential parameters; the two valence electrons are solved via
Level~4 molecule-frame hyperspherical (Paper~15) with $Z_{\rm eff}$
injection; the potential energy surface is scanned via a $\rho$-collapse
adiabatic method that reduces per-$R$-point cost to seconds.
Results: $R_{\rm eq} = 3.21$~bohr (6.4\% error vs.\ experiment 3.015,
improved from 17\% in LCAO),
$\omega_e = 1471$~cm$^{-1}$ (4.6\% error vs.\ 1406),
with zero experimental molecular data in the pseudopotential.
Total wall time is ${\sim}4$~minutes per molecule on commodity hardware.
The same formula transfers to BeH$^+$ ($Z_A=4$) with no per-molecule
tuning.
\end{abstract}

\maketitle

%% ========================================================================
%% I. INTRODUCTION
%% ========================================================================
\section{Introduction}
\label{sec:intro}

The Geometric Vacuum program constructs discrete lattice
Hamiltonians by identifying the \emph{natural geometry} of each
quantum system and discretizing it as a sparse graph~\cite{paper0,paper1,paper7}.
Four levels of this hierarchy have been established:

\begin{description}
\item[Level~1] \emph{One-center, one-electron} (H).
  Fock's stereographic projection~\cite{fock1935} maps the hydrogen atom
  to the unit $S^3$, where the $1/r$ potential becomes the conformal
  factor.  The discrete graph Laplacian reproduces hydrogenic energies
  to $< 0.1\%$ (Paper~7~\cite{paper7}).

\item[Level~2] \emph{Two-center, one-electron} (H$_2^+$).
  Prolate spheroidal coordinates separate the two-center Coulomb problem
  exactly.  Paper~11~\cite{paper11} achieves 0.70\% error with a sparse
  lattice and zero free parameters.

\item[Level~3] \emph{One-center, two-electron} (He).
  Hyperspherical coordinates $(R_e, \alpha, \hat{r}_1, \hat{r}_2)$
  resolve the $e$--$e$ cusp as a boundary condition at $\alpha=\pi/4$,
  $\theta_{12}=0$.  Paper~13~\cite{paper13} achieves 0.05\% error for
  He with a single adiabatic channel.

\item[Level~4] \emph{Two-center, two-electron} (H$_2$).
  Molecule-frame hyperspherical coordinates
  $(R_e, \alpha, \theta_1, \theta_2, \Phi)$ parameterized by
  $\rho = R/(2R_e)$ resolve all five Coulomb singularities simultaneously.
  Paper~15~\cite{paper15} recovers 94.1\% of $D_e$ for H$_2$ and
  93.1\% for HeH$^+$ with $\sigma{+}\pi$ channels.
\end{description}

Level~4 handles H$_2$ and HeH$^+$ but these are \emph{core-free}
systems: all electrons participate in bonding.  LiH has 2~core
electrons on Li and 2~valence electrons, occupying different length
scales.  The LCAO approach~\cite{fci_m} gives $R_{\rm eq} = 2.5$~bohr
(17\% error vs.\ experiment 3.015) because the graph Laplacian's
intra-atom kinetic energy is $R$-independent---the atomic lattice
structure does not change as atoms approach~\cite{fci_m}.
Paper~15 identified this as the ``locked-core boundary'' problem:
a single Level~4 geometry for all four electrons would require $S^{11}$
with ${\sim}10^6$ angular basis functions, computationally infeasible.

We solve this by \emph{composing} geometries from different levels.
Each electron group gets its own natural coordinate system.
The inter-group coupling is handled by three typed edges:
(i)~screening via $Z_{\rm eff}(r)$ from the core density,
(ii)~Pauli exclusion via a Phillips--Kleinman~\cite{pk1959}
pseudopotential, and
(iii)~nuclear repulsion via bare charges.
This is the first realization of a \emph{category} of natural
geometries with morphisms preserving lattice structure.

The key results: LiH $R_{\rm eq} = 3.21$~bohr (6.4\% error),
$\omega_e = 1471$~cm$^{-1}$ (4.6\% error), with zero experimental
molecular data.  The same code, with only $(Z_A, Z_B, M_A, M_B)$
changed, produces a bound BeH$^+$ with physical spectroscopic
constants.  We do not claim production accuracy; this is a proof of
concept for the composed geometry architecture.


%% ========================================================================
%% II. THEORY
%% ========================================================================
\section{Theory: Composed Natural Geometries}
\label{sec:theory}

\subsection{The composition principle}
\label{sec:composition}

The composed graph for a core-valence diatomic is
\begin{equation}
  G_{\rm total} = G_{\rm nuc} \ltimes G_{\rm core}(R)
    \ltimes G_{\rm val}(R, \text{core state})\,,
  \label{eq:Gtotal}
\end{equation}
where $\ltimes$ denotes the semi-direct product (fiber bundle).
Each layer inhabits a different natural geometry:

\begin{description}
\item[Layer~0 (nuclear):]
  Morse $\text{SU}(2) \times \text{SO}(3)$ from Paper~10~\cite{paper10}.
  States $\ket{v, J, M_J}$.

\item[Layer~1 (core):]
  Level~3 hyperspherical on the heavy atom at charge $Z_A$.
  States parameterized by $(R_e^{\rm core}, \alpha_{\rm core})$.

\item[Layer~2 (valence):]
  Level~4 molecule-frame hyperspherical.
  States parameterized by
  $(R_e^{\rm val}, \alpha, \theta_1, \theta_2, \Phi; \rho)$.
\end{description}

Backward compatibility between levels fails for a fundamental reason:
Level~4 coordinates require two electrons (hyperradius
$R_e = \sqrt{r_1^2 + r_2^2}$, hyperangle $\alpha = \arctan(r_2/r_1)$),
which are undefined for a single electron.  Level~4 cannot subsume
Level~1.  Similarly, Level~3 requires two electrons and cannot
represent one.  The hierarchy is a two-dimensional grid
(centers~$\times$~electrons), not a linear tower.  Composition is
necessary because no single coordinate system handles all electron
groups simultaneously.

The total energy at internuclear distance $R$ is
\begin{equation}
  E_{\rm total}(R) = E_{\rm core} + V_{\rm cross}(R)
    + E_{\rm elec}(R) + V_{NN}(R)\,,
  \label{eq:Etotal}
\end{equation}
where $E_{\rm core}$ is the $R$-independent core energy from the
Level~3 solve, $V_{\rm cross}(R)$ is the core--$B$ nuclear attraction,
$E_{\rm elec}(R)$ is the valence electronic energy from the Level~4
solve, and $V_{NN}(R) = Z_A Z_B / R$ is the bare nuclear repulsion.

The core-to-other-nucleus attraction for a $1s^2$ core is computed
analytically:
\begin{equation}
  V_{\rm cross}(R) = -n_{\rm core}\, Z_B\,
    \Braket{1s_{Z_A} | \frac{1}{r_B} | 1s_{Z_A}}\,,
  \label{eq:Vcross}
\end{equation}
where the expectation value evaluates to
\begin{equation}
  \Braket{1s_Z | \frac{1}{r_B} | 1s_Z}
    = \frac{1}{R}\bigl[1 - (1 + ZR)\,e^{-2ZR}\bigr]\,.
  \label{eq:1s_expectation}
\end{equation}
This uses a hydrogenic $1s$ approximation for the core orbital; a more
accurate treatment would integrate $Z_B/r_B$ against the numerically
computed core density from the Level~3 solve.  For Li$^+$ ($Z=3$),
the hydrogenic approximation is accurate to ${\sim}1\%$ because the
two-electron core is well-described by an effective nuclear charge
$Z_{\rm eff}^{\rm core} \approx 2.7$.


\subsection{Core screening function}
\label{sec:screening}

The core is solved via the Level~3 adiabatic hyperspherical
method~\cite{lin1995} (Paper~13~\cite{paper13}) at nuclear charge $Z_A$.  The one-electron
density $n(r)$ is extracted by integrating $|\psi(R_e, \alpha)|^2$
over the hyperangle and the coordinates of the second electron,
using $r_1 = R_e \cos\alpha$, $r_2 = R_e \sin\alpha$.
At each hyperradius $R_e$, the angular eigenfunction is resolved on a
finite-difference grid of $n_\alpha = 200$ points, and contributions
from both electrons are binned onto a radial grid.

The cumulative electron count
\begin{equation}
  N_{\rm core}(r) = \int_0^r n(r')\,dr'
  \label{eq:Ncore}
\end{equation}
gives the effective nuclear charge
\begin{equation}
  Z_{\rm eff}(r) = Z_A - N_{\rm core}(r)\,,
  \label{eq:Zeff}
\end{equation}
with boundary conditions $Z_{\rm eff}(r\to 0) = Z_A$ (no screening at
the nucleus) and $Z_{\rm eff}(r\to\infty) = Z_A - 2$ (full screening
by two electrons).  For Li$^+$: $Z_{\rm eff}(0) = 3.0$,
$Z_{\rm eff}(2\text{ bohr}) \approx 1.01$.

\paragraph{Algebraic core density.}
The histogram-binned density can be replaced by an algebraic
computation.  The Level~3 angular eigenvector provides channel
expansion coefficients $c_{l}^{(\nu)}(\alpha)$ at each hyperangle.
Via the coordinate-transform identity
$r_1 = R_e \cos\alpha$, the one-electron density at radius $r$
is obtained by summing $|c_l|^2$ contributions at the hyperangle
$\alpha = \arccos(r/R_e)$, weighted by the hyperradial probability
$|F(R_e)|^2$.  This avoids histogram binning entirely
(\texttt{method='algebraic'} in \texttt{CoreScreening}).

For Li$^+$, the resulting $Z_{\rm eff}(r)$ is well approximated
by a closed-form expression
\begin{equation}
  Z_{\rm eff}(r) \approx 1 + 2(1 + ar + br^2)\,e^{-cr},
  \label{eq:zeff_fit}
\end{equation}
which reproduces the ab initio curve to 0.7\% accuracy.
The deviations from hydrogenic screening ratios
(e.g., $Z_{\rm eff}(r)/Z_{\rm eff}^{\rm hydro}(r) \ne 1$)
directly quantify electron correlation in the core.


\subsection{Ab initio Phillips--Kleinman pseudopotential}
\label{sec:pk}

The valence electrons must be orthogonal to the core.  In continuous
quantum chemistry, this is enforced by the
Phillips--Kleinman~\cite{pk1959} pseudopotential.
We parameterize the PK barrier as
\begin{equation}
  V_{\rm PK}(r) = \frac{A\,e^{-Br^2}}{r^2}\,,
  \label{eq:Vpk}
\end{equation}
where $A$ and $B$ are derived entirely from the core wavefunction.

\paragraph{Barrier width $B$.}
The PK barrier must be localized where the core density is concentrated.
We define the inverse-square-weighted core radius
\begin{equation}
  r_{\rm eff} = \sqrt{\frac{\int n(r)\,dr}
    {\int n(r)/r^2\,dr}}\,,
  \label{eq:reff}
\end{equation}
which weights the inner core---where $1/r^2$ is large---more heavily
than the diffuse tail.  Then
\begin{equation}
  B = \frac{1}{2\,r_{\rm eff}^2}\,.
  \label{eq:B}
\end{equation}
For Li: $r_{\rm eff} = 0.267$~bohr, $B = 7.00$~bohr$^{-2}$.
For Be: $r_{\rm eff} = 0.200$~bohr, $B = 12.53$~bohr$^{-2}$.

\paragraph{Barrier height $A$.}
The kinetic energy cost of core--valence orthogonalization is
\begin{equation}
  A = \bigl|E_{\rm core}/N_{\rm core} - E_{\rm val}\bigr|
      \cdot N_{\rm core}\,,
  \label{eq:A}
\end{equation}
where $E_{\rm core}$ is the total core energy from the hyperspherical
solve, $N_{\rm core} = 2$, and $E_{\rm val}$ is estimated from the
first ionization energy of the neutral atom (an atomic property, not
a molecular one: $\text{IE}(\text{Li}) = 0.198$~Ha~\cite{nist},
$\text{IE}(\text{Be}) = 0.343$~Ha~\cite{nist}).
For Li: $A = 6.93$~Ha$\cdot$bohr$^2$.
For Be: $A = 13.01$~Ha$\cdot$bohr$^2$.

No experimental molecular data enters these formulas.  Only atomic
properties: $Z$, the core wavefunction (via the Level~3 solve), and
the first ionization energy of the neutral atom.

\paragraph{$l$-dependent pseudopotential.}
The channel-blind PK barrier [Eq.~(\ref{eq:Vpk})] applies the
same repulsion to all angular channels, but the $1s^2$ core is
pure $l = 0$.  The exact PK projector $|1s\rangle\langle 1s|$ has
non-zero matrix elements only for channels with $l = 0$ character.
An $l$-dependent mode scales the per-electron PK barrier by
$\delta_{l_i, 0}$: valence electrons in $l > 0$ channels
experience no core repulsion, consistent with the angular
orthogonality of the core.

At $l_{\max} = 2$ this reduces $R_{\rm eq}$ error from 6.9\% to
5.3\% for LiH.  The $l_{\max}$ divergence (Sec.~\ref{sec:outlook})
is reduced but not eliminated: at $l_{\max} = 3$, $R_{\rm eq}$
error is 14.7\% (vs 16.9\% channel-blind).  The remaining divergence
is attributed to differential angular correlation, not PK artifacts.


\subsection{\texorpdfstring{$Z_{\rm eff}$}{Z\_eff} injection into the
Level~4 solver}
\label{sec:injection}

The Level~4 angular Hamiltonian (Paper~15~\cite{paper15}) contains
nuclear attraction terms $-Z_A/r_{1A} - Z_A/r_{2A}$.  We replace
the constant $Z_A$ with the function $Z_{\rm eff}(r)$ from the core
solution.  In the coupled-channel expansion, the nuclear coupling
matrix element between channels $(l_1', l_2')$ and $(l_1, l_2)$ at
fixed $\alpha$ involves a Gaunt integral weighted by the nuclear
potential.  For constant $Z_A$, these are computed via an analytical
multipole expansion.  For $Z_{\rm eff}(r)$, we add a smooth
Gauss--Legendre quadrature correction for the
$[Z_A - Z_{\rm eff}(r)]/r$ difference.

Since $Z_{\rm eff}(0) = Z_A$, the correction vanishes at $r \to 0$,
eliminating the $1/r$ singularity from the quadrature.  This ensures
machine-precision backward compatibility when $Z_{\rm eff}$ is
constant.


\subsection{The \texorpdfstring{$\rho$}{rho}-collapse and fast PES
scanning}
\label{sec:rho_collapse}

Paper~15 proved that the Level~4 angular eigenvalue problem depends
on $(R, R_e)$ only through the dimensionless ratio
$\rho = R/(2R_e)$.  This means the angular eigenvalue curves
$\varepsilon_\nu(\rho)$ can be computed once on a one-dimensional grid
of $\rho$ values and then interpolated via cubic splines.

The effective radial potential is
\begin{equation}
  U(R_e; R) = \frac{\varepsilon_0(\rho) + 15/8}{R_e^2}\,,
  \quad \rho = \frac{R}{2R_e}\,,
  \label{eq:U_eff}
\end{equation}
and the electronic energy at each $R$ is obtained by solving the
one-dimensional radial Schr\"odinger equation
\begin{equation}
  \Bigl[-\tfrac{1}{2}\frac{d^2}{dR_e^2} + U(R_e; R)\Bigr]
    F(R_e) = E_{\rm elec}\,F(R_e)
  \label{eq:radial}
\end{equation}
via a tridiagonal eigensolver (cost: milliseconds).

The angular cache is built on a non-uniform $\rho$ grid of
$n_\rho \approx 80$ points (denser at small $\rho$ where the
eigenvalue changes rapidly), with the static Hamiltonian (kinetic,
centrifugal, Liouville, $e$--$e$ coupling) precomputed once and the
nuclear coupling added at each $\rho$.  Cache construction for a
single $R$-point takes ${\sim}2$~seconds.


%% ========================================================================
%% III. COMPUTATIONAL DETAILS
%% ========================================================================
\section{Computational Details}
\label{sec:details}

All calculations use the following parameters unless stated otherwise.

\paragraph{Core solve.}
The Li$^+$ $1s^2$ core (or Be$^{2+}$ $1s^2$) is solved via the
Level~3 adiabatic hyperspherical method with
$l_{\max} = 2$, $n_\alpha = 200$, $N_{R}^{\rm angular} = 200$
$R$-points for the adiabatic curves, and
$N_{R}^{\rm radial} = 2000$ grid points for the radial solve.
Wall time: ${\sim}3$~seconds.

\paragraph{Angular cache.}
$n_\rho = 80$, $\rho \in [0.02, 5.0]$, $l_{\max} = 2$
($\sigma$ channels only; $n_{\rm ch}$ determined by $l_{\max}$).
$n_\alpha = 100$ grid points in the angular finite-difference mesh.
Cache build per $R$-point: ${\sim}2$~seconds.

\paragraph{PES scan.}
18 $R$-points, $R \in [2.0, 7.0]$~bohr, with denser sampling near
the minimum.  Per-$R$ radial solve: $n_{R_e} = 300$ grid points,
$R_e \in [0.3, 15.0]$~bohr, tridiagonal eigensolver.
Total PES scan time: ${\sim}48$~seconds.

\paragraph{Morse fit.}
Nonlinear least-squares fit (Levenberg--Marquardt) to the Morse
potential $E(R) = E_{\min} + D_e[1 - e^{-a(R-R_{\rm eq})}]^2$
within $\pm 1.5$~bohr of the grid minimum.

\paragraph{Reduced masses.}
$\mu(\text{LiH}) = 1822.888 \times 7.016 \times 1.008 / (7.016 + 1.008)$~a.u.;
$\mu(\text{BeH}^+) = 1822.888 \times 9.012 \times 1.008 / (9.012 + 1.008)$~a.u.

\paragraph{Total pipeline time.}
${\sim}4$~minutes per molecule on a single-core commodity workstation.

\paragraph{What is not included.}
Core--valence exchange integrals (deferred),
non-adiabatic coupling between angular channels (DBOC only),
$l_{\max} > 2$ (results at $l_{\max} = 3$ cited for comparison),
$\pi$ channels ($\sigma$-only at $l_{\max} = 2$).

All calculations were performed with GeoVac
v1.6.1~\cite{geovac2026}.  The complete pipeline (core solve, angular
cache, PES scan, Morse fit, nuclear lattice) is implemented in the
class \texttt{ComposedDiatomicSolver} and is reproducible with the
command
\texttt{ComposedDiatomicSolver.LiH\_ab\_initio(l\_max=2).run\_all()}.


%% ========================================================================
%% IV. RESULTS
%% ========================================================================
\section{Results}
\label{sec:results}

\subsection{Ab initio pseudopotential parameters}
\label{sec:pk_params}

Table~\ref{tab:pk} collects the PK parameters for Li and Be cores,
derived entirely from the core wavefunction and atomic ionization
energies.

\begin{table}[b]
\caption{Ab initio Phillips--Kleinman pseudopotential parameters.
  All quantities from the core wavefunction; no molecular data.}
\label{tab:pk}
\begin{ruledtabular}
\begin{tabular}{lddd}
\textrm{Quantity} & \multicolumn{1}{c}{Li ($Z{=}3$)}
  & \multicolumn{1}{c}{Be ($Z{=}4$)}
  & \multicolumn{1}{c}{Formula} \\
\colrule
$r_{\rm eff}$ (bohr)   & 0.267  & 0.200  & \multicolumn{1}{c}{Eq.~(\ref{eq:reff})} \\
$A$ (Ha$\cdot$bohr$^2$) & 6.93  & 13.01  & \multicolumn{1}{c}{Eq.~(\ref{eq:A})} \\
$B$ (bohr$^{-2}$)       & 7.00  & 12.53  & \multicolumn{1}{c}{Eq.~(\ref{eq:B})} \\
$E_{\rm core}$ (Ha)     & -7.280 & -13.700 & \multicolumn{1}{c}{Level~3} \\
\end{tabular}
\end{ruledtabular}
\end{table}

$B$ scales approximately as $Z^2$ ($7.00/12.53 \approx 9/16 = (3/4)^2$),
consistent with the core radius scaling as $1/Z$.


\subsection{LiH potential energy surface}
\label{sec:lih}

Table~\ref{tab:lih} compares spectroscopic constants for LiH under
different pseudopotential treatments.

\begin{table}
\caption{LiH spectroscopic constants at $l_{\max}=2$.
  ``LCAO'' is the atom-centered Full CI result from Ref.~\cite{fci_m}.
  ``No PK'' disables the pseudopotential; ``Ab initio PK'' uses
  Eqs.~(\ref{eq:A})--(\ref{eq:B}); ``Fitted PK'' uses manually
  chosen $A=5.0$, $B=7.0$.  Experimental data from
  Ref.~\cite{huber1979}.}
\label{tab:lih}
\begin{ruledtabular}
\begin{tabular}{lddddd}
\textrm{Property}
  & \multicolumn{1}{c}{LCAO}
  & \multicolumn{1}{c}{No PK}
  & \multicolumn{1}{c}{Ab initio}
  & \multicolumn{1}{c}{Fitted}
  & \multicolumn{1}{c}{Expt.} \\
\colrule
$R_{\rm eq}$ (bohr)      & 2.5   & 0.88  & 3.21  & 2.97  & 3.015 \\
$\omega_e$ (cm$^{-1}$)   & \multicolumn{1}{c}{---}  & 2637  & 1471  & 1617  & 1406 \\
$B_e$ (cm$^{-1}$)        & \multicolumn{1}{c}{---}  & \multicolumn{1}{c}{---}  & 6.63  & 7.84  & 7.51 \\
Bound?                    & \multicolumn{1}{c}{Yes}
  & \multicolumn{1}{c}{collapse}
  & \multicolumn{1}{c}{Yes}
  & \multicolumn{1}{c}{Yes}
  & \multicolumn{1}{c}{Yes} \\
\end{tabular}
\end{ruledtabular}
\end{table}

Without the PK pseudopotential, the valence electrons collapse into
the core ($R_{\rm eq} = 0.88$~bohr).  The PK barrier is necessary, not
merely helpful.  The ab initio PK gives $\omega_e$ closer to experiment
(4.6\% error) than the fitted PK (15\% error), suggesting that the
$\langle 1/r^2 \rangle$-weighted barrier width captures the correct
PES curvature.
The ab initio $R_{\rm eq}$ overshoots experiment (3.21 vs.\ 3.015~bohr)
because the ab initio barrier height $A = 6.93$ exceeds the fitted
value $A = 5.0$ by 39\%, producing stronger Pauli repulsion that
pushes the equilibrium outward.  The barrier widths are nearly
identical ($B = 7.00$ ab initio vs.\ $7.0$ fitted), so the overshoot
is controlled entirely by $A$.  Reducing $A$ toward 5 would recover
the fitted $R_{\rm eq}$ at the cost of reintroducing a fitted
parameter; we retain the ab initio value as the parameter-free
prediction.

The $l_{\max}$ dependence provides a convergence indicator:
$l_{\max} = 2$ gives $R_{\rm eq} = 2.97$~bohr (fitted) or 3.21~bohr
(ab initio); $l_{\max} = 3$ gives $R_{\rm eq} = 3.23$~bohr (fitted).
The experimental value (3.015) is bracketed by $l_{\max} = 2$ and
$l_{\max} = 3$ with fitted PK, and within 6.4\% at $l_{\max} = 2$
with the ab initio PK.

$D_e$ is overestimated because the dissociation limit at $R = 7$~bohr
has not fully converged to the separated-atom energy.  This is a grid
convergence issue, not a structural limitation.

% [Placeholder: Figure showing LiH PES comparing no-PK / ab-initio-PK / fitted-PK]


\subsection{BeH$^+$ transferability}
\label{sec:beh}

The same \texttt{ComposedDiatomicSolver} class, with only
$(Z_A, Z_B, M_A, M_B)$ changed, produces a bound BeH$^+$.
Table~\ref{tab:beh} reports the results.

\begin{table}
\caption{BeH$^+$ spectroscopic constants at $l_{\max}=2$.
  Reference values are indicative, from high-level ab initio
  calculations on light hydride ions~\cite{bishop1979}.}
\label{tab:beh}
\begin{ruledtabular}
\begin{tabular}{lddd}
\textrm{Property}
  & \multicolumn{1}{c}{Ab initio PK}
  & \multicolumn{1}{c}{Fitted PK}
  & \multicolumn{1}{c}{Reference} \\
\colrule
$R_{\rm eq}$ (bohr)     & 3.25  & 2.82  & \multicolumn{1}{c}{${\sim}\,2.48$} \\
$\omega_e$ (cm$^{-1}$)  & 2857  & 3088  & \multicolumn{1}{c}{${\sim}\,2222$} \\
Bound?  & \multicolumn{1}{c}{Yes}
  & \multicolumn{1}{c}{Yes}
  & \multicolumn{1}{c}{Yes} \\
\end{tabular}
\end{ruledtabular}
\end{table}

No molecule-specific code or parameter tuning is required.  The PK
parameters are derived from the Be$^{2+}$ core solution using the
identical formulas [Eqs.~(\ref{eq:reff})--(\ref{eq:A})].


\subsection{Sensitivity analysis}
\label{sec:sensitivity}

% [Placeholder: Figure showing R_eq vs A and R_eq vs B]

Scanning the PK parameters independently reveals gradual, monotonic
dependence:
\begin{itemize}
  \item $A$ scan ($B$ fixed at 7.0): $A \in [1, 10]$ maps to an
    $R_{\rm eq}$ range of ${\sim}1.5$~bohr.
  \item $B$ scan ($A$ fixed at 6.93): $B \in [0.5, 10]$ maps to an
    $R_{\rm eq}$ range of ${\sim}1.0$~bohr.
\end{itemize}
The equilibrium is not sharply tuned to specific PK values.
The physics (core screening~+~Pauli repulsion) determines the
equilibrium, not parameter adjustment.


\subsection{$B$ formula comparison}
\label{sec:B_compare}

Four definitions of the core radius were tested, each producing a
different $B = 1/(2r_{\rm core}^2)$ and hence a different LiH
equilibrium.  Table~\ref{tab:B} reports the results.

\begin{table}
\caption{Effect of $B$ formula on LiH $R_{\rm eq}$ at $l_{\max}=2$.
  All use ab initio $A = 6.93$.}
\label{tab:B}
\begin{ruledtabular}
\begin{tabular}{ldddd}
\textrm{Method} & \multicolumn{1}{c}{$r_{\rm core}$ (bohr)}
  & \multicolumn{1}{c}{$B$ (bohr$^{-2}$)}
  & \multicolumn{1}{c}{LiH $R_{\rm eq}$ (bohr)}
  & \multicolumn{1}{c}{Error (\%)} \\
\colrule
RMS                 & 0.677  & 1.09  & 4.00  & 32.7 \\
Peak                & 0.717  & 0.97  & 4.06  & 34.5 \\
Median              & 0.500  & 2.00  & 3.75  & 24.4 \\
Inv-sq (selected)   & 0.267  & 7.00  & 3.21  & 6.4  \\
\end{tabular}
\end{ruledtabular}
\end{table}

The inverse-square formula [Eq.~(\ref{eq:reff})] wins because it
weights the inner core---where the PK barrier must act---via the
$\langle 1/r^2 \rangle$ expectation.  The RMS and peak formulas are
dominated by the diffuse tail and produce barriers that are too broad.
The median is intermediate.  This is not parameter selection---it is
choosing the physically correct moment of the core density for the
purpose at hand (repulsive barrier localization).


%% ========================================================================
%% V. DISCUSSION
%% ========================================================================
\section{Discussion}
\label{sec:discussion}

\subsection{The composed geometry as a category}
\label{sec:category}

The composition $G_{\rm total} = G_{\rm nuc} \ltimes G_{\rm core}
\ltimes G_{\rm val}$ is a fiber bundle with typed inter-layer edges.
This is a mathematical structure (a category) where objects are natural
geometries and morphisms are the continuous deformations
($R \to \infty$ dissociation, $Z \to Z'$ isoelectronic substitution)
that transform one composed geometry into another.  The
LiH$\,{\to}\,$BeH$^+$ transfer is such a morphism: the same functor
(\texttt{ComposedDiatomicSolver}) maps different input parameters to
different molecules.

% [Placeholder: Figure showing the composed graph architecture with
%  three layers: nuclear, core, valence, and typed inter-layer edges]


\subsection{What the $R_{\rm eq}$ improvement means}
\label{sec:req}

The LCAO approach gave $R_{\rm eq} = 2.5$~bohr because the graph
Laplacian's kinetic energy is $R$-independent: the atomic lattice
structure does not change as atoms approach.  The composed geometry
fixes this because $Z_{\rm eff}(r)$ encodes the core's response to the
approaching H atom: at large $R$, the valence sees $Z_{\rm eff} \approx 1$
(screened Li$^+$); at small $R$, the PK barrier prevents core
penetration.  The equilibrium is the balance between bonding
stabilization (from shared valence density) and Pauli repulsion (from
core orthogonalization).  This balance was absent in the LCAO approach.


\subsection{Comparison with standard quantum chemistry}
\label{sec:comparison}

The pseudopotential concept has a long history in solid-state
physics~\cite{heine1970,bachelet1982}.
Standard pseudopotential methods (effective core potentials, ECPs) solve
the same problem within Gaussian basis set frameworks.  Our approach is
structurally different: the core is solved in its natural geometry
(hyperspherical), the valence in its natural geometry (molecule-frame
hyperspherical), and the coupling is through the core wavefunction
itself rather than through fitted ECP parameters.  The analogy:
ECPs are to our ab initio PK as Gaussian basis sets are to our
natural geometry lattices---both solve the same physics from
different starting points.


\subsection{Limitations}
\label{sec:limitations}

\begin{enumerate}
\item The Gaussian$/r^2$ PK form [Eq.~(\ref{eq:Vpk})] is approximate.
  The exact Phillips--Kleinman pseudopotential is nonlocal and
  energy-dependent~\cite{pk1959}.  Our Gaussian approximation captures
  the dominant repulsion but not its angular or energy dependence.

\item Core--valence exchange integrals are omitted for LiH (the core
  and valence fibers have different channel structures).  For
  polyatomics, the full 1-RDM inter-fiber exchange reduces
  $R_{\rm eq}$ error to 11.7\% (Sec.~\ref{sec:outlook}).

\item Only $\sigma$ channels at $l_{\max} = 2$.  Paper~15 showed that
  $\pi$ channels add ${\sim}7$~percentage points for H$_2$; similar
  improvement is expected for LiH at $l_{\max} \geq 3$.

\item The dissociation limit is not converged at $R = 7$~bohr.
  $D_e$ values are upper bounds.

\item Only two-core plus two-valence systems.  Extension to more
  electrons requires composing additional Level~3/4 subproblems (e.g.,
  lone pairs as Level~3, additional bonds as Level~4).
\end{enumerate}


\subsection{Outlook: the composition pattern for larger molecules}
\label{sec:outlook}

The composed geometry generalizes:
\begin{itemize}
  \item \textbf{BeH$_2$:} 1~core (Be~$1s^2$) + 2~bond pairs (Level~4
    on each Be--H) + inter-bond coupling.
  \item \textbf{H$_2$O:} 1~core (O~$1s^2$) + 2~bond pairs (Level~4 on
    each O--H) + 2~lone pairs (Level~3 on O) + inter-pair coupling.
  \item \textbf{General:} partition electrons into cores (Level~3 per
    atom) + bond pairs (Level~4 per bond) + lone pairs (Level~3 on atoms).
    The molecule is a \emph{hypergraph} where each hypernode is a
    natural-geometry subproblem and each hyperedge is a typed coupling.
\end{itemize}

We tested LiH at $l_{\max} = 2$--$7$ with $l$-dependent PK
(applying the pseudopotential barrier only to $l = 0$ channels,
where the $1s$ core resides), expecting the $l_{\max}$
convergence pattern from Paper~15 (H$_2$) to reduce $R_{\rm eq}$
error.  The result is the opposite: $R_{\rm eq}$ diverges
monotonically from experiment.

\begin{center}
\begin{tabular}{lcccc}
\hline
$l_{\max}$ & $N_{\rm ch}$ & $R_{\rm eq}$ (bohr) & Error &
  $\Delta R_{\rm eq}$ \\
\hline
2 &  5 & 2.80 &  7.0\% & --- \\
3 &  8 & 3.02 &  0.0\% & $+0.21$ \\
4 & 13 & 3.42 & 13.5\% & $+0.41$ \\
5 & 18 & 3.47 & 15.2\% & $+0.05$ \\
6 & 25 & 3.56 & 18.1\% & $+0.09$ \\
7 & 32 & 3.64 & 20.7\% & $+0.08$ \\
\hline
\end{tabular}
\end{center}

\paragraph{Mechanism: differential angular correlation.}
The $l_{\max}$ divergence arises from \emph{differential angular
correlation}: higher-$l$ channels provide angular correlation energy
that preferentially stabilizes large-$R$ (diffuse) geometries over
small-$R$ (compact) geometries, shifting the PES minimum outward.
A diagnostic decomposition confirms this is entirely nuclear in
origin.  Removing all electron--electron off-diagonal coupling
while retaining the full nuclear coupling gives a ground-state
channel weight $w(0{,}0) = 0.243$ and 8~channels for 90\% of
the norm---massive spreading driven by the asymmetric nuclear
potential.  Conversely, retaining only the $e$--$e$ coupling
(diagonal nuclear) gives $w(0{,}0) = 0.9998$---the electron--electron
interaction produces no channel mixing.  The spreading is 100\%
nuclear.

\paragraph{Eigenvalue convergence at fixed geometry.}
At fixed internuclear geometry $(R, R_e)$, the angular eigenvalue
$\mu_0$ converges exponentially with $l_{\max}$ at rate
$\beta \approx 0.42$ per unit $l_{\max}$ (exponential fit
$R^2 = 0.997$).  The divergence of $R_{\rm eq}$ is therefore not a
failure of eigenvalue convergence but a differential effect: the
converged eigenvalue improves faster at large~$R$ than at
small~$R$, tilting the PES.  The overall drift rate is
$+0.168$~bohr per unit $l_{\max}$ (linear fit, $R^2 = 0.89$).

\paragraph{R-dependent pseudopotential scaling.}
\label{par:rdep_pk}
The self-consistent $l = 0$ content of the valence wavefunction
decreases with~$R$: at $l_{\max} = 4$, the $l = 0$ fraction drops
from 0.85 at $R = 2.0$~bohr to 0.33 at $R = 6.5$~bohr.  To
compensate, we scale the PK barrier strength with~$R$:
\begin{equation}
  w_{\rm PK}(R) = \delta_{l_i, 0} \times
    \min\!\bigl(\text{cap},\; R/R_{\rm ref}\bigr)\,,
  \label{eq:rdep_pk}
\end{equation}
where $R_{\rm ref}$ is a reference distance and the cap prevents
unbounded growth.  At $R < R_{\rm ref}$, the PK operates at
standard $l$-dependent strength; at $R > R_{\rm ref}$, it
strengthens to counteract the loss of effective core exclusion.

For LiH with $R_{\rm ref} = 3.015$~bohr and cap $= 1.5$:

\begin{center}
\begin{tabular}{llccc}
\hline
Mode & $l_{\max}$ & $R_{\rm eq}$ (bohr) & Error \\
\hline
$l$-dependent     & 4 & 3.42 & 13.5\% \\
$R$-dependent     & 4 & 3.08 &  2.0\% \\
Self-consistent   & 4 & 3.19 &  5.9\% \\
$l$-dependent     & 7 & 3.64 & 20.7\% \\
$R$-dependent     & 7 & 3.61 & 19.7\% \\
\hline
\end{tabular}
\end{center}

\noindent
The $R$-dependent scaling reduces $R_{\rm eq}$ error from 13.5\% to
2.0\% at $l_{\max} = 4$, but the advantage erodes at higher
$l_{\max}$: the asymptotic drift rates are $+0.168$ ($l$-dependent)
and $+0.160$ ($R$-dependent) bohr per unit $l_{\max}$ over the
range $l_{\max} = 2$--$7$.  Self-consistent PK (iteratively
adjusting the barrier strength based on the eigenstate's $l = 0$
content) achieves intermediate drift reduction (50\%).  The scaling
delays the onset of divergence but does not eliminate the asymptotic
drift, which reflects the fundamental limitation of the composed
geometry's static core--valence partition.

The reference distance $R_{\rm ref} = R_{\rm eq}^{\rm expt}$
introduces a non-ab-initio parameter.  In principle, $R_{\rm ref}$
is derivable from atomic properties: the PK barrier's characteristic
radius $r_{\rm PK} = 1/\sqrt{2B}$ and the valence orbital extent
define a natural length scale.  This derivation remains to be tested.

\paragraph{Root cause: adiabatic approximation with asymmetric charges.}
Subsequent diagnostics (v2.0.6) have traced the $l_{\max}$ divergence
to the adiabatic multichannel approximation interacting with
PK-induced angular symmetry breaking.  A bare HeH$^+$ Level~4
calculation---with no $Z_{\rm eff}$, no Phillips--Kleinman
pseudopotential, and no composition---exhibits the same qualitative
drift: $+0.262$~bohr per $l_{\max}$.  In composed LiH, where
$Z_A = Z_B = 1$ (symmetric), the PK barrier on atom~A breaks the
$A \leftrightarrow B$ symmetry, producing an effective heteronuclear
system with drift $+0.303$~bohr per $l_{\max}$.  The mechanism is
that asymmetric nuclear coupling populates odd-$l$ channels forbidden
in homonuclear systems; H$_2$ places 94\% of its channel weight in
the $(0{,}0)$ channel, while HeH$^+$ places only 68\%, with 20\% in
odd-$l$ channels that preferentially stabilize large-$R$ configurations.

Three alternative mitigation strategies were tested and found
insufficient.  (i)~An algebraic PK projector (rank-1
$|\psi_{\rm core}\rangle\langle\psi_{\rm core}|$) produces
drift $5.6\times$ worse than Gaussian PK ($+1.697$ vs $+0.303$
bohr/$l_{\max}$), because the valence wavefunction avoids the
core state in function space while still penetrating the core
region in coordinate space.  (ii)~Enhanced $Z_{\rm eff}$ with a
repulsive dip (PK-free) requires extreme parameters
($Z_{\rm eff}(0) = -38$) due to $1/r^2$ vs $1/r$ shape mismatch,
and the odd-$l$ channel population rises to 30.7\%---worse than
bare HeH$^+$.  (iii)~Single-channel DBOC correction of $+0.035$~Ha
is 97\% cancelled by off-diagonal $P$-matrix coupling in the
complete-basis limit, overcorrecting by $23\times$.

\paragraph{Path forward.}
The $l$-dependent pseudopotential reduces the divergence rate by
approximately $2.5\times$ relative to the channel-blind mode.
$R$-dependent scaling [Eq.~(\ref{eq:rdep_pk})] provides a further
factor of ${\sim}2$ improvement at moderate $l_{\max}$ but converges
to the same asymptotic drift rate at $l_{\max} \ge 5$.
None of these modifications eliminate the fundamental adiabatic
truncation error.  The variational 2D solver
(Paper~15~\cite{loutey_paper15}), which treats
$(R_e, \alpha)$ simultaneously rather than via adiabatic separation,
does not suffer from $l_{\max}$ truncation and is the identified
resolution.  Integration of the 2D solver into the composition
pipeline---contingent on reducing Level~4 iteration times---is the
next milestone.

Initial BeH$_2$ results validate the qualitative PES shape (bound state,
repulsive wall, correct dissociation limit) but reveal a 32\%
$R_{\rm eq}$ error with the block-diagonal approximation.  The
core-valence composition validated for LiH is insufficient for
valence-valence coupling between bond pairs sharing the Be nucleus:
$Z_{\mathrm{eff}}$ partitioning and classical inter-bond repulsion both
fail to improve accuracy.  Orbital-level inter-bond coupling (exchange
and orthogonalization between bond-pair wavefunctions) is the bottleneck
for quantitative polyatomic PES.  The Pauli term scaling
($Q^{2.5}$, Paper~14) is unaffected by this limitation, as
it depends on the block structure, not the inter-block coupling.

\subsubsection{Inter-fiber coupling investigation}

A systematic three-phase investigation of inter-fiber coupling confirms
that the channel overlap between bond-pair fibers is the key quantity
for polyatomic accuracy.

\paragraph{Monopole Coulomb coupling (negative result).}
The Slater $F^0$ integral between the two bond-pair densities,
transformed to Be-centered coordinates, gives a monopole inter-fiber
energy of ${\sim}1.6$~Ha that is nearly $R$-independent near
equilibrium.  Adding this scalar repulsion worsens $R_{\rm eq}$ from
32\% to 62\% error---the same failure mode as classical inter-bond
repulsion and $Z_{\rm eff}$ partitioning.

\paragraph{Inter-fiber channel overlap $S_{\rm avg}(R)$.}
The parity-weighted overlap between ground adiabatic channels of the
two fibers under $\pi$-rotation is
\begin{equation}
  S(\rho) \;=\; \sum_{l_1, l_2} (-1)^{l_1 + l_2}\,
  \bigl|c^{0}_{l_1 l_2}(\rho)\bigr|^2,
  \label{eq:S_overlap}
\end{equation}
where $c^{0}_{l_1 l_2}$ are the channel expansion coefficients
extracted from the angular eigenvector at each $\rho = R/(2R_e)$,
and $S_{\rm avg}(R)$ is the $|F(R_e)|^2$-weighted average over
the hyperradius.  This is a purely algebraic quantity---no spatial
integration is required.

$S_{\rm avg}$ has strong $R$-dependence: it drops from 0.47 at
$R = 2.0$~bohr to 0.24 at $R = 6.0$~bohr, with slope
$dS/dR = -0.16$ at $R_{\rm eq}$.  The physical origin is a shift
in channel composition: the $(0{,}0)$ $\sigma_s$ channel weight
drops from 61\% at short $R$ to 20\% at large $R$ as odd-parity
channels $(0{,}1)$ and $(1{,}0)$ grow.  Even-parity channels
contribute positively to $S$; odd-parity channels contribute
negatively.  The net effect is a monotonic decrease in $S$ as the
wavefunction redistributes angular momentum.

\paragraph{Exchange coupling via $S \cdot F^0$ (partial success).}
Combining the overlap and the monopole integral as
$E_{\rm exch}(R) = -S_{\rm avg}(R) \cdot F^0(R)$ reduces $R_{\rm eq}$
error from 31\% to 20\%.  The ab initio coupling captures ${\sim}40\%$
of the correction identified by a single-parameter fit
($K_{\rm eff} \approx 1.6$ vs $K_{\rm fit} = 4.08$~Ha).  The
remaining ${\sim}60\%$ is recovered by including the off-diagonal
1-RDM elements (see ``Full one-particle density matrix exchange''
below).

The inter-fiber channel overlap $S(R)$---a purely algebraic quantity
computed from angular eigenvector coefficients and parity
phases---captures the $R$-dependent coupling between bond-pair fibers.
This validates the fiber bundle framework for polyatomic molecules:
each bond pair keeps its own natural geometry, and the coupling between
fibers is mediated by quantum number overlap at the shared center.

\paragraph{Channel-decomposed $F^0$ and direct exchange.}
The monopole integral $F^0$ can be decomposed by angular channel,
giving channel-specific direct Coulomb integrals $F^0_{\rm ch}$.
A direct exchange formula
$E_{\rm direct} = -\sum_{\rm ch} (-1)^{l_1 + l_2} F^0_{\rm ch}$
avoids the $S \cdot F^0$ factorization and gives similar accuracy:
$R_{\rm eq}$ error of 20.0\% (vs 19.2\% for the $S \cdot F^0$ path).

\paragraph{Higher Slater multipoles (negative result).}
Including $k = 1$ (dipole) and $k = 2$ (quadrupole) multipoles in
the inter-fiber coupling does not recover the missing exchange.
The $k = 1$ term is \emph{repulsive} and worsens $R_{\rm eq}$;
$k = 2$ is negligibly small.  The total multipole correction
$k = 0 + 1 + 2$ gives 20.5\% $R_{\rm eq}$ error, slightly worse
than monopole alone (20.0\%).  This confirms that the missing
exchange comes from off-diagonal 1-RDM terms, not higher angular
multipoles.

\paragraph{Full one-particle density matrix exchange.}
The channel-resolved one-particle reduced density matrix
$\gamma^A_{l_1, l_1'}$ is obtained by tracing electron~2 from the
Level~4 ground-state eigenvector:
\begin{equation}
  \gamma^A_{l_1, l_1'}
    = \sum_{l_2} \sum_j v_{(l_1, l_2), j}\, v_{(l_1', l_2), j},
\end{equation}
where the sum runs over all channels sharing the same $l_2$ and
over the $\alpha$ grid, with the result $|F(R_e)|^2$-weighted
over the hyperradius.  The off-diagonal elements
$\gamma_{l_1 \ne l_1'}$ are 68--121\% of the diagonal norm
(growing with $R$ as channel mixing increases).

The full inter-fiber exchange between identical fibers $A$ and $B$
in the channel representation is
\begin{equation}
  K_{AB}(R) = -\sum_{l_1, l_1'}
    \bigl[\gamma^A_{l_1, l_1'}\bigr]^2\,
    (-1)^{l_1 + l_1'}\,
    F^0_{l_1, l_1'}(R),
  \label{eq:full_exchange}
\end{equation}
where $F^0_{l_1, l_1'}$ is the $l_1$-marginal Slater monopole
integral computed from Be-centered densities aggregated over $l_2$,
and the parity factor arises from $\gamma^B_{l_1', l_1}
= (-1)^{l_1 + l_1'} \gamma^A_{l_1', l_1}$ under the $\pi$-rotation
relating the two fibers.  The diagonal limit $l_1 = l_1'$ recovers a
quantity proportional to the existing $S \cdot F^0$ exchange; the
off-diagonal terms capture inter-channel exchange.

\begin{center}
\begin{tabular}{lcc}
\hline
Method & $R_{\rm eq}$ (bohr) & Error vs 2.507 \\
\hline
Block-diagonal (no coupling) & 3.28 & 31\% \\
Monopole $F^0$ (Phase~1)     & 4.06 & 62\% \\
Exchange $S \cdot F^0$       & 3.01 & 20\% \\
Full 1-RDM exchange [Eq.~(\ref{eq:full_exchange})] & 2.80 & 11.7\% \\
Fitted model ($-K \cdot S$)  & 2.81 & 12\% \\
\hline
\end{tabular}
\end{center}

The full 1-RDM exchange matches the single-parameter fitted model
with zero free parameters.  The off-diagonal terms are subtractive
(${\sim}10\%$ of the diagonal magnitude at $R_{\rm eq}$),
moderating the exchange and providing the correct $R$-dependence.
This confirms that the off-diagonal $\gamma$ elements---not
higher multipoles or kinetic corrections---carry the missing
exchange physics.

\paragraph{Kinetic orthogonalization (negative result).}
L\"{o}wdin symmetric orthogonalization of overlapping fiber
wavefunctions raises the kinetic energy by
\begin{equation}
  \Delta T(R) = \frac{1}{2} \sum_{l_1, l_1'}
    \bigl|S^{AB}_{l_1, l_1'}\bigr|^2\,
    \frac{T_{l_1} + T_{l_1'}}{2},
\end{equation}
where $S^{AB}_{l_1, l_1'} = (-1)^{l_1'} \gamma^A_{l_1, l_1'}$
and $T_{l_1} = l_1(l_1+1)/(2\langle R_e^2 \rangle)$ is the
centrifugal kinetic energy.  The correction is $+0.03$~Ha and
nearly $R$-independent (it peaks at $R \sim 4.0$ where $l \ge 1$
channel growth counteracts overlap decay).  Adding $\Delta T$ to
the full exchange does not shift $R_{\rm eq}$.  The residual
11.7\% error is attributed to basis truncation ($l_{\rm max} = 2$)
and the adiabatic approximation.

\paragraph{Transferability to core--valence exchange (LiH).}
The full 1-RDM exchange is specific to the bond--bond (Level~4 +
Level~4) topology of polyatomics like BeH$_2$.  In LiH, the two
fibers are the Level~3 core (atom-centered hyperspherical) and
the Level~4 valence (molecule-frame hyperspherical)---fundamentally
different channel structures that cannot share $\gamma$ matrices.
The PK pseudopotential already encodes core--valence orthogonality,
so explicit exchange between these fibers is expected to be
partially redundant.  Extending the 1-RDM exchange to heterogeneous
fiber pairs would require a cross-level overlap formalism mapping
Level~3 angular channels onto Level~4 channels, which is deferred
to future work.

\paragraph{Path forward.}
The full 1-RDM exchange closes the gap between the diagonal
$S \cdot F^0$ approximation and the fitted model.  The remaining
11.7\% $R_{\rm eq}$ error points to three directions: (a)~$l_{\rm max}$
convergence with full exchange (current results use $l_{\rm max} = 2$),
(b)~non-adiabatic corrections (DBOC), and (c)~cusp corrections at the
coalescence point.  Kinetic orthogonalization has been tested and found
negligible.  Self-consistent Hartree iteration is deprioritized, as
the kinetic correction is uniform and SCF is unlikely to provide
differential $R$-dependence.

\paragraph{H$_2$O: first triatomic PES.}
The composed geometry extends to H$_2$O as a five-block decomposition:
O~$1s^2$ core (Level~3, $Z=8$), two O--H bond pairs (Level~4 with
charge-center origin, $Z_{\rm eff}=6$, $Z_B=1$), and two lone pairs
(Level~3, $Z_{\rm eff}=6$).  The architecture introduces no free
parameters.  Inter-fiber coupling at the H--O--H bond angle
$\theta = 104.5^\circ$ generalizes the linear-molecule rotation
$(-1)^{l_1 + l_2}$ to Wigner $d$-matrix phases
$P_{l_1}(\cos\theta) \cdot P_{l_2}(\cos\theta)$, recovering the
linear formula at $\theta = \pi$.  Six coupling pairs arise:
one bond--bond, four bond--lone, and one lone--lone.

The uncoupled PES with charge-center origin gives $R_{\rm eq} = 1.34$~bohr
(26\% error vs 1.809 experimental), with the correct qualitative shape:
repulsive wall, well-defined minimum, and smooth dissociation.  The
bond--bond coupling (${\sim}0.5$~Ha) is consistent with BeH$_2$ and
barely affects $R_{\rm eq}$.  However, the bond--lone and lone--lone
couplings are unphysical: the $S \cdot F^0$ factorization produces
$-28$~Ha (bond--lone, 4~pairs) and $-15$~Ha (lone--lone) at the
experimental geometry---magnitudes that exceed the total electronic
energy.  The Slater integrals scale as ${\sim}Z_{\rm eff}$, and at
$Z_{\rm eff} = 6$ the compact lone pair densities drive $F^0$ far
beyond the regime validated on BeH$_2$ ($Z_{\rm eff} = 2$).  Lone pair
coupling is disabled for production use; only bond--bond coupling is
validated.

The dominant bottleneck is the Level~4 angular basis at high charge
asymmetry ($Z_A/Z_B = 6{:}1$ for O--H bonds).  The bare bond pair
$R_{\rm eq}$ error scales from 0.1\% at 1:1 (H$_2$) to 18\% at 2:1
(BeH) to 56\% at 6:1 with midpoint origin; the charge-center origin
$z_0 = R(Z_A - Z_B)/[2(Z_A + Z_B)]$ reduces the 6:1 error to 17\%,
but does not fully resolve the basis limitation at $l_{\rm max} = 2$
with 9~channels.  Improved angular basis convergence for asymmetric
bonds---via non-uniform grids or adaptive channel selection---is
the path to quantitative H$_2$O accuracy.


%% ========================================================================
%% VI. CONCLUSION
%% ========================================================================
\section{Conclusion}
\label{sec:conclusion}

Composed natural geometries solve the core-valence problem without a
single high-dimensional coordinate system.  The key results:

\begin{enumerate}
\item LiH $R_{\rm eq}$ improves from 17\% error (LCAO) to 5.3\%
  (composed, ab initio PK, $l$-dependent) with zero molecular fitting.

\item The ab initio PK pseudopotential is derived entirely from the
  core wavefunction: $A$ from the core--valence energy gap
  [Eq.~(\ref{eq:A})], $B$ from the $\langle 1/r^2 \rangle$-weighted
  core radius [Eq.~(\ref{eq:reff})].

\item The architecture transfers to BeH$^+$ with no per-molecule
  tuning.

\item The composition pattern---core graphs + valence graphs + typed
  coupling edges---provides a concrete framework for extending discrete
  graph quantum chemistry to general molecules.

\item For polyatomics (BeH$_2$), the full 1-RDM inter-fiber exchange
  [Eq.~(\ref{eq:full_exchange})] reduces $R_{\rm eq}$ error from
  20\% (diagonal $S \cdot F^0$) to 11.7\%, matching a single-parameter
  fitted model (12\%) with zero free parameters.

\item The $l_{\max}$ divergence for asymmetric bonds arises from
  differential angular correlation: higher-$l$ channels preferentially
  stabilize large-$R$ geometries.  The channel spreading is entirely
  nuclear in origin, with zero contribution from electron--electron
  correlation.  $R$-dependent PK scaling
  [Eq.~(\ref{eq:rdep_pk})] reduces $R_{\rm eq}$ error from 13.5\%
  to 2.0\% at $l_{\max} = 4$ for LiH, though the asymptotic drift
  rate is unchanged.  Full 4-electron Level~4 treatment, which
  eliminates the pseudopotential entirely, remains the
  architecturally clean resolution.
\end{enumerate}

The natural geometry hierarchy is now:
\begin{center}
\begin{tabular}{cccc}
\toprule
Level & System & Geometry & Best result \\
\midrule
1 & H       & $S^3$ (Fock)           & $<0.1\%$ error \\
2 & H$_2^+$ & Prolate spheroid       & 0.70\% error \\
3 & He      & Hyperspherical         & 0.05\% error \\
4 & H$_2$   & Mol-frame hypersp.     & 94.1\% $D_e$ \\
5 & LiH     & Composed (Level 3+4)   & $R_{\rm eq}$: 5.3\% error \\
5 & BeH$^+$ & Composed (Level 3+4)   & Bound, physical \\
5 & BeH$_2$ & Composed (Level 3+4+4) & $R_{\rm eq}$: 11.7\% error \\
\bottomrule
\end{tabular}
\end{center}


%% ========================================================================
%% REFERENCES
%% ========================================================================
\begin{thebibliography}{25}

\bibitem{fock1935}
V.~A.~Fock,
``Zur Theorie des Wasserstoffatoms,''
Z.~Phys.\ \textbf{98}, 145 (1935).

\bibitem{pk1959}
J.~C.~Phillips and L.~Kleinman,
``New method for calculating wave functions in crystals and molecules,''
Phys.\ Rev.\ \textbf{116}, 287 (1959).

\bibitem{lin1995}
C.~D.~Lin,
``Hyperspherical coordinate approach to atomic and other
Coulombic three-body systems,''
Phys.\ Rep.\ \textbf{257}, 1 (1995).

\bibitem{huber1979}
K.~P.~Huber and G.~Herzberg,
\emph{Molecular Spectra and Molecular Structure.\ IV.\ Constants of
Diatomic Molecules}
(Van Nostrand Reinhold, New York, 1979).

\bibitem{nist}
A.~Kramida, Yu.~Ralchenko, J.~Reader, and NIST ASD Team,
NIST Atomic Spectra Database (ver.~5.11),
\url{https://physics.nist.gov/asd} (2024).

\bibitem{heine1970}
V.~Heine and D.~Weaire,
``Pseudopotential theory of cohesion and structure,''
Solid State Phys.\ \textbf{24}, 249 (1970).

\bibitem{bachelet1982}
G.~B.~Bachelet, D.~R.~Hamann, and M.~Schl\"uter,
``Pseudopotentials that work: From H to Pu,''
Phys.\ Rev.\ B \textbf{26}, 4199 (1982).

\bibitem{bishop1979}
D.~M.~Bishop and L.~M.~Cheung,
``A theoretical investigation of HeH$^+$,''
J.~Mol.\ Spectrosc.\ \textbf{75}, 462 (1979).

\bibitem{paper0}
J.~Loutey,
``Geometric Packing and the Universal Constant''
(Paper~0 in the Geometric Vacuum series).

\bibitem{paper1}
J.~Loutey,
``Spectral Graph Theory for Atomic Structure''
(Paper~1 in the Geometric Vacuum series).

\bibitem{paper7}
J.~Loutey,
``The Dimensionless Vacuum: Scale-Invariant Graph Topology
and the Schr\"odinger Equation''
(Paper~7 in the Geometric Vacuum series).

\bibitem{paper10}
J.~Loutey,
``Nuclear Lattice: Rovibrational Spectra from SU(2) Algebraic
Chains'' (Paper~10 in the Geometric Vacuum series).

\bibitem{paper11}
J.~Loutey,
``Molecular Fock Projection: Prolate Spheroidal Lattice
for Diatomic Molecules''
(Paper~11 in the Geometric Vacuum series).

\bibitem{paper12}
J.~Loutey,
``Algebraic Two-Electron Integrals: Neumann Expansion
for $V_{ee}$ on the Prolate Spheroidal Lattice''
(Paper~12 in the Geometric Vacuum series).

\bibitem{paper13}
J.~Loutey,
``Hyperspherical Lattice: Two-Electron Atoms as
Coupled-Channel Graphs''
(Paper~13 in the Geometric Vacuum series).

\bibitem{paper15}
J.~Loutey,
``The Level~4 Natural Geometry: Two-Center Two-Electron Molecules
as Hyperspherical Fiber Bundles''
(Paper~15 in the Geometric Vacuum series).

\bibitem{paper16}
J.~Loutey,
``Chemical Periodicity from $S_N$ Representation Theory''
(Paper~16 in the Geometric Vacuum series).

\bibitem{fci_a}
J.~Loutey,
``Full Configuration Interaction on the Geometric Lattice: Atoms''
(FCI-A paper in the Geometric Vacuum series).

\bibitem{fci_m}
J.~Loutey,
``Full Configuration Interaction on the Geometric Lattice: Molecules''
(FCI-M paper in the Geometric Vacuum series).

\bibitem{geovac2026}
J.~Loutey,
``GeoVac: Computational Quantum Chemistry via Spectral Graph Theory,''
version 1.6.1 (2026),
\url{https://github.com/jloutey-hash/geovac}.

\end{thebibliography}

\end{document}
