\documentclass[aps,prl,reprint,amsmath,amssymb]{revtex4-2}

\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{braket}
\usepackage{hyperref}

\begin{document}

\title{Angular Momentum as Information Geometry:\\Isotropic Packing and the Universal Angular Cross-Section}

\author{J.~Loutey}
\affiliation{Independent Researcher, Kent, Washington}

\date{February 22, 2026}

\begin{abstract}
We show that the angular momentum quantum numbers $(\ell, m)$ emerge
from a purely geometric construction: uniform-density packing of
distinguishable states on concentric isotropic shells in two
dimensions.  Starting from two axioms---discrete binary
distinguishability and geometric indifference (maximum entropy)---the
construction yields shell capacities $2k-1$ for shell~$k$, which is
isomorphic to the spherical harmonic basis $Y_{\ell m}$ with
$\ell = k - 1$ and $m = -\ell, \ldots, +\ell$.  The principal quantum
number~$n$ corresponds to a cumulative grouping of the first~$n$
shells, producing the $n^2$ orbital count, but this grouping is not
forced by the axioms alone.  Similarly, a factor of~2 arises from the
orientability of the compactified packing manifold ($S^2$),
corresponding to spin multiplicity.  When the packing is interpreted
as a graph, its Laplacian decomposes into $(\ell, m)$ sectors that
spectrally converge to the hydrogen eigenvalues, as shown in
subsequent papers.  This angular cross-section recurs as a universal
structural factor inside every natural geometry developed in the
Geometric Vacuum series---from $S^3$ for atoms through composed fiber
bundles for multi-electron molecules---making it the foundational
motif of the framework.  This is Paper~0 in the series.
\end{abstract}

\maketitle

%% ================================================================
%%  I.  INTRODUCTION
%% ================================================================
\section{Introduction}
\label{sec:introduction}

The hydrogen atom possesses $n^2$ orbital states per principal quantum
number~$n$, each labeled by angular momentum
$\ell = 0, 1, \ldots, n-1$ and magnetic quantum number
$m = -\ell, \ldots, +\ell$, with a spin multiplicity of~2 giving
$2n^2$ states total.  The standard derivation obtains these labels
from the eigenvalue structure of the angular momentum operators
$\hat{L}^2$ and $\hat{L}_z$ acting on the Hilbert space of the
Schr\"odinger equation.  Here we ask: to what extent can this quantum
number structure be recovered from geometry alone, without invoking
operators, Hilbert spaces, or the eigenvalue equation?

We present a construction based on uniform-density packing of
distinguishable states on concentric isotropic shells in two
dimensions.  The construction rests on two axioms:
(i)~a minimum of two distinguishable states is required to define a
metric (binary distinguishability), and (ii)~in the absence of
external constraints, the distribution of states must maximize
entropy, enforcing isotropy (geometric indifference).  These axioms,
together with the natural choices of concentric shells and
area-proportional state counting, produce the following results at
three distinct levels of strength.

\medskip

\noindent\textbf{Strong claim: angular quantum numbers.}  Shell~$k$
has capacity $2k - 1$, which is isomorphic to the spherical harmonic
basis $Y_{\ell m}$ with $\ell = k - 1$.  The angular momentum labels
$(\ell, m)$ and the per-shell degeneracy $2\ell + 1$ emerge directly
from the packing.  This is the central, mathematically rigorous result
of the paper.

\medskip

\noindent\textbf{Structural correspondences.}  The principal quantum
number~$n$ arises when one groups the first $n$ shells cumulatively,
yielding the count $\sum_{k=1}^{n}(2k-1) = n^2$.  This grouping is
natural but not uniquely forced by the axioms.  The factor of~2 (spin
multiplicity) arises from the orientability of the compactified
packing manifold: conformally compactifying the plane to $S^2$
introduces two orientations, corresponding to a $\mathbb{Z}_2$
doubling.  The identification of this doubling with
spin-$\tfrac{1}{2}$ is a structural correspondence, not a derivation
from the axioms.

\medskip

\noindent\textbf{Series significance.}  The $(\ell, m)$ angular
sector constructed here recurs as a universal structural factor inside
every natural geometry developed in the Geometric Vacuum (GeoVac)
series: $S^3$ for hydrogen~\cite{paper7}, prolate spheroidal
coordinates for H$_2^+$~\cite{paper11}, hyperspherical coordinates for
He~\cite{paper13}, molecule-frame hyperspherical coordinates for
H$_2$~\cite{paper15}, and composed fiber bundles for
LiH~\cite{paper17}.  In each case, the full geometry separates into a
system-specific radial or hyperradial part and a universal angular
cross-section whose structure is precisely the packing derived here.
This universality is the reason the packing construction is
foundational to the series rather than merely a curiosity about
hydrogen.

\medskip

Several elements of this work connect to well-established results.
The counting $\sum_{\ell=0}^{n-1}(2\ell+1) = n^2$ is standard SO(3)
representation theory.  The relationship between hydrogen's
``accidental'' degeneracy and the geometry of~$S^3$ was established by
Fock~\cite{fock1935} and Bargmann~\cite{bargmann1936}.  What is new
here is the specific packing algorithm that produces the $(\ell, m)$
labeling from geometric--combinatorial reasoning independent of the
operator formalism, and the observation that this angular sector is
the universal fiber across the GeoVac natural geometries.

The paper is organized as follows.
Section~\ref{sec:construction} presents the packing algorithm.
Section~\ref{sec:angular} establishes the isomorphism between shell
capacity and the spherical harmonic basis.
Section~\ref{sec:correspondences} discusses the structural
correspondences for~$n$ and spin.
Section~\ref{sec:cross-section} shows how the angular cross-section
recurs across the GeoVac natural geometries.
Section~\ref{sec:graph} constructs the graph topology and connects it
to the spectral results of later papers.
Sections~\ref{sec:scope} and~\ref{sec:discussion} address scope,
limitations, and context.


%% ================================================================
%%  II.  THE PACKING CONSTRUCTION
%% ================================================================
\section{The Packing Construction}
\label{sec:construction}

\subsection{Axioms}

The construction rests on two axioms, which contain no reference to
quantum mechanics, operators, wavefunctions, or physical observables.

\medskip

\noindent\textbf{Axiom 1 (Binary Distinguishability).}
To define a metric space, a minimum of two distinguishable states
($N_{\mathrm{init}} = 2$) is required to establish a non-zero
fundamental scale~$d_0$.  A single point cannot define a distance; two
points create the first bit of spatial information.

\textit{Note:} The choice $N_{\mathrm{init}} = 2$ is the minimal
non-trivial initialization.  It is the simplest choice consistent with
this axiom, but not the only one; initializing with $N_{\mathrm{init}} = 3$
or more points would define a different fundamental area and modify the
downstream counting.

\medskip

\noindent\textbf{Axiom 2 (Geometric Indifference).}
In the absence of external constraints or privileged directions, the
distribution of states must maximize entropy.  By the Principle of
Indifference, this necessitates isotropy: states populate isotropic
shells (circles) rather than anisotropic tilings (squares, hexagons),
which would imply privileged directions not present in the axioms.

\textit{Note:} Isotropy motivates circular shells over anisotropic
tilings, but uniform-density packing on concentric circles is one of
several ways to implement isotropy---for instance, hexagonal
close-packing achieves higher packing density while preserving
six-fold symmetry.  Concentric shells with area-proportional counting
is the simplest realization consistent with the axioms, not the only
one.

\medskip

These axioms, together with the specific choices of concentric
circular shells, area-proportional counting, and binary initialization,
constitute the full set of assumptions.  The axioms motivate these
choices but do not uniquely determine them.  What is remarkable is that
this particular realization---arguably the simplest one consistent with
the axioms---produces exactly the angular momentum quantum numbers.

\subsection{Algorithm}

\noindent\textbf{Step 1.}  Place $N_{\mathrm{init}} = 2$ points on an
isotropic shell of radius $r_1 = d_0$, separated by the fundamental
distance~$d_0$.

\textit{Rationale:} Two points are the minimum needed to define a
distance (Axiom~1).  Isotropy requires a circular shell (Axiom~2).
This fixes both $d_0$ and the fundamental area per state
$\sigma_0 = \pi d_0^2 / 2$.

\medskip

\noindent\textbf{Step 2.}  Add concentric isotropic shell~$k$ at
radius $r_k = k \cdot d_0$.

\medskip

\noindent\textbf{Step 3.}  Determine the state count~$N_k$ on
shell~$k$ from uniform information density.  The annular area between
shells $k-1$ and $k$ is
\begin{equation}
  A_k = \pi r_k^2 - \pi r_{k-1}^2
      = \pi d_0^2 \bigl[k^2 - (k-1)^2\bigr]
      = \pi d_0^2 (2k - 1) \,.
  \label{eq:annular-area}
\end{equation}
Dividing by the fundamental area gives the state count:
\begin{equation}
  N_k = \frac{A_k}{\sigma_0}
      = \frac{\pi d_0^2 (2k-1)}{\pi d_0^2 / 2}
      = 2(2k - 1) \,.
  \label{eq:Nk}
\end{equation}

\noindent\textbf{Step 4.}  Repeat for $k = 1, 2, 3, \ldots$

\subsection{Resulting structure}

The construction yields the distribution shown in
Table~\ref{tab:packing}.

\begin{table}[h]
\centering
\begin{tabular}{ccc}
\toprule
Shell $k$ & States $N_k = 2(2k-1)$ & Cumulative $\sum_{i=1}^{k} N_i$ \\
\midrule
1 & 2  & 2  \\
2 & 6  & 8  \\
3 & 10 & 18 \\
4 & 14 & 32 \\
5 & 18 & 50 \\
$\vdots$ & $\vdots$ & $\vdots$ \\
$k$ & $2(2k-1)$ & $2k^2$ \\
\bottomrule
\end{tabular}
\caption{State distribution on isotropic shells.  Each shell~$k$
  carries $2(2k-1)$ states; the cumulative count through shell~$k$ is
  $2k^2$.}
\label{tab:packing}
\end{table}

Two features of this table merit immediate comment.  First, the
per-shell count $2(2k-1)$ factorizes as $2 \times (2k-1)$, where the
factor $2k-1$ is an odd integer determined entirely by the area
formula.  Second, the cumulative count $2k^2$ matches the hydrogen
degeneracy $2n^2$ if one identifies $k = n$.  These observations are
analyzed in the next two sections at appropriately different levels of
strength.


%% ================================================================
%%  III.  ANGULAR QUANTUM NUMBERS FROM UNIFORM DENSITY
%% ================================================================
\section{Angular Quantum Numbers from Uniform Density}
\label{sec:angular}

This section contains the central result of the paper: the per-shell
state count from the packing construction is isomorphic to the angular
momentum labeling $(\ell, m)$.

\subsection{The angular capacity of shell $k$}

The factor of $2(2k-1)$ in Eq.~\eqref{eq:Nk} factorizes into a
global factor of~2---whose origin in the initialization condition and
manifold orientability is analyzed in
Sec.~\ref{sec:correspondences}---and an angular capacity per shell:
\begin{equation}
  N_k^{\mathrm{angular}} = 2k - 1
  \label{eq:angular-capacity}
\end{equation}
distinct angular slots.

\subsection{Isomorphism with spherical harmonics}

The spherical harmonics $Y_{\ell m}(\theta, \phi)$ for a given~$\ell$
have $2\ell + 1$ independent components labeled by
$m = -\ell, -\ell+1, \ldots, +\ell$.  Under the identification
\begin{equation}
  \ell = k - 1 \,,
  \label{eq:ell-k}
\end{equation}
the angular capacity of shell~$k$ becomes
\begin{equation}
  N_k^{\mathrm{angular}} = 2(k-1) + 1 = 2\ell + 1 \,,
  \label{eq:2ell-plus-1}
\end{equation}
which is precisely the dimension of the spin-$\ell$ irreducible
representation of SO(3).  The $2k-1$ angular positions on shell~$k$
are in one-to-one correspondence with the magnetic quantum numbers
$m = -\ell, \ldots, +\ell$.

This is not a coincidence that must be checked case by case: it is an
algebraic identity.  The area formula
(Eq.~\ref{eq:annular-area}) forces the annular area of shell~$k$ to
be proportional to $2k-1$, which is the dimension of the
$(k{-}1)$-th irreducible representation of SO(3).  The packing
construction therefore generates the complete angular momentum basis
$\{(\ell, m) : 0 \leq \ell, \; -\ell \leq m \leq \ell\}$ as a direct
consequence of uniform density on isotropic shells.

\subsection{What the construction produces}

To be precise about the scope of this result:

\begin{itemize}
\item The construction produces the \emph{labeling} $(\ell, m)$ and
  the \emph{degeneracy} $2\ell + 1$ per shell.  These are the angular
  quantum numbers.

\item It does \emph{not} produce the functional form of the spherical
  harmonics, the eigenvalue $\ell(\ell+1)$ of $\hat{L}^2$, or the
  commutation relations of angular momentum operators.  Those require
  additional structure (the graph Laplacian and its continuum limit),
  developed in Papers~1 and~7.

\item The result is \emph{independent} of any specific physical
  system.  The angular labeling emerges from 2D isotropic geometry,
  not from the hydrogen atom.  Hydrogen merely happens to use this
  same angular sector---as do all rotationally symmetric quantum
  systems.
\end{itemize}


%% ================================================================
%%  IV.  STRUCTURAL CORRESPONDENCES
%% ================================================================
\section{Structural Correspondences: $n$, Spin, and $2n^2$}
\label{sec:correspondences}

The angular quantum numbers $(\ell, m)$ emerge directly from the
packing (Sec.~\ref{sec:angular}).  The principal quantum number~$n$
and the spin factor of~2 involve additional identifications that are
natural and mathematically grounded but not uniquely forced by the two
axioms.  We present them here as structural correspondences.

\subsection{The principal quantum number as cumulative grouping}

If one groups the first $n$ shells cumulatively, the total angular
state count is
\begin{equation}
  \sum_{k=1}^{n} (2k - 1) = n^2 \,,
  \label{eq:n-squared}
\end{equation}
which matches the orbital degeneracy of hydrogen's $n$-th principal
shell: $\sum_{\ell=0}^{n-1}(2\ell+1) = n^2$.  Including the spin
factor gives $2n^2$.

This grouping is natural---the shells are concentrically ordered, so
cumulative counting is the simplest aggregation---but the axioms do
not \emph{require} that shells be grouped this way.  The packing
generates an infinite sequence of shells; the decision to collect the
first~$n$ of them into a single principal shell is an additional
structural choice that corresponds to, but is not derived from, the
axioms.

\subsection{The factor of 2 and orientability}

The per-shell count $N_k = 2(2k-1)$ contains a factor of~2 that
traces back to two sources:

\begin{enumerate}
\item \textbf{Initialization.}  Axiom~1 places
  $N_{\mathrm{init}} = 2$ states on the first shell, fixing the
  fundamental area $\sigma_0 = \pi d_0^2 / 2$.  This factor of~2
  propagates through all subsequent shells via the uniform-density
  condition.

\item \textbf{Orientability.}  When the flat packing plane is
  conformally compactified to the Riemann sphere
  $S^2 \cong \mathbb{C}^*$, the resulting manifold is orientable: it
  admits two distinct normal directions (inward and outward).  This
  orientability provides a natural $\mathbb{Z}_2$ doubling of the
  state space.  Mathematically, tracking this orientation lifts the
  symmetry group from SO(3) to its double cover SU(2).
\end{enumerate}

The identification of this $\mathbb{Z}_2$ doubling with the
spin-$\tfrac{1}{2}$ degree of freedom is consistent with the
mathematical structure: orientability on $S^2$ and spinor
representations of SU(2) both produce a factor of~2.  However, the
packing construction does not derive the spin angular momentum algebra
$[\hat{S}_i, \hat{S}_j] = i\epsilon_{ijk}\hat{S}_k$ or the
eigenvalue $s(s+1)$.  The correspondence is between the \emph{counting}
(a factor of~2) and spin \emph{multiplicity} ($2s+1 = 2$ for
$s = 1/2$), not between the construction and the full spinor
formalism.

\subsection{A remark on the axioms}

The construction follows from the two axioms together with several
additional structural choices: concentric shells with linearly spaced
radii ($r_k = k d_0$), area-proportional state counting, and the
specific fundamental area $\sigma_0 = \pi d_0^2 / 2$ fixed by the
initialization.  These choices are natural and mutually
consistent---they are arguably the simplest possibilities compatible
with the axioms---but they are not uniquely determined by the axioms
alone.  The axioms constrain the construction; they do not uniquely
fix every detail of it.

This distinction matters for the epistemic status of the results.  The
angular quantum numbers $(\ell, m)$ follow from any isotropic,
uniform-density, concentric construction---a robust class.  The
specific identification of~$n$ and the factor of~2 depend on the
particular choices above.


%% ================================================================
%%  V.  UNIVERSAL ANGULAR CROSS-SECTION
%% ================================================================
\section{The Packing as Universal Angular Cross-Section}
\label{sec:cross-section}

The packing construction of Sec.~\ref{sec:construction} produces a
universal $(\ell, m)$ angular labeling.  In the subsequent papers of
the GeoVac series, this same angular sector appears as a structural
factor inside every natural geometry used for quantum chemistry
calculations.  The full geometry of each system separates into a
system-specific radial (or hyperradial) coordinate and the universal
angular cross-section derived here.

Table~\ref{tab:cross-section} summarizes the hierarchy.

\begin{table}[h]
\centering
\begin{tabular}{cllll}
\toprule
Level & System & Full Geometry & Angular Cross-Section & Ref.\ \\
\midrule
1 & H (1-center, 1$e$)
  & $S^3$ (Fock projection)
  & $Y_{\ell m}$ on $S^2 \subset S^3$
  & \cite{paper7} \\
2 & H$_2^+$ (2-center, 1$e$)
  & Prolate spheroidal
  & $m$ exact; $\ell$-like index from $\eta$-separation
  & \cite{paper11} \\
3 & He (1-center, 2$e$)
  & Hyperspherical
  & $Y_{\ell m}$ per electron in fiber
  & \cite{paper13} \\
4 & H$_2$ (2-center, 2$e$)
  & Mol-frame hyperspherical
  & $Y_{\ell m}$ angular channels
  & \cite{paper15} \\
5 & LiH (core + valence)
  & Composed fiber bundle
  & $Y_{\ell m}$ per electron group
  & \cite{paper17} \\
\bottomrule
\end{tabular}
\caption{The $(\ell, m)$ angular cross-section inside each natural
  geometry of the GeoVac series.  In every case, the full coordinate
  system separates into a system-specific radial part and the
  universal angular labeling constructed in this paper.}
\label{tab:cross-section}
\end{table}

\textbf{Level~1: Hydrogen on $S^3$.}
Fock's 1935 stereographic projection~\cite{fock1935} maps the hydrogen
momentum-space problem onto the three-sphere~$S^3$.  The eigenstates
of the Laplace--Beltrami operator on $S^3$ are hyperspherical
harmonics, which decompose as $Y_{n\ell m} = R_n(\chi) \,
Y_{\ell m}(\theta, \phi)$.  The angular factor $Y_{\ell m}$ is
precisely the per-shell structure of the packing, with $\ell = k - 1$.
Paper~7~\cite{paper7} shows that the graph Laplacian on the $2n^2$
packing is conformally equivalent to this $S^3$ operator.

\textbf{Level~2: H$_2^+$ on prolate spheroids.}
For one-electron diatomics, the natural geometry is the prolate
spheroidal coordinate system $(\xi, \eta, \phi)$, in which the
Schr\"odinger equation separates.  The azimuthal quantum number~$m$
survives exactly as the quantum number of the $\phi$-equation
($e^{im\phi}$), directly inheriting the packing's angular slot
labeling.  The quantum number~$\ell$ is no longer exactly conserved in
the two-center problem: it is replaced by a separation parameter from
the $\eta$-equation that reduces to~$\ell$ in the united-atom limit.
The angular structure is recognizably descended from the $(\ell, m)$
packing---$m$ is exact, and the $\ell$-like index organizes the
$\eta$-eigenstates into the same degeneracy pattern---even though the
two-center potential breaks the full SO(3) symmetry to axial SO(2).
Paper~11~\cite{paper11} constructs a discrete lattice in these
coordinates.

\textbf{Level~3: Helium in hyperspherical coordinates.}
For two-electron atoms, the six-dimensional configuration space is
parameterized by a hyperradius~$R$ and five angles.  The angular
eigenstates decompose into single-electron angular momenta
$(\ell_1, m_1)$ and $(\ell_2, m_2)$, each carrying the per-shell
structure of the packing.  Paper~13~\cite{paper13} implements this as
a fiber bundle: the base space is the hyperradius, and the fiber is
the angular manifold.

\textbf{Level~4: H$_2$ in molecule-frame hyperspherical coordinates.}
For two-electron diatomics, the geometry combines the molecular axis
(internuclear separation~$R$) with the hyperspherical treatment of the
two electrons.  The angular channels are labeled by $(\ell, m)$
quantum numbers that determine the multichannel expansion.
Paper~15~\cite{paper15} recovers 94.1\% of the H$_2$ dissociation
energy using this geometry.

\textbf{Level~5: LiH via composed geometries.}
For core--valence systems, the total geometry is a fiber bundle
$G_{\mathrm{total}} = G_{\mathrm{nuc}} \rtimes G_{\mathrm{core}}(R)
\rtimes G_{\mathrm{val}}(R)$, where each electron group occupies its
own natural geometry.  The angular labeling $(\ell, m)$ appears
independently in each fiber.  Paper~17~\cite{paper17} applies this to
LiH and BeH$^+$.

\medskip

The invariance of the $(\ell, m)$ angular sector across all five
levels is not imposed by hand: it is a consequence of rotational
symmetry, which is present in every geometry that admits separation of
variables.  The packing construction provides the combinatorial
substrate for this universal angular factor.

\subsection{The node structure as combinatorial invariant}
\label{sec:combinatorial_invariant}

The preceding survey reveals a structural feature that merits explicit
comment.  The same discrete quantum number skeleton
$\{(\ell, m) : 0 \leq \ell, \; -\ell \leq m \leq \ell\}$---with its
degeneracy $2\ell + 1$ and selection rules---admits multiple conformally
distinct continuum embeddings.  The five geometries catalogued in
Table~\ref{tab:cross-section} are different Riemannian manifolds with
different metrics, curvatures, and coordinate singularity structures.
$S^3$ is compact with constant positive curvature; prolate spheroidal
coordinates are non-compact with coordinate singularities at the foci;
the hyperspherical manifold $S^5$ is compact but six-dimensional (for two electrons); the
composed fiber bundle is a product of manifolds with different
dimensionalities at each level.  Yet all of them share a common
combinatorial core: the $(\ell, m)$ node structure with its labeling,
degeneracies, and angular momentum coupling rules.

This inverts a standard universality argument familiar from statistical
mechanics and lattice field theory, where many different lattice
discretizations (square, triangular, hexagonal) flow under
renormalization to the same continuum field theory.  The standard
conclusion is that the continuum description is fundamental and the
lattice is an approximation.  Here the relationship runs in the
opposite direction: one discrete node structure admits many continuum
realizations, none of which is privileged.  The lattice is the
invariant; the continuum geometries are projections.

We state this as a mathematical observation, not a metaphysical claim.
The conformal equivalences between the graph Laplacian and each
continuum operator are proven case by case: Paper~7~\cite{paper7}
provides 18~symbolic proofs for the $S^3$ embedding, and the subsequent
papers verify operator convergence for each geometry in the hierarchy.
The framework is demonstrably conformally equivalent to standard
continuous quantum mechanics at every level where it has been tested.
Whether one regards the discrete or continuum description as more
fundamental is a choice of interpretation, not a consequence of the
mathematics.

An analogy to isospectral manifolds is apt.  Kac's celebrated
question---``Can one hear the shape of a drum?''---established that
different Riemannian geometries can share spectral data (the answer, as
Gordon, Webb, and Wolpert showed, is no: non-isometric manifolds can be
isospectral).  The present result is stronger in a specific sense:
the geometries in Table~\ref{tab:cross-section} share not merely a
spectrum but an entire labeled node structure, complete with quantum
number assignments, per-shell degeneracies, and angular momentum
selection rules.  The combinatorial content that is shared across these
embeddings is richer than a list of eigenvalues.


%% ================================================================
%%  VI.  GRAPH TOPOLOGY AND THE BRIDGE TO DYNAMICS
%% ================================================================
\section{Graph Topology and the Bridge to Dynamics}
\label{sec:graph}

\subsection{Vertex set}

The packing defines a graph $G = (V, E)$ with vertex set
\begin{equation}
  V = \bigl\{(n, \ell, m, s) : 1 \leq n \leq n_{\max},\;
      0 \leq \ell < n,\;
      -\ell \leq m \leq \ell,\;
      s \in \{\uparrow, \downarrow\}\bigr\} \,,
  \label{eq:vertex-set}
\end{equation}
with cardinality $|V| = 2n_{\max}^2$ for a lattice truncated at
$n_{\max}$.

\subsection{Edge set}

Edges encode geometrically adjacent transitions:
\begin{itemize}
\item \textbf{Radial edges} ($\hat{T}_{\pm}$): connect
  $(n, \ell, m, s)$ to $(n \pm 1, \ell, m, s)$ at fixed angular
  quantum numbers $(\ell, m)$.  These correspond to radial excitation
  and de-excitation.

\item \textbf{Angular edges} ($\hat{L}_{\pm}$): connect
  $(n, \ell, m, s)$ to $(n, \ell, m \pm 1, s)$ at fixed $n$ and
  $\ell$.  These correspond to magnetic sublevel transitions within a
  shell.
\end{itemize}

The full graph topology may also include edges connecting states with
different~$\ell$ (e.g., $\ell$-changing transitions driven by
non-spherical perturbations).  However, for the spherically symmetric
Coulomb problem, the Hamiltonian is block-diagonal in~$\ell$: the
spherical symmetry decouples the $\ell$~sectors, so that the graph
Laplacian decomposes into independent $(\ell, m)$ blocks even if the
underlying graph contains $\ell$-changing edges.  This
block-diagonality is a consequence of the potential's symmetry, not a
topological constraint on the graph itself.

\subsection{Spectral convergence}

The graph Laplacian $L = D - A$ defines a discrete Hamiltonian
\begin{equation}
  H = K_{\mathrm{vac}} \, L \,,
  \label{eq:graph-hamiltonian}
\end{equation}
where $K_{\mathrm{vac}} = -1/16$ is the kinetic scale factor that
maps dimensionless graph eigenvalues to physical energies in atomic
units.  This constant is not derived from the packing alone; it is the
bridge between the dimensionless graph topology and dimensionful
physics, determined by requiring spectral agreement with the Rydberg
formula.

Within each $(\ell, m)$ sector, the radial edges form a
one-dimensional path graph in $n = \ell+1, \ell+2, \ldots, n_{\max}$.
As $n_{\max} \to \infty$, the ground-state eigenvalue of~$H$
converges to $-0.5$~Ha, the exact hydrogen ground-state energy.  The
$(\ell, m)$ angular structure is exact at every finite $n_{\max}$---it
is encoded in the graph topology, not approximated by mesh refinement.

The full proof of spectral equivalence between this graph Laplacian
and the Laplace--Beltrami operator on the unit~$S^3$ (via Fock's
stereographic projection) is given in Paper~7~\cite{paper7}, where
18~symbolic proofs validate the conformal geometry.  The energy
eigenvalues and dynamics built on this graph are developed in
Papers~1 and~6.


%% ================================================================
%%  VII.  SCOPE AND LIMITATIONS
%% ================================================================
\section{Scope and Limitations}
\label{sec:scope}

\subsection{What the construction provides}

\begin{itemize}
\item[$\checkmark$] The angular quantum number labeling $(\ell, m)$
  and the per-shell degeneracy $2\ell + 1$, as a direct consequence of
  uniform-density isotropic packing.

\item[$\checkmark$] A graph topology $(V, E)$ whose vertices carry
  quantum number labels and whose edges encode allowed transitions.

\item[$\checkmark$] The structural correspondences $n \leftrightarrow$
  cumulative grouping and spin multiplicity $\leftrightarrow$
  orientability, with their proper epistemic status identified.
\end{itemize}

\subsection{What the construction does not provide}

\begin{itemize}
\item[$\times$] Energy eigenvalues $E_n = -1/(2n^2)$.  These require
  the graph Laplacian with the kinetic scale $K_{\mathrm{vac}}$
  (Papers~1, 7).

\item[$\times$] Wavefunctions $R_{n\ell}(r)$ or
  $Y_{\ell m}(\theta, \phi)$ in their functional form.  The packing
  produces the labels, not the functions.

\item[$\times$] Time evolution and dynamics.  These require the
  Hamiltonian as an operator, developed in Paper~6.

\item[$\times$] The fine structure constant or any coupling constants.
  The construction is purely kinematic.
\end{itemize}

\subsection{Choices beyond the axioms}

As noted in Sec.~\ref{sec:correspondences}, the construction involves
structural choices---concentric shells, linearly spaced radii
($r_k = k d_0$), area-proportional counting, and the fundamental area
$\sigma_0 = \pi d_0^2 / 2$---that are natural and mutually consistent
but not uniquely determined by the two axioms.  The robustness of the
$(\ell, m)$ result rests on the observation that any isotropic,
uniform-density, concentric packing produces the same angular capacity
$2k - 1$ per shell; the specific radial spacing affects only how
shells are ordered, not their angular content.


%% ================================================================
%%  VIII.  DISCUSSION
%% ================================================================
\section{Discussion}
\label{sec:discussion}

\subsection{Historical context}

The connection between geometry and quantum mechanics has been
recognized since the earliest days of quantum theory.
Bohr~\cite{bohr1913} imposed quantization as a geometric constraint
(integer wavelengths on circular orbits).
Fock~\cite{fock1935} discovered that the hydrogen momentum-space
problem maps onto $S^3$ via stereographic projection, revealing the
SO(4) dynamical symmetry that explains the ``accidental''
$n^2$~degeneracy.  Bargmann~\cite{bargmann1936} derived the same
symmetry algebraically.  Barut and Kleinert~\cite{barut1967}
extended the symmetry analysis to transition probabilities via
noncompact dynamical groups.  Biedenharn~\cite{biedenharn1981}
provided a comprehensive treatment of the angular momentum algebra
underlying the $(\ell, m)$ structure.

The present work operates at a different level: rather than analyzing
the symmetries of the Schr\"odinger equation, it constructs the
angular labeling from geometric--combinatorial reasoning that is
logically independent of the operator formalism.  The result is the
same $(\ell, m)$ basis---as it must be, since both approaches reflect
the same underlying rotational symmetry---but obtained by a different
route.

\subsection{The kinematic--dynamic distinction}

The packing construction produces the \emph{kinematic} structure of
quantum mechanics: the state space, its labeling, and its
combinatorial organization.  It does not produce the \emph{dynamics}:
the Hamiltonian, the energy spectrum, or time evolution.  This
separation is a feature of the construction, not a limitation.  It
shows that the angular quantum numbers are determined by geometry
alone, independently of the specific force law or potential.

In the GeoVac series, dynamics are recovered when the graph Laplacian
is equipped with the kinetic scale $K_{\mathrm{vac}} = -1/16$ and
node weights encoding the Coulomb potential.  Paper~7~\cite{paper7}
proves that this graph Laplacian is conformally equivalent to the
Laplace--Beltrami operator on~$S^3$, with the $1/r$ Coulomb potential
emerging as the coordinate distortion from stereographic projection
rather than an independent force law.

\subsection{Scope of the geometric analogy}

The construction shows that information-theoretic reasoning under
geometric constraints \emph{can} reproduce the angular quantum number
structure.  It does not show that this is the \emph{only} way to
obtain these labels, nor does it establish that quantum mechanics
\emph{must} have a geometric origin.  The angular momentum algebra
$[\hat{L}_i, \hat{L}_j] = i\epsilon_{ijk}\hat{L}_k$ is a consequence
of rotational symmetry regardless of whether one arrives at it through
operator theory or geometric packing.  What the construction
demonstrates is that the \emph{state-counting} aspect of angular
momentum---the degeneracy $2\ell + 1$---has a purely geometric
derivation.


%% ================================================================
%%  IX.  CONCLUSIONS
%% ================================================================
\section{Conclusions}
\label{sec:conclusions}

The angular momentum quantum numbers $(\ell, m)$ emerge from
uniform-density packing on isotropic shells: shell~$k$ carries
$2k - 1$ angular slots, isomorphic to the spherical harmonic basis
$Y_{\ell m}$ with $\ell = k - 1$.  This result follows from two
axioms (binary distinguishability and geometric indifference) together
with natural structural choices (concentric shells, uniform density).
It is independent of the Schr\"odinger equation, operator postulates,
or any specific physical system.

The principal quantum number~$n$ corresponds to cumulative grouping of
the first~$n$ shells, yielding $n^2$ orbital states.  The factor of~2
corresponds to the orientability of the compactified packing manifold.
These are structural correspondences---genuine mathematical
observations that match hydrogen's quantum numbers---but they depend
on identifications beyond what the two axioms alone determine.

The $(\ell, m)$ angular sector constructed here recurs as the
universal angular cross-section inside every natural geometry developed
in the GeoVac series, from $S^3$ for single-electron
atoms~\cite{paper7} through composed fiber bundles for core--valence
molecules~\cite{paper17}.  When equipped with a graph Laplacian and
kinetic scale, this packing becomes the foundation for a computational
framework that has been applied to H, He, H$_2^+$, H$_2$, HeH$^+$,
LiH, and BeH$^+$, with errors ranging from ${<}\,0.1\%$ for hydrogen
to ${\sim}\,6\%$ for LiH equilibrium geometry, benchmarked against
exact and experimental values.


\section*{Acknowledgments}

This work was developed using an AI-augmented workflow, with
scientific direction and quality control by the author and
implementation assistance from Anthropic's Claude.


\begin{thebibliography}{99}

\bibitem{fock1935}
V.~Fock,
``Zur Theorie des Wasserstoffatoms,''
\textit{Z. Phys.} \textbf{98}, 145 (1935).

\bibitem{bargmann1936}
V.~Bargmann,
``Zur Theorie des Wasserstoffatoms: Bemerkungen zur gleichnamigen
Arbeit von V.~Fock,''
\textit{Z. Phys.} \textbf{99}, 576 (1936).

\bibitem{barut1967}
A.~O.~Barut and H.~Kleinert,
``Transition Probabilities of the Hydrogen Atom from Noncompact
Dynamical Groups,''
\textit{Phys. Rev.} \textbf{156}, 1541 (1967).

\bibitem{biedenharn1981}
L.~C.~Biedenharn and J.~D.~Louck,
\textit{Angular Momentum in Quantum Physics: Theory and Application}
(Addison-Wesley, Reading, MA, 1981).

\bibitem{bohr1913}
N.~Bohr,
``On the Constitution of Atoms and Molecules,''
\textit{Phil. Mag.} \textbf{26}, 1 (1913).

\bibitem{paper7}
J.~Loutey,
``The Dimensionless Vacuum: Recovering the Schr\"odinger Equation
from Graph Topology via Fock's Stereographic Projection,''
GeoVac Paper~7 (2026).

\bibitem{paper11}
J.~Loutey,
``Prolate Spheroidal Lattice for One-Electron Diatomics,''
GeoVac Paper~11 (2026).

\bibitem{paper13}
J.~Loutey,
``Hyperspherical Lattice for Two-Electron Atoms,''
GeoVac Paper~13 (2026).

\bibitem{paper15}
J.~Loutey,
``Molecule-Frame Hyperspherical Geometry for Two-Electron Diatomics,''
GeoVac Paper~15 (2026).

\bibitem{paper17}
J.~Loutey,
``Composed Natural Geometries for Core--Valence Molecules,''
GeoVac Paper~17 (2026).

\end{thebibliography}

\end{document}
