% group6_precision_observations_synthesis.tex
% GeoVac Group 6 Synthesis: Precision Observations / Projection Arc
% Status: Project archive synthesis, June 2026
% Audience: precision AMO / mathematical-physics readers
% Spine: two-layer framework (34) -> time as projection (35)
%        -> entropy as projection (27) -> entanglement (26)
%        -> multi-observable focal-length program (34 SS V.C/V.D)

\documentclass[aps,pra,twocolumn,superscriptaddress,longbibliography]{revtex4-2}

\usepackage{amsmath,amssymb,amsthm,graphicx,xcolor,bm,braket,booktabs}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{observation}{Observation}
\newtheorem{prediction}{Prediction}

\begin{document}

\title{Observables as Projections of a $\pi$-free Graph:\\
A Synthesis of the GeoVac Precision-Observation Arc}
\thanks{Group~6 synthesis in the Geometric Vacuum series}

\author{J.~Loutey}
\affiliation{Independent Researcher, Kent, Washington}

\date{June 30, 2026}

%% ========================================================================
%% ABSTRACT
%% ========================================================================

\begin{abstract}
The Geometric Vacuum (GeoVac) framework separates into two structurally
distinct layers, and that separation is the organizing principle of its
precision-observation arc.  \emph{Layer~1} is a bare combinatorial graph:
quantum-number labels $(n,\ell,m,\ldots)$, integer eigenvalues, rational
or algebraic matrix elements, no physical units, and---verified
symbolically---no $\pi$.  \emph{Layer~2} is a finite family of named
projections from that graph onto continuous physical settings; every
physical variable, every dimension, and every transcendental constant
that appears in any GeoVac calculation enters through exactly one
projection and is traceable to it.  This synthesis assembles the four
Group~6 papers into a single narrative built on that thesis.  The spine
is:\ the projection taxonomy and its three-axis tagging
(Paper~34~\cite{loutey_paper34}); time as the prototype \emph{free-side}
projection---$\pi$ enters the Klein--Gordon spectrum on
$S^3\times\mathbb{R}$ at exactly one step, temporal compactification,
while rest mass preserves the algebraic ring
(Paper~35~\cite{loutey_paper35}); entropy as an embedding-class
projection artifact, identically zero on the one-body graph and finite
only after the metric embedding of the two-body repulsion
(Paper~27~\cite{loutey_paper27}); and the entanglement structure that
isolates that repulsion in the angular-momentum eigenbasis
(Paper~26~\cite{loutey_paper26}).  A multi-observable focal-length
program closes the arc:\ Roothaan autopsies decompose precision atomic
observables into projection-chain-tagged components, exposing literature
convention mismatches and framework kernel gaps that single-observable
analyses cannot see.  Two disciplines run throughout.  \emph{First},
every transcendental named here is tagged to its projection---$\pi$ via
the Hopf and Fock volume measures, $\pi^{2k}$ via the spectral action,
$\zeta(2k)$ via even-zeta Dirichlet series, odd~$\zeta$ and Catalan~$G$
via the half-integer-Hurwitz spinor lift, $2\pi$ via temporal
compactification.  \emph{Second}, the precision matches are sub-percent
\emph{framework-native} agreements that surface convention and kernel
issues; they are \emph{not} first-principles predictions of the constants,
and the multi-focal-composition wall---the framework has no native theorem
for composing multiple Fock-style projections---is named as an active
boundary.  The unifying reading is that ``discreteness is compactness''
made operational:\ the discrete skeleton is the compact/closed regime,
and a transcendental is precisely the price of releasing compactness by
integrating over a promoted continuous parameter.
\end{abstract}

\maketitle

%% ========================================================================
\section{Introduction: two layers, one organizing observation}
%% ========================================================================

The GeoVac quantum-chemistry and quantum-computing arcs (Groups~2 and~4)
treat the framework as a sparse graph-Hamiltonian engine.  The
operator-algebra arc (Group~1) treats the same construction as a discrete
spectral triple.  These two readings are not in conflict; they describe
two different \emph{layers} of one object, and the precision-observation
arc collected here is the arc that names the layers and the bridge between
them.

Layer~1 is the bare combinatorial graph.  Its nodes are
representation-theoretic labels of compact Lie groups; its Laplacian
eigenvalues are integers ($n^2-1$ on the Coulomb $S^3$ graph, $N$ on the
Bargmann--Segal $S^5$ graph); its matrix elements are rational or
algebraic over $\mathbb{Q}[\sqrt{2},\sqrt{3},\sqrt{6},\ldots]$ from
Wigner~$3j$ algebra.  That no $\pi$ appears in Layer~1 is not an
aspiration but a verified certificate:\ on both the Coulomb $S^3$ Fock
graph and the Bargmann--Segal $S^5$ graph, every adjacency entry, every
eigenvalue, and every coupling coefficient is exact rational/algebraic in
exact arithmetic (Paper~24~\cite{loutey_paper24}, Paper~28's
graph-native QED certificate).  This is a SYMBOLIC certificate, not a
numerical observation.

Layer~2 is a finite family of named maps from the bare graph to physical
settings:\ the Fock 1935 conformal projection, the Hopf bundle, the
Bargmann--Segal transform, the Connes--Chamseddine spectral action, the
Sturmian reparameterization, the Camporesi--Higuchi spinor lift, the
Wigner~$3j$/$D$ couplings, temporal compactification, and others.  Each
projection introduces specific physical variables ($Z$, $\alpha$,
$\hbar\omega$, $R$, $\beta$, $\Lambda$, $\ldots$), attaches specific
dimensions to graph data, and carries a specific transcendental
signature.  The load-bearing structural claim of the arc is an
Observation, asserted at exactly that tier:

\begin{observation}[Single-projection origin of physical content]
Every coupling constant, energy scale, length scale, and transcendental
constant appearing in any GeoVac computation traces to exactly one
projection in Layer~2.  The bare graph contains none of $\alpha$, $Z$,
$\hbar\omega$, $R$, $\Lambda$, $\pi$, or $\zeta(2k)$; these enter by, and
only by, the projection the calculation invokes.
\end{observation}

This is the operational form of the project's organizing observation that
\emph{discreteness is compactness}.  Compact groups have discrete spectra
(Peter--Weyl), and the bit-exact rational skeleton is the closed/compact
regime; the continuum---and with it every transcendental---is what remains
when compactness is released.  Calibration data is continuum (un-packed)
data, which is why the skeleton is forced and rational while the
projections are free and transcendental.  The four Group~6 papers make
this concrete:\ Paper~34 catalogues the projections; Paper~35 locates the
exact step at which the prototype free-side projection (time) injects
$\pi$; Papers~27 and~26 show entropy and entanglement to be projection
artifacts, zero on the bare graph and finite only after metric embedding.

We hold one framing discipline throughout, following the GeoVac rhetoric
rule:\ the discrete graph and its continuous projections are dual
descriptions connected by proven maps, and no ontological priority is
asserted for either.  The contribution is a vocabulary that makes the
question ``where does this $\pi$ come from?'' answerable, not a claim
about which description is fundamental.

%% ========================================================================
\section{The projection taxonomy and master-Mellin tagging (Paper~34)}
%% ========================================================================

Paper~34 is the keystone of this group:\ the living catalogue of
\emph{twenty-eight} projection mechanisms, each tagged along three
independent axes---(a)~the physical variables it introduces, (b)~the
dimension or unit it attaches to graph data, and (c)~its transcendental
signature in the sense of Paper~18~\cite{loutey_paper18}.  The
transcendental axis is a structural sibling of Paper~18's transcendental
classification:\ each tier corresponds to a projection type, and reading
the dictionary in either direction recovers the other.  A representative
slice of the dictionary is reproduced in Table~\ref{tab:axes}.

\begin{table}[t]
\centering\small
\begin{tabular}{p{2.5cm} p{1.7cm} p{2.9cm}}
\toprule
Projection & Dimension & Transcendental signature \\
\midrule
Fock conformal & energy & $\kappa=-1/16$; $\pi$ via $\mathrm{Vol}(S^3)$ \\
Hopf bundle & dimensionless & $\pi = \mathrm{Vol}(S^2)/4$ \\
Bargmann--Segal & energy & \textit{none} (graph $\pi$-free) \\
Spectral action & energy & $\pi^{2k}\!\cdot\mathbb{Q}$ observables \\
Spinor lift (CH) & dimensionless & half-int.\ Hurwitz $\to$ odd~$\zeta$; $G$, $\beta(4)$ \\
Wigner $3j$ & dimensionless & $\mathbb{Q}[\sqrt{2k{+}1}]_k$ \\
Vector-photon & dimensionless & $1/(4\pi)$ per loop \\
Rest-mass & mass & \textit{trivial} (ring-preserving) \\
Temporal window & time & $2\pi\!\cdot\mathbb{Q}$ per Matsubara mode \\
\bottomrule
\end{tabular}
\caption{A slice of the Paper~34 projection dictionary.  Each row is a
named structural construction that introduces specific physical content
into Layer~1 graph data; the transcendental signature is in the sense of
Paper~18.  The full dictionary catalogues twenty-eight projections.}
\label{tab:axes}
\end{table}

\paragraph{Where the transcendentals live.}
The dictionary makes the tagging discipline mechanical.  The kinetic
constant $\kappa=-1/16$ and the volume $\pi$ enter at the Fock conformal
projection; the dimensionless $\pi=\mathrm{Vol}(S^2)/4$ at the Hopf
bundle; the $\pi^{2k}\cdot\mathbb{Q}$ content of vacuum-polarization-type
observables (e.g.\ $\Pi=1/(48\pi^2)$) at the Connes--Chamseddine spectral
action; the even-zeta value $\zeta_R(2)$ (the Fock-Dirichlet object $F$)
at a Dirichlet series at $s=4$; the half-integer Hurwitz content that
promotes to odd~$\zeta$, Catalan's~$G$, and $\beta(4)$ at the
Camporesi--Higuchi spinor lift's vertex selection; and $2\pi\cdot\mathbb{Q}$
at temporal compactification (Sec.~\ref{sec:time}).  None of these is an
anonymous transcendental:\ each is pinned to a projection row, which is
the discipline this group exists to model.  The fine-structure
combination $1/(4\pi)$ per loop is tagged to the vector-photon promotion;
the Paper~2 fine-structure combination rule that consumes it remains an
\textbf{Observation}, never a derivation, and the taxonomy is consistent
with that tiering rather than strengthening it.

\paragraph{The engine versus the catalogue.}
The computational engine behind the transcendental tags is the master
Mellin engine---the Mellin transform of $\mathrm{Tr}\,(D^k e^{-tD^2})$ at
$k\in\{0,1,2\}$, whose three domains $M_1/M_2/M_3$ generate the $\pi^{2k}$,
even-zeta, and odd-zeta/Catalan tiers respectively.  That engine is
developed in Paper~18~\S III.7 (Group~3, the foundations trunk); Paper~34
is the \emph{catalogue} that consumes its output and assigns each tier to
a projection.  The synthesis-level reading is that the transcendental
axis is the only genuinely independent axis of the three:\ Sprint~TX-A's
dimensional axiomatization found the variable and dimension axes to be
perfectly correlated, so the dictionary's content reduces to the
projection~$\leftrightarrow$~transcendental map.

%% ========================================================================
\section{Time as the prototype free-side projection (Paper~35)}
\label{sec:time}
%% ========================================================================

Paper~35 answers the question Paper~34 leaves open---\emph{where exactly}
does $\pi$ enter, and at no other step---in the simplest non-trivial
relativistic system the framework describes:\ a free scalar on
$S^3\times\mathbb{R}$ governed by the Klein--Gordon equation.

\paragraph{The before/after.}
The bare Klein--Gordon spectrum is $\pi$-free in the algebraic-extension
ring $\mathbb{Q}[\sqrt{d_i}]$ for every rational mass-squared parameter.
This is verified SYMBOLICALLY for $n\in[1,50]$ across the panel
$m^2\in\{0,1,1/4,2\}$ (200 cases, zero transcendentals).  Mass is
therefore a \emph{rest-mass projection}:\ it introduces a parameter of
dimension mass and \emph{preserves} the bare-graph ring.  Compactify the
temporal direction, $S^3\times\mathbb{R}\to S^3\times S^1_\beta$, and the
spectrum acquires Matsubara modes $\omega^t_k = 2\pi k/\beta$; the first
$\pi$-bearing eigenvalue is the $(n{=}0,k{=}1)$ mode with
$\omega^2=4\pi^2$.  Every $(n,0)$ eigenvalue is $\pi$-free; every
$(n,k\neq0)$ eigenvalue carries $2\pi/\beta$.  The conformally coupled
massless scalar Casimir energy on unit $S^3$ (spatial only, no temporal
compactification) is the exact rational $E_{\mathrm{Cas}}=1/240$, with no
transcendental at any step; the Stefan--Boltzmann constant $\pi^2/90$
appears only in the high-temperature expansion on
$S^3\times S^1_\beta$---through the Matsubara sum, i.e.\ exactly the
spectral $\pi$-injection.

\paragraph{The sharpened reading and its tier.}
This forces a refinement of the Paper~34 dictionary:\ the implicit
``scalar parameter projection'' splits into a ring-preserving
\emph{rest-mass projection} (introduces $m$, signature trivial) and an
\emph{observation/temporal-window projection} (introduces $\beta$,
signature $2\pi\cdot\mathbb{Q}$ per mode).  The structural statement is
that a GeoVac observable contains $\pi$ if and only if its evaluation
includes a continuous integration over a temporal or spectral parameter
promoted from the discrete graph spectrum.  This is a structural
OBSERVATION supported by a symbolic verification panel (the 208-case
panel that Paper~34's prediction subsection cites as a downstream control);
it is asserted at that tier, not as a theorem about all observables.
Time is, in this reading, the prototype free-side projection:\ the
observer's finite-time measurement window is the formal mechanism by
which the continuum---and $\pi$---enters.

This connects directly to the project's internal working hypothesis that
time-discreteness is observer-compactification (WH7):\ the only temporal
structure the metric can see is compactified time, and compactified time
is automatically discrete.  We flag the honest cap that internal
diagnostic work attaches to that hypothesis---whether the Lorentzian
\emph{signature} is metrically visible at finite cutoff remains open, and
the relevant falsifier (a metrically visible temporal algebra on a
non-compact carrier) is an active probe, not a closed result.  Paper~35's
load-bearing content---that $\pi$ enters at temporal compactification and
that rest mass is ring-preserving---stands independently of that open
question.

%% ========================================================================
\section{Entropy as an embedding-class projection (Paper~27)}
%% ========================================================================

Paper~27 places entanglement entropy in the same two-layer frame and
shows it to be a projection artifact rather than an intrinsic feature of
the graph.

\paragraph{One-body operators are entanglement-inert.}
The operator-theoretic result is an INTERNAL THEOREM:\ on any finite
lattice, the von~Neumann entropy of any reduced density matrix derived
from a \emph{non-degenerate} ground state of a purely one-body fermionic
Hamiltonian is identically zero (the ground state is a single Slater
determinant).  Numerically this is confirmed to machine precision,
$S_{\mathrm{kin}}/S_{\mathrm{full}}\sim10^{-14}$ for He at
$n_{\max}=2,3$.  All ground-state entanglement is generated by the
two-body interaction $V_{ee}$.  The non-degeneracy qualifier is
essential---open-shell and dissociated-bond states escape the floor---and
is stated as such.

\paragraph{The ``area law'' is pair counting.}
Earlier framework material presented a holographic scaling
$S_n=k\log A_n$ with $A_n\propto n^4$ in one-particle language.  Paper~27
re-derives it rigorously as a \emph{pair-counting} statement:\
$A_n=g_n^2$ with shell degeneracy $g_n=2n^2$, so the factor of four is
the two-body signature, not a genuine area law.  This corrects the
earlier presentation in place rather than propagating it---a model of the
two-way verdict discipline (a claim is re-priced to what its backing
supports).

\paragraph{A second rigidity statement.}
On the Bargmann--Segal harmonic-oscillator lattice, the two-fermion
closed-shell ground-state entropy is identically zero for \emph{any}
central two-body potential.  The mechanism is an INTERNAL THEOREM:\
Moshinsky--Talmi total-quanta conservation makes
$N_1+N_2 = N_{\mathrm{rel}}+N_{CM}$ a good quantum number, so the
closed-shell ground state is the one-dimensional lowest-quanta sector---a
single determinant $|(0s)^2\rangle$, confirmed bit-identically at
$N_{\max}=2,3$ with commutator residual $\|[H_{HO},V]\|_F/\|H_{HO}\|_F
\sim10^{-16}$.  This is the entropy-side dual of the Fock and
Bargmann--Segal rigidity theorems of Paper~24.

\paragraph{Taxonomy placement.}
Entropy slots cleanly as an \emph{embedding-class} observable in the
Paper~18 taxonomy and a projection artifact in the Paper~34 frame:\ zero
on the combinatorial graph (one-body operator alone, no transcendental),
finite only after the metric embedding of $1/r_{12}$ onto the pair-state
graph, where the spectral eigenvalues of $V_{ee}$ become irrational.  The
combinatorial graph is entropy-blind; entropy is the price of projecting
onto the metric continuum.  A measured refinement accompanies the
placement:\ Coulomb-lattice block entropy obeys a universal two-variable
scaling $S_B = A\,(\tilde w_B/\delta_B)^\gamma$ whose local exponent
Richardson-extrapolates to $\gamma_\infty\approx1.96$, slightly below the
non-degenerate second-order Rayleigh--Schr\"odinger value of~$2$---a
MEASURED extrapolation, reported with its residual gap attributed to
multi-shell aggregation, not claimed as exactly~$2$.

%% ========================================================================
\section{Entanglement structure of the angular-momentum basis (Paper~26)}
%% ========================================================================

Paper~26 supplies the computational backbone for the entropy thesis by
characterizing \emph{where} the two-body entanglement lives in the
angular-momentum eigenbasis---the basis of hydrogenic radial functions
times spherical harmonics labeled by $(n,\ell,m)$.

\paragraph{Energy--entanglement decoupling.}
The off-diagonal one-body Hamiltonian (graph-Laplacian topology, coupling
$\kappa=-1/16$) carries $10$--$39\%$ of the correlation energy but
$<0.2\%$ of the single-orbital entanglement entropy; the off-diagonal
electron repulsion carries $100\%$ of the entanglement.  The total
entanglement entropy scales as $S\sim Z^{-2.56}$ across He-like ions.
These are MEASURED quantities across $Z=2$--$10$ at $n_{\max}=2$--$4$.
The structural origin is that a one-body operator is separable and cannot
entangle orbitals, while $V_{ee}$ is the irreducible two-body interaction;
the angular-momentum basis, by nearly diagonalizing the one-body physics,
isolates the entanglement in $V_{ee}$ alone.

\paragraph{Basis-intrinsic sparsity.}
Among orbital bases for spherically symmetric systems, the
angular-momentum eigenbasis is an \emph{isolated} point of ERI sparsity:\
any unitary rotation of orbital indices, however small, fills the ERI
tensor from $42\%$ to $99\%$ density in a step-function transition at the
identity, and the nonzero ERI count is $Z$-independent (sparsity is
purely geometric).  This MEASURED step-function is the entanglement-side
counterpart of the potential-independent angular-sparsity theorem
(Paper~22, Group~3) and the structural root of the $O(Q^{2.5})$ composed
Pauli scaling reported in the quantum-computing arc (Group~4):\ the same
basis that decouples one-body energy from two-body entanglement is the
one that produces sparse ERIs.

\paragraph{Network topology and the factorization it justifies.}
Orbital mutual-information maps exhibit a hub-migration pattern
($1s\to2s\to2p$) tracking the partially filled shell across the first
row, and core--valence mutual information falls to $\approx 2\times10^{-3}$
by $Z=4$ and below $10^{-3}$ for $Z\geq5$.
The latter is the quantitative justification for the composed
fiber-bundle factorization used in the molecular framework:\ per-block
entanglement is $R$-independent, with core/bond entropy ratios of
$\sim50\times$ at matched qubit count.  Paper~26 states its limitations
plainly---$n_{\max}=2$ for the first-row network maps, $R$-independence
is a property of the composed architecture (not of the true molecular
ground state, whose entanglement diverges at dissociation), and the
$d$-orbital extension is open.

%% ========================================================================
\section{The multi-observable focal-length program (Paper~34 \S V)}
%% ========================================================================

The arc's most distinctive instrument is the multi-observable
focal-length decomposition program:\ the discovery that a global fit of
several precision observables through one structural dictionary exposes
systematics that no single-observable analysis can see.

\paragraph{Roothaan autopsies.}
For observables with a multi-component literature decomposition---the
hydrogen Lamb shift, the $21$~cm and muonic hyperfine intervals, the
muonic-deuterium Lamb shift---Paper~34 hosts \emph{Roothaan autopsies}:\
decomposition tables that present each measured observable as a sum of
focal-length-tagged components, each carrying its explicit projection
chain and a framework-native (FN) versus Layer-2-input (L2) status.  The
hydrogen $1S$ Lamb-shift autopsy is representative:\ the framework-native
components (self-energy via Fock\,$\circ$\,Sturmian\,$\circ$\,spectral
action\,$\circ$\,Drake--Swainson, Uehling vacuum polarization via
Fock\,$\circ$\,spectral action, $\ldots$) sum to $+1057.19$~MHz, $99.9\%$
of the $1057.845(9)$~MHz measurement, with the Layer-2 inputs
(multi-loop QED, finite-size, recoil~NLO) summing to a near-cancellation
specific to this observable.  These are MEASURED decompositions whose
residuals sit within the cited compilation precision; the autopsy makes
the projection-chain dictionary's reach visible at the observable level.

\paragraph{Convention exposures versus kernel gaps.}
The program's signature finding-type is the \emph{literature convention
exposure}:\ a multi-observable global fit surfaces itemization
differences between independent precision compilations
(Eides, Karshenboim, Krauth, Pachucki--Yerokhin, Antognini,
Friar--Payne) at the sub-percent level the framework operates at.  Six
are catalogued, including:\ the $\sim0.01\%$-of-$\nu_F$ recoil/multi-loop
itemization difference that propagates to $\sim25$~mfm in an extracted
Zemach radius; the Friar-moment convention difference between an RMS
radius $\langle r^2\rangle^{1/2}$ and a first moment $\langle r\rangle$
(a Gaussian-profile factor $\langle r^2\rangle/\langle r\rangle^2=4/\pi
\approx1.27$, i.e.\ $+12.7\%$ on the Friar moment); and the resolution of
a $3\sigma$ helium fine-structure disagreement traced to a numerically
incorrect relativistic Bethe-log itemization in an older compilation.
The complementary finding-type is the \emph{framework kernel gap}:\
places where the framework's leading-order operator (Eides Zemach,
Foldy--Friar contact, Friar moment) is too coarse for the precision
target.  Each precision tightening tends to relocate the load-bearing
systematic from one to the other; cataloguing which class a given
observable lands in is itself the program's output.

\paragraph{The structural prediction that replaced the naive one.}
A falsifiable structural PREDICTION emerges from re-tagging the matches
catalogue by the number of Layer-2 inputs a chain consumes.  An earlier
form scaled the residual with projection \emph{depth}; the May~2026
synthesis pass falsified that form on the catalogue itself (depth-3
chains exist at residual~$0$ and at $+286$~ppm; depth-4 chains at
$+2$~ppm and at $+0.534\%$).  The replacement is the \emph{Layer-2-presence
bound}:\ the residual of a catalogue row is bounded above by the larger
of the framework's basis-quality residual at zero Layer-2 inputs and the
largest single Layer-2 input consumed,
\[
|\epsilon(\text{obs})| \;\leq\;
\max\!\bigl(\epsilon_{\text{basis}},\ \max_i |L_2^{(i)}|\bigr).
\]
Zero-Layer-2 chains run from machine-exact (Stefan--Boltzmann $\pi^2/90$,
hydrogen static polarizability $\tfrac92 a_0^3$, $S^3$ Casimir $1/240$) to
basis-quality ceilings ($-0.534\%$ for the one-loop Lamb-shift closure);
one-input chains tighten to tens of ppm or below; multi-input chains sit
in the multi-focal-wall regime, dominated by the largest single input.
This is a PREDICTION, consistent with the present catalogue and
falsifiable by future calculation, not a phenomenological fit.

%% ========================================================================
\section{Honest scope and positioning}
%% ========================================================================

\paragraph{What is robust.}
The load-bearing results are structural and verified at their stated
tiers.  The $\pi$-free Layer~1 certificate is SYMBOLIC (exact arithmetic,
both Coulomb $S^3$ and Bargmann--Segal $S^5$).  The Klein--Gordon
$\pi$-injection at temporal compactification is a SYMBOLIC panel
($200$ cases; $E_{\mathrm{Cas}}^{S^3}=1/240$ and the conformal-scalar
chain exact).  The one-body entanglement-inertness and the HO
zero-entropy rigidity are INTERNAL THEOREMS with machine-precision
numerical confirmation.  The two-layer thesis and the single-projection
origin of physical content are stated as OBSERVATIONS, asserted at that
tier and no higher.  The projection dictionary is a concrete, structured
artifact:\ every transcendental in the arc wears its projection tag.

\paragraph{What is conditional.}
The precision matches are sub-percent \emph{framework-native} agreements,
not first-principles predictions of the physical constants.  Each
consumes external Layer-2 inputs (Zemach radii, $g$-factors, multi-loop
QED coefficients, nuclear polarizabilities) in their native compilation
conventions, and the program's value is precisely that it surfaces
where those conventions and the framework's leading-order kernels are too
coarse---a diagnostic instrument for precision systematics, not a
replacement for the precision compilations.  The block-entropy exponent
$\gamma_\infty\approx1.96$ is a MEASURED extrapolation, not the exact
second-order value~$2$.  The entropy area-law and the $R$-independence of
composed block entanglement are properties of the construction, stated
with their limitations, not physical statements about molecular
entanglement at dissociation.

\paragraph{The active wall.}
The arc's principal open boundary is the \emph{multi-focal-composition
wall}:\ the framework couples discrete labels cleanly but has \emph{no}
native composition theorem for combining multiple Fock-style projections.
Six independent instances are on record across domains (the Yukawa
non-selection theorem, the LS-8a renormalization scale, the HF spatial
recoil/Zemach/multi-loop attempts, the chemistry W1e wall).  This is why
multi-Layer-2-input observables sit in the residual-dominated regime of
the Layer-2-presence bound, and why the precision program's deepest
residuals are structural rather than numerical.  The wall is named as an
active boundary, not papered over.

\paragraph{Positioning.}
The natural reading of this arc is as a \emph{vocabulary and a
diagnostic}.  The two-layer framework gives every GeoVac observable a
definite answer to ``where does each transcendental enter,'' and the
multi-observable focal-length program turns that vocabulary into an
instrument that exposes convention mismatches and kernel gaps in precision
atomic physics.  The discrete skeleton and its continuous projections are
dual descriptions; the contribution is structural traceability, not an
ontological claim and not a derivation of the constants the projections
consume.

%% ========================================================================
%% BIBLIOGRAPHY
%% ========================================================================
\begin{thebibliography}{99}

\bibitem{loutey_paper0}
J.~Loutey,
``Angular Momentum as Information Geometry:\ Isotropic Packing and the
Universal Angular Cross-Section,''
GeoVac Paper~0 (2026).

\bibitem{loutey_paper7}
J.~Loutey,
``The Dimensionless Vacuum:\ Recovering the Schr\"odinger Equation from
Scale-Invariant Graph Topology,''
GeoVac Paper~7 (2026).

\bibitem{loutey_paper18}
J.~Loutey,
``Spectral-Geometric Exchange Constants: Projecting Discrete Spectra
onto Continuous Manifolds,''
GeoVac Paper~18 (2026).
[Master Mellin engine, \S III.7; transcendental-tier classification.]

\bibitem{loutey_paper24}
J.~Loutey,
``The Bargmann--Segal Lattice: $\pi$-Free Discretization of the Harmonic
Oscillator on $S^5$,''
GeoVac Paper~24 (2026).
[Layer-1 $\pi$-free certificate; HO rigidity theorem.]

\bibitem{loutey_paper26}
J.~Loutey,
``Entanglement Structure of the Angular Momentum Eigenbasis:\
Energy-Entanglement Decoupling and Basis-Intrinsic Sparsity,''
GeoVac Paper~26 (2026).

\bibitem{loutey_paper27}
J.~Loutey,
``Entropy as a Projection Artifact:\ One-Body Operators are
Entanglement-Inert on Sparse Lattices,''
GeoVac Paper~27 (2026).

\bibitem{loutey_paper28}
J.~Loutey,
``QED on $S^3$: Spectral Geometry of Perturbative Transcendentals,''
GeoVac Paper~28 (2026).
[Graph-native QED $\pi$-free certificate.]

\bibitem{loutey_paper31}
J.~Loutey,
``The Universal/Coulomb Partition of the GeoVac Spectral Triple,''
GeoVac Paper~31 (2026).

\bibitem{loutey_paper32}
J.~Loutey,
``The GeoVac Spectral Triple: A Synthesis Paper Locking the Framework
into the Marcolli--van~Suijlekom Gauge-Network Lineage,''
GeoVac Paper~32 (2026).

\bibitem{loutey_paper34}
J.~Loutey,
``GeoVac as a Two-Layer Framework:\ Projection Taxonomy and the Empirical
Matches Catalog,''
GeoVac Paper~34 (2026).

\bibitem{loutey_paper35}
J.~Loutey,
``Time as Projection:\ The Klein--Gordon Spectrum on
$S^3\times\mathbb{R}$ and the Algebraic / Observation Split,''
GeoVac Paper~35 (2026).

\end{thebibliography}

\end{document}
