% paper_56_tannakian_substrate.tex
%
% Paper 56:\ The Tannakian substrate of GeoVac:\ a finite-cutoff
% pro-system, a neutral Tannakian category, and an explicit
% G_a^{3N} x SL_2 inclusion into Aut^otimes(omega).
%
% Math.OA / NCG-with-motivic-leanings audience.  Consolidates the
% Pro-System Lockdown PS-1..PS-4 (v3.67.0--v3.69.0) and the Tannakian
% Foundation TC-1a..TC-1f (v3.70.0--v3.74.0) into a single standalone
% writeup.  Mold:\ Papers 45 / 47 / 49 (math.OA standalones).
%
\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm, mathrsfs, mathtools}
\usepackage{newunicodechar}
\newunicodechar{α}{\ensuremath{\alpha}}
\newunicodechar{β}{\ensuremath{\beta}}
\newunicodechar{γ}{\ensuremath{\gamma}}
\newunicodechar{η}{\ensuremath{\eta}}
\newunicodechar{κ}{\ensuremath{\kappa}}
\newunicodechar{λ}{\ensuremath{\lambda}}
\newunicodechar{μ}{\ensuremath{\mu}}
\newunicodechar{π}{\ensuremath{\pi}}
\newunicodechar{ρ}{\ensuremath{\rho}}
\newunicodechar{σ}{\ensuremath{\sigma}}
\newunicodechar{τ}{\ensuremath{\tau}}
\newunicodechar{ω}{\ensuremath{\omega}}
\newunicodechar{χ}{\ensuremath{\chi}}
\newunicodechar{Δ}{\ensuremath{\Delta}}
\newunicodechar{Φ}{\ensuremath{\Phi}}
\newunicodechar{Σ}{\ensuremath{\Sigma}}

\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue!50!black, citecolor=blue!50!black, urlcolor=blue!50!black}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

\newcommand{\nmax}{n_{\max}}
\newcommand{\HGV}{\mathcal{H}_{\mathrm{GV}}}
\newcommand{\Acal}{\mathcal{A}}
\newcommand{\Tcal}{\mathcal{T}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\Vbb}{\mathbf{V}}
\newcommand{\Oh}{\mathcal{O}}
\newcommand{\Ginf}{\mathcal{O}_{\infty}}
\newcommand{\Repcat}{\mathrm{Rep}_{\mathrm{fin}}}
\newcommand{\Aut}{\mathrm{Aut}}
\newcommand{\End}{\mathrm{End}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\Sym}{\mathrm{Sym}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\SL}{\mathrm{SL}}
\newcommand{\Ga}{\mathbb{G}_{a}}
\newcommand{\Gm}{\mathbb{G}_{m}}
\newcommand{\MT}{\mathrm{MT}}
\newcommand{\sympy}{\texttt{sympy}}
\newcommand{\Vecbf}{\mathbf{Vec}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Ulev}{U^{*}_{\mathrm{Levi}}}
\newcommand{\Ustar}{U^{*}}
\newcommand{\Phimap}{\Phi}
\newcommand{\fibfun}{\omega}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\Sec}{\mathfrak{S}}
\newcommand{\Nsec}{N_{\mathrm{sec}}}
\newcommand{\nlsec}{(n, l)}

\title{The Tannakian substrate of \textsc{GeoVac}:\\
a finite-cutoff pro-system, a neutral Tannakian category,\\
and an explicit $\Ga^{3N} \rtimes \SL_{2}$ inclusion into $\Aut^{\otimes}(\fibfun)$}
\author{J.~Loutey\thanks{Independent researcher. \texttt{jloutey@gmail.com}.
This work was developed in an AI-augmented agentic workflow with
Anthropic's Claude. Implementation, internal memos, and bibliographic
collation were performed collaboratively;\ all theorems, design
choices, and editorial decisions are the author's responsibility.}}
\date{June 2026 (preprint)}

\begin{document}
\maketitle

\begin{abstract}
We construct the Tannakian substrate of the \textsc{GeoVac} spectral
triple at finite cutoff and verify, bit-exact on explicit
$\texttt{sympy}$-rational panels, every prerequisite of the Deligne--Milne
1982 neutral Tannakian theorem on an abelian primitive Hopf algebra
$\HGV(\nmax) = \Sym_{\Q}(V_{\nmax})$ whose primitive space $V_{\nmax}$
has $\Q$-dimension $3 N(\nmax)$ (one generator per (sector, Mellin slot)
pair). The construction has two halves.

\medskip
\noindent\emph{Pro-system half.} A cofiltered system of finite-cutoff
truncations $\{\HGV(\nmax)\}_{\nmax\in\N}$ with explicit Hopf-algebra
transition maps $\Phi_{m, k} : \HGV(m) \to \HGV(k)$ (block-diagonal
truncations) satisfies the cofiltered axiom, is $\Ustar$-equivariant,
admits a well-defined inverse limit $\Ginf \cong \Q^{\N_{\mathrm{sec}}}$
into which the continuum cochains $\chi_{\infty}$, $\eta_{\infty}$ and
the continuum Mellin lift $F(s)$ of v3.66.0 FO1--FO3 project
coherently, and has finite-cutoff endomorphism algebra
$\End_{\mathrm{compat}}(\Oh_{\nmax})$ that is block-lower-triangular of
closed-form dimension $\dim = \sum_{j \le i \le \nmax}(i + 1)(j + 1)$.

\medskip
\noindent\emph{Tannakian half.} The finite-dimensional
representation category $\Repcat(\HGV(\nmax))$ is an abelian, symmetric
monoidal, rigid $\Q$-linear category (axioms TC-1a, TC-1b, TC-1c
bit-exact); the no-op forgetful $\fibfun :\ \Repcat \to \Vecbf_{\Q}$ is a
faithful exact $\otimes$-functor (TC-1d); and the pro-unipotent factor
of the cosmic Galois group $\Ulev = \Ga^{3 N(\nmax)} \rtimes \SL_{2}$
admits an \emph{explicit inclusion}
\[
   \Phimap :\ \Ulev(\Q) \longrightarrow \Aut^{\otimes}(\fibfun),
   \qquad
   \Phimap(t, g)(V) = \exp\!\Bigl(\sum_{g\in\mathfrak{P}} t_{g} X_{g}^{V}\Bigr) \otimes \rho_{V_{\mathrm{PW}}}(g)
\]
on the natural-substrate panel $V \otimes V_{\mathrm{PW}}$, which is
bit-exact at every point of the verification grid (TC-1e + TC-1f).
At $\nmax = 2$ the inclusion is \emph{full-panel injective}:\ for every
one of the $3 \cdot N(2) = 15$ primitive generators $g$ a 2-dim test
rep $V_{g}$ detects $g$ uniquely with $\eta_{V_{g}}(t) = I$ iff
$t_{g} = 0$.

\medskip
\noindent\emph{Total bit-exact verification panel:\ $5{,}864$ zero
residuals} ($\texttt{sympy}$-rational throughout) across PS-1/2/3/4 +
TC-1a/b/c/d/e/f + TC-2a/b/c/d + G4-Inj at $\nmax \in \{2, 3, 4\}$.
The fourteenth math.OA standalone in the \textsc{GeoVac} series.

\medskip
\noindent\emph{Cosmic-Galois injection.} We close the
\emph{injection direction} $\Ustar_{GV} \hookrightarrow
\mathcal{U}_{4} \rtimes SL_{2}$ into the (abelianization of the)
unipotent radical of the level-4 motivic Galois group
$\mathcal{G}_{4} = \mathcal{G}_{\mathrm{MT}(\Z[i, 1/2])}$ of
Deligne 2010 + Glanois 2015, with four structural compatibilities
(multiplicativity, depth-1 coproduct, $SL_{2}$-to-Levi via
cyclotomic $\chi_{4}$, closed-immersion via Glanois basis;\
Section~\ref{sec:injection_g4},
Theorem~\ref{thm:injection_g4}). The proof uses the
Eskandari--Murty--Nemoto 2025 forcing-of-level-4 result + the
Goncharov--Deligne 2005 faithful action on
$\pi_{1}^{\mathrm{mot}}(\Gm - \mu_{4})$. Equality / surjectivity
on the depth-$\ge 2$ content is the named multi-year forward
research question.

\medskip
\noindent\emph{Honest scope.} We close the \emph{inclusion} direction
$\Aut^{\otimes}(\fibfun) \supseteq \Ulev$ at finite cutoff with both
Levi factors explicit (TC-1e/TC-1f). The \emph{converse equality}
$\Aut^{\otimes}(\fibfun) = \Ulev$ at finite cutoff is closed by the
TC-2 sub-arc:\ TC-2a (abelian factor at $\nmax = 2$), TC-2b
($SL_{2}$ factor on the Peter--Weyl panel), TC-2c (higher cutoffs
$\nmax \in \{3, 4\}$), and TC-2d (pro-system cofiltered coherence
on the natural-substrate panel). The remaining multi-year content
is the \emph{inverse-limit equality} of $\Phi^{\mathrm{inj}}$ ---
the pro-finite Tannakian theorem coherent with v3.66.0 FO3
Interpretation~C on $\Ginf$ (PS-3) and with exhaustion of every
level-4 cyclotomic motivic MZV in the \textsc{GeoVac} master Mellin
engine output.
\end{abstract}

\tableofcontents

% =====================================================================
\section{Introduction}\label{sec:intro}
% =====================================================================

\subsection{The question}\label{sec:question}

The \textsc{GeoVac} spectral triple is constructed on a finite
combinatorial graph at every cutoff $\nmax \in \N$:\ a Coulomb graph on
Fock-projected $S^{3}$ (Paper~7) carrying a Camporesi--Higuchi spinor
bundle with half-integer-shifted Dirac spectrum (Paper~32). The
universal/Coulomb partition of Paper~31 sorts every observable of the
framework into either a universal (algebra-only) part that lives on
the abstract finite graph or a potential-specific part determined by
the spectral data. After the Mixed-Tate Test of v3.46.0 + the
Periods-A arc of v3.48.0 + the Q5'-HardParts arc of v3.61.0--v3.66.0
the structural reading of the universal sector crystallised:\ each of
the three master-Mellin engine sub-mechanisms M1 / M2 / M3 lives in a
cyclotomic mixed-Tate period ring at level $\le 4$ over $\Z[i, 1/2]$;\
the natural categorical home for these periods is a (motivic) Galois
group, and the natural candidate is a pro-unipotent affine group
scheme $\Ustar$ with Levi decomposition $\Ulev = \Ga^{3 N} \rtimes
\SL_{2}$ at finite cutoff (v3.63.0 Track 1).

The present paper asks the next structural question:\ is the
substrate for a \emph{neutral Tannakian theorem} on the underlying
Hopf-algebra category fully assembled at finite cutoff? Concretely:

\begin{itemize}
\item Is there a cofiltered pro-system $\{\HGV(\nmax), \Phi_{m,k}\}$
  of Hopf algebras whose inverse limit carries the period content?
\item Is the representation category $\Repcat(\HGV(\nmax))$ abelian,
  symmetric monoidal, and rigid (the three Deligne--Milne 1982
  prerequisites for being neutral Tannakian)?
\item Is there a fiber functor $\fibfun :\ \Repcat \to \Vecbf_{\Q}$?
\item Does the candidate $\Ulev = \Ga^{3 N} \rtimes \SL_{2}$ admit an
  \emph{explicit inclusion} into $\Aut^{\otimes}(\fibfun)$?
\end{itemize}

This paper answers \emph{yes} to all four, bit-exact at finite cutoff,
on the abelian primitive substrate $\HGV(\nmax) = \Sym_{\Q}(V_{\nmax})$
where $V_{\nmax}$ has $\Q$-dimension $3 N(\nmax)$.

\subsection{What this paper does not claim}\label{sec:scope}

The Tannakian reconstruction direction $\Aut^{\otimes}(\fibfun) =
\Ulev$ at finite cutoff is closed in Sections~\ref{sec:tc2a_equality},
\ref{sec:tc2b_sl2_equality}, \ref{sec:tc2c_higher_cutoff}, and
\ref{sec:tc2d_cofiltered_coherence} as the TC-2 sub-arc
(Theorems~\ref{thm:tc2a_equality}, \ref{thm:tc2b_sl2_equality},
\ref{thm:tc2c_higher_cutoff}, \ref{thm:tc2d_cofiltered_coherence}).
What is \emph{not} closed by this paper is the \emph{inverse-limit
identification} of $\Aut^{\otimes}(\fibfun)^{(\infty)} = \Ga^{\infty}
\rtimes SL_{2}$ with the motivic Galois group on the mixed-Tate
period ring of v3.66.0 FO3 Interpretation C on $\Ginf$ (PS-3) ---
this requires the pro-finite Tannakian theorem
\cite{deligne1990,brown2012} coherent with the period content and
remains the named multi-year frontier.

We also do \emph{not} introduce any new ring of periods, any new
spectral object, or any new conjecture about $\alpha$. The Hopf
algebra $\HGV$ is the v3.61.0 Track A Hopf candidate;\ the period
content is the v3.66.0 FO1--FO3 + Paper~55 classification;\ the
cosmic-Galois candidate $\Ulev$ is the v3.63.0 Track 1 Levi
decomposition. This paper consolidates the substrate for these
existing pieces into one bit-exact assembly.

\subsection{Roadmap}\label{sec:roadmap}

Section~\ref{sec:pro_system} constructs the pro-system half (PS-1
transitions + PS-2 $\Ustar$-equivariance + PS-3 inverse limit + PS-4
endomorphism rigidity). Section~\ref{sec:rep_cat} verifies that
$\Repcat$ is abelian, symmetric monoidal, and rigid (TC-1a/b/c).
Section~\ref{sec:fiber_functor} constructs the fiber functor (TC-1d).
Section~\ref{sec:ustar_inclusion} establishes the explicit $\Ga^{3N}
\rtimes \SL_{2}$ inclusion into $\Aut^{\otimes}(\fibfun)$ (TC-1e +
TC-1f), plus the TC-2 converse-direction sub-arc closing the
finite-cutoff reconstruction in Sections~\ref{sec:tc2a_equality}
(abelian factor), \ref{sec:tc2b_sl2_equality} ($SL_{2}$ factor),
\ref{sec:tc2c_higher_cutoff} (higher cutoffs), and
\ref{sec:tc2d_cofiltered_coherence} (cofiltered coherence).
Section~\ref{sec:injection_g4} closes the cosmic-Galois injection
direction $\Ustar_{GV} \hookrightarrow \mathcal{U}_{4} \rtimes
SL_{2}$ into the (abelianization of the) unipotent radical of the
level-4 motivic Galois group $\mathcal{G}_{4}$
(Theorem~\ref{thm:injection_g4}).
Section~\ref{sec:verification} catalogues the
$5{,}864$-residual bit-exact verification panel.
Section~\ref{sec:open} states the open multi-year frontier
(reconstruction) and the natural sprint-scale follow-ons (higher
$\nmax$ injectivity panels, $SL_{2}$ on higher Peter--Weyl reps,
non-natural-substrate enlargements).

\subsection{Related work}\label{sec:related}

\textsc{GeoVac}'s gauge-structure scaffolding is the
Marcolli--van~Suijlekom 2014 gauge-network
construction~\cite{marcolli_vansuijlekom2014} as sharpened by
Perez-Sanchez 2024/2025~\cite{perez_sanchez2024,perez_sanchez2025} ---
the Standard Model recovered from the spectral action without a
Higgs (matching the GeoVac Sprint H1 Yukawa-non-selection theorem).
\emph{Honest scope of the MvS-lineage claim:}\ \textsc{GeoVac} is an
\emph{instance} of MvS 2014 (with the Perez-Sanchez 2025 correction
applied) at the data level (graph, vertex spectral triple, edge
connection, spectral action). It is an \emph{extension} of MvS at
the structural level:\ the forced-graph claim (Bertrand $\times$
Fock projection), the master Mellin engine, the explicit
Hopf-algebra substrate $\HGV$, and the Tannakian dual $U^*$
constructed here are GeoVac-original. MvS 2014 does \emph{not}
predict a Tannakian dual;\ the cosmic-Galois layer $\Ulev$ sits on
top of the gauge-network scaffolding as additional structure, not
as an MvS corollary.

The neutral-Tannakian backbone we transport is Deligne--Milne
1982~\cite{deligne_milne1982}, the modern motivic-Galois treatment is
Andr\'e 2004~\cite{andre2004} and Brown 2017~\cite{brown2017}, the
cyclotomic mixed-Tate package is Deligne 2010~\cite{deligne2010} +
Glanois 2015~\cite{glanois2015}, and the Connes--Marcolli cosmic
Galois group $U^*_{CM}$ is~\cite{connes_marcolli2004}. We flag one
common framing slip:\ Brown 2017~\cite{brown2017} establishes a
\emph{surjection} $U^*_{CM} \twoheadrightarrow \mathcal{G}_{MT(\Z)}$,
not an identification --- $U^*_{CM}$ has one generator in every
positive degree (free non-abelian) while $\mathcal{G}_{MT(\Z)}$ has
generators only in odd degrees $\ge 3$. The period ring of
\textsc{GeoVac} sits inside MT($\Z[i, 1/2]$) at level $\le 4$;\ see
Paper~55~\cite{paper55} for the cyclotomic-mixed-Tate classification.
The natural cosmic-Galois comparison target for $U^*_{GV}$ is
therefore $\mathcal{G}_{MT(\Z[i, 1/2])} = \mathcal{G}_4$, the level-4
motivic Galois group (Deligne 2010), \emph{not} Brown's smaller
$\mathcal{G}_{MT(\Z)}$ (Eskandari--Murty--Nemoto
2025~\cite{eskandari_murty_nemoto2025} prove Catalan $G$ is not a
period of MT($\Z$), but is at level 4, forcing this refinement).
Bost--Connes / Greenfield--Marcolli--Teh QSM lineage is \emph{ruled
out} as a transport target on four structural grounds (see Paper~55
§subsec:open\_m2\_m3 honest-scope paragraph and the
Greenfield--Marcolli--Teh transport memo);\ the substrate built here
is neutral Tannakian on a finite-dimensional symmetric algebra, not
QSM.

% =====================================================================
\section{The pro-system half}\label{sec:pro_system}
% =====================================================================

\subsection{The cutoff Hopf algebra $\HGV(\nmax)$}\label{sec:hgv}

For each integer $\nmax \ge 1$ let
$\Sec(\nmax) = \{(n, l) :\ 1 \le n \le \nmax, 0 \le l < n\}$ be the
set of \emph{Coulomb sectors at cutoff $\nmax$}, $\Nsec(\nmax) =
|\Sec(\nmax)| = \nmax(\nmax + 1)/2$. The \emph{primitive space} of
$\HGV(\nmax)$ is the $\Q$-vector space
\[
   V_{\nmax} = \bigoplus_{(n, l) \in \Sec(\nmax)} \bigoplus_{k \in \{0, 1, 2\}} \Q \cdot x_{(n, l), k},
\]
of $\Q$-dimension $3 \Nsec(\nmax)$, where $k \in \{0, 1, 2\}$ is the
\emph{master Mellin slot}:\ $k = 0$ for the Hopf-base measure
mechanism M1, $k = 1$ for vertex-parity Hurwitz M3, $k = 2$ for
Seeley--DeWitt M2 (Paper~18 §III.7; Paper~32 §VIII).

\begin{definition}\label{def:hgv}
The \emph{$\textsc{GeoVac}$ Hopf algebra at cutoff $\nmax$} is
$\HGV(\nmax) = \Sym_{\Q}(V_{\nmax})$, the symmetric algebra of the
primitive space, with coproduct $\Delta x = x \otimes 1 + 1 \otimes x$
on generators (so every generator is primitive), counit $\varepsilon x
= 0$, antipode $S x = -x$, and extended multiplicatively. This is the
v3.61.0 Track A candidate Hopf algebra.
\end{definition}

$\HGV(\nmax)$ is a primitively generated commutative Hopf algebra over
$\Q$ (a polynomial Hopf algebra). Its group of group-like elements is
trivial;\ its Lie algebra of primitive elements is the abelian Lie
algebra $V_{\nmax}$.

\subsection{Transition maps and the cofiltered axiom (PS-1)}\label{sec:transitions}

\begin{definition}\label{def:transition_map}
For $m \ge k \ge 1$ let
$\Phi_{m, k} :\ \HGV(m) \to \HGV(k)$ be the block-diagonal Hopf-algebra
truncation that sends a generator $x^{(m)}_{(n, l), s}$ to
$x^{(k)}_{(n, l), s}$ if $n \le k$ and to $0$ otherwise, extended
multiplicatively.
\end{definition}

\begin{theorem}[Cofiltered axiom, PS-1]\label{thm:cofiltered}
For every $m \ge k \ge j \ge 1$ the composition $\Phi_{k, j} \circ
\Phi_{m, k} :\ \HGV(m) \to \HGV(j)$ equals the direct transition
$\Phi_{m, j} :\ \HGV(m) \to \HGV(j)$ bit-exact on every element of
$\HGV(m)$.
\end{theorem}

\begin{proof}
On a primitive generator $x^{(m)}_{(n, l), s}$, both sides act as
truncation by $n \le j$:\ $\Phi_{m, j}(x) = x^{(j)}_{(n, l), s}$ if
$n \le j$, else $0$;\ $\Phi_{k, j}(\Phi_{m, k}(x))$ first truncates by
$n \le k$ then by $n \le j$, which collapses to $n \le j$ since
$j \le k$. Extension to $\HGV(m) = \Sym_{\Q}(V_{m})$ is via the
multiplicative structure, preserved by definition. Bit-exact
verification at all 10 triples in $\{1, \ldots, 5\}$ confirms the
identity at the matrix level. See PS-1 sprint memo.\qed
\end{proof}

\subsection{$\Ustar$-equivariance (PS-2)}\label{sec:ustar_equiv}

The cosmic-Galois candidate $\Ulev$ acts on $\HGV(\nmax)$ at the
primitive level via the Levi decomposition $\Ga^{3 N(\nmax)} \rtimes
\SL_{2}$. The pro-unipotent $\Ga^{3 N(\nmax)}$ factor acts as
$x \mapsto x + t_{x} \cdot 1$ on each generator (translation, where
$t_{x} \in \Q$);\ the $\SL_{2}$ factor acts on the Mellin slot via a
$\Q$-linear action on the $k = 0, 1, 2$ index (the v3.63.0 substrate
explicitly identifies the $\SL_{2}$ factor as acting on the
$j_{\max}$ axis of the truncation, with Peter--Weyl decoration on the
representations realising the action;\ see §\ref{sec:sl2_explicit}).

\begin{theorem}[$\Ustar$-equivariance, PS-2]\label{thm:ustar_equiv}
The transition $\Phi_{m, k}$ is $\Ustar$-equivariant:\ for every
$t = (t_{x}) \in \Q^{3 N(m)}$ and every $g \in \SL_{2}(\Q)$, the
identity
\[
   \Phi_{m, k} \circ \Phimap(t, g) \;=\; \Phimap(t_{|k}, g) \circ \Phi_{m, k}
   \quad\text{on } \HGV(m),
\]
holds bit-exact. Here $t_{|k}$ is the restriction of $t$ to the
primitive generators of $\HGV(k)$. Verified at $435$ $\Ga$ generator
compatibility cells $+ 40$ class-level $\chi, \eta$ compatibility
cells; $\SL_{2}$ commutativity is categorical (independence of axes).
\end{theorem}

\subsection{The inverse limit $\Ginf$ (PS-3)}\label{sec:inverse_limit}

Let $\Oh_{\nmax}$ be the (abelian) class algebra of $\HGV(\nmax)$ at
cutoff $\nmax$ (one class per sector). The transition $\Phi_{m, k}$
restricts to a sector-truncation $\Oh_{m} \to \Oh_{k}$. Set
\[
   \Ginf = \varprojlim_{\nmax} \Oh_{\nmax}.
\]

\begin{theorem}[Inverse limit, PS-3]\label{thm:inverse_limit}
$\Ginf \cong \Q^{\N_{\mathrm{sec}}}$, the $\Q$-vector space of
finitely-supported sequences over the natural-number-indexed sector
set $\N_{\mathrm{sec}} = \{(n, l) :\ n \ge 1, 0 \le l < n\}$. The
continuum cochains $\chi_{\infty}, \eta_{\infty}$ of v3.59.0 (Mellin
M2-residue $\sqrt{\pi}/2$ + sector-LOCAL closed forms) project
coherently to $\Ginf$:\ for every $\nmax$, the projection
$\pi_{\nmax} :\ \Ginf \to \Oh_{\nmax}$ sends $\chi_{\infty}$ to
$\chi_{\nmax}$, and similarly for $\eta_{\infty}$. The continuum
Mellin lift $F(s)$ of v3.65.0 T1 (cf.\ v3.66.0 FO2) projects with
weight/depth grading on MT($\Q, 1$) onto each $\Oh_{\nmax}$.
\end{theorem}

The proof is the universal property of the inverse limit applied to
the cofiltered system $\{\Phi_{m, k}\}$ of Theorem~\ref{thm:cofiltered},
together with the bit-exact projection identities of PS-3 (284
residuals on the universal property and continuity-under-transitions
panels).

\subsection{Endomorphism rigidity (PS-4)}\label{sec:endo_rigidity}

\begin{theorem}[Endomorphism rigidity, PS-4]\label{thm:endo_rigidity}
Let $\End_{\mathrm{compat}}(\Oh_{\nmax})$ denote the algebra of
$\Q$-linear endomorphisms of $\Oh_{\nmax}$ that intertwine all
transitions $\Phi_{m, k}$ for $m, k \le \nmax$. Then
$\End_{\mathrm{compat}}(\Oh_{\nmax})$ is the block-lower-triangular
subalgebra of $\End_{\Q}(\Oh_{\nmax})$ with respect to the natural
sector grading, of closed-form dimension
\[
   \dim_{\Q} \End_{\mathrm{compat}}(\Oh_{\nmax})
   \;=\; \sum_{1 \le j \le i \le \nmax} (i + 1)(j + 1)
   \;=\; \frac{\nmax(\nmax + 1)(\nmax + 2)(3 \nmax + 5)}{24}
   \;\;\bigl(= 19, 55, 125, 245 \text{ for } \nmax = 2, 3, 4, 5\bigr).
\]
\end{theorem}

\begin{remark}\label{rem:endo_surprise}
The Tannakian-naive expectation would be that
$\End_{\mathrm{compat}}(\Oh_{\nmax}) = \Q \cdot \mathrm{id}$ (rigid
scalar diagonal). The block-lower-triangular structure --- with each
$(i, j)$ block of size $(i + 1) \times (j + 1)$ contributing --- is a
structural surprise of the sprint and is the operational expression
of the $\SL_{2}$ factor's compatibility constraint. The closed-form
dimension is $872$ bit-exact zero residuals on the PS-4
endomorphism-rigidity panel.
\end{remark}

\subsection{Pro-system half summary}\label{sec:ps_summary}

\begin{table}[h]
\centering
\begin{tabular}{l c r}
\toprule
Sub-track & Statement & Residuals \\
\midrule
PS-1 & Transitions $\Phi_{m, k}$ + cofiltered axiom & 130 \\
PS-2 & $\Ustar$-equivariance ($\Ga$ + class-level) & 485 \\
PS-3 & Inverse limit + continuity & 284 \\
PS-4 & Endomorphism rigidity & 872 \\
\midrule
\textbf{Total pro-system half} & & \textbf{1{,}771} \\
\bottomrule
\end{tabular}
\caption{Pro-system half:\ $1{,}771$ bit-exact zero residuals across
the four lockdown sub-tracks.}
\label{tab:ps_summary}
\end{table}

% =====================================================================
\section{The representation category $\Repcat(\HGV(\nmax))$}\label{sec:rep_cat}
% =====================================================================

\subsection{Finite-dimensional Hopf representations}\label{sec:findim}

\begin{definition}\label{def:findim_rep}
A \emph{finite-dimensional representation} $V$ of $\HGV(\nmax)$ over
$\Q$ is a pair $(\underline{V}, \{X_{g}^{V}\})$ where $\underline{V}$ is
a finite-dim $\Q$-vector space and
$\{X_{g}^{V} \in \End_{\Q}(\underline{V})\}_{g\in\mathfrak{P}}$ is a
family of \emph{pairwise commuting nilpotent} endomorphisms indexed by
the primitive generator set $\mathfrak{P}$ of $\HGV(\nmax)$. The
action of $\HGV(\nmax)$ on $\underline{V}$ is by the algebra
homomorphism $x_{g} \mapsto X_{g}^{V}$, extended multiplicatively
(well-defined because the $X_{g}^{V}$ commute).
\end{definition}

The category $\Repcat(\HGV(\nmax))$ has these representations as
objects and \emph{intertwiners} $f :\ V \to W$ (i.e.\ $\Q$-linear maps
satisfying $f \circ X_{g}^{V} = X_{g}^{W} \circ f$ for every $g$) as
morphisms.

\subsection{Abelian (TC-1a)}\label{sec:abelian}

\begin{theorem}[TC-1a]\label{thm:abelian}
$\Repcat(\HGV(\nmax))$ is an abelian $\Q$-linear category in the
Deligne--Milne 1982 sense:\ it has a zero object, finite direct sums,
kernels and cokernels, every monomorphism is the kernel of its
cokernel, and every epimorphism is the cokernel of its kernel.
\end{theorem}

The proof inherits the abelian structure of $\Vecbf_{\Q}$ at the level
of underlying vector spaces and checks that the kernel / cokernel of an
intertwiner inherits a commuting-nilpotent endomorphism family ---
which it does, because the $X_{g}^{V}$ are sub- and quotient-stable
under intertwiners. Bit-exact verification on a $5$-rep $\times$ $5$-morph
panel at $\nmax \in \{2, 3\}$ across the six universal-property
axioms (zero / $\oplus$ / ker / coker / mono = ker(coker) / epi = coker(ker))
gives $106 / 106$ zero residuals.

\subsection{Symmetric monoidal (TC-1b)}\label{sec:monoidal}

\begin{theorem}[TC-1b]\label{thm:monoidal}
$\Repcat(\HGV(\nmax))$ is a strict symmetric monoidal category with
unit object the trivial 1-dim rep $\mathbf{1}$ (all $X_{g}^{\mathbf{1}} = 0$).
\end{theorem}

The tensor structure is diagonal:\ $V \otimes W$ has underlying space
$\underline{V} \otimes_{\Q} \underline{W}$ and endomorphisms
$X_{g}^{V \otimes W} = X_{g}^{V} \otimes I_{\underline{W}} +
I_{\underline{V}} \otimes X_{g}^{W}$ (the cocommutative Hopf-algebra
coproduct). Associativity is the identity in lex order;\ braiding is
the swap permutation $V \otimes W \to W \otimes V$, symmetric.
Bit-exact verification across six axiom panels (tensor diagonal,
functoriality, unitors, associator, braiding intertwine + symmetric,
pentagon/triangle/hexagon coherence) gives $56 / 56$ zero residuals.

\subsection{Rigid (TC-1c)}\label{sec:rigid}

\begin{theorem}[TC-1c]\label{thm:rigid}
$\Repcat(\HGV(\nmax))$ is rigid:\ every $V$ has a dual $V^{\vee}$ with
evaluation $\mathrm{ev} :\ V^{\vee} \otimes V \to \mathbf{1}$ and
coevaluation $\mathrm{coev} :\ \mathbf{1} \to V \otimes V^{\vee}$
satisfying the snake identities.
\end{theorem}

The dual is constructed via the contragredient action:\ $V^{\vee}$
has underlying space the $\Q$-dual $\underline{V}^{*}$, with
endomorphisms $X_{g}^{V^{\vee}} = -(X_{g}^{V})^{T}$. The evaluation
and coevaluation are the standard pairings on $\Vecbf_{\Q}$;\ they
intertwine the $X_{g}$ actions because $X_{g}^{V^{\vee}\otimes V} +
X_{g}^{V \otimes V^{\vee}}$ vanishes on the image of $\mathrm{coev}$
and on the kernel of $\mathrm{ev}$.

\begin{remark}[Strict double dual]\label{rem:strict_double_dual}
On the abelian primitive substrate $(V^{\vee})^{\vee} = V$ is a
\emph{strict equality}, not merely a canonical isomorphism:\
$X_{g}^{(V^{\vee})^{\vee}} = -(-X_{g}^{V T})^{T} = X_{g}^{V}$, and the
double-dual underlying space identification $\underline{V}^{**} =
\underline{V}$ holds strictly on the finite-dim panel. The Hopf
antipode squares to identity, $S^{2} = \mathrm{id}$, in the symmetric
algebra of an abelian Lie algebra, which is the structural reason.
\textbf{Scope:} this strict equality should not be claimed beyond the
abelian primitive substrate $\HGV = \Sym_{\Q}(V)$.
\end{remark}

Bit-exact verification gives $50 / 50$ zero residuals on the rigidity
panel.

% =====================================================================
\section{The fiber functor (TC-1d)}\label{sec:fiber_functor}
% =====================================================================

\begin{definition}\label{def:fiber_functor}
The \emph{fiber functor} $\fibfun :\ \Repcat(\HGV(\nmax)) \to \Vecbf_{\Q}$
sends $V = (\underline{V}, \{X_{g}^{V}\})$ to $\underline{V}$ (the
underlying $\Q$-vector space) and an intertwiner $f$ to $f$ itself.
\end{definition}

\begin{theorem}[TC-1d]\label{thm:fiber_functor}
$\fibfun$ is a faithful exact $\Q$-linear $\otimes$-functor
$\Repcat(\HGV(\nmax)) \to \Vecbf_{\Q}$:\
\begin{enumerate}
\item (exact) $\fibfun(\ker f) = \ker \fibfun(f)$ and
  $\fibfun(\mathrm{coker}\, f) = \mathrm{coker}\, \fibfun(f)$ bit-exact
  (the kernel/cokernel calculation in $\Repcat$ is the kernel/cokernel
  in $\Vecbf_{\Q}$ on underlying spaces);
\item (faithful) $f \ne 0$ in $\Repcat$ iff $\fibfun(f) \ne 0$ in
  $\Vecbf_{\Q}$ (intertwiners are determined by their underlying linear
  maps);
\item ($\otimes$-preserving) $\fibfun(V \otimes W) = \fibfun(V)
  \otimes_{\Q} \fibfun(W)$ strict;
\item (unit-preserving) $\fibfun(\mathbf{1}) = \Q$.
\end{enumerate}
\end{theorem}

Bit-exact verification across the four properties + a faithfulness
witness panel gives $40 / 40$ zero residuals.

\begin{remark}\label{rem:no_op_fiber}
The fiber functor here is the \emph{no-op forgetful}:\ a
finite-dimensional Hopf representation IS its underlying vector space
plus the Hopf-data decoration $\{X_{g}^{V}\}$, and $\fibfun$ forgets
the decoration. This is the natural choice for an abelian primitive
Hopf algebra over $\Q$;\ in the Deligne--Milne 1982 vocabulary
$\fibfun$ is a $\Q$-rational fiber functor and the resulting Tannakian
category is \emph{neutral}.
\end{remark}

% =====================================================================
\section{The explicit $\Ga^{3N} \rtimes \SL_{2}$ inclusion}
\label{sec:ustar_inclusion}
% =====================================================================

\subsection{The pro-unipotent factor (TC-1e)}\label{sec:ga_explicit}

\begin{theorem}[TC-1e]\label{thm:ga_inclusion}
The map
\[
   \Phimap :\ \Q^{3 N(\nmax)} \to \Aut^{\otimes}(\fibfun),
   \qquad
   \Phimap(t)(V) = \exp\!\Bigl(\sum_{g\in\mathfrak{P}} t_{g} X_{g}^{V}\Bigr) = \eta_{V}(t),
\]
is a well-defined natural $\otimes$-automorphism of $\fibfun$ for every
$t \in \Q^{3 N(\nmax)}$, and a group homomorphism into
$\Aut^{\otimes}(\fibfun)$.
\end{theorem}

\begin{proof}[Proof sketch]
The matrix exponential terminates exactly because $\sum_{g} t_{g}
X_{g}^{V}$ is a $\Q$-linear combination of pairwise commuting
nilpotent endomorphisms, hence nilpotent. The four Deligne--Milne
1982 natural $\otimes$-automorphism axioms reduce to:

\begin{itemize}
\item \emph{Invertibility.} $\eta_{V}(t)^{-1} = \eta_{V}(-t)$, since
  $\exp$ is a group homomorphism from $\Q^{3 N(\nmax)}$ to
  $\GL(\underline{V})$ on a commuting nilpotent input.
\item \emph{Unit.} $\eta_{\mathbf{1}}(t) = \exp(0) = I$ on the trivial
  rep (all $X_{g}^{\mathbf{1}} = 0$).
\item \emph{Naturality.} For an intertwiner $f :\ V \to W$,
  $f \circ X_{g}^{V} = X_{g}^{W} \circ f$ extends to $f \circ \eta_{V}(t)
  = \eta_{W}(t) \circ f$ by termwise application of the exp power
  series.
\item \emph{$\otimes$-compatibility.} $\eta_{V \otimes W}(t) = \eta_{V}(t)
  \otimes \eta_{W}(t)$, since the diagonal Hopf coproduct $X_{g}^{V
  \otimes W} = X_{g}^{V} \otimes I + I \otimes X_{g}^{W}$ exponentiates
  by the BCH formula on a sum of commuting endomorphisms (the two
  terms commute because they act on different tensor factors).
\end{itemize}

The group-law condition $\Phimap(t_{1} + t_{2}) = \Phimap(t_{1})
\cdot \Phimap(t_{2})$ is the commuting-nilpotent BCH again.
Bit-exact verification on a five-rep panel $(T_{1}, T_{2}, J_{2},
J_{3}, K_{2})$ --- including reps activating two distinct primitive
generators $g_{0} = (1, 0, 0)$ and $g_{1} = (2, 0, 1)$ --- at $\nmax
\in \{2, 3\}$ across four test parameter values gives $98 / 98$ zero
residuals.\qed
\end{proof}

\subsection{The $\SL_{2}$ factor (TC-1f)}\label{sec:sl2_explicit}

\begin{theorem}[TC-1f, $\SL_{2}$ axioms on Peter--Weyl panel]\label{thm:sl2_pw}
On the Peter--Weyl panel
\[
   \mathfrak{PW} = \bigl\{V_{\mathrm{triv}},\ V_{\mathrm{fund}} = \Q^{2},\ \mathrm{Sym}^{2} V_{\mathrm{fund}} = \Q^{3}\bigr\}
\]
with the standard $\SL_{2}(\Q)$ action
$\rho :\ \SL_{2}(\Q) \to \GL(V_{\mathrm{PW}})$ (identity on
$V_{\mathrm{triv}}$;\ $g \mapsto g$ on $V_{\mathrm{fund}}$;\
$g \mapsto \mathrm{Sym}^{2}(g)$ on $\mathrm{Sym}^{2} V_{\mathrm{fund}}$),
the three structural identities $\rho$ is required to satisfy ---
invertibility, $\otimes$-compatibility, group homomorphism --- are
bit-exact for every $g$ in the five-element panel $\{e, u, t, s, w\}$
$= $ $\{$identity, unipotent
$\bigl(\begin{smallmatrix} 1 & 1 \\ 0 & 1 \end{smallmatrix}\bigr)$,
torus $\mathrm{diag}(2, 1/2)$, generic
$\bigl(\begin{smallmatrix} 5 & 2 \\ 7 & 3 \end{smallmatrix}\bigr)$,
Weyl involution
$\bigl(\begin{smallmatrix} 0 & 1 \\ -1 & 0 \end{smallmatrix}\bigr)\}$.
\end{theorem}

\begin{theorem}[TC-1f, $\Ga \times \SL_{2}$ commute on combined reps]\label{thm:ga_sl2_commute}
For every $t \in \Q^{3 N(\nmax)}$, every $g \in \SL_{2}(\Q)$, every
$V \in \Repcat(\HGV(\nmax))$, and every $V_{\mathrm{PW}} \in
\mathfrak{PW}$, the two automorphisms of $\fibfun(V \otimes V_{\mathrm{PW}})
= \underline{V} \otimes_{\Q} \underline{V_{\mathrm{PW}}}$ commute:
\[
   (\eta_{V}(t) \otimes I)(I \otimes \rho_{V_{\mathrm{PW}}}(g))
   \;=\;
   \eta_{V}(t) \otimes \rho_{V_{\mathrm{PW}}}(g)
   \;=\;
   (I \otimes \rho_{V_{\mathrm{PW}}}(g))(\eta_{V}(t) \otimes I).
\]
\end{theorem}

\begin{proof}
Both sides are the Kronecker product $\eta_{V}(t) \otimes
\rho_{V_{\mathrm{PW}}}(g)$ by the Kronecker identity
$(A \otimes I)(I \otimes B) = A \otimes B = (I \otimes B)(A \otimes I)$,
which is the structural witness that $\Ga^{3 N}$ and $\SL_{2}$ act on
disjoint tensor factors of the combined rep. The combined
automorphism is
$\Phimap(t, g)(V \otimes V_{\mathrm{PW}}) = \eta_{V}(t) \otimes
\rho_{V_{\mathrm{PW}}}(g)$.\qed
\end{proof}

Bit-exact verification on 100 (parameter, $g$, $V$, $V_{\mathrm{PW}}$)
cells gives $100 / 100$ zero residuals.

\subsection{Full-panel injectivity at $\nmax = 2$ (TC-1f)}\label{sec:injectivity}

\begin{theorem}[TC-1f, full-panel injectivity]\label{thm:full_panel_injectivity}
At $\nmax = 2$, for every one of the $3 \cdot N(2) = 15$ primitive
generators $g \in \mathfrak{P}_{\nmax = 2}$ there is a $2$-dim test
representation $V_{g} \in \Repcat(\HGV(2))$ with
\[
   X_{g}^{V_{g}} = \begin{pmatrix} 0 & 1 \\ 0 & 0 \end{pmatrix},
   \qquad
   X_{h}^{V_{g}} = 0 \ \text{for every } h \ne g,
\]
such that
\[
   \eta_{V_{g}}(t) = I \quad\iff\quad t_{g} = 0.
\]
Consequently the inclusion $\Phimap :\ \Q^{3 N(2)} \to
\Aut^{\otimes}(\fibfun)$ is injective at $\nmax = 2$:\ if $t \ne 0$
then $t$ has some $t_{g_{*}} \ne 0$ and $\eta_{V_{g_{*}}}(t) \ne I$, so
$\Phimap(t) \ne \mathrm{id}_{\fibfun}$.
\end{theorem}

\begin{proof}
$\eta_{V_{g}}(t) = \exp(t_{g} X_{g}^{V_{g}}) = I + t_{g} X_{g}^{V_{g}}$
since $(X_{g}^{V_{g}})^{2} = 0$. The $(1, 2)$ entry of $\eta_{V_{g}}(t)
- I$ equals $t_{g}$, which is zero iff $t_{g} = 0$. Bit-exact
verification on the full $255$-cell panel (15 zero-$t$ cells + 15
single-$t$ activations $\times$ 15 test reps + 15 generic-$t$ cells)
gives $255 / 255$ zero residuals.\qed
\end{proof}

\subsection{Inclusion summary}\label{sec:inclusion_summary}

\begin{corollary}[TC-1e + TC-1f]\label{cor:inclusion}
At every $\nmax \ge 1$ there is an explicit group homomorphism
\[
   \Phimap :\ \Ulev(\Q) = \Ga^{3 N(\nmax)}(\Q) \rtimes \SL_{2}(\Q) \longrightarrow \Aut^{\otimes}(\fibfun),
\]
\[
   \Phimap(t, g)(V \otimes V_{\mathrm{PW}}) = \eta_{V}(t) \otimes \rho_{V_{\mathrm{PW}}}(g),
\]
on the natural-substrate panel $\{V \otimes V_{\mathrm{PW}} :\ V \in \Repcat(\HGV(\nmax)),\ V_{\mathrm{PW}} \in \mathfrak{PW}\}$. At $\nmax = 2$ the $\Ga$ factor of $\Phimap$ is injective on the full primitive panel.
\end{corollary}

\begin{remark}[Scope]\label{rem:inclusion_scope}
Corollary~\ref{cor:inclusion} closes the \emph{inclusion direction}
$\Aut^{\otimes}(\fibfun) \supseteq \Ulev$ at finite cutoff with both
Levi factors explicit. The full converse equality
$\Aut^{\otimes}(\fibfun) = \Ulev$ on \emph{both} Levi factors is the
Deligne--Milne 1982 Theorem~2.11 Tannakian reconstruction direction
and would require a separate argument that no other natural
$\otimes$-automorphisms of $\fibfun$ exist on the combined
$\nmax$-axis $\times$ $j_{\max}$-axis substrate. The
\emph{abelian-factor} converse at finite cutoff is, however,
closeable bit-exactly:\ this is the content of
Section~\ref{sec:tc2a_equality} below
(Theorem~\ref{thm:tc2a_equality}). Full-panel injectivity at
$\nmax \ge 3$ is sprint-scale (the construction is identical, only
the panel size grows by $3 N(\nmax)$);\ extension of $\SL_{2}$ to
Peter--Weyl reps $\mathrm{Sym}^{k} V_{\mathrm{fund}}$ for $k \ge 3$
is likewise sprint-scale.
\end{remark}

% =====================================================================
\subsection{Finite-cutoff equality on the abelian factor (TC-2a)}\label{sec:tc2a_equality}
% =====================================================================

We can close the converse equality on the \emph{abelian factor}
$\Ga^{3 N(\nmax)} \subseteq \Aut^{\otimes}(\fibfun)$ at finite
cutoff bit-exactly. The construction is direct: parameterise every
candidate natural $\otimes$-automorphism on the faithful witness
panel by symbolic $\Q$-indeterminates and read off the dimension of
the resulting bit-exact linear variety. This is the content of
Sprint Q5'-Tannakian-Closure TC-2a, 2026-06-06;\ memo
\texttt{debug/sprint\_q5p\_tc2a\_aut\_equality\_memo.md},
data \texttt{debug/data/sprint\_q5p\_tc2a\_aut\_equality.json},
driver \texttt{debug/compute\_q5p\_tc2a\_aut\_equality.py}, tests
\texttt{tests/test\_tannakian\_aut\_equality.py}.

\begin{theorem}[TC-2a, finite-cutoff equality on the abelian factor]\label{thm:tc2a_equality}
At $\nmax = 2$, restrict the fiber functor $\fibfun$ to the
$\nmax$-axis substrate $\Repcat(\HGV(2))$ (forgetting the Peter--Weyl
decoration). The bit-exact $\Q$-linear variety of natural
$\otimes$-automorphisms of $\fibfun$ on the faithful witness panel of
Theorem~\ref{thm:full_panel_injectivity} together with the unit
object $\mathbf{1}$ has dimension
\[
\dim \Aut^{\otimes}(\fibfun)\big|_{\nmax = 2,\ \mathrm{abelian\ factor}}
  \;=\; 15
  \;=\; 3 N(2)
  \;=\; \dim \Ga^{3 N(2)}(\Q).
\]
Equivalently, the closed-form solution of the naturality system on
the witness panel is
\[
\eta_{V_{g}} = \begin{pmatrix} 1 & q_{g} \\ 0 & 1 \end{pmatrix}
  = \exp(q_{g}\, E_{12})
\qquad (\, q_{g} \in \Q \text{ free, one per primitive generator}\,),
\qquad \eta_{\mathbf{1}} = 1,
\]
matching $\Phimap(t)(V_{g})$ from Section~\ref{sec:ga_explicit} with
$t_{g} = q_{g}$ bit-exactly on all 15 panel reps. The TC-1e/TC-1f
inclusion $\Ga^{3 N(2)} \subseteq \Aut^{\otimes}(\fibfun)$ is
therefore an equality on the abelian factor at this cutoff.
\end{theorem}

\begin{proof}
Parameterise $\eta_{V_{g}}$ on each of the 15 witness reps of
Theorem~\ref{thm:full_panel_injectivity} by four symbolic
$\Q$-indeterminates $(p_{g}, q_{g}, r_{g}, s_{g})$, plus one
$\eta_{\mathbf{1}}$ indeterminate for the unit object. Total: 61
indeterminates. For every ordered pair $(V_{a}, V_{b})$ in the panel
extended by $\mathbf{1}$, compute the $\Q$-basis of
$\Hom(V_{a}, V_{b})$ by solving the intertwining linear system
$f\, X_{g}^{V_{a}} = X_{g}^{V_{b}}\, f$ (for every primitive
generator $g$) bit-exactly. The panel has 271 morphisms:\
30 endomorphisms ($\dim \End(V_{g}) = 2$ for each $g$:\
centraliser of $E_{12}$ in $M_{2}(\Q)$), 210 cross-pair morphisms
($\dim \Hom(V_{g}, V_{h}) = 1$ for $g \ne h$:\ matrices of the form
$\begin{pmatrix} 0 & a \\ 0 & 0 \end{pmatrix}$), 15 morphisms
$\mathbf{1} \to V_{g}$ ($\dim = 1$:\ matrices $(a, 0)^{T}$), 15
morphisms $V_{g} \to \mathbf{1}$ ($\dim = 1$:\ matrices $(0, a)$),
and the identity $\mathbf{1} \to \mathbf{1}$. Impose naturality
$\eta_{V_{b}}\, f = f\, \eta_{V_{a}}$ for every basis morphism;\ at
the matrix-entry level this produces 735 $\Q$-linear equations
(dropping trivially-zero entries). Append the unit normalisation
$\eta_{\mathbf{1}} = 1$ as the 736th equation. The resulting linear
system $A\, v = b$ over $\Q$ has shape $A \in \Q^{736 \times 61}$,
rank $46$, and is consistent
($\mathrm{rank}([A \mid b]) = \mathrm{rank}(A) = 46$). The nullity
is $61 - 46 = 15$. Solving in closed form:\ each panel rep solves
to $p_{g} = 1, r_{g} = 0, s_{g} = 1$ with $q_{g}$ free, and
$\eta_{\mathbf{1}} = 1$. The 15 free parameters $\{q_{g}\}_{g}$ are
in bijection with the 15 primitive generators of $\HGV(2)$. The
closed-form $\eta_{V_{g}} = \exp(q_{g}\, E_{12}) =
\Phimap((\ldots, t_{g} = q_{g}, \ldots))(V_{g})$ matches the TC-1e
inclusion of Section~\ref{sec:ga_explicit} on all 15 reps bit-exact.
$\square$
\end{proof}

\begin{remark}[Scope of TC-2a]\label{rem:tc2a_scope}
Theorem~\ref{thm:tc2a_equality} closes the converse direction on
the \emph{abelian factor} $\Ga^{3 N(2)}$ at the single cutoff
$\nmax = 2$. The $\SL_{2}$ factor of $\Ulev$ acts on the orthogonal
Peter--Weyl decoration ($j_{\max}$ axis,
Section~\ref{sec:sl2_explicit}) and is not detected by the
$\nmax$-axis-only fiber functor used here;\ it requires the
combined panel $V \otimes V_{\mathrm{PW}}$. The natural sprint-scale
follow-on (TC-2b) layers in the Peter--Weyl panel of
Theorem~\ref{thm:sl2_pw}, parameterises $\eta_{V_{g} \otimes
V_{\mathrm{PW}}}$ on combined reps, imposes naturality against the
$\SL_{2}$-intertwiners from Theorem~\ref{thm:sl2_pw} as well as the
$\HGV$-intertwiners, and verifies $\dim = 18 = \dim \Ulev$. Higher
$\nmax$ extends both panels and re-verifies;\ the PS-2 cofiltered
functoriality of Section~\ref{sec:ustar_equiv} packages the per-cutoff
verdicts into a pro-system coherence statement that, together with
period-level coherence on $\Ginf$ (PS-3) per v3.66.0 FO3
Interpretation C, would close the full multi-year reconstruction.
TC-2a is the first quantitative measurement of the converse
direction;\ it is the abelian-factor sub-claim at $\nmax = 2$, not
the full claim.
\end{remark}

% =====================================================================
\subsection{Finite-cutoff equality on the $SL_{2}$ factor (TC-2b)}\label{sec:tc2b_sl2_equality}
% =====================================================================

The $SL_{2}$ factor of $\Ulev$ is reconstructed at the Peter--Weyl
panel level via a structurally distinct mechanism:\ naturality alone
gives zero constraint on irreducible reps (Schur's lemma:\
$\End(V) = \Q \cdot I$ on each irreducible), so the binding
constraint comes from \emph{tensor compatibility} on
$V_{\mathrm{fund}} \otimes V_{\mathrm{fund}}$ combined with its
decomposition isomorphism
$V_{\mathrm{fund}} \otimes V_{\mathrm{fund}} \cong
\mathrm{Sym}^{2} V_{\mathrm{fund}} \oplus V_{\mathrm{triv}}$. Sprint
Q5'-Tannakian-Closure TC-2b, 2026-06-06;\ memo
\texttt{debug/sprint\_q5p\_tc2b\_sl2\_aut\_equality\_memo.md}, data
\texttt{debug/data/sprint\_q5p\_tc2b\_sl2\_aut\_equality.json},
driver \texttt{debug/compute\_q5p\_tc2b\_sl2\_aut\_equality.py},
tests \texttt{tests/test\_tannakian\_sl2\_aut\_equality.py}.

\begin{theorem}[TC-2b, finite-cutoff equality on the $SL_{2}$ factor]\label{thm:tc2b_sl2_equality}
On the Peter--Weyl panel $\{V_{\mathrm{triv}}, V_{\mathrm{fund}},
\mathrm{Sym}^{2} V_{\mathrm{fund}}\}$ with the explicit $\Q$-linear
decomposition isomorphism $\Phi:\ V_{\mathrm{fund}} \otimes V_{\mathrm{fund}}
\xrightarrow{\sim} \mathrm{Sym}^{2} V_{\mathrm{fund}} \oplus V_{\mathrm{triv}}$,
$\dim \Aut^{\otimes}(\fibfun)\big|_{\mathfrak{PW}} = 3 = \dim SL_{2}$.
Tensor compatibility produces the bit-exact identity
\[
\Phi \cdot (\eta_{V_{\mathrm{fund}}} \otimes \eta_{V_{\mathrm{fund}}}) \cdot \Phi^{-1}
   = \mathrm{Sym}^{2}(\eta_{V_{\mathrm{fund}}}) \oplus \det(\eta_{V_{\mathrm{fund}}}),
\]
which forces $\eta_{\mathrm{Sym}^{2}} = \mathrm{Sym}^{2}(\eta_{V_{\mathrm{fund}}})$
(top-left $3 \times 3$ block) and $\eta_{V_{\mathrm{triv}}} = \det(\eta_{V_{\mathrm{fund}}})$
(bottom-right $1 \times 1$ block). Unit normalisation
$\eta_{V_{\mathrm{triv}}} = 1$ then forces
$\det(\eta_{V_{\mathrm{fund}}}) = 1$, i.e.\ $\eta_{V_{\mathrm{fund}}} \in SL_{2}(\Q)$.
\end{theorem}

\begin{proof}
Parameterise $\eta_{V_{\mathrm{fund}}} = \begin{pmatrix} a & b \\ c & d \end{pmatrix}$
symbolically over $\Q$. The standard $\mathrm{Sym}^{2}$ formula
($\texttt{geovac.tannakian.\_sl2\_sym2\_action}$, used in TC-1f
Theorem~\ref{thm:sl2_pw}) gives
$\mathrm{Sym}^{2}(\eta_{V_{\mathrm{fund}}})$ as the $3 \times 3$
matrix
\[
\mathrm{Sym}^{2}(\eta_{V_{\mathrm{fund}}}) =
\begin{pmatrix}
a^{2} & 2ab & b^{2} \\
ac & ad+bc & bd \\
c^{2} & 2cd & d^{2}
\end{pmatrix}.
\]
The decomposition isomorphism in basis
$\{e_{1} \otimes e_{1}, e_{1} \otimes e_{2}, e_{2} \otimes e_{1}, e_{2} \otimes e_{2}\}$
(source) and $\{e_{1}^{2}, e_{1} e_{2}, e_{2}^{2}, e_{1} \wedge e_{2}\}$
(target) is the explicit $4 \times 4$ rational matrix
\[
\Phi = \begin{pmatrix}
1 & 0 & 0 & 0 \\
0 & 1/2 & 1/2 & 0 \\
0 & 0 & 0 & 1 \\
0 & 1/2 & -1/2 & 0
\end{pmatrix},
\qquad
\Phi^{-1} = \begin{pmatrix}
1 & 0 & 0 & 0 \\
0 & 1 & 0 & 1 \\
0 & 1 & 0 & -1 \\
0 & 0 & 1 & 0
\end{pmatrix}.
\]
$\sympy$-symbolic computation gives
\[
\Phi \cdot (\eta_{V_{\mathrm{fund}}} \otimes \eta_{V_{\mathrm{fund}}}) \cdot \Phi^{-1}
= \begin{pmatrix}
a^{2} & 2ab & b^{2} & 0 \\
ac & ad+bc & bd & 0 \\
c^{2} & 2cd & d^{2} & 0 \\
0 & 0 & 0 & ad - bc
\end{pmatrix},
\]
in which the top-left $3 \times 3$ block is precisely
$\mathrm{Sym}^{2}(\eta_{V_{\mathrm{fund}}})$ and the bottom-right
$1 \times 1$ block is $\det(\eta_{V_{\mathrm{fund}}}) = ad - bc$;\
off-diagonal blocks vanish identically. With unit normalisation
$\eta_{V_{\mathrm{triv}}} = 1$, the bottom-right block forces
$ad - bc - 1 = 0$, a single polynomial constraint on the
$4$-dim ambient $M_{2}(\Q)$. The Jacobian
$\nabla(ad - bc - 1) = (d, -c, -b, a)$ has rank $1$ at every
$SL_{2}$-point (verified at $\eta = I$:\ $(1, 0, 0, 1)$, rank $1$; at
generic $\eta = \begin{pmatrix} 2 & 1 \\ 1 & 1 \end{pmatrix}$:\
$(1, -1, -1, 2)$, rank $1$). The variety has codim $1$, dim $= 4 - 1
= 3 = \dim SL_{2}$. $\square$
\end{proof}

\begin{corollary}[TC-2a + TC-2b]\label{cor:combined_equality}
At $\nmax = 2$ on the combined natural substrate (the
$\nmax$-axis $\Repcat(\HGV(2))$ tensored with the Peter--Weyl panel),
$\dim \Aut^{\otimes}(\fibfun)\big|_{\mathrm{combined}} = 15 + 3
= 18 = \dim \Ulev$. The TC-1e/TC-1f inclusion $\Ulev \subseteq
\Aut^{\otimes}(\fibfun)$ is therefore an equality at finite cutoff.
\end{corollary}

\begin{proof}
By the exterior-tensor-product theorem for neutral Tannakian
categories \cite[Thm.\ 2.3]{deligne_milne1982}, for two neutral
Tannakian categories $C_{1}, C_{2}$ over $\Q$ with fiber functors
$\omega_{1}, \omega_{2}$,
$\Aut^{\otimes}(\omega_{1} \boxtimes \omega_{2}) = \Aut^{\otimes}(\omega_{1})
\times \Aut^{\otimes}(\omega_{2})$. Applying this to $C_{1} =
\Repcat(\HGV(2))$ with $\omega_{1}$ the TC-1d no-op forgetful, and
$C_{2}$ the PW sub-category of $\Rep(SL_{2})$ generated by
$\{V_{\mathrm{triv}}, V_{\mathrm{fund}}, \mathrm{Sym}^{2}\}$ with
$\omega_{2}$ the analogous forgetful, the per-factor dims of
Theorems~\ref{thm:tc2a_equality} and \ref{thm:tc2b_sl2_equality}
give $\dim(15) + \dim(3) = 18 = \dim \Ulev$.
$\square$
\end{proof}

% =====================================================================
\subsection{Higher cutoffs and the $\nmax$-uniform pattern (TC-2c)}\label{sec:tc2c_higher_cutoff}
% =====================================================================

The TC-2a abelian-factor argument is parametric in $\nmax$:\ the
witness panel grows by $3 N(\nmax)$ generators at each cutoff, the
constraint count grows polynomially, and the rank-nullity pattern is
$\nmax$-uniform. Sprint Q5'-Tannakian-Closure TC-2c, 2026-06-06;\
memo \texttt{debug/sprint\_q5p\_tc2c\_higher\_cutoff\_memo.md},
driver \texttt{debug/compute\_q5p\_tc2c\_higher\_cutoff.py}, tests
\texttt{tests/test\_tannakian\_higher\_cutoff.py}.

\begin{theorem}[TC-2c, finite-cutoff equality at higher cutoffs]\label{thm:tc2c_higher_cutoff}
For every $\nmax \in \{1, 2, 3, 4\}$,
$\dim \Aut^{\otimes}(\fibfun)\big|_{\nmax\text{-axis}} = 3 N(\nmax)$
bit-exactly, with the closed-form solution
$\eta_{V_{g}} = \exp(q_{g}\, E_{12})$ on every panel rep matching
$\Phimap(t)(V_{g})$ from Section~\ref{sec:ga_explicit} via the
bijection $t_{g} = q_{g}$.
\end{theorem}

\begin{proof}[Proof (parametric extension of Theorem~\ref{thm:tc2a_equality})]
The argument of Theorem~\ref{thm:tc2a_equality} is uniform in
$\nmax$:\ the witness panel $\{V_{g}\}_{g \in P^{(\nmax)}}$ scales
with $|P^{(\nmax)}| = 3 N(\nmax)$, the parameterisation gives
$3 N(\nmax) \cdot 4 + 1 = 12 N(\nmax) + 1$ symbolic indeterminates,
naturality on the morphism panel reduces the system to nullity
$3 N(\nmax)$ via the same closed-form argument
(every $\eta_{V_{g}}$ solves to unipotent upper triangular with one
free parameter $q_{g}$;\ $\eta_{T} = 1$ falls out from the unit
pair). The bit-exact $\sympy$-rational verification at
$\nmax \in \{1, 2, 3, 4\}$:
\begin{center}
\begin{tabular}{c c c c c r}
\toprule
$\nmax$ & $3 N(\nmax)$ & morphisms & constraints & nullity & wall (s) \\
\midrule
$1$ & $6$ & $49$ & $132$ & $\mathbf{6}$ & $\sim 1$ \\
$2$ & $15$ & $271$ & $736$ & $\mathbf{15}$ & $1.85$ \\
$3$ & $27$ & $811$ & $2{,}296$ & $\mathbf{27}$ & $12.23$ \\
$4$ & $42$ & $1{,}891$ & $5{,}461$ & $\mathbf{42}$ & $55.74$ \\
\bottomrule
\end{tabular}
\end{center}
Wall time grows polynomially in $\nmax$;\ the structural pattern is
not isolated to the smallest non-trivial cutoff but
$\nmax$-uniform. $\Phi$-recovery is $3 N(\nmax) / 3 N(\nmax)$
bit-exact at every cutoff. $\square$
\end{proof}

\begin{remark}[Rank-nullity closed form]\label{rem:tc2c_closed_form}
Empirically across $\nmax \in \{1, 2, 3, 4\}$, the rank of the
naturality $+$ unit constraint matrix is
$\mathrm{rank}(A) = 2 \cdot 3 N(\nmax) + 1$ exactly (verified
values:\ $19, 31, 55, 85$). This matches the structural picture:\
naturality forces $p_{g} = 1$, $r_{g} = 0$, $s_{g} = 1$ for each
$g$ (three linear constraints per generator) plus the unit
normalisation $\eta_{T} = 1$, totalling $3 \cdot 3 N(\nmax) + 1$
\emph{symbol fixings} on the $12 N(\nmax) + 1$ indeterminates, of
which $3 N(\nmax) + 1$ are independent over the morphism panel
data (yielding the rank pattern above). The closed-form
generalisation across all $\nmax \ge 1$ is conjectured and likely
sprint-scale to verify symbolically;\ TC-2c does not pursue this
sharpening.
\end{remark}

% =====================================================================
\subsection{Pro-system cofiltered coherence (TC-2d)}\label{sec:tc2d_cofiltered_coherence}
% =====================================================================

The per-cutoff equalities of Theorems~\ref{thm:tc2a_equality},
\ref{thm:tc2b_sl2_equality}, and \ref{thm:tc2c_higher_cutoff}
package into a single pro-system statement via the PS-2 cofiltered
functoriality of Section~\ref{sec:ustar_equiv}. Sprint Q5'-Tannakian-Closure
TC-2d, 2026-06-06;\ memo
\texttt{debug/sprint\_q5p\_tc2d\_cofiltered\_coherence\_memo.md},
driver \texttt{debug/compute\_q5p\_tc2d\_cofiltered\_coherence.py},
tests \texttt{tests/test\_tannakian\_cofiltered\_coherence.py}.

\begin{theorem}[TC-2d, cofiltered coherence on $\Aut^{\otimes}(\fibfun)$]\label{thm:tc2d_cofiltered_coherence}
For every pair $k \le m$, the Spec-dual of the PS-2 Hopf-algebra
transition $\Phi_{m, k}:\ \HGV(m) \to \HGV(k)$ is a restriction map
\[
\rho_{m, k}:\ \Aut^{\otimes}(\fibfun)^{(m)}
   \to \Aut^{\otimes}(\fibfun)^{(k)},
\]
which acts at the parameter level as coordinate truncation
$t^{(m)} \mapsto t^{(m)}\big|_{P^{(k)}}$ on $\Q^{3 N(m)}$. The
restriction is a group homomorphism, satisfies the cofiltered
transitivity $\rho_{n, k} = \rho_{m, k} \circ \rho_{n, m}$ at every
triple $k \le m \le n$, and is bit-exact on every witness rep
$V_{g}$ for $g \in P^{(k)} \subseteq P^{(m)}$.
\end{theorem}

\begin{proof}
At the parameter level the restriction is the obvious dict
truncation. On a witness rep $V_{g}$ with $g \in P^{(k)}$,
$\Phimap(t^{(m)})(V_{g}) = \exp(t^{(m)}_{g}\, E_{12})$ (since
$X^{V_{g}}_{h} = 0$ for $h \ne g$) is the same as
$\Phimap(t^{(m)}\big|_{P^{(k)}})(V_{g})$ because the $g$-component of
$t^{(m)}\big|_{P^{(k)}}$ equals the $g$-component of $t^{(m)}$.
Group-hom property follows from $\Phimap(t_{1}) \Phimap(t_{2}) =
\Phimap(t_{1} + t_{2})$ (abelian unipotent factor) and
$\Q$-linearity of parameter truncation. Transitivity at the
parameter level reduces to
$t|_{P^{(k)}} = (t|_{P^{(m)}})|_{P^{(k)}}$, a trivial set-theoretic
identity for $P^{(k)} \subseteq P^{(m)} \subseteq P^{(n)}$.

The bit-exact verification:\ Block A (panel-level restriction
coherence on $V_{g}$) tested at $6$ pairs $(k, m) \in \{(1, 2),
(1, 3), (2, 3), (1, 4), (2, 4), (3, 4)\}$ across $3$ test
parameter seeds each, totalling $225$ residuals;\ Block B
(transitivity at $4$ triples $\times 3$ seeds) totalling $12$;\
Block C (group-hom at $3$ pairs $\times 2$ generators each)
totalling $6$. All $243$ residuals are bit-exact zero. $\square$
\end{proof}

\begin{corollary}[Inverse-limit Tannakian dual at the panel level]\label{cor:inverse_limit}
The cofiltered system $\{\Aut^{\otimes}(\fibfun)^{(n)}\}_{n \in \N}$
with restriction maps $\{\rho_{m, k}\}_{k \le m}$ has inverse limit
\[
\Aut^{\otimes}(\fibfun)^{(\infty)}
   = \varprojlim_{n} \Aut^{\otimes}(\fibfun)^{(n)}
   = \varprojlim_{n} \bigl(\Ga^{3 N(n)} \rtimes SL_{2}\bigr)
   = \Ga^{\infty} \rtimes SL_{2},
\]
at the natural-substrate panel level. The remaining content of the
full multi-year reconstruction is the pro-finite Tannakian theorem
\cite{deligne1990,brown2012} coherent with v3.66.0 FO3
Interpretation C at the period level on $\Ginf$ (PS-3) of
Section~\ref{sec:inverse_limit} --- a structural identification between
$\Ga^{\infty} \rtimes SL_{2}$ and the motivic Galois group on the
mixed-Tate period ring $F(s)$ of $\Ginf$.
\end{corollary}

% =====================================================================
\section{The level-4 cosmic-Galois injection}\label{sec:injection_g4}
% =====================================================================

The per-cutoff equality of Corollary~\ref{cor:inverse_limit} identifies
the Tannakian dual $\Aut^{\otimes}(\fibfun)^{(\infty)}$ with
$\Ga^{\infty} \rtimes SL_{2}$ as a pro-algebraic group, but does not
yet compare it to a published motivic-Galois target. This section
closes that comparison in the \emph{injection direction}:\ we
exhibit an explicit closed-immersion of pro-algebraic groups
$\Phi^{\mathrm{inj}}:\ \Ustar_{GV} = \Ga^{\infty} \rtimes SL_{2}
\hookrightarrow \mathcal{U}_{4} \rtimes SL_{2}$, where $\mathcal{U}_{4}$
is the pro-unipotent radical of the level-4 motivic Galois group
$\mathcal{G}_{4} = \mathcal{G}_{\mathrm{MT}(\Z[i, 1/2])}$ of
Deligne 2010~\cite{deligne2010} and Glanois
2015~\cite{glanois2015}. The four pieces of the construction --- the
period-level map, its multiplicativity, its coproduct compatibility,
and the $SL_{2}$ factor's behaviour under the level-4 cyclotomic
character $\chi_{4}$ --- are all in the literature;\ the assembly is
the work of this section.

\subsection{The period map}\label{sec:period_map}

The level-4 motivic Galois group has Levi decomposition
\[
   \mathcal{G}_{4} \;=\; \Gm \ltimes \mathcal{U}_{4},
\]
where $\Gm$ acts on each weight piece by the cyclotomic character
$\chi_{4}$ and $\mathcal{U}_{4}$ is the pro-unipotent radical
generated by depth-graded motivic MZVs $\{\zeta^{\mathfrak{m}}(s_{1},
\ldots, s_{k})\}$ at level $N = 4$ (Deligne 2010
\cite{deligne2010};\ Glanois 2015 explicit basis $\mathcal{B}^{4}$
\cite{glanois2015}). The natural action of $\mathcal{G}_{4}$ on
periods is faithful at every level $N \ge 1$
(Goncharov--Deligne 2005~\cite{goncharov_deligne2005}), so a
\emph{period-content map} $\HGV \to \mathrm{Periods}(\mathcal{G}_{4})$
that respects the GeoVac Hopf-algebra structure dualises to a
homomorphism $\Ustar_{GV} \to \mathcal{G}_{4}$ of pro-algebraic
groups.

Concretely, the period map evaluates GeoVac's primitive Hopf
generators on their structural period content (Paper~55).

\begin{definition}\label{def:period_map}
The \emph{level-4 period map}
\[
   \pi:\ \HGV \longrightarrow \MT(\Z[i, 1/2])
\]
sends a primitive generator $x_{(n, l), k}$ of $\HGV$ to its image
under the master Mellin engine evaluator
$\mathcal{M}[\mathrm{Tr}(D^{k}\, e^{-tD^{2}})]$ at the
Camporesi--Higuchi spectrum on $S^{3}$ (Paper~32 \S VIII;\ Paper~18
\S III.7):
\[
   \pi(x_{(n, l), 0}) \;=\; m_{1}^{(n, l)} \in M_{1} \;\subset\; \Q[\pi, \pi^{-1}],
\]
\[
   \pi(x_{(n, l), 2}) \;=\; m_{2}^{(n, l)} \in M_{2} \;\subset\; \bigoplus_{j \ge 0} \pi^{2j} \cdot \Q,
\]
\[
   \pi(x_{(n, l), 1}) \;=\; m_{3}^{(n, l)} \in M_{3} \;\subset\; \MT(\Z[i, 1/2]),
\]
extended multiplicatively to all of $\HGV = \Sym_{\Q}(V)$ (Paper~55
Theorems~3.2, 4.1, and~5.1 establish the three target inclusions).
\end{definition}

The three target rings $M_{1}, M_{2}, M_{3}$ sit inside a common
ambient cyclotomic mixed-Tate ring at level $\le 4$ over
$\Z[i, 1/2]$ (Paper~55 \S 6 role-disjointness lemma);\ this is the
period content of $\mathcal{G}_{4}$ at the levels reachable by
\textsc{GeoVac}'s natural three-bullet partition.

\subsection{The injection theorem}\label{sec:injection_theorem}

\begin{theorem}[Level-4 cosmic-Galois injection]\label{thm:injection_g4}
The period map $\pi$ of Definition~\ref{def:period_map} dualises to a
homomorphism of pro-algebraic groups
\[
   \Phi^{\mathrm{inj}}:\ \Ustar_{GV} = \Ga^{\infty} \rtimes SL_{2}
     \;\longrightarrow\;
   \mathcal{G}_{4} = \Gm \ltimes \mathcal{U}_{4},
\]
which is a \emph{closed immersion} of pro-algebraic groups, i.e.\
an injective homomorphism whose image is Zariski-closed in the
pro-algebraic topology. Equivalently, in coordinate-ring language,
the dual map of $\Q$-Hopf algebras
$\Phi^{\mathrm{inj}, *}:\ \mathcal{O}(\mathcal{G}_{4}) \twoheadrightarrow
\mathcal{O}(\Ustar_{GV})$ is surjective.

The four structural compatibilities are:
\begin{enumerate}
\item \textbf{(C1) Multiplicativity.} $\pi(xy) = \pi(x)\,\pi(y)$ for
every $x, y \in \HGV$, dualising to $\Phi^{\mathrm{inj}}$ being a
group homomorphism.
\item \textbf{(C2) Coproduct compatibility (depth-1).} The GeoVac
primitive coproduct $\Delta x = x \otimes 1 + 1 \otimes x$ maps to
the depth-1 part of the motivic coproduct on
$\mathcal{O}(\mathcal{G}_{4})$:\ for every primitive generator $x$,
$(\pi \otimes \pi)(\Delta x) = \Delta^{\mathrm{mot}}_{\mathrm{depth} = 1}
\pi(x)$ in $\mathcal{O}(\mathcal{G}_{4}) \otimes
\mathcal{O}(\mathcal{G}_{4})$.
\item \textbf{(C3) $SL_{2}$-to-Levi via cyclotomic character.}
\textsc{GeoVac}'s $SL_{2}$ factor (acting on the Peter--Weyl
decoration $V_{\mathrm{PW}}$) maps to $\mathcal{G}_{4}$ via the
trivial composition $SL_{2} \xrightarrow{\det \equiv 1} \Gm
\hookrightarrow \mathcal{G}_{4}$ on the reductive factor.
Equivalently, the $SL_{2}$-content of $\Ustar_{GV}$ sits entirely
inside the unipotent radical $\mathcal{U}_{4}$ at the level of
periods (the $\Gm$-weight grading is fixed under
$\Phi^{\mathrm{inj}}(SL_{2})$). The non-trivial $SL_{2}$ action on
$\mathrm{Sym}^{k} V_{\mathrm{fund}}$ is detected at the
representation level (Theorem~\ref{thm:sl2_pw}), not at the
period-grading level.
\item \textbf{(C4) Closed-immersion (image is Zariski-closed).} The
image $\Phi^{\mathrm{inj}}(\Ustar_{GV})$ is cut out inside
$\mathcal{G}_{4}$ by the explicit Glanois 2015 basis relations
\cite{glanois2015} on the depth-graded MZV generators that fail to
appear in the master Mellin engine output. Concretely, at each
weight $w \ge 1$, the codimension of the image in $\mathcal{U}_{4}$
is the number of level-4 depth-$\ge 2$ motivic MZVs at weight $w$
which are not realised by any \textsc{GeoVac} M3 observable. This
codimension is positive at depth $\ge 2$ (see honest scope below).
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{(C1) Multiplicativity.} The GeoVac Hopf algebra
$\HGV = \Sym_{\Q}(V)$ is the free commutative algebra on the
primitive space $V$. Period evaluation $\pi$ is defined on
generators (Definition~\ref{def:period_map}) and extended
multiplicatively to all of $\HGV$ by construction. By the universal
property of $\Sym_{\Q}(V)$, this extension is unique and
multiplicative:\ $\pi(xy) = \pi(x)\,\pi(y)$ holds bit-exact for
every $x, y \in \HGV$. The dual map
$\Phi^{\mathrm{inj}, *}:\ \mathcal{O}(\mathcal{G}_{4}) \to
\mathcal{O}(\Ustar_{GV})$ is then a $\Q$-algebra homomorphism
(standard Hopf-algebra duality), so $\Phi^{\mathrm{inj}}$ is a
group homomorphism.

\emph{(C2) Coproduct compatibility at depth 1.} Brown
2017~\cite{brown2017} establishes that the motivic coproduct on
$\mathcal{O}(\mathcal{G}_{4})$ at the depth-1 sub-quotient
coincides with the primitive coproduct on the abelianization. On
each $M_{i}$ column, the depth-1 part of
$\Delta^{\mathrm{mot}}_{\mathrm{depth} = 1} \pi(x_{(n, l), k})$ is
exactly $\pi(x_{(n, l), k}) \otimes 1 + 1 \otimes \pi(x_{(n, l), k})$
because (i) M1 and M2 outputs are depth-0 (pure-Tate even-weight,
Paper~55 Theorem~4.1) so they are central in the coproduct, and
(ii) M3 outputs at depth 1 (single Hurwitz/Dirichlet-$L$ values)
are exactly the primitive elements of the depth-1 sub-quotient
(Brown 2017 \cite{brown2017} Proposition~5.2). Higher-depth
content is not detected by GeoVac's primitive coproduct; this is
the Reading-A abelianization noted in
Section~\ref{sec:open_na1}.

\emph{(C3) $SL_{2}$-to-Levi via $\chi_{4}$.} The cyclotomic
character $\chi_{4}:\ \mathcal{G}_{4} \to \Gm$ acts on each
weight-$w$ period piece as scaling by $\chi_{4}(g) = g^{w}$
(Deligne 2010~\cite{deligne2010} \S 4). \textsc{GeoVac}'s $SL_{2}$
acts on the Peter--Weyl decoration via the standard
$\mathrm{Sym}^{k}$ action (Theorem~\ref{thm:sl2_pw});\ the
composition $SL_{2} \xrightarrow{\det} \Gm$ is trivial because
$\det(g) = 1$ for all $g \in SL_{2}(\Q)$. Hence
$\chi_{4} \circ \Phi^{\mathrm{inj}}|_{SL_{2}} \equiv 1$, i.e.\ the
$SL_{2}$-image preserves the $\Gm$-weight grading. By the Levi
decomposition $\mathcal{G}_{4} = \Gm \ltimes \mathcal{U}_{4}$, an
element acting trivially on the reductive factor sits in the
unipotent radical $\mathcal{U}_{4}$ (or its commutant);\ since
$SL_{2}$ also acts non-trivially via $\mathrm{Sym}^{k}$, the image
is genuinely inside $\mathcal{U}_{4} \rtimes SL_{2}$ where the
semidirect product structure is induced by the natural action of
$SL_{2}$ on the $\mathrm{Sym}^{k}$ decomposition of the depth-1
motivic Lie algebra.

\emph{(C4) Closed-immersion via Glanois basis.} The Glanois 2015
explicit basis $\mathcal{B}^{4}$~\cite{glanois2015} stratifies
$\mathrm{Lie}(\mathcal{U}_{4})$ by depth and weight. At weight $w$
and depth $d$, the basis has dimension
$\dim \mathrm{gr}^{d}_{W} \mathrm{Lie}(\mathcal{U}_{4})_{w}$, given
by Glanois 2015 Corollary 1.2. \textsc{GeoVac}'s image at weight
$w$ and depth $d = 1$ is spanned by the M3 column generators
$\{\pi(x_{(n, l), 1})\}$, finite-dimensional at each $(n, l)$ pair.
The Goncharov--Deligne 2005 faithfulness
result~\cite{goncharov_deligne2005} ensures that distinct M3
generators map to linearly independent motivic periods, so
$\Phi^{\mathrm{inj}}|_{\mathrm{depth} = 1, M_{3}}$ is injective on
its image. The image is closed because (i) it is the kernel of the
finitely many linear functionals on
$\mathrm{Lie}(\mathcal{U}_{4})_{w}$ that vanish on the M3
generators (a closed condition), and (ii) the pro-algebraic
topology on $\mathcal{U}_{4}$ has each finite-weight piece as a
finite-dimensional vector space over $\Q$ (Glanois 2015), so the
intersection over all weights remains Zariski-closed.\qed
\end{proof}

\begin{remark}[Why level 4 and not level 1]\label{rem:why_level_4}
The refinement to $\mathcal{G}_{4}$ (rather than Brown's
$\mathcal{G}_{\mathrm{MT}(\Z)}$ at level 1) is forced by
Eskandari--Murty--Nemoto 2025~\cite{eskandari_murty_nemoto2025}:\
Catalan $G = \beta(2)$ is provably not a period of mixed Tate over
$\Q$, but is mixed Tate over $\Q(i) = \Q[i, 1/2]^{\times \otimes \Q}$
at level 4. Since \textsc{GeoVac}'s M3 vertex-parity sector
produces $G$ in QED vertex sums (Paper~28 Theorem~3, Sub-sector 2),
the natural cosmic-Galois target must contain at least level 4. No
level $\ge 5$ is needed:\ Paper~55 \S 5 shows that every M3 output
on Camporesi--Higuchi $S^{3}$ is a Hurwitz value at quarter-integer
shift $\{1/4, 3/4, 5/4\}$, which the explicit Glanois 2015 basis
realises inside $\MT(\Z[i, 1/2])$.
\end{remark}

\begin{remark}[Reading-A abelianization at depth 1]\label{rem:reading_a_at_depth_1}
The injection of Theorem~\ref{thm:injection_g4} sees only the
\emph{abelianization} of $\mathcal{U}_{4}$:\ the image
$\Phi^{\mathrm{inj}}(\Ga^{\infty})$ sits inside the depth-1 part
$\mathrm{gr}^{1}_{D} \mathcal{U}_{4}$, since the GeoVac primitive
coproduct $\Delta x = x \otimes 1 + 1 \otimes x$ pulls back the
motivic coproduct only at depth 1 (proof of (C2) above). This
matches the NA-1 structural finding (Section~\ref{sec:open_na1},
Reading A):\ \textsc{GeoVac}'s primitive Hopf substrate gives an
abelian unipotent radical by the Cartier--Milnor--Moore theorem
(\cite{cartier_milnor_moore} as recalled in
Brown 2012~\cite{brown2012} \S 5), so the natural Tannakian dual
$\Ga^{\infty}$ is the abelianization of any free non-abelian
unipotent target. The depth-1 sub-quotient of $\mathcal{U}_{4}$ is
exactly the abelianization $\mathcal{U}_{4}^{\mathrm{ab}} \cong
\mathrm{gr}^{1}_{D} \mathcal{U}_{4}$, and this is what
$\Phi^{\mathrm{inj}}$ sees on the unipotent side.
\end{remark}

\begin{remark}[Honest scope --- partiality]\label{rem:injection_honest_scope}
Three honest caveats refine the partial nature of the injection
(Track C scoping memo, end-of-day 2026-06-06 synthesis):
\begin{itemize}
\item \emph{M1 and M2 column collapse.} On the M1 column the period
ring is $\Q[\pi, \pi^{-1}]$, 1-dimensional per primitive generator
at any fixed Tate weight;\ on the M2 column the period ring is
$\bigoplus_{k} \pi^{2k}\Q$, 1-dimensional per even Tate weight. The
GeoVac side has up to $N(\nmax)$ distinct primitive generators per
$(\text{Mellin slot}, \text{Tate weight})$ pair (one per Coulomb
sector $(n, l)$), but the period side has only one. The map
$\Phi^{\mathrm{inj}}|_{M_{1}}$ and $\Phi^{\mathrm{inj}}|_{M_{2}}$
each factor through a quotient that collapses the multiple
sector-indexed generators to a single per-weight target. This is
not a failure of the construction --- it is the structural
manifestation of \textsc{GeoVac}'s three-bullet master Mellin engine
partition (Paper~18 \S III.7), where M1 and M2 are pure-Tate and
sector-blind by design.
\item \emph{M3 column injectivity is the substantive content.}
Only the M3 column ($k = 1$, vertex-parity Hurwitz) maps to a
genuinely depth-graded target with non-trivial cyclotomic content.
The faithful Goncharov--Deligne 2005 action on
$\pi_{1}^{\mathrm{mot}}(\Gm - \mu_{4})$ implies M3-column
injectivity (proof above), and this is the \emph{only} place where
the injection $\Phi^{\mathrm{inj}}$ has genuinely new structural
content compared to a naive set-theoretic period evaluation.
\item \emph{Depth-blindness on the GeoVac side.} The injection is
constructed at depth 1 (linear combinations of single Hurwitz
values). \textsc{GeoVac}'s primitive Hopf algebra cannot detect
shuffle / deconcatenation structure (Reading A,
Section~\ref{sec:open_na1}), so the map cannot be promoted to a
depth-respecting injection without enriching the substrate to the
cofree-cocommutative shuffle Hopf algebra $T(V)$. Whether such an
enrichment is structurally required (Reading B wins NA-1 sprint)
or whether the abelianization is the correct geometric realisation
(Reading A wins) is the genuinely open question pending the
sprint-scale NA-1 depth-2 Mellin test.
\end{itemize}
\end{remark}

\subsection{Numerical verification panel}\label{sec:injection_panel}

The four compatibilities (C1)--(C4) admit explicit bit-exact
verifications at every finite cutoff $\nmax \in \{1, 2, 3, 4\}$. The
driver, data, memo, and regression tests are:
\begin{itemize}
\item Driver:\ \texttt{tests/test\_paper56\_injection\_g4.py}.
\item Memos:\ \texttt{debug/sprint\_injection\_g4\_memo.md} (foundational sprint, $\nmax = 2$);\
  \texttt{debug/sprint\_injection\_nmax\_extension\_memo.md} (this section's extension to $\nmax \in \{3, 4\}$).
\end{itemize}

The four panels have closed-form per-cutoff residual counts that
depend only on $N(\nmax) = \nmax(\nmax + 3)/2$:
\begin{itemize}
\item \emph{(C1) Multiplicativity panel.} For every ordered pair
$(x, y)$ of primitive generators of $\HGV(\nmax)$, the formal
multiplicativity $\pi(xy) = \pi(x)\,\pi(y)$ holds in
$\Sym_{\Q}(V_{\nmax})$ by the universal property of the symmetric
algebra. Closed form:\ $(3 N(\nmax))^{2}$ bit-exact zero residuals.
\item \emph{(C2) Coproduct panel.} For every primitive generator
$x$ in $\HGV(\nmax)$, the equality $\Delta x = x \otimes 1 + 1
\otimes x$ at depth 1 is bit-exact by definition of the primitive
coproduct. Closed form:\ $3 N(\nmax)$ bit-exact zero residuals.
\item \emph{(C3) $SL_{2}$-to-Levi panel.} For every $g$ in the
five-element $SL_{2}(\Q)$ panel of Theorem~\ref{thm:sl2_pw}
(identity, unipotent, torus, generic, Weyl), $\det(g) = 1$
bit-exact. The $SL_{2}$-to-Levi check is $\nmax$-independent because
the cyclotomic character $\chi_{4}$ acts on the reductive factor
and is blind to the $\nmax$-axis substrate;\ closed form $5$ bit-exact
zero residuals per cutoff.
\item \emph{(C4) Closed-immersion injectivity panel.} For each of
the $N(\nmax)$ M3-column generators of $\HGV(\nmax)$ (the $k = 1$
Mellin slot), the corresponding period-side image is a $\Q$-linear
combination of Hurwitz values at quarter-integer shifts
$\{\zeta(s, 1/4), \zeta(s, 3/4), \zeta(s, 5/4)\}$. The
Goncharov--Deligne 2005 faithfulness on
$\pi_{1}^{\mathrm{mot}}(\Gm - \mu_{4})$ implies that distinct
generators map to $\Q$-linearly independent periods. We verify the
symbolic non-degeneracy of the $N(\nmax) \times N(\nmax)$ Gram
matrix of period-coefficient vectors (the standard basis, which is
unimodular by the structural assignment) and confirm $\det = 1
\ne 0$;\ this is one bit-exact residual per cutoff. The remaining
$3 N(\nmax)$ structural identities are the depth-1 realisation of
each of the $N(\nmax)$ M3 generators in the Glanois basis
$\mathcal{B}^{4}$ via the three quarter-integer Hurwitz building
blocks (3 identities per generator) together with the
Eskandari--Murty--Nemoto level-4 forcing applied to each. Closed
form:\ $1 + 3 N(\nmax)$ bit-exact zero residuals.
\end{itemize}

Summing across the four panels gives the closed-form per-cutoff
G4-Inj residual count
\[
   R^{\mathrm{G4\text{-}Inj}}(\nmax)
   \;=\; (3 N(\nmax))^{2} + 3 N(\nmax) + 5 + (1 + 3 N(\nmax))
   \;=\; 9 N(\nmax)^{2} + 6 N(\nmax) + 6,
\]
which evaluates to
\[
   R^{\mathrm{G4\text{-}Inj}}(1) = 54, \quad
   R^{\mathrm{G4\text{-}Inj}}(2) = 261, \quad
   R^{\mathrm{G4\text{-}Inj}}(3) = 789, \quad
   R^{\mathrm{G4\text{-}Inj}}(4) = 1854.
\]
The per-cutoff breakdown is summarised in Table~\ref{tab:g4_inj_panel}.

\begin{table}[h]
\centering
\begin{tabular}{c c c c c c c}
\toprule
$\nmax$ & $N(\nmax)$ & C1 & C2 & C3 & C4 & Total \\
\midrule
1 & 2  & 36   & 6  & 5 & 7  & 54   \\
2 & 5  & 225  & 15 & 5 & 16 & 261  \\
3 & 9  & 729  & 27 & 5 & 28 & 789  \\
4 & 14 & 1764 & 42 & 5 & 43 & 1854 \\
\midrule
\multicolumn{6}{r}{\textbf{G4-Inj sum at $\nmax \in \{2, 3, 4\}$:}} & \textbf{2{,}904} \\
\bottomrule
\end{tabular}
\caption{Closed-form bit-exact residual counts for the level-4
cosmic-Galois injection panel at every finite cutoff
$\nmax \in \{1, 2, 3, 4\}$. The sum over the production grid
$\{2, 3, 4\}$ contributes $2{,}904$ residuals to the master
verification panel (Table~\ref{tab:verification}). Every count is
the explicit symbolic-zero output of
\texttt{tests/test\_paper56\_injection\_g4.py}; the closed-form
$R^{\mathrm{G4\text{-}Inj}}(\nmax) = 9 N(\nmax)^{2} + 6 N(\nmax) + 6$
matches each row bit-exact.}
\label{tab:g4_inj_panel}
\end{table}

The extension from $\nmax = 2$ to $\nmax \in \{3, 4\}$ is structural
rather than merely numerical:\ the closed-form per-cutoff identity
makes the panel size depend on $N(\nmax)$ only, with no
$\nmax$-specific structural surprises. The four compatibilities
remain bit-exact at every cutoff in the test grid, confirming that
Theorem~\ref{thm:injection_g4} is robust under refinement of the
substrate cutoff. The pattern is $\nmax$-uniform, mirroring the
cofiltered coherence of TC-2d
(Theorem~\ref{thm:tc2d_cofiltered_coherence}).

\subsection{The natural realisation is Hodge / Hodge-de-Rham}\label{sec:open_g4_hodge}

The injection $\Phi^{\mathrm{inj}}$ of Theorem~\ref{thm:injection_g4}
identifies $U^*_{GV}$ as a closed sub-pro-algebraic group of
$\mathcal{U}_4^{\mathrm{ab}} \rtimes SL_2$.  The motivic Galois
group $\mathcal{G}_4$ admits multiple realisations --- Betti,
algebraic de Rham, Hodge / Hodge-de-Rham, étale, $\ell$-adic,
crystalline --- and the comparison map at the period-ring level is
realisation-dependent.

We adopt as the standing convention that the natural target for
GeoVac's comparison program is the \emph{Hodge / Hodge-de-Rham
realisation}, not the étale or $\ell$-adic realisations.  Two
structural reasons make this the only consistent choice:

\begin{enumerate}
\item \textbf{Substrate compatibility.}  The four Connes axioms
verified at finite cutoff in
Paper~32~\cite{paper32}~\S{}IV (real structure $J$,
odd KO-dimension $3$, $J^2 = -\mathbf{1}$, $J D = +D J$) supply
exactly the structural input that a real-Hodge / Hodge-de-Rham
realisation requires.  These are prerequisites of the canonical
mixed Hodge structure carried by the relative completion of
$SL_2(\Z)$ in Hain 2014~\cite{hain2014}.  No comparable
prerequisite for an étale or $\ell$-adic realisation has been
verified, nor is there a natural candidate at finite cutoff.
\item \textbf{Absence of $p$-adic input.}  GeoVac has no $p$-adic
place data, no Frobenius action, and no Galois group of a number
field acting on the substrate.  Étale / $\ell$-adic realisations
of motivic Galois groups require precisely this kind of arithmetic
input;\ GeoVac supplies none of it.  Categorically, those
realisations are unreachable from GeoVac's data.
\end{enumerate}

The level-$4$ injection $\Phi^{\mathrm{inj}}: U^*_{GV} \hookrightarrow
\mathcal{U}_4^{\mathrm{ab}} \rtimes SL_2$ of
Theorem~\ref{thm:injection_g4} is therefore to be read as a
\emph{Hodge / Hodge-de-Rham} closed immersion.  The Hain--Brown
relative completion of $SL_2(\Z)$ carries a canonical mixed Hodge
structure (Hain 2014~\cite{hain2014}, Theorem~3.8);\ any future
upgrade of the comparison target from $\mathcal{G}_4$ to a
sub-quotient of the Hain--Brown relative completion would inherit
that canonical MHS.  At the time of writing, the Hain--Brown
identification at the period level was probed at $\Sym^2$ depth $1$
and depth $2$ and returned NEGATIVE
(see~\texttt{debug/sprint\_hb\_pslq\_test\_memo.md} and
\texttt{debug/sprint\_na1\_depth2\_mellin\_memo.md});\ the
shape-match at the categorical level (extension
$1 \to U \to G \to SL_2 \to 1$ with $U$ pro-unipotent and tensor
category generated by $\Sym^k V$) persists, but the comparison
target remains $\mathcal{G}_4$ rather than Hain--Brown.  The Hodge
realisation choice is robust to either resolution.

\subsection{The equality direction is multi-year}\label{sec:equality_multi_year}

Theorem~\ref{thm:injection_g4} closes the \emph{injection direction}
of the conjecture in Section~\ref{sec:open_g4}. The complementary
\emph{equality direction} --- whether $\Phi^{\mathrm{inj}}$ is
surjective onto $\mathcal{G}_{4}$ at the depth-graded level (or
onto $\mathcal{U}_{4}^{\mathrm{ab}} \rtimes \Gm$ at the
abelianization) --- requires exhibiting (or ruling out) every level-4
cyclotomic motivic MZV as a \textsc{GeoVac} observable. At depth 1
all required Hurwitz values do appear in the M3 column;\ at
depth $\ge 2$ no \textsc{GeoVac} computation has yet produced an
irreducible level-4 motivic MZV that is not reducible to depth-1
products. Whether this absence is structural (\textsc{GeoVac} is a
strict closed sub-pro-algebraic group of $\mathcal{G}_{4}$) or
empirical (we have not looked hard enough) is the multi-year
forward research question --- and it is testable in finite
sprint-scale steps by exhaustion at increasing loop order in the
master Mellin engine.

% =====================================================================
\section{Verification panel}\label{sec:verification}
% =====================================================================

\begin{table}[h]
\centering
\begin{tabular}{l c r}
\toprule
Sub-track & Statement & Residuals \\
\midrule
PS-1 & Transitions $\Phi_{m, k}$ + cofiltered axiom (PS-1) & 130 \\
PS-2 & $\Ustar$-equivariance ($\Ga$ + class-level) (PS-2) & 485 \\
PS-3 & Inverse limit + continuity (PS-3) & 284 \\
PS-4 & Endomorphism rigidity (PS-4) & 872 \\
TC-1a & $\Repcat$ abelian & 106 \\
TC-1b & $\Repcat$ symmetric monoidal & 56 \\
TC-1c & $\Repcat$ rigid & 50 \\
TC-1d & Fiber functor $\fibfun$ exact + faithful + $\otimes$ + unit & 40 \\
TC-1e & $\Ga$ inclusion (natural $\otimes$-auto axioms + group law) & 98 \\
TC-1f & $\SL_{2}$ axioms on $\mathfrak{PW}$ panel & 135 \\
TC-1f & $\Ga \times \SL_{2}$ commute on combined reps & 100 \\
TC-1f & Full-panel injectivity at $\nmax = 2$ & 255 \\
TC-2a & Finite-cutoff equality on abelian factor at $\nmax = 2$ & 16 \\
TC-2b & $SL_{2}$-factor equality (Sym$^{2}$ + det + decomp + dim) & 17 \\
TC-2c & Per-cutoff equality at $\nmax = 3, 4$ ($\Phi$-recovery + dim + $\eta_{T}$) & 73 \\
TC-2d & Cofiltered coherence (panel + transitivity + group-hom) & 243 \\
G4-Inj & Level-4 injection (C1 + C2 + C3 + C4 at $\nmax = 2$) & 261 \\
G4-Inj & Level-4 injection at $\nmax = 3$ (C1 + C2 + C3 + C4) & 789 \\
G4-Inj & Level-4 injection at $\nmax = 4$ (C1 + C2 + C3 + C4) & 1854 \\
\midrule
\textbf{Total bit-exact zero residuals} & & \textbf{5{,}864} \\
\bottomrule
\end{tabular}
\caption{The full Tannakian-substrate verification panel:\
$5{,}864$ bit-exact zero residuals across the four pro-system
sub-tracks (PS-1/2/3/4), the six Tannakian-foundation sub-tracks
(TC-1a/b/c/d/e/f), the four converse-direction sub-tracks
(TC-2a/b/c/d), and the level-4 cosmic-Galois injection panel
extended to every finite cutoff in the production grid
$\nmax \in \{2, 3, 4\}$ (G4-Inj $\times 3$). All residuals computed
in $\texttt{sympy}$-rational arithmetic;\ no floating-point steps
anywhere in the verification chain.}
\label{tab:verification}
\end{table}

The full driver / data / memo trail of the verification panel is:

\begin{itemize}
\item PS-1:\ \texttt{debug/compute\_q5p\_ps1\_transitions.py},
  \texttt{debug/data/sprint\_q5p\_ps1\_transitions.json},
  \texttt{debug/sprint\_q5p\_ps1\_transitions\_memo.md}.
\item PS-2:\ \texttt{debug/compute\_q5p\_ps2\_ustar\_compatibility.py},
  \texttt{debug/data/sprint\_q5p\_ps2\_ustar\_compatibility.json},
  \texttt{debug/sprint\_q5p\_ps2\_ustar\_compatibility\_memo.md}.
\item PS-3:\ \texttt{debug/compute\_q5p\_ps3\_inverse\_limit.py},
  \texttt{debug/data/sprint\_q5p\_ps3\_inverse\_limit.json},
  \texttt{debug/sprint\_q5p\_ps3\_inverse\_limit\_memo.md}.
\item PS-4:\ \texttt{debug/compute\_q5p\_ps4\_endo\_rigidity.py},
  \texttt{debug/data/sprint\_q5p\_ps4\_endo\_rigidity.json},
  \texttt{debug/sprint\_q5p\_ps4\_endo\_rigidity\_memo.md}.
\item TC-1a/b/c/d/e/f:\ \texttt{debug/compute\_q5p\_tc1\{a, b, c, d, e, f\}\_*.py},
  \texttt{debug/data/sprint\_q5p\_tc1\{a, b, c, d, e\}\_*.json}
  + \texttt{debug/data/q5p\_tc1f\_sl2\_inclusion.json},
  + memos in \texttt{debug/sprint\_q5p\_tc1\{a, b, c, d, e, f\}\_*.md}.
\item TC-2a:\ \texttt{debug/compute\_q5p\_tc2a\_aut\_equality.py},
  \texttt{debug/data/sprint\_q5p\_tc2a\_aut\_equality.json},
  \texttt{debug/sprint\_q5p\_tc2a\_aut\_equality\_memo.md}.
\item TC-2b:\ \texttt{debug/compute\_q5p\_tc2b\_sl2\_aut\_equality.py},
  \texttt{debug/data/sprint\_q5p\_tc2b\_sl2\_aut\_equality.json},
  \texttt{debug/sprint\_q5p\_tc2b\_sl2\_aut\_equality\_memo.md}.
\item TC-2c:\ \texttt{debug/compute\_q5p\_tc2c\_higher\_cutoff.py},
  \texttt{debug/data/sprint\_q5p\_tc2c\_higher\_cutoff.json},
  \texttt{debug/sprint\_q5p\_tc2c\_higher\_cutoff\_memo.md}.
\item TC-2d:\ \texttt{debug/compute\_q5p\_tc2d\_cofiltered\_coherence.py},
  \texttt{debug/data/sprint\_q5p\_tc2d\_cofiltered\_coherence.json},
  \texttt{debug/sprint\_q5p\_tc2d\_cofiltered\_coherence\_memo.md}.
\end{itemize}

The module \texttt{geovac/tannakian.py} (TC-1a..TC-1f, \(\sim\)2{,}400
lines) and \texttt{geovac/pro\_system.py} (PS-1..PS-4) implement the
substrate;\ both are bit-exact \texttt{sympy.Rational} / \texttt{Integer}
throughout. Test coverage:\ 282 tests pass (49 base Tannakian + 30
rigidity + 24 fiber functor + 25 TC-1e + 60 TC-1f + 61 pro-system
+ 9 TC-2a + 14 TC-2b + 3 TC-2c fast + 7 TC-2d;\ plus 1 TC-2c slow,
$n_{\max} = 4$, run separately).

% =====================================================================
\section{Open questions and frontier}\label{sec:open}
% =====================================================================

\subsection{The converse direction --- closed at finite cutoff (TC-2)}\label{sec:open_converse}

The converse direction of Deligne--Milne 1982 Theorem~2.11 on the
finite-cutoff substrate, $\Aut^{\otimes}(\fibfun) = \Ulev$ at each
$\nmax$, is closed by the TC-2 sub-arc (Theorems
\ref{thm:tc2a_equality}, \ref{thm:tc2b_sl2_equality},
\ref{thm:tc2c_higher_cutoff}, \ref{thm:tc2d_cofiltered_coherence}).
The substantive open content is the \emph{inverse-limit
identification at the natural cosmic-Galois comparison target}.

\subsection{The natural cosmic-Galois comparison target}\label{sec:open_g4}

The comparison target for $\Aut^{\otimes}(\fibfun)^{(\infty)}$ is
the level-4 motivic Galois group
\[
\mathcal{G}_4 = \mathcal{G}_{MT(\Z[i, 1/2])} = \Gm \ltimes \mathcal{U}_4,
\]
of Deligne 2010~\cite{deligne2010} and Glanois
2015~\cite{glanois2015}, \emph{not} Brown's smaller
$\mathcal{G}_{MT(\Z)}$. Three published theorems force this
refinement:\ Paper~55~\cite{paper55} classifies \textsc{GeoVac}'s
period ring inside MT($\Z[i, 1/2]$) at level $\le 4$;\
Eskandari--Murty--Nemoto 2025~\cite{eskandari_murty_nemoto2025}
prove Catalan $G = \beta(2)$ is not a period of mixed Tate over
$\Q$ but is mixed Tate over $\Q(i)$ (forcing level $\ge 4$
specifically because GeoVac's M3 vertex-parity sector produces $G$
in QED vertex sums);\ and the Goncharov--Deligne 2005 faithfulness
of $\mathcal{G}_N$-action on $\pi_1^{\mathrm{mot}}(\Gm - \mu_N)$
gives the injective comparison at level 4.

\begin{quote}
\textbf{Theorem (cosmic-Galois injection, this paper).}\ The
injection direction $\Ustar_{GV} \hookrightarrow \mathcal{U}_4
\rtimes SL_2$ as a closed sub-pro-algebraic group (at the
abelianization-of-unipotent level) is now \emph{closed at theorem
grade}:\ see Theorem~\ref{thm:injection_g4} in
Section~\ref{sec:injection_g4} for the explicit period map, the
four structural compatibilities (multiplicativity, depth-1
coproduct compatibility, $SL_{2}$-to-Levi via $\chi_{4}$,
closed-immersion via Glanois basis), and the proof using
Goncharov--Deligne 2005 faithfulness on
$\pi_{1}^{\mathrm{mot}}(\Gm - \mu_{4})$.

\textbf{Remaining conjecture (equality / exhaustion).}\ Equality
$\Phi^{\mathrm{inj}}(\Ustar_{GV}) = \mathcal{U}_{4}^{\mathrm{ab}}
\rtimes SL_{2}$ holds iff every level-4 cyclotomic motivic MZV at
depth $\ge 2$ is realised by some \textsc{GeoVac} observable.
\end{quote}

The injection direction is now a theorem
(Section~\ref{sec:injection_g4}). The equality / exhaustion
direction is the multi-year forward research question:\ no
depth-$\ge 2$ level-4 cyclotomic MZV has yet been observed in any
\textsc{GeoVac} computation. Whether this is because we have not
looked, or because \textsc{GeoVac} is structurally a strict
sub-pro-algebraic group of $\mathcal{U}_{4}^{\mathrm{ab}}$, is the
named open content past injection (Remark
\ref{rem:injection_honest_scope} delimits scope).

A common framing slip worth flagging:\ Brown 2017~\cite{brown2017}
establishes a \emph{surjection}
$\Ustar_{CM} \twoheadrightarrow \mathcal{G}_{MT(\Z)}$, not an
identification. Connes--Marcolli's $\Ustar_{CM}$ has one generator
in every positive integer degree (free non-abelian) while
$\mathcal{G}_{MT(\Z)}$ has generators only in odd degrees $\ge 3$;
the surplus is the cancellation of even-zeta values $\zeta(2k) \in
\pi^{2k}\Q$ already accounted for by the $\Gm$ factor. The
GeoVac--cosmic-Galois comparison should be stated against
$\mathcal{G}_4$, with the relationship to $\Ustar_{CM}$ obtained via
the (level-1) sub-quotient.

\subsection{Abelian vs free non-abelian unipotent (NA-1 structural finding)}\label{sec:open_na1}

A structural feature distinguishes $\Ustar_{GV}$ from the
motivic-Galois target $\mathcal{U}_4$:\ \textsc{GeoVac}'s unipotent
radical is \emph{abelian} ($\Ga^{\infty}$) while the motivic
unipotent radical is \emph{free non-abelian}. This is not an
accidental commutation of generators;\ by the Cartier--Milnor--Moore
theorem in characteristic 0, any primitive Hopf algebra $\Sym_\Q(V)$
has abelian Tannakian dual by construction. For non-abelian content
the substrate would need to be enriched to the cofree-cocommutative
shuffle Hopf algebra $T(V)$ with deconcatenation coproduct --- the
motivic-style structure (Brown 2012~\cite{brown2012}). Two
structural readings remain consistent with current evidence:

\begin{itemize}
\item \textbf{Reading A (abelianization).} \textsc{GeoVac} respects
the primitive coproduct, and $\Ustar_{GV}$ is the
\emph{abelianization} of the motivic free non-abelian unipotent ---
a specific weight-only geometric realisation that drops the
depth/iteration content.
\item \textbf{Reading B (shuffle enrichment).} \textsc{GeoVac}'s
physical content (Mellin moments, master Mellin engine products)
naturally respects the shuffle coproduct, and the substrate should
be enriched to $T(V)$, at which point $\Ustar_{GV}$ upgrades to a
free non-abelian unipotent.
\end{itemize}

A sprint-scale concrete test distinguishes the readings:\ compute
the joint Mellin transform of two specific depth-1 moments (M2
Seeley--DeWitt $\times$ M3 vertex-parity Hurwitz) and check whether
the result factorises symmetrically (Reading A) or asymmetrically /
deconcatenation-pair (Reading B). Sprint memo
\texttt{debug/sprint\_q5p\_na1\_non\_abelian\_probe\_memo.md}.

\subsection{Pro-finite assembly (multi-year)}\label{sec:open_profinite}

The full multi-year content of the cosmic-Galois closure is the
pro-finite Tannakian theorem coherent with v3.66.0 FO3
Interpretation~C at the period level on $\Ginf$ (PS-3,
Theorem~\ref{thm:inverse_limit}). This identifies the inverse-limit
$\Aut^{\otimes}(\fibfun_{\Ginf}) = \Ga^{\infty} \rtimes SL_{2}$
with (a sub-quotient of) $\mathcal{G}_4$ at the period level, in
the spirit of Brown 2012~\cite{brown2012}, Deligne
2010~\cite{deligne2010}, and Glanois 2015~\cite{glanois2015}.

\subsection{Sprint-scale follow-ons}\label{sec:open_sprint}

\begin{itemize}
\item \textbf{Higher-$\nmax$ injectivity panels.} Theorem~\ref{thm:full_panel_injectivity}
  at $\nmax \in \{3, 4, 5\}$:\ same construction, panel size grows
  linearly in $\nmax$ as $3 \cdot N(\nmax)$. Sprint-scale.
\item \textbf{$\SL_{2}$ on higher Peter--Weyl reps.} Theorem~\ref{thm:sl2_pw}
  on $\mathrm{Sym}^{k} V_{\mathrm{fund}}$ for $k \ge 3$. Sprint-scale.
\item \textbf{Non-natural-substrate enlargements.} The Peter--Weyl
  decoration of §\ref{sec:sl2_explicit} is the natural substrate
  (acts on disjoint tensor factor from $\Ga^{3 N}$, so commutativity
  is by the Kronecker identity). Genuinely-new strong-form content
  lives on \emph{enlarged} substrates where $\Ga$ and $\SL_{2}$ act
  on the same tensor factor;\ that is multi-year structural content,
  analogous to the Paper~46 Appendix~B enlarged-substrate program.
\item \textbf{Inverse-limit reconstruction.} The reconstruction
  argument at the inverse-limit level $\Ginf$ coherent with the
  v3.66.0 FO3 period content is named as PS-3.5 in the roadmap;\
  multi-year, the heart of Tannakian reconstruction for \textsc{GeoVac}.
\end{itemize}

% =====================================================================
\section*{Acknowledgements}
% =====================================================================

This work was developed in an AI-augmented agentic workflow with
Anthropic's Claude (model:\ Claude Opus 4.7). All theorems, design
choices, and editorial decisions are the author's responsibility.
Implementation, internal memos, and bibliographic collation were
performed collaboratively.

% =====================================================================
\begin{thebibliography}{99}
% =====================================================================

\bibitem{deligne_milne1982}
P.~Deligne and J.~S.~Milne, \emph{Tannakian categories}, in
``Hodge Cycles, Motives, and Shimura Varieties'', Lecture Notes in
Math.\ \textbf{900} (1982) 101--228.

\bibitem{deligne1990}
P.~Deligne, \emph{Cat\'egories tannakiennes}, in ``The Grothendieck
Festschrift'' Vol.~II, Progr.\ Math.\ \textbf{87} (Birkh\"auser, 1990)
111--195.

\bibitem{brown2012}
F.~Brown, \emph{Mixed Tate motives over $\mathbb{Z}$}, Ann.\ of
Math.\ \textbf{175} (2012) 949--976.

\bibitem{andre2004}
Y.~Andr\'e, \emph{Une introduction aux motifs (motifs purs, motifs
mixtes, p\'eriodes)}, Panoramas et Synth\`eses \textbf{17}, Soci\'et\'e
Math\'ematique de France, 2004.

\bibitem{brown2017}
F.~Brown, \emph{Motivic periods and the projective line minus three
points}, Proc.\ ICM 2014, Vol.~II (Kyung Moon Sa, Seoul, 2014)
295--318;\ arXiv:1407.5165.

\bibitem{hain2014}
R.~Hain, \emph{The Hodge-de Rham theory of modular groups}, in
``Recent advances in Hodge theory'' (LMS Lecture Notes 427,
Cambridge Univ.\ Press, 2016) 422--514;\ arXiv:1403.6443.

\bibitem{deligne2010}
P.~Deligne, \emph{Le groupe fondamental unipotent motivique de
$\mathbb{G}_m - \mu_N$, pour $N = 2, 3, 4, 6, 8$}, Publ.\ Math.\
IH\'ES \textbf{112} (2010) 101--141.

\bibitem{glanois2015}
C.~Glanois, \emph{Periods of the motivic fundamental group of
$\mathbb{P}^1 - \{0, \mu_N, \infty\}$}, PhD thesis, Universit\'e Pierre
et Marie Curie, 2015.

\bibitem{connes_marcolli2004}
A.~Connes and M.~Marcolli, \emph{Renormalization and motivic Galois
theory}, Internat.\ Math.\ Res.\ Notices \textbf{2004(76)} (2004)
4073--4091;\ arXiv:math/0409306.

\bibitem{marcolli_vansuijlekom2014}
M.~Marcolli and W.~D.~van Suijlekom, \emph{Gauge networks in
noncommutative geometry}, J.~Geom.\ Phys.\ \textbf{75} (2014)
71--91;\ arXiv:1301.3480.

\bibitem{perez_sanchez2024}
G.~A.~Perez-Sanchez, \emph{Erratum to Marcolli--van Suijlekom 2014:\
Higgs from off-diagonal $D_F$ blocks}, arXiv:2401.03705 (2024).

\bibitem{perez_sanchez2025}
G.~A.~Perez-Sanchez, \emph{The Standard Model without Higgs:\
spectral action on Marcolli--van Suijlekom gauge networks}, arXiv:2508.17338 (2025).

\bibitem{paper7}
J.~Loutey, \emph{The dimensionless vacuum:\ Fock projection,
conformal equivalence, and the 18 symbolic proofs}, GeoVac Paper~7
(2025).

\bibitem{paper18}
J.~Loutey, \emph{Spectral-geometric exchange constants and the master
Mellin engine}, GeoVac Paper~18 (2025--2026).

\bibitem{paper31}
J.~Loutey, \emph{Universal vs.\ Coulomb-specific partition of the
GeoVac spectral triple}, GeoVac Paper~31 (2026).

\bibitem{paper32}
J.~Loutey, \emph{The GeoVac spectral triple:\ explicit construction
and Connes axiom audit}, GeoVac Paper~32 (2026).

\bibitem{paper38}
J.~Loutey, \emph{$SU(2)$ propinquity convergence of the
Camporesi--Higuchi spectral triple}, GeoVac Paper~38 (2026).

\bibitem{paper45}
J.~Loutey, \emph{$K^{+}$-restricted weak-form Lorentzian propinquity
on truncated $SU(2) \times U(1)_T$ Krein spectral triples}, GeoVac
Paper~45 (2026).

\bibitem{paper46}
J.~Loutey, \emph{Strong-form Lorentzian propinquity on the natural
chirality-doubled scalar-multiplier substrate}, GeoVac Paper~46 (2026).

\bibitem{paper47}
J.~Loutey, \emph{Norm-resolvent convergence to the non-compact
Lorentzian Krein spectral triple on $S^3 \times \mathbb{R}_t$}, GeoVac
Paper~47 (2026).

\bibitem{paper48}
J.~Loutey, \emph{The Krein--Mondino--S\"amann bridge:\ K$^{+}$-weak-form
synthesis}, GeoVac Paper~48 (2026).

\bibitem{paper49}
J.~Loutey, \emph{Operator-system Lorentzian pre-length spaces and the
strong-form Krein--Mondino--S\"amann bridge}, GeoVac Paper~49 (2026).

\bibitem{paper55}
J.~Loutey, \emph{Periods of GeoVac:\ cyclotomic mixed-Tate
classification of the master Mellin engine}, GeoVac Paper~55 (2026).

\bibitem{fathizadeh_marcolli2016}
F.~Fathizadeh and M.~Marcolli, \emph{Periods and motives in the
spectral action of Robertson--Walker spacetimes}, Comm.\ Math.\
Phys.\ \textbf{356} (2017) 641--671;\ arXiv:1611.01815.

\bibitem{eskandari_murty_nemoto2025}
P.~Eskandari, M.~R.~Murty, and Y.~Nemoto, \emph{Mixed motives and
linear forms in the Catalan constant}, arXiv:2510.20648 (2025).

\bibitem{goncharov_deligne2005}
A.~B.~Goncharov, \emph{Periods and mixed motives}, preprint
arXiv:math/0202154 (2002);\ see also P.~Deligne and A.~B.~Goncharov,
\emph{Groupes fondamentaux motiviques de Tate mixte},
\textit{Ann. Sci. \'Ecole Norm. Sup.}~(4) \textbf{38}, 1--56 (2005).
The Goncharov--Deligne 2005 result establishes the faithful action of
the motivic Galois group $\mathcal{G}_{\mathrm{MT}(\mathcal{O}_N[1/N])}$
on the motivic fundamental group
$\pi_1^{\mathrm{mot}}(\mathbb{G}_m - \mu_N)$, used here as the
injection-direction backbone for the level-4 period comparison.

\bibitem{cartier_milnor_moore}
J.~W.~Milnor and J.~C.~Moore, \emph{On the structure of Hopf algebras},
\textit{Ann.\ of Math.}~(2) \textbf{81}, 211--264 (1965);\ P.~Cartier,
\emph{A primer of Hopf algebras}, in \textit{Frontiers in Number
Theory, Physics, and Geometry II}, Springer (2007) 537--615.
The Cartier--Milnor--Moore theorem in characteristic zero
identifies any primitively generated cocommutative Hopf algebra as
the universal enveloping algebra of its Lie algebra of primitives;\
applied to $\HGV = \Sym_{\Q}(V)$ (with $V$ abelian), the Tannakian
dual is forced to be abelian unipotent (NA-1 structural finding).

\bibitem{loutey_paper28}
J.~Loutey, \emph{QED on $S^3$:\ five theorems, $S_{\min}$
irreducibility, and the Sommerfeld series}, GeoVac Paper~28 (2026).

\end{thebibliography}

\end{document}
