\documentclass[aps,prl,twocolumn,superscriptaddress]{revtex4-2}
\usepackage{amsmath,amssymb,graphicx,xcolor}

\begin{document}

\title{The Fine Structure Constant from Spectral Geometry of the Hopf Fibration}

\author{J.~Loutey}
\affiliation{Independent Researcher, Kent, Washington}

\date{February 25, 2026}

\begin{abstract}
We observe that the fine structure constant $\alpha$ satisfies the cubic
equation $\alpha^3 - K\alpha + 1 = 0$, where the coefficient
$K = \pi(42 + \pi^2/6 - 1/40) = 137.036064$ is constructed from
spectral invariants of the Hopf fibration $S^1 \to S^3 \to S^2$: the
degeneracy-weighted Casimir trace of the $S^2$ base ($B = 42$), the
spectral zeta function of the $S^1$ fiber ($F = \zeta(2) = \pi^2/6$),
and a boundary correction from the $S^3$ total space
($\Delta = 1/40$). The selection principle $B/N = \dim(S^3) = 3$ is
proven algebraically to select $n_{\max} = 3$ uniquely. The resulting
$\alpha^{-1} = 137.035987$ agrees with experiment to
$8.8 \times 10^{-8}$ relative error with zero free parameters. A
combinatorial search over $1.92 \times 10^9$ formulas built from the
same spectral ingredients yields a $p$-value of
$5.2 \times 10^{-9}$, establishing that this precision is very
unlikely to be accidental. The cubic is shown to be the characteristic
polynomial of a traceless $\mathbb{Z}_3$-symmetric circulant matrix,
suggesting democratic coupling among the three bundle components.
However, the combination rule $K = \pi(B + F - \Delta)$ remains
conjectural: this is an empirical formula with structural support, not
a first-principles derivation.
\end{abstract}

\maketitle

%======================================================================
\section{Introduction}
%======================================================================

Richard Feynman called the fine structure constant
$\alpha = e^2/(4\pi\epsilon_0\hbar c) \approx 1/137.036$ ``one of the
greatest damn mysteries of physics''~\cite{feynman1985}. Despite a
century of quantum theory, $\alpha$ remains an unexplained input to
the Standard Model. Attempts to derive it
numerically---from~$\pi$,~$e$, prime numbers, or Platonic
solids---have uniformly failed~\cite{eddington1935,barrow2002}.
Eddington's ``proton--electron mass ratio'' argument and Wyler's
symmetric-space formula~\cite{wyler1969} both achieved suggestive
precision but were criticized for lacking a physical mechanism
connecting the mathematical structure to electromagnetic
coupling~\cite{robertson1971}.

The present work is situated within the GeoVac program, which
established that the discrete graph Laplacian for hydrogen is
mathematically equivalent to the Laplace--Beltrami operator on the
unit three-sphere~$S^3$, related to the Schr\"odinger equation via
Fock's 1935 stereographic projection~\cite{paper7}. The electron's
bound-state manifold \textit{is}~$S^3$---a result supported by 18
independent symbolic proofs~\cite{paper7}.

This three-sphere carries a unique fiber bundle structure: the Hopf
fibration~\cite{hopf1931,urbantke2003}
\begin{equation}\label{eq:hopf}
  S^1 \;\longrightarrow\; S^3 \;\longrightarrow\; S^2.
\end{equation}
The base $S^2$ parametrizes photon propagation directions, while the
fiber $S^1$ encodes the $U(1)$ electromagnetic gauge phase. We
identify a formula for $\alpha$ built entirely from the spectral
invariants of these three manifolds, validate it statistically against
a large space of alternative formulas, and identify structural
underpinnings (a $\mathbb{Z}_3$-symmetric circulant matrix) that
explain the cubic form. We also characterize precisely what remains
unestablished.

We state clearly at the outset: \textit{this is an empirical formula
with structural support, not a first-principles derivation.} The
combination rule that assembles the spectral invariants into the
coupling constant $K$ is observed, not derived.

An earlier version of this work~\cite{paper2_old} attempted to extract
$\alpha$ from a ``symplectic impedance'' ratio on the electron
lattice, achieving $6.2 \times 10^{-5}$ relative error with a fitted
helical pitch. The present result eliminates all fitted parameters and
improves precision by a factor of~500.


%======================================================================
\section{The Hopf Bundle as Electron--Photon Geometry}
%======================================================================

Fock's 1935 stereographic projection maps the hydrogen momentum
eigenvalue problem onto the unit three-sphere~\cite{fock1935}. The
eigenvalues of the Laplace--Beltrami operator on $S^3$ are
\begin{equation}\label{eq:s3eig}
  \lambda_n = -(n^2 - 1), \qquad n = 1, 2, 3, \ldots
\end{equation}
with degeneracy $g_n = n^2$, reproducing the hydrogen spectrum upon
projection to flat space via the energy-shell constraint
$p_0^2 = -2E$~\cite{paper7}. This identification is exact: the graph
Laplacian on the discrete lattice and the continuum operator on $S^3$
share the same spectrum, as verified by 18 independent symbolic
proofs~\cite{paper7}.

The three-sphere admits a unique fiber bundle structure, the Hopf
fibration~(\ref{eq:hopf}). Concretely, the map
$\pi: S^3 \to S^2$ sends each point $(z_1, z_2) \in \mathbb{C}^2$
with $|z_1|^2 + |z_2|^2 = 1$ to the ratio $z_1/z_2 \in S^2$. Each
fiber $\pi^{-1}(p)$ is a great circle $S^1 \subset S^3$.

We interpret the three components physically:
\begin{itemize}
\item \textbf{Total space $S^3$:} The electron bound-state manifold,
  as established by the Fock projection.
\item \textbf{Base $S^2$:} The photon momentum sphere, parametrizing
  propagation directions of the electromagnetic field.
\item \textbf{Fiber $S^1$:} The $U(1)$ gauge phase of the
  electromagnetic potential.
\end{itemize}

This identification is natural: the Hopf fibration is the geometric
expression of $U(1)$ gauge symmetry acting on the electron's state
space. Electromagnetic coupling is the ``cost'' of projecting $S^3$
onto~$S^2$---the information lost in the fiber.


%======================================================================
\section{Spectral Invariants of the Bundle}
%======================================================================

Each component of the Hopf bundle carries intrinsic spectral data. We
extract one canonical invariant from each.

\subsection{Base manifold $S^2$: Casimir trace}

The eigenvalues of the Laplacian on $S^2$ are $l(l+1)$ with
degeneracy $2l+1$. These are the Casimir eigenvalues of $SO(3)$. We
define the \textit{degeneracy-weighted Casimir trace} as
\begin{equation}\label{eq:casimir}
  B(n_{\max}) = \sum_{n=1}^{n_{\max}} \sum_{l=0}^{n-1}
  (2l+1)\,l(l+1),
\end{equation}
where the outer sum runs over principal shells (each shell $n$
contains angular momenta $l = 0, \ldots, n-1$). This is the total
angular momentum content of all electron states up to
shell~$n_{\max}$, weighted by the magnetic degeneracy of each
subshell.

At $n_{\max} = 3$, the explicit computation gives
\begin{align}
  B(3) &= \underbrace{0}_{(1,0)}
         + \underbrace{0}_{(2,0)} + \underbrace{6}_{(2,1)}
         + \underbrace{0}_{(3,0)} + \underbrace{6}_{(3,1)}
         + \underbrace{30}_{(3,2)} \notag \\
       &= 42,
\end{align}
where subscripts denote $(n, l)$ pairs.


\subsection{Selection principle}

The total number of states through shell $n_{\max}$ is
$N(n_{\max}) = \sum_{n=1}^{n_{\max}} n^2 = n_{\max}(n_{\max}+1)(2n_{\max}+1)/6$.
We prove that the ratio
\begin{equation}\label{eq:selection}
  \frac{B(n_{\max})}{N(n_{\max})} = \dim(S^3) = 3
\end{equation}
is satisfied uniquely at $n_{\max} = 3$.

The inner sum in Eq.~(\ref{eq:casimir}) has a closed form:
\begin{equation}\label{eq:innersum}
  \sum_{l=0}^{n-1}(2l+1)\,l(l+1) = \frac{n^2(n^2-1)}{2}.
\end{equation}
Therefore $B(m) = \sum_{n=1}^{m} n^2(n^2-1)/2$, which, using the
standard power-sum identities $\sum n^2$ and $\sum n^4$, evaluates to
\begin{equation}\label{eq:Bclosed}
  B(m) = \frac{m(m+1)(2m+1)(m+2)(m-1)}{20}.
\end{equation}
The ratio simplifies by cancellation:
\begin{equation}\label{eq:ratioclosed}
  \frac{B(m)}{N(m)} = \frac{3(m+2)(m-1)}{10}.
\end{equation}
Setting $B/N = 3$ gives $(m+2)(m-1) = 10$, i.e.,
$m^2 + m - 12 = (m+4)(m-3) = 0$,
whose unique positive root is $m = 3$. This completes the algebraic
proof: $n_{\max} = 3$ is the \textit{only} positive integer at which
the selection principle holds.

\begin{table}[h]
\centering
\begin{tabular}{cccc}
\hline\hline
$n_{\max}$ & $B(n_{\max})$ & $N(n_{\max})$ & $B/N$ \\
\hline
1 & 0   & 1  & 0.000 \\
2 & 6   & 5  & 1.200 \\
3 & 42  & 14 & 3.000 \\
4 & 162 & 30 & 5.400 \\
5 & 462 & 55 & 8.400 \\
\hline\hline
\end{tabular}
\caption{The selection principle $B/N = 3$ is satisfied uniquely at
$n_{\max} = 3$, as proven algebraically via
Eq.~(\ref{eq:ratioclosed}).}
\label{tab:selection}
\end{table}

This result connects to the Casimir structure of $SO(4)$. In the
Peter--Weyl decomposition of $L^2(S^3)$, each shell~$n$ carries the
$(j,j)$ representation of $SO(4) \cong (SU(2) \times SU(2))/\mathbb{Z}_2$
with $j = (n-1)/2$. The $SO(3) \subset SO(4)$ Casimir has per-shell
average
\begin{equation}\label{eq:casimir_identity}
  \langle C_3 \rangle_n
  = \frac{1}{n^2}\sum_{l=0}^{n-1}(2l+1)\,l(l+1)
  = \frac{n^2-1}{2} = C_4(n),
\end{equation}
which equals the $SO(4)$ Casimir eigenvalue. The selection principle
$B/N = 3$ is therefore equivalent to requiring that the
degeneracy-weighted average of the $SO(4)$ Casimir over shells
$1 \leq n \leq n_{\max}$ equals $\dim(S^3)$.

The base manifold invariant is
\begin{equation}\label{eq:base}
  \boxed{B = \sum_{n=1}^{3}\sum_{l=0}^{n-1}(2l+1)\,l(l+1) = 42.}
  \vphantom{\Bigg|}
\end{equation}


\subsection{Fiber $S^1$: Spectral zeta function}

The eigenvalues of the Laplacian on $S^1$ (a circle of circumference
$2\pi$) are $k^2$ for $k \in \mathbb{Z}$. The spectral zeta function
is
\begin{equation}
  \zeta_{S^1}(s) = 2\sum_{k=1}^{\infty} k^{-2s}
                 = 2\,\zeta_R(2s),
\end{equation}
where $\zeta_R$ is the Riemann zeta function. At $s = 1$:
\begin{equation}\label{eq:fiber}
  F = \zeta_R(2) = \frac{\pi^2}{6}.
\end{equation}
This is the zeta-regularized spectral invariant of the photon gauge
phase circle. Equivalently, $F$ is a Dirichlet series of the Fock
shell degeneracy,
$F = D_{n^2}(d_{\max}) := \sum_{n\geq 1} n^2\, n^{-d_{\max}} =
\zeta_R(2)$, where $n^2$ is the $n$-th $S^3$ shell degeneracy and
$d_{\max}=4$ is the packing lattice maximum degree (Paper~0),
linking $F$ to both the Fock projection and the packing axioms.


\subsection{Total space $S^3$: Boundary correction}

The total space $S^3$ contributes a finite-size correction from
the interplay of its eigenvalue spectrum~(\ref{eq:s3eig}) with the
cumulative state count. At the selected cutoff $n_{\max} = 3$, the
highest eigenvalue is $\lambda_3 = -(3^2 - 1) = -8$ and the
cumulative state count through the first non-trivial shell is
$N(2) = \sum_{n=1}^{2} n^2 = 1 + 4 = 5$. The boundary term is
\begin{equation}\label{eq:boundary}
  \boxed{\Delta = \frac{1}{|\lambda_3| \times N(2)}
                = \frac{1}{8 \times 5} = \frac{1}{40}.}
                \vphantom{\Bigg|}
\end{equation}
The physical significance of this boundary term is not established.
It may be suggestive of UV/IR mixing on the compact manifold, but
this interpretation is speculative.


%======================================================================
\section{The Formula}
%======================================================================

Combining the three spectral invariants, we define the
\textit{coupling constant}:
\begin{equation}\label{eq:K}
  K = \pi\!\left(B + F - \Delta\right)
    = \pi\!\left(42 + \frac{\pi^2}{6} - \frac{1}{40}\right).
\end{equation}
Numerically,
\begin{equation}
  K = \pi\,(42 + 1.644934 - 0.025000)
    = \pi \times 43.619934
    = 137.036064.
\end{equation}

The physical $\alpha$ satisfies a self-consistency condition
\begin{equation}\label{eq:selfconsistent}
  \frac{1}{\alpha} + \alpha^2 = K,
\end{equation}
which, upon multiplication by $\alpha$, yields
\begin{equation}\label{eq:cubic}
  \boxed{\alpha^3 - K\alpha + 1 = 0.}
\end{equation}

This depressed cubic has three real roots (verified by its
discriminant $4K^3 - 27 > 0$). The physical root is the smallest
positive one, corresponding to perturbative QED ($\alpha \ll 1$).

Solving numerically:

\begin{table}[h]
\centering
\begin{tabular}{lcc}
\hline\hline
Quantity & Value & Source \\
\hline
$K$ & $137.036064$ & Eq.~(\ref{eq:K}) \\
$\alpha^{-1}$ (formula) & $137.035987$ & Eq.~(\ref{eq:cubic}) \\
$\alpha^{-1}$ (CODATA 2018) & $137.035999\ldots$ & Experiment \\
\hline
Relative error & $8.8 \times 10^{-8}$ & \\
\hline\hline
\end{tabular}
\caption{Comparison of the Hopf bundle formula with the experimental
value.}
\label{tab:comparison}
\end{table}


%======================================================================
\section{Statistical Validation}
%======================================================================

A formula involving $\pi$, $42$, and $\pi^2/6$ matching $\alpha^{-1}$
to $8.8 \times 10^{-8}$ could in principle be a numerical
coincidence. To test this, we performed a systematic combinatorial
search~\cite{phase2_audit}.

\subsection{Search space}

The search considers formulas of the form $\alpha^{-1} = T(A + B + C)$
or, equivalently, the cubic $\alpha^3 - T(A+B+C)\alpha + 1 = 0$,
where:
\begin{itemize}
\item $A$, $B$, $C$ are drawn from a pool of spectral quantities:
  eigenvalues $|\lambda_n|$, degeneracies $n^2$ and $2l+1$, Casimir
  values $l(l+1)$, cumulative counts $N(n)$, their pairwise products
  up to~50, and the transcendentals $\zeta(2)$, $\zeta(3)$, $\zeta(4)$,
  $\ln 2$, $\pi$, $\pi^2$ (743 unique term values total).
\item $T$ ranges over 14 transcendental prefactors: $\pi$, $2\pi$,
  $\pi^2$, $\pi/2$, $4\pi$, $4\pi^2$, $1/(2\pi)$, $1$, $2$,
  $1/2$, $\pi/4$, $\pi/6$, $1/\pi$, $\sqrt{\pi}$.
\end{itemize}

Both linear ($\alpha^{-1} = T \cdot S$) and cubic
($\alpha^3 - T \cdot S \cdot \alpha + 1 = 0$) interpretations are
tested, giving $1.92 \times 10^9$ total formulas.

\subsection{Results}

\begin{table}[h]
\centering
\begin{tabular}{rrrr}
\hline\hline
Threshold & Hits & Fraction \\
\hline
$10^{-2}$          & 1{,}283{,}592  & $6.7 \times 10^{-4}$ \\
$10^{-3}$          &   125{,}027    & $6.5 \times 10^{-5}$ \\
$10^{-4}$          &    14{,}476    & $7.5 \times 10^{-6}$ \\
$10^{-5}$          &       682      & $3.5 \times 10^{-7}$ \\
$10^{-6}$          &        37      & $1.9 \times 10^{-8}$ \\
$10^{-7}$          &        11      & $5.7 \times 10^{-9}$ \\
$8.8\times 10^{-8}$ &       10      & $5.2 \times 10^{-9}$ \\
\hline\hline
\end{tabular}
\caption{Hit distribution across precision thresholds. The hit
fraction scales approximately linearly with threshold, consistent with
a uniform distribution in $\alpha^{-1}$ space.}
\label{tab:hits}
\end{table}

At the paper's precision of $8.8 \times 10^{-8}$, only 10 formulas
out of $1.92 \times 10^9$ match as well or better, yielding
\begin{equation}
  \boxed{p\text{-value} = 5.2 \times 10^{-9}.}
\end{equation}
The 10 formulas that beat the paper's precision involve combinations
such as $4\pi(5/49 + 14/15 + \pi^2)$ that lack physical
interpretation in the Hopf bundle context. The paper's formula is the
only one among the top matches with a coherent geometric narrative.

The $p$-value establishes that the precision is very unlikely to be
accidental. It does not, by itself, constitute a derivation---but it
does distinguish this formula from generic numerology.


%======================================================================
\section{The Circulant Structure}
%======================================================================

The cubic $\alpha^3 - K\alpha + 1 = 0$ is not an arbitrary polynomial
ansatz. It arises naturally as the characteristic polynomial of a
traceless $3 \times 3$ circulant matrix.

\subsection{Circulant eigenvalue equation}

Consider the traceless circulant
\begin{equation}\label{eq:circulant}
  M = \begin{pmatrix} 0 & b & c \\ c & 0 & b \\ b & c & 0
      \end{pmatrix},
\end{equation}
which has $\mathbb{Z}_3$ symmetry (invariance under cyclic permutation
of rows and columns). Its characteristic polynomial is
\begin{equation}
  \det(M - sI) = -s^3 + 3bc\,s + (b^3 + c^3) = 0.
\end{equation}
Setting $bc = K/3$ and $b^3 + c^3 = -1$ (equivalently,
$\det M = -1$), this becomes
\begin{equation}
  s^3 - Ks + 1 = 0,
\end{equation}
which is \textit{exactly} the paper's cubic with $s = \alpha$. The
eigenvalues of $M$ are the three roots of the cubic.

\subsection{Physical interpretation}

The $\mathbb{Z}_3$ symmetry of the circulant represents
\textit{democratic coupling}: each of the three objects (labeled $1$,
$2$, $3$) interacts equally with the other two. In the Hopf bundle
context, the three objects are the fiber $S^1$, the base $S^2$, and
the total space $S^3$. Each component contributes a spectral
invariant; the circulant structure implies that their coupling respects
the cyclic symmetry of the bundle decomposition.

The $SU(2)$ structure constants $\varepsilon_{ijk}$ exhibit the same
$\mathbb{Z}_3$ cyclic symmetry, producing a circulant with $b = c = 1$
and characteristic polynomial $s^3 - 3s - 2 = 0$. The paper's cubic
has the \textit{same algebraic structure} with coupling strength
$K/3 \approx 45.7$ instead of~1.

\subsection{Structural content and limitations}

The circulant interpretation is a \textit{structural} result: it
explains why the self-consistency equation takes the form of a
depressed cubic with unit constant term. These features follow from
three conditions:
\begin{enumerate}
\item Tracelessness: $\mathrm{tr}(M) = 0$ (eliminates the $s^2$ term).
\item $\mathbb{Z}_3$ symmetry: only two free parameters ($b$, $c$).
\item Unit determinant condition: $\det(M) = b^3 + c^3 = -1$ (fixes
  the constant term).
\end{enumerate}

The condition $\det(M) = -1$ is consistent with the chirality of the
Hopf map (linking number $+1$) and with the fermionic sign convention
($\psi \to -\psi$ under $2\pi$ rotation of the $S^1$ fiber), but
neither identification constitutes a derivation.

The circulant explains \textit{why a cubic}, but does not derive
\textit{why this specific~$K$}. The single free parameter $bc = K/3$
encodes the coupling strength, and its value
$\pi(42 + \pi^2/6 - 1/40)/3$ is not determined by the circulant
structure alone.

\subsection{Forced Hermiticity and the physical phase}

The coupling parameters $b$, $c$ are necessarily complex conjugates.
Setting $s = b + c$ and $p = bc = K/3$, the constraint $b^3 + c^3 = -1$
reduces to $s^3 - Ks + 1 = 0$---the \textit{same cubic} as for
$\alpha$. For real $b$ and $c$, one requires $s^2 \geq 4K/3$, but all
three roots satisfy $s_i^2 < 4K/3 \approx 182.7$ (the largest is
$s_1^2 \approx 137.1$). Therefore~\cite{phase3_audit}
\begin{equation}\label{eq:polar}
  b = \sqrt{K/3}\; e^{i\theta}, \qquad
  c = \sqrt{K/3}\; e^{-i\theta},
\end{equation}
with universal modulus $|b| = |c| = \sqrt{K/3} \approx 6.76$. The
determinant condition fixes the phase:
\begin{equation}\label{eq:phase}
  \cos(3\theta) = -\frac{1}{2(K/3)^{3/2}} \approx -0.00162.
\end{equation}
Three solutions separated by ${\sim}120^\circ$ correspond to the
three roots. The physical root $\alpha$ has $\theta \approx 3\pi/2$
(nearly pure imaginary coupling: $b \approx -i\sqrt{K/3}$).

The circulant $M$ is therefore \textit{Hermitian}, not real symmetric,
consistent with the $U(1)$ gauge structure of the Hopf fiber: the
off-diagonal coupling carries a phase, as expected for a connection on
a principal $U(1)$-bundle.

\subsection{Self-referential property}

The fact that $b + c$ satisfies the same cubic as $\alpha$ is
structural, not coincidental. For any circulant of the
form~(\ref{eq:circulant}), the $k = 0$ discrete Fourier transform (DFT)
mode is $\lambda_0 = b + c$, which is by construction an eigenvalue
of~$M$ and therefore satisfies its characteristic polynomial. All three
eigenvalues of $M$ are the three cubic roots, regardless of which root
$b + c$ equals~\cite{phase3_audit}.

The circulant decomposition does not factor $K$ into independent
spectral invariants of individual bundle components. The modulus
$|b| = \sqrt{K/3}$ and the phase $\theta$ are both determined by $K$
alone. The irreducible datum remains $K$ itself.


%======================================================================
\section{What Is and Is Not Established}
%======================================================================

Following the epistemic standards of the GeoVac program, we assess
each link in the hypothetical derivation chain.

\begin{table}[h]
\centering
\begin{tabular}{clc}
\hline\hline
Link & Description & Status \\
\hline
1 & Hopf bundle as geometric arena & $\checkmark$ \\
2 & Spectral data $\to$ $B$, $F$, $\Delta$ & $\bullet$\footnotemark[1] \\
3 & Combination rule $K = \pi(B+F-\Delta)$ & $\times$ \\
4 & $\mathbb{Z}_3$ circulant $\to$ cubic & $\circ$\footnotemark[2] \\
5 & $\alpha$ from cubic root & $\checkmark$ \\
\hline\hline
\end{tabular}
\caption{Derivation chain assessment.
$\checkmark$ = established,
$\bullet$ = largely established (see footnote),
$\circ$ = partially established,
$\times$ = not established.}
\label{tab:chain}
\end{table}
\footnotetext[1]{The selection principle $B/N = 3$ is algebraically
proven (Sec.~III), and the Casimir identity
$\langle C_3\rangle_n = C_4(n)$ connects $B$ to the $SO(4)$
representation theory. The remaining gap: why the degeneracy-weighted
Casimir trace specifically (rather than some other spectral quantity)
for each bundle component. The second selection principle
(Sec.~\ref{sec:second_selection}) provides independent support.}
\footnotetext[2]{The Hermiticity of the circulant is now proven:
$b$ and $c$ are necessarily complex conjugates (Sec.~VI\,D). This is
consistent with $U(1)$ gauge structure but does not yet derive
$bc = K/3$.}

\textbf{Link~1} (established): The Hopf fibration is the unique
principal $U(1)$-bundle over $S^2$ with $c_1 = 1$. That $S^3$ is the
electron state manifold is proven in Ref.~\cite{paper7}. Using the
Hopf bundle as a geometric framework is a natural choice.

\textbf{Link~2} (largely established): The selection principle
$B/N = 3$ is proven algebraically to select $n_{\max} = 3$ uniquely
(Sec.~III). The per-shell Casimir identity
$\langle C_3\rangle_n = C_4(n) = (n^2-1)/2$ establishes that $B$ is
the trace of the $SO(3)$ Casimir over the truncated Peter--Weyl
decomposition of $L^2(S^3)$, connecting it to the representation
theory of $SO(4)$. The remaining gap is the \textit{choice} of which
spectral quantity to extract from each bundle component: why the
Casimir trace for the base (not, say, the spectral determinant), why
$\zeta(2)$ for the fiber (not $\zeta(1)$ or $\zeta(3)$), and why
$1/(|\lambda_3| \times N(2))$ for the boundary.

\textbf{Link~3} (not established): This is the critical gap. No
principle selects the specific additive combination
$K = \pi(B + F - \Delta)$ over alternatives such as
$K = \pi B + F - \Delta$ or $K = \pi B F / \Delta$. The overall
prefactor $\pi$ could be argued as natural (it appears in the
stereographic projection), but the additive structure is unexplained.
A systematic search over spectral determinants, Ray--Singer analytic
torsion, Seeley--DeWitt heat kernel coefficients, and
Atiyah--Patodi--Singer invariants of the three bundle components finds
no natural combination that reproduces $K$ or $K/\pi$. The spectral
determinant product
$\det'(\Delta_{S^1}) \cdot \det'(\Delta_{S^3})/\pi \approx 41.957$
approaches $B = 42$ to $0.1\%$ (see Sec.~VIII) but the gap is not
bridgeable by known spectral corrections. The combination rule mixes a
discrete combinatorial quantity ($B = 42$) with a continuous spectral
invariant ($F = \zeta(2)$) in a way that has no precedent in spectral
geometry. If Link~3 can be closed, the mechanism likely involves the
representation theory of $SO(4)$ rather than the analysis of smooth
differential operators.

\textbf{Link~4} (partial): The cubic form arises naturally from
$\mathbb{Z}_3$-symmetric coupling, and the $SU(2)$ structure constants
share this symmetry. But no derivation connects the Hopf bundle to the
specific circulant with $bc = K/3$.

\textbf{Link~5} (established): Given the cubic, selecting the smallest
positive root is pure algebra.

The structural choices that remain underived are:
\begin{enumerate}
\item Why additive combination $B + F - \Delta$ (not multiplicative)?
\item Why $\pi$ as the overall prefactor?
\item Why $\zeta(2)$ specifically for the fiber (not $\zeta(1)$,
  $\zeta(3)$, etc.)?
\item Why $1/(|\lambda_3| \times N(2))$ for the boundary (not other
  spectral ratios)?
\item Why $\det(M) = -1$?
\end{enumerate}

\textit{Three-tier composition.} $K = \pi(B + F - \Delta)$ assembles
three categorically different objects: $B$ (finite Casimir, rational),
$F$ (infinite Dirichlet series at the packing exponent,
transcendental), $\Delta$ (boundary product at the truncation edge,
rational). Computation identifies each piece but finds no common
generator. The open question is reframed from ``how is each piece
derived'' to ``why does their additive combination equal
$\alpha^{-1}$ to $8.8\times 10^{-8}$''---a structural conspiracy
about the sum, not a derivation about the parts.


%======================================================================
\section{Discussion}
%======================================================================

\subsection{Comparison with Wyler's formula}

Wyler's 1969 formula~\cite{wyler1969} also invokes symmetric spaces
and achieves $\sim 10^{-5}$ precision. However, Wyler's derivation
was criticized for lacking a physical mechanism connecting the
symmetric space volumes to electromagnetic
coupling~\cite{robertson1971}. The present work improves on this
situation in two respects: (i)~$S^3$ is the \textit{proven} electron
state manifold, providing a physical mechanism, and (ii)~the
$p$-value of $5.2 \times 10^{-9}$ quantitatively distinguishes the
formula from numerology. However, both approaches share the weakness
of an unjustified combination rule.

\subsection{Comparison with previous approach}

An earlier attempt by the same author~\cite{paper2_old} modeled
$\alpha^{-1}$ as a ``symplectic impedance'' ratio on the
paraboloid lattice, achieving $6.2 \times 10^{-5}$ relative error
with a fitted helical pitch. The present result achieves
$8.8 \times 10^{-8}$---a $500\times$ improvement---with zero free
parameters.

\begin{table}[h]
\centering
\begin{tabular}{lccc}
\hline\hline
Method & Error & Free params & Cutoff \\
\hline
Symplectic impedance~\cite{paper2_old} & $6.2\times 10^{-5}$ & 1 & $n=5$ \\
\textbf{Hopf bundle (this work)} & $\mathbf{8.8\times 10^{-8}}$ & \textbf{0} & $n=3$ \\
\hline\hline
\end{tabular}
\caption{Evolution of the geometric approach.}
\label{tab:evolution}
\end{table}


\subsection{Spectral determinant near-miss}

The zeta-regularized spectral determinants of the bundle components
are $\det'(\Delta_{S^1}) = 4\pi^2$,
$\det'(\Delta_{S^2}) = e^{1/2 - 4\zeta'_R(-1)}$, and
$\det'(\Delta_{S^3}) = \pi\, e^{\zeta(3)/(2\pi^2)}$. The product
\begin{equation}
  \frac{\det'(\Delta_{S^1}) \cdot \det'(\Delta_{S^3})}{\pi}
  = 4\pi^2 e^{\zeta(3)/(2\pi^2)} \approx 41.957
\end{equation}
is $0.1\%$ from $B = 42$. Whether this near-miss reflects a deeper
connection between the Casimir trace and spectral determinants, or is
merely a coincidence, remains an open question. If a correction term
derivable from the fibration geometry could bridge the $0.1\%$ gap
between $4\pi^2 e^{\zeta(3)/(2\pi^2)}$ and~$42$, it would provide a
path from standard spectral determinants to the Casimir trace,
potentially grounding Link~2 of the derivation chain
(Table~\ref{tab:chain}) in established spectral geometry. Replacing $B = 42$
with this determinant product makes the agreement with CODATA
$11{,}000\times$ \textit{worse}, confirming that the integer Casimir
trace is the correct object, not the spectral determinant.

A systematic search over additive corrections to the spectral
determinant product finds the best candidates to be $+\pi/72$ (0.002\%
residual) and $+1/24$ (0.003\% residual), but neither is derivable from
first principles~\cite{phase2_kappa}. The quantity $\pi/72 =
\pi/(|\lambda_3| \cdot n_{\max}^2)$ could be a finite-size correction,
and $1/24$ appears in heat kernel coefficients, but both remain
\textit{ad hoc}. A broader search over simple arithmetic combinations of
spectral determinants and fibration data finds no exact bridge. This
strengthens the conclusion that the integer Casimir trace $B = 42$---not
the spectral determinant---is the correct object for the base invariant.


\subsection{Algebraic structure of $\alpha$}

The formula implies that $\alpha$ is algebraic over the field
$\mathbb{Q}(\pi)$, since $\zeta(2) = \pi^2/6$. That is,
$\alpha$ is a root of a polynomial whose coefficients are rational
functions of $\pi$ alone. If confirmed, this would constrain $\alpha$
far more tightly than the Standard Model currently does, and would
imply that $\alpha$ is transcendental (since $\pi$ is).


\subsection{$S^3$ specificity}\label{sec:s3_specificity}

\textit{A universal algebraic identity.}
For any round sphere $S^d$, define the \textit{formal} spectral moment
\begin{equation}\label{eq:B_formal}
  B_{\mathrm{formal}}(m) \;=\;
  \tfrac{1}{2}\sum_{k=1}^{m} g_k\,|\lambda_k|,
  \qquad
  N(m) \;=\; \sum_{k=1}^{m} g_k,
\end{equation}
where $\lambda_k = -k(k+d-1)$ and
$g_k = \binom{k+d}{d} - \binom{k+d-2}{d}$ are the eigenvalues and
degeneracies of the Laplace--Beltrami operator on $S^d$. At $m = 2$
these evaluate to $B_{\mathrm{formal}}(2) = \tfrac{1}{2}(d+1)d(d+4)$
and $N(2) = (d+1)(d+4)/2$, giving
\begin{equation}\label{eq:universal_identity}
  \frac{B_{\mathrm{formal}}(2)}{N(2)} \;=\; d
  \qquad\text{for all } d \geq 1.
\end{equation}
Setting $B_{\mathrm{formal}}(m)/N(m) = d$ yields the quadratic
$m^2 + dm - 2(d+2) = 0$, whose unique positive root is $m = 2$
regardless of~$d$. The dimension-matching condition is therefore a
universal property of eigenvalue moments on round spheres, not a
selection principle specific to~$S^3$.

\textit{Why the formula is specific to $S^3$.}
The quantity $B$ appearing in the formula (Sec.~\ref{sec:selection})
is \textit{not} $B_{\mathrm{formal}}$. It is the
degeneracy-weighted trace of the $SO(3)$ \textit{sub}-Casimir
$l(l+1)$ over the $SO(4) \to SO(3)$ branching of each $S^3$ shell:
\begin{equation}\label{eq:B_branch}
  B \;=\; \sum_{n=1}^{m}\sum_{l=0}^{n-1}(2l+1)\,l(l+1).
\end{equation}
For $S^3$, $B = B_{\mathrm{formal}}$ because the diagonal
$SO(3) \subset SO(4)$ embedding has index~1, giving the identity
$\langle C_{SO(3)}\rangle_n = n(n+2)/2 = |\lambda_n|/2$. For all
other spheres $S^d$ with $d \neq 3$, $B \neq B_{\mathrm{formal}}$
and $B/N = d$ has no solution at any integer~$m$.

Three independent properties of $S^3$ underlie this coincidence:
\begin{enumerate}
\item $SO(4) \cong (SU(2) \times SU(2))/\mathbb{Z}_2$ is a product
  group, yielding the clean Clebsch--Gordan branching
  $l = 0, \ldots, n{-}1$ within each shell. No analogous product
  structure exists for $SO(d{+}1)$ with $d \neq 3$.
\item $S^3 \cong SU(2)$ is the only sphere that is a Lie group,
  enabling the Peter--Weyl decomposition that makes $B$ computable
  as a representation-theoretic trace.
\item The embedding index of diagonal $SO(3) \subset SO(4)$ is~1.
  For the quaternionic Hopf fibration, the corresponding
  $SO(5) \subset SO(8)$ embedding through $Sp(2) \times Sp(1)$ has
  index ratio $5/14$, which would give $B/N = 5 \neq 7$ if used as
  the branching factor.
\end{enumerate}
The formula is not one instance of a family parametrized by $d$; it
exists only for~$S^3$.

\textit{Quaternionic and octonionic Hopf fibrations.}
Applying the combination rule $K = \pi(B + F - \Delta)$ formally to
all four Hopf fibrations
($S^0 \to S^1 \to S^1$, $S^1 \to S^3 \to S^2$,
$S^3 \to S^7 \to S^4$, $S^7 \to S^{15} \to S^8$) yields
$1/\alpha \approx 15.4$, $137.036$, $970.0$, and $7164.1$
respectively~\cite{phase6_hopf}. Only the complex Hopf value matches
a known coupling constant. The quaternionic value $K/\pi \approx 309$
satisfies $K_{\mathrm{quat}}/K_{\mathrm{em}} \approx 7.08 \approx
\dim(S^7)$, but the $1.1\%$ deviation from~7 and the absence of any
coupling at $\alpha_W \approx 1/29.5$ rule out a weak-interaction
interpretation. The representation-theoretic obstructions above
explain why: without the $SO(4)$ product structure, the
branching-based $B$ that makes the formula work has no natural
generalization.

\textit{Dynamical specificity: the Fock projection rigidity theorem.}
The representation-theoretic arguments above show that the
\textit{algebraic structure} of $B = 42$ is unique to $S^3$. An
independent \textit{dynamical} argument reaches the same conclusion
from the Fock projection itself, rather than from the $SO(4)$
branching combinatorics. The rigidity theorem (established in the
nuclear extension of the GeoVac framework) states that the
stereographic projection $p_0 = \sqrt{-2 E_n}$ maps a one-electron
central-field Hamiltonian onto the free Laplacian on $S^3$ if and
only if the spectrum $E_{nl}$ is independent of $l$ within each
shell~$n$. The Coulomb potential $-Z/r$ is the unique central
potential exhibiting this accidental degeneracy, by the $SO(4)$
symmetry generated by the Runge--Lenz vector. Any deformation
$V(r) = -Z/r + \delta V(r)$ with $\delta V \not\equiv 0$ lifts the
$l$-degeneracy and breaks the conformal equivalence between the
radial Schr\"odinger problem and the $S^3$ graph Laplacian.
The harmonic oscillator, Woods--Saxon, square well, and Yukawa
potentials all share the angular momentum algebra ($SO(3)$ Gaunt
selection rules) of the Coulomb problem, but none of them carries
the Fock projection because none has the $SO(4)$ accidental
degeneracy. The angular sparsity of the GeoVac
framework~\cite{paper22_sparsity} is universal across spherical
fermion systems; the $S^3$ conformal projection and the Hopf bundle
structure built upon it are Coulomb-specific.

The implication for the present conjecture is that any derivation of
$\alpha$ from spectral geometry must use the Coulomb-specific
features of $S^3$ --- the accidental degeneracy, the Runge--Lenz
vector, and the conformal weight assignments that the Fock projection
imposes --- not merely the $SO(3)$ angular momentum structure that
$S^3$ shares with other manifolds. As a numerical check on this
narrowing, the analog of $B = 42$ in the nuclear shell model
($j$-coupled $(2j+1)\,j(j+1)$ trace at the same truncation
$n_{\max} = 3$) evaluates to $103.5$ and shows no coincidence with
any quantity in $K = \pi(B + F - \Delta)$ at the $p < 10^{-3}$
level~\cite{track_nj_alpha_memo}. This is consistent with the
structural argument: nuclear shell model angular momentum lives on
$SO(3)$ with broken $SO(4)$, lacks the Fock projection, and
therefore cannot be expected to produce the same combinatorial
constants as the Coulomb-specific calculation.

The Bargmann--Segal lattice for the harmonic oscillator (Paper~24,
\cite{paper24_bargmann}) sharpens this further: the harmonic
oscillator's natural discretization on the Hardy space of $S^5$ is
demonstrably $\pi$-free in exact rational arithmetic, with a linear
projection $E_N = \hbar\omega(N + 3/2)$ that requires no calibration
exchange constant. The harmonic oscillator's complex / first-order
geometry produces no spectral zeta corrections at all, so no
$\pi$-class transcendental enters its graph-to-physics map. The
appearance of $\pi$ in $K = \pi(B + F - \Delta)$ is therefore not a
generic feature of quantum discretization but a specific consequence
of the Coulomb potential's $S^3$ Riemannian (second-order) character;
the harmonic oscillator's $S^5$ complex (first-order) character has
no analog. Any future derivation of the combination rule must rely on
the Riemannian/$SO(4)$ structure that distinguishes Coulomb from
every other central potential.


\subsection{Transition operators and the Hopf geometry}

The discrete graph Laplacian for hydrogen has two types of lattice
transitions~\cite{phase2_kappa}: $T_\pm$ (changing $n$ by $\pm 1$,
preserving $l$ and $m$) and $L_\pm$ (changing $m$ by $\pm 1$, preserving
$n$ and $l$). We observe that these correspond naturally to the Hopf
fibration:
\begin{itemize}
\item $L_\pm$ is motion along the Hopf fiber $S^1$. The magnetic quantum
  number $m$ is the $U(1)$ charge (eigenvalue of $J_z$); incrementing
  $m$ rotates around the fiber circle.
\item $T_\pm$ is radial motion on $S^3$, perpendicular to the fiber.
  Changing $n$ moves between eigenspaces of $\Delta_{S^3}$; in the Fock
  stereographic picture, this changes the ``latitude'' on~$S^3$.
\end{itemize}
The angular momentum $l$ is conserved by both transitions---it labels
the $SO(3)$ representation within each $SO(4)$ shell but does not
contribute an independent transition type. The base $S^2$ constrains
state labeling (which $l$, $m$ values exist) but does not generate
lattice transitions. The Fock stereographic projection collapses the
2-dimensional base directions into a single radial variable (the
principal quantum number $n$), explaining why $d_{\max} = 2 \times 2 = 4$
(two motion types $\times$ two directions) rather than~6.


\subsection{Second selection principle}\label{sec:second_selection}

The topological maximum degree $d_{\max} = 4$ gives an asymptotic
bipartite spectral radius bound of $2 d_{\max} = 8$ for the graph
Laplacian~\cite{phase1_kappa}. The $S^3$ Laplace--Beltrami eigenvalue
$|\lambda_n| = n^2 - 1$ equals this bound uniquely at $n = 3$:
\begin{equation}\label{eq:second_selection}
  n^2 - 1 = 2\,d_{\max} \quad\Longrightarrow\quad n_{\max} = 3.
\end{equation}
This provides an independent selection of $n_{\max} = 3$, from the
discrete--continuous compatibility condition rather than from the Casimir
selection $B/N = \dim(S^3)$.

We note a subtlety: $d_{\max} = 4$ is the topological maximum degree for
interior nodes of the lattice class (first realized at $n_{\max} = 4$),
not the realized maximum at $n_{\max} = 3$ (which is~$3$, since all 14
nodes are boundary nodes)~\cite{phase2_kappa}. The selection principle
should be read as: the $S^3$ eigenvalue at $n_{\max}$ matches the
\textit{asymptotic} spectral radius bound of the lattice topology.

The connection to $\kappa$ is immediate: if
$\kappa = -E_1/|\lambda_{n_{\max}}| = -1/(2(n^2-1))$, then the Hopf
selection $n_{\max} = 3$ gives $\kappa = -1/16$, the kinetic scale
factor of the GeoVac program~\cite{paper7}.

\textit{Status:} this is a structural observation, not a derivation. The
two selection principles ($B/N = 3$ and $2d_{\max} = n^2 - 1$) are
algebraically independent; whether they share a common origin in the
Hopf fibration geometry is an open question.


\subsection{Open questions}

\begin{enumerate}
\item \textit{Derive the combination rule} from a path integral or
  spectral determinant identity on the Hopf bundle. This is the
  critical gap (Link~3 in Table~\ref{tab:chain}).

\item \textit{Connect the $\mathbb{Z}_3$ circulant} to the
  differential geometry of the Hopf connection. The $SU(2)$ structure
  constants share the cyclic symmetry; can the coupling strength
  $K/3$ be derived from the connection curvature?

\item \textit{Understand the residual $8.8 \times 10^{-8}$.} Higher-order
  spectral invariants (e.g., the $\eta$-invariant of $S^3$, which
  vanishes by symmetry), gravitational corrections, or weak-mixing
  contributions could account for the discrepancy. One-loop QED
  running of the formula's $\alpha$ from the electron mass to $1$~TeV
  shows that the formula's value corresponds to the Thomson limit
  ($q^2 \to 0$), matching CODATA most closely at $\mu \approx m_e$.
  The residual is intrinsic to the formula, not explained by
  renormalization group running.

\item \textit{The other cubic roots.} The two non-physical roots of
  Eq.~(\ref{eq:cubic}) satisfy $\alpha \approx \pm 11.7$,
  corresponding to $1/\alpha \approx \pm 0.085$. A systematic
  comparison of all natural transformations of these roots (including
  $r$, $1/r$, $r^2$, $\sin^2(\arctan r)$, etc.) against known
  Standard Model parameters ($\sin^2\theta_W$, $\alpha_s$, Cabibbo
  angle, Yukawa couplings, mass ratios) finds no match at the $1\%$
  level. The other roots do not appear to encode additional coupling
  constants.

\item \textit{Common origin of the two selection principles.} The
  second selection principle ($2d_{\max} = n^2 - 1$ at $n = 3$) and
  the Casimir selection ($B/N = 3$ at $n = 3$) are algebraically
  independent. Whether they share a common origin in the Hopf
  fibration geometry is open.

\item \textit{Circulant phase and the Hopf connection.} The
  Hermiticity of the circulant coupling and its $\theta \approx
  3\pi/2$ phase at the physical root may encode the $U(1)$ gauge
  structure. A derivation connecting the circulant phase to the Hopf
  connection 1-form would ground Link~4 of
  Table~\ref{tab:chain}.
\end{enumerate}


%======================================================================
\section{Conclusion}
%======================================================================

The fine structure constant satisfies the cubic equation
$\alpha^3 - K\alpha + 1 = 0$, where
$K = \pi(42 + \pi^2/6 - 1/40)$ is constructed from three spectral
invariants of the Hopf fibration. The selection principle
$B/N = \dim(S^3)$ is proven algebraically to select $n_{\max} = 3$
uniquely, via the closed-form ratio $B/N = 3(m+2)(m-1)/10$; this
result is specific to~$S^3$: a formal spectral moment
$B_{\mathrm{formal}}/N = d$ holds universally at $m = 2$ for all
round spheres (Sec.~\ref{sec:s3_specificity}), but the
branching-based $B$ that enters the formula coincides with
$B_{\mathrm{formal}}$ only for $d = 3$, due to the unit embedding
index of $SO(3) \subset SO(4)$. The quaternionic and octonionic Hopf
fibrations yield $1/\alpha \approx 970$ and $7164$ respectively,
matching no known coupling constants. The formula contains no fitted parameters and achieves
$8.8 \times 10^{-8}$ relative agreement with experiment. A
combinatorial search over $1.92 \times 10^9$ formulas yields a
$p$-value of $5.2 \times 10^{-9}$, establishing that this precision
is very unlikely to be accidental. The cubic form is the
characteristic polynomial of a traceless $\mathbb{Z}_3$-symmetric
circulant matrix, providing structural justification for the
self-consistency equation.

The circulant coupling is necessarily Hermitian ($b$ and $c$ are
complex conjugates), with the physical root at phase
$\theta \approx 3\pi/2$, consistent with $U(1)$ gauge structure. A
second selection principle---the bipartite spectral radius bound
$2d_{\max} = 8$ matching $|\lambda_3| = n^2 - 1 = 8$---independently
selects $n_{\max} = 3$ and connects to the kinetic scale factor
$\kappa = -1/16$.

The combination rule $K = \pi(B + F - \Delta)$ remains conjectural.
A systematic investigation of spectral determinants, analytic torsion,
heat kernels, and index-theoretic invariants finds no smooth
spectral-geometric derivation; the rule mixes discrete
representation-theoretic data ($B = 42$) with continuous spectral
invariants ($F = \zeta(2)$) in a way that has no known precedent.
The formula has the character of a remarkable empirical observation
with structural support---the spectral ingredients are natural, the
cubic form is natural, the selection principle is proven, but their
assembly into $K$ awaits a first-principles derivation.


\begin{acknowledgments}
This work supersedes an earlier ``symplectic impedance''
approach~\cite{paper2_old} by the same author. The evolution from
fitted to parameter-free is documented for intellectual transparency.
The four-phase computational audit (arithmetic verification,
combinatorial $p$-value analysis, cubic structure investigation, and
derivation chain assessment) that validated the formula and identified
the circulant structure is available as supplementary
material~\cite{phase2_audit}. A systematic investigation of spectral
determinants, analytic torsion, heat kernel expansions, and
index-theoretic invariants of the Hopf bundle components, documented
in the project repository, established that the combination rule
(Link~3) lies outside the scope of standard smooth spectral geometry.
A subsequent three-phase investigation of the kinetic scale factor
$\kappa = -1/16$ established the transition operator--Hopf
correspondence, a second selection principle from the bipartite
spectral radius bound, and the forced Hermiticity of the circulant
coupling~\cite{phase1_kappa,phase2_kappa,phase3_audit}.
A further investigation applied the formula's recipe to all four Hopf
fibrations, discovered the universal algebraic identity
$B_{\mathrm{formal}}/N = d$, and confirmed the $S^3$ specificity of
the branching-based selection
principle~\cite{phase6_hopf}.
Computational implementation and documentation drafting were performed
with the assistance of large language models (Anthropic Claude) under
the author's scientific direction. All results were validated against
analytical benchmarks.
\end{acknowledgments}

\begin{thebibliography}{20}

\bibitem{feynman1985}
R.~P. Feynman, \textit{QED: The Strange Theory of Light and Matter}
(Princeton University Press, 1985).

\bibitem{eddington1935}
A.~S. Eddington, \textit{New Pathways in Science}
(Cambridge University Press, 1935).

\bibitem{barrow2002}
J.~D. Barrow, \textit{The Constants of Nature}
(Vintage Books, 2002).

\bibitem{paper7}
J.~Loutey, ``The Dimensionless Vacuum: $S^3$ Conformal Geometry and
the Schr\"odinger Equation,'' GeoVac Paper~7 (2026).

\bibitem{paper22_sparsity}
J.~Loutey, ``Potential-Independent Angular Sparsity in Spherical
Fermion Systems,'' GeoVac Paper~22 (2026).

\bibitem{paper24_bargmann}
J.~Loutey, ``The Bargmann--Segal Lattice: $\pi$-Free Discretization
of the Harmonic Oscillator on $S^5$,'' GeoVac Paper~24 (2026).

\bibitem{track_nj_alpha_memo}
J.~Loutey, ``Track NJ: Fine Structure Constant and the Nuclear
Extension --- Theory Memo,'' GeoVac internal memo (2026). Available
at \texttt{docs/track\_nj\_alpha\_memo.md} in the project repository.

\bibitem{hopf1931}
H.~Hopf, ``\"Uber die Abbildungen der dreidimensionalen Sph\"are auf
die Kugelfl\"ache,'' \textit{Math.\ Ann.}\ \textbf{104}, 637 (1931).

\bibitem{urbantke2003}
H.~K. Urbantke, ``The Hopf fibration---seven times in physics,''
\textit{J.\ Geom.\ Phys.}\ \textbf{46}, 125 (2003).

\bibitem{fock1935}
V.~Fock, ``Zur Theorie des Wasserstoffatoms,''
\textit{Z.\ Phys.}\ \textbf{98}, 145 (1935).

\bibitem{paper2_old}
J.~Loutey, ``The Fine Structure Constant as Geometric Impedance: A
Symplectic Framework,'' GeoVac Paper~2, v1 (2026). [Superseded by
the present work.]

\bibitem{wyler1969}
A.~Wyler, ``L'espace sym\'etrique du groupe des \'equations de
Maxwell,'' \textit{C.\ R.\ Acad.\ Sci.\ Paris}\ \textbf{269A}, 743
(1969).

\bibitem{robertson1971}
B.~Robertson, ``Wyler's expression for the fine-structure constant,''
\textit{Phys.\ Rev.\ Lett.}\ \textbf{27}, 1545 (1971).

\bibitem{phase2_audit}
J.~Loutey, ``Paper~2 Computational Audit: Phases 1--4,'' GeoVac
supplementary material (2026). Available at
\texttt{debug/alpha\_audit/} in the project repository.

\bibitem{phase1_kappa}
J.~Loutey, ``$\kappa = -1/16$ Investigation: Phase~1,'' GeoVac
supplementary material (2026). Available at
\texttt{debug/kappa\_investigation/} in the project repository.

\bibitem{phase2_kappa}
J.~Loutey, ``Spectral Determinants \& Second Selection Principle:
Phase~2,'' GeoVac supplementary material (2026). Available at
\texttt{debug/kappa\_investigation/phase2/} in the project repository.

\bibitem{phase3_audit}
J.~Loutey, ``Circulant Structure of the Cubic: Phase~3,'' GeoVac
supplementary material (2026). Available at
\texttt{debug/kappa\_investigation/phase3/} in the project repository.

\bibitem{phase6_hopf}
J.~Loutey, ``Quaternionic Hopf Fibration \& Universal Algebraic
Identity: Phase~6,'' GeoVac supplementary material (2026). Available
at \texttt{debug/kappa\_investigation/phase6/} in the project
repository.

\end{thebibliography}

\end{document}
