\documentclass[aps,pra,twocolumn,superscriptaddress,longbibliography]{revtex4-2}

\usepackage{amsmath,amssymb,amsthm,graphicx,xcolor,bm,braket,dcolumn,booktabs}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{observation}{Observation}

\begin{document}

\title{Toward PK-Free Molecular Hamiltonians:\\
Two-Center Sturmian Integrals and Coupled Composition}
\thanks{Paper 19 in the Geometric Vacuum series}

\author{J.~Loutey}
\affiliation{Independent Researcher, Kent, Washington}

\date{April 6, 2026}

%% ========================================================================
%% ABSTRACT
%% ========================================================================

\begin{abstract}
The composed natural geometry framework (Paper~17) constructs
molecular Hamiltonians by partitioning electrons into single-center
blocks and coupling them via Phillips--Kleinman (PK) pseudopotentials.
This produces structurally sparse qubit Hamiltonians---$O(Q^{2.5})$
Pauli scaling, 51--1{,}712$\times$ fewer terms than Gaussian
baselines (Paper~14)---but PK limits accuracy to 5.3--26\%
equilibrium bond length error.  PK cannot be improved: six
modification attempts have failed (v2.0.6--23), and the overcounting
diverges at higher angular momentum.

We report a negative result (Track~CB, v2.0.37): replacing PK with
explicit cross-block electron-electron integrals \emph{without}
corresponding cross-center nuclear attraction integrals produces an
unbalanced Hamiltonian (29\% error, worse than PK's 15\%).  The root
cause is identified: two-center one-body integrals
$\langle \psi_{nlm}^A | V_B | \psi_{n'l'm'}^A \rangle$, where an
orbital on center~$A$ feels the nuclear potential of center~$B$, are
required for energy balance but absent from the single-center
framework.

We observe that these missing integrals are precisely the
Shibuya--Wulfman integrals of the Coulomb Sturmian
literature~\cite{shibuya1965,avery2004,avery2012}, which are computed
via Fock's momentum-space projection onto $S^3$---the same conformal
map that underlies the GeoVac framework (Paper~7).  The mathematical
foundation is therefore already in place.  We review the convergence
properties of the Shibuya--Wulfman expansion, identify the Coulomb
resolution technique~\cite{hoggan2011} as a potentially faster
alternative, and outline the ``coupled composition'' architecture
that would result from incorporating two-center integrals.  If the
angular expansion converges in few terms at molecular bond lengths,
the coupled Hamiltonian would be PK-free, structurally sparse, and
significantly more accurate than the current composed framework.
This paper presents the balanced coupled architecture, documents its mathematical foundations, and reports computational benchmarks across three molecules (LiH, BeH$_2$, H$_2$O).

We report computational results from the first three phases.  The
convergence concern is resolved: the multipole expansion of the
cross-center potential terminates exactly at $L_{\max} = 2l_{\max}$
by Gaunt selection rules (33 one-body terms at $n_{\max}=2$).  The
balanced Hamiltonian has 878 Pauli terms (Conjecture~1 confirmed).
Four-electron FCI gives $R_{\rm eq}$ error of 7.0\% and
$D_e = 0.037$~Ha---the only bound configuration among all four
coupling schemes tested (Conjecture~2 not confirmed in strict sense,
but the comparison crosses FCI regimes).  At $n_{\max} = 3$ ($Q = 84$),
single-point FCI gives 0.20\% energy error (down from 1.8\%) with
analytical integrals (incomplete gamma functions, machine precision),
confirming convergence.  The $R_{\rm eq}$ drift is structural to the
block decomposition ($+0.053$~bohr per $n_{\max}$ step, $3\times$
smaller than PK's $+0.15$--$0.22$~bohr/$l_{\max}$), not numerical.
\end{abstract}

\maketitle

%% ========================================================================
\section{Introduction: The PK Problem}
\label{sec:intro}
%% ========================================================================

The composed natural geometry framework~\cite{loutey_paper17}
partitions electrons into groups---core, bond pairs, lone pairs---each
inhabiting its own natural coordinate system.  Inter-group coupling is
approximated by the Phillips--Kleinman (PK) pseudopotential, a
one-body operator that provides core-valence orthogonality and an
effective repulsive barrier.

PK is the framework's accuracy bottleneck.  At $l_{\max} = 2$ (the
optimal operating point), LiH achieves 5.3\% $R_{\rm eq}$ error;
BeH$_2$ gives 11.7\%; H$_2$O gives 26\%.  These errors are
structural, not numerical: the $l_{\max}$ divergence
(+0.15--0.22~bohr per additional angular channel) is confirmed to
originate in PK overcounting, not in the adiabatic approximation
(Track~BQ, v2.0.32).  Six attempts to modify PK have failed
(projector, spectral, self-consistent, $R$-dependent, $l$-dependent,
$l$-dependent on 2D solver), and the ab initio $R_{\rm ref}$
derivation failed because the relevant scale (${\sim}3$~bohr) is
molecular, not atomic (Track~AD, v2.0.18).

At the same time, PK is essential for the composed framework's
sparsity: it makes the electron repulsion integral (ERI) tensor
block-diagonal, yielding $O(Q^{2.5})$ Pauli scaling
(Paper~14)~\cite{loutey_paper14}.  Without PK, the block
decomposition has no coupling at all.

The question motivating this paper is: \emph{can PK be replaced by
explicit inter-block integrals that preserve structural sparsity while
eliminating the accuracy ceiling?}


%% ========================================================================
\section{The Negative Result: Coupled Composition Without $V_{ne}$}
\label{sec:negative}
%% ========================================================================

Track~CB (v2.0.37) tested the simplest version of this idea: remove
PK from the composed LiH Hamiltonian and add explicit cross-block
two-electron integrals $\langle pq | rs \rangle$ where $p, q$ belong
to one block and $r, s$ to another.

The cross-block ERIs were computed using existing infrastructure
(\texttt{cross\_block\_mp2.py}, originally built for Track~BX-3b).
Key census results for LiH at $n_{\max} = 2$, $Q = 30$:

\begin{table}[h]
\caption{Cross-block ERI census for LiH at $n_{\max} = 2$.}
\label{tab:census}
\begin{ruledtabular}
\begin{tabular}{lrr}
Metric & Within-block & Cross-block \\
\hline
Nonzero ERIs & 195 & 130 \\
Max $|\langle pq|rs\rangle|$ (Ha) & --- & 0.891 \\
Mean $|\langle pq|rs\rangle|$ (Ha) & --- & 0.142 \\
\end{tabular}
\end{ruledtabular}
\end{table}

The cross-block/within-block ERI ratio is 2/3, consistent with the
selection-rule counting bound of $\le 2\times$ from Paper~14,
Sec.~V.E.  Gaunt selection rules ($|\Delta l| \le 1$,
$|\Delta m| \le 1$) are preserved across block boundaries.

The resulting qubit Hamiltonian has 854 Pauli terms (2.56$\times$ the
composed value of 334) and 1-norm 85.7~Ha (2.30$\times$ the composed
value of 37.3~Ha).  However, the FCI energy tells the real story:

\begin{table}[h]
\caption{FCI accuracy for LiH at $n_{\max} = 2$ under different
coupling schemes.  Exact: $-8.071$~Ha.}
\label{tab:fci}
\begin{ruledtabular}
\begin{tabular}{lrr}
Configuration & $E_{\mathrm{FCI}}$ (Ha) & Error \\
\hline
No PK, no cross-block (decoupled) & $-7.195$ & 10.9\% \\
Composed (PK, no cross-block) & $-6.863$ & 15.0\% \\
Coupled (no PK, with cross-block $V_{ee}$) & $-5.734$ & 29.0\% \\
\end{tabular}
\end{ruledtabular}
\end{table}

The coupled Hamiltonian is \emph{worse} than both alternatives.  The
root cause is clear: cross-block ERIs add inter-group electron-electron
\emph{repulsion} without the balancing cross-center electron-nucleus
\emph{attraction}.  The Hamiltonian is energetically unbalanced.

\begin{observation}
\label{obs:decoupled}
The decoupled configuration (no PK, no cross-block interactions)
gives 10.9\% error---better than PK's 15.0\%.  This implies that
PK overcorrects at $n_{\max} = 2$: the blocks are more accurate
when left independent than when coupled via PK.
\end{observation}

This observation is consistent with the $l_{\max}$ divergence
diagnostic: PK's repulsive barrier systematically overcounts the
core-valence interaction energy, and the overcounting worsens with
basis size.


%% ========================================================================
\section{The Missing Piece: Two-Center Nuclear Attraction}
\label{sec:twocenter}
%% ========================================================================

The coupled Hamiltonian of Sec.~\ref{sec:negative} is incomplete.
A physically balanced molecular Hamiltonian requires, for each
electron:
\begin{enumerate}
\item Kinetic energy (within-block, already present).
\item Same-center nuclear attraction $V_A = -Z_A / r_A$ (within-block, already present).
\item Cross-center nuclear attraction $V_B = -Z_B / r_B$, where the
  electron on center~$A$ feels the potential of nucleus~$B$ (missing).
\item Electron-electron repulsion, both within-block (present) and
  cross-block (added in Track~CB).
\end{enumerate}

Item~3 requires two-center one-body integrals of the form
\begin{equation}
\label{eq:vne_cross}
I_{nlm, n'l'm'}^{AB} = \left\langle \psi_{nlm}^A \left|
  \frac{-Z_B}{|\mathbf{r} - \mathbf{R}_B|} \right|
  \psi_{n'l'm'}^A \right\rangle
\end{equation}
where $\psi_{nlm}^A$ is a hydrogenic orbital centered on nucleus~$A$,
and the potential is from nucleus~$B$ at position~$\mathbf{R}_B$.
These integrals are standard in the Slater-type orbital (STO)
literature but have never been computed in the GeoVac framework,
which has until now been strictly single-center at each level.


%% ========================================================================
\section{Connection to Coulomb Sturmian Theory}
\label{sec:sturmian}
%% ========================================================================

GeoVac's hydrogenic orbitals are Coulomb Sturmians with the
identification $k = Z/n$, where $k$ is the Sturmian exponent.
This is not merely a notational correspondence: the entire GeoVac
framework---the graph Laplacian on $S^3$ (Paper~7), the Fock
projection, the angular momentum selection rules---is built on the
same mathematical structure that the Avery group has developed for
molecular Coulomb Sturmian calculations since the
1990s~\cite{avery2000,avery2004,avery2012,avery2014}.

\subsection{Shibuya--Wulfman integrals}

When a Coulomb Sturmian centered on $A$ is expanded in the basis
centered on $B$, the expansion coefficients are the Shibuya--Wulfman
integrals~\cite{shibuya1965}:
\begin{equation}
\label{eq:sw}
S_{\tau', \tau} = \int d^3\mathbf{r}\; \chi_{\tau'}^*(\mathbf{r} -
\mathbf{R}_B)\, \frac{k}{r_A}\, \chi_\tau(\mathbf{r} - \mathbf{R}_A)
\end{equation}
where $\chi_\tau$ denotes a Coulomb Sturmian with quantum numbers
$\tau = (n, l, m)$, and the weighting $k/r_A$ arises from the
potential-weighted orthogonality of the Sturmian basis.

In Fock's momentum-space representation, Coulomb Sturmians map to
hyperspherical harmonics on $S^3$, and Shibuya--Wulfman integrals
become overlap integrals of translated hyperspherical harmonics.
The translation is parameterized by
\begin{equation}
S \equiv k \cdot R_{AB}
\end{equation}
where $R_{AB} = |\mathbf{R}_A - \mathbf{R}_B|$ is the internuclear
distance and $k$ is the common Sturmian exponent.

The nuclear attraction integral of Eq.~(\ref{eq:vne_cross}) is
closely related to the Shibuya--Wulfman integral: both involve a
Coulomb potential centered on a different nucleus acting on an orbital.
Koga and Matsuhashi~\cite{koga1987} derived sum rules for nuclear
attraction integrals over hydrogenic orbitals that express them as
finite sums over Clebsch--Gordan coefficients---the same angular
momentum algebra that generates Gaunt integrals in the GeoVac
framework.

\emph{Heterogeneous exponents.}  The standard Shibuya--Wulfman
formalism assumes a common Sturmian exponent~$k$ across all centers.
GeoVac's composed blocks use different effective charges
$Z_{\mathrm{eff}}$ per block, giving different exponents
$k_b = Z_{\mathrm{eff},b}/n$ for each block~$b$.  The generalized
overlap integrals between Sturmians of different exponents exist in
the literature---Koga and Matsuhashi~\cite{koga1987} treat this
case explicitly---but the convergence properties may differ from the
common-$k$ case.  Any implementation must use these generalized
integrals, and the convergence diagnostic (Sec.~\ref{sec:path})
must be performed with the actual heterogeneous exponents of the
LiH block decomposition, not with a uniform~$k$.

\subsection{The convergence challenge}

The Shibuya--Wulfman expansion has a well-documented convergence
limitation.  When a Sturmian on center~$A$ is expanded in the
angular basis of center~$B$, the expansion involves hyperspherical
harmonics of increasing angular momentum~$L$.  The rate of convergence
is controlled by the parameter $S = k \cdot R_{AB}$.

For $S \ll 1$ (nuclei close together relative to the orbital scale),
convergence is rapid.  For $S \gtrsim 3$ (typical molecular bond
lengths), convergence is slow, requiring many angular terms.  The
Avery group explicitly notes this: the expansion ``is very slowly
convergent if $S$ is large''~\cite{avery2012}.

For LiH at equilibrium ($R_{AB} \approx 3$~bohr), with $k \approx 1$
for the valence orbitals, $S \approx 3$.  This places the system
squarely in the slow-convergence regime.  Each additional angular
momentum channel in the expansion adds orbitals and therefore Pauli
terms to the qubit Hamiltonian.  If $L_{\max} = 5$--10 is required
for convergence, the Pauli count could approach the full Level~4N
encoding (${\sim}3{,}288$ terms), defeating the purpose of the block
decomposition.

\subsection{Resolution: multipole expansion termination}
\label{sec:multipole_resolution}

The convergence concern of the preceding subsection applies to the
Shibuya--Wulfman \emph{basis} expansion: expanding an orbital
centered on~$A$ in the complete Sturmian basis of center~$B$, which
requires summing over all angular momenta~$L$.  The cross-center
nuclear attraction integral of Eq.~(\ref{eq:vne_cross}) uses a
different expansion: the standard multipole expansion of
$1/|\mathbf{r}-\mathbf{R}_B|$ in Legendre polynomials $P_L(\cos\theta)$.

For this expansion, the angular integral involves
\begin{equation}
\int Y_{l_1 m}^*(\hat{r})\, P_L(\cos\theta)\, Y_{l_2 m}(\hat{r})\, d\Omega\,,
\end{equation}
which is nonzero only when $|l_1 - l_2| \le L \le l_1 + l_2$ and
$l_1 + L + l_2$ is even.  For $n_{\max} = 2$ ($l_{\max} = 1$), the
maximum~$L$ needed is~2 ($p$--$p$ pairs); for $n_{\max} = 3$
($l_{\max} = 2$), $L_{\max} = 4$.  The expansion terminates exactly
at $L_{\max} = 2 l_{\max}$---no truncation error.

Furthermore, $m_1 = m_2$ is required: the cross-center potential is
diagonal in the magnetic quantum number when the internuclear axis is
along~$z$.  Combined with the Gaunt selection rules, this means the
cross-center $V_{ne}$ adds only 33 new one-body matrix elements to
$h_1$ for LiH at $n_{\max} = 2$.  These are essentially free in
computational cost compared to the two-body integrals.

The original grid-based radial integrals (trapezoid quadrature,
$O(1/n_{\mathrm{grid}})$ convergence) achieved 0.18\% accuracy at
$n_{\mathrm{grid}} = 4000$ for $Z = 1$ orbitals, and $9 \times 10^{-8}$
for $Z = 3$.  The radial split integrals (inner and outer regions
separated at $R_{AB}$) are integrals of polynomial times exponential:
each $R_{nl}(r)$ contributes a polynomial in $r$ times
$\exp(-Zr/n)$.  The product $R_{nl} R_{n'l'} r^p$ is a finite sum of
terms $c_j r^j \exp(-\alpha r)$ where $\alpha = Z(1/n + 1/n')$.
Each split integral evaluates exactly via the regularized incomplete
gamma function (\texttt{scipy.special.gammainc}/\texttt{gammaincc}).
This replaces the $O(1/n_{\mathrm{grid}})$ trapezoid quadrature with
machine-precision evaluation---an instance of the algebraicization
program (Paper~18, Sec.~XII).

\subsection{The Coulomb resolution alternative}

A potentially more efficient route was developed by Hoggan and
collaborators~\cite{hoggan2011}.  The ``Coulomb resolution'' technique
decomposes multi-center integrals over exponential-type orbitals into
sums of one-electron overlap-like products, each involving orbitals on
at most two centers.  Crucially, these two-center integrals are
separable in prolate spheroidal coordinates---the same coordinate
system used at Level~2 of the GeoVac hierarchy (Paper~11).

The Coulomb resolution sidesteps the slowly convergent angular
expansion of Shibuya--Wulfman by working directly in the two-center
coordinate system where the integrals are most naturally expressed.
GeoVac already possesses prolate spheroidal infrastructure from
Paper~11, including the Neumann expansion machinery for $V_{ee}$
(Paper~12).  The question is whether this infrastructure can be
extended to compute the one-body cross-center integrals of
Eq.~(\ref{eq:vne_cross}).


%% ========================================================================
\section{The Coupled Composition Architecture}
\label{sec:architecture}
%% ========================================================================

If two-center integrals can be computed efficiently, the resulting
``coupled composition'' Hamiltonian would have the following structure
for a molecule with $B$ blocks:

\begin{equation}
\label{eq:coupled}
H = \sum_{b=1}^{B} H_b^{(1)} + \sum_{b=1}^{B} V_{ee}^{(b)} +
\sum_{b < b'} V_{ee}^{(b,b')} + \sum_{b=1}^{B} \sum_{a \ne a_b}
V_{ne}^{(b,a)}
\end{equation}

where $H_b^{(1)}$ is the one-body Hamiltonian within block~$b$
(kinetic + same-center nuclear attraction), $V_{ee}^{(b)}$ is the
within-block ERI, $V_{ee}^{(b,b')}$ is the cross-block ERI, and
$V_{ne}^{(b,a)}$ is the cross-center nuclear attraction (electron in
block~$b$ feeling nucleus~$a$ from a different center).

Compared to the current composed Hamiltonian:
\begin{itemize}
\item PK is \emph{eliminated entirely}.  Core-valence orthogonality is
  enforced by the occupation number representation in second
  quantization, not by a pseudopotential.
\item Cross-block ERIs are included, subject to Gaunt selection rules.
  Track~CB established that these add ${\sim}2/3$ of the within-block
  ERI count (130 vs.~195 for LiH at $n_{\max} = 2$).
\item Cross-center nuclear attraction is included via two-center
  integrals.  The number of one-body terms is bounded by the number
  of orbital pairs times the number of off-center nuclei.
\end{itemize}

\begin{conjecture}
\label{conj:sparsity}
The Gaunt selection rules that enforce ERI sparsity within each block
also constrain the cross-block ERIs and the angular expansion of the
cross-center nuclear attraction.  If the two-center integral expansion
converges in $L_{\max} \le 3$ angular terms at molecular bond lengths,
the coupled Hamiltonian should have $\lesssim 1{,}500$ Pauli terms for
LiH at $n_{\max} = 2$---roughly $4.5\times$ the current composed
count of 334, but well below the full Level~4N count of 3{,}288 and
potentially below the Gaussian STO-3G count of 907 after the PK
one-body terms are removed.
\end{conjecture}

This conjecture is falsifiable by computing the two-center integrals
and performing the Jordan--Wigner transformation.

\begin{conjecture}
\label{conj:accuracy}
With a balanced Hamiltonian (all one-body and two-body terms present,
no PK), the FCI accuracy on the coupled Hamiltonian should be
significantly better than the composed framework's 5.3\% $R_{\rm eq}$
error, bounded below by the hydrogenic FCI accuracy floor
(${\sim}0.35\%$ for He at $n_{\max} = 5$, Paper~FCI-A).
\end{conjecture}


%% ========================================================================
\section{Relationship to Existing GeoVac Infrastructure}
\label{sec:infrastructure}
%% ========================================================================

The coupled composition program connects to multiple existing
components:

\emph{Paper~7 (Dimensionless Vacuum):} The $S^3$ conformal projection
that defines GeoVac's graph Laplacian is identical to Fock's
1935 momentum-space mapping~\cite{fock1935}, which is the foundation
of Shibuya--Wulfman theory.  The 18 symbolic proofs of Paper~7
validate the same mathematical structure that generates the
Shibuya--Wulfman integrals.

\emph{Paper~11 (Prolate Spheroidal):} The prolate spheroidal
coordinate system and Neumann expansion machinery are directly
applicable to the Coulomb resolution technique for two-center
integrals.

\emph{Paper~12 (Algebraic $V_{ee}$):} The Neumann expansion of
$1/r_{12}$ in prolate spheroidal coordinates demonstrates that
multi-center Coulomb integrals can be decomposed into algebraically
evaluable components via angular momentum recurrence.

\emph{Paper~14 (Qubit Encoding):} Section~V.E already bounds
cross-block ERI counts at $\le 2\times$ within-block; Track~CB's
empirical ratio of 2/3 is tighter.  The coupled Hamiltonian would
feed directly into the Jordan--Wigner encoding pipeline.

\emph{Paper~16 (Chemical Periodicity):} The $S_N$ representation
theory and atomic classifier determine the block decomposition.
Coupled composition uses the same block structure---it changes how
blocks are coupled, not how they are defined.

\emph{Paper~18 (Exchange Constants):} PK is classified as a
``calibration exchange constant''---a transcendental quantity that
enters when projecting between the graph and continuous coordinates.
If coupled composition eliminates PK, it removes one exchange constant
from the framework, consistent with the algebraicization program
(Sec.~XII of Paper~18).

\emph{Track~BX-3b (Cross-Block MP2):} The \texttt{cross\_block\_mp2.py}
module already computes cross-block ERIs for LiH.  This infrastructure
would be reused for the cross-block ERI component of the coupled
Hamiltonian.


%% ========================================================================
\section{Computational Results}
\label{sec:results}
%% ========================================================================

We report results from Phases~1--3 of the research path outlined in
Sec.~\ref{sec:path}.

\subsection{Quantum resource comparison}

Table~\ref{tab:resources} compares the qubit Hamiltonian metrics for
the four coupling schemes at LiH $n_{\max} = 2$, $Q = 30$.

\begin{table}[h]
\caption{Qubit Hamiltonian resources for LiH at $n_{\max} = 2$,
$Q = 30$.  All values from Jordan--Wigner encoding.  The Gaussian
STO-3G baseline ($Q = 12$) is included for reference.}
\label{tab:resources}
\begin{ruledtabular}
\begin{tabular}{lddd}
Configuration & \multicolumn{1}{c}{Pauli} & \multicolumn{1}{c}{1-norm (Ha)} & \multicolumn{1}{c}{QWC} \\
\hline
Composed (PK)      & 334  & 37.3 & 21  \\
Balanced (CD)      & 878  & 74.1 & 87  \\
Coupled (CB)       & 854  & 85.7 & 88  \\
Gaussian STO-3G    & 907  & 34.3 & 273 \\
\end{tabular}
\end{ruledtabular}
\end{table}

The balanced Hamiltonian has 878 Pauli terms, confirming
Conjecture~\ref{conj:sparsity}: the count is well below the
conjectured bound of ${\sim}1{,}500$.  The 1-norm of the balanced
Hamiltonian (74.1~Ha) is \emph{lower} than the coupled CB value
(85.7~Ha) because the attractive cross-center $V_{ne}$ partially
cancels the repulsive cross-block $V_{ee}$.  The QWC group count
(87) remains far below the Gaussian baseline (273).

\subsection{Cross-center $V_{ne}$ census}

The cross-center nuclear attraction integrals (Sec.~\ref{sec:multipole_resolution})
add 33 nonzero one-body matrix elements to $h_1$ for LiH at
$n_{\max} = 2$:

\begin{table}[h]
\caption{Cross-center $V_{ne}$ census for LiH at $n_{\max} = 2$,
$R = 3.015$~bohr.}
\label{tab:vne_census}
\begin{ruledtabular}
\begin{tabular}{lddd}
Block $\to$ nucleus & \multicolumn{1}{c}{Nonzero} & \multicolumn{1}{c}{Max (Ha)} & \multicolumn{1}{c}{Trace (Ha)} \\
\hline
Core ($Z\!=\!3$) $\to$ H  & 11 & 0.373 & -1.646 \\
Val-Li ($Z\!=\!1$) $\to$ H & 11 & 0.328 & -1.182 \\
H-side ($Z\!=\!1$) $\to$ Li & 11 & 0.985 & -3.544 \\
\hline
Total & 33 & --- & -6.372 \\
\end{tabular}
\end{ruledtabular}
\end{table}

The large trace from the H-side block feeling the $Z = 3$ lithium
nucleus ($-3.544$~Ha) is the dominant contribution, consistent with
the physical expectation that the hydrogen electron is most strongly
affected by the nearby heavier nucleus.

\subsection{Four-electron FCI}

Table~\ref{tab:fci_balanced} presents FCI results at $R = 3.015$~bohr
for all four coupling schemes, including the new balanced configuration.
Nuclear repulsion is $V_{NN}$ only (no PK contribution).

\begin{table}[h]
\caption{Four-electron FCI for LiH at $n_{\max} = 2$,
$R = 3.015$~bohr.  Exact: $-8.071$~Ha.}
\label{tab:fci_balanced}
\begin{ruledtabular}
\begin{tabular}{lddl}
Configuration & \multicolumn{1}{c}{$E_{\mathrm{FCI}}$ (Ha)} & \multicolumn{1}{c}{Error} & Bound? \\
\hline
Balanced (CD)        & -7.924 & 1.8\%  & YES \\
Decoupled            & -7.195 & 10.9\% & NO  \\
Composed (PK)        & -6.863 & 15.0\% & NO  \\
Coupled CB           & -5.734 & 29.0\% & NO  \\
Exact                & -8.071 & 0\%    & YES \\
\end{tabular}
\end{ruledtabular}
\end{table}

The balanced configuration is the only coupling scheme that produces a
bound molecule.  The PES scan gives $R_{\rm eq} = 3.226$~bohr (7.0\%
error vs.\ exact 3.015~bohr) and $D_e = 0.037$~Ha (exact: 0.092~Ha).
The variational bound is respected at all $R$-points.

Conjecture~\ref{conj:accuracy} predicted that the balanced Hamiltonian
would achieve significantly better accuracy than PK's 5.3\%
$R_{\rm eq}$ error.  The result (7.0\%) does not confirm this in strict
sense.  However, the comparison is cross-regime: the 5.3\% figure
uses $l$-dependent PK at $l_{\max} = 2$ with continuous PES optimization,
while the current result uses $n_{\max} = 2$ FCI on a qubit Hamiltonian
with grid-computed integrals (0.18\% radial accuracy for $Z = 1$).
The qualitative result---the balanced coupled configuration is the
\emph{only} bound configuration among all four coupling schemes---is the
primary finding of this phase.

\subsection{Basis convergence: $n_{\max} = 3$}

At $n_{\max} = 3$ ($Q = 84$, $l_{\max} = 2$), the balanced coupled
Hamiltonian has 19{,}959 Pauli terms, 448.9~Ha 1-norm, and 2{,}298 QWC
groups.  The Pauli scaling exponent (2-point fit from $Q = 30$ to
$Q = 84$) is 3.03; the 1-norm exponent is 1.75.  The
Pauli-to-composed ratio (2.53$\times$) is consistent with
$n_{\max} = 2$ (2.63$\times$), indicating that the cross-block
overhead is a constant factor, not a growing penalty.

The cross-center $V_{ne}$ multipole expansion terminates exactly at
$L_{\max} = 4$ for $l_{\max} = 2$ ($d$--$d$ pairs), confirmed by
comparison to $L_{\max} = 10$ (max difference: machine zero).  The
total cross-center $V_{ne}$ trace is $-12.54$~Ha (168 nonzero terms).

The original grid-based integrals (trapezoid quadrature,
$O(1/n_{\mathrm{grid}})$ convergence) systematically underestimated
cross-center nuclear attraction by 0.09--0.47\% for diffuse $Z = 1$
orbitals.  Replacing with analytical evaluation via incomplete gamma
functions eliminates this error entirely (machine precision).  This
algebraicization is an instance of the exchange constant program
(Paper~18, Sec.~VII): the grid-based $V_{ne}$ was a calibration
exchange constant that proved eliminable once the right algebraic
structure was identified.  The
corrected $n_{\max} = 3$ energy at $R = 3.015$ is $-8.055$~Ha (0.20\%
error), improved from grid-based $-8.048$ (0.28\%).  The $R_{\rm eq}$,
however, moved only from 3.287 (grid) to 3.280 (analytical), confirming
that the outward drift is structural to the block decomposition, not
numerical.

\begin{table}[h]
\caption{Balanced coupled LiH convergence with basis size.
Exact energy at $R = 3.015$~bohr: $-8.071$~Ha.  Grid: trapezoid
quadrature ($n_{\mathrm{grid}} = 4000$).  Analytical: incomplete gamma
functions (machine precision).}
\label{tab:convergence}
\begin{ruledtabular}
\begin{tabular}{ldddddd}
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{$n_{\max}$} & \multicolumn{1}{c}{$Q$} &
\multicolumn{1}{c}{Pauli} & \multicolumn{1}{c}{1-norm (Ha)} &
\multicolumn{1}{c}{$E(3.015)$ (Ha)} & \multicolumn{1}{c}{Error} \\
\hline
Grid       & 2  & 30 & 878    & 74.1  & -7.924 & 1.8\%  \\
Analytical & 2  & 30 & 878    & 74.1  & -7.929 & 1.7\%  \\
Grid       & 3  & 84 & 19959  & 448.9 & -8.048 & 0.28\% \\
Analytical & 3  & 84 & 19959  & 448.9 & -8.055 & 0.20\% \\
\end{tabular}
\end{ruledtabular}
\end{table}

Table~\ref{tab:req_comparison} shows the definitive $R_{\rm eq}$
comparison:

\begin{table}[h]
\caption{$R_{\rm eq}$ comparison: grid vs.\ analytical integrals.
Exact: 3.015~bohr.}
\label{tab:req_comparison}
\begin{ruledtabular}
\begin{tabular}{ldddd}
\multicolumn{1}{c}{Method} & \multicolumn{1}{c}{$n_{\max}$} &
\multicolumn{1}{c}{$R_{\rm eq}$ (bohr)} &
\multicolumn{1}{c}{$R_{\rm eq}$ err} &
\multicolumn{1}{c}{$E(3.015)$ err} \\
\hline
Grid       & 2 & 3.226 & 7.0\% & 1.8\%  \\
Analytical & 2 & 3.227 & 7.0\% & 1.7\%  \\
Grid       & 3 & 3.287 & 9.0\% & 0.28\% \\
Analytical & 3 & 3.280 & 8.8\% & 0.20\% \\
Exact      & - & 3.015 & 0\%   & 0\%    \\
\end{tabular}
\end{ruledtabular}
\end{table}

The $n_{\max} = 3$ analytical PES (5 R-points):

\begin{table}[h]
\caption{Balanced coupled LiH PES at $n_{\max} = 3$ (analytical integrals).}
\label{tab:pes_nmax3}
\begin{ruledtabular}
\begin{tabular}{dd}
\multicolumn{1}{c}{$R$ (bohr)} & \multicolumn{1}{c}{$E$ (Ha)} \\
\hline
2.9   & -8.0494 \\
3.015 & -8.0545 \\
3.1   & -8.0571 \\
3.3   & -8.0592 \\
3.5   & -8.0563 \\
\end{tabular}
\end{ruledtabular}
\end{table}

\subsection{Summary of conjecture status}

Conjecture~\ref{conj:sparsity} (Pauli count): \textbf{confirmed}.
The balanced Hamiltonian has 878 Pauli terms, well below the
conjectured ${\sim}1{,}500$ bound.

Conjecture~\ref{conj:accuracy} (accuracy): \textbf{MIXED}.  Analytical
integrals (machine precision via incomplete gamma functions) confirm that
the $R_{\rm eq}$ drift is structural to the block decomposition, not
numerical: grid error contributed only 0.007~bohr to $R_{\rm eq}$ at
$n_{\max} = 3$.  The drift is $+0.053$~bohr per $n_{\max}$ step
($3\times$ smaller than PK's $+0.15$--$0.22$~bohr/$l_{\max}$) but in
the same outward direction.  Energy converges excellently:
$1.8\% \to 0.20\%$ ($9\times$ improvement) from $n_{\max} = 2$ to 3.
The balanced approach is optimal for single-point quantum simulation at
fixed geometries (0.20\% energy error), but not for PES-based equilibrium
geometry determination.


%% ========================================================================
\section{Research Path}
\label{sec:path}
%% ========================================================================

The following steps are required to test the conjectures of
Sec.~\ref{sec:architecture}:

\begin{enumerate}
\item \textbf{Two-center integral implementation.}  \emph{COMPLETE.}
  The convergence concern from the Shibuya--Wulfman basis expansion
  (Sec.~\ref{sec:sturmian}) was resolved: the cross-center $V_{ne}$
  uses the standard multipole expansion, which terminates exactly at
  $L_{\max} = 2 l_{\max}$ by Gaunt selection rules
  (Sec.~\ref{sec:multipole_resolution}).  For LiH at $n_{\max} = 2$,
  only 33 one-body matrix elements are needed.  Original grid numerical accuracy:
  0.18\% at $n_{\mathrm{grid}} = 4000$ for $Z = 1$ orbitals,
  $9 \times 10^{-8}$ for $Z = 3$.  Subsequently replaced by analytical
  evaluation via incomplete gamma functions (machine precision, zero
  quadrature).  The decision gate ($L_{\max} > 5$)
  is moot---the expansion terminates at $L_{\max} = 2$.

\item \textbf{Balanced coupled Hamiltonian.}  \emph{COMPLETE.}
  The balanced Hamiltonian (Eq.~\ref{eq:coupled} with all four
  interaction types) gives 878 Pauli terms, 74.1~Ha 1-norm, and
  87 QWC groups (Table~\ref{tab:resources}).
  Conjecture~\ref{conj:sparsity} confirmed.

\item \textbf{FCI benchmark.}  \emph{COMPLETE.}
  Four-electron FCI gives $E = -7.924$~Ha (1.8\% error),
  $R_{\rm eq} = 3.226$~bohr (7.0\%), $D_e = 0.037$~Ha.
  The balanced configuration is the only bound coupling scheme
  (Table~\ref{tab:fci_balanced}).  Conjecture~\ref{conj:accuracy}
  not confirmed in strict sense (7.0\% vs.\ 5.3\% PK), but the
  comparison is cross-regime.

\item \textbf{Scaling study.}  \emph{COMPLETE.}  $n_{\max} = 3$
  FCI with analytical integrals (incomplete gamma functions, machine
  precision): $E(3.015) = -8.055$~Ha (0.20\% error, down from 1.8\%
  at $n_{\max} = 2$; see Table~\ref{tab:convergence}).
  Pauli scaling exponent 3.03, 1-norm exponent 1.75.
  $R_{\rm eq} = 3.280$~bohr (8.8\% error), confirming structural drift
  of $+0.053$~bohr per $n_{\max}$ step ($3\times$ smaller than PK's
  $+0.15$--$0.22$~bohr/$l_{\max}$).  Grid error contributes only
  0.007~bohr to $R_{\rm eq}$ (negligible).  Classification: MIXED---energy
  converges excellently, $R_{\rm eq}$ drifts structurally.
  Extension to BeH$_2$ and H$_2$O: COMPLETE (v2.0.41--42).
\end{enumerate}

The critical risk is Step~1: if the angular expansion requires
$L_{\max} > 5$ for convergence, the Pauli count will approach the
full Level~4N encoding and the approach loses its structural advantage.
The Coulomb resolution route (approach~b) is the fallback if direct
expansion is too slow.


%% ========================================================================
\subsection{Polyatomic census}
\label{sec:polyatomic}
%% ========================================================================

The balanced coupled framework was extended to BeH$_2$ (collinear,
v2.0.41) and H$_2$O (non-collinear, v2.0.42), completing the
polyatomic census for all three composed molecules.

\begin{table}[h]
\centering
\begin{tabular}{lccccccc}
\hline
System & Blocks & $Q$ & Composed & Balanced & Pauli & $\lambda_\text{comp}$ & $\lambda_\text{bal}$ \\
       &        &     & Pauli    & Pauli    & ratio & (Ha)                  & (Ha) \\
\hline
LiH    & 2 & 30 & 334   & 878   & 2.63$\times$ & 37.3  & 74.1  \\
BeH$_2$ & 3 & 50 & 556   & 2,652 & 4.77$\times$ & 354.9 & 304.7 \\
H$_2$O & 5 & 70 & 778   & 5,798 & 7.45$\times$ & 361$^\dagger$ / 28,053 & 1,509.3 \\
\hline
\end{tabular}
\caption{Balanced coupled resource census. $^\dagger$H$_2$O composed electronic-only (PK partitioned).}
\label{tab:balanced_census}
\end{table}

BeH$_2$ four-electron FCI gives 10.7\% energy error with the
balanced Hamiltonian, compared to 27.4\% with PK and 10.9\%
decoupled.  The balanced 1-norm (304.7~Ha) is \emph{lower} than the
composed 1-norm (354.9~Ha), confirming that PK adds more 1-norm than
cross-center $V_{ne}$ for this system.

H$_2$O required a non-collinear generalization: the O--H bond vectors
make a 104.5$^\circ$ angle, so the cross-center $V_{ne}$ matrices
cannot be computed in a shared $z$-axis frame.  The solution is Wigner
$D$-matrix rotation of the real spherical harmonic basis: compute
$V_{ne}$ in the $z$-frame aligned with each bond vector, then rotate
via block-diagonal $D \cdot V_z \cdot D^T$ where $D$ is the rotation
matrix for real spherical harmonics (identity for $l = 0$, Cartesian
rotation permuted to $m = (-1, 0, 1)$ ordering for $l = 1$).  FCI is
infeasible for H$_2$O (10 electrons, $Q = 70$).  The lone pair
$V_{ne}$ integrals are well-behaved: all traces are below 3~Ha per
nucleus, confirming that the multipole expansion does not produce
unphysical couplings for lone pair blocks.

The Pauli ratio (balanced/composed) grows with block count:
$2.63\times$ (2-block LiH) $\to$ $4.77\times$ (3-block BeH$_2$)
$\to$ $7.45\times$ (5-block H$_2$O), because each block pair adds
cross-block ERIs and cross-center $V_{ne}$ terms.  The growth is
consistent with an $O(B^2)$ scaling in the number of blocks $B$.

The 1-norm advantage is regime-dependent.  For VQE/NISQ applications
where Pauli count and QWC groups dominate circuit cost, the composed
architecture with PK remains cheaper.  For fault-tolerant QPE where
the 1-norm determines the number of Trotter steps, the balanced
framework eliminates PK entirely.  This is decisive for molecules
with large nuclear charges: H$_2$O's PK contributed 98.7\% of the
total composed 1-norm (28,053~Ha), and the balanced 1-norm
(1,509.3~Ha) is $18.6\times$ cheaper.  Even compared to the
electronic-only composed 1-norm (361~Ha, with PK classically
partitioned), the balanced 1-norm is $4.18\times$ higher---but the
balanced Hamiltonian does not require the classical 1-RDM post-processing
step that PK partitioning demands.


%% ========================================================================
\section{Discussion}
\label{sec:discussion}
%% ========================================================================

The composed framework's PK pseudopotential was a necessary compromise
for \emph{classical} solvers that could not handle the full
inter-group Coulomb interaction.  In second quantization on a quantum
computer, antisymmetry is enforced by the fermionic algebra, not by
coordinate-space projectors.  The occupation number representation
naturally prevents double-occupancy without PK.  This suggests that
PK's \emph{antisymmetry enforcement} role is a classical solver
artifact.  However, PK also approximates the physical core-valence
Coulomb interaction energy---this role must be \emph{replaced} by
explicit inter-block integrals, not simply removed.

Track~CB's negative result confirms this distinction.  The failure
was not because PK was needed for antisymmetry, but because the
replacement was incomplete: cross-block $V_{ee}$ was added without
the balancing cross-center $V_{ne}$.  The 10.9\% error of the fully
decoupled Hamiltonian (better than PK's 15.0\%) reinforces the
interpretation that PK overcorrects the Coulomb interaction, but the
remaining 10.9\% error shows that inter-block coupling \emph{is}
needed for quantitative accuracy.

The four-electron FCI results (Sec.~\ref{sec:results}) confirm the
diagnosis from Track~CB.  PK overcorrects (15.0\% error, unbound).
Removing all inter-block coupling undercorrects (10.9\%, unbound).
Adding only cross-block $V_{ee}$ without $V_{ne}$ is energetically
unbalanced (29.0\%, worst of all).  Only the balanced combination of
all four interaction types---within-block $h_1$ and $V_{ee}$,
cross-block $V_{ee}$, and cross-center $V_{ne}$---produces a bound
molecule with the correct qualitative PES shape.  This suggests that
the physical content of PK is not pseudopotential enforcement of
orthogonality, but rather an incomplete approximation to the sum of
cross-block $V_{ee}$ and cross-center $V_{ne}$.

A practical concern: Track~CB found that adding cross-block ERIs
increases the 1-norm from 37.3 to 85.7~Ha.  Even if PK is
eliminated, the net quantum resource cost could increase if the
balanced coupled Hamiltonian has higher 1-norm than the composed
Hamiltonian with PK classically partitioned (Track~BF: electronic-only
1-norm 33.3~Ha).  The sparsity advantage in Pauli count may be
partially offset by a 1-norm disadvantage.  This tradeoff must be
quantified for the balanced Hamiltonian.

The mathematical infrastructure for computing the missing integrals
exists in the Coulomb Sturmian literature and connects directly to
GeoVac's $S^3$ foundation.  The open question is convergence: does
the Shibuya--Wulfman expansion converge fast enough at molecular bond
lengths to preserve the structural sparsity that is GeoVac's primary
computational advantage?

If the answer is yes, the composed framework would be superseded by
coupled composition: same block structure, same Gaunt selection
rules, same $O(Q^{2.5})$ scaling class, but without PK and with
significantly better accuracy.  Paper~17's composed architecture
would then move to the archive, replaced by the coupled composition
as the production molecular Hamiltonian builder.

If the answer is no, the composed framework with PK remains the
production architecture, and the accuracy ceiling is accepted as the
structural cost of maintaining block-diagonal sparsity.  In either
case, this paper documents the mathematical connections and the
concrete data (Track~CB census, FCI benchmarks) that define the
research frontier.

The $n_{\max} = 3$ results with analytical integrals definitively
resolve the key open questions from Phase~3.  The energy convergence
is excellent: 1.8\% $\to$ 0.20\% ($9\times$ improvement) as the
basis grows from $Q = 30$ to $Q = 84$, with the variational bound
respected.  This rules out the PK-like divergence scenario (where
higher angular momentum channels systematically overcounted
correlation).

The $R_{\rm eq}$ drift, however, is confirmed as structural to the
block decomposition, not numerical.  Analytical integrals (machine
precision via incomplete gamma functions) changed $R_{\rm eq}$ by
only 0.007~bohr at $n_{\max} = 3$ (3.287~$\to$~3.280~bohr), while
the drift from $n_{\max} = 2$ to 3 is $+0.053$~bohr.  This drift
is $3\times$ smaller than PK's $+0.15$--$0.22$~bohr/$l_{\max}$ but
in the same outward direction.  The root cause is the block
decomposition itself: each block uses a different effective nuclear
charge ($Z_{\mathrm{eff}}$), and orbitals on different blocks do not
span the same Hilbert space.  The cross-center $V_{ne}$ partially
bridges this gap but cannot fully compensate for the incomplete
orbital overlap between blocks at finite basis.  The balanced
approach is optimal for single-point quantum simulation at fixed
geometries (0.20\% energy error), but not for PES-based equilibrium
geometry determination.  The analytical evaluation of $V_{ne}$ via
incomplete gamma functions adds the cross-center nuclear attraction
to the algebraic registry (Paper~18, Table~I), confirming that the
balanced coupled framework introduces no new exchange constants
relative to the composed architecture.

\emph{Relationship to the LCAO negative result.}  The coupled
composition program reconstructs a multi-center molecular Hamiltonian
from atom-centered orbitals, which is superficially similar to the
LCAO approach abandoned in v0.9.x (Section~3 of the project
guidelines).  The key difference: LCAO used unstructured graph
concatenation with no natural geometry, producing $R$-independent
kinetic energies.  Coupled composition retains the natural geometry
block structure---each electron group inhabits its own optimal
coordinate system---and Gaunt selection rules enforce sparsity within
and across blocks.  The block decomposition provides physical
structure that LCAO lacked.

\emph{Applications paper.}  Paper~20 presents the GeoVac Hamiltonian
library as a practical tool for the quantum computing community, with
benchmark tables comparing GeoVac and Gaussian resource costs at
matched accuracy, FCI PES characterization, and installation
instructions.  The balanced coupled architecture documented in this
paper (Paper~19) provides the PK-free Hamiltonians benchmarked there.


%% ========================================================================
%% BIBLIOGRAPHY
%% ========================================================================

\begin{thebibliography}{30}

\bibitem{loutey_paper7}
J.~Loutey, ``The Dimensionless Vacuum: Conformal Equivalence of
  Graph and Continuum Quantum Mechanics,'' GeoVac Paper~7 (2025).

\bibitem{loutey_paper11}
J.~Loutey, ``Prolate Spheroidal Lattice for Diatomic Molecules,''
  GeoVac Paper~11 (2026).

\bibitem{loutey_paper12}
J.~Loutey, ``Algebraic Two-Electron Integrals on the Prolate
  Spheroidal Lattice,'' GeoVac Paper~12 (2026).

\bibitem{loutey_paper14}
J.~Loutey, ``Structurally Sparse Qubit Hamiltonians from Spectral
  Graph Theory,'' GeoVac Paper~14 (2026).

\bibitem{loutey_paper17}
J.~Loutey, ``Composed Natural Geometries for Core-Valence Diatomics,''
  GeoVac Paper~17 (2026).

\bibitem{fock1935}
V.~Fock, ``Zur Theorie des Wasserstoffatoms,''
  Z.~Phys.\ \textbf{98}, 145 (1935).

\bibitem{shibuya1965}
T.~I.~Shibuya and C.~E.~Wulfman, ``Molecular orbitals in momentum
  space,'' Proc.\ Roy.\ Soc.\ A \textbf{286}, 376 (1965).

\bibitem{koga1987}
T.~Koga and T.~Matsuhashi, ``Sum rules for nuclear attraction
  integrals over hydrogenic orbitals,''
  J.~Chem.\ Phys.\ \textbf{87}, 4696 (1987).

\bibitem{avery2000}
J.~Avery, \emph{Hyperspherical Harmonics and Generalized Sturmians}
  (Kluwer Academic, Dordrecht, 2000).

\bibitem{avery2004}
J.~Avery, ``Many-center Coulomb Sturmians and Shibuya--Wulfman
  integrals,'' Int.\ J.\ Quantum Chem.\ \textbf{100}, 121 (2004).

\bibitem{hoggan2011}
P.~E.~Hoggan, ``How Exponential Type Orbitals Recently Became a Viable
  Basis Set Choice in Molecular Electronic Structure Work,'' in
  \emph{Solving the Schr\"odinger Equation: Has Everything Been
  Tried?}, edited by P.~Popelier (Imperial College Press, 2011),
  Chap.~7.

\bibitem{avery2012}
J.~S.~Avery and J.~E.~Avery, ``Coulomb Sturmians as a basis for
  molecular calculations,'' Mol.\ Phys.\ \textbf{110}, 1593 (2012).

\bibitem{avery2014}
J.~E.~Avery and J.~S.~Avery, ``Molecular integrals for Slater type
  orbitals using Coulomb Sturmians,''
  J.~Math.\ Chem.\ \textbf{52}, 301 (2014).

\bibitem{herbst2018}
M.~F.~Herbst, J.~E.~Avery, and A.~Dreuw, ``Quantum chemistry with
  Coulomb Sturmians: Construction and convergence of Coulomb Sturmian
  basis sets at Hartree--Fock level,'' arXiv:1811.05777 (2018).

\end{thebibliography}

\end{document}
