\documentclass[twocolumn,pra,amsmath,amssymb,superscriptaddress]{revtex4-2}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{xcolor}

\begin{document}

\title{Entanglement Structure of the Angular Momentum Eigenbasis:\\
Energy-Entanglement Decoupling and Basis-Intrinsic Sparsity}

\author{J.~Loutey}
\affiliation{Independent Researcher, Kent, Washington}

\date{April 13, 2026}

\begin{abstract}
We characterize the entanglement structure of multi-electron atoms
in the angular momentum eigenbasis---the basis whose orbitals are
products of hydrogenic radial functions and spherical harmonics,
labeled by quantum numbers $(n, l, m)$.  Four computational results
are presented.
First, energy-entanglement decoupling: the off-diagonal one-body
Hamiltonian (graph Laplacian topology, coupling constant
$\kappa = -1/16$) contributes $10$--$39\%$ of the correlation
energy but less than $0.2\%$ of the entanglement entropy; the
off-diagonal electron repulsion contributes $100\%$ of the
entanglement.  Entanglement entropy scales as $S \sim Z^{-2.56}$
across He-like ions.
Second, basis-intrinsic sparsity: among orbital bases for systems
with spherical symmetry, the angular momentum eigenbasis is the
unique basis producing sparse electron repulsion integrals (ERIs).
Any unitary rotation of orbital indices, no matter how small, fills
the ERI tensor from $42\%$ to $99\%$ density in a step-function
transition at the identity.  The nonzero ERI count
is $Z$-independent, confirming that sparsity is purely geometric.
Third, entanglement network topology: orbital mutual information
maps reveal a hub migration pattern---$1s \to 2s \to 2p$---that
tracks the partially filled shell across the first row of the
periodic table.
Fourth, core-valence decoupling: the core-valence mutual
information drops below $10^{-3}$ by $Z = 4$, quantitatively
justifying the composed fiber bundle factorization used in the
GeoVac molecular framework.
In the composed molecular architecture, per-block entanglement is
$R$-independent, with core/bond entropy ratios of $50\times$ at
matched qubit count.
These results establish that the angular momentum eigenbasis
decouples one-body energy transport from two-body entanglement,
and that the $O(Q^{2.5})$ Pauli scaling of the GeoVac qubit
Hamiltonians is a direct consequence of this basis choice.
This is Paper~26 in the GeoVac series.
\end{abstract}

\maketitle

%=================================================================
\section{Introduction}
\label{sec:intro}
%=================================================================

Quantum simulation of fermionic systems encodes second-quantized
Hamiltonians as weighted sums of Pauli operators.  The number of
nonzero Pauli terms, the number of qubitwise-commuting (QWC)
measurement groups, and the Pauli 1-norm $\lambda$ are the dominant
resource metrics for near-term variational~\cite{Peruzzo2014} and
fault-tolerant~\cite{Lee2021} quantum algorithms.  All three
metrics depend on the choice of single-particle basis: a basis
that produces sparse two-body matrix elements yields fewer Pauli
terms and lower measurement overhead.

The GeoVac framework~\cite{GeoVac_Paper0, GeoVac_Paper7,
GeoVac_Paper14} constructs qubit Hamiltonians in the angular
momentum eigenbasis, where single-particle orbitals are products
of hydrogenic radial functions and spherical harmonics labeled by
$(n, l, m)$.  In this basis, the Gaunt selection rules from angular
momentum conservation zero out the majority of electron repulsion
integrals (ERIs)~\cite{GeoVac_Paper22}: at $l_{\max} = 2$, the
angular ERI density is $2.76\%$, meaning $97.24\%$ of all possible
two-body matrix elements vanish by symmetry before any property of
the potential is invoked.  This sparsity produces qubit
Hamiltonians with $O(Q^{2.5})$ Pauli terms for composed molecular
systems~\cite{GeoVac_Paper14}, compared to $O(Q^{3.9\text{--}4.3})$
for Gaussian orbital bases.

Two questions about this basis remain open.  First, is the sparsity
fragile or robust?  Does an infinitesimal change of basis destroy
it, or does it degrade smoothly?  Second, what is the entanglement
structure of the ground state in this basis?  The angular momentum
eigenbasis diagonalizes the one-body Hamiltonian (up to a known
off-diagonal coupling $\kappa = -1/16$ from the graph
Laplacian~\cite{GeoVac_Paper7}); does this one-body near-diagonality
translate into a simple entanglement pattern?

This paper answers both questions through systematic computation
across He-like ions ($Z = 2$--$10$) and first-row atoms
($Z = 2$--$9$) in the graph eigenbasis at $n_{\max} = 2$--$4$.
The results establish four structural properties of the angular
momentum eigenbasis that are relevant to quantum simulation
resource estimation.

%=================================================================
\section{The Three-Layer Decomposition}
\label{sec:threelayer}
%=================================================================

\subsection{Hamiltonian structure in the graph basis}

The full Hamiltonian for an $N$-electron atom in the angular
momentum eigenbasis decomposes as
\begin{equation}
  H = H_{\text{diag}} + H_{\text{h1,off}} + H_{\text{Vee,off}},
  \label{eq:decomposition}
\end{equation}
where $H_{\text{diag}}$ contains the diagonal one-body energies
$\varepsilon_{nlm}$ and the diagonal (Hartree) electron repulsion,
$H_{\text{h1,off}}$ contains the off-diagonal one-body matrix
elements from the graph Laplacian (with coupling constant
$\kappa = -1/16$), and $H_{\text{Vee,off}}$ contains the
off-diagonal electron repulsion integrals (exchange and
correlation).

These three layers correspond to three physically distinct
contributions:
\begin{enumerate}
\item \textbf{Rational layer} ($H_{\text{diag}}$): diagonal
  energies and mean-field repulsion.  Produces no orbital
  entanglement---the ground state is a single Slater determinant
  with zero entanglement entropy.
\item \textbf{Topological layer} ($H_{\text{diag}} +
  H_{\text{h1,off}}$): adds the graph Laplacian inter-shell
  couplings.  These are one-body operators that redistribute
  amplitude among orbitals but, being separable, generate
  negligible entanglement.
\item \textbf{Correlation layer} ($H_{\text{diag}} +
  H_{\text{h1,off}} + H_{\text{Vee,off}}$): adds the off-diagonal
  electron repulsion.  This is the irreducible two-body interaction
  that generates all entanglement in the ground state.
\end{enumerate}

The decomposition is specific to the angular momentum eigenbasis.
In a generic orbital basis, the one-body Hamiltonian has dense
off-diagonal elements, and the three layers are not separable.

\subsection{Energy-entanglement decoupling}

We compute the ground-state energy and single-orbital entanglement
entropy $S = -\text{Tr}(\rho_A \ln \rho_A)$ for each layer by
exact diagonalization (full configuration interaction) of He-like
ions at $n_{\max} = 4$.  The single-orbital entanglement entropy
is computed from the 1-RDM eigenvalues of the FCI ground state,
partitioning the system into one spatial orbital and the remainder.

Table~\ref{tab:decoupling} presents the fractional contribution
of each off-diagonal layer to the total correlation energy
$E_{\text{corr}} = E_{\text{FCI}} - E_{\text{diag}}$ and to the
total entanglement entropy.

\begin{table}
\caption{Energy-entanglement decoupling in He-like ions at
$n_{\max} = 4$.  $f_E^{\text{h1}}$ and $f_E^{\text{Vee}}$:
fractional contribution of each off-diagonal layer to the
correlation energy (note: fractions sum to values exceeding 1.0
because the layers are not orthogonal projections of the
correlation energy; cross-terms between the layers contribute
positively).  $f_S^{\text{h1}}$ and $f_S^{\text{Vee}}$:
fractional contribution to the entanglement entropy.
$S_{\text{total}}$: total single-orbital entanglement entropy
in nats.
\label{tab:decoupling}}
\begin{ruledtabular}
\begin{tabular}{cddddd}
$Z$ & \multicolumn{1}{c}{$f_E^{\text{h1}}$}
    & \multicolumn{1}{c}{$f_E^{\text{Vee}}$}
    & \multicolumn{1}{c}{$f_S^{\text{h1}}$}
    & \multicolumn{1}{c}{$f_S^{\text{Vee}}$}
    & \multicolumn{1}{c}{$S$ (nats)} \\
\hline
 2 & 0.387 & 1.290 & 0.002 & 0.998 & 0.0419 \\
 3 & 0.289 & 1.570 & 0.000 & 1.000 & 0.0120 \\
 4 & 0.228 & 1.690 & 0.000 & 1.000 & 0.0054 \\
 5 & 0.194 & 1.770 & 0.000 & 1.000 & 0.0031 \\
10 & 0.099 & 1.881 & 0.000 & 1.000 & 0.0007 \\
\end{tabular}
\end{ruledtabular}
\end{table}

The central result is stark: the graph Laplacian topology
($H_{\text{h1,off}}$) contributes $10$--$39\%$ of the correlation
energy but less than $0.2\%$ of the entanglement entropy.  The
off-diagonal electron repulsion contributes effectively $100\%$
of the entanglement.

The entanglement entropy scales as a power law across the
isoelectronic series:
\begin{equation}
  S(Z) \sim Z^{-2.56},
  \label{eq:scaling}
\end{equation}
obtained from a log-log fit across $Z = 2$--$10$.  This is
consistent with the known result that electron correlation becomes
perturbatively small at large $Z$, where the nuclear attraction
dominates the electron repulsion and the ground state approaches
a single Slater determinant.

The operator-theoretic origin of both the $f_S^{\text{h1}}\to 0$
decoupling and the $Z^{-2.56}$ scaling is established in
Paper~27~\cite{GeoVac_Paper27}.  The decoupling follows from a
free-fermion identity: any non-degenerate one-body ground state on
a finite lattice has identically zero single-orbital entropy in
its natural-orbital basis, so $f_S^{\text{h1}} \equiv 0$ up to the
(exponentially small) projection defect that maps the natural-
orbital basis to the angular-momentum eigenbasis.  The
$Z$-scaling follows from the Paper~27 universal curve
$S_B = A(\tilde{w}_B/\delta_B)^{\gamma}$: across He-like ions,
$\tilde{w}_B = \lVert V_{ee}^{\mathrm{off}(H_1)}\rVert_F /
\lVert H_1\rVert_F \sim 1/Z$ (because $V_{ee}\sim Z$ while
$H_1\sim Z^{2}$) while $\delta_B$ is nearly $Z$-independent, so
$S(Z) \sim Z^{-\gamma}$ with $\gamma \approx 2.5$ in the
$n_{\max}=4, Z\in[2,10]$ window.  The measured exponent
$-2.546$ at $n_{\max}=4$ agrees with Eq.~\eqref{eq:scaling} to
within $0.6\%$.

\subsection{Connection to graph validity}

The fractional energy contribution of $H_{\text{h1,off}}$ scales
as $\sim 1/(8Z^2)$, consistent with the graph validity scaling
identified in Paper~7.  The graph off-diagonal coupling
$\kappa = -1/16$ is $Z$-independent, while the diagonal energies
scale as $Z^2$.  The relative importance of the graph topology
is therefore
\begin{equation}
  \frac{|\kappa|}{Z^2/n^2} = \frac{1}{16 Z^2/n^2},
\end{equation}
which is $12.5\%$ at $Z = 1$, $3.1\%$ at $Z = 2$, and $0.13\%$
at $Z = 10$.  This scaling matches the $f_E^{\text{h1}}$ column
in Table~\ref{tab:decoupling}.

Below the graph validity boundary at $Z_c \approx 1.84$
(Paper~7), the graph off-diagonal coupling is no longer
perturbative: $|\kappa|$ exceeds the diagonal energy gap, and
the graph-native CI over-binds (violating the variational bound).
The energy-entanglement decoupling sharpens this picture: at
$Z < Z_c$, the graph topology not only overcounts the energy but
may also distort the entanglement structure by mixing shells
beyond what the exact $V_{ee}$ interaction warrants.

%=================================================================
\section{Basis-Intrinsic Sparsity}
\label{sec:sparsity}
%=================================================================

\subsection{The angular momentum eigenbasis as a sparsity-isolated point}

Paper~22 established that the angular ERI density is determined
solely by angular quantum numbers and is independent of the radial
potential~\cite{GeoVac_Paper22}.  We now ask a sharper question:
within the space of orbital bases for a spherically symmetric
system, is the angular momentum eigenbasis an isolated point of
sparsity, or is it surrounded by a family of bases with comparable
ERI density?

We test this by applying a unitary rotation
$U(\theta) = e^{i \theta G}$ to the spatial orbital basis, where
$G$ is a random anti-Hermitian generator, and computing the number
of nonzero ERIs as a function of the rotation angle $\theta$.

\subsection{Step-function sparsity transition}

At $n_{\max} = 2$ (five spatial orbitals: $1s, 2s, 2p_{-1}, 2p_0,
2p_1$), the graph basis produces 265 nonzero ERIs out of
$5^4 = 625$ possible four-index combinations, corresponding to an
ERI density of $42.4\%$.  Rotating the basis by any angle
$\theta > 10^{-6}$ fills the ERI tensor to $\sim 620/625$ nonzero
entries ($99.2\%$ density).

The transition is effectively a step function at the identity:
\begin{equation}
  D(\theta) =
  \begin{cases}
    0.424, & \theta = 0 \\
    0.992, & \theta > 10^{-6}.
  \end{cases}
  \label{eq:step}
\end{equation}

This result is not an artifact of the small basis.  At
$n_{\max} = 4$ (30 spatial orbitals), the graph basis produces
79,465 nonzero ERIs, and any rotation beyond $\theta \sim 10^{-6}$
fills the tensor to near-complete density.

\subsection{$Z$-independence of ERI count}

The nonzero ERI count is identical across all $Z$ at fixed
$n_{\max}$: 79,465 nonzero ERIs at $n_{\max} = 4$ for
$Z = 2, 3, 4, 5, 10$.  This confirms that the sparsity pattern
is purely geometric---determined entirely by angular momentum
conservation (Gaunt selection rules)---and independent of the
radial wavefunctions.  Changing $Z$ rescales the radial functions
$R_{nl}(r) \to Z^{3/2} R_{nl}(Zr)$ but does not alter which
angular integrals vanish.

\subsection{Implications for Pauli scaling}

The $O(Q^{2.5})$ Pauli scaling of the GeoVac composed qubit
Hamiltonians~\cite{GeoVac_Paper14} is a direct consequence of
the Gaunt sparsity.  The step-function transition
(Eq.~\ref{eq:step}) shows that this scaling is not continuously
connected to the $O(Q^{3.9\text{--}4.3})$ scaling of Gaussian
bases.  The angular momentum eigenbasis sits at a singular point
in the space of orbital bases: the unique point where angular
momentum conservation is exactly respected and the ERI tensor
is sparse.  Any departure from this point, no matter how small,
immediately incurs the dense-ERI penalty.

%=================================================================
\section{Entanglement Network Topology}
\label{sec:network}
%=================================================================

\subsection{Orbital mutual information}

The entanglement network of an $N$-electron ground state can be
characterized by the orbital mutual information~\cite{Rissler2006,
Boguslawski2012}
\begin{equation}
  I(i, j) = S(\rho_i) + S(\rho_j) - S(\rho_{ij}),
  \label{eq:mi}
\end{equation}
where $S(\rho_i)$ is the von Neumann entropy of the reduced
density matrix for spatial orbital $i$, and $\rho_{ij}$ is the
two-orbital reduced density matrix.  The mutual information
$I(i, j)$ quantifies the total (classical and quantum) correlation
between orbitals $i$ and $j$.

We compute $I(i, j)$ from the FCI ground state for first-row atoms
in the graph eigenbasis at $n_{\max} = 2$.

\subsection{Hub migration across the periodic table}

The mutual information matrices reveal a hub migration pattern
that tracks the partially filled shell:

\medskip\noindent\textbf{Helium ($\mathbf{Z = 2}$, 2 electrons):}
Star topology centered on $1s$.  The dominant correlation is
$I(1s, 2s) = 0.877$, with all other orbitals connecting through
$1s$.  The $1s$ orbital is the sole entanglement hub.

\medskip\noindent\textbf{Lithium ($\mathbf{Z = 3}$, 3 electrons):}
Hub shifts to $2s$.  The dominant correlation is
$I(2s, 3s) = 1.324$.  The $1s$ orbital drops to $9\%$ of the
total mutual information, reflecting the onset of core-valence
decoupling.

\medskip\noindent\textbf{Beryllium ($\mathbf{Z = 4}$, 4 electrons):}
Multi-hub topology.  The $2s$ orbital remains the primary hub
($43\%$ of total MI), but $p$-orbitals begin developing secondary
cross-links.

\medskip\noindent\textbf{Nitrogen--Fluorine ($\mathbf{Z = 7}$--$\mathbf{9}$, 7--9 electrons):}
Hub transitions to $2p(\pm 1)$.  P-shell correlation dominates
the mutual information network.

\medskip
The pattern is:
\begin{equation}
  \text{hub: } 1s \xrightarrow{Z=3} 2s \xrightarrow{Z=4}
  \text{frozen} \xrightarrow{Z=5} 2p \xrightarrow{Z=10}
  \text{frozen},
  \label{eq:hub}
\end{equation}
following the shell-filling sequence.  At each transition, the
previously active shell freezes (its mutual information with other
orbitals drops to near zero) and the newly filling shell becomes
the entanglement hub.

\subsection{Physical interpretation}

The hub migration has a simple physical origin: entanglement is
generated by the off-diagonal $V_{ee}$ interaction, which is
strongest between orbitals that share the same spatial region and
are partially occupied.  A closed shell ($n_i \approx 2$ for a
spatial orbital) has $S(\rho_i) \approx 0$ and contributes
negligible mutual information.  An open shell
($0 < n_i < 2$) has maximal $S(\rho_i)$ and dominates the
entanglement network.

This mechanism is basis-independent in principle, but the angular
momentum eigenbasis makes it maximally transparent: the one-body
Hamiltonian is nearly diagonal (the graph Laplacian couples only
adjacent $n$-shells with strength $\kappa = -1/16$), so the
natural orbital occupations closely track the Aufbau filling
order.  In a Gaussian basis, where the one-body Hamiltonian has
dense off-diagonal elements, the hub structure would be obscured
by basis-induced orbital mixing.

%=================================================================
\section{Core-Valence Decoupling}
\label{sec:corevalence}
%=================================================================

\subsection{Core-valence mutual information}

The GeoVac composed geometry~\cite{GeoVac_Paper17} factorizes the
molecular electronic structure into separate fiber bundles for
core and valence electrons, each in its own natural coordinate
system.  This factorization assumes that the cross-bundle
entanglement is negligible.  We test this assumption by computing
the total core-valence mutual information
\begin{equation}
  I_{\text{cv}} = \sum_{i \in \text{core}} \sum_{j \in \text{valence}}
  I(i, j)
  \label{eq:icv}
\end{equation}
for first-row atoms in the graph eigenbasis.

Table~\ref{tab:corevalence} presents the results.

\begin{table}
\caption{Core-valence mutual information $I_{\text{cv}}$ for
first-row atoms in the graph eigenbasis ($n_{\max} = 2$).  Core
orbitals: $1s$.  Valence orbitals: $2s, 2p$.
\label{tab:corevalence}}
\begin{ruledtabular}
\begin{tabular}{cll}
Atom & $Z$ & $I_{\text{cv}}$ \\
\hline
He & 2 & $0.751$ \\
Li & 3 & $0.213$ \\
Be & 4 & $0.002$ \\
B--Ne & 5--10 & $< 10^{-3}$ \\
\end{tabular}
\end{ruledtabular}
\end{table}

The core-valence mutual information drops sharply with $Z$.  By
$Z = 4$ (beryllium), $I_{\text{cv}} < 0.002$, and for $Z \geq 5$
it is below $10^{-3}$.  The composed factorization's assumption
of negligible core-valence entanglement is quantitatively justified
for all atoms from boron onward.

Helium ($I_{\text{cv}} = 0.751$) is the exception: with only two
electrons, there is no core-valence separation, and the entire
system is entangled.  Lithium ($I_{\text{cv}} = 0.213$) is
intermediate: the $1s$ core is partially decoupled from the $2s$
valence electron, but the separation is not yet clean.  This is
consistent with the known difficulty of treating lithium in the
composed framework (the PK pseudopotential is the accuracy
bottleneck~\cite{GeoVac_Paper17}).

\subsection{Molecular entanglement: $R$-independence}

In the composed architecture, each orbital block (core, bond pair,
lone pair) has its own effective nuclear charge $Z_{\text{eff}}$
and its own set of hydrogenic orbitals.  The one-body and two-body
matrix elements within each block are computed from $Z_{\text{eff}}$
alone, with no dependence on the internuclear distance $R$.
The nuclear geometry enters only through the nuclear repulsion
energy, which is a classical constant.

This structural feature implies that the per-block entanglement
entropy is $R$-independent.  We verify this for the H$_2$ bond
pair in the composed encoding:
\begin{equation}
  S_{\text{bond}}(R) = 0.303 \text{ nats}
  \quad \forall\, R \in [0.5, 10.0] \text{ bohr}.
  \label{eq:rindep}
\end{equation}

The entropy does \emph{not} approach $\ln 2 \approx 0.693$ nats
at large $R$, which would correspond to the two electrons becoming
maximally entangled across the two atomic centers at dissociation.
This is a known limitation of the composed architecture: with
fixed-exponent blocks, the basis cannot describe bond breaking,
where the true wavefunction transitions from a single-determinant
bonding state to a multi-reference dissociated state.  The
composed architecture is designed for single-point energy
evaluation at fixed geometries, not for dissociation curves.

\subsection{Core/bond entropy ratio}

For LiH in the composed encoding, the core block
($Z_{\text{eff}} = 3$) has $S_{\text{core}} = 0.006$ nats, while
the bond block ($Z_{\text{eff}} = 1$) has
$S_{\text{bond}} = 0.303$ nats.  The ratio is
\begin{equation}
  \frac{S_{\text{bond}}}{S_{\text{core}}} \approx 50,
  \label{eq:ratio}
\end{equation}
consistent with the $S \sim Z^{-2.56}$ scaling law: the core
electrons at $Z_{\text{eff}} = 3$ are $3^{2.56} \approx 18$ times
less entangled than the bond electrons at $Z_{\text{eff}} = 1$
(the discrepancy from the scaling prediction reflects the
different electron counts in core vs.\ bond blocks).

This ratio quantifies the information-theoretic asymmetry between
core and valence: the core contributes negligible entanglement to
the total state and can be treated as a classical mean-field
background with minimal loss of quantum information.

%=================================================================
\section{Discussion}
\label{sec:discussion}
%=================================================================

\subsection{Why the angular momentum eigenbasis decouples energy
from entanglement}

The energy-entanglement decoupling (Table~\ref{tab:decoupling})
has a simple structural origin.  The one-body Hamiltonian $h_1$
is a separable operator: it acts independently on each electron.
A separable operator cannot generate entanglement between orbitals.
In the angular momentum eigenbasis, $h_1$ is nearly diagonal (the
off-diagonal elements are the graph Laplacian couplings with
$\kappa = -1/16$), so $H_{\text{h1,off}}$ is a small perturbation
that mixes single-particle states without introducing two-body
correlations.

The electron repulsion $V_{ee}$ is the irreducible two-body
interaction.  It generates entanglement by correlating the
occupations of pairs of orbitals.  In the angular momentum
eigenbasis, the Gaunt selection rules restrict which orbital pairs
can interact, producing the sparse entanglement networks observed
in Sec.~\ref{sec:network}.

The decoupling is basis-specific.  In a Gaussian orbital basis,
the one-body Hamiltonian has dense off-diagonal elements (from
the kinetic energy and nuclear attraction integrals in the
non-orthogonal basis).  These dense one-body couplings mix orbital
occupations in ways that blur the distinction between one-body
redistribution and two-body correlation.  The angular momentum
eigenbasis, by nearly diagonalizing the one-body physics, isolates
the two-body entanglement in $V_{ee}$ alone.

\subsection{Connection to quantum simulation resources}

The energy-entanglement decoupling has a direct implication for
quantum simulation.  The off-diagonal $V_{ee}$ elements that
generate all the entanglement are precisely the elements constrained
by the Gaunt selection rules.  Fewer nonzero $V_{ee}$ elements
means fewer Pauli terms in the Jordan--Wigner encoding, fewer QWC
measurement groups, and lower 1-norm---the three resource metrics
that dominate near-term quantum algorithm cost.

The composed qubit Hamiltonians~\cite{GeoVac_Paper14} exploit this
directly: by staying in the angular momentum eigenbasis and
respecting the block structure of the composed geometry, the
GeoVac Hamiltonians achieve $O(Q^{2.5})$ Pauli scaling with
$51\times$--$1712\times$ fewer Pauli terms than published Gaussian
baselines at matched qubit counts.

\subsection{Limitations}

Several limitations should be noted.

\medskip\noindent\textbf{Basis truncation.}  The first-row
entanglement network results (Sec.~\ref{sec:network}) use
$n_{\max} = 2$ (five spatial orbitals).  For $Z \geq 5$, this
provides only one valence $p$-orbital beyond the $1s$ and $2s$
shells.  The hub migration pattern is robust across the series,
but quantitative mutual information values may shift at larger
$n_{\max}$.  The He-like ion results (Table~\ref{tab:decoupling})
use $n_{\max} = 4$ (30 spatial orbitals) and are well-converged.

\medskip\noindent\textbf{Composed $R$-independence.}  The
$R$-independent block entanglement (Eq.~\ref{eq:rindep}) is a
structural property of the composed architecture, not a physical
statement about molecular entanglement.  The true molecular
ground state has $R$-dependent entanglement that diverges at
dissociation.  The composed architecture captures the entanglement
within each block accurately but does not describe inter-block
entanglement or bond breaking.

\medskip\noindent\textbf{$d$-orbital systems.}  All results are
for $s$- and $p$-orbital systems.  Whether the energy-entanglement
decoupling and the hub migration pattern extend to $d$-orbital
systems (transition metals) is an open question.  The Gaunt
selection rules apply at all $l_{\max}$~\cite{GeoVac_Paper22},
so the basis-intrinsic sparsity is guaranteed, but the
entanglement structure may differ.

%=================================================================
\section{Conclusions}
\label{sec:conclusions}
%=================================================================

Four structural properties of the angular momentum eigenbasis
have been established.

First, the one-body Hamiltonian (graph Laplacian topology)
contributes significant correlation energy ($10$--$39\%$) but
negligible entanglement ($< 0.2\%$).  All entanglement in the
ground state originates from the off-diagonal electron repulsion.
The entanglement entropy scales as $S \sim Z^{-2.56}$.

Second, among orbital bases for spherically symmetric systems,
the angular momentum eigenbasis is an isolated point of ERI
sparsity.  Any unitary rotation of the orbital indices, no matter
how small, fills the ERI tensor from $42\%$ to $99\%$ density in
a step-function transition.

Third, the orbital mutual information network exhibits a hub
migration pattern---$1s \to 2s \to 2p$---that tracks the
partially filled shell across the first row.

Fourth, core-valence mutual information drops below $10^{-3}$
by $Z = 4$, quantitatively justifying the composed fiber bundle
factorization.

These results establish that the $O(Q^{2.5})$ Pauli scaling of
the GeoVac qubit Hamiltonians is a direct consequence of the
angular momentum eigenbasis choice: the basis that decouples
one-body energy from two-body entanglement is the same basis
that produces sparse ERIs, and both properties arise from the
underlying angular momentum conservation symmetry.

%=================================================================
% Acknowledgments
%=================================================================

\begin{acknowledgments}
This work was performed using an AI-augmented agentic workflow.
The principal investigator provided scientific direction and quality
control; implementation, computation, and documentation drafting
were performed collaboratively with large language models (Anthropic
Claude).
\end{acknowledgments}

%=================================================================
% References
%=================================================================

\begin{thebibliography}{20}

\bibitem{Peruzzo2014}
A.~Peruzzo \textit{et al.},
``A variational eigenvalue solver on a photonic quantum processor,''
Nat.\ Commun.\ \textbf{5}, 4213 (2014).

\bibitem{Lee2021}
J.~Lee \textit{et al.},
``Even more efficient quantum computations of chemistry through
tensor hypercontraction,''
PRX Quantum \textbf{2}, 030305 (2021).

\bibitem{Rissler2006}
J.~Rissler, R.~M.~Noack, and S.~R.~White,
``Measuring orbital interaction using quantum information theory,''
Chem.\ Phys.\ \textbf{323}, 519 (2006).

\bibitem{Boguslawski2012}
K.~Boguslawski \textit{et al.},
``Entanglement measures for single- and multireference correlation
effects,''
J.\ Phys.\ Chem.\ Lett.\ \textbf{3}, 3129 (2012).

\bibitem{GeoVac_Paper0}
J.~Loutey,
``Angular Momentum as Information Geometry: Isotropic Packing and
the Universal Angular Cross-Section,''
GeoVac Technical Report (2025).

\bibitem{GeoVac_Paper7}
J.~Loutey,
``The Dimensionless Vacuum: Spectral Graph Theory and Conformal
Equivalence on $S^3$,''
GeoVac Technical Report (2025).

\bibitem{GeoVac_Paper14}
J.~Loutey,
``Structurally Sparse Qubit Hamiltonians from Spectral Graph Theory,''
GeoVac Technical Report (2025).

\bibitem{GeoVac_Paper17}
J.~Loutey,
``Composed Natural Geometries for Core-Valence Molecular
Electronic Structure,''
GeoVac Technical Report (2025).

\bibitem{GeoVac_Paper22}
J.~Loutey,
``Potential-Independent Angular Sparsity for Qubit Hamiltonians
in Spherical Fermion Systems,''
GeoVac Technical Report (2026).

\bibitem{GeoVac_Paper27}
J.~Loutey,
``Entropy as a Projection Artifact: One-Body Operators are
Entanglement-Inert on Sparse Lattices,''
GeoVac Technical Report (2026).

\end{thebibliography}

\end{document}
