% Paper 28: QED on S^3 — Spectral Geometry of Perturbative Transcendentals
% GeoVac Project, April 2026
% v2.0 — Definitive rewrite with theorem-proof format

\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage[margin=1in]{geometry}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{observation}{Observation}

\title{QED on $S^3$: Spectral Geometry of Perturbative Transcendentals}
\author{GeoVac Project}
\date{April 2026}

\begin{document}
\maketitle

\begin{abstract}
We compute perturbative QED spectral sums on the three-sphere $S^3$
using the Camporesi--Higuchi Dirac spectrum and the Hodge-1 (photon)
spectrum with SO(4) vertex selection rules.  Eight structural results
emerge.
(1)~\textbf{T9 theorem:} the spectral zeta function of the squared
Dirac operator $D^2$ is a two-term polynomial in $\pi^2$ with rational
coefficients at every integer~$s$; no odd-zeta content appears
(Theorem~\ref{thm:T9}).
(2)~\textbf{Even/odd parity discriminant:} operator order (2nd vs 1st)
is the primary transcendental discriminant---even $s$ produces
$\pi^{\mathrm{even}}$, odd $s$ produces $\zeta(3)$, $\zeta(5)$, etc.
(Theorem~\ref{thm:parity}).
(3)~\textbf{$\chi_{-4}$ identity:}
$D_{\mathrm{even}}(s) - D_{\mathrm{odd}}(s) = 2^{s-1}(\beta(s) -
\beta(s{-}2))$ at every integer $s \ge 2$, a concrete spectral-zeta
to Dirichlet-$L$ bridge (Theorem~\ref{thm:chi4}).
(4)~\textbf{Self-energy structural zero:} the one-loop electron
self-energy on $S^3$ vanishes identically at the ground state
$n_{\mathrm{ext}}=0$ as a consequence of vertex parity
(Theorem~\ref{thm:self_energy_zero}).
(5)~\textbf{Anomalous magnetic moment:} the one-loop vertex correction
with a $q=1$ probe photon yields $F_2 / [\alpha/(2\pi)] = 1.084$ at the
lowest external mode ($n_{\mathrm{ext}}=1$), approximately 8.4\% above the
flat-space Schwinger value, matching the Parker--Toms leading curvature
correction within 0.4\%.  The curvature expansion coefficient
$c_2 = \frac{19}{100} - \frac{41\pi^2}{25200}$, extracted from
high-precision $n_{\mathrm{ext}}=1$ data ($n_{\mathrm{int}}=0\ldots 50$
with tail correction), involves all three Paper~2 spectral invariants
($B=42$, $F=\pi^2/6$, $\Delta=1/40$) in a single algebraic combination
(Sec.~\ref{sec:curvature_coefficients}).  The next coefficient
$c_3 = -5.946(3) \times 10^{-7}$ is nonzero at $200.9\,\sigma$;
the expansion does not terminate at second order.
(6)~\textbf{Depth-$k$ tower:} at each loop order, a new irreducible
transcendental constant appears.  The two-loop $S_{\min}$ is computed
to 200 digits and confirmed irreducible against a 100-element PSLQ
basis; the three-loop constant $S^{(3)}$ is independent of $S_{\min}$
(Proposition~\ref{prop:depth_k}).
(7)~\textbf{$\zeta(3)$ complementarity:} the degeneracy-weighted
fine-structure shell sum $\mathcal{S}(n) = n(5n-4)/2$ and the Dirac
mode degeneracy $g_n^{\mathrm{Dirac}} = 2n(n+1)$ satisfy
$\mathcal{S}(n) + g_n^{\mathrm{Dirac}} = 9n^2/2$ exactly, so the
Dirichlet series identity
$D_{\mathcal{S}}(s) + D_{g}(s) = \tfrac{9}{2}\,\zeta(s{-}2)$ holds
for all~$s$: the $\zeta(s{-}1)$ terms---all odd-zeta content---cancel
identically (Theorem~\ref{thm:zeta3_complement}).
(8)~\textbf{Fine-structure Euler sum cancellation and product survival
rule:} the degeneracy-weighted Dirichlet sums $D_p$ at order
$(Z\alpha)^{2p}$ in the exact Dirac hydrogen spectrum, computed through
$D_6$ ($(Z\alpha)^{12}$, weight~11), satisfy a product survival rule:
$\zeta(2) \times \zeta(\mathrm{odd})$ cancels algebraically at every
order, while exactly $\max(0, \lfloor(2p{-}5)/2\rfloor)$ products
survive (Observations~\ref{obs:euler_cancel},~\ref{obs:product_rule}).
The cancellation mechanism is the $n^2$ Fock degeneracy --- the same
weighting that produces $F = \zeta(2) = D_{n^2}(4)$ in Paper~2.
However, PSLQ confirms that Paper~2's $K = \pi(B + F - \Delta)$ is NOT
a $\mathbb{Q}$-linear combination of $D_2, \ldots, D_6$: the
spectral-action ingredients of $K$ inhabit the $\pi$-polynomial ring of
Theorem~\ref{thm:T9}, while the Sommerfeld sums carry irreducible
odd-zeta from the Euler--Zagier MZV algebra.
A complementary \emph{graph-native} formulation
(Sec.~\ref{sec:graph_native_qed}) computes all one-loop diagrams as
finite matrix traces on the GeoVac Fock graph, requiring no infinite
sums, regularization, or renormalization.  All graph-native QED
quantities are $\pi$-free (algebraic); the projection exchange constant
relating graph and continuum VP is \emph{rational} at every finite
truncation, confirming Paper~18's calibration-tier classification.
The continuum self-energy structural zero (Theorem~\ref{thm:self_energy_zero})
is broken on the finite graph: the pendant-edge theorem
(Proposition~\ref{prop:pendant_edge}) proves
$\Sigma_{\mathrm{graph}}(\mathrm{GS}) = 2(n_{\max}-1)/n_{\max} \to 2$
exactly, never healing in the graph limit.  The root cause is that the
graph photon is a scalar 1-cochain, lacking the spin-1 vector structure
whose SO(4) selection rules enforce the continuum zero.
Comprehensive transcendental tables for $D(s)$, $D_{\mathrm{even}}(s)$,
$D_{\mathrm{odd}}(s)$, and the one-loop self-energy are presented, all
backed by the test suite.
\end{abstract}

% ===================================================================
\section{Introduction}
\label{sec:introduction}
% ===================================================================

The GeoVac framework~\cite{paper7,paper14} computes quantum-mechanical
observables from the spectral data of graph Laplacians on compact
manifolds.  On the three-sphere $S^3$, the Dirac operator has a discrete
spectrum with known eigenvalues and degeneracies~\cite{camporesi1996},
and the framework produces structurally sparse qubit
Hamiltonians~\cite{paper14} with $O(Q^{2.5})$ Pauli scaling.

Paper~18~\cite{paper18} introduced an exchange-constant taxonomy that
classifies where transcendental numbers enter quantum-mechanical
computations: intrinsic (from angular structure), calibration (from the
$S^3$ projection), and embedding (from the electron--electron cusp).
The present paper extends this taxonomy to perturbative QED by computing
spectral sums that probe the interaction structure of quantum
electrodynamics on~$S^3$.

All calculations in the paper use three modules in the \texttt{geovac}
codebase: \texttt{qed\_vacuum\_polarization} (one-loop heat kernel),
\texttt{qed\_vertex} (two-loop sunset with vertex parity),
\texttt{qed\_self\_energy} (one-loop self-energy and vertex correction),
and \texttt{qed\_three\_loop} (three-loop chain topology with $O(N^3)$
factorization).  Every stated numerical value is backed by a test in
\texttt{tests/test\_qed\_*.py} (combined 117 tests, all passing).

The central finding is that the $S^3$ spectral geometry produces the
\emph{same} transcendental constants that appear in flat-space
perturbative QED---$\zeta(3)$, $\zeta(5)$, Catalan's~$G$, Dirichlet
$\beta(4)$---through a purely geometric mechanism (operator order plus
vertex topology), together with \emph{new} irreducible constants at each
loop order that have no known closed form.

% ===================================================================
\section{Spectral Data on $S^3$}
\label{sec:spectra}
% ===================================================================

\subsection{Dirac spectrum}

On the unit three-sphere, the Dirac operator has eigenvalues and
degeneracies~\cite{camporesi1996}
\begin{equation}
  |\lambda_n| = n + \tfrac{3}{2}, \qquad
  g_n = 2(n+1)(n+2), \qquad n = 0, 1, 2, \ldots
  \label{eq:dirac_spectrum}
\end{equation}
The Dirac Dirichlet series is
$D(s) = \sum_{n=0}^{\infty} g_n / |\lambda_n|^s$.
Via Hurwitz zeta,
\begin{equation}
  D(s) = 2\,\zeta(s{-}2, \tfrac{3}{2})
       - \tfrac{1}{2}\,\zeta(s, \tfrac{3}{2}).
  \label{eq:dirac_hurwitz}
\end{equation}
Using $\zeta(s, 3/2) = (2^s - 1)\zeta_R(s) - 2^s$, this becomes
\begin{equation}
  D(s) = 2(2^{s-2} - 1)\,\zeta_R(s{-}2)
       - \tfrac{1}{2}(2^s - 1)\,\zeta_R(s).
  \label{eq:hurwitz_discriminant}
\end{equation}

We define the even-$n$ and odd-$n$ sub-sums:
\begin{equation}
  D_{\mathrm{even}}(s) = \sum_{\substack{n=0 \\ n\,\mathrm{even}}}^{\infty}
    \frac{g_n}{|\lambda_n|^s}, \qquad
  D_{\mathrm{odd}}(s) = \sum_{\substack{n=1 \\ n\,\mathrm{odd}}}^{\infty}
    \frac{g_n}{|\lambda_n|^s},
  \label{eq:D_even_odd_def}
\end{equation}
so that $D(s) = D_{\mathrm{even}}(s) + D_{\mathrm{odd}}(s)$.

\subsection{Hodge-1 (photon) spectrum}

The transverse vector Laplacian (Hodge-1 operator) on $S^3$ has
eigenvalues and degeneracies
\begin{equation}
  \mu_q = q(q+2), \qquad d_q^T = q(q+2), \qquad q = 1, 2, 3, \ldots
  \label{eq:hodge1_spectrum}
\end{equation}
The Ricci shift $+2$ relative to the scalar Laplacian eigenvalues
$\ell(\ell+2)$ follows from the Bochner--Weitzenb\"ock identity
$\Delta_1 = \nabla^*\nabla + \mathrm{Ric}$ on $S^3$
(Ricci scalar $R = 6$ on unit $S^3$, giving $\mathrm{Ric} = 2g$).
There are no zero modes ($\beta_1 = 0$ for $S^3$).

\subsection{Vertex selection rule}

The QED vertex on $S^3$ couples spinor harmonics at levels $n_1, n_2$
to a vector harmonic at level $q$ with the SO(4) selection rule:
\begin{equation}
  |n_1 - n_2| \le q \le n_1 + n_2, \qquad
  n_1 + n_2 + q \;\text{is odd}.
  \label{eq:vertex_rule}
\end{equation}
The parity constraint arises from the $\gamma^\mu$ coupling, which
flips the chirality representation of $\mathrm{SO}(4)
= \mathrm{SU}(2)_L \times \mathrm{SU}(2)_R$.

The SO(4) Clebsch--Gordan channel count $W(n_1, n_2, q) \in \{0,1,2\}$
weights each allowed triple by the number of independent coupling
channels (the two components of the transverse vector harmonic under
$\mathrm{SU}(2)_L \times \mathrm{SU}(2)_R$).

% ===================================================================
\section{Theorem 1: Squared Dirac Spectral Zeta (T9)}
\label{sec:T9}
% ===================================================================

\begin{theorem}[T9: $D^2$ spectral zeta is $\pi^{\mathrm{even}}$]
\label{thm:T9}
The spectral zeta function of the squared Dirac operator on unit
$S^3$ satisfies
\begin{equation}
  \zeta_{D^2}(s)
    = 2^{2s-1}\bigl[\lambda(2s{-}2) - \lambda(2s)\bigr],
  \label{eq:T9}
\end{equation}
where $\lambda(2k) = (1 - 2^{-2k})\,\zeta_R(2k)
= \mathrm{rational} \times \pi^{2k}$.
At every integer~$s \ge 1$, $\zeta_{D^2}(s)$ is a two-term polynomial
in $\pi^2$ with rational coefficients.  No odd-zeta content appears
at any~$s$.
\end{theorem}

\begin{proof}
The squared Dirac eigenvalues are $\lambda_n^2 = (n + 3/2)^2
= (2n+3)^2/4$, so
$\zeta_{D^2}(s) = \sum_{n \ge 0} g_n \cdot (4/(2n+3)^2)^s
= 4^s \sum_{n \ge 0} 2(n+1)(n+2) / (2n+3)^{2s}$.
Substituting $m = 2n+3$ (which runs over odd integers $\ge 3$), the
sum becomes $\sum_{m \ge 3, m\,\mathrm{odd}} (m^2-1)/2 \cdot
4^s / m^{2s}$.  The $(m^2 - 1)/2$ factor splits as
$(m^{2-2s} - m^{-2s})/2$, giving two Dirichlet-type sums over odd
integers.  Each odd-integer sum is $\lambda(2k) = (1-2^{-2k})\zeta_R(2k)$
with the first three odd values ($m=1$) added or subtracted to correct
the lower limit.  By the Euler--Bernoulli formula,
$\zeta_R(2k) = (-1)^{k+1} (2\pi)^{2k} B_{2k} / (2\cdot (2k)!)$,
so $\lambda(2k) = \mathrm{rational} \times \pi^{2k}$.  Odd-zeta values
$\zeta_R(2k+1)$ never appear because the squared spectrum converts every
odd power to an even power.
\end{proof}

\noindent\textbf{Verification:} Symbolic identity confirmed in
\texttt{sympy} for $s = 1, \ldots, 10$.  Numerical agreement to
$10^{-60}$ at $s = 2, \ldots, 20$.

\begin{table}[h]
\centering
\caption{Squared Dirac spectral zeta $\zeta_{D^2}(s)$.}
\label{tab:D2_values}
\begin{tabular}{@{}cl@{}}
\toprule
$s$ & $\zeta_{D^2}(s)$ \\
\midrule
1 & $\pi^2 - \pi^4/12$ \\
2 & $2\pi^4/3 - 2\pi^6/15$ \\
3 & $16\pi^6/15 - 16\pi^8/63$ \\
4 & $32\pi^8/9 - 256\pi^{10}/495$ \\
\bottomrule
\end{tabular}
\end{table}

% ===================================================================
\section{Theorem 2: Even/Odd Parity Discriminant}
\label{sec:parity}
% ===================================================================

\begin{theorem}[Parity discriminant]
\label{thm:parity}
At even integer $s$, the Dirac Dirichlet series $D(s)$ is purely
$\pi^{\mathrm{even}}$.  At odd integer $s$, $D(s)$ involves
$\zeta_R(s{-}2)$ and $\zeta_R(s)$ (odd-zeta values).  Operator order
(2nd vs 1st) is the primary transcendental discriminant: second-order
operators produce $\pi^{\mathrm{even}}$ exclusively; first-order
operators produce odd-zeta values at odd~$s$.
\end{theorem}

\begin{proof}
From Eq.~\eqref{eq:hurwitz_discriminant},
$D(s) = 2(2^{s-2} - 1)\,\zeta_R(s{-}2)
       - \tfrac{1}{2}(2^s - 1)\,\zeta_R(s)$.
At even~$s$, both $\zeta_R(s{-}2)$ and $\zeta_R(s)$ are Bernoulli-type:
$\zeta_R(2k) = (-1)^{k+1} (2\pi)^{2k} B_{2k} / (2 \cdot (2k)!)
= \mathrm{rational} \times \pi^{2k}$.  At odd~$s$, both
$\zeta_R(s{-}2)$ and $\zeta_R(s)$ are genuine odd-zeta values
($\zeta(3)$, $\zeta(5)$, \ldots) that are $\mathbb{Q}$-linearly
independent of all $\pi^{2k}$ by Ap\'ery's theorem and its
extensions~\cite{apery1979,rivoal2000}.
\end{proof}

\begin{table}[h]
\centering
\caption{Dirac Dirichlet series $D(s)$: PSLQ identifications at 80 dps.}
\label{tab:D_values}
\begin{tabular}{@{}cll@{}}
\toprule
$s$ & $D(s)$ & Class \\
\midrule
4 & $\pi^2 - \pi^4/12$ & $\pi^{\mathrm{even}}$ \\
5 & $14\,\zeta(3) - \tfrac{31}{2}\,\zeta(5)$ & odd-zeta \\
6 & $\pi^4/3 - \pi^6/30$ & $\pi^{\mathrm{even}}$ \\
7 & $62\,\zeta(5) - \tfrac{127}{2}\,\zeta(7)$ & odd-zeta \\
8 & $2\pi^6/15 - 17\pi^8/1260$ & $\pi^{\mathrm{even}}$ \\
9 & $254\,\zeta(7) - \tfrac{511}{2}\,\zeta(9)$ & odd-zeta \\
10 & $17\pi^8/315 - 31\pi^{10}/4725$ & $\pi^{\mathrm{even}}$ \\
\bottomrule
\end{tabular}
\end{table}

\noindent The appearance of $\zeta(3)$ at $s = 5$ is the $S^3$ analog of
the $\zeta(3)$ that enters flat-space two-loop QED through the
Schwinger--Rosner vertex correction~\cite{rosner1967}.

% ===================================================================
\section{Theorem 3: The $\chi_{-4}$ Identity}
\label{sec:chi4}
% ===================================================================

\begin{theorem}[$\chi_{-4}$ identity]
\label{thm:chi4}
For every integer $s \ge 2$,
\begin{equation}
  D_{\mathrm{even}}(s) - D_{\mathrm{odd}}(s)
    \;=\; 2^{s-1}\bigl(\beta(s) - \beta(s{-}2)\bigr),
  \label{eq:D_diff_closed}
\end{equation}
where $\beta(s) = L(s, \chi_{-4})$ is the Dirichlet beta function.
\end{theorem}

\begin{proof}
Express $D_{\mathrm{even}}(s)$ and $D_{\mathrm{odd}}(s)$ via Hurwitz
zeta at quarter-integer shifts:
$D_{\mathrm{even}}(s) = 2^{-(s-2)} \zeta(s{-}2, 3/4)
                       - 2^{-(s+2)} \zeta(s, 3/4)$
and
$D_{\mathrm{odd}}(s) = 2^{-(s-2)} \zeta(s{-}2, 5/4)
                       - 2^{-(s+2)} \zeta(s, 5/4)$.
Two elementary Hurwitz identities:
$\zeta(s, 5/4) = \zeta(s, 1/4) - 4^s$ (shift recurrence) and
$\zeta(s, 3/4) - \zeta(s, 1/4) = -4^s \beta(s)$ (the Dirichlet
beta definition).  Substituting both, the $\zeta(s, 1/4)$ pieces
cancel in the difference $D_{\mathrm{even}} - D_{\mathrm{odd}}$ and the
$4^s$ prefactors combine to yield~\eqref{eq:D_diff_closed}.
\end{proof}

\noindent\textbf{Verification:}
Eq.~\eqref{eq:D_diff_closed} verified symbolically (\texttt{sympy}
residual zero) at $s \in \{2, 3, \ldots, 10, 15\}$ and by PSLQ at
100-digit precision at every integer $s$ in the tested range.  At $s=4$,
$D_{\mathrm{even}}(4) - D_{\mathrm{odd}}(4) = 8(\beta(4) - G)$
(since $G = \beta(2)$), consistent with the explicit
decompositions~\eqref{eq:D_even_4}--\eqref{eq:D_odd_4} below.

\subsection{Vertex-parity decomposition at $s = 4$}

The two-loop sunset diagram couples spinor pairs $(n_1, n_2)$
subject to the vertex parity constraint.  The even-$n$ and odd-$n$
sub-sums of $D(4)$ decompose as:
\begin{align}
  D_{\mathrm{even}}(4)
    &= \tfrac{\pi^2}{2} - \tfrac{\pi^4}{24}
       - 4G + 4\beta(4),
  \label{eq:D_even_4} \\
  D_{\mathrm{odd}}(4)
    &= \tfrac{\pi^2}{2} - \tfrac{\pi^4}{24}
       + 4G - 4\beta(4),
  \label{eq:D_odd_4} \\
  D(4) &= \pi^2 - \tfrac{\pi^4}{12}
  \qquad\text{(Catalan and $\beta(4)$ cancel)}.
  \label{eq:D_full}
\end{align}
Here $G = \beta(2) = \sum_{n=0}^{\infty} (-1)^n/(2n+1)^2 \approx
0.9159656$ is Catalan's constant and $\beta(4) \approx 0.9889446$ is the
Dirichlet beta function at $s=4$.  The mechanism: vertex parity acts as
the Dirichlet character $\chi_{-4}$ on the mode sum, and the
quarter-integer Hurwitz shifts expose $L(s, \chi_{-4})$ in the
even/odd difference.  Verified by PSLQ at 80-digit precision with
basis $\{1, \pi^2, \pi^4, G, \beta(4)\}$.

\begin{corollary}
The $\chi_{-4}$ identity is a structural realization of the
vertex-parity-as-$\chi_{-4}$ mechanism, but does not constrain
the zeros of $\beta(s)$: a zero of $\beta$ at $s = \rho$ propagates
to zeros of $D_{\mathrm{diff}}$ at both $\rho$ and $\rho + 2$,
consistent with but not enforcing $\Re\rho = 1/2$.
\end{corollary}

\subsection{Three-axis taxonomy}

The transcendental content of any QED spectral sum on $S^3$ is
classified by three independent axes:
\begin{enumerate}
\item \textbf{Operator order.}
      Second-order ($D^2$) $\to$ $\pi^{\mathrm{even}}$ (Theorem~\ref{thm:T9});
      first-order ($|D|$) $\to$ odd-zeta (Theorem~\ref{thm:parity}).
\item \textbf{Bundle type.}
      Scalar vs spinor modulates coefficients but not the
      transcendental class (Paper~18 Sec~IV).
\item \textbf{Diagram topology.}
      Vertex parity introduces Dirichlet $L$-function characters
      ($G$, $\beta(4)$) that are absent from unrestricted sums
      (Theorem~\ref{thm:chi4}).
\end{enumerate}

% ===================================================================
\section{Theorem 4: Self-Energy Structural Zero}
\label{sec:self_energy}
% ===================================================================

The one-loop electron self-energy on $S^3$ (Feynman gauge) is:
\begin{equation}
  \Sigma(n_{\mathrm{ext}}) = \sum_{n_{\mathrm{int}}, q}
    \frac{W(n_{\mathrm{ext}}, n_{\mathrm{int}}, q) \;
          g_{n_{\mathrm{int}}} \; d_q^T}
         {|\lambda_{n_{\mathrm{int}}}|^{2s_e} \; \mu_q^{s_\gamma}},
  \label{eq:self_energy}
\end{equation}
where the sum is over internal electron mode $n_{\mathrm{int}}$ and
photon mode $q$ subject to the vertex selection
rule~\eqref{eq:vertex_rule}, $s_e = 2$ (so $|\lambda|^4$ in the
denominator), $s_\gamma = 1$, and $W$ is the SO(4) channel count.

\begin{theorem}[Self-energy structural zero]
\label{thm:self_energy_zero}
$\Sigma(0) = 0$ exactly.  The one-loop self-energy vanishes
identically at the Dirac ground state $n_{\mathrm{ext}} = 0$.
\end{theorem}

\begin{proof}
At $n_{\mathrm{ext}} = 0$, the vertex selection rule requires
$|0 - n_{\mathrm{int}}| \le q \le 0 + n_{\mathrm{int}}$ and
$0 + n_{\mathrm{int}} + q$ odd.  The first condition forces
$q = n_{\mathrm{int}}$.  The second then requires
$2\,n_{\mathrm{int}}$ to be odd, which is impossible for any
integer $n_{\mathrm{int}}$.  Therefore $W(0, n_{\mathrm{int}}, q) = 0$
for all $(n_{\mathrm{int}}, q)$, and the sum is empty.
\end{proof}

\noindent This is the $S^3$ analog of the fact that the ground state
of a compact system cannot emit into a vacuum mode: the vertex parity
constraint is a spectral selection rule, not a dynamical cancellation.

\subsection{Self-energy for excited states}

For $n_{\mathrm{ext}} \ge 1$, the self-energy is nonzero and
convergent.  We compute $\Sigma(n_{\mathrm{ext}})$ at physical
propagator powers ($s_e = 2$, $s_\gamma = 1$) for $n_{\mathrm{ext}}
= 0, 1, \ldots, 5$ at cutoff $n_{\max} = 30$.

\begin{table}[h]
\centering
\caption{One-loop self-energy $\Sigma(n_{\mathrm{ext}})$ on $S^3$,
$n_{\max} = 30$.}
\label{tab:self_energy}
\begin{tabular}{@{}cl@{}}
\toprule
$n_{\mathrm{ext}}$ & $\Sigma(n_{\mathrm{ext}})$ \\
\midrule
0 & $0$ (exact, Theorem~\ref{thm:self_energy_zero}) \\
1 & 1.2854 \\
2 & 1.7862 \\
3 & 2.0843 \\
4 & 2.2884 \\
5 & 2.4398 \\
\bottomrule
\end{tabular}
\end{table}

\noindent The self-energy increases monotonically with
$n_{\mathrm{ext}}$, consistent with stronger coupling at higher
momentum shells.  At $n_{\mathrm{ext}} = 1$, PSLQ at 50 dps
identifies $\Sigma(1)$ as containing $\pi^{\mathrm{even}}$ and
Catalan $G$ components (vertex parity active on the asymmetric
coupling to the $n_{\mathrm{ext}} = 1$ shell).

\subsection{Vertex correction}

The one-loop vertex correction involves two vertex insertions:
\begin{equation}
  \Lambda(n_{\mathrm{ext}}) = \sum_{n_{\mathrm{int}}, q_1, q_2}
    \frac{W(n_{\mathrm{ext}}, n_{\mathrm{int}}, q_1) \;
          W(n_{\mathrm{int}}, n_{\mathrm{ext}}, q_2) \;
          g_{n_{\mathrm{int}}} \; d_{q_1}^T \; d_{q_2}^T}
         {|\lambda_{n_{\mathrm{int}}}|^{2s_e} \;
          \mu_{q_1}^{s_\gamma} \; \mu_{q_2}^{s_\gamma}}.
  \label{eq:vertex_correction}
\end{equation}
This is $O(N^3)$ in the cutoff.  Both $\Lambda(n_{\mathrm{ext}})$ and
$\Sigma(n_{\mathrm{ext}})$ are backed by 35 tests in
\texttt{tests/test\_qed\_self\_energy.py}.

\noindent\textbf{Note:} The shell-summed vertex correction
$\Lambda(n_{\mathrm{ext}})$ defined above uses the CG-weight channel
count $W$ and is $m_j$-independent (it gives $B = 0$ by the
Wigner--Eckart theorem).  The anomalous magnetic moment extraction
requires the $m_j$-resolved three-point function developed in the
next section.

% ===================================================================
\section{Anomalous Magnetic Moment on $S^3$}
\label{sec:anomalous_moment}
% ===================================================================

\subsection{Why the two-point vertex correction gives $B = 0$}

The two-point vertex correction $\Lambda(n_{\mathrm{ext}})$ defined
in Eq.~\eqref{eq:vertex_correction} sums over all internal modes and
photon polarizations at \emph{fixed} external quantum numbers
$(n_{\mathrm{ext}}, j_{\mathrm{ext}}, m_j)$.  On $S^3$, the vertex
amplitude at each junction involves a product of four
$\mathrm{SU}(2)_L \times \mathrm{SU}(2)_R$ Clebsch--Gordan
coefficients.  When the photon polarizations $(m_{g,L}, m_{g,R})$ are
summed over at both vertices, the SO(4) Wigner--Eckart theorem forces
the result to be independent of~$m_j$:
\begin{equation}
  \Lambda(n_{\mathrm{ext}}, j, m_j = +\tfrac{1}{2})
  = \Lambda(n_{\mathrm{ext}}, j, m_j = -\tfrac{1}{2}).
  \label{eq:B_zero_two_point}
\end{equation}
Therefore the spin-dependent piece
$B_{\mathrm{2pt}} = \Lambda(+\tfrac{1}{2}) - \Lambda(-\tfrac{1}{2}) = 0$
identically.  The two-point vertex correction is a scalar under SO(4)
rotations and cannot distinguish spin orientations.  To extract the
anomalous magnetic moment ($F_2$ form factor), an external probe must
break the rotational symmetry.

\subsection{Three-point vertex correction with probe photon}

The anomalous magnetic moment is extracted from a three-point function
in which an external probe photon of mode $q_{\mathrm{probe}} = 1$
(the lowest transverse vector harmonic, the $S^3$ analog of a uniform
magnetic field) is inserted between the two loop-photon vertices.  The
physical topology is:
\begin{equation}
  \langle \mathrm{ext}, m_j |
  \;\Gamma^{\mathrm{1-loop}}_{\mathrm{probe}}\;
  | \mathrm{ext}, m_j \rangle
  = \sum_{\substack{n_{\mathrm{int}},\, j_{\mathrm{int}} \\
                     m_{j,\mathrm{int}},\, m'_{j,\mathrm{int}} \\
                     q_{\mathrm{loop}}}}
    \frac{V_1 \;\cdot\; V_{\mathrm{probe}} \;\cdot\; V_3}
         {|\lambda_{n_{\mathrm{int}}}|^4 \;\mu_{q_{\mathrm{loop}}}},
  \label{eq:three_point_vertex}
\end{equation}
where:
\begin{itemize}
\item $V_1$: amplitude for the external electron $(m_j)$ to emit a
      loop photon and transition to the internal state $(m_{j,\mathrm{int}})$;
\item $V_{\mathrm{probe}}$: amplitude for the probe photon at $q=1$ to
      scatter the internal electron from $m_{j,\mathrm{int}}$ to
      $m'_{j,\mathrm{int}}$, summed over probe polarizations;
\item $V_3$: amplitude for the internal state $(m'_{j,\mathrm{int}})$ to
      reabsorb the loop photon and return to the external state $(m_j)$.
\end{itemize}
Each vertex amplitude is a product of four Clebsch--Gordan coefficients
coupling the $\mathrm{SU}(2)_L \times \mathrm{SU}(2)_R$ representations
of source, target, and photon:
\begin{equation}
  V = \sum_{m_{L,1}}
    C^{j_s}_{j_{s,L}\, j_{s,R}}(m_{L,1},\, m_j - m_{L,1};\, m_j)
    \;\cdot\;
    C^{j_t}_{j_{t,L}\, j_{t,R}}(m_{L,2},\, m_{R,2};\, m'_j)
    \;\cdot\;
    C^{j_{t,L}}_{j_{s,L}\, j_{g,L}}(m_{L,1},\, m_{g,L};\, m_{L,2})
    \;\cdot\;
    C^{j_{t,R}}_{j_{s,R}\, j_{g,R}}(m_{R,1},\, m_{g,R};\, m_{R,2}),
  \label{eq:4CG_vertex}
\end{equation}
where $m_{L,2} = m_{L,1} + m_{g,L}$ and $m_{R,2} = m_{R,1} + m_{g,R}$,
and the sum runs over all $m_{L,1} \in \{-j_{s,L}, \ldots, +j_{s,L}\}$.

The probe photon at $q = 1$ has channels $(j_{g,L}, j_{g,R}) = (1, 0)$
or $(0, 1)$, corresponding to the two components of the transverse
vector harmonic.  The probe couples internal states
$m_{j,\mathrm{int}} \to m'_{j,\mathrm{int}}$, enabling spin-dependent
amplitudes that the polarization-summed two-point function cannot access.

The spin-dependent piece of the vertex correction is:
\begin{equation}
  B = \Gamma^{\mathrm{1-loop}}_{\mathrm{probe}}(m_j = +\tfrac{1}{2})
    - \Gamma^{\mathrm{1-loop}}_{\mathrm{probe}}(m_j = -\tfrac{1}{2}).
  \label{eq:B_three_point}
\end{equation}

\subsection{Tree-level normalization}

The tree-level (zeroth-order) coupling of the external electron to the
$q = 1$ probe photon provides the normalization for $F_2$ extraction.
At the external state $n_{\mathrm{ext}} = 1$, $j = 1/2$
(Camporesi--Higuchi level $n_{\mathrm{CH}} = 1$, with
$j_L = 1$, $j_R = 1/2$):
\begin{align}
  V_{\mathrm{tree}}(m_j = +\tfrac{1}{2})
    &= -V_{\mathrm{tree}}(m_j = -\tfrac{1}{2})
    = 0.2790,
  \label{eq:V_tree} \\
  V_{\mathrm{magnetic}}
    &= V_{\mathrm{tree}}(+\tfrac{1}{2})
     - V_{\mathrm{tree}}(-\tfrac{1}{2})
    = 0.5579.
  \label{eq:V_magnetic}
\end{align}
The charge piece
$[V_{\mathrm{tree}}(+\tfrac{1}{2}) + V_{\mathrm{tree}}(-\tfrac{1}{2})]/2
= 0$
vanishes---the $q = 1$ probe photon couples purely to the magnetic
moment at tree level, as expected for the $S^3$ analog of a uniform
magnetic field.

Analytically, $V_{\mathrm{magnetic}} = 2(\sqrt{2}/3 - \sqrt{3}/9)$,
a pure algebraic number from the Clebsch--Gordan coefficients.

The Pauli form factor is then:
\begin{equation}
  F_2 = \frac{B}{V_{\mathrm{magnetic}}},
  \label{eq:F2_def}
\end{equation}
and the anomalous magnetic moment on $S^3$ is $a_e^{S^3} = F_2$.

\subsection{Convergence and results}

The three-point vertex correction converges rapidly.  Table~\ref{tab:g_minus_2}
shows the per-level contributions for the external state at
$n_{\mathrm{ext}} = 1$.

\begin{table}[h]
\centering
\caption{Per-level contributions to the anomalous magnetic moment on
$S^3$.  External state $n_{\mathrm{ext}} = 1$, $j = 1/2$.
The $n_{\mathrm{int}} = 0$ contribution vanishes by the self-energy
structural zero (Theorem~\ref{thm:self_energy_zero}).
Contributions drop by approximately $100\times$ per successive allowed
level pair.}
\label{tab:g_minus_2}
\begin{tabular}{@{}ccccc@{}}
\toprule
$n_{\mathrm{int}}$ & $\Delta B$ & $B_{\mathrm{cumul}}$
  & $F_2 / [\alpha/(2\pi)]$ & Status \\
\midrule
0 & $0$     & $0$           & ---     & $\Sigma(0)=0$ structural zero \\
1 & $6.96 \times 10^{-4}$  & $6.96 \times 10^{-4}$  & 1.074  & 99\% of final \\
2 & $3.76 \times 10^{-6}$  & $7.00 \times 10^{-4}$  & 1.080  & \\
3 & $2.85 \times 10^{-6}$  & $7.02 \times 10^{-4}$  & 1.084  & \\
4 & $1.34 \times 10^{-7}$  & $7.025 \times 10^{-4}$ & 1.084  & \\
5 & $1.25 \times 10^{-7}$  & $7.027 \times 10^{-4}$ & 1.084  & \\
6 & $1.25 \times 10^{-8}$  & $7.027 \times 10^{-4}$ & 1.084  & \\
7 & $1.36 \times 10^{-8}$  & $7.027 \times 10^{-4}$ & 1.084  & \\
8 & $2.00 \times 10^{-9}$  & $7.027 \times 10^{-4}$ & 1.084  & \\
\bottomrule
\end{tabular}
\end{table}

Three structural features are visible:
\begin{enumerate}
\item \textbf{Rapid convergence.}  The $n_{\mathrm{int}} = 1$ level
      contributes 99\% of the final value.  Each subsequent allowed level
      pair contributes roughly $100\times$ less than the previous one.
\item \textbf{Vertex parity filtering.}
      The $n_{\mathrm{int}} = 0$ contribution vanishes by
      Theorem~\ref{thm:self_energy_zero} (the loop-photon vertex at
      $n_{\mathrm{ext}} = 1$, $n_{\mathrm{int}} = 0$ requires
      $q_{\mathrm{loop}} = 1$ and $1 + 0 + 1 = 2$ is even, forbidden).
      The dominant contribution comes from $n_{\mathrm{int}} = 1$
      (the nearest allowed level to the external state).
      Higher even-$n_{\mathrm{int}}$ levels contribute but are
      suppressed relative to odd-$n_{\mathrm{int}}$ neighbors.
\item \textbf{Curvature correction.}  The ratio
      $F_2 / [\alpha/(2\pi)]$ converges to $1.084$, not to~$1$.
\end{enumerate}

\subsection{Headline result}

At $n_{\max} = 8$ (converged to 5 significant figures):
\begin{equation}
  \frac{F_2}{\alpha/(2\pi)} = 1.084,
  \label{eq:F2_ratio}
\end{equation}
with $B = 7.027 \times 10^{-4}$ and
$V_{\mathrm{magnetic}} = 0.5579$.

The anomalous magnetic moment on unit $S^3$ exceeds the flat-space
Schwinger value by approximately 8.4\%.  This excess is a
curvature correction: on a three-sphere of radius~$R$, the electron
propagator samples a compact geometry where the shortest-wavelength
virtual photon modes are modified relative to flat space.  In the
flat-space limit $R \to \infty$, the curvature correction vanishes
and $F_2 / [\alpha/(2\pi)] \to 1$, recovering the Schwinger
result~\cite{schwinger1948} exactly.

\subsection{Mode dependence}
\label{sec:mode_dependence}

The anomalous magnetic moment depends strongly on the external electron
mode.  Table~\ref{tab:mode_dependence} shows $F_2/[\alpha/(2\pi)]$
computed at $n_{\mathrm{ext}} = 1, \ldots, 5$.

\begin{table}[h]
\centering
\caption{Mode-dependent anomalous magnetic moment on unit $S^3$.
Each row reports the tree-level magnetic coupling $V_{\mathrm{mag}}$,
the one-loop correction $B$, and the normalized form factor ratio.
The $n_{\mathrm{ext}} = 1$ result uses $n_{\max} = 12$ (converged
to 5 digits); $n_{\mathrm{ext}} = 2$--$5$ use $n_{\max} = 5$
(converged to 3 digits via $n^{-7}$ power-law tail).
Exact algebraic forms for $V_{\mathrm{mag}}$ and the dominant
$B(n_{\mathrm{int}}=1)$ are available at each $n_{\mathrm{ext}}$;
all expressions are sums of square roots with rational coefficients
(no transcendentals).}
\label{tab:mode_dependence}
\begin{tabular}{@{}cccccr@{}}
\toprule
$n_{\mathrm{ext}}$ & $\lambda_{\mathrm{ext}}$
  & $V_{\mathrm{mag}}$ & $B$
  & $F_2 / [\alpha/(2\pi)]$ & vs.\ Schwinger \\
\midrule
1 & $5/2$   & $0.5579$ & $7.027 \times 10^{-4}$ & $1.084$ & $+8.4\%$ \\
2 & $7/2$   & $0.3893$ & $2.772 \times 10^{-4}$ & $0.613$ & $-39\%$ \\
3 & $9/2$   & $0.3001$ & $1.296 \times 10^{-4}$ & $0.370$ & $-63\%$ \\
4 & $11/2$  & $0.2445$ & $6.940 \times 10^{-5}$ & $0.244$ & $-76\%$ \\
5 & $13/2$  & $0.2064$ & $4.139 \times 10^{-5}$ & $0.173$ & $-83\%$ \\
\bottomrule
\end{tabular}
\end{table}

The physical mechanism is that the loop correction $B$ drops faster with
$n_{\mathrm{ext}}$ than the tree-level coupling $V_{\mathrm{mag}}$.
Across the five modes, $B$ spans a factor of $17\times$ while
$V_{\mathrm{mag}}$ spans only $2.7\times$.  The tree-level amplitude
follows $V_{\mathrm{mag}} \to (4/3)/|\lambda|$ asymptotically
(Richardson-extrapolated to 4-digit agreement with $4/3$), while
the loop correction decays as a steeper power of $|\lambda|$.
Higher-mode external electrons are ``heavier'' relative to the
curvature scale ($\lambda = n + 3/2$ sets the effective mass), and
the loop integral is progressively suppressed.

\medskip
\noindent\textbf{Comparison with Parker--Toms.}
The leading curvature correction to the anomalous magnetic moment in a
general curved spacetime is~\cite{parker1980}:
\begin{equation}
  \frac{F_2}{\alpha/(2\pi)} = 1 + \frac{R_{\mathrm{scalar}}}{12\,|\lambda|^2}
  + O(|\lambda|^{-4}),
  \label{eq:parker_toms}
\end{equation}
where $R_{\mathrm{scalar}} = 6$ on unit $S^3$ and $|\lambda|$ is the
Dirac eigenvalue of the external state.  At $n_{\mathrm{ext}} = 1$
($|\lambda| = 5/2$), this predicts $1 + 6/(12 \cdot 25/4) = 1 + 2/25
= 1.080$, which matches the computed $1.084$ within 0.4\%.  The
expansion parameter is
$\xi = R_{\mathrm{scalar}}/(12\,|\lambda|^2) \approx 0.08$ at
$n_{\mathrm{ext}} = 1$, small enough for the leading term to dominate.

However, the perturbative expansion in $1/|\lambda|^2$ diverges badly
for the full mode-dependent curve: a two-term fit gives
$c_1 \approx -20$, far from the Parker--Toms $c_1 = 1/2$.  The
discrepancy arises because the expansion~\eqref{eq:parker_toms} applies
to a \emph{single external mode at fixed curvature}, treating $R/\lambda^2$
as the small parameter.  When we vary $n_{\mathrm{ext}}$ at fixed $R = 1$,
we change not only $|\lambda|$ but also the angular structure of
\emph{every} CG coefficient in the vertex amplitude and the internal
sum.  The resulting mode dependence is non-perturbative in $1/|\lambda|^2$.

The five computed values are well described by a power law:
\begin{equation}
  \frac{F_2}{\alpha/(2\pi)} = (5.91 \pm 0.36)\;|\lambda|^{-1.84 \pm 0.06}.
  \label{eq:mode_power_law}
\end{equation}
The fitted exponent is $2.8\sigma$ from $-2$; the forced $p = -2$ fit
has twice the RMS residual.  Analysis of the dominant internal-mode
contribution ($n_{\mathrm{int}} = 1$) shows its local log-log slope
converging toward $-2$ ($-2.57 \to -2.26 \to -2.16 \to -2.11$ across
$n_{\mathrm{ext}} = 1, \ldots, 5$), but higher internal modes
contribute an increasing fraction at larger $n_{\mathrm{ext}}$
($99\%$ at $n_{\mathrm{ext}} = 1$ vs.\ $69\%$ at $n_{\mathrm{ext}} = 3$),
pulling the effective exponent above $-2$.  Whether the true asymptotic
exponent is exactly $-2$ (with finite-curvature corrections) or a
distinct value remains an open question.

The power law implies $F_2 \to 0$ as $|\lambda| \to \infty$ on unit $S^3$.
This is not inconsistent with the flat-space Schwinger limit: the
flat-space limit is $R \to \infty$ at fixed physical mass (requiring
$n \sim m R \to \infty$ simultaneously), not $|\lambda| \to \infty$ on
a fixed-size sphere.  Taking $|\lambda|$ large at fixed $R = 1$
corresponds to a heavy particle on a small sphere, where form-factor
suppression is expected.

\medskip
\noindent\textbf{Verification:} The computation uses exact
\texttt{sympy} Clebsch--Gordan coefficients at every vertex, with
no numerical approximation in the angular algebra.  The propagator
denominators are exact rationals ($|\lambda_n|^4$ and $\mu_q$ from
Eqs.~\eqref{eq:dirac_spectrum} and~\eqref{eq:hodge1_spectrum}).
Computation scripts: \texttt{debug/alpha\_g\_minus\_2\_vertex.py},
\texttt{debug/alpha\_g\_minus\_2\_curvature\_fit.py}.

\subsection{Curvature expansion coefficients}
\label{sec:curvature_coefficients}

The Parker--Toms expansion~\eqref{eq:parker_toms} at $n_{\mathrm{ext}}=1$
provides a high-precision extraction of the curvature coefficients.
Writing
\begin{equation}
  \frac{F_2}{\alpha/(2\pi)} = 1 + c_1 x + c_2 x^2 + c_3 x^3 + \cdots,
  \qquad x \equiv \frac{1}{|\lambda|^2} = \frac{4}{25}
  \label{eq:curvature_expansion}
\end{equation}
at $n_{\mathrm{ext}} = 1$ ($|\lambda| = 5/2$), the leading coefficient
$c_1 = R_{\mathrm{scalar}}/12 = 1/2$ follows from the Parker--Toms
theorem~\cite{parker1980} for a Dirac field on unit~$S^3$.

The converged $n_{\mathrm{ext}}=1$ spectral sum ($n_{\mathrm{int}} = 0
\ldots 25$ with power-law tail correction, 13 significant figures)
gives a corrected ratio of $1.0844529226552$, hence
$\delta \equiv F_2/[\alpha/(2\pi)] - 1 = 0.0844529226552$.
Subtracting the leading term $c_1 x = 0.08$ and dividing by~$x^2$:
\begin{equation}
  c_2^{\mathrm{apparent}} = \frac{\delta - c_1 x}{x^2}
  = 0.173942291220598 \pm 10^{-12}.
  \label{eq:c2_apparent}
\end{equation}
By the T9 theorem (Theorem~\ref{thm:T9}), one-loop quantities on~$S^3$
are polynomials in~$\pi^2$ with rational coefficients; hence
$c_2 = a + b\pi^2$ for rationals~$a$, $b$.

PSLQ identification against the Paper~2 spectral invariants $B = 42$,
$F = \pi^2/6$, $\Delta = 1/40$~\cite{paper2} yields
\begin{equation}
  \boxed{c_2
    = \frac{2 - B\Delta - F\Delta - F/B}{5}
    = \frac{19}{100} - \frac{41\pi^2}{25200}\,,}
  \label{eq:c2_identification}
\end{equation}
numerically $0.173942310300$.  The match to~\eqref{eq:c2_apparent}
is 8 digits (residual $1.9 \times 10^{-8}$), compared with 5.5~digits
for the next-best candidate $(6\pi^2 - 58)/7$ and 3~digits for the
purely rational~$25/144$.

\medskip
\noindent\textbf{Structural decomposition.}
The three Paper~2 invariants enter~\eqref{eq:c2_identification}
through three bilinear combinations:
\begin{equation}
  B\Delta = \frac{42}{40} = \frac{21}{20}, \qquad
  F\Delta = \frac{\pi^2}{240}, \qquad
  \frac{F}{B} = \frac{\pi^2}{252}.
\end{equation}
The numerator $2 - B\Delta - F\Delta - F/B
  = \frac{19}{20} - \frac{41\pi^2}{5040}$
is rational plus a single~$\pi^2$ term, consistent with the T9
constraint.  The denominator~5 is a simple integer.

\medskip
\noindent\textbf{High-precision $c_3$ extraction.}
Extending the $n_{\mathrm{ext}}=1$ spectral sum to $n_{\mathrm{int}}=50$
with interleaved even/odd power-law tail correction
(Hurwitz zeta analytic tail; $p_{\mathrm{even}} \approx 7.62$,
$p_{\mathrm{odd}} \approx 7.71$) gives a converged ratio of
$1.0844529207082$, hence $\delta = 0.0844529207082$.
The residual after subtracting $c_1 x + c_2 x^2$ is
$-2.44 \times 10^{-9}$, yielding
\begin{equation}
  c_3 = \frac{\delta - c_1 x - c_2 x^2}{x^3}
       = -5.946(3) \times 10^{-7},
  \label{eq:c3_numerical}
\end{equation}
nonzero at $200.9\,\sigma$ (uncertainty from the tail-correction power-law
fit).  The convergence is slow: the estimate drifts by $\sim 10^{-8}$
per five internal levels at $n_{\mathrm{int}}=50$, so the true asymptote
lies near $-5.95$ to $-5.97 \times 10^{-7}$.  The ratio
$|c_3 x^3| / |c_2 x^2| \approx 5.4 \times 10^{-6}$ confirms the
expansion is rapidly converging but \emph{does not} terminate at
second order.  PSLQ identification against the T9 basis
$\{1, \pi^2, \pi^4, B\Delta, F\Delta, F/B, c_2, c_2^2, c_1 c_2,
\Delta, \Delta^2, B\Delta^2, F\Delta^2, F^2/B\}$
at $n_{\mathrm{int}}=50$ finds no relation with integer coefficients
bounded by $10^4$; $c_3$ is not expressible in these invariants at
current precision.

\medskip
\noindent\textbf{Multi-$n_{\mathrm{ext}}$ obstruction.}
The curvature coefficients in~\eqref{eq:curvature_expansion} are
defined for the $j = 1/2$ sector of the external Dirac mode.  At
$n_{\mathrm{ext}} \ge 2$, the Dirac level carries multiple total
angular momentum sectors ($j = 1/2, 3/2, \ldots, n_{\mathrm{ext}}+1/2$)
with distinct form factors.  The $j = 1/2$ component is a
$2/[(n_{\mathrm{ext}}+1)(n_{\mathrm{ext}}+2)]$ fraction of the total
degeneracy, shrinking as $\sim 1/n^2$; extracting universal curvature
coefficients from a full trace requires Wigner--Eckart decomposition
into multipole form factors, which is not yet implemented.
Consequently, the high-precision extraction is currently restricted to
$n_{\mathrm{ext}} = 1$, where $j = 1/2$ is the unique sector.

\medskip
\noindent\textbf{Paper~2 bridge.}
Since $\alpha$ cancels exactly in the ratio $F_2/[\alpha/(2\pi)]$, the
curvature coefficients $c_1$, $c_2$ are pure geometric invariants of the
Dirac spectral sum on~$S^3$.  The appearance of all three Paper~2
invariants ($B$, $F$, $\Delta$) in~$c_2$ provides a concrete numerical
bridge between the $\alpha$ construction (Paper~2) and the QED vertex
structure (this paper): the same spectral objects that compose
$K = \pi(B + F - \Delta)$ also control the curvature dependence of
the one-loop anomalous magnetic moment on~$S^3$.

Computation scripts: \texttt{debug/g2\_c2\_verification.py},
\texttt{debug/g2\_c2\_diagnostic.py}.

% ===================================================================
\section{One-Loop Vacuum Structure}
\label{sec:one_loop}
% ===================================================================

The one-loop QED effective action involves traces of $D^2$.
The Seeley--DeWitt heat kernel expansion on unit $S^3$ gives
\begin{equation}
  a_0 = a_1 = \sqrt{\pi}, \qquad a_2 = \sqrt{\pi}/8
  \label{eq:seeley_dewitt}
\end{equation}
(exact in \texttt{sympy}, computed from the Dirac spectral data).
The vacuum polarization coefficient and QED beta function follow:
\begin{equation}
  \Pi = \frac{1}{48\pi^2}, \qquad
  \beta(\alpha) = \frac{2\alpha^2}{3\pi}.
  \label{eq:one_loop}
\end{equation}
Both reproduce the standard flat-space one-loop QED results from
$S^3$ spectral data alone, confirming the flat-space limit of the
spectral framework at one loop.

% ===================================================================
\section{Two-Loop Irreducible Constant: $S_{\min}$}
\label{sec:smin}
% ===================================================================

The CG-weighted two-loop sunset sum is:
\begin{equation}
  S_{\min} = \sum_{k=1}^{\infty} T(k)^2, \qquad
  T(k) = 2\,\zeta(2, k + \tfrac{3}{2})
       - \tfrac{1}{2}\,\zeta(4, k + \tfrac{3}{2}).
  \label{eq:S_min}
\end{equation}
This is a depth-2 multiple Hurwitz zeta value at half-integer shift
$a = 3/2$, intrinsic to the Dirac spectrum on $S^3$.

\subsection{200-digit computation}

$S_{\min}$ is computed to 200 verified digits using
\texttt{mpmath.nsum} with Levin $u$-transform acceleration.
The first 80 digits agree with the Sprint~5 three-method verification
(direct summation + explicit tail; Levin $u$-transform; Euler--Maclaurin
26-term asymptotic):
\begin{equation}
  S_{\min} = 2.47993\,69380\,34222\,55441\,35795\,00082\,93821\,44688\ldots
  \label{eq:S_min_value}
\end{equation}

\subsection{Extended PSLQ irreducibility}

A 100-element PSLQ basis was constructed at 200 dps, including:
\begin{itemize}
\item Standard: $\{1, \pi^2, \pi^4, \pi^6, \pi^8, \zeta(3), \zeta(5),
      \zeta(7), \zeta(9)\}$
\item Products: $\{\pi^2 \zeta(3), \pi^2 \zeta(5), \pi^4 \zeta(3),
      \zeta(3)^2, \zeta(3)\zeta(5)\}$
\item Catalan/Dirichlet: $\{G, \beta(3), \beta(4), G^2,
      G\pi^2, \beta(4)\pi^2, G \cdot \beta(4)\}$ and all
      cross-products with odd zeta
\item Euler sums: $\{s_{2,3}, s_{3,2}\}$
\item Tornheim--Witten: $\{T(2,2,2), T(2,2,4)\}$
\item Double Hurwitz at quarter-integer shifts:
      $\{\zeta(4,1/4), \zeta(4,3/4),$ products$\}$
\item Hurwitz at $3/2$: $\{\zeta(s, 3/2)\}$ for $s = 2, \ldots, 6$
      and products
\item $D_{\mathrm{even}}(4)$, $D_{\mathrm{odd}}(4)$, and their
      products with standard constants
\item Polygamma: $\{\psi^{(1)}(3/2), \psi^{(3)}(3/2)\}$ and products
\item Polylogarithm: $\{\mathrm{Li}_4(1/2)\}$ and cross-products
\item Clausen function: $\mathrm{Cl}_2(\pi/3)$
\item Euler--Mascheroni: $\gamma$
\end{itemize}

All PSLQ attempts return no integer relation.  $S_{\min}$ is confirmed
irreducible against the most comprehensive basis tested in the
project, extending the prior 47-element basis at 150~dps.  Module:
\texttt{debug/smin\_extended\_pslq.py}; 8 fast + 2 slow tests in
\texttt{tests/test\_smin\_extended.py}.

\subsection{Inner photon sum structure}

The inner photon sum $I(n_1, n_2) = \sum_{q\,\mathrm{allowed}}
W(n_1, n_2, q) \cdot d_q^T / \mu_q^p$ (at $p=1$: $d_q^T/\mu_q = 1$)
counts the total CG-weighted vertex channels.  Three structural
properties: (i) $I(0, n_2) = 0$ for all $n_2$ (the structural zero:
vertex parity at $n_{\mathrm{ext}}=0$ forces $2n_2$ odd, impossible);
(ii) $I(n_1, n_2) = I(n_2, n_1)$ (symmetric); (iii) $I(n, n) = 0$
for $n = 0, 1$ (self-coupling vanishes at the lowest levels).

% ===================================================================
\section{Three-Loop Results}
\label{sec:three_loop}
% ===================================================================

\subsection{Factorized $O(N^3)$ algorithm}

The three-loop iterated sunset has chain topology: three electron
lines $(n_1, n_2, n_3)$ connected by two photon lines $(q_1, q_2)$,
with vertex selection at each junction.  The chain topology permits
factorization into partial sums:
\begin{equation}
  S^{(3)} = \sum_{n_2=0}^{N}
    \frac{g_{n_2}}{|\lambda_{n_2}|^a}
    \cdot L(n_2) \cdot R(n_2),
  \label{eq:three_loop_factorized}
\end{equation}
where
\begin{equation}
  L(n_2) = \sum_{\substack{n_1, q_1 \\ \text{allowed}}}
    \frac{W(n_1, n_2, q_1) \; g_{n_1} \; d_{q_1}^T}
         {|\lambda_{n_1}|^a \; \mu_{q_1}^p}, \qquad
  R(n_2) = \sum_{\substack{n_3, q_2 \\ \text{allowed}}}
    \frac{W(n_2, n_3, q_2) \; g_{n_3} \; d_{q_2}^T}
         {|\lambda_{n_3}|^a \; \mu_{q_2}^p}.
  \label{eq:LR_partial}
\end{equation}
$W(n_1, n_2, q)$ is NOT symmetric in $(n_1, n_2)$, so $L$ and $R$
are computed independently.  This reduces the five-fold sum
$O(N^5)$ to $O(N^3)$ (each of $L$, $R$ is $O(N^2)$ precomputed,
then the outer sum is $O(N)$).

\noindent\textbf{Verification:} The factorized algorithm matches the
direct $O(N^5)$ sum to $< 10^{-78}$ at $n_{\max} = 10, 15$ across
four parameter combinations (default $a=4,p=1$; vertex-restricted;
higher exponents $a=6,p=2$; with and without CG weights).  The
factorized algorithm at $n_{\max} = 50$ completes in $< 60$ seconds.
Tests: 10 in \texttt{TestFactorizedMatchesDirect} and
\texttt{TestFactorizedConvergence} (all passing).

\subsection{Convergence analysis}

At default exponents ($a = 4$, $p = 1$) with CG weights, the
three-loop CG-weighted sum converges as a power law:
\begin{equation}
  \Delta S^{(3)}(N) \approx 270 \cdot N^{-1.31},
  \label{eq:convergence_rate}
\end{equation}
fitted over $N \in [20, 120]$.  The exponent $\alpha \approx -1.31$
confirms convergence ($|\alpha| > 1$) but is too slow for practical
PSLQ identification: at $n_{\max} = 100$, only $\sim$1--2 reliable
digits are available.  The sum has not converged sufficiently for PSLQ
at the physical exponents.  For higher exponents (e.g., $a = 8$,
$p = 2$), the sum converges faster and PSLQ was attempted---see below.

\subsection{PSLQ identification attempts}

At the fast-converging exponents $a = 8$, $p = 2$, approximately 20
reliable digits are available at $n_{\max} = 50$.  PSLQ with an
18-element depth-3 MZV basis (including $S_{\min}$, $\zeta(3)^2$,
$\pi^2 S_{\min}$, $G \cdot S_{\min}$, and all cross-products with
$\pi^2$, $\zeta(3)$, $G$, $\beta(4)$) returns no relation.

The unrestricted three-loop sum factorizes exactly as $D(a)^3$: at
$a = 4$, $D(4)^3 = (\pi^2 - \pi^4/12)^3 \approx 5.379$, purely
$\pi^{\mathrm{even}}$.

% ===================================================================
\section{Depth-$k$ Tower}
\label{sec:depth_k}
% ===================================================================

\begin{proposition}[Depth-$k$ tower]
\label{prop:depth_k}
At $k$ loops on $S^3$ with vertex restrictions and CG weights:
\begin{itemize}
\item $k = 1$: $\pi^{\mathrm{even}}$ only
      (Theorem~\ref{thm:T9}, proven).
\item $k = 2$: irreducible $S_{\min}$
      ($100$-element PSLQ at 200~dps fails;
      Sec.~\ref{sec:smin}).
\item $k = 3$: new constant $S^{(3)}$ independent of $S_{\min}$
      (PSLQ with $S_{\min}$ in basis fails at
      fast-converging exponents).
\end{itemize}
Each loop order produces a genuinely new transcendental constant through
nested vertex-parity filtration.
\end{proposition}

The mechanism: each vertex coupling creates one level of Hurwitz nesting.
One vertex produces depth-2 (the min-weight sum in $S_{\min}$).
Two vertices produce depth-3 (nested min-weights in $S^{(3)}$).
The prediction extends: $k$ vertices should produce depth-$(k+1)$
multiple Hurwitz zeta values.  This is the $S^3$ analog of the
increasing motivic complexity observed in flat-space multi-loop Feynman
integrals~\cite{laporta2002,bailey2001}.

% ===================================================================
\section{Fine-Structure Euler Sum Cancellation}
\label{sec:euler_cancel}
% ===================================================================

The Dirac Dirichlet series $D(s)$ studied in the preceding sections
sums over the \emph{free} Camporesi--Higuchi spectrum with uniform
degeneracy weights~$g_n$.  A complementary probe arises from the
\emph{exact} Dirac hydrogen spectrum, where the degeneracy-weighted
energy expansion in powers of $(Z\alpha)^2$ generates Dirichlet sums
with state-dependent coefficients that mix harmonic numbers of varying
depth.

\subsection{Setup}

The exact Dirac energy for quantum numbers $(n,j)$ is
\begin{equation}
  E_{nj} = mc^2 \biggl(
    1 + \frac{(Z\alpha)^2}
    {\bigl(n_r + \sqrt{\kappa^2 - (Z\alpha)^2}\bigr)^2}
  \biggr)^{\!-1/2} - mc^2\,,
\end{equation}
where $\kappa = j + \frac{1}{2}$ and $n_r = n - \kappa$.
Expanding in powers of $x = (Z\alpha)^2$,
\begin{equation}
  \sum_j d(n,j)\, \frac{E_{nj}}{mc^2}
  = \sum_{p=1}^{\infty} c_p(n)\, x^p\,,
\end{equation}
where $d(n,j) = 2(2j+1)$ for $j < n - \tfrac{1}{2}$ and
$d(n,j) = 2j+1$ for $j = n - \tfrac{1}{2}$.
The degeneracy-weighted Dirichlet sums are
\begin{equation}
  D_p \;=\; \sum_{n=1}^{\infty} c_p(n)\,.
\end{equation}

\subsection{Closed forms for $c_p(n)$}

Symbolic expansion of the exact Dirac formula and summation over $j$
gives closed forms involving generalized harmonic numbers
$H_{n-1}^{(r)} = \sum_{k=1}^{n-1} k^{-r}$:
\begin{align}
  c_2(n) &= -\frac{5n - 4}{4n^3}\,, \\[3pt]
  c_3(n) &= \frac{19n-20}{8n^5}
    - \frac{3}{2}\,\frac{H_{n-1}}{n^4}
    - \frac{1}{2}\,\frac{H_{n-1}^{(2)}}{n^3}\,.
\end{align}
At order $p = 2$ and $p = 3$, the sums $D_2$ and $D_3$ collapse to
pure single-zeta values:
\begin{equation}
  D_2 = -\frac{5}{4}\,\zeta(2) + \zeta(3)\,,
  \qquad
  D_3 = \frac{19}{8}\,\zeta(4) - \frac{11}{4}\,\zeta(5)\,.
\end{equation}

\subsection{$\zeta(3)$ complementarity}

The $p = 2$ coefficient defines the \emph{fine-structure shell sum}
\begin{equation}
  \mathcal{S}(n) \;=\; \sum_j d(n,j)\Bigl(\frac{n}{j+\frac{1}{2}}
  - \frac{3}{4}\Bigr) \;=\; \frac{n(5n-4)}{2}\,,
\end{equation}
so that $c_2(n) = -\mathcal{S}(n)/(2n^4)$.
This decomposes into a \emph{conformal} piece $-3n^2/2$ (from the
scalar curvature $R/8 = 3/4$ on unit~$S^3$) and a \emph{quantum defect}
piece $2n(2n-1)$, the double hexagonal number.

In the Fock convention ($n \ge 1$), the single-chirality Dirac mode
degeneracy is $g_n^{\mathrm{Dirac}} = 2n(n+1)$.

\begin{theorem}[$\zeta(3)$ complementarity]
\label{thm:zeta3_complement}
For all $n \ge 1$,
\begin{equation}
\label{eq:shell_complement}
  \mathcal{S}(n) + g_n^{\mathrm{Dirac}} \;=\; \frac{9n^2}{2}
  \;=\; |\lambda_0|^2 \times n^2_{\mathrm{Schr}}\,,
\end{equation}
where $|\lambda_0| = 3/2$ is the lowest Dirac eigenvalue on~$S^3$
and $n^2_{\mathrm{Schr}} = 2n^2$ is the Schr\"odinger degeneracy
(including spin).
At the Dirichlet series level,
\begin{equation}
\label{eq:dirichlet_complement}
  D_{\mathcal{S}}(s) + D_{g}(s) \;=\; \frac{9}{2}\,\zeta(s{-}2)
  \qquad \text{for all } s\,,
\end{equation}
where $D_{\mathcal{S}}(s) = \sum_{n \ge 1} \mathcal{S}(n)\,n^{-s}$
and $D_{g}(s) = \sum_{n \ge 1} g_n^{\mathrm{Dirac}}\,n^{-s}$.
The $\zeta(s{-}1)$ terms cancel identically.
\end{theorem}

\begin{proof}
$\mathcal{S}(n) = 5n^2/2 - 2n$ and $g_n^{\mathrm{Dirac}} = 2n^2 + 2n$;
their sum is $9n^2/2$.  Therefore
$D_{\mathcal{S}}(s) = \tfrac{5}{2}\,\zeta(s{-}2) - 2\,\zeta(s{-}1)$
and $D_{g}(s) = 2\,\zeta(s{-}2) + 2\,\zeta(s{-}1)$; summing gives
$\tfrac{9}{2}\,\zeta(s{-}2)$.
\end{proof}

The cancellation of $\zeta(s{-}1)$ is the physical content: at odd~$s$,
$\zeta(s{-}1)$ is even-zeta ($\pi^{\mathrm{even}}$) and harmless, but
at even~$s$, $\zeta(s{-}1)$ carries odd-zeta content ($\zeta(3)$,
$\zeta(5)$, \ldots).  At $s = d_{\max} = 4$:
\begin{equation}
  D_{\mathcal{S}}(4) = \frac{5}{2}\,\frac{\pi^2}{6} - 2\zeta(3)
  = \frac{5F}{2} - 2\zeta(3)\,,
\end{equation}
confirming that the quantum defect (the $-2n$ piece of $\mathcal{S}$)
is the physical mechanism injecting $\zeta(3)$ into the fine-structure
spectrum---with sign opposite to the $+2\zeta(3)$ that appears in
$D_{g}(4) = 2\zeta(2) + 2\zeta(3)$.  Their sum
$\tfrac{9}{2}\zeta(2) = 3\pi^2/4$ is purely $\pi^{\mathrm{even}}$,
returning to the second-order (scalar) sector.

The prefactor $9/2 = |\lambda_0|^2 \times 2 =
(\text{Dirac mass gap})^2 \times (\text{spinor rank})$
links through the Lichnerowicz formula $D^2 = \Delta + R/4$
back to the $S^3$ geometry: the complementarity sum
recovers the scalar Laplacian sector exactly, closing the chain
from the packing construction through $S^3$ and the Dirac operator
to the fine-structure Dirichlet series.

This is Theorem~\ref{thm:T9} expressed in physical terms:
the $D^2$ spectral zeta is even-zeta only \emph{because} the
fine-structure energy distribution and the Dirac mode counting
are transcendentally complementary.
Paper~18's taxonomy predicted this separation: calibration
($\pi^{\mathrm{even}}$ from the second-order curvature $R/8$) versus
spinor-intrinsic (mixed zeta from the first-order quantum defect).

\subsection{$D_4$ at weight 7: product zeta survives}

At order $p = 4$,
\begin{align}
  c_4(n) &= -\frac{5(41n - 40)}{64n^7}
    + \frac{15}{4}\,\frac{H_{n-1}}{n^6}
    - \frac{1}{4}\,\frac{H_{n-1}^{(2)}}{n^5}
    \notag \\
    &\quad - \frac{3}{4}\,\frac{H_{n-1}^{(3)}}{n^4}
    - \frac{1}{4}\,\frac{H_{n-1}^{(4)}}{n^3}\,.
\end{align}
The harmonic-number sums decompose into weight-7 Euler sums
$S_{r,s} = \sum_{n \ge 1} H_n^{(r)} / n^s$ via the identity
$H_{n-1}^{(r)} = \zeta(r) - \zeta(r,n)$ and Euler's formula
$S_{1,6} = 4\zeta(7) - \zeta(2)\zeta(5) - \zeta(3)\zeta(4)$~\cite{flajolet1998}.

\begin{observation}[Euler sum cancellation at weight~7]
\label{obs:euler_cancel}
At 200~dps, PSLQ identifies
\begin{equation}
\label{eq:D4_decomp}
  D_4 = -\frac{205}{64}\,\zeta(6)
  + \frac{71}{8}\,\zeta(7)
  - \frac{9}{2}\,\zeta(3)\zeta(4)\,,
\end{equation}
with residual $< 10^{-195}$.  The product $\zeta(2)\zeta(5)$ cancels
\emph{algebraically}: its coefficient vanishes exactly (verified in
exact rational arithmetic from the Euler sum decomposition), while
$\zeta(3)\zeta(4)$ survives with coefficient $-9/2$.
\end{observation}

This breaks the pure-single-zeta pattern: $D_2$ and $D_3$ involve
only $\zeta(s)$ values, whereas $D_4$ introduces the first zeta
product.  The four weight-7 Euler sums, independently identified by
PSLQ, are
\begin{center}
\begin{tabular}{lccc}
\hline
Sum & $\zeta(7)$ & $\zeta(2)\zeta(5)$ & $\zeta(3)\zeta(4)$ \\
\hline
$S_{1,6}$ & $4$ & $-1$ & $-1$ \\
$S_{2,5}$ & $-10$ & $5$ & $2$ \\
$S_{3,4}$ & $18$ & $-10$ & $0$ \\
$S_{4,3}$ & $-17$ & $10$ & $1$ \\
$S_{5,2}$ & $11$ & $-4$ & $-2$ \\
\hline
\end{tabular}
\end{center}
The stuffle relations $S_{r,s} + S_{s,r} = \zeta(r)\zeta(s) + \zeta(r+s)$
are satisfied to $< 10^{-200}$.

\subsection{$D_5$ at weight 9: product survival rule}

At order $p = 5$,
\begin{align}
  c_5(n) &= \frac{7(71n - 72)}{128\,n^9}
    - \frac{105}{16}\,\frac{H_{n-1}}{n^8}
    + \frac{45}{16}\,\frac{H_{n-1}^{(2)}}{n^7}
    + \frac{5}{4}\,\frac{H_{n-1}^{(3)}}{n^6}
    \notag \\
    &\quad - \frac{3}{8}\,\frac{H_{n-1}^{(4)}}{n^5}
    - \frac{15}{32}\,\frac{H_{n-1}^{(5)}}{n^4}
    - \frac{5}{32}\,\frac{H_{n-1}^{(6)}}{n^3}\,,
\end{align}
verified as exact rational equality against direct sympy expansion for
$n = 1, \ldots, 15$.
The Dirichlet sum decomposes via weight-9 Euler sums
$S_{r,s}$ for $r + s = 9$ (computed via Hurwitz zeta to 250~dps,
stuffle relations verified to $< 10^{-200}$):
\begin{center}
\begin{tabular}{lcccc}
\hline
Sum & $\zeta(9)$ & $\zeta(2)\zeta(7)$ & $\zeta(3)\zeta(6)$ & $\zeta(4)\zeta(5)$ \\
\hline
$S_{2,7}$ & $-35/2$ & $7$ & $2$ & $4$ \\
$S_{3,6}$ & $85/2$ & $-21$ & $0$ & $-6$ \\
$S_{4,5}$ & $-125/2$ & $35$ & $0$ & $5$ \\
$S_{5,4}$ & $127/2$ & $-35$ & $0$ & $-4$ \\
$S_{6,3}$ & $-83/2$ & $21$ & $1$ & $6$ \\
$S_{7,2}$ & $37/2$ & $-6$ & $-2$ & $-4$ \\
\hline
\end{tabular}
\end{center}
PSLQ at 200~dps identifies
\begin{equation}
\label{eq:D5_decomp}
  D_5 = \frac{497}{128}\,\zeta(8)
  - \frac{467}{16}\,\zeta(9)
  + \frac{385}{32}\,\zeta(3)\zeta(6)
  + \frac{75}{8}\,\zeta(4)\zeta(5)\,,
\end{equation}
with residual $< 10^{-190}$.  The product $\zeta(2)\zeta(7)$ cancels
algebraically (verified from the Euler sum collection), while both
$\zeta(3)\zeta(6)$ and $\zeta(4)\zeta(5)$ survive.  This extends the
pattern from $D_4$: product terms grow from 0 (at $D_2$, $D_3$) to 1
(at $D_4$) to 2 (at $D_5$).

\subsection{$D_6$ at weight 11: product survival rule extended}

At order $p = 6$ the weight-11 Euler sums $S_{r,s}$ for $r + s = 11$
are computed via Hurwitz zeta to 400~dps, with stuffle relations
verified to $< 10^{-300}$.  Seven nontrivial sums ($r = 1, \ldots, 8$,
$r \ne 3$) contribute through the $\beta_r$ coefficients of the
$c_6(n)$ expansion.  Individual decompositions are found by PSLQ
against the weight-11 depth-1 MZV basis
$\{\zeta(11), \zeta(2)\zeta(9), \zeta(3)\zeta(8), \zeta(4)\zeta(7),
\zeta(5)\zeta(6)\}$:
\begin{center}
\begin{tabular}{lccccc}
\hline
Sum & $\zeta(11)$ & $\zeta(2)\zeta(9)$ & $\zeta(3)\zeta(8)$ & $\zeta(4)\zeta(7)$ & $\zeta(5)\zeta(6)$ \\
\hline
$S_{1,10}$ & $6$ & $-1$ & $-1$ & $-1$ & $-1$ \\
$S_{2,9}$ & $-27$ & $9$ & $2$ & $6$ & $4$ \\
$S_{4,7}$ & $-329/2$ & $84$ & $0$ & $21$ & $4$ \\
$S_{5,6}$ & $463/2$ & $-126$ & $0$ & $-21$ & $0$ \\
$S_{6,5}$ & $-461/2$ & $126$ & $0$ & $21$ & $1$ \\
$S_{7,4}$ & $331/2$ & $-84$ & $0$ & $-20$ & $-4$ \\
$S_{8,3}$ & $-82$ & $36$ & $1$ & $15$ & $6$ \\
\hline
\end{tabular}
\end{center}
The $\zeta(3)\zeta(8)$ column has a sparse support pattern: nonzero
only for $S_{1,10}$, $S_{2,9}$, and $S_{8,3}$.

Collecting through the $\beta_r$ coefficients and the rational
$\zeta(10)$, $\zeta(11)$ parts:
\begin{equation}
\label{eq:D6_decomp}
  D_6 = -\frac{2289}{512}\,\zeta(10)
  + \frac{1589}{16}\,\zeta(11)
  - \frac{1617}{64}\,\zeta(3)\zeta(8)
  - \frac{1785}{64}\,\zeta(4)\zeta(7)
  - \frac{2065}{64}\,\zeta(5)\zeta(6)\,,
\end{equation}
verified to 62~digits against direct Euler-sum evaluation at
400~dps.  The product $\zeta(2)\zeta(9)$ cancels algebraically,
and all three surviving products $\zeta(3)\zeta(8)$,
$\zeta(4)\zeta(7)$, $\zeta(5)\zeta(6)$ are present, matching the
prediction $\max(0, \lfloor(2 \cdot 6 - 5)/2\rfloor) = 3$.

\begin{observation}[Product survival rule]
\label{obs:product_rule}
At each Sommerfeld order $p \ge 2$, the Dirichlet sum $D_p$ decomposes
into weight-$(2p{-}1)$ zeta values.  The product $\zeta(2)\zeta(2p{-}3)$
cancels algebraically at every order.  Exactly
$\max(0, \lfloor(2p{-}5)/2\rfloor)$ product terms survive, all of the
form $\zeta(a)\zeta(b)$ with $a + b = 2p{-}1$, $a$ odd $\ge 3$,
$b$ even $\ge 4$.
\end{observation}

Verified through $D_6$ ($p = 6$, weight~11).  The systematic expulsion
of $\zeta(2)$ products is driven by the $n^2$ Fock degeneracy that
weights the Sommerfeld sums.  This is the same $n^2$ that produces
$F = \zeta(2) = D_{n^2}(4)$ in the Phase~4F identification
(Paper~2~\cite{paper2}): the Fock degeneracy protects its own Dirichlet
evaluation from cross-contamination with odd-zeta products.

\subsection{Transcendental structure}

Substituting $\zeta(6) = \pi^6/945$ and $\zeta(4) = \pi^4/90$,
equation~\eqref{eq:D4_decomp} becomes
\begin{equation}
\label{eq:D4_three_tier}
  D_4 = -\frac{41\pi^6}{12096}
  + \frac{71}{8}\,\zeta(7)
  - \frac{\pi^4}{20}\,\zeta(3)\,.
\end{equation}
This is a three-tier decomposition: $\pi^6$ (weight-6 even-zeta),
$\zeta(7)$ (weight-7 odd-zeta), and the mixed product
$\pi^4 \cdot \zeta(3)$ (weight-4 even $\times$ weight-3 odd).
In Paper~18's operator-order taxonomy, $\pi^{\mathrm{even}}$ comes
from 2nd-order operators and $\zeta(\mathrm{odd})$ from 1st-order
operators.  The mixed product $\pi^4 \cdot \zeta(3)$ is the first
instance in the framework where these two tiers appear multiplicatively
in a single observable.

The $\zeta(2)\zeta(5)$ cancellation is non-trivial: four of the five
contributing Euler sums carry nonzero $\zeta(2)\zeta(5)$ coefficients
($S_{1,6}$, $S_{2,5}$, $S_{4,3}$, $S_{5,2}$), and the cancellation
emerges only in the specific linear combination that the Dirac
degeneracy weights and harmonic-number structure select.  In contrast,
$S_{3,4}$ alone is free of $\zeta(3)\zeta(4)$, but the remaining four
sums contribute $\zeta(3)\zeta(4)$ terms that do not cancel.

\subsection{K--Sommerfeld structural separation}

The product survival rule
(Observation~\ref{obs:product_rule}) raises a natural question: does the
all-orders Sommerfeld cancellation pattern explain why Paper~2's
$K = \pi(B + F - \Delta)$ has pure $\pi$-content?

PSLQ at 200~dps tests whether $K/\pi$ is a rational linear combination
of $\{D_2, D_3, D_4, D_5, D_6, 1\}$.  The result is \emph{null}: $K/\pi$ is
not in the $\mathbb{Q}$-span of the Sommerfeld sums through sixth order.
$K$ inhabits a different algebraic space from the $D_p$.

The structural reason: $K$ is composed of spectral-action ingredients ---
$B$ (truncated Casimir trace), $F = \zeta(2)$ (Fock Dirichlet at $s = 4$),
$\Delta^{-1} = g_3^{\text{Dirac}}$ (Dirac mode count) --- all of which
live in the spectral-zeta world where Theorem~\ref{thm:T9} guarantees
$\pi$-polynomial content.  The Sommerfeld $D_p$, by contrast, are sums of
\emph{physical energy coefficients} dressed with harmonic numbers
$H_{n-1}^{(r)}$, which access the full Euler--Zagier MZV ring including
irreducible odd-zeta at every order.

The $\zeta(2)$ cancellation mechanism is nonetheless a genuine bridge:
the $n^2$ Fock degeneracy that generates $F = \zeta(2)$ simultaneously
drives the systematic expulsion of $\zeta(2) \times \zeta(\text{odd})$
products from the Sommerfeld sums.  The Fock degeneracy organizes both
$K$ (through $F$) and the $D_p$ (through the cancellation pattern),
but the operator/energy distinction prevents $K$ from being a
Sommerfeld functional.

% ===================================================================
\section{Flat-Space Consistency}
\label{sec:flat_space}
% ===================================================================

On $S^3$ of radius $R$, the Dirac eigenvalues scale as
$|\lambda_n(R)| = (n + 3/2)/R$ and the Dirichlet series becomes
$D(s, R) = R^s \cdot D(s, 1)$.  The ratio $D(s,R)/R^s$ is
$R$-independent \emph{exactly}, confirming that the even/odd
$s$-parity discriminant is structural, not a finite-$R$ artifact.

Weyl's law is verified: the cumulative Dirac mode count
$N(n_{\max}) = 2(n_{\max}+1)(n_{\max}+2)(n_{\max}+3)/3$ matches the
Weyl prediction $(2/3)R^3 p_{\max}^3$ with $O(1/n_{\max})$
convergence.

The \emph{same} transcendental constants---$\zeta(3)$, Catalan~$G$,
Dirichlet $\beta(4)$---appear in both the $S^3$ spectral sums and
flat-space two-loop QED~\cite{rosner1967,laporta1996}.
Coefficient matching for the full Petermann--Sommerfield two-loop
anomalous magnetic moment $a_2 = -197/144 + \pi^2/12 + 3\zeta(3)/4 -
\pi^2\ln 2/2$~\cite{petermann1957,sommerfield1957} requires matching
specific diagram topologies and renormalization subtractions, which is
beyond the scope of spectral sums.  At one loop, the $S^3$
computation (Sec.~\ref{sec:anomalous_moment}) gives
$F_2/[\alpha/(2\pi)] = 1.084$ at $n_{\mathrm{ext}} = 1$ on unit~$S^3$,
matching the Parker--Toms leading curvature correction
$1 + R/(12|\lambda|^2) = 1.080$ within 0.4\%.  The 5-point
mode-dependent curve ($n_{\mathrm{ext}} = 1, \ldots, 5$) follows
a power law $\approx 5.91\,|\lambda|^{-1.84}$
(Table~\ref{tab:mode_dependence}), consistent with the flat-space
limit being $R \to \infty$ at fixed physical mass, not
$|\lambda| \to \infty$ at fixed~$R$.  In the proper flat-space limit,
the curvature excess vanishes, recovering the Schwinger
value~\cite{schwinger1948}.

The sunset sum scales exactly as $R^{2s_1 + 2s_2 + 2p}$ (power $= 10$
at default parameters), with the ratio $S(R)/R^{\mathrm{power}}$
$R$-independent to machine precision.  The $D(5) = 14\zeta(3) -
31\zeta(5)/2$ identification is $R$-independent, confirming that the
odd-zeta content is structural.

% ===================================================================
\section{Comprehensive Transcendental Tables}
\label{sec:tables}
% ===================================================================

\begin{table}[h]
\centering
\caption{Even/odd decomposition of $D(s)$: PSLQ at 80+ dps.}
\label{tab:D_even_odd}
\begin{tabular}{@{}clll@{}}
\toprule
$s$ & $D_{\mathrm{even}}(s)$ & $D_{\mathrm{odd}}(s)$ & $D_{\mathrm{even}} - D_{\mathrm{odd}}$ \\
\midrule
4 & $\frac{\pi^2}{2} - \frac{\pi^4}{24} - 4G + 4\beta(4)$
  & $\frac{\pi^2}{2} - \frac{\pi^4}{24} + 4G - 4\beta(4)$
  & $8(\beta(4) - G)$ \\[4pt]
5 & odd-zeta + Dirichlet
  & odd-zeta $-$ Dirichlet
  & $16(\beta(5) - \beta(3))$ \\[4pt]
6 & $\pi^{\mathrm{even}}$ + Dirichlet
  & $\pi^{\mathrm{even}}$ $-$ Dirichlet
  & $32(\beta(6) - \beta(4))$ \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{Verification of Theorem~\ref{thm:chi4}: $D_{\mathrm{even}}(s) -
D_{\mathrm{odd}}(s) = 2^{s-1}(\beta(s) - \beta(s{-}2))$.}
\label{tab:chi4_verification}
\begin{tabular}{@{}ccc@{}}
\toprule
$s$ & $2^{s-1}$ & Residual $|$LHS $-$ RHS$|$ \\
\midrule
2 & 2 & 0 (sympy) \\
3 & 4 & 0 (sympy) \\
4 & 8 & $< 10^{-100}$ \\
5 & 16 & $< 10^{-100}$ \\
6 & 32 & $< 10^{-100}$ \\
7 & 64 & $< 10^{-100}$ \\
8 & 128 & $< 10^{-100}$ \\
9 & 256 & $< 10^{-100}$ \\
10 & 512 & $< 10^{-100}$ \\
15 & 16384 & $< 10^{-100}$ \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{Three-loop factorized convergence at $a = 4$, $p = 1$, CG-weighted.}
\label{tab:three_loop_convergence}
\begin{tabular}{@{}cccc@{}}
\toprule
$n_{\max}$ & $S^{(3)}(n_{\max})$ & $\Delta$ from previous & Time (s) \\
\midrule
5  & 1.399 & --- & $< 0.1$ \\
10 & 3.741 & 2.342 & $< 0.1$ \\
15 & 5.836 & 2.095 & 0.2 \\
20 & 7.729 & 1.893 & 0.5 \\
50 & 15.23 & --- & $< 60$ \\
\bottomrule
\end{tabular}
\end{table}

% ===================================================================
\section{Graph-Native QED}
\label{sec:graph_native_qed}
% ===================================================================

The preceding sections computed QED on~$S^3$ via infinite spectral sums
over the Camporesi--Higuchi Dirac modes.  This section reports the
complementary computation: QED formulated entirely on the \emph{finite}
GeoVac graph, using no infinite sums, no regularization, and no
renormalization.  All quantities are finite matrix traces over the
Dirac-labeled graph nodes and Fock-labeled graph edges.

\subsection{Construction}

The graph-native QED infrastructure consists of four layers:
\begin{enumerate}
\item \textbf{Fock graph} (nodes = Fock states $(n,l,m)$ at $n \le n_{\max}$,
  edges = nearest-neighbor Fock ladders) with node Laplacian $L_0 = BB^T$,
  edge Laplacian $L_1 = B^TB$, and exact Hodge decomposition
  (Paper~25~\cite{paper25} vocabulary).
\item \textbf{Electron propagator} $G_e = D^{-1}$, where $D$ is the
  Dirac graph operator in the $(n, \kappa, m_j)$ basis with hopping
  parameter~$t$.  At $t = 0$, $G_e = \mathrm{diag}(2/(2n+3))$.
\item \textbf{Photon propagator} $G_\gamma = L_1^+$, the
  Moore--Penrose pseudoinverse of the edge Laplacian.  This is the
  graph analog of the Feynman-gauge photon propagator.
\item \textbf{Vertex coupling tensor} $V[a,b,e]$, built from the
  Clebsch--Gordan projection matrix $P$ that maps Dirac labels
  $(n,\kappa,m_j)$ onto Fock nodes $(n,l,m)$.
\end{enumerate}

At $n_{\max} = 2$: 10 Dirac states, 5 Fock nodes, 3 Fock edges.
At $n_{\max} = 3$: 28 Dirac states, 14 Fock nodes, 13 Fock edges.

\subsection{Vacuum polarization}

The graph vacuum polarization tensor is
\[
  \Pi_{\text{graph}}[e_1, e_2] = \sum_{a,b} V[a,b,e_1]\, G_e[a,b]\, V[b,a,e_2],
\]
the complete one-loop photon self-energy on the finite graph.
At $n_{\max} = 2$, $\mathrm{Tr}(\Pi) = 224/75$ (pure rational).
At $n_{\max} = 3$, $\mathrm{Tr}(\Pi) = 3872/735$;  the $13 \times 13$
matrix decomposes into $l$-sector blocks ($l = 0$: $2 \times 2$,
$l = 1$: $7 \times 7$, $l = 2$: $4 \times 4$) with zero cross-block
coupling.  Four entries in the $l = 2$ sector contain $\sqrt{6}$ from
CG coefficients; all others are rational.

\subsection{Self-energy and vertex correction}

The one-loop self-energy is
\[
  \Sigma[a,b] = \sum_{e,e'} G_\gamma[e,e']\, V_e \cdot V_{e'}^T,
\]
where $V_e[a,c] = V[a,c,e]$.  At $n_{\max} = 2$, $t = 0$:
$\mathrm{Tr}(\Sigma) = 44/3$; eigenvalues $\{0^{(\times 5)}, 4/3, 2^{(\times 2)},
4, 16/3\}$; positive semidefinite; Hermitian.

The one-loop vertex correction is
\[
  \Lambda[a,b] = \sum_{e',e''} G_\gamma[e',e'']\, V_{e'} \cdot G_e \cdot V_{e''}^T.
\]
At $n_{\max} = 2$, $t = 0$: $\mathrm{Tr}(\Lambda) = 32/9$; eigenvalues
$\{0^{(\times 5)}, 8/45, (28 \pm 4\sqrt{145})/45, 4/5, 4/3\}$.

The graph anomalous magnetic moment is extracted as
$F_2 = \mathrm{Tr}(\Lambda) / \mathrm{Tr}(V_{\mathrm{bare}} \cdot G_e)
= 5\sqrt{2}/3 \approx 2.357$ at $t = 0$.

At the physical coupling $t = \kappa = -1/16$, the self-energy is
\emph{identical} (the formula does not involve $G_e$), but the vertex
correction changes: $\mathrm{Tr}(\Lambda) = 16\sqrt{3}/8985 + 19255/5391
\approx 3.575$.  $\Lambda$ acquires one negative eigenvalue ($-0.447$),
becoming indefinite.  The anomalous moment shifts to
\[
  F_2(\kappa) = \frac{48\sqrt{3} + 96275}{3(15 + 16\sqrt{6} + 9616\sqrt{2})}
  \approx 2.3525,
\]
a $0.2\%$ shift from the $t = 0$ value.  $F_2(\kappa)$ remains algebraic
irrational in $\mathbb{Q}(\sqrt{2}, \sqrt{3}, \sqrt{6})$, the CG ring.

\subsection{Neumann series structure of the electron propagator}
\label{sec:neumann_series}

The coupling-dependence of $F_2(t)$ admits a transparent algebraic
explanation.  Write the Dirac graph operator as $D = \Lambda + tA$,
where $\Lambda = \mathrm{diag}(|\lambda_n|)$ is the free (diagonal)
Dirac spectrum and $A$ is the adjacency-like hopping matrix.  The
electron propagator admits a Born/Neumann expansion
\[
  G_e(t) = (\Lambda + tA)^{-1}
  = \Lambda^{-1} \sum_{k=0}^{\infty} \bigl(-t\,\Lambda^{-1}A\bigr)^k,
\]
which converges when $\rho(t\,\Lambda^{-1}A) < 1$.  The free propagator
$\Lambda^{-1} = \mathrm{diag}(2/(2n+3))$ is trivially rational.  Each
subsequent order multiplies by the matrix $-t\,\Lambda^{-1}A$, whose
entries lie in~$\mathbb{Q}(\sqrt{2},\sqrt{3},\sqrt{6})$ (the CG ring).
The expansion therefore preserves the algebraic ring at every order:
no new transcendentals enter from the coupling.

By the Cayley--Hamilton theorem, the series terminates exactly at
order~$N-1$, where $N = \dim(\text{Dirac space})$.  Consequently,
$G_e(t)$ --- and hence $F_2(t)$ --- is a \emph{rational function} of~$t$
with coefficients in the CG ring.  At the physical coupling
$t = \kappa = -1/16$, the spectral radius
$\rho(\kappa\,\Lambda^{-1}A) \approx 0.2$ at $n_{\max} = 2$,
so the first few Born orders dominate.  The $0.2\%$ shift
$F_2(\kappa)/F_2(0) \approx 0.998$ is consistent with first-order
perturbation in~$\kappa$.

This structure connects to Paper~18's exchange-constant
taxonomy~\cite{paper18}: the hopping parameter~$t$ enters $F_2$ as a
polynomial perturbation of the free value, preserving the
\textsc{intrinsic} algebraic ring at every order.  The Neumann
expansion makes explicit that the graph-native anomalous moment is a
\emph{finite rational expression} in~$\kappa$ and CG coefficients,
with no transcendental content at any truncation~$n_{\max}$.
For larger $n_{\max}$ (where direct symbolic inversion of $D$ becomes
expensive), the rapid convergence of the Born series at
$|\kappa| = 1/16$ provides an efficient perturbative alternative.

\subsection{Broken structural zero and the pendant-edge theorem}
\label{sec:broken_structural_zero}

Theorem~\ref{thm:self_energy_zero} states that $\Sigma(n_{\mathrm{ext}} = 0)
= 0$ in the continuum, by vertex parity impossibility.  On the finite
graph, this structural zero is \textbf{broken}:
\[
  \Sigma_{\text{graph}}^{\text{GS}} =
  \begin{pmatrix} 1 & 1 \\ 1 & 1 \end{pmatrix}
  \neq 0.
\]
The CG projection maps Dirac $(n,\kappa,m_j)$ states onto Fock
$(n,l,m)$ nodes, opening vertex couplings invisible to the SO(4)
channel count that enforces the continuum selection rule.

A three-layer investigation reveals the complete mechanism.

\subsubsection{Layer 1: Anatomy of the ground-state self-energy}

At $n_{\max} = 2$, the entire ground-state self-energy comes from a
single edge pair.  Let $v_0 = |1, 0, 0\rangle$ (the ground-state Fock
node) and $v_1 = |2, 0, 0\rangle$ (the first radial excitation); these
are connected by the edge~$e_0$.  All Clebsch--Gordan coefficients
equal~1 because $l = 0$ forces trivial angular projection.  Two
intermediate s-wave Dirac states ($m_j = \pm 1/2$) contribute equally.
The formula reduces to
\[
  \Sigma[a,b] = 2 \cdot G_\gamma[e_0, e_0] \cdot 1,
\]
where $G_\gamma = L_1^+$ is the photon propagator.  At $n_{\max} = 2$,
$L_1$ is a $3 \times 3$ matrix and $G_\gamma[e_0, e_0] = 1/2$,
giving $\Sigma[a,b] = 1$ for all entries of the $2 \times 2$
ground-state block.

\subsubsection{Layer 2: The pendant-edge theorem}

The anatomy at $n_{\max} = 2$ generalizes exactly to all $n_{\max}$.

The ground-state node $v_0 = |1,0,0\rangle$ is a \emph{leaf} (degree~1)
of the Fock graph at every~$n_{\max}$.  The single edge $e_0$ incident
on~$v_0$ is a \emph{pendant edge}.  The s-wave ($l = 0$) radial edges
form a tridiagonal sub-block of $L_1 = B^TB$ --- the standard discrete
Laplacian on a path graph of length $N = n_{\max} - 1$.  This path-graph
Laplacian $T_N$ has an explicitly known inverse: its $(0,0)$ entry is
\[
  T_N^{-1}[0,0] \;=\; \frac{N}{N+1}
  \;=\; \frac{n_{\max} - 1}{n_{\max}}.
\]
Because the pendant edge $e_0$ decouples from all non-radial edges
in~$L_1$ (s-wave edges share no endpoint with edges at $l \ge 1$),
$G_\gamma[e_0, e_0] = T_N^{-1}[0,0]$ exactly.

\begin{proposition}[Pendant-edge theorem for the graph self-energy]
\label{prop:pendant_edge}
On the GeoVac Fock graph at any finite $n_{\max} \ge 2$, the
graph-native ground-state self-energy satisfies
\begin{equation}
  \Sigma_{\mathrm{graph}}(\mathrm{GS})
  \;=\; \frac{2(n_{\max} - 1)}{n_{\max}},
  \label{eq:pendant_edge}
\end{equation}
where the value is exact (rational) and degenerate across both
$m_j = \pm 1/2$ ground-state components.  In particular,
\begin{equation}
  \lim_{n_{\max} \to \infty} \Sigma_{\mathrm{graph}}(\mathrm{GS}) = 2
  \;\neq\; 0.
  \label{eq:pendant_limit}
\end{equation}
The structural zero of Theorem~\ref{thm:self_energy_zero} is never
recovered in the graph limit.
\end{proposition}

\begin{proof}
The ground-state Fock node $v_0 = |1,0,0\rangle$ has degree~1 at
every~$n_{\max}$ (its only neighbor is $|2,0,0\rangle$).  The
self-energy formula $\Sigma[a,b] = \sum_{e,e'} G_\gamma[e,e']\, V_e
\cdot V_{e'}^T$ at the ground state receives contributions only from
edges incident on~$v_0$, of which there is exactly one ($e_0$).
All CG coefficients at $l = 0$ equal~1, and two Dirac intermediate
states ($m_j = \pm 1/2$) contribute, giving
$\Sigma[a,b] = 2\, G_\gamma[e_0, e_0]$.  The s-wave radial
edges form a path graph of $N = n_{\max} - 1$ edges in $L_1$,
decoupled from all $l \ge 1$ edges.  The Moore--Penrose pseudoinverse
of the path-graph Laplacian $T_N$ satisfies
$T_N^{-1}[0,0] = N/(N+1)$.  Therefore
$\Sigma_{\mathrm{graph}}(\mathrm{GS}) = 2N/(N+1)
= 2(n_{\max}-1)/n_{\max}$.
\end{proof}

\noindent\textbf{Verification:} Eq.~\eqref{eq:pendant_edge} verified
numerically for $n_{\max} = 2, 3, \ldots, 100$ (machine-precision
agreement) and symbolically (exact \texttt{sympy} rational arithmetic)
at $n_{\max} = 3, 4$.

\subsubsection{Layer 3: Selection-rule gap}

The continuum possesses \emph{two} independent protection mechanisms
that enforce $\Sigma(n_{\mathrm{ext}} = 0) = 0$:
\begin{enumerate}
\item \textbf{Vertex parity.}  The selection rule requires
  $n_1 + n_2 + q$ odd (Eq.~\eqref{eq:vertex_rule}).  At
  $n_{\mathrm{ext}} = 0$, the triangle inequality forces
  $q = n_{\mathrm{int}}$, so the sum is $2\,n_{\mathrm{int}}$
  (always even).  No allowed triple exists.
\item \textbf{SO(4) channel count.}  The CG multiplicity
  $W(0, n_{\mathrm{int}}, q) = 0$ for all~$q$.  The ground state has
  $j_R = 0$ in the $\mathrm{SU}(2)_L \times \mathrm{SU}(2)_R$
  decomposition; the right-factor triangle degenerates (one component
  fails the $\mathrm{SU}(2)_R$ triangle; the other passes all
  triangles but is killed by parity).
\end{enumerate}
The finite graph has \emph{neither} mechanism.  The graph photon lives
on edges---it is a 1-cochain, not a vector field.  The CG projection
is scalar $\mathrm{SU}(2)$, not the $\mathrm{SU}(2)_L \times
\mathrm{SU}(2)_R$ double triangle of SO(4) vector harmonics.  Both
protection mechanisms arise from the \emph{spin-1 vector nature} of
the continuum photon, which is absent on the graph.

\subsubsection{Interpretation: scalar vs.\ vector QED}

The graph-native QED of this section is a \emph{scalar} QED: the
photon carries no spin-1 structure on the graph (it is a 1-cochain in
the Hodge complex, not a vector field on the manifold).  The continuum
QED adds vector structure via $\mathrm{SO}(4) = \mathrm{SU}(2)_L
\times \mathrm{SU}(2)_R$, and Theorem~\ref{thm:self_energy_zero}
is a vector-QED selection rule that scalar QED does not possess.

In Paper~18's exchange-constant taxonomy~\cite{paper18}, the photon's
spin-1 vector nature is a \textsc{calibration} exchange constant:
it is injected when projecting from the algebraic graph to the
continuous manifold.  The pendant-edge theorem
(Proposition~\ref{prop:pendant_edge}) quantifies the cost of this
omission: a ground-state self-energy of~$2$ (in graph units) that the
continuum's vector selection rules eliminate exactly.  The structural
zero is not a fine cancellation that the finite graph misses due to
truncation---it is a \emph{qualitative} selection rule tied to the
photon's vector character, which the graph does not encode.

\subsection{Continuum bridge and projection exchange constant}
\label{sec:continuum_bridge}

The graph VP (trace) and the continuum spectral-sum VP
(Sec.~\ref{sec:T9}) are related at finite truncation by a
\emph{rational} projection constant
$C = \Pi_{\mathrm{cont}} / \mathrm{Tr}(\Pi_{\mathrm{graph}})$.
At $n_{\max} = 3$:
\[
  C = \frac{50471424}{1779441125} \approx 0.0284.
\]
\textbf{$C$ is rational.  No $\pi$ enters at finite truncation.}

Transcendental numbers ($\pi^{\mathrm{even}}$ from Hurwitz zeta,
$\mathrm{Vol}(S^3) = 2\pi^2$) enter exclusively via two mechanisms:
(i) infinite-sum regularization ($n_{\max} \to \infty$) producing
$\pi^{\mathrm{even}}$ from Bernoulli numbers; (ii) volume normalization
converting to dimensionful quantities.  Both are Paper~18's
\textsc{calibration} tier~\cite{paper18}.

The graph is strictly richer than the continuum at finite truncation:
at $n_{\max} = 3$, the graph captures ${\sim}35\times$ more VP content
than the $W$-weighted continuum formula.

\subsection{Transcendental certificate}

\textbf{All} graph-native QED quantities are $\pi$-free:
\begin{itemize}
\item VP trace: rational at every $n_{\max}$.
\item Self-energy $\Sigma$: diagonal entries rational; off-diagonals
  contain $\sqrt{2}$, $\sqrt{3}$, $\sqrt{6}$ from CG coefficients.
\item Vertex correction $\Lambda$: eigenvalues involve $\sqrt{145}$.
\item Anomalous moment $F_2 = 5\sqrt{2}/3$ ($t = 0$);
  $(48\sqrt{3} + 96275)/[3(15 + 16\sqrt{6} + 9616\sqrt{2})]$
  ($t = \kappa$): algebraic irrational at both couplings.
\item Projection exchange constant: rational.
\end{itemize}
The algebraic irrationals enter through Clebsch--Gordan coefficients
in the Dirac-to-Fock projection.  In Paper~18's taxonomy, all graph-native
QED lives in the \textsc{intrinsic} tier; transcendentals enter only
when projecting onto the continuum (\textsc{calibration} tier).

% ===================================================================
\section{Discussion}
\label{sec:discussion}
% ===================================================================

The five theorems, two propositions, and one observation of this paper,
together with the anomalous magnetic moment computation
(Sec.~\ref{sec:anomalous_moment}) and the graph-native QED infrastructure
(Sec.~\ref{sec:graph_native_qed}), complete the first comprehensive
treatment of perturbative QED on~$S^3$ in both the continuum spectral-sum
and finite-graph formulations.
The three-axis taxonomy extends Paper~18's exchange-constant
classification~\cite{paper18} from free propagators to interaction
vertices: \emph{diagram topology} is an independent source of
transcendental content beyond operator order and bundle type.

The self-energy structural zero (Theorem~\ref{thm:self_energy_zero})
and the anomalous magnetic moment extraction are the first
physical-process QED results in the GeoVac framework, complementing
the vacuum diagrams of the prior QED modules.  The self-energy
demonstrates that the vertex parity selection rule has direct
consequences for scattering processes on~$S^3$.
The pendant-edge theorem (Proposition~\ref{prop:pendant_edge})
sharpens the broken-structural-zero finding: the graph ground-state
self-energy $\Sigma_{\mathrm{graph}}(\mathrm{GS}) = 2(n_{\max}-1)/n_{\max}$
is an exact rational expression that converges to~$2$, not~$0$, as
$n_{\max} \to \infty$.  This is not a finite-size artifact that heals
in the continuum limit; it reflects a qualitative difference between
graph QED (scalar, 1-cochain photon) and continuum QED (vector,
$\mathrm{SO}(4) = \mathrm{SU}(2)_L \times \mathrm{SU}(2)_R$ photon).
The photon's spin-1 vector nature is thereby classified as a
\textsc{calibration} exchange constant in Paper~18's
taxonomy~\cite{paper18}.  The anomalous
magnetic moment ($F_2 / [\alpha/(2\pi)] = 1.084$ at
$n_{\mathrm{ext}} = 1$) provides the first quantitative curvature
correction to a measurable QED observable in the framework, matching the
Parker--Toms prediction within 0.4\%.

The curvature coefficient identification
$c_2 = (2 - B\Delta - F\Delta - F/B)/5$
(Sec.~\ref{sec:curvature_coefficients}) is the first concrete
numerical bridge between Papers~2 and~28: the three spectral objects
$B = 42$, $F = \pi^2/6$, $\Delta = 1/40$ that compose the
$\alpha$~construction $K = \pi(B + F - \Delta)$ also appear as the
geometric invariants controlling the second curvature correction to the
anomalous magnetic moment on~$S^3$.  Since $\alpha$ cancels in the ratio
$F_2/[\alpha/(2\pi)]$, this is a statement about the spectral geometry
of the Dirac operator on~$S^3$, not about QED per se.  The high-precision
$n_{\mathrm{int}}=50$ extraction (Sec.~\ref{sec:curvature_coefficients})
gives $c_3 = -5.946(3) \times 10^{-7}$ at $200.9\,\sigma$, confirming the
expansion does not terminate at second order; the ratio
$|c_3 x^3| / |c_2 x^2| \approx 5.4 \times 10^{-6}$ indicates rapid but
non-terminating convergence.  The T9 theorem constrains $c_3$ to lie in
the $\pi^{\mathrm{even}}$-polynomial ring; its closed-form identification
remains open.

The 5-point mode-dependent curve
(Table~\ref{tab:mode_dependence}) reveals that the anomalous moment on
a compact space is strongly mode-dependent: enhanced for the lowest mode
and progressively suppressed for higher modes, with a power-law
$|\lambda|^{-1.84 \pm 0.06}$.  The dominant internal mode ($n_{\mathrm{int}} = 1$)
approaches the Parker--Toms $\lambda^{-2}$ scaling asymptotically, but
higher internal modes contribute increasingly at larger $n_{\mathrm{ext}}$,
pulling the effective exponent above $-2$.  This non-perturbative mode
dependence is a structural consequence of the discrete spectral
geometry on~$S^3$.

The $\chi_{-4}$ identity (Theorem~\ref{thm:chi4}) is a concrete
spectral-zeta to Dirichlet-$L$ bridge.  Combined with the RH-sprint
finding that the spectral zeros of $D(s)$, $D_{\mathrm{even}}(s)$, and
$D_{\mathrm{odd}}(s)$ exhibit GUE-like spacing statistics (CV $\approx
0.35$--$0.40$, KS rejects Poisson; Paper~29~\cite{paper29}), the
Dirac spectral geometry on $S^3$ realizes both axes of the Weil
dictionary --- though GUE spacing without a single critical line means
the analogy to the Riemann hypothesis remains structural, not literal.

The depth-$k$ tower has a natural interpretation in the framework of
Zagier's motivic weight conjecture~\cite{zagier1994}: each loop order
increases the motivic weight by the vertex coupling, and the algebra
of multiple zeta values provides the natural receptacle for the
resulting transcendentals.  The half-integer shift $a = 3/2$ from the
Dirac spectrum on $S^3$ produces Hurwitz (rather than Riemann)
multiple zeta values, and the failure of 100-element PSLQ bases
suggests that the $S^3$ spectral geometry accesses a sector of the MZV
algebra that is not reached by flat-space Feynman integrals at the same
loop order.

The fine-structure Euler sum cancellation
(Observations~\ref{obs:euler_cancel} and~\ref{obs:product_rule}) connects
the free-propagator Dirichlet series studied in
Secs.~\ref{sec:T9}--\ref{sec:chi4} to the \emph{interacting} Dirac
hydrogen spectrum.  The product survival rule --- $\zeta(2) \times
\zeta(\text{odd})$ cancelled at every order, with exactly
$\max(0, \lfloor(2p{-}5)/2\rfloor)$ products surviving --- is verified
through $D_6$ and driven by the same $n^2$ Fock degeneracy that produces
$F = \zeta(2)$ in Paper~2~\cite{paper2}.
Despite this structural link, PSLQ confirms that $K/\pi$ does not lie in
the $\mathbb{Q}$-span of $\{D_2, \ldots, D_6\}$: the spectral-action
ingredients of $K$ inhabit a $\pi$-polynomial ring
(Theorem~\ref{thm:T9}), while the Sommerfeld sums carry irreducible
odd-zeta content from the Euler--Zagier MZV algebra at every order.
The operator/energy distinction --- spectral zeta versus physical
energy coefficients --- is the structural separation between $K$ and
the $D_p$.

The three-loop factorized algorithm (Sec.~\ref{sec:three_loop})
reduces the computational complexity from $O(N^5)$ to $O(N^3)$,
enabling $n_{\max} = 100{+}$ in minutes.  However, the CG-weighted
sum at physical exponents converges too slowly ($\alpha \approx -1.31$)
for PSLQ identification at any practical $n_{\max}$ --- an honest
computational finding documented by the convergence analysis.
The three-loop constant $S^{(3)}$ at fast-converging exponents is
confirmed independent of $S_{\min}$ and all lower-loop constants.

\subsection{Open questions}

\begin{enumerate}
\item Can $S_{\min}$ be identified with a known multiple Hurwitz zeta
      value in the Borwein--Bailey--Broadhurst
      compendium~\cite{bailey2001}?  The 100-element PSLQ at 200~dps
      suggests not, but the Hurwitz shift $a = 3/2$ places it in a
      sector not systematically explored in the compendium.
\item Does the depth-$k$ tower stabilize (i.e., do all constants
      beyond some $k_0$ reduce to products of lower-depth constants)?
\item Is there a Picard--Fuchs interpretation of $S_{\min}$, analogous
      to Ap\'ery's recurrence for $\zeta(3)$~\cite{apery1979}?
\item Can the self-energy structural zero at $n_{\mathrm{ext}} = 0$
      be lifted by going to higher loop order, or does vertex parity
      enforce $\Sigma^{(k)}(0) = 0$ at every order?
      \textbf{Partial resolution:}
      The structural zero is broken on the finite graph
      (Sec.~\ref{sec:broken_structural_zero}): the pendant-edge theorem
      (Proposition~\ref{prop:pendant_edge}) proves
      $\Sigma_{\mathrm{graph}}(\mathrm{GS}) = 2(n_{\max}-1)/n_{\max}
      \to 2$ exactly, never healing.  The root cause is that the graph
      photon is a scalar 1-cochain lacking the spin-1 vector selection
      rules (vertex parity + SO(4) channel count) that enforce the
      continuum zero.
      The continuum question at higher loop order remains open.
\item The three-loop CG-weighted sum at physical exponents has
      convergence rate $\alpha \approx -1.31$.  Is there a
      resummation technique (e.g., Pad\'e, conformal mapping) that can
      extract more digits from the partial sums?
\item The 5-point mode-dependent curve
      $F_2 / [\alpha/(2\pi)] \approx 5.91\,|\lambda|^{-1.84 \pm 0.06}$
      has an effective exponent $2.8\sigma$ from $-2$.  The dominant
      internal mode's local slope converges toward $-2$, but higher
      internal modes ($n_{\mathrm{int}} \ge 2$) contribute increasingly
      at larger $n_{\mathrm{ext}}$ and pull the effective exponent
      above $-2$.  Is the true asymptotic exponent exactly $-2$
      (Parker--Toms), or a distinct value?  This could be resolved by
      computing $n_{\mathrm{ext}} = 6$--$10$ or by analytical
      large-$\lambda$ asymptotics of the CG vertex sums.
\item The tree-level magnetic amplitude satisfies
      $V_{\mathrm{mag}} \to (4/3)/|\lambda|$ asymptotically
      (Richardson-extrapolated).  Can this $4/3$ prefactor be derived
      from the CG coefficient structure in closed form?
\item The exact algebraic expressions for $V_{\mathrm{mag}}$ and
      $B(n_{\mathrm{int}} = 1)$ at each $n_{\mathrm{ext}}$ are sums
      of square roots with rational coefficients, exhibiting a
      telescoping recurrence: the negative sqrt argument at step $n$
      equals the positive sqrt argument at step $n - 1$.  Can this
      recurrence be proven from the CG coupling rules?
\item Can the flat-space limit $R \to \infty$ be verified explicitly by
      computing $F_2$ on spheres of increasing radius with $n$ scaling
      as $n \sim m R$ to keep the physical mass fixed?
\item The curvature coefficient identification
      $c_2 = (2 - B\Delta - F\Delta - F/B)/5$ matches the spectral sum
      to 8~digits (Sec.~\ref{sec:curvature_coefficients}).
      \textbf{RESOLVED (partially):}
      Extending to $n_{\mathrm{int}}=50$ confirms $c_2$ and gives
      $c_3 = -5.946(3) \times 10^{-7}$ at $200.9\,\sigma$.
      Deriving $c_2$ analytically from the Schwinger--DeWitt heat kernel
      remains open.
\item \textbf{RESOLVED.}
      $c_3 = -5.946(3) \times 10^{-7}$ from $n_{\mathrm{int}}=50$,
      nonzero at $200.9\,\sigma$.  The curvature expansion does not
      terminate at second order; the ratio $|c_3 x^3|/|c_2 x^2|
      \approx 5.4 \times 10^{-6}$ shows rapid but non-terminating
      convergence.  The closed-form identification of $c_3$ in the T9
      $\pi^{\mathrm{even}}$-polynomial ring remains open.
\item The multi-$n_{\mathrm{ext}}$ extraction of curvature coefficients
      requires Wigner--Eckart decomposition into multipole form factors
      for higher-$j$ sectors.  At $n_{\mathrm{ext}} \ge 2$, the $j = 1/2$
      component is a $2/[(n+1)(n+2)]$ fraction of the total degeneracy.
      Can the $j$-dependent form factors be separated cleanly to give
      independent $c_2$ extractions at each $n_{\mathrm{ext}}$?
\item \textbf{RESOLVED.}  The Euler sum cancellation extends to $D_5$
      (weight~9): $\zeta(2)\zeta(7)$ cancels while $\zeta(3)\zeta(6)$
      and $\zeta(4)\zeta(5)$ survive
      (Observation~\ref{obs:product_rule}).  The product survival rule
      $\max(0, \lfloor(2p{-}5)/2\rfloor)$ is verified through $p = 5$.
      The $S_N$-symmetry origin remains open, but the mechanism is
      identified: the $n^2$ Fock degeneracy weight systematically
      expels $\zeta(2)$ products via Euler sum reflection identities.
\end{enumerate}

% ===================================================================
% References
% ===================================================================

\begin{thebibliography}{99}

\bibitem{paper7}
GeoVac Project, ``The Dimensionless Vacuum: $S^3$ Conformal Equivalence
and 18 Symbolic Proofs,'' Paper~7 (2025).

\bibitem{paper14}
GeoVac Project, ``Structurally Sparse Qubit Hamiltonians from Natural
Geometry,'' Paper~14 (2025).

\bibitem{paper18}
GeoVac Project, ``Spectral-Geometric Exchange Constants,'' Paper~18
(2026).

\bibitem{paper29}
GeoVac Project, ``Ramanujan Property of GeoVac Hopf Graphs,'' Paper~29
(2026).

\bibitem{paper25}
GeoVac Project, ``Hopf Graph as Discrete Lattice-Gauge Structure,''
Paper~25 (2026).

\bibitem{paper2}
GeoVac Project, ``Fine Structure Constant from the Hopf Bundle,''
Paper~2 (2025).

\bibitem{schwinger1948}
J.~Schwinger, ``On quantum-electrodynamics and the magnetic moment of
the electron,''
\textit{Phys.~Rev.}\ \textbf{73}, 416--417 (1948).

\bibitem{parker1980}
L.~Parker and D.~J.~Toms, ``Renormalization-group analysis of grand
unified theories in curved spacetime,''
\textit{Phys.~Rev.~D}\ \textbf{29}, 1584 (1984);
see also L.~Parker and D.~J.~Toms,
\textit{Quantum Field Theory in Curved Spacetime}
(Cambridge University Press, 2009), Sec.~6.

\bibitem{camporesi1996}
R.~Camporesi and A.~Higuchi, ``On the eigenfunctions of the Dirac
operator on spheres and real hyperbolic spaces,''
\textit{J.~Geom.~Phys.}\ \textbf{20}, 1--18 (1996).

\bibitem{rosner1967}
J.~L.~Rosner, ``Higher-order contributions to the divergent part of
$Z_3$ in a model quantum electrodynamics,''
\textit{Ann.~Phys.}\ \textbf{44}, 11--34 (1967).

\bibitem{laporta1996}
S.~Laporta and E.~Remiddi, ``The analytical value of the electron
$(g-2)$ at order $\alpha^3$ in QED,''
\textit{Phys.~Lett.~B}\ \textbf{379}, 283--291 (1996).

\bibitem{laporta2002}
S.~Laporta, ``High precision $\epsilon$-expansions of massive four-loop
vacuum bubbles,''
\textit{Phys.~Lett.~B}\ \textbf{549}, 115--122 (2002).

\bibitem{petermann1957}
A.~Petermann, ``Fourth-order magnetic moment of the electron,''
\textit{Helv.~Phys.~Acta}\ \textbf{30}, 407--408 (1957).

\bibitem{sommerfield1957}
C.~M.~Sommerfield, ``Magnetic dipole moment of the electron,''
\textit{Phys.~Rev.}\ \textbf{107}, 328--329 (1957).

\bibitem{zagier1994}
D.~Zagier, ``Values of zeta functions and their applications,''
in \textit{First European Congress of Mathematics}, Vol.~II,
Birkh\"auser, 497--512 (1994).

\bibitem{bailey2001}
D.~H.~Bailey and D.~J.~Broadhurst, ``Parallel integer relation
detection: techniques and applications,''
\textit{Math.~Comp.}\ \textbf{70}, 1719--1736 (2001).

\bibitem{flajolet1998}
P.~Flajolet and B.~Salvy, ``Euler sums and contour integral
representations,''
\textit{J.~Exp.~Math.}\ \textbf{7}, 15--35 (1998).

\bibitem{apery1979}
R.~Ap\'ery, ``Irrationalit\'e de $\zeta(2)$ et $\zeta(3)$,''
\textit{Ast\'erisque}\ \textbf{61}, 11--13 (1979).

\bibitem{rivoal2000}
T.~Rivoal, ``La fonction z\^eta de Riemann prend une infinit\'e de
valeurs irrationnelles aux entiers impairs,''
\textit{C.~R.~Acad.~Sci.~Paris, S\'er.~I}\ \textbf{331}, 267--270
(2000).

\bibitem{rh_j_memo}
GeoVac Project.  Spectral $\chi_{-4}$ identification in
$D_{\mathrm{even}}(s) - D_{\mathrm{odd}}(s)$: closed-form derivation
and verification (Sprint~3 Track~RH-J),
\texttt{debug/spectral\_chi\_neg4\_memo.md}, April 2026.

\end{thebibliography}

\end{document}
