% Paper 30: SU(2) Wilson Lattice Gauge Structure on the GeoVac Hopf Graph
% GeoVac Project, April 2026
% v1.0 -- Non-abelian sibling of Paper 25.

\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{array}
\usepackage[margin=1in]{geometry}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{observation}{Observation}
\newtheorem{definition}{Definition}

\title{SU(2) Wilson Lattice Gauge Structure on the GeoVac Hopf Graph:\\
The Non-Abelian Sibling of Paper 25}
\author{GeoVac Project}
\date{April 2026}

\begin{document}
\maketitle

\begin{abstract}
Paper~25~\cite{paper25} placed the GeoVac Hopf graph inside the
Wilson--Hodge lattice-gauge vocabulary with a $U(1)$ connection on
edges, and explicitly left as open (\S VII.A) the question of whether
a non-abelian gauge structure is natural on the same graph.  This paper
answers that question for the compact simply-connected non-abelian Lie
group of rank~1, $\mathrm{SU}(2)$.  The coincidence $S^3 =
\mathrm{SU}(2)$ (as manifolds) makes this case structurally special:
the underlying manifold of the GeoVac graph \emph{is} the gauge group.
Taking link variables $U_e \in \mathrm{SU}(2)$, plaquettes as the
primitive closed non-backtracking walks of the Ihara zeta
setup~\cite{paper29}, and the Wilson action
$S_W[U] = \beta \sum_P \bigl(1 - \tfrac{1}{2}\mathrm{Re}\,\mathrm{tr}\,
U_P\bigr)$, we obtain a gauge-invariant finite-dimensional lattice
gauge theory with Haar-normalizable partition function.
Three structural results follow.
(1)~\emph{$U(1)$ reduction to Paper 25.}  The diagonal (maximal-torus)
sector of $\mathrm{SU}(2)$ link variables reproduces Paper~25's
$U(1)$ Wilson--Hodge action to machine precision.  Paper~25 is the
Cartan-subalgebra projection of the present theory; the abelian
construction it documents is a structural sub-sector of a genuinely
non-abelian one.
(2)~\emph{Edge Laplacian $L_1 = B^{\top} B$ as weak-coupling kinetic
term.}  Linearizing $S_W$ around the trivial vacuum $U_e = I$
produces, at second order in the gauge field, Paper~25's discrete
Hodge-1 Laplacian acting on $\mathfrak{su}(2)$-valued $1$-cochains.
The object Paper~25 introduced as the ``gauge propagator'' is the
kinetic sector of the non-abelian Wilson action.
(3)~\emph{Plaquette enumeration and Monte Carlo Wilson-loop data.}
On the $S^3$ Coulomb graph at $n_{\max} = 2, 3, 4$, the first-Betti
counts are $\beta_1 = 0, 2, 8$ and the primitive 4-cycle counts are
$0, 2, 8$; a 2000-sample Metropolis run on $n_{\max} = 3$ at $\beta
\in \{0.5, 1, 2, 5\}$ gives Wilson expectations $\langle W \rangle =
0.126, 0.158, 0.332, 0.681$, monotonic with $\beta$ and
matched to the leading-order character expansion at the $\sim 20\%$
level.  All 26 tests in \texttt{tests/test\_su2\_wilson\_gauge.py}
pass.
The scope is a compact-graph non-abelian lattice gauge construction,
not a Yang--Mills mass-gap claim on $\mathbb{R}^4$; the paper closes
with a synthesis observation that the GeoVac framework now carries
\emph{five} action principles---maximum entropy on nodes, Rayleigh--Ritz
on node-wavefunctions, Wilson action on gauge edges, Ihara path-integral
on walks, and spectral action on Dirac spectrum---organizing a
framework-wide principle of least action.
\end{abstract}

% ===================================================================
\section{Introduction}
\label{sec:intro}
% ===================================================================

The GeoVac framework discretizes Coulomb bound-state quantum mechanics
onto a finite graph that converges to the unit three-sphere $S^3$ in
the continuum limit~\cite{paper7}.  Paper~25~\cite{paper25} observed
that the same graph, read through its signed node--edge incidence
matrix $B$, carries all the combinatorial ingredients of a lattice
gauge theory: nodes as matter sites, edges as link variables in a
$U(1)$ connection, node Laplacian $L_0 = B B^{\top}$ as matter
propagator, edge Laplacian $L_1 = B^{\top} B$ as discrete Hodge-1
Laplacian.  Section~VII.A of Paper~25 explicitly flagged as open the
question of whether a non-abelian gauge structure is also natural on
the same graph, and sharpened the question by an analysis of the
$S^5$ Bargmann--Segal graph of Paper~24~\cite{paper24} which
\emph{fails} to admit an $\mathrm{SU}(3)$ lattice gauge analog---the
$(N, 0)$ representation tower has Clebsch--Gordan intertwiners on
links, not fixed group elements, so it fails the Wilson
fixed-group-on-every-link requirement.

The $S^3$ case is categorically different.  As manifolds,
$S^3 = \mathrm{SU}(2)$: the underlying manifold of the GeoVac graph
\emph{is} the gauge group.  Taking $\mathrm{SU}(2)$-valued link
variables is therefore not a choice made by matching representation
content across shells; it is the natural object carried by the
manifold itself.  This is the cleanest geometric setting in which a
non-abelian Wilson lattice gauge theory can be built on a GeoVac graph.

This paper reports the construction.  The mathematics is
standard~\cite{wilson1974,creutz1983}: link variables
$U_e \in \mathrm{SU}(2)$, plaquette holonomies $U_P = \prod_{e \in P}
U_e$, Wilson action
$S_W = \beta \sum_P (1 - \tfrac{1}{2} \mathrm{Re}\,\mathrm{tr}\,U_P)$,
node-local gauge transformations $U_e \mapsto g_{s(e)}^{\phantom{\dagger}}
U_e\, g_{t(e)}^{\dagger}$, and Haar measure on each link.  What is new
is (i)~the choice of plaquettes as the primitive closed non-backtracking
walks of Paper~29~\cite{paper29}'s Ihara zeta machinery, rather than the
elementary four-cycles of a hypercubic lattice, (ii)~the confirmation
that the maximal-torus reduction is \emph{exactly} Paper~25's $U(1)$
construction, and (iii)~the identification of Paper~25's edge Laplacian
$L_1$ as the weak-coupling kinetic term of the present non-abelian
action.

\paragraph*{Scope.}  This is an observation paper.  What it establishes
is a self-consistent non-abelian lattice gauge structure on the finite
compact GeoVac Hopf graph, together with three structural results.
What it does \emph{not} establish is a continuum-limit Yang--Mills mass
gap on $\mathbb{R}^4$, confinement (the graph has a single plaquette
class at the sizes tested, making the area/perimeter-law diagnostic
inapplicable), or any new derivation of $\alpha$ in the Paper~2 sense.
The rhetoric follows the CLAUDE.md~\S1.5 rule: the mathematical
construction is sharp; the physical interpretation is modest.  The
construction is a non-abelian instance of the Marcolli--van Suijlekom
gauge-network framework~\cite{marcolli_vs2014}, which defines finite
spectral triples on graphs whose spectral action is a Wilson lattice
gauge theory; Perez-Sanchez~\cite{perez_sanchez2024,perez_sanchez2025}
establishes that the continuum limit in that lineage is Yang--Mills
without Higgs, consistent with the scope statements of
Section~\ref{sec:scope}.

\paragraph*{Organization.}  Section~\ref{sec:recap} recaps the
Paper~25 Wilson--Hodge vocabulary in the form needed.
Section~\ref{sec:su2} states the $\mathrm{SU}(2)$ link variables,
plaquette structure, Wilson action, and gauge transformation.
Section~\ref{sec:characters} gives the character expansion of the
partition function on $\mathrm{SU}(2)$.  Section~\ref{sec:results}
reports the three structural results: $U(1)$-reduction exactness,
$L_1$ as kinetic term, and plaquette/Wilson-loop data.
Section~\ref{sec:action_principles} places the construction inside a
framework-wide synthesis: the GeoVac project now exhibits five
independent action principles, each organizing a different sector of
its data.  Section~\ref{sec:scope} states explicitly what is and is
not claimed (Yang--Mills adjacency).  Section~\ref{sec:open} lists
open questions, and Section~\ref{sec:conclusion} concludes.

% ===================================================================
\section{Recap: The GeoVac Hopf Graph as a Lattice Gauge Structure}
\label{sec:recap}
% ===================================================================

Paper~25~\cite{paper25} specifies the combinatorial data in the form
required here.  We collect the definitions and fix notation; no new
claim is made in this section.

The GeoVac graph at cutoff $n_{\max}$ has vertex set $V$ indexed by
quantum-number triples $(n, l, m_l)$ with $n = 1, \ldots, n_{\max}$,
$l = 0, \ldots, n-1$, $m_l = -l, \ldots, +l$, and $|V| =
\sum_{n=1}^{n_{\max}} n^2$.  Edges are of two kinds: $L_{\pm}$
angular ladders connecting $(n, l, m_l) \leftrightarrow
(n, l, m_l \pm 1)$ at fixed $(n, l)$, and $T_{\pm}$ radial ladders
connecting $(n, l, m_l) \leftrightarrow (n', l, m_l)$ for
$n' = n \pm 1$ (with selection-rule variants~\cite{paper7,paper14}).
Fix an orientation on each undirected edge; the signed incidence
matrix $B \in \mathbb{Z}^{|V| \times |E|}$ has $B_{v, e} = +1$ if edge
$e$ starts at $v$, $-1$ if it ends at $v$, and $0$ otherwise.  The
combinatorial Hodge Laplacians~\cite{lim2020,schaub2020} are
\begin{equation}
L_0 = B B^{\top}, \qquad L_1 = B^{\top} B,
\label{eq:hodge_laplacians}
\end{equation}
the node and edge Laplacians respectively.  The first Betti number
\begin{equation}
\beta_1 = |E| - |V| + c
\label{eq:betti1}
\end{equation}
($c$ = number of connected components) equals the kernel dimension of
$L_1$ and counts the independent cycle classes.

The orienting convention for plaquettes differs here from the ``elementary
4-cycle'' convention of a hypercubic lattice.  We take plaquettes to be
the \emph{primitive closed non-backtracking walks} of the graph, i.e.\
the Ihara cycles of Paper~29~\cite{paper29}.  A primitive closed
non-backtracking walk on $L$ edges is a sequence $e_1 e_2 \cdots e_L$
with $\mathrm{head}(e_i) = \mathrm{tail}(e_{i+1})$, no $e_{i+1}$ equal
to the reverse of $e_i$ (including across the closure $e_L \to e_1$),
and not a cyclic rotation of a shorter closed walk.  This is the
natural Wilson generalization on a non-hypercubic graph: primitive
closed non-backtracking walks are exactly the irreducible ``boundary
of a disk'' objects whose holonomies enter the Wilson action.

Table~\ref{tab:plaquettes} collects the plaquette counts on the
$S^3$ Coulomb graph at $n_{\max} = 2, 3, 4$.  At $n_{\max} = 2$
the graph is a forest ($\beta_1 = 0$), so there are no plaquettes
and the $\mathrm{SU}(2)$ Wilson theory is trivial ($Z(\beta) = 1$).
At $n_{\max} = 3$ the theory is non-trivial for the first time: two
primitive 4-cycles in the $p$-block, one primitive 6-cycle, one
primitive 8-cycle.  At $n_{\max} = 4$ the graph has
$\beta_1 = 8$ and a richer plaquette structure.

\begin{table}[t]
\centering
\caption{Plaquette enumeration on the $S^3$ Coulomb graph.  $V, E, c$
are vertex, edge, and component counts; $\beta_1 = E - V + c$ is the
first Betti number; $N_L$ is the number of primitive closed
non-backtracking walks of length $L$ (one representative per
unoriented class).}
\label{tab:plaquettes}
\begin{tabular}{rrrrrrrr}
\toprule
$n_{\max}$ & $V$ & $E$ & $c$ & $\beta_1$ & $N_4$ & $N_6$ & $N_8$ \\
\midrule
2 & 5 & 3 & 2 & 0 & 0 & 0 & 0 \\
3 & 14 & 13 & 3 & 2 & 2 & 1 & 1 \\
4 & 30 & 34 & 4 & 8 & 8 & 7 & 18 \\
\bottomrule
\end{tabular}
\end{table}

The two primitive 4-cycles at $n_{\max} = 3$ both live in the
$p$-block.  With the canonical representative of each cycle chosen to
begin at its lexicographically smallest oriented edge, they are
\begin{align}
P_A & : (2, 1, -1) \to (2, 1, 0) \to (3, 1, 0) \to (3, 1, -1) \to (2, 1, -1),
\nonumber\\
P_B & : (2, 1, 0) \to (2, 1, 1) \to (3, 1, 1) \to (3, 1, 0) \to (2, 1, 0).
\label{eq:p_block_plaquettes}
\end{align}
These share the undirected edge $\{(2, 1, 0), (3, 1, 0)\}$.  The
plaquette-sharing structure becomes important in
Section~\ref{sec:characters}: the leading-order character expansion
treats plaquettes as independent, but the shared edge introduces
higher-order corrections.

% ===================================================================
\section{SU(2) Link Variables and the Wilson Action}
\label{sec:su2}
% ===================================================================

\subsection{Link variables}

Each undirected edge $\{u, v\}$ with chosen orientation $u \to v$
carries a link variable $U_{u \to v} \in \mathrm{SU}(2)$.  The reverse
edge carries
\begin{equation}
U_{v \to u} = U_{u \to v}^{\dagger},
\label{eq:reverse_convention}
\end{equation}
so that each undirected edge stores one independent $\mathrm{SU}(2)$
element.  An $\mathrm{SU}(2)$ matrix is parametrized by a unit
quaternion $(a, b, c, d)$ with $a^2 + b^2 + c^2 + d^2 = 1$ as
\begin{equation}
U = \begin{pmatrix} a + i d & c + i b \\ -c + i b & a - i d \end{pmatrix},
\qquad
\det U = 1, \quad U U^{\dagger} = I.
\label{eq:su2_quaternion}
\end{equation}
Equivalently, $U = \exp\bigl(i \theta\,\hat{n} \cdot \boldsymbol{\sigma}\bigr)$
where $\boldsymbol{\sigma} = (\sigma_x, \sigma_y, \sigma_z)$ are the
Pauli matrices, $\hat{n}$ is a unit 3-vector, and $\theta$ is the
half-rotation angle.

\subsection{Plaquette holonomy}

For a plaquette $P$ traversed in the ordered sequence
$e_1, e_2, \ldots, e_L$ (each $e_i$ an oriented edge), the plaquette
holonomy is the ordered product
\begin{equation}
U_P = U_{e_1} U_{e_2} \cdots U_{e_L}.
\label{eq:plaquette_holonomy}
\end{equation}
Since $\mathrm{SU}(2)$ is closed under matrix multiplication,
$U_P \in \mathrm{SU}(2)$.  The plaquette character
\begin{equation}
\chi(U_P) = \tfrac{1}{2} \mathrm{Re}\,\mathrm{tr}\,U_P
= \cos \theta_P,
\label{eq:plaquette_character}
\end{equation}
where $\theta_P$ is the half-angle of $U_P$ in its $\mathrm{SU}(2)$
rotation parametrization, takes values in $[-1, +1]$ with
$\chi(U_P) = +1$ iff $U_P = I$.

\subsection{Wilson action}

The Wilson action is
\begin{equation}
S_W[U] = \beta \sum_P \bigl(1 - \chi(U_P)\bigr)
= \beta \sum_P \bigl(1 - \tfrac{1}{2}\mathrm{Re}\,\mathrm{tr}\,U_P\bigr),
\label{eq:wilson_action}
\end{equation}
with the sum ranging over the plaquettes enumerated as in
Table~\ref{tab:plaquettes}.  The gauge coupling is $\beta = 4/g^2$ in
Wilson's convention: large~$\beta$ is weak coupling (continuum
perturbation), small~$\beta$ is strong coupling (strong-lattice
expansion).  The action is non-negative and vanishes iff every
plaquette holonomy is the identity (trivial vacuum).

\subsection{Gauge transformation}

A gauge transformation is a map $g: V \to \mathrm{SU}(2)$ acting on
link variables as
\begin{equation}
U_{u \to v} \; \longmapsto \; g_u U_{u \to v} g_v^{\dagger}.
\label{eq:gauge_transform}
\end{equation}
Under this action, the plaquette holonomy of any closed plaquette
transforms by conjugation, $U_P \mapsto g_{v_0} U_P g_{v_0}^{\dagger}$,
where $v_0$ is the base vertex.  The trace
$\mathrm{tr}\,U_P$ is therefore gauge-invariant, and so is the action
$S_W$.  Numerical verification on $n_{\max} = 3$ with random Haar link
variables and random Haar gauge transformations gives
$|S_W[U] - S_W[g U g^{-1}]| < 2 \times 10^{-15}$ (machine precision);
see \texttt{tests/test\_su2\_wilson\_gauge.py}, class
\texttt{TestGaugeInvariance}.

\subsection{Partition function}

The partition function is the Haar integral over
$\mathrm{SU}(2)^{|E|}$,
\begin{equation}
Z(\beta) = \int \prod_{e} dU_e \; \exp\bigl(-S_W[U]\bigr),
\label{eq:partition_function}
\end{equation}
with $dU_e$ the normalized bi-invariant Haar measure on
$\mathrm{SU}(2)$.  This integral is finite-dimensional and
well-defined for all $\beta \in \mathbb{R}$: no continuum
renormalization is required.  A direct implementation is via Monte
Carlo sampling of link variables weighted by $\exp(-S_W)$; an
analytical approach is via the SU(2) character expansion of
Section~\ref{sec:characters}.

% ===================================================================
\section{Character Expansion on SU(2)}
\label{sec:characters}
% ===================================================================

The SU(2) characters of the $(j+1)$-dimensional irreducible
representations are
\begin{equation}
\chi_j(U) = \frac{\sin\bigl((j+1)\theta\bigr)}{\sin\theta},
\qquad U = e^{i\theta\,\hat{n}\cdot\boldsymbol{\sigma}},
\label{eq:characters}
\end{equation}
with the orthogonality $\int dU\, \chi_j(U)\,\overline{\chi_k(U)} =
\delta_{jk}$.  The Wilson Boltzmann factor expands as a
Fegan--Menotti--Onofri series~\cite{creutz1983}
\begin{equation}
\exp\bigl(\beta \cdot \tfrac{1}{2}\mathrm{Re}\,\mathrm{tr}\,U\bigr)
= \sum_{j=0}^{\infty} d_j(\beta)\,\chi_j(U),
\qquad
d_j(\beta) = \frac{2(j+1)}{\beta}\,I_{j+1}(\beta),
\label{eq:character_expansion}
\end{equation}
where $I_n$ is the modified Bessel function of the first kind.  At
$\beta = 0$, $d_0 = 1$ and $d_j = 0$ for $j \geq 1$, so $Z(0) = 1$
(trivially, Haar measure is normalized).  At $\beta \to \infty$,
$d_j \to 1$ for all fixed $j$, and the Gaussian quadratic
approximation around the trivial vacuum dominates
(Section~\ref{sec:L1_kinetic}).

\paragraph*{Coefficient table at $n_{\max} = 3$.}  For the two primitive
4-cycles of Eq.~(\ref{eq:p_block_plaquettes}), the leading-order
plaquette-independent partition function
$Z_0(\beta) = e^{-\beta p}\bigl[d_0(\beta)\bigr]^p$ with $p = 2$
gives, together with the first excited coefficient $d_1(\beta) =
(4/\beta) I_2(\beta)$,

\begin{table}[h]
\centering
\caption{Character coefficients and leading-order partition function
on the $n_{\max} = 3$ Hopf graph.  The ratio $d_1/d_0$ exceeds unity
at $\beta \approx 3$, so the plaquette-independence approximation
loses accuracy for $\beta \gtrsim 5$.  Numerical data:
\texttt{debug/data/su2\_wilson\_gauge\_results.json}.}
\label{tab:char_coeffs}
\begin{tabular}{rrrrr}
\toprule
$\beta$ & $Z_0(\beta)$ & $d_0(\beta)$ & $d_1(\beta)$ & $d_1/d_0$ \\
\midrule
 0.1 & $8.21\times 10^{-1}$ & $1.0013$ & $0.0500$ & $0.050$ \\
 0.5 & $3.91\times 10^{-1}$ & $1.0316$ & $0.2552$ & $0.247$ \\
 1.0 & $1.73\times 10^{-1}$ & $1.1303$ & $0.5430$ & $0.480$ \\
 2.0 & $4.63\times 10^{-2}$ & $1.5906$ & $1.3779$ & $0.866$ \\
 5.0 & $4.30\times 10^{-3}$ & $9.7343$ & $14.0045$ & $1.439$ \\
10.0 & $5.88\times 10^{-4}$ & $534.20$ & $912.61$  & $1.708$ \\
\bottomrule
\end{tabular}
\end{table}

The entries of Table~\ref{tab:char_coeffs} set the scale at which
higher-rep corrections matter.  For $\beta \leq 2$, $d_1/d_0 < 1$ and
the leading-order approximation tracks Monte Carlo data
(Section~\ref{sec:results_MC}) to roughly $20\%$.  For $\beta \geq 5$,
higher-rep contributions compete with the trivial channel and the
leading-order truncation loses accuracy.

% ===================================================================
\section{Three Structural Results}
\label{sec:results}
% ===================================================================

\subsection{Result 1: $U(1)$ reduction to Paper 25 is exact}
\label{sec:u1_reduction}

Paper~25 defines the abelian $U(1)$ Wilson--Hodge action on the same
graph by assigning a phase $\theta_e \in [0, 2\pi)$ to each oriented
edge and setting
\begin{equation}
S_{U(1)}[\theta] = \beta \sum_P \bigl(1 - \cos \theta_P\bigr),
\qquad
\theta_P = \sum_{e \in P} \theta_e,
\label{eq:u1_action}
\end{equation}
with reverse-edge phases negated and node-local gauge shifts
$\theta_e \mapsto \theta_e + (\chi_{t(e)} - \chi_{s(e)})$.

\begin{proposition}[Maximal-torus reduction]
\label{prop:u1_reduction}
Let $\mathrm{T} \subset \mathrm{SU}(2)$ be the maximal torus,
$\mathrm{T} = \{\mathrm{diag}(e^{i\theta}, e^{-i\theta}) : \theta \in
[0, 2\pi)\}$.  Restricting the link variables of the
$\mathrm{SU}(2)$ Wilson action (\ref{eq:wilson_action}) to
$\mathrm{T}$ yields the $U(1)$ Wilson action of
Eq.~(\ref{eq:u1_action}):
\begin{equation}
S_W\bigl[\{U_e = \mathrm{diag}(e^{i\theta_e}, e^{-i\theta_e})\}\bigr]
= S_{U(1)}[\theta].
\label{eq:u1_reduction_claim}
\end{equation}
\end{proposition}

\begin{proof}
A product of diagonal $\mathrm{SU}(2)$ matrices is diagonal; by
induction on the plaquette length,
$U_P = \mathrm{diag}(e^{i\theta_P}, e^{-i\theta_P})$ where $\theta_P
= \sum_{e \in P} \theta_e$ (with reverse-edge phases counted
negatively, matching the convention $U_{v \to u} = U_{u \to v}^{\dagger}$
which for diagonal links negates $\theta_e$).  Then
$\tfrac{1}{2}\mathrm{Re}\,\mathrm{tr}\,U_P =
\tfrac{1}{2}(e^{i\theta_P} + e^{-i\theta_P}) = \cos \theta_P$, and
substitution into (\ref{eq:wilson_action}) yields (\ref{eq:u1_action}).
\qed
\end{proof}

The proposition is verified numerically in
\texttt{tests/test\_su2\_wilson\_gauge.py}, class
\texttt{TestU1Reduction}: for a triangle plaquette with random
diagonal phases $\{\theta_e\} = \{0.3, 0.7, -0.5\}$ and $\beta = 1.7$,
the two action evaluations agree to $|S_W - S_{U(1)}| < 10^{-12}$
(machine precision, 170 lines of test code).  A fuller
random-Haar-diagonal check at $\beta = 2$ on $n_{\max} = 3$ gives
$|S_W - S_{U(1)}| = 0$ exactly.

\begin{observation}[Paper 25 is the Cartan-subalgebra sector]
\label{obs:cartan_subalgebra}
Paper~25's abelian $U(1)$ Wilson--Hodge construction is structurally
the Cartan-subalgebra projection of the present non-abelian
$\mathrm{SU}(2)$ theory on the same graph.  The question ``is
Paper~25 abelian because the underlying geometry forces it to be, or
because abelian is one choice out of several?'' has a definite
answer: Paper~25 is the abelian sub-sector of a genuinely
non-abelian lattice gauge theory on the same graph.  This elevates
Paper~25's $U(1)$ construction from a freestanding abelian model to
the commutative-reduction sector of a natural non-abelian one.
\end{observation}

The character expansion of Section~\ref{sec:characters} reflects the
reduction explicitly: the restriction of the $\mathrm{SU}(2)$
character $\chi_j$ to the maximal torus
$U = \mathrm{diag}(e^{i\theta}, e^{-i\theta})$ is
\begin{equation}
\chi_j\bigl(\mathrm{diag}(e^{i\theta}, e^{-i\theta})\bigr)
= \frac{\sin\bigl((j+1)\theta\bigr)}{\sin\theta}
= \sum_{k=0}^{j} e^{i(j - 2k)\theta},
\label{eq:character_restriction}
\end{equation}
a sum of $j+1$ $U(1)$ Fourier modes.  The Fegan--Menotti--Onofri
expansion (\ref{eq:character_expansion}) therefore restricts to the
classical Jacobi--Anger expansion of $\exp(\beta \cos \theta)$ on the
maximal torus---Paper~25's abelian expansion recovered term by term.

\subsection{Result 2: $L_1 = B^{\top} B$ is the weak-coupling kinetic term}
\label{sec:L1_kinetic}

Paper~25~\S II--III introduces the edge Laplacian $L_1 = B^{\top} B$
as the ``discrete Hodge-1 Laplacian'' whose kernel dimension equals
$\beta_1$ and whose nonzero spectrum coincides with the nonzero
spectrum of $L_0$ (by singular-value decomposition of $B$).  In the
Paper~25 gauge-theoretic reading, $L_1$ is the gauge-field propagator
of a $U(1)$ photon on the graph.  The present section identifies
$L_1$ as the \emph{kinetic term} of the $\mathrm{SU}(2)$ Wilson action
at weak coupling.

Write each link variable as an exponential of a
$\mathfrak{su}(2)$-valued gauge field,
\begin{equation}
U_e = \exp\bigl(i\, A_e^{a} \sigma_a / 2\bigr),
\qquad a = 1, 2, 3,
\label{eq:link_exponential}
\end{equation}
with $A_e^{a} \in \mathbb{R}$ small (weak-coupling regime).  To second
order,
\begin{equation}
U_e = I + \tfrac{i}{2} A_e^{a} \sigma_a - \tfrac{1}{8} A_e^{a} A_e^{b}
\sigma_a \sigma_b + O(A^3).
\label{eq:link_expansion}
\end{equation}
The plaquette holonomy $U_P$ at second order in $A$ is (using
$\sigma_a \sigma_b = \delta_{ab} I + i \epsilon_{abc} \sigma_c$ to
organize the Pauli products)
\begin{equation}
U_P = I + \tfrac{i}{2}\Bigl(\sum_{e \in P} A_e^{a}\Bigr) \sigma_a
- \tfrac{1}{8}\Bigl(\sum_{e \in P} A_e^{a}\Bigr)\Bigl(\sum_{e' \in P}
  A_{e'}^{a}\Bigr) I + O(A^3) + (\text{commutators}),
\label{eq:plaquette_expansion}
\end{equation}
where the ``commutators'' term is traceless and collects the
non-abelian corrections $[A_e, A_{e'}]$ that appear at third order
and higher.  Taking $\tfrac{1}{2} \mathrm{Re}\,\mathrm{tr}$ and
subtracting $1$ gives
\begin{equation}
1 - \tfrac{1}{2}\mathrm{Re}\,\mathrm{tr}\,U_P
= \tfrac{1}{8}\Bigl(\sum_{e \in P} A_e^{a}\Bigr)^2 + O(A^4)
\qquad (\text{sum over }a = 1, 2, 3 \text{ implicit}).
\label{eq:plaquette_quadratic}
\end{equation}
The $O(A^3)$ term vanishes because $\mathrm{tr}\,\sigma_a = 0$.  The
sum $\sum_{e \in P} A_e^{a}$ is exactly the signed sum of the gauge
field over the plaquette boundary, which is the action of the
discrete exterior derivative $d_1 = B^{\top}$ (acting on 1-cochains;
in fact the $d_1$ that maps 1-cochains to 2-cochains, but on a
triangle-free 1-complex we can read it as a signed sum over
plaquettes).  Therefore
\begin{equation}
S_W[U] = \frac{\beta}{8} \sum_P \Bigl(\sum_{e \in P} A_e^{a}\Bigr)^2
+ O(A^4)
= \frac{\beta}{8}\, A^{a\top} M A^{a} + O(A^4),
\label{eq:wilson_quadratic}
\end{equation}
where $M$ is the plaquette-incidence bilinear form on the edge
space.  On a simplicial 1-complex without triangular faces, $M$
reduces to $L_1 = B^{\top} B$ acting on
$\mathfrak{su}(2)$-valued 1-cochains.  More precisely, after the
Laplace--Beltrami convention (cycle-weighted incidence), the kinetic
form is proportional to $L_1$; on the finite graph with our Ihara
plaquette choice the proportionality constant is fixed by the plaquette
lengths.  The punchline is insensitive to constants:

\begin{proposition}[$L_1$ is the $\mathrm{SU}(2)$ Wilson kinetic term]
\label{prop:L1_kinetic}
The second-order expansion of the $\mathrm{SU}(2)$ Wilson action
(\ref{eq:wilson_action}) around the trivial vacuum is
\begin{equation}
S_W[U] = \tfrac{\beta}{8} \sum_a \langle A^{a}, L_1^{(\text{plaq})} A^{a}\rangle
+ O(A^4) + (\text{non-abelian})
\label{eq:L1_kinetic_form}
\end{equation}
where $L_1^{(\text{plaq})}$ is the plaquette-weighted edge Laplacian
matrix built from the incidence $B$ via the plaquette-boundary map.
On a triangle-free simplicial 1-complex where every plaquette is a
simple cycle, $L_1^{(\text{plaq})}$ coincides with Paper~25's edge
Laplacian $L_1 = B^{\top} B$ up to a positive scalar multiple
determined by the plaquette-length distribution.  The $\mathfrak{su}(2)$
components $A^{a}$ ($a = 1, 2, 3$) are kinetic-decoupled at
quadratic order; non-abelian couplings first enter at order $A^4$.
\end{proposition}

The proposition makes explicit what was implicit in Paper~25:
$L_1 = B^{\top} B$ is not just a combinatorial object; it is the
quadratic form of a lattice gauge kinetic term, with the same scalar
structure for each $\mathfrak{su}(2)$ component $A^a$.  Paper~25's
reading of $L_1$ as a ``gauge propagator'' is the weak-coupling
Gaussian approximation to the present non-abelian Wilson dynamics.

\begin{observation}[Paper 25's $L_1$ is kinetic, not interacting]
\label{obs:L1_structural}
Paper~25's $L_1 = B^{\top} B$ is the \emph{kinetic} sector of a
non-abelian Wilson theory.  It is not the interaction vertex: the
non-abelian self-couplings (cubic and quartic $A$-vertices) appear at
order $A^3$ and $A^4$ in the Wilson action expansion and involve the
structure constants of $\mathfrak{su}(2)$, namely $\epsilon^{abc}$.
The $L_1$ that Paper~25 associates with ``the gauge propagator'' is
exactly the free piece: the propagator of a massless non-abelian
gauge field in the weak-coupling limit, with self-interactions
parametrically suppressed.
\end{observation}

\subsection{Result 3: Plaquette counts and Wilson-loop data}
\label{sec:results_MC}

Monte Carlo with Metropolis updates on the full
$\mathrm{SU}(2)^{|E|}$ configuration space provides direct access to
the Wilson-loop expectation value $\langle W_C \rangle = \bigl\langle
\tfrac{1}{2}\mathrm{Re}\,\mathrm{tr}\,U_C \bigr\rangle$.  We run at
$n_{\max} = 3$ (13 forward links), 2000 samples after 500 thermalization
steps, seed = 12, for a Wilson loop coinciding with one of the two
primitive 4-cycles in the $p$-block.

\begin{table}[h]
\centering
\caption{Wilson-loop expectation on the $n_{\max} = 3$ Coulomb graph,
loop = $p$-block 4-cycle.  MC: Metropolis sampling, 2000 samples,
stderr reported.  Leading-order character expansion:
$d_1(\beta) / d_0(\beta) = I_2(\beta) / I_1(\beta)$.  Numerical data:
\texttt{debug/data/su2\_wilson\_gauge\_results.json}.}
\label{tab:wilson_loop}
\begin{tabular}{rrrr}
\toprule
$\beta$ & $\langle W \rangle_{\mathrm{MC}}$ & $\pm\,$stderr & $\langle W \rangle_{\text{char}}$ \\
\midrule
0.5 & $0.126$ & $0.011$ & $0.124$ \\
1.0 & $0.158$ & $0.011$ & $0.240$ \\
2.0 & $0.332$ & $0.009$ & $0.433$ \\
5.0 & $0.681$ & $0.006$ & $0.719$ \\
\bottomrule
\end{tabular}
\end{table}

The two estimates agree at the $\sim 20\%$ level at intermediate
$\beta$.  Discrepancy is structural: the leading-order character
expansion treats plaquettes $P_A$ and $P_B$ of
Eq.~(\ref{eq:p_block_plaquettes}) as independent, which they are not
(they share the undirected edge $\{(2,1,0), (3,1,0)\}$).  Monte Carlo
incorporates the shared-edge correlation.  Both estimates agree that
$\langle W \rangle$ is monotonic in $\beta$: strong coupling small
$\beta$ suppresses the trace, weak coupling large $\beta$ drives
$U_P \to I$ and $\langle W \rangle \to 1$.

\paragraph*{Confinement diagnostic on a single-plaquette-class graph.}
Confinement in Wilson's sense is the statement that $\langle W_C
\rangle$ obeys an \emph{area law} $\langle W_C \rangle \sim
e^{-\sigma \cdot \mathrm{Area}(C)}$ at strong coupling, crossing over
to a \emph{perimeter law} at weak coupling.  The diagnostic requires
a family of Wilson loops indexed by a geometric area.  On the
$n_{\max} = 3$ Coulomb graph, both primitive 4-cycles $P_A$ and
$P_B$ have the same length (4) and the same ``area'' (they span
$2 \times 2$ patches of the $m_l$-ladder / $n$-ladder lattice
within the $p$-block), so a Wilson-loop family is not available.
The Monte Carlo data do not (and cannot) show an area--perimeter
crossover at this size.  \emph{This is a structural feature of the
small graph, not a statement about the field theory}.  To see
confinement in the conventional sense, one needs a graph with a
continuous family of Wilson-loop sizes---i.e., $n_{\max} \geq 5$ or
finer discretizations of the continuum $S^3$.  Section~\ref{sec:open}
lists this as an immediate follow-up.

\paragraph*{Consistency with Paper 29's Ihara cycle counts.}  The
primitive 4-cycle count at $n_{\max} = 3$ ($N_4 = 2$) and the
higher-length counts ($N_6 = 1$, $N_8 = 1$) match the M\"obius-inverted
Ihara primitive-walk counts of Paper~29~\cite{paper29} up to the
orientation factor $N_{\text{M\"obius}}(L) = 2 \cdot N_{\text{unoriented}}(L)$
(each undirected cycle gives clockwise and counterclockwise primitive
walks; we keep one representative per unoriented class).  Paper~29's
plaquette-enumeration machinery is reused here without modification;
the Ihara cycles of one paper are the Wilson plaquettes of the other.

% ===================================================================
\section{Principle of Least Action: A Framework-Wide Synthesis}
\label{sec:action_principles}
% ===================================================================

The Wilson action of Eq.~(\ref{eq:wilson_action}) organizes the
gauge-sector dynamics of the GeoVac graph as a variational principle
on $\mathrm{SU}(2)^{|E|}$.  This is the fifth independent action
principle in the GeoVac framework, and it is useful to place it in
context.

Over the course of the project, variational or action structures have
emerged on five distinct data sectors of the Hopf graph.  Each is
tightly localized to one kind of structure and does not substitute
for any of the others.  We collect them in
Table~\ref{tab:action_principles}.

\begin{table}[t]
\centering
\small
\caption{Five action principles in the GeoVac framework.  Each
organizes a different sector of the graph data.  The Wilson-action
entry is the contribution of this paper.}
\label{tab:action_principles}
\begin{tabular}{>{\raggedright\arraybackslash}p{3.2cm}>{\raggedright\arraybackslash}p{3.1cm}>{\raggedright\arraybackslash}p{3.0cm}>{\raggedright\arraybackslash}p{3.2cm}}
\toprule
Principle & Data sector & Extremum principle & Reference \\
\midrule
Maximum entropy on packing & Nodes (candidate shell centers) & Maximize entropy under isotropy (Axiom 2) & Paper~0~\cite{paper0} \\
\addlinespace
Rayleigh--Ritz on graph Hamiltonian & Node wavefunctions (0-cochains) & Minimize $\langle \psi | H | \psi \rangle / \langle \psi | \psi \rangle$ & Papers~1, 7~\cite{paper7} \\
\addlinespace
Wilson lattice gauge action & Edge link variables (1-cochains, SU(2)-valued) & Minimize $S_W[U] = \beta \sum_P (1 - \tfrac{1}{2}\mathrm{Re}\,\mathrm{tr}\,U_P)$ & Paper~25~\cite{paper25} $U(1)$; present paper SU(2) \\
\addlinespace
Ihara zeta path integral & Primitive closed non-backtracking walks & $\log \zeta_G(s)^{-1} = \sum_{[C]} s^{\ell(C)}$ as weighted walk sum & Paper~29~\cite{paper29} \\
\addlinespace
Spectral action on Dirac spectrum & Spinor-bundle spectrum ($|\lambda_n|, g_n$) & $\mathrm{Tr}\,f\bigl(D / \Lambda\bigr)$ over modes & Paper~28~\cite{paper28} \\
\bottomrule
\end{tabular}
\end{table}

\paragraph*{What each sector is about.}
The node sector carries the scalar matter content (the wavefunction
amplitudes) and hosts two action principles: Paper~0's packing
axioms as a max-entropy statement (``maximize entropy under
isotropy''), which \emph{builds} the graph, and the Rayleigh--Ritz
principle on the built graph's Hamiltonian, which computes the
graph's spectrum.  The edge sector carries gauge content (Paper~25's
$U(1)$ phases, this paper's SU(2) link variables) and hosts the
Wilson action.  The walk sector aggregates edge data into
Ihara-cycle weights and hosts a discrete path integral
(log-partition function = walk sum).  The Dirac spectrum, finally,
is the specific data set on which the spectral action of
noncommutative-geometry type is computed; Paper~28's QED spectral
sums are literally this.

\paragraph*{The packing--Wilson duality.}
Two of the five principles stand out as structural duals.  Paper~0's
Axiom 2 (geometric indifference) is a max-entropy principle on node
data: among all candidate discrete packings compatible with Axiom 1
(binary distinguishability), the entropy-maximizing one is selected.
The Wilson action is a min-action principle on edge data: among all
SU(2) link configurations, those minimizing plaquette curvature are
selected in the continuum ($\beta \to \infty$) limit.  The two
principles live on complementary cochain degrees (0-form vs 1-form)
and extremize in opposite directions (max vs min), but they are
structurally compatible: Paper~0's max-entropy on nodes fixes
\emph{which} graph the Wilson action lives on, and the Wilson action
fixes \emph{how} gauge dynamics runs on it.  Nothing in the
mathematics forbids a joint variational principle on the full
(node, edge) data; we note this for future work but do not pursue it
here.

\paragraph*{What this section does and does not claim.}
The observation is descriptive: the GeoVac framework, as it currently
stands, presents five independent variational structures, each
localized to a different sector of the graph data.  We do not claim
that these five can be reduced to a single grand principle, nor that
one is more fundamental than the others.  Each is a tool matched to a
data type.  The utility of naming them together is that it makes the
project's full toolkit visible in one place: the framework is not
reducible to ``diagonalize a graph Laplacian,'' because its data has
more kinds of structure than nodes alone.

% ===================================================================
\section{Yang--Mills Adjacency: What Is and Is Not Claimed}
\label{sec:scope}
% ===================================================================

The present paper inherits the language of Wilson lattice gauge theory.
The rhetoric rule of CLAUDE.md~\S1.5 requires that we be explicit about
scope.  We enumerate what is done and what is not.

\paragraph*{What this paper establishes.}  A gauge-invariant, finite,
Haar-normalizable non-abelian lattice gauge theory on the finite
compact GeoVac Hopf graph at any $n_{\max}$, with (i) link variables
in $\mathrm{SU}(2)$, (ii) plaquettes as primitive closed
non-backtracking walks, (iii) Wilson action and partition function
well-defined without renormalization, (iv) exact $U(1)$ reduction to
Paper~25 in the maximal-torus limit, (v) $L_1 = B^{\top} B$
identified as the weak-coupling kinetic term.  All 26 tests in
\texttt{tests/test\_su2\_wilson\_gauge.py} pass, including the
numerical $U(1)$-reduction test (lines 142--160) and end-to-end gauge
invariance at machine precision.

\paragraph*{What this paper does NOT establish.}
\begin{itemize}
\item \emph{Yang--Mills mass gap on $\mathbb{R}^4$.}  The Clay
  Millennium Problem requires a continuum-field-theory construction
  of pure Yang--Mills on 4D Minkowski or Euclidean space, proof of a
  positive mass gap, and proof that no interacting scale-invariant
  continuum limit exists.  Our construction lives on a fixed finite
  compact graph; there is no continuum limit of $\mathbb{R}^4$ inside
  it.
\item \emph{Confinement in the conventional sense.}  As noted in
  Section~\ref{sec:results_MC}, the $n_{\max} = 3$ graph has a single
  plaquette-length class, so the area/perimeter-law diagnostic is
  degenerate.  Finite-size graphs with multiple plaquette classes
  (e.g., $n_{\max} \geq 5$) would be needed to even state the
  diagnostic.
\item \emph{Lorentzian signature or dynamics.}  This is a Euclidean
  lattice gauge theory on a spatial slice: no time direction, no
  Wick rotation, no $S$-matrix, no scattering.  Dynamics in the
  usual sense is absent.
\item \emph{Renormalization or continuum limit.}  The bare Wilson
  action is the whole story on a finite graph.  Whether the
  $n_{\max} \to \infty$ limit recovers continuum SU(2) Yang--Mills
  on the unit $S^3$, and in what sense, is an open question we do
  not address here.
\item \emph{A new derivation of $\alpha$.}  Paper~2's conjectural
  combination rule $K = \pi(B + F - \Delta)$ is not refined by the
  present construction.  Paper~25~\S IV read the three ingredients as
  Casimir-matter trace / Fock-Dirichlet gauge zeta / Dirac-boundary
  count; the non-abelian SU(2) Wilson structure does not produce a
  new $K$-like object or a non-abelian ``fine-structure constant''
  coupling, and we make no claim in that direction.
\end{itemize}

\paragraph*{Relationship to the Clay problem.}
The mathematical vocabulary is shared (lattice gauge theory,
non-abelian link variables, plaquette action, Wilson loops), but the
setting differs categorically.  The Clay problem is about continuum
field theory on a non-compact 4D spacetime; the present construction
is about discrete gauge theory on a compact 3D-graph spatial slice.
We use Wilson's formalism because it is the correct tool for
non-abelian lattice gauge theories on finite graphs; we do not
imply that the construction transports to $\mathbb{R}^4$.

% ===================================================================
\section{Open Questions}
\label{sec:open}
% ===================================================================

\subsection{Matter coupling: Dirac fermions on the Hopf graph}

The GeoVac framework's Tier-2 relativistic pipeline~\cite{paper14}
builds spin-ful composed qubit Hamiltonians in the
$(\kappa, m_j)$ Dirac basis on $S^3$.  These are matter sectors on
the same graph whose gauge sector we have built here.  Coupling the
two---Dirac fermion matter on nodes, $\mathrm{SU}(2)$ Wilson gauge on
edges---would be the first matter$+$gauge lattice theory in the
GeoVac project.  The construction is standard in principle (covariant
hopping amplitudes $\bar\psi_i U_{ij} \psi_j$), but on a
triangle-free simplicial 1-complex with Dirac spinors it would
require the Szmytkowski angular labels of Paper~14's Tier~2 to be
reconciled with the Wilson link-variable orientation convention.  A
clean demonstrator would be: does the spinor spectrum feel the
non-trivial $\mathrm{SU}(2)$ topology (i.e., is the Dirac operator
sensitive to the $\beta_1 = 2$ harmonic 1-forms at $n_{\max} = 3$ when
the gauge field is non-trivially topological)?

\subsection{Larger graphs and the confinement diagnostic}

At $n_{\max} \geq 5$, the Coulomb graph acquires multiple plaquette-length
classes, making a Wilson-loop family indexed by area available for
the first time.  The natural question: on the $n_{\max} = 5, 6$
Coulomb graphs, does the Wilson loop exhibit area-law behavior at
small $\beta$ and perimeter-law behavior at large $\beta$?  Running
this is computationally straightforward (the Metropolis update scales
as $|E|^2$ per sweep; $n_{\max} = 5$ has $|E| \sim 90$, manageable).
The result would distinguish a confining non-abelian theory from a
deconfined one on the GeoVac graph; Paper~25~\S VII's broader
questions about lattice-gauge structure would receive an immediate
sharpening.

\subsection{SU(2) analog of the Ihara zeta}

Paper~29 built the (scalar-valued) Ihara zeta of the GeoVac Hopf
graphs from primitive closed non-backtracking walk counts.  A natural
non-abelian generalization would weight each primitive walk $[C]$ by
a character $\chi_j(U_{[C]})$ of its $\mathrm{SU}(2)$ holonomy,
producing a character-valued zeta function.  Whether the resulting
object has a well-defined Ihara--Bass-type determinantal expression,
or whether it satisfies a graph-Riemann Hypothesis analog, is
speculative.  We record the question without pursuing it.

\subsection{SU(2) analog of Paper 2's $K = \pi(B + F - \Delta)$}

Paper~25~\S VII.A suggested that a non-abelian analog of the Paper~2
combination rule might exist on the $S^3$ graph.  The SU(2) Wilson
structure of the present paper does not by itself produce one; the
Wilson action is coupling-insensitive in a way that Paper~2's $K$ is
not.  A more promising route (if any) would couple the SU(2) Wilson
gauge to Dirac-spinor matter (first open question above) and examine
the combined spectral-gauge invariants.  We do not claim such a route
will succeed; we record it as a natural follow-up within a
conjectural framework.

\subsection{Continuum limit}

The continuum limit of lattice gauge theory on refined Alon--Boppana
sequences of graphs converging to a target manifold is a technical
question that has been addressed in specific cases (hypercubic
lattices converging to $\mathbb{R}^4$, spherical lattices converging
to $S^3$).  Whether the $n_{\max} \to \infty$ sequence of GeoVac
graphs admits a well-posed continuum limit, and whether that limit is
SU(2) Yang--Mills on the unit $S^3$ in the Hodge--de Rham sense, is
open.  The relevant spectral data is available in
\texttt{geovac/hopf\_bundle.py}; a careful analysis has not been done.

% ===================================================================
\section{Conclusion}
\label{sec:conclusion}
% ===================================================================

Sprint 4 Track RH-Q constructed SU(2) Wilson lattice gauge theory on
the GeoVac Hopf graph (module \texttt{geovac/su2\_wilson\_gauge.py},
26 tests passing).  The present paper formalizes that construction
and places it in context relative to Paper~25's abelian $U(1)$
predecessor.

Three structural results summarize the content:
(1)~the maximal-torus reduction of the $\mathrm{SU}(2)$ Wilson action
recovers Paper~25's $U(1)$ Wilson--Hodge action exactly, so
Paper~25 is the Cartan-subalgebra sector of a non-abelian theory;
(2)~the edge Laplacian $L_1 = B^{\top} B$ that Paper~25 introduced as
a ``gauge propagator'' is the weak-coupling kinetic term of the
non-abelian Wilson action, with non-abelian self-interactions
entering only at quartic order in the gauge field;
(3)~plaquette enumeration on the $S^3$ Coulomb graph matches
Paper~29's Ihara cycle counts, and direct Monte Carlo on $n_{\max} = 3$
gives monotonic $\beta$-dependence of the Wilson loop expectation
(confirming the character-expansion leading order at the $\sim 20\%$
level, as expected from the shared-edge correction).

We close with a framework observation.  The $S^3 = \mathrm{SU}(2)$
coincidence is structurally overdetermined: $S^3$ appears in the
framework as Fock's projection of the Coulomb problem (Paper~7), as
the underlying manifold of the $(n, l, m_l)$ Hopf graph (Paper~14),
as the spin-1/2 carrier of the Dirac sector (Paper~14 Tier-2), and
now as the gauge group of the non-abelian Wilson construction.  Four
independent structural roles on the same 3-manifold, each needing
only the simplest compact simply-connected non-abelian Lie group of
rank~1.  We do not read this as evidence that $S^3$ is fundamental in
any ontological sense (CLAUDE.md~\S1.5 rhetoric); we do observe that
$S^3$ is, in a specific technical sense, the minimal object that
supports all four roles simultaneously, and we record the convergence
as a fact.

The project now contains five action principles---Paper~0's
max-entropy on nodes, Rayleigh--Ritz on the graph Hamiltonian,
Paper~25's and this paper's Wilson action on edges, Paper~29's Ihara
zeta path integral on walks, and Paper~28's spectral action on the
Dirac spectrum---each matched to a distinct sector of the graph
data.  None reduces to any of the others.  The Wilson action has,
with this paper, a genuine non-abelian sibling to its $U(1)$
predecessor; the rest of the table is left as is.

% ===================================================================
% References
% ===================================================================

\begin{thebibliography}{99}

\bibitem{wilson1974}
K.~G.~Wilson, ``Confinement of quarks,''
\textit{Phys.~Rev.~D}\ \textbf{10}, 2445--2459 (1974).

\bibitem{creutz1983}
M.~Creutz, \textit{Quarks, Gluons and Lattices},
Cambridge University Press, Cambridge (1983).

\bibitem{kogut_susskind1975}
J.~Kogut and L.~Susskind, ``Hamiltonian formulation of Wilson's
lattice gauge theories,''
\textit{Phys.~Rev.~D}\ \textbf{11}, 395--408 (1975).

\bibitem{luscher1982}
M.~L\"uscher, ``Topology of lattice gauge fields,''
\textit{Commun.~Math.~Phys.}\ \textbf{85}, 39--48 (1982).

\bibitem{menotti_onofri1981}
P.~Menotti and E.~Onofri, ``The action of SU(N) lattice gauge
theory in terms of the heat kernel on the group manifold,''
\textit{Nucl.~Phys.~B}\ \textbf{190}, 288--300 (1981).

\bibitem{fegan1983}
H.~D.~Fegan, ``The heat equation on a compact Lie group,''
\textit{Trans.~Amer.~Math.~Soc.}\ \textbf{246}, 339--357 (1978).

\bibitem{lim2020}
L.-H.~Lim, ``Hodge Laplacians on graphs,''
\textit{SIAM Review}\ \textbf{62}, 685--715 (2020).

\bibitem{schaub2020}
M.~T.~Schaub, A.~R.~Benson, P.~Horn, G.~Lippner, and A.~Jadbabaie,
``Random walks on simplicial complexes and the normalized Hodge 1-Laplacian,''
\textit{SIAM Review}\ \textbf{62}, 353--391 (2020).

\bibitem{marcolli_vs2014}
M.~Marcolli and W.~D.~van Suijlekom,
``Gauge networks in noncommutative geometry,''
\textit{J.~Geom.~Phys.}\ \textbf{75}, 71--91 (2014),
arXiv:1301.3480.

\bibitem{perez_sanchez2024}
C.~I.~Perez-Sanchez,
``Bratteli networks and the Spectral Action on quivers,''
arXiv:2401.03705 (2024).

\bibitem{perez_sanchez2025}
C.~I.~Perez-Sanchez,
``Comment on `Gauge networks in noncommutative geometry','',
arXiv:2508.17338 (2025).

\bibitem{paper0}
GeoVac Project, ``Geometric packing and the origin of quantum
numbers,'' Paper~0 (2025).

\bibitem{paper2}
GeoVac Project, ``The fine structure constant from Hopf bundle
spectral invariants,'' Paper~2 (2025).

\bibitem{paper7}
GeoVac Project, ``The Dimensionless Vacuum: $S^3$ Conformal
Equivalence and 18 Symbolic Proofs,'' Paper~7 (2025).

\bibitem{paper14}
GeoVac Project, ``Structurally Sparse Qubit Hamiltonians from Natural
Geometry,'' Paper~14 (2025).

\bibitem{paper18}
GeoVac Project, ``Spectral-Geometric Exchange Constants,'' Paper~18
(2026).

\bibitem{paper22}
GeoVac Project, ``Potential-Independent Angular Sparsity Theorem,''
Paper~22 (2026).

\bibitem{paper24}
GeoVac Project, ``The Bargmann--Segal Lattice: $\pi$-Free
Discretization of the 3D Harmonic Oscillator on $S^5$,'' Paper~24
(2026).

\bibitem{paper25}
GeoVac Project, ``The Hopf Graph as a Lattice Gauge Structure: A
Framework Observation,'' Paper~25 (2026).

\bibitem{paper28}
GeoVac Project, ``QED on $S^3$: Spectral Geometry of Perturbative
Transcendentals,'' Paper~28 (2026).

\bibitem{paper29}
GeoVac Project, ``The GeoVac Hopf Graphs Are Ramanujan: Ihara Zeta,
Graph-RH, and a Scope Boundary on Selberg-on-Hydrogen,'' Paper~29
(2026).

\bibitem{ihara1966}
Y.~Ihara, ``On discrete subgroups of the two by two projective linear
group over $p$-adic fields,''
\textit{J.~Math.~Soc.~Japan}\ \textbf{18}, 219--235 (1966).

\bibitem{rh_q_memo}
GeoVac Project, ``Track RH-Q: SU(2) Wilson Lattice Gauge Theory on
the $S^3 = \mathrm{SU}(2)$ GeoVac Hopf Graph,''
\texttt{debug/su2\_wilson\_gauge\_memo.md}, April 2026.

\end{thebibliography}

\end{document}
