%% ===================================================================
%% Paper 18 §IV drop-in proposal (Track T5, Dirac-on-S³ Tier 2 sprint).
%%
%% Target file:  papers/core/paper_18_exchange_constants.tex
%% Target site:  immediately AFTER the "Odd-zeta content from first-order
%%               spectral operators (new tier)" paragraph (currently the
%%               last \paragraph before the "Parallel to Paper 24"
%%               paragraph — ~line 740).
%% PI decision:  T6 will apply (or skip) this drop-in at the sprint commit.
%%               Do NOT paste into the core paper without PI approval.
%%
%% This is the T5 deliverable specified in docs/dirac_s3_tier2_sprint_plan.md:
%%   "new subtier 'spinor-intrinsic content' for α² fine-structure factors
%%    and √(1-(Zα)²) coefficient ring."
%%
%% Structural parallel: this paragraph is to the T2 Breit-Pauli SO block
%% what the Tier-1 "Odd-zeta content" paragraph is to the Dirichlet-series
%% result on S³ — a first-order-operator, spinor-bundle analog of Paper 24's
%% second-order-operator, scalar-bundle calibration result.
%% ===================================================================

\paragraph{Spinor-intrinsic content from first-order operators on a
spinor bundle (new subtier).}
The Dirac-on-$S^3$ Tier 2 sprint (2026, Track T5) identified a second
piece of structurally new transcendental content in the GeoVac
framework: the fine-structure constant squared~$\alpha^2$ and the
relativistic radial coefficient $\gamma := \sqrt{1 - (Z\alpha)^2}$,
arising jointly from first-order spectral operators acting on curved-space
\emph{spinor bundles}. The mechanism is the Breit--Pauli reduction of
the Dirac equation: the leading-order spin-orbit coupling
\begin{equation}\label{eq:bp_so}
  H_{\mathrm{SO}}
  \;=\; \tfrac{1}{2 m^2 c^2}\,\tfrac{1}{r}\,\tfrac{dV}{dr}\,\mathbf{L}\cdot\mathbf{S}
  \;=\; \tfrac{Z\alpha^2}{2}\,\tfrac{1}{r^3}\,\mathbf{L}\cdot\mathbf{S}
  \quad\text{(Coulomb),}
\end{equation}
when evaluated in the $(\kappa, m_j)$ basis using Szmytkowski's
reduction $\langle \mathbf{L}\cdot\mathbf{S}\rangle = -(\kappa+1)/2$ and
the closed-form hydrogenic $\langle 1/r^3\rangle_{n,l}
= Z^3/[n^3\, l(l+\tfrac{1}{2})(l+1)]$, produces matrix elements
\begin{equation}\label{eq:bp_so_matrix}
  \langle n,\kappa,m_j|\,H_{\mathrm{SO}}\,|n,\kappa,m_j\rangle
  \;=\; -\,\frac{Z^4\,\alpha^2\,(\kappa+1)}{4\,n^3\, l(l+\tfrac{1}{2})(l+1)},
\end{equation}
with $l = |\kappa + \tfrac{1}{2}| - \tfrac{1}{2}$ and the Kramers
cancellation $H_{\mathrm{SO}} = 0$ at $l=0$ (where $\kappa = -1$ forces
the numerator to zero before the formally divergent $\langle 1/r^3\rangle$
is evaluated). Symbolically, Eq.~(\ref{eq:bp_so_matrix}) is a sympy-exact
rational in $(Z, n, l)$ times $\alpha^2$, with zero $\pi$, zero $\zeta$,
and zero transcendentals beyond~$\alpha$ itself.

The full-Dirac radial corrections enter through
$\gamma := \sqrt{1 - (Z\alpha)^2}$, which appears in the Martínez-y-Romero
recursions for relativistic $\langle r^k\rangle_{\text{Dirac}}$ but is not
required at the Breit--Pauli leading order (Track T1 reserved $\gamma$
symbolically; Track T2 does not bind it). Algebraically, $\gamma$
satisfies the polynomial relation
\begin{equation}\label{eq:gamma_def}
  \gamma^2 + (Z\alpha)^2 \;=\; 1,
\end{equation}
so $\gamma \in \mathbb{Q}(\alpha^2)[\sqrt{\cdot}]$, i.e.\ it is
algebraic of degree~2 over $\mathbb{Q}(\alpha^2)$. This is the
relativistic analog of the non-relativistic radial matrix elements
already registered as algebraic in Sec.~\ref{sec:algebraic_registry}.

This spinor-intrinsic content is categorically different from the
four existing tiers (intrinsic, calibration, embedding, flow/composition)
and from the newly added odd-zeta tier. The distinctions:

\begin{itemize}
  \item \textbf{Source:} a first-order spectral operator (the Dirac
    operator or the Breit--Pauli reduction of it) acting on a
    \emph{spinor bundle} over curved space. Calibration constants and
    the odd-zeta tier both arise on scalar fields; the spinor-intrinsic
    content requires the bundle to carry spin.

  \item \textbf{Mechanism:} the $\alpha^2$ prefactor is not a basis
    regularization (as $\kappa$ is) and not a spectral sum (as
    $\zeta_R(2)$ and $\zeta_R(3)$ are); it is the coupling strength that
    multiplies the spin-orbit operator, arising from the Foldy--Wouthuysen /
    Breit--Pauli expansion of the relativistic kinetic energy. It is
    present in the Hamiltonian \emph{coefficients}, not in the basis or
    spectrum.

  \item \textbf{Dependency:} depends only on the existence of spin
    coupling in the operator. Independent of discretization, basis
    choice, and factorization topology. Any first-order operator that
    couples $\mathbf{L}$ and $\mathbf{S}$ will introduce $\alpha^2$;
    any full-Dirac radial recursion will introduce~$\gamma$.

  \item \textbf{Algebraic status:} $\alpha$ is transcendental (a
    dimensionless physical constant whose value must be supplied
    empirically), but $\alpha^2$ appears polynomially in every
    spinor-intrinsic coefficient to the order at which the Breit--Pauli
    expansion is truncated ($\alpha^2$ at leading order, $\alpha^4$ with
    Darwin + mass-velocity, etc.). $\gamma$ is algebraic of degree~2
    over $\mathbb{Q}(\alpha^2)$ via Eq.~(\ref{eq:gamma_def}). Together
    they generate the ring
    \[
      R_{\mathrm{sp}} \;:=\; \mathbb{Q}\bigl(\alpha^2\bigr)
        \bigl[\gamma\bigr]/\bigl(\gamma^2 + (Z\alpha)^2 - 1\bigr),
    \]
    in which every Tier-2 coefficient lies. A sympy-based certifier
    (``\texttt{geovac/spinor\_certificate.py}::verify\_spinor\_pi\_free})''
    mechanically checks that this ring is clean: no $\pi$, no $\zeta$,
    no $E_1$, no unregistered transcendental.
\end{itemize}

\paragraph{Updated structural partition.}
With the Tier 2 addition, the full Paper 18 partition of transcendental
content across bundle and operator-order now reads:

\begin{table}[h]
\caption{Operator-order $\times$ bundle classification of transcendental
  content in the GeoVac framework, after the Tier 1 and Tier 2
  Dirac-on-$S^3$ sprints.}
\label{tab:bundle_operator_tiers}
\begin{ruledtabular}
\begin{tabular}{llll}
  Tier & Example transcendentals & Operator order & Bundle \\
  \hline
  Intrinsic         & $\pi^{d/2}$ Weyl prefactors & --- & scalar \\
  Calibration       & $\kappa = -1/16$, $F = \pi^2/6$ (even $\zeta$)
                    & 2nd (Laplace--Beltrami)
                    & scalar on curved space \\
  Embedding         & $e^a E_1(a)$,  $1/r_{12}$
                    & ---
                    & projection from graph to $\mathbb{R}^3$ \\
  Flow / composition & piecewise $\mu(\rho,R)$, PK pseudopot.
                    & ---
                    & multi-geometry factorization \\
  Odd-zeta (Tier 1 new) & $\zeta_R(3), \zeta_R(5), \dots$
                    & 1st (Dirac)
                    & Dirac spectrum on curved space \\
  Spinor-intrinsic (Tier 2 new)
                    & $\alpha^2$, $\gamma = \sqrt{1-(Z\alpha)^2}$
                    & 1st (Dirac / Breit--Pauli)
                    & spinor bundle over curved space \\
\end{tabular}
\end{ruledtabular}
\end{table}

The two Tier-1/Tier-2 additions are parallel but distinct: Tier 1
($\zeta$) enters through the \emph{spectrum} of the curved-space Dirac
operator (Camporesi--Higuchi eigenvalues $n+3/2$ and degeneracies
$2(n+1)(n+2)$ produce the Dirichlet-series identity
Eq.~(\ref{eq:dirac_dirichlet_zeta3})); Tier 2 ($\alpha^2$, $\gamma$)
enters through the \emph{coupling} of spin to orbital angular momentum
in the Hamiltonian, not through the basis or spectrum. Neither
introduces $\pi$ beyond what is already present in the calibration
tier; both are orthogonal to the embedding and flow tiers.

\paragraph{Why ``spinor-intrinsic'', not ``calibration''.}
Calibration constants live in the \emph{scalar} spectrum on curved
space (Paper~24 HO rigidity: the Bargmann--Segal edge weights are
$\pi$-free rationals; the calibration $\pi^2/6$ enters only through an
infinite-sum analysis of the scalar Fock Dirichlet series at $s = 4$).
Spinor-intrinsic $\alpha^2$ is a \emph{coupling} content --- it does
not appear in the basis construction or in the spectrum of the
operator; it appears in the Hamiltonian coefficients once spin is
coupled to orbital angular momentum. This distinction is taxonomic, not
cosmetic: it predicts that any future tier of the framework introducing
relativistic or QED corrections (e.g., $\alpha^4$ Darwin and
mass-velocity, $\alpha^3$ Lamb shift, Breit interaction
corrections $\alpha^2$ in $V_{ee}$) will populate this same subtier,
adding powers of $\alpha$ and algebraic combinations of $\gamma$, but
will \emph{not} create new subtiers and will \emph{not} bleed into
calibration or embedding content.

\paragraph{Parallel to Paper 24 and to the Tier-1 odd-zeta tier.}
Paper~24 established that calibration $\pi$ is Coulomb-specific
(second-order Riemannian operators with nonlinear projections). Tier~1
(2026) added that odd-zeta content $\zeta_R(3)$ is the first-order,
scalar-spectrum analog on $S^3$. Tier~2 (2026) completes the parallel:
$\alpha^2$ and $\gamma$ are the first-order, spinor-coupling analog ---
the content introduced when a first-order operator acts on a \emph{spinor}
bundle rather than a scalar field. The three together describe the
transcendental architecture of curved-space quantum mechanics with or
without spin, to first or second order:

\begin{center}
\begin{tabular}{l|cc}
  & \textbf{2nd-order operator} & \textbf{1st-order operator} \\
  \hline
  \textbf{scalar bundle}  & calibration $\pi$ (even $\zeta$)
                          & odd-zeta tier ($\zeta_R(3), \zeta_R(5), \dots$) \\
  \textbf{spinor bundle}  & (not yet encountered)
                          & \textbf{spinor-intrinsic ($\alpha^2$, $\gamma$)} \\
\end{tabular}
\end{center}

The lower-left cell (2nd-order on spinor bundle) would describe
e.g.\ a squared Dirac operator or a Pauli--Villars regularized 2-spinor
action. No GeoVac Hamiltonian to date produces this content; Tier~3+
may or may not.

\paragraph{Certification and taxonomy wiring.}
The spinor-intrinsic ring $R_{\mathrm{sp}}$ is certified mechanically by
\texttt{verify\_spinor\_pi\_free} in
\texttt{geovac/spinor\_certificate.py}
(Track~T5, v2.11.0). The certifier walks the sympy expression tree of a
coefficient and rejects any appearance of $\pi$, $\zeta$, $\log$, $E_1$,
or any Symbol outside the registered set $\{Z, \alpha, \gamma\}$
(user-extensible for downstream indices). T3's symbolic spin-orbit block
\texttt{build\_so\_hamiltonian\_block(n\_max, Z\_sym, alpha\_sym)} passes the
certifier cleanly for all tested $n_{\max}$ up to~4; manual contamination
by $\pi \cdot \alpha^2 / 96$ is rejected with a clear diagnostic. See
the design memos \texttt{spin\_orbit\_design\_memo.md} §``Paper 18
classification'' and \texttt{spin\_ful\_composed\_design\_memo.md} §8 for
the per-block audit, and the sprint plan
\texttt{docs/dirac\_s3\_tier2\_sprint\_plan.md} Track~T5 for scope.

%% ===================================================================
%% End of §IV drop-in. The "Parallel to Paper 24" paragraph that
%% originally appeared here stays — it talks about the odd-zeta tier,
%% which this subtier complements rather than replaces.
%% ===================================================================
