% Extracted from Paper_8_Bond_Sphere_Sturmian.tex (Section XII)
% Moved to archive during v1.0.0 cleanup, March 12, 2026
% This section provides a complete MO-FCI specification for the Sturmian
% bond sphere basis. Superseded by the prolate spheroidal approach (Paper 11).

\section{Molecular Orbital FCI Specification}
\label{sec:mo_fci}

This section provides a complete theoretical specification for FCI in
the molecular Sturmian basis.  A reader should be able to implement
the v0.9.31 solver from this section alone.

\subsection{Basis Functions}

The FCI basis consists of molecular Sturmian functions labeled by
$(m, n_{\text{sph}}, n_{\text{rad}})$---the magnetic quantum number,
angular nodal index, and radial nodal index in the prolate spheroidal
coordinate system.  For each $(m, n_{\text{sph}}, n_{\text{rad}})$,
the $\beta_k$ eigenvalue is computed by solving the prolate spheroidal
matching condition at the self-consistent $p_0$.

\subsection{Hamiltonian Matrix Elements}

\paragraph{Diagonal.}
Every orbital has the same diagonal energy:
\begin{equation}
\langle k | \hat{h}_1 | k \rangle = -\frac{p_0^2}{2}.
\end{equation}
Nuclear repulsion $V_{NN} = Z_A Z_B / R$ is added as a constant.

\paragraph{One-electron off-diagonal.}
The off-diagonal $H_1$ matrix elements couple MOs with the same $m$
at the bond angle $\gamma$.  These are the $D$-matrix elements
weighted by the nuclear charges:
\begin{equation}
\langle k' | \hat{h}_1 | k \rangle
= -\frac{Z_A + Z_B}{p_0}\, D^{(n)}_{k',k}(\gamma)\,\beta_k,
\quad k' \neq k,\; m_{k'} = m_k.
\end{equation}

\paragraph{Two-electron integrals.}
The two-electron repulsion integrals are computed between MOs projected
onto atom-centered functions via the prolate spheroidal wavefunctions.
For each MO $k$, the projection onto center $\alpha \in \{A, B\}$
gives expansion coefficients $c_{k,\alpha}^{(n,l,m)}$, and the
two-electron integrals are
\begin{equation}
\langle kl | rs \rangle = \sum_{\alpha} \sum_{n_i l_i m_i}
c_{k,\alpha}^* c_{l,\alpha} c_{r,\alpha}^* c_{s,\alpha}\,
F^0(\alpha; n_k l_k, n_r l_r),
\end{equation}
where $F^0$ are the same-center Slater direct integrals.

\subsection{CI Expansion}

The CI expansion is over Slater determinants of the molecular Sturmian
spin-orbitals.  The Hamiltonian assembly follows the same Slater--Condon
rules as the atom-centered FCI.

\subsection{Self-Consistency}

The self-consistency loop is:
\begin{enumerate}
\item Initialize $p_0^{(0)} = \sqrt{(Z_A^2 + Z_B^2)/2}$.
\item At each iteration $k$:
  \begin{enumerate}
  \item Solve the prolate spheroidal eigenvalue problem for all
  $\beta_k^{(k)}$ at the current $p_0^{(k)}$.
  \item Build the FCI Hamiltonian with the current $p_0^{(k)}$,
  $\beta_k^{(k)}$, and $\gamma^{(k)}$.
  \item Diagonalize to obtain $E_{\text{mol}}^{(k)}$.
  \item Update $p_0^{(k+1)} = \sqrt{-2E_{\text{mol}}^{(k)}}$
  (with damping $\alpha \leq 0.5$ if needed).
  \end{enumerate}
\item Converge when $|p_0^{(k+1)} - p_0^{(k)}| < \varepsilon$.
\end{enumerate}
